### 2020-07-10 MidWest_DataManagement_20200706.Rmd
Add: MidWest_DataManagement_2020706.Rmd

---
title: "MidWest Data Management"
author: "Seoghyun Kim"
date: "2/5/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r # WD and Package}
#Read Data
setwd("D:\\UNCG works\\MidWestData\\UM_TN_BiomonData\\For analysis\\Data management")
getwd()

# install package
library(reshape2);library(plyr);library(arm);library(ggplot2);library(scales);library(knitr);library(tidyr);library(bbmle);library(chron);library(grid);library(fmsb);library(foreign)

require(dplyr)

```

# 1. MN Data Management

## (1) Data Property
Three datasets were used to manage data. Each dataset has different property, thus we need to use and filter them out. Particularly, 'Visit_originalfile.csv' has date, 'Station_originalfile.csv' has GPS cordinates, and 'FishData_originalfile.csv' has fish data.
Data property:
(1) Station_originalfile.csv: FieldNum (site ID), GPS coodinates
(2) Visit_originalfile.csv: FieldNum (site ID), VisitNum (Unique sampling ID), Date
(3) FishData_originalfile.csv: FieldNum (site ID), VisitNum (Unique sampling ID), Fish list
Therefore, mating each file based on FieldNum (site ID) and VisitNum (Unique sampling ID) is the key process for the data management, and missing data should be removed.
```{r MN data}
## Read Data ##
# Visit data - this file has sampling date
MN.Visit <- read.csv("data/org-data_mn_visit.csv", header=TRUE, strip.white=TRUE)

# Station data - this file has GPS data
MN.Station <- read.csv("data/org-data_mn_station.csv", header=TRUE, strip.white=TRUE)

# Fish sampling data - this file has fish sampling data
MN.FishData <- read.csv("data/org-data_mn_fish.csv", header=TRUE, strip.white=TRUE)
MN.FishData$CommonName <- gsub(" ", "_", MN.FishData$CommonName) # replace space to underscore (under bar)
MN.FishData$CommonName <- toupper(MN.FishData$CommonName) # change common name format
```

## (2) Fish data treatment
This is to remove all unidentified species and hybrids that appeared in data. 
```{r MN Fish data treatment}
# Remove unidentified species and hybrid
MN.FishData <-MN.FishData[!(MN.FishData$CommonName %in% c("AMEIURUS_SPP.","CAMPOSTOMA_SPP.","CARPIODES_SPP.","CATOSTOMIDAE_-_UNIDENTIFIED","COMMON_SHINER_X_CREEK_CHUB","COMMON_SHINER_X_EMERALD_SHINER","COMMON_SHINER_X_HORNYHEAD
","COMMON_SHINER_X_SOUTHERN_REDBELLY_DACE","COMMON_SHINER_X_STONEROLLER","COMMON_SHINER_X_UNKNOWN","COMMON_SHINER_X_HORNYHEAD","COTTUS_SPP.","CREEK_CHUB_X_HORNYHEAD_CHUB","CREEK_CHUB_X_UNKNOWN","CYPRINELLA_SPP.","CYPRINIDAE_-_UNIDENTIFIED","FAM:_LAMPREY","FAM:_MINNOWS","GEN:_BUFFALOS","GEN:_CARPSUCKERS","GEN:_CATOSTOMUS","GEN:_COMMON_SUNFISHES","GEN:_ETHEOSTOMA","GEN:_NOTROPIS","GEN:_PERCINA","GEN:_PHOXINUS","GEN:_REDHORSES","GEN:_STONEROLLERS","GREEN_SUNFISH_X_BLUEGILL","GREEN_SUNFISH_X_BLUEGILL_X_PUMPKINSEED","GREEN_SUNFISH_X_ORANGESPOTTED_SUNFISH","GREEN_SUNFISH_X_PUMPKINSEED","HIODON_SPP.","HYBOGNATHUS_SPP.","HYBRID:_COMMON_SHINER_X_SO._REDBELLY_DACE","HYBRID:_GREEN_SUNF._X_BLUEGILL","HYBRID_MINNOW","HYBRID_PHOXINUS","HYBRID_SUNFISH","ICTIOBUS_SPP.","LAMPREY_AMMOCOETE","LAMPREYS_(AMMOCOETE)","LAMPREYS","LEPISOSTEUS_SPP.","MOXOSTOMA_SPP.","NO_FISH_CAPTURED","NOTROPIS_SPP.","PERCINA_SPP.","POMOXIS_SPP.","PUMPKINSEED_X_BLUEGILL","PUMPKINSEED_X_WARMOUTH","ROSYFACE/CARMINE_SHINER","RUSTY_CRAYFISH","STICKLEBACKS_UNSP.","SUBFAM:_BUFFALO/CARPSUCKERS","TIGER_TROUT","TIGER_TROUT_(I21_X_I22)", "STONEROLLERS","PEARL_DACE", "QUILLBACK_CARPSUCKER", "GOLDFISH")),]

# Change name
MN.FishData[MN.FishData=="AMERICAN_BROOK_LAMPREY_(AMMOCOETE)"]<- "AMERICAN_BROOK_LAMPREY"
MN.FishData[MN.FishData=="CHESNUT_LAMPREY_(AMMOCOETE)"]<- "CHESTNUT_LAMPREY"
MN.FishData[MN.FishData=="NORTHERN_BROOK_LAMPREY_(AMMOCOETE)"]<- "NORTHERN_BROOK_LAMPREY"
MN.FishData[MN.FishData=="SILVER_LAMPREY_(AMMOCOETE)"]<- "SILVER_LAMPREY"
MN.FishData[MN.FishData=="SOUTHERN_BROOK_LAMPREY_(AMMOCOETE)"]<- "SOUTHERN_BROOK_LAMPREY"
MN.FishData[MN.FishData=="NORTHERN_HOG_SUCKER"]<- "NORTHERN_HOGSUCKER"
MN.FishData[MN.FishData=="TROUT-PERCH"]<- "TROUT_PERCH"
MN.FishData[MN.FishData=="TROUTPERCH"]<- "TROUT_PERCH"
```

## (3) Manage and prepare masterfile
Following script is to check/assess data property and prepare masterfile of MN data.
```{r class.source="bg-success", class.output="bg-warning"}
# MN Data management #
## (1) Extract fish sampling site number - unique sampling (VisitNum) and site number (FieldNum)
MN.Fish.site <- MN.FishData %>%
                select(VisitNum, FieldNum)

 # Check the unique number of stations based on FieldNum
MN.Fish.site01 <- MN.Fish.site[!duplicated(MN.Fish.site[c('FieldNum')]),]
str(MN.Fish.site01) # n=2545
MN.Fish.site02 <- MN.Fish.site[!duplicated(MN.Fish.site[c('VisitNum')]),]
str(MN.Fish.site02) # n= 3405 - there is a mismatch

 # Mark stations where actually caught fish 
MN.Fish.site02$FishSample <- '1' # Add one column to mark actual fish sampling
MN.Fish.site02$FieldNum <- NULL # Remove FieldNum

## (2) Extract fish sampling station from "MN.Visit" file

 # Attach Fish.site02 to MN.Visit 
MN.Visit02 <- left_join(MN.Visit, MN.Fish.site02, by = "VisitNum")
MN.Visit02$FishSample[is.na(MN.Visit02$FishSample)] <- 0 # fill NA to 0

 # Remove sites without fish sampling data
MN.Visit03 <- MN.Visit02[which(MN.Visit02$FishSample=='1'), ] 
str(MN.Visit03) # n=3049

 # How about unique number of sampling stations?
MN.Visit031 <- MN.Visit03[!duplicated(MN.Visit03[c('FieldNum')]),] 
str(MN.Visit031) # n=2372

 # Attach MN.Station to MN.Visit03 
MN.Visit04 <- left_join(MN.Visit03, MN.Station, by = "FieldNum")

 # Check multiple sampling occasions in each station (duplicate)
MN.Site.Duplicate <-aggregate(VisitNum ~ FieldNum, data = MN.Visit04, "NROW")
summary(MN.Site.Duplicate) # 530 sites were visited more than one time. Range: 2 - 7, median= 1

## (3) Prepare Masterfile

 # Extract columns from station data
MN.Visit06 <- MN.Visit04 %>%
              select(State, FieldNum, VisitNum, VisitDate, LAT8xDD, LON8xDD, StationLength) # select column

 # Extract columns from fish sampling data
MN.FishData02 <- MN.FishData %>%
                 select(VisitNum, Name1, Name2, CommonName, Number) %>% # select column
                 rename(GenusName= Name1, Speciesname= Name2) # change column name

 # Attach fish data to station data
MN.Masterfile01 <- left_join(MN.FishData02, MN.Visit06, by = "VisitNum")  
str(MN.Masterfile01) # This data still has Sampling occasion without collected fish

 # Remove station which has no fish sampling data
MN.Visit07 <- MN.Visit04 %>%
              select(VisitNum, FishSample)

MN.Masterfile02 <- left_join(MN.Visit07, MN.Masterfile01, by = "VisitNum")  
MN.Masterfile02 <- MN.Masterfile02[which(MN.Masterfile02$FishSample=='1'), ] # select stations which collected fish
MN.Masterfile02$FishSample <- NULL # Remove 'FishSample' column

 # Check duplicate
MN.Masterfile02.check1 <- MN.Masterfile02[!duplicated(MN.Masterfile02[c('FieldNum')]),] 
str(MN.Masterfile02.check1) # n=2372 correct
MN.Masterfile02.check2 <- MN.Masterfile02[!duplicated(MN.Masterfile02[c('VisitNum')]),] 
str(MN.Masterfile02.check2) # n= 3049 correct

 # Re-order column
MN.Masterfile02 <-MN.Masterfile02[c("State", "FieldNum", "VisitNum", "VisitDate", "LAT8xDD", "LON8xDD", "GenusName", "Speciesname", "CommonName",  "Number")]

 # Change column name
names(MN.Masterfile02) <- c("State", "SiteID", "VisitUniqueID", "Date", "LAT", "LON", "GenusName", "SpeciesName", "CommonName", "Abundance")

 # Several treatments
MN.Masterfile02$GenusName <- NULL # Remove genus name
MN.Masterfile02$SpeciesName <- NULL # Remove species name
MN.Masterfile.fishdata <- MN.Masterfile02 # Rename
MN.Masterfile.fishdata$VisitUniqueID <-as.character(MN.Masterfile.fishdata$VisitUniqueID) # make as character
MN.Masterfile.fishdata$SiteID <-as.character(MN.Masterfile.fishdata$SiteID) # make as character
MN.Masterfile.fishdata$Abundance <-as.numeric(MN.Masterfile.fishdata$Abundance) # make as numeric value

## (4) Masterfile including all sampling occasions (combination of site and date)

str(MN.Masterfile.fishdata)

## (5) Select the latest sampling occasion in each station

 # Split Date into month, day, year
MN.Masterfile.fishdata$Date <- as.Date(MN.Masterfile.fishdata$Date, "%m/%d/%Y")

 # Filter SiteID then select the latest Occasion
MN.Masterfile.sort <- aggregate(Date ~ SiteID, data= MN.Masterfile.fishdata, "max") # select latest sampling occasion based on sampling date
MN.Masterfile.sort$Latest <-'1' # Add Column to mark this site
MN.Masterfile.sort2 <- left_join(MN.Masterfile.fishdata, MN.Masterfile.sort, by = c("SiteID", "Date")) # Merge two data frames based on SiteID and Date

 # Select the latest sampling occasion based on mark
MN.Masterfile.sort3 <- MN.Masterfile.sort2[which(MN.Masterfile.sort2$Latest=='1'), ]
MN.Masterfile.sort3$Latest <- NULL # Remove "Latest" column
MN.Masterfile.sort3 <- MN.Masterfile.sort3[!duplicated(MN.Masterfile.sort3[c('SiteID', 'CommonName')]),]
MN.Master.fish.latest <- MN.Masterfile.sort3 # Change name

 ## Final data ##

str(MN.Master.fish.latest)
```

# 2. WI Data Management

## (1) Data Property
The file 'WI_station_info_originalfile.csv' has unique site number and GPS coordinates. The file 'WI_Fish_dataset_originalfile.csv' has Site ID, sampling date, fish abundance or information of each collected individuals. Thus, additional treatments, such as calculating abundance of each species in each sampling site, is required.
Data property:
(1) WI_station_info_originalfile.csv: WBIC (site ID), MONIT_STATION_SEQ_NO (unique sampling ID), GPS coordinates
(2) WI_Fish_dataset_originalfile.csv: WBIC (site ID), MONIT_STATION_SEQ_NO (unique sampling ID), date, collected fish (by individuals)
Similar to MN data, there are mismatch between site and fish data, thus a couple of filtering process is required.
```{r WI read data}
# Station data
WI.Station <- read.csv("WI_station_info_originalfile.csv", header=TRUE, strip.white=TRUE)

# "MONIT_STATION_SEQ_NO" in WI.Station is matched with "SiteSeqNo" in WI.FishData. Therefore, let's change the column name "MONIT_STATION_SEQ_NO" to "SiteSeqNo."
colnames(WI.Station)[which(names(WI.Station) == "MONIT_STATION_SEQ_NO")] <- "SiteSeqNo"

# Fish data
WI.FishData <- read.csv("WI_Fish_dataset_originalfile.csv", header=TRUE, strip.white=TRUE)
WI.FishData$Species <- gsub(" ", "_", WI.FishData$Species) # replace space to underscore (underbar)
WI.FishData$Species <- toupper(WI.FishData$Species) # change common name format
```

## (2) Fish data treatment
This is to remove all unidentified species and hybrids that appeared in data. 
```{r WI Fish data treatment}
# Remove unidentified species and hybrid
WI.FishData <-WI.FishData[!(WI.FishData$Species %in% c("AMEIURUS_SPP.","CAMPOSTOMA_SPP.","CARPIODES_SPP.","CATOSTOMIDAE_-_UNIDENTIFIED","COMMON_SHINER_X_CREEK_CHUB","COMMON_SHINER_X_EMERALD_SHINER","COMMON_SHINER_X_HORNYHEAD
","COMMON_SHINER_X_HORNYHEAD","COMMON_SHINER_X_SOUTHERN_REDBELLY_DACE","COMMON_SHINER_X_STONEROLLER","COMMON_SHINER_X_UNKNOWN","COTTUS_SPP.","CREEK_CHUB_X_HORNYHEAD_CHUB","CREEK_CHUB_X_UNKNOWN","CYPRINELLA_SPP.","CYPRINIDAE_-_UNIDENTIFIED","FAM:_LAMPREY","FAM:_MINNOWS","GEN:_BUFFALOS","GEN:_CARPSUCKERS","GEN:_CATOSTOMUS","GEN:_COMMON_SUNFISHES","GEN:_ETHEOSTOMA","GEN:_NOTROPIS","GEN:_PERCINA","GEN:_PHOXINUS","GEN:_REDHORSES","GEN:_STONEROLLERS","GREEN_SUNFISH_X_BLUEGILL","GREEN_SUNFISH_X_BLUEGILL_X_PUMPKINSEED","GREEN_SUNFISH_X_ORANGESPOTTED_SUNFISH","GREEN_SUNFISH_X_PUMPKINSEED","HIODON_SPP.","HYBOGNATHUS_SPP.","HYBRID:_COMMON_SHINER_X_SO._REDBELLY_DACE","HYBRID:_GREEN_SUNF._X_BLUEGILL","HYBRID_MINNOW","HYBRID_PHOXINUS","HYBRID_SUNFISH","ICTIOBUS_SPP.","LAMPREY_AMMOCOETE","LAMPREYS_(AMMOCOETE)","LAMPREYS","LEPISOSTEUS_SPP.","MOXOSTOMA_SPP.","NO_FISH_CAPTURED","NOTROPIS_SPP.","PERCINA_SPP.","POMOXIS_SPP.","PUMPKINSEED_X_BLUEGILL","PUMPKINSEED_X_WARMOUTH","ROSYFACE/CARMINE_SHINER","RUSTY_CRAYFISH","STICKLEBACKS_UNSP.","SUBFAM:_BUFFALO/CARPSUCKERS","TIGER_TROUT","TIGER_TROUT_(I21_X_I22)", "STONEROLLERS","PEARL_DACE", "QUILLBACK_CARPSUCKER", "GOLDFISH")),]

# Change name
WI.FishData[WI.FishData=="AMERICAN_BROOK_LAMPREY_(AMMOCOETE)"]<- "AMERICAN_BROOK_LAMPREY"
WI.FishData[WI.FishData=="CHESNUT_LAMPREY_(AMMOCOETE)"]<- "CHESTNUT_LAMPREY"
WI.FishData[WI.FishData=="NORTHERN_BROOK_LAMPREY_(AMMOCOETE)"]<- "NORTHERN_BROOK_LAMPREY"
WI.FishData[WI.FishData=="SILVER_LAMPREY_(AMMOCOETE)"]<- "SILVER_LAMPREY"
WI.FishData[WI.FishData=="SOUTHERN_BROOK_LAMPREY_(AMMOCOETE)"]<- "SOUTHERN_BROOK_LAMPREY"
WI.FishData[WI.FishData=="NORTHERN_HOG_SUCKER"]<- "NORTHERN_HOGSUCKER"
WI.FishData[WI.FishData=="TROUT-PERCH"]<- "TROUT_PERCH"
WI.FishData[WI.FishData=="TROUTPERCH"]<- "TROUT_PERCH"
```

## (3) Manage and prepare masterfile
```{r class.source="bg-success", class.output="bg-warning"}

##  WI Data management

## (1) Extract fish sampling station number - unique sampling (SiteSeqNo) and station number (WBIC)
WI.Fish.site <- WI.FishData %>%
                select(SiteSeqNo, WBIC)

 # Unique number of site based on WBIC
WI.Fish.site01 <- WI.Fish.site[!duplicated(WI.Fish.site[c('WBIC')]),]
str(WI.Fish.site01) # n=2830

 # Unique number of site based on SiteSeqNo
WI.Fish.site02 <- WI.Fish.site[!duplicated(WI.Fish.site[c('SiteSeqNo')]),]
WI.Fish.site02$FishSample <- '1' # Add one column to show fish sampling
WI.Fish.site02$WBIC <- NULL # Remove WBIC to avoid duplicate 
str(WI.Fish.site02)

## (2) Extract fish sampling site from "WI.Visit" file

 # Attach 'Fish.site02' (confirmed sampling sites) to 'WI.Visit (station info)' 
WI.Visit02 <- left_join(WI.Fish.site02, WI.Station, by = "SiteSeqNo")
WI.Visit02$FishSample[is.na(WI.Visit02$FishSample)] <- 0 # fill NA to 0 
WI.Visit03 <- WI.Visit02[which(WI.Visit02$FishSample=='1'), ]  # Remove stations without fish sampling
str(WI.Visit03)

 # Remove fish sampling sites which have no GPS coordinates
WI.Visit03$CALC_LL_LAT_DD_AMT[is.na(WI.Visit03$CALC_LL_LAT_DD_AMT)] <- 0 # fill NA to 0 (to remove site without GPS)
WI.Visit04 <- WI.Visit03[!(WI.Visit03$CALC_LL_LAT_DD_AMT %in% c("0")),] 
WI.Visit04$State <- 'WI' # add state
str(WI.Visit04) # unique sampling number: n=1956

 # Check duplicate 
WI.Site.Duplicate <-aggregate(SiteSeqNo ~ WBIC, data = WI.Visit04, "NROW")
summary(WI.Site.Duplicate) # 370 sites were visited more than one time. Range: 2 - 10, median= 1.

## (3) Prepare Masterfile

 # Extract columns from station data
WI.Visit05 <- WI.Visit04 %>%
              select(State, WBIC, SiteSeqNo, CALC_LL_LAT_DD_AMT, CALC_LL_LONG_DD_AMT) %>% # select column
              rename(SiteID =WBIC, VisitUniqueID= SiteSeqNo, LAT= CALC_LL_LAT_DD_AMT, LON= CALC_LL_LONG_DD_AMT) # change column name

 # Extract column from fish data
WI.FishData02 <- WI.FishData %>%
              select(SiteSeqNo, SampleDate, Species, NumberofFish) %>% # select column
              rename(VisitUniqueID= SiteSeqNo, Date= SampleDate, CommonName= Species, Abundance= NumberofFish) # change column name

 # Calculate abundance of each species in each station
WI.FishData021 <-aggregate(Abundance ~ VisitUniqueID + CommonName, data = WI.FishData02, "sum") # calculate fish abundance based on VisitUniqueID

 # Extract unique visit number and date 
WI.FishData_uniqueID <- WI.FishData02[!duplicated(WI.FishData02[c('VisitUniqueID')]),] # remove duplicate based on VisitUniqueID
WI.FishData_uniqueID <- WI.FishData_uniqueID %>% 
                        select(VisitUniqueID, Date) # only select VisitUniqueID and Date

 # Attach fish abundance and unique visit number and date
WI.FishData022 <- left_join(WI.FishData_uniqueID, WI.FishData021, by = "VisitUniqueID") # Attached fish data
str(WI.FishData022)

 # Attach fish abundance data to station data
WI.Masterfile01 <- left_join(WI.FishData022, WI.Visit05, by = "VisitUniqueID") # attach station data (e.g., GPS)
str(WI.Masterfile01)

 # Remove stations which have no GPS coordinates
WI.Masterfile01$LAT[is.na(WI.Masterfile01$LAT)] <- 0 # fill NA to 0 
WI.Masterfile02 <-WI.Masterfile01[!(WI.Masterfile01$LAT %in% c("0")),]

 # Check duplicate
WI.Masterfile02.check1 <- WI.Masterfile02[!duplicated(WI.Masterfile02[c('SiteID')]),] 
str(WI.Masterfile02.check1) # n=1361 correct (unique number of stations)
WI.Masterfile02.check2 <- WI.Masterfile02[!duplicated(WI.Masterfile02[c('VisitUniqueID')]),] 
str(WI.Masterfile02.check2) # n= 1956 correct (unique number of sampling occasions)

 # Change column order
WI.Masterfile02 <-WI.Masterfile02[c("State", "SiteID", "VisitUniqueID", "Date", "LAT", "LON", "CommonName", "Abundance")]
WI.Masterfile.fishdata <- WI.Masterfile02 # rename
WI.Masterfile.fishdata$SiteID <-as.character(WI.Masterfile.fishdata$SiteID) # make as character
WI.Masterfile.fishdata$VisitUniqueID <-as.character(WI.Masterfile.fishdata$VisitUniqueID) # make as character
WI.Masterfile.fishdata$CommonName <-as.character(WI.Masterfile.fishdata$CommonName)
WI.Masterfile.fishdata$Abundance <-as.numeric(WI.Masterfile.fishdata$Abundance) # make as numeric value

## (4) Masterfile including all unique visit number (combination of stations and date) ##

str(WI.Masterfile.fishdata)

## (5) Only select latest sampling occasion in each site ###

 # split Date into month, day, year
WI.Masterfile.fishdata$Date <- as.Date(WI.Masterfile.fishdata$Date, "%m/%d/%Y")

 # Filter SiteID with latest date
WI.Masterfile.sort <- aggregate(Date ~ SiteID, data= WI.Masterfile.fishdata, "max") # select latest sampling occasion based on sampling date
WI.Masterfile.sort$Latest <-'1' # Add Column to mark this site

 # Merge two data frames based on SiteID and Date
WI.Masterfile.sort2 <- left_join(WI.Masterfile.sort, WI.Masterfile.fishdata, by = c("SiteID", "Date"))

 # Select the latest sampling occasion
WI.Masterfile.sort3 <- WI.Masterfile.sort2[which(WI.Masterfile.sort2$Latest=='1'), ]
WI.Masterfile.sort3$Latest <- NULL # Remove "Latest" column
WI.Masterfile.fishdata.latest <- WI.Masterfile.sort3 # Change name

 ## IMPORTANT!! Combine multiple sites in a single siteID - this only happens in WI data
WI.Masterfile.sort4 <- aggregate(Abundance ~ SiteID + CommonName, data= WI.Masterfile.fishdata.latest, "sum") # combine fish abundance
WI.Masterfile.fishdata.lates2 <- WI.Masterfile.fishdata.latest[!duplicated(WI.Masterfile.fishdata.latest[c('Date', 'SiteID')]),] # remove duplicate based on Date and siteID

 # Remove columns
WI.Masterfile.fishdata.lates2$CommonName <- NULL
WI.Masterfile.fishdata.lates2$Abundance <- NULL

 # Attach files
WI.Masterfile.fishdata.lates3 <- left_join(WI.Masterfile.sort4, WI.Masterfile.fishdata.lates2, by = c("SiteID"))

 # re-order column
WI.Master.fishdata.lates3 <-WI.Masterfile.fishdata.lates3[c("State", "SiteID", "VisitUniqueID", "Date", "LAT", "LON", "CommonName", "Abundance")]

 ## Final data ##
WI.Master.fish.latest <- WI.Master.fishdata.lates3
str(WI.Master.fish.latest)

```

# 3. IA Data Management

## (1) Data Property
The file 'IA_DNR_Fish_collections_originalfile.csv' has sampling data, species name and abuduance. The file 'IA_DNR_site_info_originalfile.csv' has Site ID, sampling date, and GPS coordinates. Datesets are well-organized compare with other two states.
Data property:
(1) IA_DNR_site_info_originalfile.csv: SiteID (site ID), SessionID (unique sampling ID), GPS coodinates
(2) IA_DNR_Fish_collections_originalfile.csv: SiteID (site ID), SessionID (unique sampling ID), date, fish list (with abundance)
```{r IA read data}
# Station data
IA.Station <- read.csv("IA_DNR_site_info_originalfile.csv", header=TRUE, strip.white=TRUE)
IA.Station$State <- 'IA' # add state

# Fish data
IA.FishData <- read.csv("IA_DNR_Fish_collections_originalfile.csv", header=TRUE, strip.white=TRUE)
IA.FishData$Species <- gsub(" ", "_", IA.FishData$Species) # replace space to underscore (underbar)
IA.FishData$Species <- toupper(IA.FishData$Species) # change common name format
```

## (2) Fish data treatment
```{r IA Fish data treatment}
# Remove unidentified species and hybrid
IA.FishData <-IA.FishData[!(IA.FishData$Species %in% c("AMEIURUS_SPP.","CAMPOSTOMA_SPP.","CARPIODES_SPP.","CATOSTOMIDAE_-_UNIDENTIFIED","COMMON_SHINER_X_CREEK_CHUB","COMMON_SHINER_X_EMERALD_SHINER","COMMON_SHINER_X_HORNYHEAD
","COMMON_SHINER_X_HORNYHEAD","COMMON_SHINER_X_SOUTHERN_REDBELLY_DACE","COMMON_SHINER_X_STONEROLLER","COMMON_SHINER_X_UNKNOWN","COTTUS_SPP.","CREEK_CHUB_X_HORNYHEAD_CHUB","CREEK_CHUB_X_UNKNOWN","CYPRINELLA_SPP.","CYPRINIDAE_-_UNIDENTIFIED","FAM:_LAMPREY","FAM:_MINNOWS","GEN:_BUFFALOS","GEN:_CARPSUCKERS","GEN:_CATOSTOMUS","GEN:_COMMON_SUNFISHES","GEN:_ETHEOSTOMA","GEN:_NOTROPIS","GEN:_PERCINA","GEN:_PHOXINUS","GEN:_REDHORSES","GEN:_STONEROLLERS","GREEN_SUNFISH_X_BLUEGILL","GREEN_SUNFISH_X_BLUEGILL_X_PUMPKINSEED","GREEN_SUNFISH_X_ORANGESPOTTED_SUNFISH","GREEN_SUNFISH_X_PUMPKINSEED","HIODON_SPP.","HYBOGNATHUS_SPP.","HYBRID:_COMMON_SHINER_X_SO._REDBELLY_DACE","HYBRID:_GREEN_SUNF._X_BLUEGILL","HYBRID_MINNOW","HYBRID_PHOXINUS","HYBRID_SUNFISH","ICTIOBUS_SPP.","LAMPREY_AMMOCOETE","LAMPREYS_(AMMOCOETE)","LAMPREYS","LEPISOSTEUS_SPP.","MOXOSTOMA_SPP.","NO_FISH_CAPTURED","NOTROPIS_SPP.","PERCINA_SPP.","POMOXIS_SPP.","PUMPKINSEED_X_BLUEGILL","PUMPKINSEED_X_WARMOUTH","ROSYFACE/CARMINE_SHINER","RUSTY_CRAYFISH","STICKLEBACKS_UNSP.","SUBFAM:_BUFFALO/CARPSUCKERS","TIGER_TROUT","TIGER_TROUT_(I21_X_I22)", "STONEROLLERS","PEARL_DACE", "QUILLBACK_CARPSUCKER", "GOLDFISH")),]

# Change name
IA.FishData[IA.FishData=="AMERICAN_BROOK_LAMPREY_(AMMOCOETE)"]<- "AMERICAN_BROOK_LAMPREY"
IA.FishData[IA.FishData=="CHESNUT_LAMPREY_(AMMOCOETE)"]<- "CHESTNUT_LAMPREY"
IA.FishData[IA.FishData=="NORTHERN_BROOK_LAMPREY_(AMMOCOETE)"]<- "NORTHERN_BROOK_LAMPREY"
IA.FishData[IA.FishData=="SILVER_LAMPREY_(AMMOCOETE)"]<- "SILVER_LAMPREY"
IA.FishData[IA.FishData=="SOUTHERN_BROOK_LAMPREY_(AMMOCOETE)"]<- "SOUTHERN_BROOK_LAMPREY"
IA.FishData[IA.FishData=="NORTHERN_HOG_SUCKER"]<- "NORTHERN_HOGSUCKER"
IA.FishData[IA.FishData=="TROUT-PERCH"]<- "TROUT_PERCH"
IA.FishData[IA.FishData=="TROUTPERCH"]<- "TROUT_PERCH"
```

## (3) Manage and prepare masterfile
```{r class.source="bg-success", class.output="bg-warning"}

## IA Data management

## (1) Extract fish sampling site
IA.Fish.site <- IA.FishData %>%
                select(SessionID, SiteID) # select column

 # Unique number of site based on SiteID
IA.Fish.site01 <- IA.Fish.site[!duplicated(IA.Fish.site[c('SiteID')]),]
str(IA.Fish.site01) # n=696

 # Unique number of site based on SessionID
IA.Fish.site02 <- IA.Fish.site[!duplicated(IA.Fish.site[c('SessionID')]),]
IA.Fish.site02$FishSample <- '1' # Add one column to show fish sampling
str(IA.Fish.site02) # n= 1277

## (2) Extract fish sampling site form "IA.Visit" file

 # Attach Fish.site02 to IA.Visit 
IA.Visit02 <- left_join(IA.Fish.site02, IA.Station, by = "SiteID")

 # Remove sites without fish sampling
IA.Visit03 <- IA.Visit02[which(IA.Visit02$FishSample=='1'), ] # n=1277

 # Remove fish sampling sites without GPS
IA.Visit03$LatDD[is.na(IA.Visit03$LatDD)] <- 0 # fill NA to 0 (to remove site IAthout GPS)
IA.Visit04 <- IA.Visit03[!(IA.Visit03$LatDD %in% c("0")),] # n=1277: no missing GPS data

 ## Since there is no missing data/value in site and fish data. Let's attached two datasets directly

 # Extract core columns from station data
IA.Station01 <- IA.Station %>%
                select(State, SiteID, LatDD, LonDD) %>% # select column
                rename(LAT= LatDD, LON= LonDD) # change column name

 # Extract core columns from fish data
IA.FishData01 <- IA.FishData %>%
                 select(SessionID, SiteID, Species, SampleDate, TotalCount) %>% # select column
                 rename(VisitUniqueID= SessionID, CommonName= Species, Date= SampleDate,Abundance= TotalCount) # change column name

## (3) Prepare Masterfile

 # Attach fishdata to master file
IA.Masterfile01 <- left_join(IA.FishData01, IA.Station01, by = "SiteID")  
str(IA.Masterfile01)

 # Check duplicate
IA.Masterfile02.check1 <- IA.Masterfile01[!duplicated(IA.Masterfile01[c('SiteID')]),] 
str(IA.Masterfile02.check1) # n=696 correct
IA.Masterfile02.check2 <- IA.Masterfile01[!duplicated(IA.Masterfile01[c('VisitUniqueID')]),] 
str(IA.Masterfile02.check2) # n= 1277 correct

 # Several treatments
IA.Masterfile.fishdata <- IA.Masterfile01 # rename
IA.Masterfile.fishdata$SiteID <-as.character(IA.Masterfile.fishdata$SiteID) # make as character
IA.Masterfile.fishdata$CommonName <-as.character(IA.Masterfile.fishdata$CommonName) # make as character
IA.Masterfile.fishdata$VisitUniqueID <-as.character(IA.Masterfile.fishdata$VisitUniqueID) # make as character
IA.Masterfile.fishdata <-IA.Masterfile.fishdata[c("State", "SiteID", "VisitUniqueID", "Date", "LAT", "LON", "CommonName", "Abundance")]
IA.Masterfile.fishdata$Abundance <-as.numeric(IA.Masterfile.fishdata$Abundance) # make as numeric value

## (4) Masterfile including all unique visit number (combination of stations and date) ##

str(IA.Masterfile.fishdata)

## (5) Select the latest sampling occasion in each site ##

 # Split Date into month, day, year
IA.Masterfile.fishdata$Date <- as.Date(IA.Masterfile.fishdata$Date, "%m/%d/%Y")

 # Filter SiteID and select only latest date
IA.Masterfile.sort <- aggregate(Date ~ SiteID, data= IA.Masterfile.fishdata, "max") # select latest sampling occasion based on sampling date
IA.Masterfile.sort$Latest <-'1' # Add Column to mark this site

 # Merge two data frames based on SiteID and Date
IA.Masterfile.sort2 <- left_join(IA.Masterfile.fishdata, IA.Masterfile.sort, by = c("SiteID", "Date"))

 # Select the latest sampling occasion
IA.Masterfile.sort3 <- IA.Masterfile.sort2[which(IA.Masterfile.sort2$Latest=='1'), ]

 # Remove last column and rename
IA.Masterfile.sort3$Latest <- NULL # Remove "Latest" column
IA.Master.fish.latest <- IA.Masterfile.sort3 # renmae

 ## Final data ##

str(IA.Master.fish.latest)

```

# 4. Masterfile
Here are two masterfiles such as (1) all sites including duplicates (site X date) and (2) selected the latest sampling occasion
```{r class.source="bg-success", class.output="bg-warning"}

## Masterfiles ##

## (1) All data including every sampling occasion 
Fish.Masterfile.all <- rbind(MN.Masterfile.fishdata, WI.Masterfile.fishdata, IA.Masterfile.fishdata) # correct
str(Fish.Masterfile.all)
#write.csv(Fish.Masterfile.all, "Fish.Masterfile.all.csv")

## (2) Select the latest sampling data 
Fish.Masterfile.latest <- rbind(MN.Master.fish.latest, WI.Master.fish.latest, IA.Master.fish.latest) # correct
str(Fish.Masterfile.latest)
#write.csv(Fish.Masterfile.latest, "Fish.Masterfile.latest.csv")
```

# 5. Add Wastershed ID into masterfile
In this section, watershed ID resulted from GIS analysis was attached to fish masterfile based on siteID.
The GIS file 'epsg5070_Station_Clip5.dbf' has SiteID, join_arcid (SegmentID), WatershedID(Id).
```{r class.source="bg-success", class.output="bg-warning"}

## (1) Read Shapefile (dbf)
station_polygon <- read.dbf("epsg5070_Station_Clip5.dbf") # read shapefile (dbf file)

 # Select Site ID and Watershed ID
station_polygon1 <- station_polygon %>%
                select(SiteID, join_arcid, Id)  %>% # select column
                rename(WatershedID= Id, SegmentID= join_arcid) # change column name
station_polygon1$WatershedID <- paste("ws", station_polygon1$WatershedID, sep="") # add "ws" character in watershedID
station_polygon1$Sampled <-'1' # Marked target polygons

## (2) Attach fish masterfile to watershed ID
Masterfile.LatestFishdata2 <- left_join(Fish.Masterfile.latest, station_polygon1, by = c("SiteID")) # attach Watershed ID to fish masterfile
Masterfile.LatestFishdata2 <- Masterfile.LatestFishdata2[which(Masterfile.LatestFishdata2$Sampled=='1'), ] # select wathershedID which has sampling sites
Masterfile.LatestFishdata2$Sampled <- NULL

 # (2-1) How many unique number of sites in each Watershed ID?
Watershed_site <- aggregate(SiteID ~ WatershedID, data= Masterfile.LatestFishdata2, FUN=function(x) length(unique(x)))
str(Watershed_site)

 # (2-2) How many unique number of species in each Watershed ID?
Watershed_spp <- aggregate(CommonName ~ WatershedID, data= Masterfile.LatestFishdata2, FUN=function(x) length(unique(x)))
str(Watershed_spp)

## (3) Filter watershed based on the number of sites in watershed (threshold: 9 <)
 # Remove watershed which have less than 10 sites
Watershed_site2 <-Watershed_site %>% filter(SiteID > 9)
names(Watershed_site2) <- c("WatershedID", "SiteNum")
str(Watershed_site2) # 93 watersheds are selected (correct)

 # Attach this selected watershed to fish data
Masterfile.LatestFishdata3 <-left_join(Masterfile.LatestFishdata2, Watershed_site2, by = c("WatershedID"))

 # Remove sites which are not included in selected watershed
Masterfile.LatestFishdata3[is.na(Masterfile.LatestFishdata3)] <- 0 # fill NA to 0
Masterfile.LatestFishdata3  <- Masterfile.LatestFishdata3[!(Masterfile.LatestFishdata3$SiteNum %in% c("0")),] # remove "0" thus we only select stations which have watershedID

 # Re-order column
Fish.Masterfile.latest2 <-Masterfile.LatestFishdata3[c("State", "WatershedID","SiteNum","SegmentID", "SiteID", "VisitUniqueID", "Date", "LAT", "LON", "CommonName", "Abundance")]

## Final data ## - This data only includes sites located at 93 selected watershed.
str(Fish.Masterfile.latest2)
##write.csv(Fish.Masterfile.latest2, "Fish.Masterfile.latest2.csv")
```

### 2020-11-07 manuscript/manuscript.Rmd
major update

---
title: "Ecosystem size and complexity dictate riverine biodiversity"
author:
- name: Akira Terui
  email: hanabi0111@gmail.com
  affiliation: Department of Biology, University of North Carolina at Greensboro
  footnote: Corresponding Author
- name: Seoghyun Kim
  email: s_kim53@uncg.edu
  affiliation: Department of Biology, University of North Carolina at Greensboro
address:
- address: Department of Biology, Greensboro, NC
output: html_notebook
bibliography: reference.bib
csl: nature.csl
abstract: |
  This is the abstract.
  It consists of two paragraphs.
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, sf)
setwd(here::here("empirical"))

## read gis files
filename <- list.files(path = 'data_gis', full.names = T)
wsd_subset <- lapply(filename[str_detect(filename, "wsd_subset")], st_read)
point_subset <- lapply(filename[str_detect(filename, "point_subset")], st_read)
shape <- lapply(filename[str_detect(filename, "shape")], st_read)
shape[[1]] <- st_set_crs(shape[[1]], st_crs(wsd_subset[[1]]))

```

Ecologists have long sought to understand the general drivers of biodiversity. One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area (the species-area relationship; SAR). In 1921, XXX formulated the SAR as a power-law $S = cA^z$ ($S$ is the number of species observed in a given geographic area $A$), the equation currently known as the Arrhenius species-area relationship. Since then, the spatial scaling of species richness has been observed in nearly all taxonomic groups, although the underlying mechanisms are still hotly debated. The SAR is general because multiple mechanisms produce an apparently similar pattern. Larger ecosystems typically support more diverse communities due to increased habitat diversity, larger (meta)community size, and/or enhanced colonization dynamics. Importantly, the SAR provides the foundation for global conservation efforts. For example, conservation ecologists have used the SAR estimates to design marine and terrestrial protected areas, which currently encompass more than ~ km² globally.

However, many ecosystems possess a dimension of spatial complexity that cannot be described by area (i.e., the scale-invariant complexity). Such spatial complexity is evident in branching ecosystems, such as rivers, trees, and mountain ranges, to name just a few. Geomorphic or biological processes generate a pronounced self-similarity in complex branching structure so that the part and the whole look alike. Even though the branching structure is independent of spatial scale, it forms a physical template that determines habitat diversity and dispersal corridors for living organisms. Evidence suggests that ecological dynamics driven by branching structure cannot be predicted by scale-dependent theories; this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems. However, most research either has explored the consequences of branching complexity for local biodiversity patterns or relied on theoretical arguments with limited replicates of artificial branching networks. At present, no studies have integrated theoretical and empirical approaches to link branching complexity and $\gamma$ diversity (i. e., the total species richness in a metacommunity). This knowledge gap significantly limits our ability to guide biodiversity conservation in spatially complex ecosystems.

Here, we hypothesize that ecosystem size and complexity dictate $\gamma$ diversity in rivers, a prime example of complex branching ecosystems. In branching river networks, streams with diverse geological backgrounds recurrently join to form a larger, ecologically distinct channel. As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], should control the habitat heterogeneity of the ecosystem (habitat diversity per unit area). Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity). We predict that ecosystem size and branching complexity increase $\gamma$ diversity. The present study combines theory and statistical analysis of extensive community data to provide crucial insights into how ecological communities are structured in complex branching networks.

First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity. We constructed a general simulation model of metacommunity dynamics [@thompsonProcessbasedMetacommunityFramework2020], in which 50 competing species disperse and spatially interact in a random branching network. Simulated species with different niche in abiotic conditions (optimum and width) compete for resources with varied strengths. For simplicity, other ecological traits are assumed to be identical among species (e.g., dispersal probability). Here, branching networks are depicted as a spatial network of connected habitat patches (or a discretized river section) where mean environmental conditions at each habitat patch are determined by two factors: (1) environments of headwaters (the most upstream habitat patch) and (2) local environmental noises. Environmental values at headwaters are produced randomly and propagate downstream with local environmental noises (i.e., the spatial autoregressive process with  a white noise). These values recurrently 'mix' at confluences considering the relative size of joining tributaries (see Methods). Therefore, our simulation resembles ecological processes of how branching river networks create diverse habitats in a metacommunity. We prepared 16 simulation scenarios with varied ecological (dispersal and competition strength) and landscape contexts (environmental variation at headwaters and the degree of local environmental noises). Under each scenario, we simulated metacommunity dynamics in 1000 branching networks that have different ecosystem size (the number of habitat patches in a network) and complexity (branching probability) to examine their effects on $\gamma$ diversity.

Our theoretical analysis yielded results consistent with our prediction. Ecosystem size and complexity both increased $\gamma$ diversity under realistic landscape contexts, where the environmental variation at headwaters ($\sigma_h$) is greater than the degree of local environmental noises ($\sigma_l$) [@petersonModellingDendriticEcological2013; @teruiMetapopulationStabilityBranching2018]. The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios: the strength of competition and dispersal probability did not change the form of the relationships between $\gamma$ diversity and ecosystem properties. The effect of ecosystem size on $\gamma$ diversity was largely driven by the spatial turnover of species composition among habitat patches ($\beta$ diversity) regardless of ecological scenarios. $\beta$ diversity increased significantly with increasing ecosystem size, while local diversity (average species richness in a single habitat patch; $\alpha$ diversity) remained almost unchanged.

In contrast, the relative importance of $\alpha$ and $\beta$ diversity in the complexity-$\gamma$ diversity relationship was dependent on the dispersal probability of constituent species. When dispersal probability of species was low, the positive effect of branching complexity on $\gamma$ diversity was driven mainly by increased $\beta$ diversity, reflecting significant spatial turnover of species composition. However, with higher dispersal probability, the relationship between $\beta$ diversity and branching complexity became a hump-shaped form. A clear increase in $\alpha$ diversity compensated for the slight decrease in $\beta$ diversity at high branching probabilities, maintaining the positive complexity-$\gamma$ diversity relationship. This likely occurred through the increased connectivity of highly branched networks. The average network distance between a pair of habitat patches decreases with increasing branching probability because highly branched networks have a compressed form compared to less branched networks. Therefore, increased dispersal readily homogenizes community composition while increasing $\alpha$ diversity through enhanced immigration from suitable habitat patches (i.e., mass effects). This result highlights how different mechanisms can generate an apparently similar pattern in the complexity-$\gamma$ diversity relationship.

It is important to note that the effect of branching complexity diminished when the environmental variation at headwaters is smaller or equal to the degree of local environmental noises ($\sigma_h \le \sigma_l$). When local environmental noises are very large relative to environmental variation among headwaters, the net habitat diversity should be correlated with ecosystem size but not with branching complexity. This simulation setup decouples the intimate relationship between branching structure and habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity. This theoretical prediction may not apply to natural river networks because streams originating from different sources are known to show distinct environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes. Yet, this result illustrates the crucial role of habitat diversity produced by branching structure, rather than branching structure itself, in the emerging complexity-$\gamma$ diversity relationship.

## Empirical evidence
We tested our theoretical predictions using a large data set of fish communities in two geographic regions: the Hokkaido island in Japan and the Midwest in the US. These regions are located in comparable ranges of latitude but support distinct fish communities. Therefore, this data set provides an excellent opportunity to examine the generality of our theoretical predictions. Our data set comprised presence-absence of fish species at XXX sites, which encompassed the majority of the two geographic regions. We estimated $\gamma$ diversity using a method of incidence-based extrapolation (i.e., the asymptotic species richness; see Methods) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in Midwest). Individual watersheds, i.e., metacommunity replicates in our analysis, were considered as independent if they flow into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).

Our empirical data analysis provided a strong support for theoretical predictions. Our theory predicts that $\gamma$ diversity increases with increasing ecosystem size and complexity. This is exactly what was observed in nature. The estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) of the studied river networks. Importantly, the patterns were consistent across two geographic regions (i.e., non-significant effects of interactions with region) that support distinct fish communities. Moreover, the effects of watershed area and branching probability remained significant even after accounting for the potential influences of other environmental factors (precipitation, temperature, and land use). As predicted by theory, the scaling of $\gamma$ diversity by ecosystem size or complexity was a power-law. Given the uncertainty of estimated $\gamma$ diversity, we repeated our analysis with lower (5%) and upper (95%) confidence intervals of $\gamma$ diversity estimates. Overall, we found qualitatively similar results, implying the robustness of our findings. Our results, therefore, provides strong empirical evidence that ecosystem complexity, not only ecosystem size, represents a dimension of ecosystem properties that scale riverine biodiversity.

Detailed analysis of $\alpha$ and $\beta$ diversity patterns provides deeper insights into underlying ecological mechanisms.

# Methods

### 2020-11-07 manuscript/table.Rmd
major update

---
title: "R Notebook"
output: html_notebook
---
```{r setup, include=FALSE}
# setup -------------------------------------------------------------------

  rm(list = ls(all.names = TRUE))
  pacman::p_load(tidyverse, MuMIn, gt)
  options(na.action = "na.fail")
  setwd(here::here("empirical"))

# read data ---------------------------------------------------------------

  dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
  dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
  dat <- bind_rows(dat_hkd, dat_mw) %>% 
    rename(gamma = Estimator,
           gamma_lower = '95% Lower',
           gamma_upper = '95% Upper') %>% 
    mutate(beta = gamma/mu_alpha,
           beta_lower = gamma_lower/mu_alpha,
           beta_upper = gamma_upper/mu_alpha,
           logit_forest = log(frac_forest) - log(1 - frac_forest))

  ## gamma
  fit <- lm(log(gamma) ~ log(area)*region + log(p_branch)*region + scale(mean_temp) + scale(mean_ppt) + scale(logit_forest), dat)
  m <- dredge(fit, rank = "AIC")
  re <- model.avg(object = m, subset = delta < 2)
  x <- summary(re)
  knitr::kable(x$coefmat.subset)
  predict(re$call)
```

### 2020-11-07 empirical/analysis.R

@@ -20,10 +20,15 @@
   
   ## gamma
   fit <- lm(log(gamma) ~ log(area)*region + log(p_branch)*region +
-                         scale(mean_temp) + scale(mean_ppt) + frac_forest, dat)
+            scale(mean_temp)*region + scale(mean_ppt)*region + scale(frac_forest)*region,
+            dat)
   m <- dredge(fit, rank = "AIC")
   re <- model.avg(object = m, subset = delta < 2)
   summary(re)
+  
+  weight <- 1/dist(cbind(d0$lat, d0$lon), diag = TRUE, upper = TRUE)
+  diag(weight) <- 0
+  Moran.I(resid(fit), data.matrix(weight))
   
   ## alpha
   fit <- lm(log(mu_alpha) ~ log(area)*region + log(p_branch)*region +

### 2020-11-07 empirical/analysis_moran_i.R

@@ -1,0 +1,31 @@
+
+# setup -------------------------------------------------------------------
+
+rm(list = ls(all.names = TRUE))
+pacman::p_load(tidyverse, MuMIn)
+options(na.action = "na.fail")
+setwd(here::here("empirical"))
+
+# read data ---------------------------------------------------------------
+
+dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
+dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
+dat <- bind_rows(dat_hkd, dat_mw) %>% 
+  rename(gamma = Estimator,
+         gamma_lower = '95% Lower',
+         gamma_upper = '95% Upper') %>% 
+  mutate(beta = gamma/mu_alpha,
+         beta_lower = gamma_lower/mu_alpha,
+         beta_upper = gamma_upper/mu_alpha)
+
+## gamma
+fit <- lm(log(gamma) ~ log(area)*region + log(p_branch)*region +
+            scale(mean_temp)*region + scale(mean_ppt)*region + scale(frac_forest)*region,
+          dat)
+m <- dredge(fit, rank = "AIC")
+re <- model.avg(object = m, subset = delta < 2)
+summary(re)
+
+weight <- 1/dist(cbind(d0$lat, d0$lon), diag = TRUE, upper = TRUE)
+diag(weight) <- 0
+Moran.I(resid(fit), data.matrix(weight))

### 2020-11-07 empirical/data_merge_hkd.R

@@ -10,7 +10,11 @@
   watershed <- st_read(dsn = 'data_gis/albers_watershed_hkd_final.gpkg') %>% 
     rename(watershed_id = id) %>% 
     arrange(watershed_id)
-
+  
+  watershed <- watershed %>%
+    mutate(lon = st_coordinates(st_transform(st_centroid(.), 4326))[,1],
+           lat = st_coordinates(st_transform(st_centroid(.), 4326))[,2])
+  
 # merge fish and gis data -------------------------------------------------
 
   d0 <- read_csv('data_org_hkd/data_fmt_hkd_latest.csv') %>% 
@@ -20,7 +24,9 @@
     st_join(watershed)
 
   ## watershed ID with more than X sampling sites
+  ## with > 5 branches
   wsd_subset <- d0 %>% 
+    filter(n_branch >= 3) %>% 
     group_by(watershed_id) %>% 
     summarise(n_site = n_distinct(SiteID)) %>% 
     filter(n_site >= 10) %>% 
@@ -77,8 +83,7 @@
   dat_hkd <- div_est %>%
     left_join(as_tibble(watershed), by = "watershed_id") %>% 
     left_join(dat_alpha, by = "watershed_id") %>% 
-    select(-geom) %>% 
-    na.omit()
+    select(-geom)
   
   write_csv(dat_hkd, "data_out/data_hkd.csv")
   

### 2020-11-07 empirical/data_merge_mw.R

@@ -3,14 +3,18 @@
   
   rm(list = ls(all.names = TRUE))
   setwd(here::here("empirical"))
-  pacman::p_load(tidyverse, tidyverse, sf, iNEXT, foreach, tmap)  
+  pacman::p_load(tidyverse, sf, iNEXT, foreach, tmap)  
 
 # read gis data -----------------------------------------------------------
 
   watershed <- st_read(dsn = 'data_gis/albers_watershed_mw_final.gpkg') %>% 
     rename(watershed_id = id) %>% 
     arrange(watershed_id)
-
+  
+  watershed <- watershed %>%
+    mutate(lon = st_coordinates(st_transform(st_centroid(.), 4326))[,1],
+           lat = st_coordinates(st_transform(st_centroid(.), 4326))[,2])
+  
 # merge fish and gis data -------------------------------------------------
   
   fishdata <- list.files(path = "data_org_mw", full.names = TRUE) %>%
@@ -22,7 +26,9 @@
     st_join(watershed)
   
   ## watershed ID with more than X sampling sites
+  ## with > 5 branches
   wsd_subset <- d0 %>% 
+    filter(n_branch >= 3) %>% 
     group_by(watershed_id) %>% 
     summarise(n_site = n_distinct(SiteID)) %>% 
     filter(n_site >= 10) %>% 

### 2020-11-07 empirical/figure.R

@@ -1,24 +1,0 @@
-ggplot(dat, aes(x = p_branch, y = gamma, color = region)) +
-  scale_y_continuous(trans='log10') +
-  scale_x_continuous(trans='log10') +
-  geom_point() +
-  geom_smooth(method = "lm", se = F)
-
-ggplot(dat, aes(x = area, y = gamma, color = region)) +
-  scale_y_continuous(trans='log10') +
-  scale_x_continuous(trans='log10') +
-  geom_point() +
-  geom_smooth(method = "lm", se = F)
-
-ggplot(dat, aes(x = p_branch, y = mu_alpha, color = region)) +
-  scale_y_continuous(trans='log10') +
-  scale_x_continuous(trans='log10') +
-  geom_point() +
-  geom_smooth(method = "lm", se = F)
-
-ggplot(dat, aes(x = p_branch, y = beta, color = region)) +
-  scale_y_continuous(trans='log10') +
-  scale_x_continuous(trans='log10') +
-  geom_point() +
-  geom_smooth(method = "lm", se = F)
-

### 2020-11-07 empirical/figure_diversity.R

@@ -1,0 +1,54 @@
+
+# setup -------------------------------------------------------------------
+
+  rm(list = ls(all.names = TRUE))
+  pacman::p_load(tidyverse, sf, patchwork)
+  setwd(here::here("empirical"))
+
+# fig: gamma --------------------------------------------------------------
+
+  ## read data
+  dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
+  dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
+  
+  dat <- bind_rows(dat_hkd, dat_mw) %>% 
+    rename(gamma = Estimator,
+           gamma_lower = '95% Lower',
+           gamma_upper = '95% Upper') %>% 
+    mutate(beta = gamma/mu_alpha,
+           beta_lower = gamma_lower/mu_alpha,
+           beta_upper = gamma_upper/mu_alpha)
+  
+  ## set theme
+  theme_set(theme_bw())
+  
+  ## plot
+  ggplot(dat, aes(x = p_branch, y = gamma, color = region)) +
+    scale_y_continuous(trans='log10') +
+    scale_x_continuous(trans='log10') +
+    geom_point() +
+    geom_smooth(method = "lm", se = F)
+  
+  ggplot(dat, aes(x = frac_forest, y = gamma, color = region)) +
+    scale_y_continuous(trans='log10') +
+    geom_point() +
+    geom_smooth(method = "lm", se = F)
+  
+  ggplot(dat, aes(x = area, y = gamma, color = region)) +
+    scale_y_continuous(trans='log10') +
+    scale_x_continuous(trans='log10') +
+    geom_point() +
+    geom_smooth(method = "lm", se = F)
+  
+  ggplot(dat, aes(x = p_branch, y = mu_alpha, color = region)) +
+    scale_y_continuous(trans='log10') +
+    scale_x_continuous(trans='log10') +
+    geom_point() +
+    geom_smooth(method = "lm", se = F)
+  
+  ggplot(dat, aes(x = p_branch, y = beta, color = region)) +
+    scale_y_continuous(trans='log10') +
+    scale_x_continuous(trans='log10') +
+    geom_point() +
+    geom_smooth(method = "lm", se = F)
+  

### 2020-11-07 empirical/figure_map.R

@@ -1,0 +1,37 @@
+
+
+# setup -------------------------------------------------------------------
+  
+  rm(list = ls(all.names = TRUE))
+  pacman::p_load(tidyverse, sf, patchwork)
+  setwd(here::here("empirical"))
+
+# fig: map ----------------------------------------------------------------
+
+  ## read data
+  filename <- list.files(path = 'data_gis', full.names = T)
+  wsd_subset <- lapply(filename[str_detect(filename, "wsd_subset")], st_read)
+  point_subset <- lapply(filename[str_detect(filename, "point_subset")], st_read)
+  shape <- lapply(filename[str_detect(filename, "shape")], st_read)
+  shape[[1]] <- st_set_crs(shape[[1]], st_crs(wsd_subset[[1]]))
+  
+  ## set theme
+  theme_set(theme_bw())
+  
+  ## hokkaido
+  hkd <- ggplot() +
+    geom_sf(data = shape[[1]], fill = grey(0.99), size = 0.01) +
+    geom_sf(data = wsd_subset[[1]], fill = alpha("steelblue", alpha = 0.1), size = 0.01) +
+    geom_sf(data = point_subset[[1]], size = 0.001, color = alpha("salmon", 0.5)) + 
+    ggtitle(paste0("Hokkaido, Japan\n", eval(nrow(wsd_subset[[1]])), " watersheds"))
+  
+  ## midwest
+  mw <- ggplot() +
+    geom_sf(data = shape[[2]], fill = grey(0.99), size = 0.01) +
+    geom_sf(data = wsd_subset[[2]], fill = alpha("steelblue", alpha = 0.1), size = 0.01) +
+    geom_sf(data = point_subset[[2]], size = 0.001, color = alpha("salmon", 0.5)) + 
+    ggtitle(paste0("Midwest, US\n", eval(nrow(wsd_subset[[2]])), " watersheds"))
+  
+  print(mw + hkd)
+  
+  

### 2020-11-07 theory/figure.R

@@ -2,16 +2,15 @@
 
 # setup -------------------------------------------------------------------
 
-  library(tidyverse)
-  library(broom)
-  library(here)
-  setwd(here("theory"))
+  rm(list = ls(all.names = TRUE))
+  pacman::p_load(tidyverse, broom)
+  setwd(here::here("theory"))
 
 # read data ---------------------------------------------------------------
 
-  dat <- read_csv("result/result_sim2020-10-24.csv") %>% 
+  dat <- read_csv("result/result_sim2020-11-03.csv") %>% 
     select(-beta_div) %>% 
-    filter(alpha_div > 0 & gamma_div > 0,
+    filter(alpha_div >= 1 & gamma_div >= 1,
            sd_env_source == 1,
            sd_env_lon == 0.01) %>% 
     mutate(beta_div = gamma_div/alpha_div) %>% 
@@ -58,7 +57,7 @@
   dat %>% 
     ggplot(aes(x = n_patch, y = value, color = metric, fill = metric)) +
     geom_smooth(method = "loess", size = 0.3) +
-    geom_point(alpha = 0.075, size = 0.3) +
+    geom_point(alpha = 0.2, size = 0.75) +
     scale_y_continuous(trans = "log10") +
     scale_x_continuous(trans = "log10") +
     scale_color_hue(name = NULL, labels = labels) +
@@ -75,7 +74,7 @@
   dat %>% 
     ggplot(aes(x = p_branch, y = value, color = metric, fill = metric)) +
     geom_smooth(method = "loess", size = 0.3) +
-    geom_point(alpha = 0.075, size = 0.3) +
+    geom_point(alpha = 0.2, size = 0.75) +
     scale_y_continuous(trans = "log10") +
     scale_x_continuous(trans = "log10") +
     scale_color_hue(name = NULL, labels = labels) +

### 2020-11-07 theory/run_simulation.R

@@ -2,14 +2,10 @@
 # library -----------------------------------------------------------------
   
   rm(list = ls(all.names = TRUE))
-  library(here)
-  library(tidyverse)
-  library(foreach)
-  library(mcbrnet)
-  library(doParallel)
-  library(doSNOW)
+  pacman::p_load(here, tidyverse, foreach, mcbrnet, doParallel, doSNOW)
 
-# parallel set up ---------------------------------------------------------
+
+# parallel setup ----------------------------------------------------------
 
   cl <- makeCluster(detectCores())
   registerDoSNOW(cl)
@@ -40,7 +36,7 @@
   n_rep <- 1000
   repeat {
     n_patch <- round(runif(n = n_rep, min = 10, max = 150))
-    p_branch <- runif(n = n_rep, min = 0.001, max = 0.999)
+    p_branch <- runif(n = n_rep, min = 0.01, max = 0.99)
     if(min(n_patch) == 10 & max(n_patch) == 150) break    
   }
   

### 2020-11-12 manuscript/figures.Rmd
Edits: major change

---
title: "Figures"
output:
  pdf_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

```

```{r, fig.height=7, fig.width=8, fig.cap="(A) Example of theoretical branching river networks. Branching river networks are dipicted as a network of connected habitat patches, in which the number of habitat patches $N$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example). Environmental conditions at the headwaters (the most upstream patches) are generated randomly and propagate downstream with local noises. Habitat patches are colored in proportion to environmental values (similarly-colored habitat patches have similar environmental values). (B) Map of study regions (left, Midwest, US; right, Hokkaido, Japan). Watersheds (i.e., metacommunities) are colored in propotion to the number of sites for fish surveys."}

source(normalizePath("../empirical/figure_map.R"))

```

\newpage

```{r, fig.height=5, fig.width=7}

source(normalizePath("../theory/figure_n_patch.R"))

```

\newpage

```{r, fig.height=5, fig.width=7}

source(normalizePath("../theory/figure_p_branch.R"))

```

\newpage

```{r, fig.height=6, fig.width=8}

source(normalizePath("../empirical/figure_diversity.R"))

```

### 2020-11-12 manuscript/manuscript.Rmd
Edits: major change

@@
   affiliation: Department of Biology, University of North Carolina at Greensboro
-address:
-- address: Department of Biology, Greensboro, NC
+- name: Christy Dolph
+  email: XXX
+  affiliation: XXX
 output: html_notebook

### 2020-11-12 manuscript/table.Rmd
Edits: major change

@@
 ---
-title: "R Notebook"
-output: html_notebook
+title: "Tables"
+output:
+  pdf_document: default
 ---
+
 ```{r setup, include=FALSE}
-# setup -------------------------------------------------------------------
 
-  rm(list = ls(all.names = TRUE))
-  pacman::p_load(tidyverse, MuMIn, gt)
-  options(na.action = "na.fail")
-  setwd(here::here("empirical"))
+  knitr::opts_knit$set(root.dir = here::here("empirical"))
 
-# read data ---------------------------------------------------------------
+```
 
-  dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
-  dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
-  dat <- bind_rows(dat_hkd, dat_mw) %>% 
-    rename(gamma = Estimator,
-           gamma_lower = '95% Lower',
-           gamma_upper = '95% Upper') %>% 
-    mutate(beta = gamma/mu_alpha,
-           beta_lower = gamma_lower/mu_alpha,
-           beta_upper = gamma_upper/mu_alpha,
-           logit_forest = log(frac_forest) - log(1 - frac_forest))
+```{r, echo = FALSE, message=FALSE, results='asis'}
 
-  ## gamma
-  fit <- lm(log(gamma) ~ log(area)*region + log(p_branch)*region + scale(mean_temp) + scale(mean_ppt) + scale(logit_forest), dat)
-  m <- dredge(fit, rank = "AIC")
-  re <- model.avg(object = m, subset = delta < 2)
-  x <- summary(re)
-  knitr::kable(x$coefmat.subset)
-  predict(re$call)
+source(normalizePath("../empirical/analysis_lm.R"))
+
+stargazer::stargazer(m_alpha$model, m_beta$model, m_gamma$model,
+                     header = FALSE,
+                     title = "Estimated parameters of robust linear regression models explaining fish species richness in Hokkaido (Japan) and Midwest (US) regions.
+Dependent variables were log-10 transformed.
+Environmental variables (air temperature, precipitation, logit \\% forest) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one.",
+                     type = "latex",
+                     ci = TRUE,
+                     covariate.labels = c("$log_{10}$ Watershed area",
+                                          "$log_{10}$ Branching probability",
+                                          "Region (Midwest vs. Hokkaido)",
+                                          "Air temperature",
+                                          "Precipitation",
+                                          "Logit \\% forest",
+                                          "Intercept"),
+                     single.row = FALSE,
+                     digits = 2,
+                     dep.var.labels.include = FALSE,
+                     column.labels = c("$\\alpha$ richness", "$\\beta$ richness", "$\\gamma$ richness"),
+                     keep.stat = c("rsq"),
+                     model.numbers = FALSE)
+
 ```

### 2020-11-12 empirical/analysis.R

@@ -1,47 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-  rm(list = ls(all.names = TRUE))
-  pacman::p_load(tidyverse, MuMIn)
-  options(na.action = "na.fail")
-  setwd(here::here("empirical"))
-
-# read data ---------------------------------------------------------------
-
-  dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
-  dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
-  dat <- bind_rows(dat_hkd, dat_mw) %>% 
-    rename(gamma = Estimator,
-           gamma_lower = '95% Lower',
-           gamma_upper = '95% Upper') %>% 
-    mutate(beta = gamma/mu_alpha,
-           beta_lower = gamma_lower/mu_alpha,
-           beta_upper = gamma_upper/mu_alpha)
-  
-  ## gamma
-  fit <- lm(log(gamma) ~ log(area)*region + log(p_branch)*region +
-            scale(mean_temp)*region + scale(mean_ppt)*region + scale(frac_forest)*region,
-            dat)
-  m <- dredge(fit, rank = "AIC")
-  re <- model.avg(object = m, subset = delta < 2)
-  summary(re)
-  
-  weight <- 1/dist(cbind(d0$lat, d0$lon), diag = TRUE, upper = TRUE)
-  diag(weight) <- 0
-  Moran.I(resid(fit), data.matrix(weight))
-  
-  ## alpha
-  fit <- lm(log(mu_alpha) ~ log(area)*region + log(p_branch)*region +
-              scale(mean_temp) + scale(mean_ppt) + frac_forest, dat)
-  m <- dredge(fit, rank = "AIC")
-  re <- model.avg(object = m, subset = delta < 2)
-  summary(re)
-  
-  ## beta
-  fit <- lm(log(beta) ~ log(area)*region + log(p_branch)*region +
-              scale(mean_temp) + scale(mean_ppt) + frac_forest, dat)
-  m <- dredge(fit, rank = "AIC")
-  re <- model.avg(object = m, subset = delta < 2)
-  summary(re)
-  
-  

### 2020-11-12 empirical/analysis_iNEXT_sim.R

@@ -1,0 +1,59 @@
+
+# setup -------------------------------------------------------------------
+
+  rm(list = ls(all.names = TRUE))
+  pacman::p_load(tidyverse, MuMIn, foreach)
+  options(na.action = "na.fail")
+  setwd(here::here("empirical"))
+  
+
+
+# simulation function -----------------------------------------------------
+
+  f_sim <- function(n_species, n_site, p_min = 0, p_max = 0.8){
+    p <- runif(n = n_species, p_min, p_max)
+    freq <- sapply(seq_len(n_species), FUN = function(x) rbinom(n = n_site, prob = p[x], size = 1))
+    x <- c(n_site, sort(colSums(freq), decreasing = T))
+    
+    y <- iNEXT(x, datatype = "incidence_freq")  
+    return(y[[3]][,"Estimator"][1])
+  }
+  
+
+# simulation --------------------------------------------------------------
+
+  n_species <- seq(10, 100, by = 30)
+  n_site <- c(seq(5, 20, by = 5), 100)
+  n_rep <- 100
+  para <- expand.grid(n_species = n_species, n_site = n_site)
+  
+  sim_re <- foreach(i = seq_len(nrow(para)), .combine = bind_rows) %do% {
+    df_set <- foreach(j = seq_len(n_rep), .combine = bind_rows) %do% {
+      est <- f_sim(n_species = para$n_species[i], n_site = para$n_site[i])
+      df <- tibble(replicate = j,
+                   estimate = est,
+                   n_species = para$n_species[i],
+                   n_site = para$n_site[i])
+      return(df)
+    }
+    return(df_set)
+  }
+    
+  sim_re <- sim_re %>% 
+    mutate(bias = 100*((estimate - n_species) / n_species))
+  
+  sim_summary <- sim_re %>% 
+    group_by(n_species, n_site) %>% 
+    summarise(median_bias = median(bias),
+              iql_bias = quantile(bias, probs = 0.75) - quantile(bias, probs = 0.25))
+  
+
+# plot --------------------------------------------------------------------
+  
+  sim_re %>% 
+    ggplot(aes(y = bias, x = factor(n_site))) +
+    facet_wrap(facets = ~ n_species) +
+    geom_boxplot(alpha = 0.5) +
+    geom_jitter(alpha = 0.5, size = 0.5) +
+    geom_hline(yintercept = 0)
+  

### 2020-11-12 empirical/analysis_lm.R

@@ -1,0 +1,57 @@
+
+# setup -------------------------------------------------------------------
+
+  rm(list = ls(all.names = TRUE))
+  pacman::p_load(tidyverse, MuMIn, MASS)
+  options(na.action = "na.fail")
+  setwd(here::here("empirical"))
+
+# read data ---------------------------------------------------------------
+  
+  dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
+  dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
+  
+  dat <- bind_rows(dat_hkd, dat_mw) %>% 
+    rename(gamma = Estimator,
+           alpha = mu_alpha) %>% 
+    mutate(beta = gamma/alpha,
+           logit_forest = log(frac_forest) - log(1 - frac_forest)) %>% 
+    mutate(resid_forest = resid(lm(logit_forest ~ region, data = .)),
+           resid_temp = resid(lm(mean_temp ~ region, data = .)),
+           resid_ppt = resid(lm(mean_ppt ~ region, data = .)))
+  
+
+# model selection ---------------------------------------------------------
+
+  m_compare <- function(response, data) {
+    
+    fit <<- list(NULL)
+    fit[[1]] <<- lm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
+                      scale(resid_temp) + scale(resid_ppt) + scale(resid_forest),
+                    data = data)
+    
+    fit[[2]] <<- lm(log(response, 10) ~ log(area, 10)*region + log(p_branch, 10)*region + region +
+                      scale(resid_temp) + scale(resid_ppt) + scale(resid_forest),
+                    data = data)
+    
+    fit[[3]] <<- lm(log(response, 10) ~ 1,
+                    data = data)
+    
+    m <- fit[[which.min(sapply(fit, FUN = BIC))]]
+    df <- tibble(model = c("global", "region-specific", "null"),
+                 AIC = sapply(fit, FUN = AIC),
+                 AICc = sapply(fit, FUN = AICc),
+                 BIC = sapply(fit, FUN = BIC))
+    
+    return(list(model = m, model_table = df))
+  }
+  
+  ## alpha 
+  m_alpha <- m_compare(dat$alpha, data = dat)
+  
+  ## beta
+  m_beta <- m_compare(dat$beta, data = dat)
+  
+  ## gamma
+  m_gamma <- m_compare(dat$gamma, data = dat)
+  

### 2020-11-12 empirical/analysis_moran_i.R

@@ -1,31 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-rm(list = ls(all.names = TRUE))
-pacman::p_load(tidyverse, MuMIn)
-options(na.action = "na.fail")
-setwd(here::here("empirical"))
-
-# read data ---------------------------------------------------------------
-
-dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
-dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
-dat <- bind_rows(dat_hkd, dat_mw) %>% 
-  rename(gamma = Estimator,
-         gamma_lower = '95% Lower',
-         gamma_upper = '95% Upper') %>% 
-  mutate(beta = gamma/mu_alpha,
-         beta_lower = gamma_lower/mu_alpha,
-         beta_upper = gamma_upper/mu_alpha)
-
-## gamma
-fit <- lm(log(gamma) ~ log(area)*region + log(p_branch)*region +
-            scale(mean_temp)*region + scale(mean_ppt)*region + scale(frac_forest)*region,
-          dat)
-m <- dredge(fit, rank = "AIC")
-re <- model.avg(object = m, subset = delta < 2)
-summary(re)
-
-weight <- 1/dist(cbind(d0$lat, d0$lon), diag = TRUE, upper = TRUE)
-diag(weight) <- 0
-Moran.I(resid(fit), data.matrix(weight))

### 2020-11-12 empirical/data_merge_hkd.R

@@ -3,7 +3,7 @@
   
   rm(list = ls(all.names = TRUE))
   setwd(here::here("empirical"))
-  pacman::p_load(tidyverse, tidyverse, sf, iNEXT, foreach, tmap)  
+  pacman::p_load(tidyverse, tidyverse, sf, iNEXT, foreach, magrittr)  
   
 # read gis data -----------------------------------------------------------
 
@@ -12,52 +12,50 @@
     arrange(watershed_id)
   
   watershed <- watershed %>%
-    mutate(lon = st_coordinates(st_transform(st_centroid(.), 4326))[,1],
-           lat = st_coordinates(st_transform(st_centroid(.), 4326))[,2])
+    mutate(lon = st_coordinates(st_transform(st_centroid(., quiet = TRUE), 4326))[,1],
+           lat = st_coordinates(st_transform(st_centroid(., quiet = TRUE), 4326))[,2])
   
 # merge fish and gis data -------------------------------------------------
 
   d0 <- read_csv('data_org_hkd/data_fmt_hkd_latest.csv') %>% 
+    rename(Species = OTU) %>% 
     st_as_sf(coords = c("Lon", "Lat"), crs = 4326) %>% 
     st_transform(crs = st_crs(watershed)$wkt) %>% 
     filter(Year >= 1990) %>% 
     st_join(watershed)
-
-  ## watershed ID with more than X sampling sites
-  ## with > 5 branches
-  wsd_subset <- d0 %>% 
-    filter(n_branch >= 3) %>% 
+  
+  n_site_stat <- d0 %>%
+    as_tibble() %>% 
     group_by(watershed_id) %>% 
     summarise(n_site = n_distinct(SiteID)) %>% 
-    filter(n_site >= 10) %>% 
-    drop_na(watershed_id) %>% 
+    right_join(as_tibble(watershed), by = "watershed_id") %>% 
+    select(watershed_id, n_site, area, n_branch) %>% 
+    mutate(density_site = n_site/area)
+  
+  ## watershed ID with more than X site
+  ## watershed ID with more than X branch
+  wsd_candidate <- n_site_stat %>% 
+    filter(n_site >= 10 & n_branch >= 10) %>% 
     pull(watershed_id)
   
   dat_fish <- d0 %>% 
-    filter(watershed_id %in% wsd_subset) %>% 
+    filter(watershed_id %in% wsd_candidate) %>% 
     as_tibble()
 
   dat_alpha <- dat_fish %>% 
[…]

### 2020-11-12 empirical/data_merge_mw.R

@@ -12,8 +12,8 @@
     arrange(watershed_id)
   
   watershed <- watershed %>%
-    mutate(lon = st_coordinates(st_transform(st_centroid(.), 4326))[,1],
-           lat = st_coordinates(st_transform(st_centroid(.), 4326))[,2])
+    mutate(lon = st_coordinates(st_transform(st_centroid(., quiet = TRUE), 4326))[,1],
+           lat = st_coordinates(st_transform(st_centroid(., quiet = TRUE), 4326))[,2])
   
 # merge fish and gis data -------------------------------------------------
   
@@ -25,18 +25,22 @@
     st_transform(crs = st_crs(watershed)$wkt) %>% 
     st_join(watershed)
   
-  ## watershed ID with more than X sampling sites
-  ## with > 5 branches
-  wsd_subset <- d0 %>% 
-    filter(n_branch >= 3) %>% 
+  n_site_stat <- d0 %>%
+    as_tibble() %>% 
     group_by(watershed_id) %>% 
     summarise(n_site = n_distinct(SiteID)) %>% 
-    filter(n_site >= 10) %>% 
-    drop_na(watershed_id) %>% 
+    right_join(as_tibble(watershed), by = "watershed_id") %>% 
+    select(watershed_id, n_site, area, n_branch) %>% 
+    mutate(density_site = n_site/area)
+  
+  ## watershed ID with more than X site
+  ## watershed ID with more than X branch
+  wsd_candidate <- n_site_stat %>% 
+    filter(n_site >= 10 & n_branch >= 10) %>% 
     pull(watershed_id)
   
   dat_fish <- d0 %>% 
-    filter(watershed_id %in% wsd_subset) %>% 
+    filter(watershed_id %in% wsd_candidate) %>% 
     as_tibble()
   
   dat_alpha <- dat_fish %>% 
@@ -45,17 +49,9 @@
     group_by(watershed_id) %>% 
     summarise(mu_alpha = mean(alpha_div))
 
-  ## export point data
-  albers_point <- d0 %>% 
-    filter(watershed_id %in% wsd_subset) %>% 
-    group_by(SiteID) %>% 
-    distinct(SiteID)
-  
-  st_write(albers_point, "data_gis/albers_point_subset_mw.gpkg", append = FALSE)
-  
-  
 # rarefaction -------------------------------------------------------------
-
+  
+  ## convert data to frequency
   dat_freq <- dat_fish %>% 
[…]

### 2020-11-12 empirical/figure_diversity.R

@@ -5,50 +5,102 @@
   pacman::p_load(tidyverse, sf, patchwork)
   setwd(here::here("empirical"))
 
-# fig: gamma --------------------------------------------------------------
+# set plot theme ----------------------------------------------------------
+  
+  plt_theme <- theme_bw() + theme(
+    plot.background = element_blank(),
+    
+    panel.background = element_rect(grey(0.99)),
+    panel.border = element_rect(),
+    
+    panel.grid = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    panel.grid.minor.y = element_blank(),
+    
+    strip.background = element_blank(),
+    strip.text.x = element_text(size = 10),
+    strip.text.y = element_text(size = 10),
+    axis.title = element_text(size = 10)
+  )
+  
+  theme_set(plt_theme)
+  
 
-  ## read data
+# read data ---------------------------------------------------------------
+  
+  ## model estimate
+  source(normalizePath("../empirical/analysis_lm.R"))
+  
+  ## redefine data.frame
   dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
   dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
   
   dat <- bind_rows(dat_hkd, dat_mw) %>% 
-    rename(gamma = Estimator,
-           gamma_lower = '95% Lower',
-           gamma_upper = '95% Upper') %>% 
-    mutate(beta = gamma/mu_alpha,
-           beta_lower = gamma_lower/mu_alpha,
-           beta_upper = gamma_upper/mu_alpha)
+    rename(gamma = Estimator, alpha = mu_alpha) %>% 
+    mutate(beta = gamma/alpha,
+           logit_forest = log(frac_forest) - log(1 - frac_forest)) %>% 
+    mutate(resid_forest = resid(lm(logit_forest ~ region, data = .)),
+           resid_temp = resid(lm(mean_temp ~ region, data = .)),
+           resid_ppt = resid(lm(mean_ppt ~ region, data = .))) %>% 
+    pivot_longer(cols = c(alpha, beta, gamma),
[…]

### 2020-11-12 empirical/figure_map.R

@@ -3,35 +3,124 @@
 # setup -------------------------------------------------------------------
   
   rm(list = ls(all.names = TRUE))
-  pacman::p_load(tidyverse, sf, patchwork)
+  pacman::p_load(tidyverse, sf, patchwork, mcbrnet, igraph, ggraph, foreach)
   setwd(here::here("empirical"))
 
+
+# fig: network ------------------------------------------------------------
+  
+  ## set theme
+  plt_theme <- theme_bw() + theme(
+    plot.background = element_blank(),
+    
+    panel.background = element_blank(),
+    panel.border = element_blank(),
+    
+    panel.grid = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    panel.grid.minor.y = element_blank(),
+    
+    strip.background = element_blank(),
+    strip.text.x = element_text(size = 10),
+    strip.text.y = element_text(size = 10),
+    axis.title = element_text(size = 10)
+  )
+  
+  theme_set(plt_theme)
+  
+  ## network generation
+  n_patch <- 50
+  p_branch <- seq(0.2, 0.8, by = 0.3)
+  
+  set.seed(111)
+  net <- lapply(p_branch, FUN = function(x) brnet(n_patch = n_patch, p_branch = x, plot= FALSE,
+                                                  sd_env_lon = 0.01, sd_env_source = 1))
+  v_env <- unlist(lapply(seq_len(length(net)), FUN = function(x) net[[x]]$df_patch$environment))
+  
+  colvalue <- data.frame(color = viridis::viridis(length(v_env)),
+                         value = sort(v_env))
+  
+  
+  ng <- foreach(i = seq_len(length(net))) %do% {
+    adj <-  net[[i]]$adjacency_matrix %>% graph.adjacency()
+    V(adj)$env <- net[[i]]$df_patch$environment
+    
+    adj %>% 
+      ggraph(layout = layout_as_tree(., flip.y = FALSE, root = 1)) +
+      geom_edge_link(color = alpha("steelblue", 0.5)) +
+      geom_node_point(shape = 21,
+                      fill = colvalue$color[match(V(adj)$env, colvalue$value)],
[…]

### 2020-11-12 theory/figure.R

@@ -1,88 +1,0 @@
-
-
-# setup -------------------------------------------------------------------
-
-  rm(list = ls(all.names = TRUE))
-  pacman::p_load(tidyverse, broom)
-  setwd(here::here("theory"))
-
-# read data ---------------------------------------------------------------
-
-  dat <- read_csv("result/result_sim2020-11-03.csv") %>% 
-    select(-beta_div) %>% 
-    filter(alpha_div >= 1 & gamma_div >= 1,
-           sd_env_source == 1,
-           sd_env_lon == 0.01) %>% 
-    mutate(beta_div = gamma_div/alpha_div) %>% 
-    pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
-                 names_to = "metric") %>% 
-    mutate(competition = recode(max_alpha,
-                                `0.75` = "Weak competition",
-                                `1.5` = "Strong competition"))
-
-  dat$disp_label <- sprintf('Dispersal prob. = %.2f', dat$p_dispersal)
-  dat$disp_label <- factor(dat$disp_label, levels = unique(dat$disp_label))
-  
-  labels <- c(expression(alpha), expression(beta), expression(gamma))
-  
-
-# set plot theme ----------------------------------------------------------
-
-  plt_theme <- theme_bw() + theme(
-    plot.background = element_blank(),
-    
-    panel.background = element_rect(grey(0.95)),
-    panel.border = element_rect(),
-    
-    panel.grid = element_blank(),
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    
-    panel.grid.major.x = element_blank(),
-    panel.grid.major.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    panel.grid.minor.y = element_blank(),
-    
-    strip.background = element_blank(),
-    strip.text.x = element_text(size = 10),
-    strip.text.y = element_text(size = 10),
-    axis.title = element_text(size = 10)
-  )
-  
-  theme_set(plt_theme)
-  
-  
-# ecosystem size effect ---------------------------------------------------
-    
-  dat %>% 
-    ggplot(aes(x = n_patch, y = value, color = metric, fill = metric)) +
-    geom_smooth(method = "loess", size = 0.3) +
-    geom_point(alpha = 0.2, size = 0.75) +
-    scale_y_continuous(trans = "log10") +
-    scale_x_continuous(trans = "log10") +
[…]

### 2020-11-12 theory/figure_n_patch.R

@@ -1,0 +1,70 @@
+
+# setup -------------------------------------------------------------------
+
+  rm(list = ls(all.names = TRUE))
+  pacman::p_load(tidyverse)
+
+# read data ---------------------------------------------------------------
+
+  dat <- read_csv(normalizePath("../theory/result/result_sim2020-11-10.csv")) %>% 
+    select(-beta_div) %>% 
+    filter(alpha_div > 0 & gamma_div > 0,
+           p_dispersal == 0.01,
+           sd_env_source == 1,
+           sd_env_lon == 0.01) %>% 
+    mutate(beta_div = gamma_div/alpha_div) %>% 
+    pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
+                 names_to = "metric") %>% 
+    mutate(competition = recode(max_alpha,
+                                `0.75` = sprintf('"Weak competition"~(alpha[max]=="%.2f")', max_alpha),
+                                `1.5` = sprintf('"Strong competition"~(alpha[max]=="%.2f")', max_alpha)),
+           dispersal = recode(theta,
+                              `0.1` = sprintf('"Long-distance dispersal "(theta=="%.2f")', theta),
+                              `1.0` = sprintf('"Short-distance dispersal "(theta=="%.2f")', theta)))
+  
+  labels <- c(expression(alpha~"diversity"),
+              expression(beta~"diversity"),
+              expression(gamma~"diversity"))
+  
+
+# set plot theme ----------------------------------------------------------
+
+  plt_theme <- theme_bw() + theme(
+    plot.background = element_blank(),
+    
+    panel.background = element_rect(grey(0.99)),
+    panel.border = element_rect(),
+    
+    panel.grid = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    panel.grid.minor.y = element_blank(),
+    
+    strip.background = element_blank(),
+    strip.text.x = element_text(size = 10),
+    strip.text.y = element_text(size = 10),
+    axis.title = element_text(size = 10)
+  )
+  
+  theme_set(plt_theme)
+
+
+# ecosystem size effect ---------------------------------------------------
+
+  g <- dat %>% 
+    ggplot(aes(x = n_patch, y = value, color = metric, fill = metric)) +
[…]

### 2020-11-12 theory/figure_p_branch.R

@@ -1,0 +1,70 @@
+
+# setup -------------------------------------------------------------------
+  
+  rm(list = ls(all.names = TRUE))
+  pacman::p_load(tidyverse)
+
+# read data ---------------------------------------------------------------
+  
+  dat <- read_csv(normalizePath("../theory/result/result_sim2020-11-10.csv")) %>% 
+    select(-beta_div) %>% 
+    filter(alpha_div > 0 & gamma_div > 0,
+           p_dispersal == 0.01,
+           sd_env_source == 1,
+           sd_env_lon == 0.01) %>% 
+    mutate(beta_div = gamma_div/alpha_div) %>% 
+    pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
+                 names_to = "metric") %>% 
+    mutate(competition = recode(max_alpha,
+                                `0.75` = sprintf('"Weak competition"~(alpha[max]=="%.2f")', max_alpha),
+                                `1.5` = sprintf('"Strong competition"~(alpha[max]=="%.2f")', max_alpha)),
+           dispersal = recode(theta,
+                              `0.1` = sprintf('"Long-distance dispersal"~(theta=="%.2f")', theta),
+                              `1.0` = sprintf('"Short-distance dispersal"~(theta=="%.2f")', theta)))
+  
+  labels <- c(expression(alpha~"diversity"),
+              expression(beta~"diversity"),
+              expression(gamma~"diversity"))
+
+
+# set plot theme ----------------------------------------------------------
+
+  plt_theme <- theme_bw() + theme(
+    plot.background = element_blank(),
+    
+    panel.background = element_rect(grey(0.99)),
+    panel.border = element_rect(),
+    
+    panel.grid = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    panel.grid.minor.y = element_blank(),
+    
+    strip.background = element_blank(),
+    strip.text.x = element_text(size = 10),
+    strip.text.y = element_text(size = 10),
+    axis.title = element_text(size = 10)
+  )
+  
+  theme_set(plt_theme)
+
+
+# complexity effect -------------------------------------------------------
+
+  g <- dat %>% 
[…]

### 2020-11-12 theory/run_simulation.R

@@ -20,7 +20,7 @@
                       min_optim = -1,
                       max_optim = 1,
                       sd_env_lon = c(0.01, 1),
-                      theta = 1,
+                      theta = c(0.1, 1),
                       K0 = 100,
                       sd_env = 0.1,
                       spatial_env_cor = TRUE,

### 2020-11-14 empirical/figure_diversity.R
Update figure_diversity.R

@@ -34,7 +34,7 @@
 # read data ---------------------------------------------------------------
   
   ## model estimate
-  source(normalizePath("../empirical/analysis_lm.R"))
+  source(normalizePath("../empirical/analysis_rlm.R"))
   
   ## redefine data.frame
   dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
@@ -102,5 +102,7 @@
     scale_x_continuous(trans='log10')
   
   print(  
-    ((g1 + theme(legend.position = "none") + ylab("Species richness")))/(g2 + ylab("Species richness")) + plot_layout(guides = "collect")
+    (g1 + theme(legend.position = "none") + ylab("Species richness"))/
+    (g2 + ylab("Species richness")) + plot_layout(guides = "collect") +
+    plot_annotation(tag_levels = 'A')
   )  

### 2020-11-14 theory/figure_n_patch.R
Edits: figure change line width

@@ -57,7 +57,7 @@
 
   g <- dat %>% 
     ggplot(aes(x = n_patch, y = value, color = metric, fill = metric)) +
-    geom_smooth(method = "loess", size = 0.3) +
+    geom_smooth(method = "loess", size = 0.5) +
     scale_y_continuous(trans = "log10") +
     scale_x_continuous(trans = "log10") +
     scale_color_hue(name = NULL, labels = labels) +

### 2020-11-14 theory/figure_p_branch.R

@@ -57,7 +57,7 @@
 
   g <- dat %>% 
     ggplot(aes(x = p_branch, y = value, color = metric, fill = metric)) +
-    geom_smooth(method = "loess", size = 0.3) +
+    geom_smooth(method = "loess", size = 0.5) +
     scale_y_continuous(trans = "log10") +
     scale_x_continuous(trans = "log10", breaks = c(0.01, 0.1, 0.5, 1.0)) +
     scale_color_hue(name = NULL, labels = labels) +

### 2020-11-14 manuscript/_main.Rmd
Edits: figures Rmd file

--- 2020-11-12 manuscript/manuscript.Rmd
@@
+---
+title: "Figures"
+output:
+  pdf_document: default
+---
+
+```{r setup, include=FALSE}
+
+knitr::opts_chunk$set(echo = FALSE,
+                      message = FALSE,
+                      warning = FALSE)
+
+```
+
+```{r, fig.height=6, fig.width=8, fig.cap="(A) Framework of generating theoretical branching river networks.
+Branching river networks are dipicted as a network of connected habitat patches, in which the number of habitat patches $N$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example).
+Environmental conditions at headwaters (i.e., the most upstream patches) are generated randomly as a realization of a normal distribution and propagate downstream with local environmental noises (a spatially autoregressive process with a white noise; Methods).
+Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values).
+(B) Example of intesively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in C).
+Red dots indicate sampling sites for fish surveys.
+(C) Map of study regions (left, Midwest, US; right, Hokkaido, Japan).
+Watersheds (i.e., metacommunities) are gray-shaded in propotion to the number of sampling sites."}
+
+source(normalizePath("../empirical/figure_map.R"))
+
+```
+
+\newpage
+
+```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
+Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
+Rows represent different compeition strength.
+Competitive coefficients ($\\alpha_{c}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
+Columns represent different dispersal scenarios.
+Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$).
+In this simulation, environmental vairiability among headwaters (i.e., the most upstream patches), which is expressed as the standard deviation of a normal distribution ($\\sigma_{h} = 1.0$), was greater than that of local environmental noises occurring at each habitat patch ($\\sigma_{l} = 0.01$).
+Dispersal probability $p_{d}$ was 0.01 for all the scenarios."}
+
+source(normalizePath("../theory/figure_n_patch.R"))
+```
+
+\newpage
+
+```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
+Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
+See Figure 2 for details."}
+
+source(normalizePath("../theory/figure_p_branch.R"))
+```
+
+\newpage
+
+```{r, fig.height=6, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (left), $\\beta$ (middle), and $\\gamma$ diversity (right) in Hokkaido and Midwest regions.
+Dots represent watershed replicates (i.e., metacommunities) and lines are predicted values from the linear regression models."}
+
+source(normalizePath("../empirical/figure_diversity.R"))
+```
+
+<!--chapter:end:figures.Rmd-->
+
 ---
@@
 # Methods
+
+<!--chapter:end:manuscript.Rmd-->
+
+---
+title: "Tables"
+output:
+  pdf_document: default
+---
+
+```{r setup, include=FALSE}
+
+  knitr::opts_knit$set(root.dir = here::here("empirical"))
+
+```
+
+```{r, echo = FALSE, message=FALSE, results='asis'}
+
+source(normalizePath("../empirical/analysis_lm.R"))
+
+stargazer::stargazer(m_alpha$model, m_beta$model, m_gamma$model,
+                     header = FALSE,
+                     title = "Estimated parameters of robust linear regression models explaining fish species richness in Hokkaido (Japan) and Midwest (US) regions.
+Dependent variables were log-10 transformed.
+Environmental variables (air temperature, precipitation, logit \\% forest) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one.",
+                     type = "latex",
+                     ci = TRUE,
+                     covariate.labels = c("$log_{10}$ Watershed area",
+                                          "$log_{10}$ Branching probability",
+                                          "Region (Midwest vs. Hokkaido)",
+                                          "Air temperature",
+                                          "Precipitation",
+                                          "Logit \\% forest",
+                                          "Intercept"),
+                     single.row = FALSE,
+                     digits = 2,
+                     dep.var.labels.include = FALSE,
+                     column.labels = c("$\\alpha$ richness", "$\\beta$ richness", "$\\gamma$ richness"),
+                     keep.stat = c("rsq"),
+                     model.numbers = FALSE)
+
+```
+
+<!--chapter:end:table.Rmd-->

### 2020-11-14 manuscript/figures.Rmd
Edits: figures Rmd file

@@
 
-```{r, fig.height=7, fig.width=8, fig.cap="(A) Example of theoretical branching river networks.
-Branching river networks are dipicted as a network of connected habitat patches, in which the number of habitat patches $N$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example).
-Environmental conditions at the headwaters (the most upstream patches) are generated randomly and propagate downstream with local noises.
-Habitat patches are colored in proportion to environmental values (similarly-colored habitat patches have similar environmental values).
-(B) Map of study regions (left, Midwest, US; right, Hokkaido, Japan).
-Watersheds (i.e., metacommunities) are colored in propotion to the number of sites for fish surveys."}
+```{r, fig.height=6, fig.width=8, fig.cap="(A) Framework for generating theoretical branching river networks.
+Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example).
+Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (a spatially autoregressive process with white noise; Methods).
+Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values).
+(B) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in C).
+Red dots indicate sampling sites for fish surveys.
+(C) Map of study regions (left, Midwest, US; right, Hokkaido, Japan).
+Watersheds (i.e., metacommunities) are gray-shaded in proportion to the number of sampling sites."}
 
@@
 
-```{r, fig.height=5, fig.width=7}
+```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
+Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals.
+Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
+Rows represent different competition strength.
+Competitive coefficients ($\\alpha_{c}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
+Columns represent different dispersal scenarios.
+Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$).
+In this simulation, environmental variability among headwaters (i.e., the most upstream patches), which is expressed as the standard deviation of a normal distribution ($\\sigma_{h} = 1.0$), was greater than that of local environmental noise occurring at each habitat patch ($\\sigma_{l} = 0.01$).
+Dispersal probability $p_{d}$ was 0.01 for all the scenarios."}
 
 source(normalizePath("../theory/figure_n_patch.R"))
-
 ```
@@
 
-```{r, fig.height=5, fig.width=7}
+```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
+Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals.
+Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
+See Figure 2 for details."}
 
 source(normalizePath("../theory/figure_p_branch.R"))
-
 ```
@@
 
-```{r, fig.height=6, fig.width=8}
+```{r, fig.height=6, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (left), $\\beta$ (middle), and $\\gamma$ diversity (right) in Hokkaido and Midwest regions.
+Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the linear regression models."}
 
 source(normalizePath("../empirical/figure_diversity.R"))
-
 ```

### 2020-11-16 empirical/figure_diversity.R
Edits: figure files

@@ -34,7 +34,7 @@
 # read data ---------------------------------------------------------------
   
   ## model estimate
-  source(normalizePath("../empirical/analysis_rlm.R"))
+  source(normalizePath("../empirical/analysis_lm_bf.R"))
   
   ## redefine data.frame
   dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
@@ -50,36 +50,42 @@
     pivot_longer(cols = c(alpha, beta, gamma),
                  names_to = "metric")
   
-  ## data.frame for prediction
-  f_area <- 10^mean(log(dat$area, 10))
-  x_area <- rep(seq(min(dat$area), max(dat$area), length = 100), times = 2)
-  
-  f_p_branch = 10^mean(log(dat$p_branch, 10))
-  x_p_branch = rep(seq(min(dat$p_branch), max(dat$p_branch), length = 100), times = 2)
-  
   dat_base <- data.frame(region = factor(rep(c("hokkaido", "midwest"), each = 100)),
                          resid_temp = mean(dat$resid_temp),
                          resid_ppt = mean(dat$resid_ppt),
                          resid_forest = mean(dat$resid_forest))
+
+# data frame for prediction -----------------------------------------------
   
-  dat_area <- data.frame(area = x_area, p_branch = f_p_branch, dat_base)
-  dat_bp <- data.frame(area = f_area, p_branch = x_p_branch, dat_base)
+  f_area <- 10^mean(log(dat$area, 10))
+  f_p_branch = 10^mean(log(dat$p_branch, 10))
+  
+  ## area prediction
+  dat_area <- dat %>% 
+    group_by(region) %>% 
+    summarise(area = seq(min(area), max(area), length = 100)) %>% 
+    left_join(dat_base, by = "region") %>% 
+    mutate(p_branch = f_p_branch)
+  
+  dat_bp <- dat %>% 
+    group_by(region) %>% 
+    summarise(p_branch = seq(min(p_branch), max(p_branch), length = 100)) %>% 
+    left_join(dat_base, by = "region") %>% 
+    mutate(area = f_area)
   
   ### area
-  dat_area$alpha <- 10^predict(m_alpha$model, dat_area)
-  dat_area$beta <- 10^predict(m_beta$model, dat_area)
-  dat_area$gamma <- 10^predict(m_gamma$model, dat_area)
[…]

### 2020-11-16 empirical/figure_map.R

@@ -95,13 +95,13 @@
   
   ## example channel
   channel_eg <- channel_hkd %>% 
-    filter(id == 1012)
+    filter(id == 1009)
   
   polygon_eg <- wsd_subset[[1]] %>% 
-    filter(watershed_id == 1012)
+    filter(watershed_id == 1009)
   
   point_eg <- st_join(point_subset[[1]], wsd_subset[[1]]) %>% 
-    filter(watershed_id == 1012)
+    filter(watershed_id == 1009)
   
   eg <- ggplot() +
     geom_sf(data = polygon_eg, fill = grey(0.99)) +

### 2020-11-16 theory/figure_n_patch.R

@@ -6,7 +6,7 @@
 
 # read data ---------------------------------------------------------------
 
-  dat <- read_csv(normalizePath("../theory/result/result_sim2020-11-10.csv")) %>% 
+  dat <- read_csv(here::here("theory/result/result_sim2020-11-10.csv")) %>% 
     select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
            p_dispersal == 0.01,
@@ -19,8 +19,8 @@
                                 `0.75` = sprintf('"Weak competition"~(alpha[max]=="%.2f")', max_alpha),
                                 `1.5` = sprintf('"Strong competition"~(alpha[max]=="%.2f")', max_alpha)),
            dispersal = recode(theta,
-                              `0.1` = sprintf('"Long-distance dispersal "(theta=="%.2f")', theta),
-                              `1.0` = sprintf('"Short-distance dispersal "(theta=="%.2f")', theta)))
+                              `0.1` = sprintf('"Long-distance dispersal"~(theta=="%.2f")', theta),
+                              `1.0` = sprintf('"Short-distance dispersal"~(theta=="%.2f")', theta)))
   
   labels <- c(expression(alpha~"diversity"),
               expression(beta~"diversity"),

### 2020-11-16 theory/figure_n_patch_si.R

@@ -1,17 +1,17 @@
 
 # setup -------------------------------------------------------------------
-  
+
   rm(list = ls(all.names = TRUE))
   pacman::p_load(tidyverse)
 
 # read data ---------------------------------------------------------------
-  
+
   dat <- read_csv(here::here("theory/result/result_sim2020-11-10.csv")) %>% 
     select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
-           p_dispersal == 0.01,
+           p_dispersal == 0.1,
            sd_env_source == 1,
-           sd_env_lon == 0.01) %>% 
+           sd_env_lon == 1) %>% 
     mutate(beta_div = gamma_div/alpha_div) %>% 
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
@@ -25,7 +25,7 @@
   labels <- c(expression(alpha~"diversity"),
               expression(beta~"diversity"),
               expression(gamma~"diversity"))
-
+  
 
 # set plot theme ----------------------------------------------------------
 
@@ -53,16 +53,16 @@
   theme_set(plt_theme)
 
 
-# complexity effect -------------------------------------------------------
+# ecosystem size effect ---------------------------------------------------
 
   g <- dat %>% 
-    ggplot(aes(x = p_branch, y = value, color = metric, fill = metric)) +
+    ggplot(aes(x = n_patch, y = value, color = metric, fill = metric)) +
     geom_smooth(method = "loess", size = 0.5) +
     scale_y_continuous(trans = "log10") +
-    scale_x_continuous(trans = "log10", breaks = c(0.01, 0.1, 0.5, 1.0)) +
+    scale_x_continuous(trans = "log10") +
     scale_color_hue(name = NULL, labels = labels) +
     facet_grid(rows = vars(competition), cols = vars(dispersal), labeller = label_parsed) +
-    labs(x = "Branching probability",
+    labs(x = "Number of habitat patches",
          y = "Species richness") +
     guides(color = guide_legend(override.aes = list(fill = NA)),
            fill = FALSE)

### 2020-11-16 theory/figure_p_branch_si.R

@@ -9,9 +9,9 @@
   dat <- read_csv(here::here("theory/result/result_sim2020-11-10.csv")) %>% 
     select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
-           p_dispersal == 0.01,
+           p_dispersal == 0.1,
            sd_env_source == 1,
-           sd_env_lon == 0.01) %>% 
+           sd_env_lon == 1) %>% 
     mutate(beta_div = gamma_div/alpha_div) %>% 
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 

### 2020-11-16 empirical/analysis_lm.R
Edits: analysis files

@@ -1,57 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-  rm(list = ls(all.names = TRUE))
-  pacman::p_load(tidyverse, MuMIn, MASS)
-  options(na.action = "na.fail")
-  setwd(here::here("empirical"))
-
-# read data ---------------------------------------------------------------
-  
-  dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
-  dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
-  
-  dat <- bind_rows(dat_hkd, dat_mw) %>% 
-    rename(gamma = Estimator,
-           alpha = mu_alpha) %>% 
-    mutate(beta = gamma/alpha,
-           logit_forest = log(frac_forest) - log(1 - frac_forest)) %>% 
-    mutate(resid_forest = resid(lm(logit_forest ~ region, data = .)),
-           resid_temp = resid(lm(mean_temp ~ region, data = .)),
-           resid_ppt = resid(lm(mean_ppt ~ region, data = .)))
-  
-
-# model selection ---------------------------------------------------------
-
-  m_compare <- function(response, data) {
-    
-    fit <<- list(NULL)
-    fit[[1]] <<- lm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
-                                        scale(resid_temp) + scale(resid_ppt) + scale(resid_forest),
-                    data = data)
-    
-    fit[[2]] <<- lm(log(response, 10) ~ log(area, 10)*region + log(p_branch, 10)*region + region +
-                                        scale(resid_temp) + scale(resid_ppt) + scale(resid_forest),
-                    data = data)
-    
-    fit[[3]] <<- lm(log(response, 10) ~ 1,
-                    data = data)
-    
-    m <- fit[[which.min(sapply(fit, FUN = BIC))]]
-    df <- tibble(model = c("global", "region-specific", "null"),
-                 AIC = sapply(fit, FUN = AIC),
-                 AICc = sapply(fit, FUN = AICc),
-                 BIC = sapply(fit, FUN = BIC))
-    
-    return(list(model = m, model_table = df))
-  }
-  
-  ## alpha 
-  m_alpha <- m_compare(dat$alpha, data = dat, rank = BIC)
-  
-  ## beta
[…]

### 2020-11-16 empirical/analysis_lm_bf.R

@@ -1,0 +1,45 @@
+
+# setup -------------------------------------------------------------------
+
+  rm(list = ls(all.names = TRUE))
+  pacman::p_load(tidyverse)
+  setwd(here::here("empirical"))
+
+# read data ---------------------------------------------------------------
+  
+  dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
+  dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
+  
+  dat <- bind_rows(dat_hkd, dat_mw) %>% 
+    rename(gamma = Estimator,
+           alpha = mu_alpha) %>% 
+    mutate(beta = gamma/alpha,
+           logit_forest = log(frac_forest) - log(1 - frac_forest)) %>% 
+    mutate(resid_forest = resid(lm(logit_forest ~ region, data = .)),
+           resid_temp = resid(lm(mean_temp ~ region, data = .)),
+           resid_ppt = resid(lm(mean_ppt ~ region, data = .)))
+  
+
+# model selection ---------------------------------------------------------
+
+  m_compare <- function(response, data) {
+    
+    mod1 <<- lm(log(response, 10) ~ log(area, 10)*region + log(p_branch, 10)*region + region +
+                                    scale(resid_temp) + scale(resid_ppt) + scale(resid_forest),
+                data = data)
+    
+    mod0 <<- lm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
+                                    scale(resid_temp) + scale(resid_ppt) + scale(resid_forest),
+                    data = data)
+    
+    # bf01: bayes factor in favor of mod0 over mod1
+    bf01 <- exp(0.5*(BIC(mod1) - BIC(mod0)))
+    
+    if(bf01 >= 1) m <- mod0 else m <- mod1
+    
+    return(list(model = m, bayes_factor = bf01))
+    
+  }
+  
+  fit <- lapply(dat[,c("alpha", "beta", "gamma")], FUN = m_compare, data = dat)
+  

### 2020-11-16 empirical/analysis_rlm.R

@@ -1,57 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-  rm(list = ls(all.names = TRUE))
-  pacman::p_load(tidyverse, MuMIn, MASS)
-  options(na.action = "na.fail")
-  setwd(here::here("empirical"))
-
-# read data ---------------------------------------------------------------
-  
-  dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
-  dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
-  
-  dat <- bind_rows(dat_hkd, dat_mw) %>% 
-    rename(gamma = Estimator,
-           alpha = mu_alpha) %>% 
-    mutate(beta = gamma/alpha,
-           logit_forest = log(frac_forest) - log(1 - frac_forest)) %>% 
-    mutate(resid_forest = resid(lm(logit_forest ~ region, data = .)),
-           resid_temp = resid(lm(mean_temp ~ region, data = .)),
-           resid_ppt = resid(lm(mean_ppt ~ region, data = .)))
-  
-
-# model selection ---------------------------------------------------------
-
-  m_compare <- function(response, data, rank) {
-    
-    fit <<- list(NULL)
-    fit[[1]] <<- rlm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
-                                         scale(resid_temp) + scale(resid_ppt) + scale(resid_forest),
-                     data = data, method = "M", psi = psi.huber)
-    
-    fit[[2]] <<- rlm(log(response, 10) ~ log(area, 10)*region + log(p_branch, 10)*region + region +
-                                         scale(resid_temp) + scale(resid_ppt) + scale(resid_forest),
-                     data = data, method = "M", psi = psi.huber)
-    
-    fit[[3]] <<- rlm(log(response, 10) ~ 1,
-                     data = data, method = "M", psi = psi.huber)
-    
-    m <- fit[[which.min(sapply(fit, FUN = rank))]]
-    df <- tibble(model = c("global", "region-specific", "null"),
-                 AIC = sapply(fit, FUN = AIC),
-                 AICc = sapply(fit, FUN = AICc),
-                 BIC = sapply(fit, FUN = BIC))
-    
-    return(list(model = m, model_table = df))
-  }
-  
-  ## alpha 
[…]

### 2020-11-16 manuscript/manuscript.Rmd
Edits: misc

@@
 author:
-- name: Akira Terui
-  email: hanabi0111@gmail.com
-  affiliation: Department of Biology, University of North Carolina at Greensboro
-  footnote: Corresponding Author
-- name: Seoghyun Kim
-  email: s_kim53@uncg.edu
-  affiliation: Department of Biology, University of North Carolina at Greensboro
-- name: Christy Dolph
-  email: XXX
-  affiliation: XXX
-output: html_notebook
+- Akira Terui^[Department of Biology, University of North Carolina at Greensboro]
+- Seoghyn Kim\footnotemark[1]
+- Christine L. Dolph^[Department of Ecology, Evolution and Behavior]
+output:
+  html_notebook: default
+abstract: |
+  |This is the abstract.
 bibliography: reference.bib
 csl: nature.csl
-abstract: |
-  This is the abstract.
-  It consists of two paragraphs.
 ---
@@
 ```{r setup, include=FALSE}
+
 pacman::p_load(tidyverse, sf)
-setwd(here::here("empirical"))
 
 ## read gis files
-filename <- list.files(path = 'data_gis', full.names = T)
+filename <- list.files(path = normalizePath('../empirical/data_gis'), full.names = T)
 wsd_subset <- lapply(filename[str_detect(filename, "wsd_subset")], st_read)
@@
 
+## read theory file
+dat_sim <- read_csv(normalizePath('../theory/result/result_sim2020-11-10.csv'))
+
+n_scenario <- dat_sim %>% distinct(n_species,
+                     mean_env_source,
+                     sd_env_source,
+                     rho,
+                     asymmetry_factor,
+                     min_optim,
+                     max_optim,
+                     sd_env_lon,
+                     theta,
+                     K0,
+                     sd_env,
+                     spatial_env_cor,
+                     phi,
+                     min_niche_width,
+                     max_niche_width,
+                     niche_cost,
+                     p_dispersal,
+                     min_alpha,
+                     max_alpha) %>% 
+  nrow()
+
 ```
@@
 One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area (the species-area relationship; SAR).
-In 1921, XXX formulated the SAR as a power-law $S = cA^z$ ($S$ is the number of species observed in a given geographic area $A$), the equation currently known as the Arrhenius species-area relationship.
+In 1921, XXX formulated the SAR as a power-law $S = cA^z$ ($S$ is the number of species observed in a given geographic area $A$), which is currently called as the Arrhenius species-area relationship.
 Since then, the spatial scaling of species richness has been observed in nearly all taxonomic groups, although the underlying mechanisms are still hotly debated.
 The SAR is general because multiple mechanisms produce an apparently similar pattern.
-Larger ecosystems typically support more diverse communities due to increased habitat diversity, larger (meta)community size, and/or enhanced colonization dynamics.
+Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity, larger metacommunity size, and/or enhanced colonization dynamics.
 Importantly, the SAR provides the foundation for global conservation efforts.
@@
 
-However, many ecosystems possess a dimension of spatial complexity that cannot be described by area (i.e., the scale-invariant complexity).
-Such spatial complexity is evident in branching ecosystems, such as rivers, trees, and mountain ranges, to name just a few.
-Geomorphic or biological processes generate a pronounced self-similarity in complex branching structure so that the part and the whole look alike.
+Many ecosystems, however, possess complex spatial structure that cannot be represented by area, a dimension known as the scale-invariant complexity.
+Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few.
+Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike.
 Even though the branching structure is independent of spatial scale, it forms a physical template that determines habitat diversity and dispersal corridors for living organisms.
-Evidence suggests that ecological dynamics driven by branching structure cannot be predicted by scale-dependent theories; this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems.
+Evidence suggests that scale-dependent theories cannot predict ecological dynamics driven by branching structure, and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@altermattDiversityRiverineMetacommunities2013; @carraraComplexInteractionDendritic2014; @carraraDendriticConnectivityControls2012; @teruiMetapopulationStabilityBranching2018].
 However, most research either has explored the consequences of branching complexity for local biodiversity patterns or relied on theoretical arguments with limited replicates of artificial branching networks.
-At present, no studies have integrated theoretical and empirical approaches to link branching complexity and $\gamma$ diversity (i.
-e., the total species richness in a metacommunity).
+At present, no studies have investigated how ecosystem size and complexity jointly regulate species diversity at the metacommunity level (i.
+e., $\gamma$ diversity).
 This knowledge gap significantly limits our ability to guide biodiversity conservation in spatially complex ecosystems.
@@
 Simulated species with different niche in abiotic conditions (optimum and width) compete for resources with varied strengths.
-For simplicity, other ecological traits are assumed to be identical among species (e.g., dispersal probability).
-Here, branching networks are depicted as a spatial network of connected habitat patches (or a discretized river section) where mean environmental conditions at each habitat patch are determined by two factors: (1) environments of headwaters (the most upstream habitat patch) and (2) local environmental noises.
-Environmental values at headwaters are produced randomly and propagate downstream with local environmental noises (i.e., the spatial autoregressive process with  a white noise).
+For simplicity, other ecological traits, such as dispersal probability, are assumed to be identical among species.
+Here, branching networks are depicted as a spatial network of connected habitat patches (or a discretized river section; see **Figure 1**) where mean environmental conditions at each habitat patch are determined by two factors: (1) the headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+Environmental values at the headwaters are drawn randomly from a normal distribution and propagates downstream with local environmental noise (i.e., the spatial autoregressive process with white noise).
 These values recurrently 'mix' at confluences considering the relative size of joining tributaries (see Methods).
-Therefore, our simulation resembles ecological processes of how branching river networks create diverse habitats in a metacommunity.
-We prepared 16 simulation scenarios with varied ecological (dispersal and competition strength) and landscape contexts (environmental variation at headwaters and the degree of local environmental noises).
-Under each scenario, we simulated metacommunity dynamics in 1000 branching networks that have different ecosystem size (the number of habitat patches in a network) and complexity (branching probability) to examine their effects on $\gamma$ diversity.
+Therefore, our simulation resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
+We prepared `r n_scenario` simulation scenarios with varied ecological (dispersal and competition strength) and landscape contexts (the environmental variation at headwaters and the degree of local environmental noise).
+Under each scenario, we simulated metacommunity dynamics in `r max(dat_sim$n_rep)` branching networks that have different ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`) to examine their effects on $\gamma$ diversity.
 
 Our theoretical analysis yielded results consistent with our prediction.
-Ecosystem size and complexity both increased $\gamma$ diversity under realistic landscape contexts, where the environmental variation at headwaters ($\sigma_h$) is greater than the degree of local environmental noises ($\sigma_l$) [@petersonModellingDendriticEcological2013; @teruiMetapopulationStabilityBranching2018].
-The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios: the strength of competition and dispersal probability did not change the form of the relationships between $\gamma$ diversity and ecosystem properties.
-The effect of ecosystem size on $\gamma$ diversity was largely driven by the spatial turnover of species composition among habitat patches ($\beta$ diversity) regardless of ecological scenarios.
-$\beta$ diversity increased significantly with increasing ecosystem size, while local diversity (average species richness in a single habitat patch; $\alpha$ diversity) remained almost unchanged.
+Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape context (**Figures 2 and 3**), where the environmental variation at headwaters ($\sigma_h$) is greater than the degree of local environmental noise ($\sigma_l$) [@petersonModellingDendriticEcological2013; @teruiMetapopulationStabilityBranching2018].
+The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios.
+The strength of competition and dispersal processes (dispersal distance and probability) did not change the form of the relationships between $\gamma$ diversity and ecosystem properties.
+Hence, the ecosystem size and complexity are both expected to increase $\gamma$ diversity regardless of ecological scenarios.
 
-In contrast, the relative importance of $\alpha$ and $\beta$ diversity in the complexity-$\gamma$ diversity relationship was dependent on the dispersal probability of constituent species.
-When dispersal probability of species was low, the positive effect of branching complexity on $\gamma$ diversity was driven mainly by increased $\beta$ diversity, reflecting significant spatial turnover of species composition.
-However, with higher dispersal probability, the relationship between $\beta$ diversity and branching complexity became a hump-shaped form.
-A clear increase in $\alpha$ diversity compensated for the slight decrease in $\beta$ diversity at high branching probabilities, maintaining the positive complexity-$\gamma$ diversity relationship.
-This likely occurred through the increased connectivity of highly branched networks.
-The average network distance between a pair of habitat patches decreases with increasing branching probability because highly branched networks have a compressed form compared to less branched networks.
-Therefore, increased dispersal readily homogenizes community composition while increasing $\alpha$ diversity through enhanced immigration from suitable habitat patches (i.e., mass effects).
-This result highlights how different mechanisms can generate an apparently similar pattern in the complexity-$\gamma$ diversity relationship.
+Dispersal processes, however, affected underlying mechanisms that produce the positive effects of ecosystem size and complexity on $\gamma$ diversity.
+We observed a greater contribution of $\beta$ diversity, which we defined as $\frac{\alpha}{\gamma}$, to increased $\gamma$ diversity in larger and more complex ecosystems when dispersal limitation exists (i.e., species travel short distances).
+This pattern reflects significant spatial turnover of species composition over the branching network.
+In contrast, once the dispersal limitation is relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
+This is understandable because increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects).
+These patterns were consistent across different levels of emigration probabilities (**cite SI figure**).
+Our theory, therefore, highlights how the apparently similar patterns in $\gamma$ diversity emerges through different ecological pathways.
 
-It is important to note that the effect of branching complexity diminished when the environmental variation at headwaters is smaller or equal to the degree of local environmental noises ($\sigma_h \le \sigma_l$).
-When local environmental noises are very large relative to environmental variation among headwaters, the net habitat diversity should be correlated with ecosystem size but not with branching complexity.
-This simulation setup decouples the intimate relationship between branching structure and habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
-This theoretical prediction may not apply to natural river networks because streams originating from different sources are known to show distinct environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes.
-Yet, this result illustrates the crucial role of habitat diversity produced by branching structure, rather than branching structure itself, in the emerging complexity-$\gamma$ diversity relationship.
+Influences of ecosystem size and complexity, however, differed significantly in their dependence on landscape scenarios.
+Ecosystem size had positive effects on $\gamma$ diversity regardless of the net habitat diversity in the ecosystem (environmental variation among headwaters + local environmental noise), though the slopes were steeper when environmental variation was greater.
+This is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity.
+In contrast, the effect of branching complexity depended strongly on the environmental variation at headwaters ($\sigma_h$; see **XXX**).
+If environmental variation among headwaters is small, there is no foundation for branching complexity to produce diverse environmental conditions over the landscape.
+Therefore, this landscape scenario decouples the intimate relationship between branching structure and habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
+This theoretical prediction may not apply to natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinctiveness in a variety of environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes.
+Yet, this result illustrates the crucial role of habitat diversity produced by branching structure in the emerging complexity-$\gamma$ diversity relationship.
 

### 2020-11-22 manuscript/manuscript.Rmd
Edits: manuscript

@@
 
+source(normalizePath('../empirical/analysis_lm_bf.R'))
+
 ```
@@
 Ecologists have long sought to understand the general drivers of biodiversity.
-One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area (the species-area relationship; SAR).
-In 1921, XXX formulated the SAR as a power-law $S = cA^z$ ($S$ is the number of species observed in a given geographic area $A$), which is currently called as the Arrhenius species-area relationship.
-Since then, the spatial scaling of species richness has been observed in nearly all taxonomic groups, although the underlying mechanisms are still hotly debated.
-The SAR is general because multiple mechanisms produce an apparently similar pattern.
-Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity, larger metacommunity size, and/or enhanced colonization dynamics.
+One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR)[@lomolinoEcologyMostGeneral2000a].
+In 1921, Arrhenius[@arrheniusSpeciesArea1921] formulated the SAR as a power-law $S = cA^z$ ($S$ is the number of species observed in a given geographic area $A$), an equation currently known as the Arrhenius species-area relationship.
+Since then, the spatial scaling of species richness has been observed in nearly all taxonomic group, although the underlying mechanisms are still hotly debated[@ben-hurDisentanglingMechanismsUnderlying2020].
+The SAR is ubiquitous because multiple mechanisms produce an apparently similar pattern.
+Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity[@kallimanisHowDoesHabitat2008], larger metacommunity size[@ben-hurDisentanglingMechanismsUnderlying2020], and/or enhanced colonization dynamics[@lososTheoryIslandBiogeography2009].
 Importantly, the SAR provides the foundation for global conservation efforts.
@@
 
-Many ecosystems, however, possess complex spatial structure that cannot be represented by area, a dimension known as the scale-invariant complexity.
-Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few.
+Many ecosystems, however, possess complex spatial structure that cannot be represented by area, a dimension referred to as the scale-invariant complexity[@rinaldoEvolutionSelectionRiver2014a; @rodriguez-iturbeFractalRiverBasins2001].
+Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few[@rodriguez-iturbeFractalRiverBasins2001].
 Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike.
-Even though the branching structure is independent of spatial scale, it forms a physical template that determines habitat diversity and dispersal corridors for living organisms.
-Evidence suggests that scale-dependent theories cannot predict ecological dynamics driven by branching structure, and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@altermattDiversityRiverineMetacommunities2013; @carraraComplexInteractionDendritic2014; @carraraDendriticConnectivityControls2012; @teruiMetapopulationStabilityBranching2018].
-However, most research either has explored the consequences of branching complexity for local biodiversity patterns or relied on theoretical arguments with limited replicates of artificial branching networks.
-At present, no studies have investigated how ecosystem size and complexity jointly regulate species diversity at the metacommunity level (i.
-e., $\gamma$ diversity).
-This knowledge gap significantly limits our ability to guide biodiversity conservation in spatially complex ecosystems.
+Even though the branching structure is independent of spatial scale, it forms a physical template that determines habitat diversity and dispersal corridors for living organisms[@grantLivingBranchesPopulation2007; @rinaldoRiverNetworksEcological2018].
+Limited, but accumulating evidence suggests that classical concepts cannot predict ecological dynamics driven by branching structure, and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@altermattDiversityRiverineMetacommunities2013; @carraraComplexInteractionDendritic2014; @carraraDendriticConnectivityControls2012; @teruiMetapopulationStabilityBranching2018].
+However, most research either has explored the consequences of branching complexity for local variation in species richness or relied on theoretical arguments with limited replicates of artificial branching networks.
+At present, we lack a comprehensive evaluation of how branching complexity, in combination with ecosystem size, scales biodiversity at the metacommunity level.
+Filling this knowledge gap may provide fundamental ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services.
 
-Here, we hypothesize that ecosystem size and complexity dictate $\gamma$ diversity in rivers, a prime example of complex branching ecosystems.
-In branching river networks, streams with diverse geological backgrounds recurrently join to form a larger, ecologically distinct channel.
-As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], should control the habitat heterogeneity of the ecosystem (habitat diversity per unit area).
+Here, we hypothesize that ecosystem size and complexity dictate biodiversity patterns in rivers, a prime example of complex branching ecosystems.
+In branching river networks, diverse streams recurrently join to form a larger, ecologically distinct channel.
+As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a], should control the habitat heterogeneity of the ecosystem (habitat diversity per unit area).
 Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity).
-We predict that ecosystem size and branching complexity increase $\gamma$ diversity.
+We predict that ecosystem size and branching complexity increase $\gamma$ diversity by enhancing either $\alpha$ and/or $\beta$ diversity under different ecological scenarios.
 The present study combines theory and statistical analysis of extensive community data to provide crucial insights into how ecological communities are structured in complex branching networks.
@@
 For simplicity, other ecological traits, such as dispersal probability, are assumed to be identical among species.
-Here, branching networks are depicted as a spatial network of connected habitat patches (or a discretized river section; see **Figure 1**) where mean environmental conditions at each habitat patch are determined by two factors: (1) the headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+Here, we depicted branching ecosystems as a spatial network of connected habitat patches (or a discretized river section; see **Figure 1**) where mean environmental conditions at each habitat patch are determined by two factors: (1) the headwater environments (the most upstream habitat patch) and (2) local environmental noise.
 Environmental values at the headwaters are drawn randomly from a normal distribution and propagates downstream with local environmental noise (i.e., the spatial autoregressive process with white noise).
@@
 Therefore, our simulation resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
-We prepared `r n_scenario` simulation scenarios with varied ecological (dispersal and competition strength) and landscape contexts (the environmental variation at headwaters and the degree of local environmental noise).
+We prepared `r n_scenario` sets of parameter combinations with varied ecological (dispersal and competition strength) and landscape scenarios (the environmental variation at headwaters and the degree of local environmental noise).
 Under each scenario, we simulated metacommunity dynamics in `r max(dat_sim$n_rep)` branching networks that have different ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`) to examine their effects on $\gamma$ diversity.
@@
 Our theoretical analysis yielded results consistent with our prediction.
-Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape context (**Figures 2 and 3**), where the environmental variation at headwaters ($\sigma_h$) is greater than the degree of local environmental noise ($\sigma_l$) [@petersonModellingDendriticEcological2013; @teruiMetapopulationStabilityBranching2018].
+Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters ($\sigma_h$) is greater than the degree of local environmental noise ($\sigma_l$) [@petersonModellingDendriticEcological2013; @teruiMetapopulationStabilityBranching2018].
 The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios.
@@
 Dispersal processes, however, affected underlying mechanisms that produce the positive effects of ecosystem size and complexity on $\gamma$ diversity.
-We observed a greater contribution of $\beta$ diversity, which we defined as $\frac{\alpha}{\gamma}$, to increased $\gamma$ diversity in larger and more complex ecosystems when dispersal limitation exists (i.e., species travel short distances).
+We observed a greater contribution of $\beta$ diversity, which we defined as $\frac{\gamma}{\alpha}$, to increased $\gamma$ diversity in larger and more complex ecosystems when dispersal limitation exists (i.e., species travel short distances).
 This pattern reflects significant spatial turnover of species composition over the branching network.
-In contrast, once the dispersal limitation is relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
+In contrast, once the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
 This is understandable because increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects).
-These patterns were consistent across different levels of emigration probabilities (**cite SI figure**).
+These patterns were consistent across different levels of dispersal probabilities (**cite SI figure**).
 Our theory, therefore, highlights how the apparently similar patterns in $\gamma$ diversity emerges through different ecological pathways.
@@
 Influences of ecosystem size and complexity, however, differed significantly in their dependence on landscape scenarios.
-Ecosystem size had positive effects on $\gamma$ diversity regardless of the net habitat diversity in the ecosystem (environmental variation among headwaters + local environmental noise), though the slopes were steeper when environmental variation was greater.
-This is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity.
-In contrast, the effect of branching complexity depended strongly on the environmental variation at headwaters ($\sigma_h$; see **XXX**).
-If environmental variation among headwaters is small, there is no foundation for branching complexity to produce diverse environmental conditions over the landscape.
+Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$).
+This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity.
+In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$).
+Under this scenario, having more branches may not contribute to the habitat diversity in the ecosystem because local environmental noise masks among-branch environmental differences.
 Therefore, this landscape scenario decouples the intimate relationship between branching structure and habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
-This theoretical prediction may not apply to natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinctiveness in a variety of environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes.
-Yet, this result illustrates the crucial role of habitat diversity produced by branching structure in the emerging complexity-$\gamma$ diversity relationship.
+This theoretical prediction may not apply to pristine to semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinctiveness in a variety of environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes.
+Instead, this result may be more relevant to severely altered landscapes where human activities compromise the environmental distinctiveness of each branch through flow regulations by dams and land use change.
+Hence, our theory, along with previous theoretical efforts, has important implications for riverine biodiversity conservation by pointing the crucial role of habitat diversity produced by branching structure[@holtRoleBranchingMaintenance2018].
 
-## Empirical evidence
-We tested our theoretical predictions using a large data set of fish communities in two geographic regions: the Hokkaido island in Japan and the Midwest in the US.
+Our theory provided important insights into how ecological communities are structured in branching networks; however, empirically testing the predictions is extremely difficult because it requires metacommunity-level replications, which are exceedingly rare.
+To confront this logistical challenge, we compiled existing community data of fishes from a variety of sources and developed a unique large dataset that spans across two geographic regions: the Hokkaido island in Japan and the Midwest in the United States.
 These regions are located in comparable ranges of latitude but support distinct fish communities.
-Therefore, this data set provides an excellent opportunity to examine the generality of our theoretical predictions.
-Our data set comprised presence-absence of fish species at XXX sites, which encompassed the majority of the two geographic regions.
-We estimated $\gamma$ diversity using a method of incidence-based extrapolation (i.e., the asymptotic species richness; see Methods) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in Midwest).
-Individual watersheds, i.e., metacommunity replicates in our analysis, were considered as independent if they flow into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
+Therefore, this dataset provides an excellent opportunity to examine the generality of our theoretical predictions.
+After careful data selection, we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; Methods) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
+Individual watersheds, i.e., metacommunity replicates in our analysis, were considered as separated if they flow into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
+We combined this dataset with geospatial information (annual mean temperature, annual cumulative precipitation, and percent forest) to account for potential influences of macro-scale drivers of species diversity.
+Using this dataset, we developed global and region-specific models for each of diversity measures ($\alpha$, $\beta$, and $\gamma$ diversity) to examine whether observed patterns are consistent across the two geographic regions.
+In the global model, we assumed that effects of ecosystem size (watershed area) and complexity (branching probability) are constant across the two regions (i.e., fixed slopes).
+Meanwhile, the region-specific model assumes region-specific slopes of ecosystem size and complexity by including interaction terms with the dummy binary variable of region (Hokkaido = 0; Midwest = 1).
+We compared the performance of these competing models using the Bayes factor, a measure of the strength of evidence in favor of one model over the alternative.
 
-Our empirical data analysis provided a strong support for theoretical predictions.
-Our theory predicts that $\gamma$ diversity increases with increasing ecosystem size and complexity.
-This is exactly what was observed in nature.
-The estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) of the studied river networks.
-Importantly, the patterns were consistent across two geographic regions (i.e., non-significant effects of interactions with region) that support distinct fish communities.
-Moreover, the effects of watershed area and branching probability remained significant even after accounting for the potential influences of other environmental factors (precipitation, temperature, and land use).
-As predicted by theory, the scaling of $\gamma$ diversity by ecosystem size or complexity was a power-law.
-Given the uncertainty of estimated $\gamma$ diversity, we repeated our analysis with lower (5%) and upper (95%) confidence intervals of $\gamma$ diversity estimates.
-Overall, we found qualitatively similar results, implying the robustness of our findings.
-Our results, therefore, provides strong empirical evidence that ecosystem complexity, not only ecosystem size, represents a dimension of ecosystem properties that scale riverine biodiversity.
+Despite the substantial difference in fish fauna between the study regions, the estimated Bayes factor in favor of the global model explaining $\gamma$ diversity was `r round(fit$gamma$bayes_factor, 1)`; this result strongly supports the consistent effects of ecosystem size and complexity on $\gamma$ diversity across the two biogeographic regions.
+Further, we found patterns consistent with our theoretical predictions.
+The estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) across watersheds.
+These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, and land use).
+Overall, our statistical analysis provides strong empirical evidence that ecosystem size and complexity jointly, but independently, scale riverine biodiversity at the metacommunity level.
 
-Detailed analysis of $\alpha$ and $\beta$ diversity patterns provides deeper insights into underlying ecological mechanisms.
+Similarly, we found weak to moderate supports for the global models explaining observed patterns of $\alpha$ and $\beta$ diversity (Bayes factor: `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
+In both regions, $\beta$ diversity, rather than $\alpha$ diversity, responded significantly to ecosystem size and complexity.
+In our simulations, this pattern has emerged in the scenarios with dispersal limitation, which elegantly match the previous observations of stream fish movement.
+Direct (mark-recapture) and indirect observations (e.g., genotyping) recurrently revealed restricted movement of stream fish, typically limited to several tens to hundreds of meters in distance.
+Therefore, it is reasonable to observe the increased spatial turnover of species composition with increasing ecosystem size and complexity.
+
+It is noteworthy that the effect of branching probability on $\gamma$ diversity was consistent across the study regions.
+The watersheds in the Midwest are severely altered by agriculture (median % agricultural land use: `r round(median(wsd_subset[[2]]$frac_agri)*100)`%) while the Hokkaido region is relatively intact (median % agricultural land use: `r round(median(wsd_subset[[1]]$frac_agri)*100)`%).
+If the land use change causes significant homogenization of in-stream habitat conditions among tributaries, theory predicts weakened effects of branching probability on $\gamma$ diversity.
+However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions and contribute to high spatial turnover of species composition over the landscape (i.e., high $\beta$ diversity).
+Indeed, $\beta$ diversity increased with increasing branching probability in both regions (**Figure 4**).
+It is conceivable that even in highly modified landscape, local geological and geomorphological differences, such as slope, aspect, and
+soil porosity, persist to support diversity of in-stream processes among tributaties.
+Although our analysis is correlative and cannot provide conclusive evidence, the finding is encouraging because branching complexity of river networks may serve as a natural defense system to human-induced environmental changes.
+
+There may be confounding factors that could not be incorporated in our statistical models.
+However, we are confident on our statistical inference for the following reason.
+The observed patterns were elegantly consistent with our theoretical predictions that are free from any confounding factors.
+Further, our fitted models generally showed high R^2^ values ($\alpha$ diversity: `r round(summary(fit$alpha$model)$r.squared, 2)`; $\beta$ diversity, `r round(summary(fit$beta$model)$r.squared, 2)`; $\gamma$ diversity `r round(summary(fit$gamma$model)$r.squared, 2)`) with no signs of spatial autocorrelation in residuals.
+Therefore, it is very unlikely that our results were driven by spurious correlations.
+
+While the prevailing evidence supports the scaling relationship between species diversity and ecosystem size, the importance of spatial complexity of ecosystems, especially branching structure, has not received the attention it deserves.
+Our results fill this knowledge gap by illuminating the dual regulation of riverine biodiversity by ecosystem size and complexity.
+
+The emerging complexity-diversity relationship points to several important avenues for improving riverine biodiversity conservation.
+First and foremost, there is now clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
+In rivers, the emerging technologies enabled us to estimate branching patterns across the globe, and there is ongoing efforts to refine global geospatial dataset.
+Such information may be used to identify areas that should be prioritized for conservation.
+Second, the complexity perspective may provide viable options to reconcile conflicts between biodiversity conservation and societal needs.
+Although protected areas spearhead global conservation efforts, habitat preservation and restoration over large areas are often impractical because of conflicts with stakeholders.
+This is particularly true for riverine ecosystems, where numerous stakeholders are involved within a single watershed and enormous efforts are required to reach consensus.
+In such a scenario, small-scale conservation, such as restoration of connectivity to small tributaties, could still significantly enhance the 'realized' network complexity that organisms may experience, potentially supporting biodiversity at the metacommunity level.
+Hence, findings from this research offer an alternative pathway to design conservation strategies in spatially complex ecosystems.
 
 # Methods
+
+## Model description
+
+The metacommunity dynamics are described as a function of local community dynamics and dispersal[@thompsonProcessbasedMetacommunityFramework2020].
+Specifically, the realized number of individuals $N_{ix}(t + 1)$ (species $i$ at patch $x$ and time $t+1$) is given as:
+
+$$
+N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
+$$
+where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}$(t) the expected number of immigrants to patch $x$, and $E_{ix}$(t) the expected number of emigrants from patch $x$.
+Local community dynamics are simulated based on the Beverton-Holt model:
+
+$$
+n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_j^S{\alpha_{ij}N_{jx}(t)}}
+$$
+
+where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, and $\alpha_{ij}$ the interaction coefficient between species $i$ and $j$.
+The parameter $\alpha_{ij}$ is the strength of interspecific competition relative to that of intraspecific competition (interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ > 1; intraspecific competition coefficient $\alpha_{ii}$ equals 1.0).
+The density-independent reproductive rate $r_{ix}(t)$ is affected by environments and determined by a Gaussian function:
+
+$$
+r_{ix}(t) = cr_{0,i}~exp[{-\frac{(\mu_i-z_x(t))^2}{2\sigma^2_{niche,i}}}]
+$$
+where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche}$ the niche width of species $i$.
+The cost of having wider niche is expressed by multiplying $c$[@chaianunpornEvolutionaryResponsesClimate2015]:
+
+$$
+c = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
+$$
+
+Smaller values of $\nu$ imply greater costs of having wider niche (i.e., decreased maximum reproductive rate). There is no cost if $\nu$ approaches infinity.
+
+The environmental value $z_x(t)$, which may vary spatially and temporarily, is assumed to follow a multivariate normal distribution:
+
+$$
+z_{x}(t) \sim MVN(\mu_z, \Omega_z)
+$$
+$\mu_z$ is the vector of mean environmental conditions of patches and $\Omega_z$ is the variance-covariance matrix. Spatial autocorrelation is considered by describing the off-diagonal elements as:
+
+$$
+\Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy})
+$$
+where $\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (randomly generated or specified by argument distance_matrix).
+The parameter $\phi$ determines distance decay of environmental correlates.
+
+The expected number of emigrants at time $t$, $E_{ix}(t)$, is the product of dispersal probability $p_d$ and $n_{ix}(t)$.
+The immigration probability at patch $x$, $\xi_{ix}$, is calculated given the structural connectivity of patch $x$, in which the model assumes the exponential decay of successful immigration with the increasing separation distance between habitat patches:
+
+$$
+\xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}
+$$
+where $d_{xy}$ is the separation distance between patch $x$ and $y$.
+The parameter $\theta$ dictates the dispersal distance of species ($\theta^{-1}$ corresponds to the expected dispersal distance) and is assumed to be constant across species.
+The expected number of immigrants is calculated as:
+
+$$
+I_{ix}(t) = \xi_{ix}(t)\sum E_{ix}
+$$
+
+# References

### 2020-11-22 manuscript/supporting_info.Rmd
Edits: manuscript

--- 2020-11-14 manuscript/figures.Rmd
@@
 
-```{r, fig.height=6, fig.width=8, fig.cap="(A) Framework for generating theoretical branching river networks.
-Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example).
-Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (a spatially autoregressive process with white noise; Methods).
-Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values).
-(B) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in C).
-Red dots indicate sampling sites for fish surveys.
-(C) Map of study regions (left, Midwest, US; right, Hokkaido, Japan).
-Watersheds (i.e., metacommunities) are gray-shaded in proportion to the number of sampling sites."}
-
-source(normalizePath("../empirical/figure_map.R"))
-
-```
-
-\newpage
-
 ```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
@@
 
-source(normalizePath("../theory/figure_n_patch.R"))
+source(normalizePath("../theory/figure_n_patch_si.R"))
+n_patch_fig(p_dispersal = 0.01, sd_env_lon = 0.01, sd_env_source = 0.01)
 ```
@@
 \newpage
-
-```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
-Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals.
-Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
-See Figure 2 for details."}
-
-source(normalizePath("../theory/figure_p_branch.R"))
-```
-
-\newpage
-
-```{r, fig.height=6, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (left), $\\beta$ (middle), and $\\gamma$ diversity (right) in Hokkaido and Midwest regions.
-Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the linear regression models."}
-
-source(normalizePath("../empirical/figure_diversity.R"))
-```

### 2020-11-22 empirical/analysis_lm_bf.R
Edits: minor

@@ -1,14 +1,12 @@
 
 # setup -------------------------------------------------------------------
 
-  rm(list = ls(all.names = TRUE))
   pacman::p_load(tidyverse)
-  setwd(here::here("empirical"))
 
 # read data ---------------------------------------------------------------
   
-  dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
-  dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
+  dat_hkd <- read_csv(here::here("empirical/data_out/data_hkd.csv")) %>% mutate(region = "hokkaido")
+  dat_mw <- read_csv(here::here("empirical/data_out/data_mw.csv")) %>% mutate(region = "midwest")
   
   dat <- bind_rows(dat_hkd, dat_mw) %>% 
     rename(gamma = Estimator,

### 2020-11-22 theory/figure_n_patch_si.R

@@ -9,9 +9,9 @@
   dat <- read_csv(here::here("theory/result/result_sim2020-11-10.csv")) %>% 
     select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
-           p_dispersal == 0.1,
-           sd_env_source == 1,
-           sd_env_lon == 1) %>% 
+           p_dispersal == 0.01,
+           sd_env_source == 0.01,
+           sd_env_lon == 0.01) %>% 
     mutate(beta_div = gamma_div/alpha_div) %>% 
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
@@ -68,3 +68,4 @@
            fill = FALSE)
   
   print(g)
+  

### 2020-11-22 theory/figure_p_branch_si.R

@@ -9,7 +9,7 @@
   dat <- read_csv(here::here("theory/result/result_sim2020-11-10.csv")) %>% 
     select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
-           p_dispersal == 0.1,
+           p_dispersal == 0.01,
            sd_env_source == 1,
            sd_env_lon == 1) %>% 
     mutate(beta_div = gamma_div/alpha_div) %>% 

### 2020-12-24 empirical/data_merge_mw.R
Edits: data_merge_mw
check for CRS definition influence

@@ -16,10 +16,25 @@
   fishdata <- list.files(path = "data_org_mw", full.names = TRUE) %>%
     lapply(read_csv)
   
+  ## IA: wgs84; MI, WI, IL: NAD83
   d0 <- do.call(what = bind_rows, args = fishdata) %>% 
     st_as_sf(coords = c("Lon", "Lat"), crs = 4326) %>% 
     st_transform(crs = st_crs(watershed)$wkt) %>% 
     st_join(watershed)
+  
+  ## checking for CRS definition influence
+  #d0_ia <- do.call(what = bind_rows, args = fishdata) %>% 
+  #  filter(State == "IA") %>% 
+  #  st_as_sf(coords = c("Lon", "Lat"), crs = 4326)
+  #  
+  #d0_mwi <- do.call(what = bind_rows, args = fishdata) %>% 
+  #  filter(State %in% c("MN", "WI", "IL")) %>% 
+  #  st_as_sf(coords = c("Lon", "Lat"), crs = 4269) %>% 
+  #  st_transform(crs = 4326)
+  #  
+  #d0 <- bind_rows(d0_ia, d0_mwi) %>% 
+  #  st_transform(crs = st_crs(watershed)$wkt) %>% 
+  #  st_join(watershed)
   
   n_site_stat <- d0 %>%
     as_tibble() %>% 

### 2020-12-24 manuscript/manuscript.Rmd
misc

@@
   html_notebook: default
+  word_document: default
 abstract: |
@@
 In 1921, Arrhenius[@arrheniusSpeciesArea1921] formulated the SAR as a power-law $S = cA^z$ ($S$ is the number of species observed in a given geographic area $A$), an equation currently known as the Arrhenius species-area relationship.
-Since then, the spatial scaling of species richness has been observed in nearly all taxonomic group, although the underlying mechanisms are still hotly debated[@ben-hurDisentanglingMechanismsUnderlying2020].
+Since then, the spatial scaling of species richness has been observed in nearly all taxonomic groups[@triantisIslandSpeciesArea2012], although the underlying mechanisms are still hotly debated[@ben-hurDisentanglingMechanismsUnderlying2020].
 The SAR is ubiquitous because multiple mechanisms produce an apparently similar pattern.
-Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity[@kallimanisHowDoesHabitat2008], larger metacommunity size[@ben-hurDisentanglingMechanismsUnderlying2020], and/or enhanced colonization dynamics[@lososTheoryIslandBiogeography2009].
+Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity[@kallimanisHowDoesHabitat2008a], larger metacommunity size[@ben-hurDisentanglingMechanismsUnderlying2020;@hubbellUnifiedNeutralTheory2001], and/or enhanced colonization dynamics[@lososTheoryIslandBiogeography2009].
 Importantly, the SAR provides the foundation for global conservation efforts.
-For example, conservation ecologists have used the SAR estimates to design marine and terrestrial protected areas, which currently encompass more than ~ km² globally.
+For example, conservation ecologists have used the SAR estimates to design marine and terrestrial protected areas, which currently encompass more than 30 million km² globally.
 
-Many ecosystems, however, possess complex spatial structure that cannot be represented by area, a dimension referred to as the scale-invariant complexity[@rinaldoEvolutionSelectionRiver2014a; @rodriguez-iturbeFractalRiverBasins2001].
+Many ecosystems, however, possess complex spatial structure that cannot be represented by area - a dimension referred to as the scale-invariant complexity[@rinaldoEvolutionSelectionRiver2014; @rodriguez-iturbeFractalRiverBasins2001].
 Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few[@rodriguez-iturbeFractalRiverBasins2001].
-Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike.
-Even though the branching structure is independent of spatial scale, it forms a physical template that determines habitat diversity and dispersal corridors for living organisms[@grantLivingBranchesPopulation2007; @rinaldoRiverNetworksEcological2018].
-Limited, but accumulating evidence suggests that classical concepts cannot predict ecological dynamics driven by branching structure, and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@altermattDiversityRiverineMetacommunities2013; @carraraComplexInteractionDendritic2014; @carraraDendriticConnectivityControls2012; @teruiMetapopulationStabilityBranching2018].
+Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike[@rodriguez-iturbeFractalRiverBasins2001].
+Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms[@grantLivingBranchesPopulation2007; @rinaldoRiverNetworksEcological2018;@tonkinRoleDispersalRiver2018].
+Limited, but accumulating evidence suggests that classical concepts cannot predict ecological dynamics driven by branching structure[@faganConnectivityFragmentationExtinction2002; @grantUseMultipleDispersal2010; @teruiMetapopulationStabilityBranching2018], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@altermattDiversityRiverineMetacommunities2013; @carraraComplexInteractionDendritic2014; @carraraDendriticConnectivityControls2012; @teruiMetapopulationStabilityBranching2018].
 However, most research either has explored the consequences of branching complexity for local variation in species richness or relied on theoretical arguments with limited replicates of artificial branching networks.
 At present, we lack a comprehensive evaluation of how branching complexity, in combination with ecosystem size, scales biodiversity at the metacommunity level.
-Filling this knowledge gap may provide fundamental ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services.
+Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services.
 
 Here, we hypothesize that ecosystem size and complexity dictate biodiversity patterns in rivers, a prime example of complex branching ecosystems.
-In branching river networks, diverse streams recurrently join to form a larger, ecologically distinct channel.
+The recurrent merging of diverse streams and rivers produces larger, ecologically distinct channels, ultimately forming a fluvial network with fractal branching patterns[@rodriguez-iturbeFractalRiverBasins2001].
 As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a], should control the habitat heterogeneity of the ecosystem (habitat diversity per unit area).
@@
 Environmental values at the headwaters are drawn randomly from a normal distribution and propagates downstream with local environmental noise (i.e., the spatial autoregressive process with white noise).
-These values recurrently 'mix' at confluences considering the relative size of joining tributaries (see Methods).
+These environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see Methods).
 Therefore, our simulation resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
-We prepared `r n_scenario` sets of parameter combinations with varied ecological (dispersal and competition strength) and landscape scenarios (the environmental variation at headwaters and the degree of local environmental noise).
-Under each scenario, we simulated metacommunity dynamics in `r max(dat_sim$n_rep)` branching networks that have different ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`) to examine their effects on $\gamma$ diversity.
+We used `r n_scenario` sets of parameter combinations with varied ecological (dispersal and competition strength) and landscape scenarios (the environmental variation at headwaters and the degree of local environmental noise).
+Under each scenario, we simulated metacommunity dynamics in `r max(dat_sim$n_rep)` branching networks that have different ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`) to examine their effects on species diversity.
 
@@
 Dispersal processes, however, affected underlying mechanisms that produce the positive effects of ecosystem size and complexity on $\gamma$ diversity.
-We observed a greater contribution of $\beta$ diversity, which we defined as $\frac{\gamma}{\alpha}$, to increased $\gamma$ diversity in larger and more complex ecosystems when dispersal limitation exists (i.e., species travel short distances).
+We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation exists (i.e., species travel short distances).
 This pattern reflects significant spatial turnover of species composition over the branching network.
 In contrast, once the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
-This is understandable because increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects).
+The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects)[@thompsonProcessbasedMetacommunityFramework2020].
 These patterns were consistent across different levels of dispersal probabilities (**cite SI figure**).
-Our theory, therefore, highlights how the apparently similar patterns in $\gamma$ diversity emerges through different ecological pathways.
+The strength of competition decreased maximum levels of $\alpha$ diversity but did not change the functional forms of the scaling relationships with ecosystem properties (**Figures 2 and 3**).
+In summary, our theory highlights how the apparently similar patterns in $\gamma$ diversity emerges through different ecological pathways.
 
-Influences of ecosystem size and complexity, however, differed significantly in their dependence on landscape scenarios.
+Influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios.
 Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$).
-This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity.
+This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity[@hubbellUnifiedNeutralTheory2001].
 In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$).
-Under this scenario, having more branches may not contribute to the habitat diversity in the ecosystem because local environmental noise masks among-branch environmental differences.
+Under this scenario, having more branches may not contribute to the habitat diversity in the ecosystem because local environmental noise masks environmental differences between branches.
 Therefore, this landscape scenario decouples the intimate relationship between branching structure and habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
-This theoretical prediction may not apply to pristine to semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinctiveness in a variety of environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes.
-Instead, this result may be more relevant to severely altered landscapes where human activities compromise the environmental distinctiveness of each branch through flow regulations by dams and land use change.
-Hence, our theory, along with previous theoretical efforts, has important implications for riverine biodiversity conservation by pointing the crucial role of habitat diversity produced by branching structure[@holtRoleBranchingMaintenance2018].
+This theoretical prediction may not apply to pristine to semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes.
+Instead, it may be more relevant to severely altered landscapes where human disturbance compromises the environmental distinctiveness of each branch through, for example, flow regulations by dams.
+Hence, our theory has important implications for riverine biodiversity conservation by pointing the crucial role of habitat diversity produced by branching structure[@holtRoleBranchingMaintenance2018].
 
-Our theory provided important insights into how ecological communities are structured in branching networks; however, empirically testing the predictions is extremely difficult because it requires metacommunity-level replications, which are exceedingly rare.
+The proposed theory provided important insights into how ecological communities are structured in branching networks; however, empirically testing the predictions is extremely difficult because it requires metacommunity-level replications.
 To confront this logistical challenge, we compiled existing community data of fishes from a variety of sources and developed a unique large dataset that spans across two geographic regions: the Hokkaido island in Japan and the Midwest in the United States.
@@
 Individual watersheds, i.e., metacommunity replicates in our analysis, were considered as separated if they flow into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-We combined this dataset with geospatial information (annual mean temperature, annual cumulative precipitation, and percent forest) to account for potential influences of macro-scale drivers of species diversity.
+We combined this dataset with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, and percent forest) to examine potential influences of macro-scale drivers of species diversity.
 Using this dataset, we developed global and region-specific models for each of diversity measures ($\alpha$, $\beta$, and $\gamma$ diversity) to examine whether observed patterns are consistent across the two geographic regions.
@@
 Similarly, we found weak to moderate supports for the global models explaining observed patterns of $\alpha$ and $\beta$ diversity (Bayes factor: `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
-In both regions, $\beta$ diversity, rather than $\alpha$ diversity, responded significantly to ecosystem size and complexity.
-In our simulations, this pattern has emerged in the scenarios with dispersal limitation, which elegantly match the previous observations of stream fish movement.
-Direct (mark-recapture) and indirect observations (e.g., genotyping) recurrently revealed restricted movement of stream fish, typically limited to several tens to hundreds of meters in distance.
-Therefore, it is reasonable to observe the increased spatial turnover of species composition with increasing ecosystem size and complexity.
+In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity.
+In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly match the previous observations of stream fish movement.
+Direct (mark-recapture) and indirect observations (e.g., genotyping) recurrently revealed restricted movement of stream fish, typically limited to several tens to hundreds of meters in distance[@comteFishDispersalFlowing2018; @radingerPatternsPredictorsFish2014; @rodriguezRestrictedMovementStream2002].
+The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
 
-It is noteworthy that the effect of branching probability on $\gamma$ diversity was consistent across the study regions.
-The watersheds in the Midwest are severely altered by agriculture (median % agricultural land use: `r round(median(wsd_subset[[2]]$frac_agri)*100)`%) while the Hokkaido region is relatively intact (median % agricultural land use: `r round(median(wsd_subset[[1]]$frac_agri)*100)`%).
-If the land use change causes significant homogenization of in-stream habitat conditions among tributaries, theory predicts weakened effects of branching probability on $\gamma$ diversity.
-However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions and contribute to high spatial turnover of species composition over the landscape (i.e., high $\beta$ diversity).
-Indeed, $\beta$ diversity increased with increasing branching probability in both regions (**Figure 4**).
-It is conceivable that even in highly modified landscape, local geological and geomorphological differences, such as slope, aspect, and
-soil porosity, persist to support diversity of in-stream processes among tributaties.
+The consistent effect of branching probability on $\gamma$ diversity across the study regions is noteworthy because the watersheds in the Midwest are severely altered by agriculture (median % agricultural land use: `r round(median(wsd_subset[[2]]$frac_agri)*100)`% for Midwest and `r round(median(wsd_subset[[1]]$frac_agri)*100)`% for Hokkaido).
+If the intensive land use by humans causes significant homogenization of in-stream habitat conditions among tributaries, theory predicts weakened effects of branching probability on $\gamma$ diversity.
+However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions to support high spatial trunover of species composition.
+In support of this interpretation, $\beta$ diversity increased with increasing branching probability in both regions (**Figure 4**).
+It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, still persist in human-dominated landscapes to maintain diversity of in-stream processes among tributaties[@bendaNetworkDynamicsHypothesis2004].
 Although our analysis is correlative and cannot provide conclusive evidence, the finding is encouraging because branching complexity of river networks may serve as a natural defense system to human-induced environmental changes.
 
-There may be confounding factors that could not be incorporated in our statistical models.
-However, we are confident on our statistical inference for the following reason.
-The observed patterns were elegantly consistent with our theoretical predictions that are free from any confounding factors.
+There may be confounding factors that are not incorporated in our statistical models.
+However, we are confident on our statistical inference because the observed patterns were fairly consistent with our theoretical predictions that are free from any confounding effects.
 Further, our fitted models generally showed high R^2^ values ($\alpha$ diversity: `r round(summary(fit$alpha$model)$r.squared, 2)`; $\beta$ diversity, `r round(summary(fit$beta$model)$r.squared, 2)`; $\gamma$ diversity `r round(summary(fit$gamma$model)$r.squared, 2)`) with no signs of spatial autocorrelation in residuals.
@@
 
-While the prevailing evidence supports the scaling relationship between species diversity and ecosystem size, the importance of spatial complexity of ecosystems, especially branching structure, has not received the attention it deserves.
-Our results fill this knowledge gap by illuminating the dual regulation of riverine biodiversity by ecosystem size and complexity.
-
-The emerging complexity-diversity relationship points to several important avenues for improving riverine biodiversity conservation.
-First and foremost, there is now clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
-In rivers, the emerging technologies enabled us to estimate branching patterns across the globe, and there is ongoing efforts to refine global geospatial dataset.
-Such information may be used to identify areas that should be prioritized for conservation.
+The emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
+First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
+Human alterations, including flow regulation[@poffHomogenizationRegionalRiver2007], habitat fragmentation, and stream burial, may compromise or restrict access to the diverse habitats that complex branching networks may provide.
+Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human alterations.
 Second, the complexity perspective may provide viable options to reconcile conflicts between biodiversity conservation and societal needs.
 Although protected areas spearhead global conservation efforts, habitat preservation and restoration over large areas are often impractical because of conflicts with stakeholders.
-This is particularly true for riverine ecosystems, where numerous stakeholders are involved within a single watershed and enormous efforts are required to reach consensus.
-In such a scenario, small-scale conservation, such as restoration of connectivity to small tributaties, could still significantly enhance the 'realized' network complexity that organisms may experience, potentially supporting biodiversity at the metacommunity level.
-Hence, findings from this research offer an alternative pathway to design conservation strategies in spatially complex ecosystems.
+This is particularly true for riverine ecosystems, where numerous stakeholders are involved within a single watershed and enormous efforts are required to reach consensus[@palmerEcologicalRestorationStreams2014].
+In such a scenario, spatial planning of small-scale conservation, such as restoration of connectivity to small tributaties, may be critical to enhancing the 'realized' network complexity that organisms may experience.
+Our theoretical framework may be used to design spatial arrangement of small-scale conservation that improves ecological outcomes at the metacommunity level.
+
+While the prevailing evidence supports the importance of ecosystem size in scaling species diversity, ecosystem complexity - especially branching structure - has not received the attention it deserves.
+Ecosystems are inherently complex in its spatial structure, providing a physical template that creates a wide spectrum of niche opportunities for living organisms.
+Hence, our findings should be broadly applicable to many taxa and ecosystems.
+Generalization of the complexity perspective is a frontier for future research.
 
@@
 
-## Model description
+## Theoretical branching networks
 
-The metacommunity dynamics are described as a function of local community dynamics and dispersal[@thompsonProcessbasedMetacommunityFramework2020].
-Specifically, the realized number of individuals $N_{ix}(t + 1)$ (species $i$ at patch $x$ and time $t+1$) is given as:
+We depicted branching ecosystems as a spatial network of connected habitat patches.
+Habitat patches can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
+Two parameters determine geometric properties of simulated branching networks: the number of habitat patches $N_p$ (ecosystem size) and branching probability $P_b$ (ecosystem complexity).
+Each habitat patch is assigned to be a branching patch (including upstream terminals) with probability $P_b$ or non-branching patch with probability $1-P_b$.
+In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in a single branch $n_b$ is a realization of a random variable drawn from a geometric distribution $n_{b} \sim Ge(P_{b})$.
+This representation has two merits.
+First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution).
+Second, it preserves the fractal nature of branching patterns[@peckhamReformulationHortonLaws1999].
+
+The long-term average of abiotic environment $\mu_z$ at each habitat patch is characterized by two sources of variation: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
+We draw random values from a normal distribution with a mean of zero and SD of $\sigma_{h}$ and assigned them to headwater patches (i.e., the most upstream patches).
+These environmental values at headwaters propagate downstream through a spatial autoregressive process defined as:
+
+$$
+\mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k}
+$$
+
+where $\mu_{z,k}$ is the environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and SD of $\sigma_l$.
+The parameter $\rho$ can take values of $0-1$ with larger values indicating greater spatial autocorrelation.
+In this study, we set $\rho = 1$ to mimic strong spatial autocorrelation in rinverine environments.
+At confluences, we took a weighted mean of environmental values given the relative size of upstream contributing area of joining tributaries:
+
+$$
+\begin{align}
+\mu_{z,k} &= \omega(\rho \mu_{z,k+1}^R + \epsilon_{k}^R) + (1-\omega)(\rho \mu_{z,k+1}^L + \epsilon_{k}^L) \\
+\omega &= \frac{A_{k+1}^R}{A_{k+1}^R + A_{k+1}^L}
+\end{align}
+$$
+where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at patch $k$ (akin to upstream watershed area).
+With this expression, larger tributaties have a greater influence on the downstream environment, as observed in natural river networks[@bendaNetworkDynamicsHypothesis2004].
+
+## Metacommunity model
+We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al.[@thompsonProcessbasedMetacommunityFramework2020].
+In this framework, abiotic environmental conditions (density independent), intra- and interspecific competition (density dependent), and dispersal regulate the realized population growth of a species.
+Below, we describe details of our metacommunity model.
+
+The realized number of individuals $N_{ix}(t + 1)$ (species $i$ at patch $x$ and time $t+1$) is given as:
 
@@
 $$
-where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}$(t) the expected number of immigrants to patch $x$, and $E_{ix}$(t) the expected number of emigrants from patch $x$.
-Local community dynamics are simulated based on the Beverton-Holt model:
+where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$.
+The realized discrete number of individuals is drawn from a Poisson distribution to account for stochasticity in demographic and dispersal processes[@fronhoferClassicalMetapopulationDynamics2017; @thompsonProcessbasedMetacommunityFramework2020].
+Local community dynamics are simulated based on the Beverton-Holt equation:
 
 $$
-n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_j^S{\alpha_{ij}N_{jx}(t)}}
+n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}}
 $$
 
-where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, and $\alpha_{ij}$ the interaction coefficient between species $i$ and $j$.
-The parameter $\alpha_{ij}$ is the strength of interspecific competition relative to that of intraspecific competition (interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ > 1; intraspecific competition coefficient $\alpha_{ii}$ equals 1.0).
-The density-independent reproductive rate $r_{ix}(t)$ is affected by environments and determined by a Gaussian function:
+where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the interaction coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
+The parameter $\alpha_{ij}$ is expressed as the strength of interspecific competition relative to that of intraspecific competition such that interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ > 1 (intraspecific competition coefficient $\alpha_{ii} = 1$).
+The density-independent reproductive rate $r_{ix}(t)$ is affected by abiotic environments (non-consumable) and determined by the following Gaussian function:
 
@@
 where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche}$ the niche width of species $i$.
-The cost of having wider niche is expressed by multiplying $c$[@chaianunpornEvolutionaryResponsesClimate2015]:
+Species with wider niche (greater values of $\sigma_{niche}$) should always have greater competitive ability in the absence of the cost of wide niche.
+Therefore, we introduced the cost of wide niche by multiplying $c$[@chaianunpornEvolutionaryResponsesClimate2015]:
 
@@
 
-Smaller values of $\nu$ imply greater costs of having wider niche (i.e., decreased maximum reproductive rate). There is no cost if $\nu$ approaches infinity.
+Smaller values of $\nu$ imply greater costs of having wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$.
 
-The environmental value $z_x(t)$, which may vary spatially and temporarily, is assumed to follow a multivariate normal distribution:
-
-$$
-z_{x}(t) \sim MVN(\mu_z, \Omega_z)
-$$
-$\mu_z$ is the vector of mean environmental conditions of patches and $\Omega_z$ is the variance-covariance matrix. Spatial autocorrelation is considered by describing the off-diagonal elements as:
+The environmental value at patch $x$ and time $t$, $z_x(t)$, is assumed to follow a multivariate normal distribution as $z_{x}(t) \sim MVN(\mu_z, \Omega_z)$.
+$\mu_z$ is the vector of mean environmental conditions of patches and $\Omega_z$ is the variance-covariance matrix.
+Spatial autocorrelation in temporal environmental dynamics is considered by expressing the off-diagonal elements as:
 
@@
 $$
-where $\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (randomly generated or specified by argument distance_matrix).
-The parameter $\phi$ determines distance decay of environmental correlates.
 
-The expected number of emigrants at time $t$, $E_{ix}(t)$, is the product of dispersal probability $p_d$ and $n_{ix}(t)$.
-The immigration probability at patch $x$, $\xi_{ix}$, is calculated given the structural connectivity of patch $x$, in which the model assumes the exponential decay of successful immigration with the increasing separation distance between habitat patches:
+where $\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$.
+The parameter $\phi$ determines the degree of distance decay of environmental correlates.
+
+The expected number of emigrants at time $t$ is the product of dispersal probability $p_d$ and $n_{ix}(t)$: $E_{ix}(t) = p_{d}n_{ix}(t)$.
+The immigration probability at patch $x$ for species $i$, $\xi_{ix}(t)$, is calculated using the following equation that accounts for separation distance among habitat patches and dispersal capability of a species:
 
@@
 where $d_{xy}$ is the separation distance between patch $x$ and $y$.
-The parameter $\theta$ dictates the dispersal distance of species ($\theta^{-1}$ corresponds to the expected dispersal distance) and is assumed to be constant across species.
-The expected number of immigrants is calculated as:
+The parameter $\theta$ regulates the dispersal distance of a species that follows an exponential distribution ($\theta^{-1}$ corresponds to the expected dispersal distance).
+The expected number of immigrants is calculated as $I_{ix}(t) = \xi_{ix}(t)\sum_x^{N_p} E_{ix}$.
 
-$$
-I_{ix}(t) = \xi_{ix}(t)\sum E_{ix}
-$$
+## Simulation
+We used `r n_scenario` sets of parameter combinations to produce different landscape (four patterns of habitat heterogeneity) and ecological scenarios (eight patterns of dispersal and competition).
+To create landscape scenarios with different patterns of habitat heterogeneity, we varied environmental variation at headwaters ($\sigma_h$) and the degree of local environmental noise ($\sigma_l$) separately.
+Larger values of $\sigma_h$ and/or $\sigma_l$ produce greater variation in environmental conditions among habitat patches.
+We used two values for each of the SD parameters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)` and $\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), resulting in four sets of parameter combinations.
+When $\sigma_h > \sigma_l$, having more tributaries in a network exhibits important effects on overall habitat diversity as branching is the primary source of environmental variation.
+When $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on overall habitat diversity in a network.
+For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`).
+This setup results in eight ecological scenarios with different levels of dispersal and competition.
+
+We used fixed values for the following parameters: maximum reproductive number ($r_{0,i} =$ 4), niche cost ($\nu =$ `r unique(dat_sim$niche_cost)`), the degree of temporal fluctuation in abiotic environments ($\sigma_z =$ `r unique(dat_sim$sd_env)`), and the degree of spatial autocorrelation in temporal environmental dynamics ($\phi =$ `r unique(dat_sim$phi)`).
+
+## Empirical data
+We compiled fish data at two biogeographic regions: Hokkaido island, Japan and Midwest, US.
+For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish, monitoring data at protected watersheds, and primary data collected by the authors.
+Collectively, these fish data encompass more than 7000 sites and covers the entire Hokkaido island.
+For the Midwest, we assembled fish community data collected by XXX.
+
+We selected data based on the following criterion. First, we reviewed
 

### 2020-12-24 manuscript/manuscript.tex
misc

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Ecosystem size and complexity dictate riverine biodiversity},
  pdfauthor={Akira Terui; Seoghyn Kim; Christine L. Dolph},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {}%
  {\par}

\title{Ecosystem size and complexity dictate riverine biodiversity}
\author{Akira Terui\footnote{Department of Biology, University of North
  Carolina at Greensboro} \and Seoghyn
Kim\footnotemark[1] \and Christine L. Dolph\footnote{Department of
  Ecology, Evolution and Behavior}}
\date{}

\begin{document}
\maketitle
\begin{abstract}
\textbar This is the abstract.
\end{abstract}

Ecologists have long sought to understand the general drivers of
biodiversity. One of the most robust empirical generalizations in
ecology is the positive relationship between species richness and area,
i.e., the species-area relationship (the SAR)\textsuperscript{1}. In
1921, Arrhenius\textsuperscript{2} formulated the SAR as a power-law
\(S = cA^z\) (\(S\) is the number of species observed in a given
geographic area \(A\)), an equation currently known as the Arrhenius
species-area relationship. Since then, the spatial scaling of species
richness has been observed in nearly all taxonomic
group\textsuperscript{3}, although the underlying mechanisms are still
hotly debated\textsuperscript{4}. The SAR is ubiquitous because multiple
mechanisms produce an apparently similar pattern. Larger ecosystems
typically support more diverse metacommunities due to increased habitat
diversity\textsuperscript{5}, larger metacommunity
size\textsuperscript{4,6}, and/or enhanced colonization
dynamics\textsuperscript{7}. Importantly, the SAR provides the
foundation for global conservation efforts. For example, conservation
ecologists have used the SAR estimates to design marine and terrestrial
protected areas, which currently encompass more than XXX km² globally.

Many ecosystems, however, possess complex spatial structure that cannot
be represented by area - a dimension referred to as the scale-invariant
complexity\textsuperscript{8,9}. Such complexity is evident in branching
ecosystems, including rivers, trees, and mountain ranges, to name just a
few\textsuperscript{9}. Geomorphic or biological processes generate a
pronounced self-similarity in complex branching patterns such that the
part and the whole look alike\textsuperscript{9}. Even though the
branching structure is independent of spatial scale, it forms a physical
template that dictates habitat diversity and dispersal corridors for
living organisms\textsuperscript{10--12}. Limited, but accumulating
evidence suggests that classical concepts cannot predict ecological
dynamics driven by branching structure\textsuperscript{13--15}, and this
recognition has led to recent developments of spatial theories devoted
to complex branching ecosystems\textsuperscript{15--18}. However, most
research either has explored the consequences of branching complexity
for local variation in species richness or relied on theoretical
arguments with limited replicates of artificial branching networks. At
present, we lack a comprehensive evaluation of how branching complexity,
in combination with ecosystem size, scales biodiversity at the
metacommunity level. Filling this knowledge gap may provide common
ground for achieving successful conservation in spatially complex
ecosystems, where the accelerated species loss threatens the delivery of
ecosystem services.

Here, we hypothesize that ecosystem size and complexity dictate
biodiversity patterns in rivers, a prime example of complex branching
ecosystems. The recurrent merging of diverse streams and rivers produces
larger, ecologically distinct channels, ultimately forming a fluvial
network with fractal branching patterns. As such, the complexity of
branching structure, which we define here as the probability of
branching per unit river distance,\textsuperscript{15,19} should control
the habitat heterogeneity of the ecosystem (habitat diversity per unit
area). Meanwhile, ecosystem size (watershed area) should determine the
metacommunity size and total habitat diversity (area x heterogeneity).
We predict that ecosystem size and branching complexity increase
\(\gamma\) diversity by enhancing either \(\alpha\) and/or \(\beta\)
diversity under different ecological scenarios. The present study
combines theory and statistical analysis of extensive community data to
provide crucial insights into how ecological communities are structured
in complex branching networks.

First, we theoretically analyzed the influences of ecosystem size and
branching complexity on \(\gamma\) diversity. We constructed a general
simulation model of metacommunity dynamics,\textsuperscript{20} in which
50 competing species disperse and spatially interact in a random
branching network. Simulated species with different niche in abiotic
conditions (optimum and width) compete for resources with varied
strengths. For simplicity, other ecological traits, such as dispersal
probability, are assumed to be identical among species. Here, we
depicted branching ecosystems as a spatial network of connected habitat
patches (or a discretized river section; see \textbf{Figure 1}) where
mean environmental conditions at each habitat patch are determined by
two factors: (1) the headwater environments (the most upstream habitat
patch) and (2) local environmental noise. Environmental values at the
headwaters are drawn randomly from a normal distribution and propagates
downstream with local environmental noise (i.e., the spatial
autoregressive process with white noise). These values recurrently `mix'
at confluences considering the relative size of joining tributaries (see
Methods). Therefore, our simulation resembles natural processes of how
branching river networks create diverse habitats in a metacommunity. We
used 32 sets of parameter combinations with varied ecological (dispersal
and competition strength) and landscape scenarios (the environmental
variation at headwaters and the degree of local environmental noise).
Under each scenario, we simulated metacommunity dynamics in 1000
branching networks that have different ecosystem size (the number of
habitat patches: 10 to 150) and complexity (branching probability: 0.01
to 0.99) to examine their effects on species diversity.

Our theoretical analysis yielded results consistent with our prediction.
Ecosystem size and complexity both increased \(\gamma\) diversity under
a realistic landscape scenario (\textbf{Figures 2 and 3}), where the
environmental variation at headwaters (\(\sigma_h\)) is greater than the
degree of local environmental noise
(\(\sigma_l\)).\textsuperscript{15,21} The relationships had a
characteristic of power-law (i.e., linear in a log-log scale) and were
consistent under various ecological scenarios. The strength of
competition and dispersal processes (dispersal distance and probability)
did not change the form of the relationships between \(\gamma\)
diversity and ecosystem properties. Hence, the ecosystem size and
complexity are both expected to increase \(\gamma\) diversity regardless
of ecological scenarios.

Dispersal processes, however, affected underlying mechanisms that
produce the positive effects of ecosystem size and complexity on
\(\gamma\) diversity. We observed a greater contribution of \(\beta\)
diversity (defined as \(\frac{\gamma}{\alpha}\)) to increased \(\gamma\)
diversity when dispersal limitation exists (i.e., species travel short
distances). This pattern reflects significant spatial turnover of
species composition over the branching network. In contrast, once the
dispersal limitation was relaxed (species travel long distances), a
clear increase in \(\alpha\) diversity underpinned the positive
relationships between \(\gamma\) diversity and ecosystem properties. The
results agree with previous predictions that increased dispersal
homogenizes community composition while enhancing local diversity
through increased immigrants from suitable habitat patches (i.e., mass
effects). These patterns were consistent across different levels of
dispersal probabilities (\textbf{cite SI figure}). The strength of
competition decreased maximum levels of \(\alpha\) diversity but did not
change the functional forms of the scaling relationships with ecosystem
properties (\textbf{Figures 2 and 3}). In summary, our theory highlights
how the apparently similar patterns in \(\gamma\) diversity emerges
through different ecological pathways.

Influences of ecosystem size and complexity differed significantly in
their dependence on landscape scenarios. Ecosystem size had positive
effects on \(\gamma\) diversity regardless of landscape scenarios,
although the slopes were steeper with greater environmental variation
(higher \(\sigma_h\) and/or \(\sigma_l\)). This result is attributable
to the fact that larger ecosystems can hold more individuals in a
metacommunity\textsuperscript{6}. In contrast, we observed limited or no
influences of branching complexity when local environmental noise was
equal to or exceeded environmental variation at headwaters
(\(\sigma_l \ge \sigma_h\)). Under this scenario, having more branches
may not contribute to the habitat diversity in the ecosystem because
local environmental noise masks environmental differences between
branches. Therefore, this landscape scenario decouples the intimate
relationship between branching structure and habitat diversity, thereby
eliminating the positive effect of branching complexity on \(\gamma\)
diversity. This theoretical prediction may not apply to pristine to
semi-natural river networks where individual streams with diverse
geological and/or climatic backgrounds show distinct environmental
conditions, including water temperature, water chemistry, substrate, and
flow/sediment regimes. Instead, it may be more relevant to severely
altered landscapes where human disturbance compromises the environmental
distinctiveness of each branch through, for example, flow regulations by
dams. Hence, our theory has important implications for riverine
biodiversity conservation by pointing the crucial role of habitat
diversity produced by branching structure\textsuperscript{22}.

The proposed theory provided important insights into how ecological
communities are structured in branching networks; however, empirically
testing the predictions is extremely difficult because it requires
metacommunity-level replications. To confront this logistical challenge,
we compiled existing community data of fishes from a variety of sources
and developed a unique large dataset that spans across two geographic
regions: the Hokkaido island in Japan and the Midwest in the United
States. These regions are located in comparable ranges of latitude but
support distinct fish communities. Therefore, this dataset provides an
excellent opportunity to examine the generality of our theoretical
predictions. After careful data selection, we estimated \(\alpha\),
\(\beta\), and \(\gamma\) diversity (asymptotic species richness;
Methods) at 181 watersheds (60 in Hokkaido and 121 in Midwest), each of
which comprised \(\ge\) 10 sites of presence-absence fish community data
(a total of 6608 sites). Individual watersheds, i.e., metacommunity
replicates in our analysis, were considered as separated if they flow
into one of the following: the ocean, a large lake (\(\ge\) 10 km² in
the areal area) or a large river that may represent lentic habitats
(\(\ge\) 5000 km² in the watershed area). We combined this dataset with
geospatial information (watershed area, branching probability, annual
mean temperature, annual cumulative precipitation, and percent forest)
to examine potential influences of macro-scale drivers of species
diversity. Using this dataset, we developed global and region-specific
models for each of diversity measures (\(\alpha\), \(\beta\), and
\(\gamma\) diversity) to examine whether observed patterns are
consistent across the two geographic regions. In the global model, we
assumed that effects of ecosystem size (watershed area) and complexity
(branching probability) are constant across the two regions (i.e., fixed
slopes). Meanwhile, the region-specific model assumes region-specific
slopes of ecosystem size and complexity by including interaction terms
with the dummy binary variable of region (Hokkaido = 0; Midwest = 1). We
compared the performance of these competing models using the Bayes
factor, a measure of the strength of evidence in favor of one model over
the alternative.

Despite the substantial difference in fish fauna between the study
regions, the estimated Bayes factor in favor of the global model
explaining \(\gamma\) diversity was 159.7; this result strongly supports
the consistent effects of ecosystem size and complexity on \(\gamma\)
diversity across the two biogeographic regions. Further, we found
patterns consistent with our theoretical predictions. The estimated
\(\gamma\) diversity increased with increasing watershed area (ecosystem
size) and branching probability (ecosystem complexity) across
watersheds. These effects remained significant even after controlling
for the potential influences of other environmental factors
(precipitation, temperature, and land use). Overall, our statistical
analysis provides strong empirical evidence that ecosystem size and
complexity jointly, but independently, scale riverine biodiversity at
the metacommunity level.

Similarly, we found weak to moderate supports for the global models
explaining observed patterns of \(\alpha\) and \(\beta\) diversity
(Bayes factor: 1.8 and 9.6, respectively). In both regions, \(\beta\)
diversity responded significantly to ecosystem size and complexity. In
our simulations, this pattern has emerged under the scenarios with
dispersal limitation, which elegantly match the previous observations of
stream fish movement. Direct (mark-recapture) and indirect observations
(e.g., genotyping) recurrently revealed restricted movement of stream
fish, typically limited to several tens to hundreds of meters in
distance\textsuperscript{23--25}. The reciprocal agreement of
theoretical and empirical patterns provides indirect but convincing
evidence that dispersal limitation plays a key role in driving the
associations between \(\gamma\) diversity and ecosystem properties in
rivers.

The consistent effect of branching probability on \(\gamma\) diversity
across the study regions is noteworthy because the watersheds in the
Midwest are severely altered by agriculture (median \% agricultural land
use: 66\% for Midwest and 2\% for Hokkaido). If the intensive land use
by humans causes significant homogenization of in-stream habitat
conditions among tributaries, theory predicts weakened effects of
branching probability on \(\gamma\) diversity. However, \(\gamma\)
diversity increased significantly with increasing branching probability
in this highly modified landscape, suggesting that tributaries still
sustain unique environmental conditions to support high spatial trunover
of species composition. In support of this interpretation, \(\beta\)
diversity increased with increasing branching probability in both
regions (\textbf{Figure 4}). It is conceivable that local geological and
geomorphological differences, such as slope, aspect, and soil porosity,
still persist in human-dominated landscapes to maintain diversity of
in-stream processes among tributaties\textsuperscript{26}. Although our
analysis is correlative and cannot provide conclusive evidence, the
finding is encouraging because branching complexity of river networks
may serve as a natural defense system to human-induced environmental
changes.

There may be confounding factors that are not incorporated in our
statistical models. However, we are confident on our statistical
inference because the observed patterns were fairly consistent with our
theoretical predictions that are free from any confounding effects.
Further, our fitted models generally showed high R\textsuperscript{2}
values (\(\alpha\) diversity: 0.8; \(\beta\) diversity, 0.27; \(\gamma\)
diversity 0.77) with no signs of spatial autocorrelation in residuals.
Therefore, it is very unlikely that our results were driven by spurious
correlations.

The emerging complexity-diversity relationship points to several
important avenues for riverine biodiversity conservation. First and
foremost, there is now a clear need to explicitly consider the dimension
of ecosystem complexity to achieve successful conservation. Human
alterations, including flow regulation\textsuperscript{27}, habitat
fragmentation, and stream burial, may compromise or restrict access to
the diverse habitats that complex branching networks may provide. Hence,
it is imperative to recognize the role of branching complexity and
minimize the homogenizing effects of human alterations. Second, the
complexity perspective may provide viable options to reconcile conflicts
between biodiversity conservation and societal needs. Although protected
areas spearhead global conservation efforts, habitat preservation and
restoration over large areas are often impractical because of conflicts
with stakeholders. This is particularly true for riverine ecosystems,
where numerous stakeholders are involved within a single watershed and
enormous efforts are required to reach consensus\textsuperscript{28}. In
such a scenario, spatial planning of small-scale conservation, such as
restoration of connectivity to small tributaties, may be critical to
enhancing the `realized' network complexity that organisms may
experience. Our theoretical framework may be used to design spatial
arrangement of small-scale conservation that improves ecological
outcomes at the metacommunity level.

While the prevailing evidence supports the importance of ecosystem size
in scaling species diversity, ecosystem complexity - especially
branching structure - has not received the attention it deserves.
Ecosystems are inherently complex in its spatial structure, providing a
physical template that creates a wide spectrum of niche opportunities
for living organisms. Hence, our findings should be broadly applicable
to many taxa and ecosystems, and robust generalization of this
complexity perspective is a frontier for future research.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{theoretical-branching-networks}{%
\subsection{Theoretical branching
networks}\label{theoretical-branching-networks}}

We depicted branching ecosystems as a spatial network of connected
habitat patches. Habitat patches can be either non-branching or
branching river sections with a unit length \(l\), which defines the
scale of local species interactions. Two parameters determine geometric
properties of simulated branching networks: the number of habitat
patches \(N_p\) (ecosystem size) and branching probability \(P_b\)
(ecosystem complexity). Each habitat patch is assigned to be a branching
patch (including upstream terminals) with probability \(P_b\) or
non-branching patch with probability \(1-P_b\). In this framework, an
individual branch is a consecutive series of non-branching patches
terminated at a branching patch; therefore, the number of habitat
patches in a single branch \(n_b\) is a realization of a random variable
drawn from a geometric distribution \(n_{b} \sim Ge(P_{b})\). This
representation has two merits. First, it reflects observed patterns of
branch length distribution, which is known to follow an exponential
distribution (a continuous version of a geometric distribution). Second,
it preserves the fractal nature of branching patterns that is intimately
linked to branching probability. There are other metrics to simulate
fluvial networks; however, our framework is most appropriate in this
study because it allows us to directly test the relationship between
biodiversity patterns and ecosystem properties (ecosystem size and
complexity).

The long-term average of abiotic environment \(\mu_z\) at each habitat
patch is characterized by two sources of variation: environmental
variation at headwaters (\(\sigma_h\)) and local environmental noise
(\(\sigma_l\)). We draw random values from a normal distribution with a
mean of zero and SD of \(\sigma_{h}\) and assigned them to headwater
patches (i.e., the most upstream patches). These environmental values at
headwaters propagate downstream through a spatial autoregressive process
defined as:

\[
\mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k}
\]

where \(\mu_{z,k}\) is the environmental value at longitudinal position
\(k\) (\(k\) is the network distance from the outlet patch; \(k = 1\) at
the outlet), \(\rho\) is the strength of spatial autocorrelation and
\(\epsilon_k\) is the local environmental noise that follows a normal
distribution with a mean of zero and SD of \(\sigma_l\). The parameter
\(\rho\) can take values of \(0-1\) with larger values indicating
greater spatial autocorrelation. In this study, we set \(\rho = 1\) to
mimic strong spatial autocorrelation in rinverine environments. At
confluences, we took a weighted mean of environmental values given the
relative size of upstream contributing area of joining tributaries:

\[
\begin{align}
\mu_{z,k} &= \omega(\rho \mu_{z,k+1}^R + \epsilon_{k}^R) + (1-\omega)(\rho \mu_{z,k+1}^L + \epsilon_{k}^L) \\
\omega &= \frac{A_{k+1}^R}{A_{k+1}^R + A_{k+1}^L}
\end{align}
\] where \(R\) and \(L\) denote ``right'' and ``left'' branches,
respectively, and \(A_k\) is the number of upstream habitat patches at
patch \(k\). With this expression, larger tributaties have a greater
influence on the downstream environment, as observed in natural river
networks\textsuperscript{26}.

\hypertarget{metacommunity-model}{%
\subsection{Metacommunity model}\label{metacommunity-model}}

We simulated metacommunity dynamics in simulated branching river
networks. The metacommunity dynamics are described as a function of
local community dynamics and dispersal, following Thompson et
al.\textsuperscript{20}. Specifically, the realized number of
individuals \(N_{ix}(t + 1)\) (species \(i\) at patch \(x\) and time
\(t+1\)) is given as:

\[
N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
\] where \(n_{ix}(t)\) is the expected number of individuals given the
local community dynamics at time \(t\), \(I_{ix}(t)\) the expected
number of immigrants to patch \(x\), and \(E_{ix}(t)\) the expected
number of emigrants from patch \(x\). The realized discrete number of
individuals is drawn from a Poisson distribution to account for
stochasticity in demographic and dispersal processes. Local community
dynamics are simulated based on the Beverton-Holt equation:

\[
n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}}
\]

where \(r_{ix}(t)\) is the reproductive rate of species \(i\) given the
environmental condition at patch \(x\) and time \(t\), \(r_{0,i}\) the
maximum reproductive rate of species \(i\), \(K_{x}\) the carrying
capacity at patch \(x\), \(\alpha_{ij}\) the interaction coefficient
between species \(i\) and \(j\), and \(S\) the number of species in a
metacommunity. The parameter \(\alpha_{ij}\) was expressed as the
strength of interspecific competition relative to that of intraspecific
competition such that interspecific competition is greater than
intraspecific competition if \(\alpha_{ij}\) \textgreater{} 1
(intraspecific competition coefficient \(\alpha_{ii} = 1\)). The
density-independent reproductive rate \(r_{ix}(t)\) is affected by
abiotic environments (non-consumable) and determined by the following
Gaussian function:

\[
r_{ix}(t) = cr_{0,i}~exp[{-\frac{(\mu_i-z_x(t))^2}{2\sigma^2_{niche,i}}}]
\] where \(\mu_i\) is the optimal environmental value for species \(i\),
\(z_x(t)\) the environmental value at patch \(x\) and time \(t\), and
\(\sigma_{niche}\) the niche width of species \(i\). The cost of having
wider niche is expressed by multiplying \(c\)\textsuperscript{29}:

\[
c = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
\]

Smaller values of \(\nu\) imply greater costs of having wider niche
(i.e., decreased maximum reproductive rate). There is no cost if \(\nu\)
approaches infinity.

The environmental value \(z_x(t)\) is assumed to follow a multivariate
normal distribution as \(z_{x}(t) \sim MVN(\mu_z, \Omega_z)\). \(\mu_z\)
is the vector of mean environmental conditions of patches and
\(\Omega_z\) is the variance-covariance matrix. Spatial autocorrelation
in temporal environmental dynamics is considered by expressing the
off-diagonal elements as:

\[
\Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy})
\]

where \(\Omega_{xy}\) denotes the temporal covariance of environmental
conditions between patch \(x\) and \(y\), which is assumed to decay
exponentially with increasing distance between the patches \(d_{xy}\).
The parameter \(\phi\) determines the degree of distance decay of
environmental correlates.

The expected number of emigrants at time \(t\) is the product of
dispersal probability \(p_d\) and \(n_{ix}(t)\):
\(E_{ix}(t) = p_{d}n_{ix}(t)\). The immigration probability at patch
\(x\) for species \(i\), \(\xi_{ix}(t)\), is calculated using the
following equation that accounts for separation distance among habitat
patches and dispersal capability of species:

\[
\xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}
\] where \(d_{xy}\) is the separation distance between patch \(x\) and
\(y\). The parameter \(\theta\) regulates the dispersal distance of
species that follows an exponential distribution (\(\theta^{-1}\)
corresponds to the expected dispersal distance). The expected number of
immigrants is calculated as
\(I_{ix}(t) = \xi_{ix}(t)\sum_x^{N_p} E_{ix}\).

\hypertarget{simulation}{%
\subsection{Simulation}\label{simulation}}

We used 32 sets of parameter combinations to produce different landscape
(four patterns of environmental heterogeneity) and ecological scenarios
(eight patterns of dispersal and competition). To create landscape
scenarios with different patterns of environmental heterogeneity, we
varied environmental variation at headwaters (\(\sigma_h\)) and the
degree of local environmental noise (\(\sigma_l\)) separately. Larger
values of \(\sigma_h\) and/or \(\sigma_l\) produce greater variation in
environmental conditions among habitat patches. We used two values for
each of the SD parameters (\(\sigma_h =\) 0.01, 1 and \(\sigma_l =\)
0.01, 1), resulting in four sets of parameter combinations. When
\(\sigma_h > \sigma_l\), having more tributaries in a network exhibits
important effects on environmental heterogeneity as branching is the
primary source of environmental variation. When
\(\sigma_h \le \sigma_l\), local environmental noise masks environmental
variation among tributaries, leading to minimal influences of branching
on environmental heterogeneity in a network. For ecological scenarios,
we varied three ecological parameters that are relevent for dispersal
and interspecific competition: dispersal distance (\(\theta =\) 0.1, 1),
dispersal probability (\(p_d =\) 0.01, 0.1), and the maximum value of
competition coefficients (\(\alpha_{max} =\) 0.75, 1.5). This results in
eight ecological scenarios with different levels of dispersal and
competition.

We used fixed values for the following parameters: maximum reproductive
number (\(r_{0,i} =\) 4), niche cost (\(\nu =\) 1), the degree of
temporal fluctuation in abiotic environments (\(\sigma_z =\) 0.1), and
the degree of spatial autocorrelation in temporal environmental dynamics
(\(\phi =\) 0.05).

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-lomolinoEcologyMostGeneral2000a}{}%
1. Lomolino, M. V. Ecology's Most General, Yet Protean Pattern: The
Species-Area Relationship. \emph{Journal of Biogeography} \textbf{27},
17--26 (2000).

\leavevmode\hypertarget{ref-arrheniusSpeciesArea1921}{}%
2. Arrhenius, O. Species and Area. \emph{Journal of Ecology} \textbf{9},
95--99 (1921).

\leavevmode\hypertarget{ref-triantisIslandSpeciesArea2012}{}%
3. Triantis, K. A., Guilhaumon, F. \& Whittaker, R. J. The island
speciesArea relationship: Biology and statistics. \emph{Journal of
Biogeography} \textbf{39}, 215--231 (2012).

\leavevmode\hypertarget{ref-ben-hurDisentanglingMechanismsUnderlying2020}{}%
4. Ben-Hur, E. \& Kadmon, R. Disentangling the mechanisms underlying the
speciesArea relationship: A mesocosm experiment with annual plants.
\emph{Journal of Ecology} (2020).

\leavevmode\hypertarget{ref-kallimanisHowDoesHabitat2008a}{}%
5. Kallimanis, A. S. \emph{et al.} How does habitat diversity affect the
speciesArea relationship? \emph{Global Ecology and Biogeography}
\textbf{17}, 532--538 (2008).

\leavevmode\hypertarget{ref-hubbellUnifiedNeutralTheory2001}{}%
6. Hubbell, S. P. \emph{The Unified Neutral Theory of Biodiversity and
Biogeography}. (Princeton University Press, 2001).

\leavevmode\hypertarget{ref-lososTheoryIslandBiogeography2009}{}%
7. Losos, J. B. \& Ricklefs, R. E. \emph{The theory of island
biogeography revisited}. (Princeton University Press, 2009).

\leavevmode\hypertarget{ref-rinaldoEvolutionSelectionRiver2014}{}%
8. Rinaldo, A., Rigon, R., Banavar, J. R., Maritan, A. \&
Rodriguez-Iturbe, I. Evolution and selection of river networks: Statics,
dynamics, and complexity. \emph{Proceedings of the National Academy of
Sciences} \textbf{111}, 2417--2424 (2014).

\leavevmode\hypertarget{ref-rodriguez-iturbeFractalRiverBasins2001}{}%
9. Rodríguez-Iturbe, I. \& Rinaldo, A. \emph{Fractal river basins:
Chance and self-organization}. (Cambridge University Press, 2001).

\leavevmode\hypertarget{ref-grantLivingBranchesPopulation2007}{}%
10. Grant, E. H. C., Lowe, W. H. \& Fagan, W. F. Living in the branches:
Population dynamics and ecological processes in dendritic networks.
\emph{Ecology Letters} \textbf{10}, 165--175 (2007).

\leavevmode\hypertarget{ref-rinaldoRiverNetworksEcological2018}{}%
11. Rinaldo, A., Gatto, M. \& Rodriguez-Iturbe, I. River networks as
ecological corridors: A coherent ecohydrological perspective.
\emph{Advances in Water Resources} \textbf{112}, 27--58.

\leavevmode\hypertarget{ref-tonkinRoleDispersalRiver2018}{}%
12. Tonkin, J. D. \emph{et al.} The role of dispersal in river network
metacommunities: Patterns, processes, and pathways. \emph{Freshwater
Biology} \textbf{63}, 141--163 (2018).

\leavevmode\hypertarget{ref-faganConnectivityFragmentationExtinction2002}{}%
13. Fagan, W. F. Connectivity, fragmentation, and extinction risk in
dendritic metapopulations. \emph{Ecology} \textbf{83}, 3243--3249
(2002).

\leavevmode\hypertarget{ref-grantUseMultipleDispersal2010}{}%
14. Grant, E. H. C., Nichols, J. D., Lowe, W. H. \& Fagan, W. F. Use of
multiple dispersal pathways facilitates amphibian persistence in stream
networks. \emph{Proceedings of the National Academy of Sciences}
\textbf{107}, 6936--6940 (2010).

\leavevmode\hypertarget{ref-teruiMetapopulationStabilityBranching2018}{}%
15. Terui, A. \emph{et al.} Metapopulation stability in branching river
networks. \emph{Proceedings of the National Academy of Sciences}
\textbf{115}, E5963--E5969 (2018).

\leavevmode\hypertarget{ref-altermattDiversityRiverineMetacommunities2013}{}%
16. Altermatt, F. Diversity in riverine metacommunities: A network
perspective. \emph{Aquatic Ecology} \textbf{47}, 365--377 (2013).

\leavevmode\hypertarget{ref-carraraComplexInteractionDendritic2014}{}%
17. Carrara, F., Rinaldo, A., Giometto, A. \& Altermatt, F. Complex
interaction of dendritic connectivity and hierarchical patch size on
biodiversity in river-like landscapes. \emph{American Naturalist}
\textbf{183}, 13--25 (2014).

\leavevmode\hypertarget{ref-carraraDendriticConnectivityControls2012}{}%
18. Carrara, F., Altermatt, F., Rodriguez-Iturbe, I. \& Rinaldo, A.
Dendritic connectivity controls biodiversity patterns in experimental
metacommunities. \emph{Proceedings of the National Academy of Sciences}
\textbf{109}, 5761--5766 (2012).

\leavevmode\hypertarget{ref-yeakelSynchronisationStabilityRiver2014a}{}%
19. Yeakel, J. D., Moore, J. W., Guimarães, P. R. \& Aguiar, M. A. M.
de. Synchronisation and stability in river metapopulation networks.
\emph{Ecology Letters} \textbf{17}, 273--283 (2014).

\leavevmode\hypertarget{ref-thompsonProcessbasedMetacommunityFramework2020}{}%
20. Thompson, P. L. \emph{et al.} A process-based metacommunity
framework linking local and regional scale community ecology.
\emph{Ecology Letters} (2020)
doi:\href{https://doi.org/10.1111/ele.13568}{10.1111/ele.13568}.

\leavevmode\hypertarget{ref-petersonModellingDendriticEcological2013}{}%
21. Peterson, E. E. \emph{et al.} Modelling dendritic ecological
networks in space: An integrated network perspective. \emph{Ecology
Letters} \textbf{16}, 707--719 (2013).

\leavevmode\hypertarget{ref-holtRoleBranchingMaintenance2018}{}%
22. Holt, G. \& Chesson, P. The role of branching in the maintenance of
diversity in watersheds. \emph{Freshwater Science} \textbf{37}, 712--730
(2018).

\leavevmode\hypertarget{ref-comteFishDispersalFlowing2018}{}%
23. Comte, L. \& Olden, J. D. Fish dispersal in flowing waters: A
synthesis of movement- and genetic-based studies. \emph{Fish and
Fisheries} \textbf{19}, 1063--1077 (2018).

\leavevmode\hypertarget{ref-radingerPatternsPredictorsFish2014}{}%
24. Radinger, J. \& Wolter, C. Patterns and predictors of fish dispersal
in rivers. \emph{Fish and Fisheries} \textbf{15}, 456--473 (2014).

\leavevmode\hypertarget{ref-rodriguezRestrictedMovementStream2002}{}%
25. Rodríguez, M. A. Restricted movement in stream fish: The paradigm is
incomplete, not lost. \emph{Ecology} \textbf{83}, 1--13 (2002).

\leavevmode\hypertarget{ref-bendaNetworkDynamicsHypothesis2004}{}%
26. Benda, L. E. E. \emph{et al.} The network dynamics hypothesis: How
channel networks structure riverine habitats. \emph{Bioscience}
\textbf{54}, 413--427 (2004).

\leavevmode\hypertarget{ref-poffHomogenizationRegionalRiver2007}{}%
27. Poff, N. L., Olden, J. D., Merritt, D. M. \& Pepin, D. M.
Homogenization of regional river dynamics by dams and global
biodiversity implications. \emph{Proceedings of the National Academy of
Sciences} \textbf{104}, 5732--5737 (2007).

\leavevmode\hypertarget{ref-palmerEcologicalRestorationStreams2014}{}%
28. Palmer, M. A., Hondula, K. L. \& Koch, B. J. Ecological restoration
of streams and rivers: Shifting strategies and shifting goals.
\emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{45},
247--269 (2014).

\leavevmode\hypertarget{ref-chaianunpornEvolutionaryResponsesClimate2015}{}%
29. Chaianunporn, T. \& Hovestadt, T. Evolutionary responses to climate
change in parasitic systems. \emph{Global Change Biology} \textbf{21},
2905--2916 (2015).
\end{cslreferences}

\end{document}

### 2021-01-05 manuscript.Rmd
bulk edits

--- 2020-12-24 manuscript/manuscript.Rmd
@@
 
-Despite the substantial difference in fish fauna between the study regions, the estimated Bayes factor in favor of the global model explaining $\gamma$ diversity was `r round(fit$gamma$bayes_factor, 1)`; this result strongly supports the consistent effects of ecosystem size and complexity on $\gamma$ diversity across the two biogeographic regions.
+Despite the substantial difference in fish fauna between the study regions, the estimated Bayes factor in favor of the global model was `r round(fit$gamma$bayes_factor, 1)` for $\gamma$ diversity; this result strongly supports the consistent effects of ecosystem size and complexity on $\gamma$ diversity across the two biogeographic regions.
 Further, we found patterns consistent with our theoretical predictions.
@@
 Hence, our findings should be broadly applicable to many taxa and ecosystems.
-Generalization of the complexity perspective is a frontier for future research.
+Generalization of our findings to other spatially complex ecosystems represents a frontier for future research.
 
@@
 
-## Theoretical branching networks
+## Theory
+
+### Theoretical branching networks
 
@@
 
-## Metacommunity model
+### Metacommunity model
 We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al.[@thompsonProcessbasedMetacommunityFramework2020].
@@
 
-Smaller values of $\nu$ imply greater costs of having wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$.
+Smaller values of $\nu$ imply greater costs of having wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$ near the niche optimum.
 
@@
 
-## Simulation
+### Simulation
 We used `r n_scenario` sets of parameter combinations to produce different landscape (four patterns of habitat heterogeneity) and ecological scenarios (eight patterns of dispersal and competition).
@@
 
-## Empirical data
+## Empirical data analysis
+
+### Fish community data
+
 We compiled fish data at two biogeographic regions: Hokkaido island, Japan and Midwest, US.
-For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish, monitoring data at protected watersheds, and primary data collected by the authors.
+For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish, monitoring data at protected watersheds, and primary data collected from literature.
 Collectively, these fish data encompass more than 7000 sites and covers the entire Hokkaido island.
 For the Midwest, we assembled fish community data collected by XXX.
+We detailed procedures for initial data screening in SI.
 
-We selected data based on the following criterion. First, we reviewed
+We further selected data based on the following criteria.
+First, we selected sampling sites with reliable coordinates.
+Sampling sites were treated as the same site if coordinates are identical at 3 decimal degrees.
+Second, for sites with multiple site visits (i.e., temporal replicates), we used the latest data at each sampling site to minimize variation in sampling efforts among sites.
+Lastly, we selected metacommunities (i.e., watersheds) that contain more than 10 sampling sites to reduce statistical uncertainties in estimating $\gamma$ diversity.
+We considered watersheds as separated from others if the river network flows into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in watershed area).
+
+We estimated $\alpha$, $\beta$ and $\gamma$ diversity at each watershed.
+$\gamma$ diversity is the total species richness at each watershed.
+Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
+Asymptotic species richness is the estimated total species richness in a given area and can be estimated from spatial replicates of local community data within a metacommunity.
+We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity).
+We assessed the completeness of the observed species richness based on sample coverage, which is the proportion of observed species richness to asymptotic species richness.
+We excluded watersheds whose sample coverage was below 0.9 because the estimates of asymptotic species richness may contain non-negligible statistical uncertainty.
+$\alpha$ diversity was estimated by taking an average of local species richness at each site.
+$\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity.
+
+After the data selection procedure, we obtained diversity estimates from `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (Hokkaido: `r nrow(wsd_subset[[1]])`, Midwest: `r nrow(wsd_subset[[2]])`), which encompassed a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites (Hokkaido: `r nrow(point_subset[[1]])`, Midwest: `r nrow(point_subset[[2]])`).
+
+### Environmental data
+
+We estimated watershed characteristics (watershed area and branching probability), climatic variables (annual mean air temperature and cumulative precipitation), and land use (% forest).
+We delineated watershed polygons and riverlines using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] with ArcMap 10.7 and SAGA 6.3.0 combined with an R package 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018].
+Watershed area was estimated based on the delineated watershed polygons using functions in an R package 'sf'[@pebesmaSimpleFeaturesStandardized2018].
+Branching probability was estimated by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$.
+A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
+For each watershed, we estimated the spatial averages of air temperature and cumulative precipitation at a 1-km resolution, which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005] via R package 'raster'.
+We calculated % forest for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
+
+### Statistical analysis
 

### 2021-01-05 manuscript.Rmd
Updates

@@
 
-Similarly, we found weak to moderate supports for the global models explaining observed patterns of $\alpha$ and $\beta$ diversity (Bayes factor: `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
+Similarly, we found weak to moderate supports for the global models of $\alpha$ and $\beta$ diversity (Bayes factor: `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
 In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity.
@@
 When $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on overall habitat diversity in a network.
+
 For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`).
@@
 Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness is the estimated total species richness in a given area and can be estimated from spatial replicates of local community data within a metacommunity.
-We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity).
+Asymptotic species richness can be interpreted as the estimated true species richness in a given area when it is estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014a; @chaseEcosystemDecayExacerbates2020].
+We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via an R package iNEXT[@hsiehINEXTPackageRarefaction2016].
 We assessed the completeness of the observed species richness based on sample coverage, which is the proportion of observed species richness to asymptotic species richness.
@@
 After the data selection procedure, we obtained diversity estimates from `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (Hokkaido: `r nrow(wsd_subset[[1]])`, Midwest: `r nrow(wsd_subset[[2]])`), which encompassed a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites (Hokkaido: `r nrow(point_subset[[1]])`, Midwest: `r nrow(point_subset[[2]])`).
+We used this dataset for statistical analysis.
 

### 2021-01-08 empirical/data_merge_hkd.R
Edits: minor

@@ -93,6 +93,7 @@
   ## export species list
   splist <- d0 %>% 
     filter(watershed_id %in% wsd_subset) %>% 
+    arrange(Species) %>% 
     as_tibble() %>% 
     distinct(Species)
     

### 2021-01-08 empirical/data_merge_mw.R

@@ -109,6 +109,7 @@
   ## export species list
   splist <- d0 %>% 
     filter(watershed_id %in% wsd_subset) %>% 
+    arrange(Species) %>% 
     as_tibble() %>% 
     distinct(Species)
   

### 2021-01-08 manuscript.Rmd
Update manuscript.Rmd

@@
 - Seoghyn Kim\footnotemark[1]
-- Christine L. Dolph^[Department of Ecology, Evolution and Behavior]
+- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of Minnesota]
+- Taku Kadoya^[National Institute for Environmental Studies]
+- Yusuke Miyazaki^[Shiraume Gakuen University]
+- Jacques C. Finlay\footnotemark[2]
 output:
@@
 ## read gis files
-filename <- list.files(path = normalizePath('../empirical/data_gis'), full.names = T)
+filename <- list.files(path = here::here('/empirical/data_gis'), full.names = T)
 wsd_subset <- lapply(filename[str_detect(filename, "wsd_subset")], st_read)
@@
 ## read theory file
-dat_sim <- read_csv(normalizePath('../theory/result/result_sim2020-11-10.csv'))
+dat_sim <- read_csv(here::here('/theory/result/result_sim2020-11-10.csv'))
 
@@
 
-source(normalizePath('../empirical/analysis_lm_bf.R'))
+source(here::here('/empirical/analysis_lm_bf.R'))
 
@@
 In 1921, Arrhenius[@arrheniusSpeciesArea1921] formulated the SAR as a power-law $S = cA^z$ ($S$ is the number of species observed in a given geographic area $A$), an equation currently known as the Arrhenius species-area relationship.
-Since then, the spatial scaling of species richness has been observed in nearly all taxonomic groups[@triantisIslandSpeciesArea2012], although the underlying mechanisms are still hotly debated[@ben-hurDisentanglingMechanismsUnderlying2020].
+Since then, the spatial scaling of species richness has been observed in many taxonomic groups[@triantisIslandSpeciesArea2012], although the underlying mechanisms are still hotly debated[@ben-hurDisentanglingMechanismsUnderlying2020].
 The SAR is ubiquitous because multiple mechanisms produce an apparently similar pattern.
@@
 Limited, but accumulating evidence suggests that classical concepts cannot predict ecological dynamics driven by branching structure[@faganConnectivityFragmentationExtinction2002; @grantUseMultipleDispersal2010; @teruiMetapopulationStabilityBranching2018], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@altermattDiversityRiverineMetacommunities2013; @carraraComplexInteractionDendritic2014; @carraraDendriticConnectivityControls2012; @teruiMetapopulationStabilityBranching2018].
-However, most research either has explored the consequences of branching complexity for local variation in species richness or relied on theoretical arguments with limited replicates of artificial branching networks.
+However, most research either has explored the consequences of branching complexity for local community structure[@altermattRiverNetworkProperties2013; @brownDendriticNetworkStructure2010] or relied solely on theoretical arguments[@holtRoleBranchingMaintenance2018].
 At present, we lack a comprehensive evaluation of how branching complexity, in combination with ecosystem size, scales biodiversity at the metacommunity level.
-Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services.
+Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006].
 
@@
 We predict that ecosystem size and branching complexity increase $\gamma$ diversity by enhancing either $\alpha$ and/or $\beta$ diversity under different ecological scenarios.
-The present study combines theory and statistical analysis of extensive community data to provide crucial insights into how ecological communities are structured in complex branching networks.
+The present study combines theory and empirical analysis of extensive community data to provide crucial insights into how ecological communities are structured in complex branching networks.
 
@@
 Simulated species with different niche in abiotic conditions (optimum and width) compete for resources with varied strengths.
-For simplicity, other ecological traits, such as dispersal probability, are assumed to be identical among species.
-Here, we depicted branching ecosystems as a spatial network of connected habitat patches (or a discretized river section; see **Figure 1**) where mean environmental conditions at each habitat patch are determined by two factors: (1) the headwater environments (the most upstream habitat patch) and (2) local environmental noise.
-Environmental values at the headwaters are drawn randomly from a normal distribution and propagates downstream with local environmental noise (i.e., the spatial autoregressive process with white noise).
+Here, we depicted branching ecosystems as a spatial network of connected habitat patches (**Figure 1**) where mean environmental conditions at each habitat patch are determined by two factors: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+Environmental values at headwaters are drawn randomly from a normal distribution and propagate downstream with local environmental noise (i.e., a spatial autoregressive process with white noise).
 These environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see Methods).
@@
 The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios.
-The strength of competition and dispersal processes (dispersal distance and probability) did not change the form of the relationships between $\gamma$ diversity and ecosystem properties.
+The strength of competition and dispersal processes (dispersal distance and probability) did not change the form of the relationships between $\gamma$ diversity and ecosystem properties (compare panels in **Figures 2 and 3**).
 Hence, the ecosystem size and complexity are both expected to increase $\gamma$ diversity regardless of ecological scenarios.
 
-Dispersal processes, however, affected underlying mechanisms that produce the positive effects of ecosystem size and complexity on $\gamma$ diversity.
+Dispersal processes, however, affected mechanisms that underlie the positive effects of ecosystem size and complexity on $\gamma$ diversity (compare left and right columns in **Figures 2 and 3**).
 We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation exists (i.e., species travel short distances).
 This pattern reflects significant spatial turnover of species composition over the branching network.
-In contrast, once the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
+In contrast, when the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
 The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects)[@thompsonProcessbasedMetacommunityFramework2020].
@@
 Influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios.
-Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$).
+Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) ().
 This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity[@hubbellUnifiedNeutralTheory2001].
 In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$).
-Under this scenario, having more branches may not contribute to the habitat diversity in the ecosystem because local environmental noise masks environmental differences between branches.
+Under this scenario, having more branches may not contribute to the overall habitat diversity in the ecosystem because local environmental noise masks environmental differences between branches.
 Therefore, this landscape scenario decouples the intimate relationship between branching structure and habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
-This theoretical prediction may not apply to pristine to semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes.
-Instead, it may be more relevant to severely altered landscapes where human disturbance compromises the environmental distinctiveness of each branch through, for example, flow regulations by dams.
-Hence, our theory has important implications for riverine biodiversity conservation by pointing the crucial role of habitat diversity produced by branching structure[@holtRoleBranchingMaintenance2018].
+This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes[@altermattDiversityRiverineMetacommunities2013; @bendaNetworkDynamicsHypothesis2004; @mooreEmergentStabilityLarge2015; @nakamuraDisturbanceRegimesStream2000; @petersonModellingDendriticEcological2013; @teruiMetapopulationStabilityBranching2018].
+Instead, it may be more relevant to severely altered landscapes where human disturbance compromises the environmental distinctiveness of branches through, for example, flow regulations by dams[@poffHomogenizationRegionalRiver2007].
+Hence, our theory has important implications for riverine biodiversity conservation by pointing the crucial role of habitat diversity produced by branching structure.
 
@@
 Similarly, we found weak to moderate supports for the global models of $\alpha$ and $\beta$ diversity (Bayes factor: `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
-In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity.
+In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity while $\alpha$ diversity showing a vague response to these ecosystem properties.
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly match the previous observations of stream fish movement.
@@
 First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
-Human alterations, including flow regulation[@poffHomogenizationRegionalRiver2007], habitat fragmentation, and stream burial, may compromise or restrict access to the diverse habitats that complex branching networks may provide.
-Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human alterations.
-Second, the complexity perspective may provide viable options to reconcile conflicts between biodiversity conservation and societal needs.
-Although protected areas spearhead global conservation efforts, habitat preservation and restoration over large areas are often impractical because of conflicts with stakeholders.
-This is particularly true for riverine ecosystems, where numerous stakeholders are involved within a single watershed and enormous efforts are required to reach consensus[@palmerEcologicalRestorationStreams2014].
-In such a scenario, spatial planning of small-scale conservation, such as restoration of connectivity to small tributaties, may be critical to enhancing the 'realized' network complexity that organisms may experience.
-Our theoretical framework may be used to design spatial arrangement of small-scale conservation that improves ecological outcomes at the metacommunity level.
+Human-induced habitat alterations, including flow regulation[@poffHomogenizationRegionalRiver2007], habitat fragmentation[@fukushimaModellingEffectsDams2007; @moritaEffectsHabitatFragmentation2002], and stream burial, may compromise or restrict access to the diverse habitats that complex branching networks may provide.
+Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human activities.
+Second, the complexity perspective may provide insights into the spatial arrangement of conservation efforts.
+A growing body of evidence suggests the effectiveness of riverine reserves and local restoration, and how to arrange a spatial network of conservation sites in rivers is an area of active research[@koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013; @sundermannRiverRestorationSuccess2011].
+The results of this study clearly indicate that riverine conservation networks should be designed to involve diverse tributaries, as inferred from a successful reserve network of the Salween basin in Thailand[@koningNetworkGrassrootsReserves2020].
 
@@
 Hence, our findings should be broadly applicable to many taxa and ecosystems.
-Generalization of our findings to other spatially complex ecosystems represents a frontier for future research.
+Generalization of our findings in spatially complex ecosystems represents a frontier for future research.
 
@@
 
-We estimated watershed characteristics (watershed area and branching probability), climatic variables (annual mean air temperature and cumulative precipitation), and land use (% forest).
+We collected data for watershed characteristics (watershed area and branching probability), climatic variables (annual mean air temperature and cumulative precipitation), and land use (% forest).
 We delineated watershed polygons and riverlines using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] with ArcMap 10.7 and SAGA 6.3.0 combined with an R package 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018].
@@
 
+We developed linear models to examine the effects of macro-scale drivers on diversity metrics.
+Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $i$, $log_{10}~y_i$, are assumed to follow a normal distribution as $log_{10}~y_i \sim Normal(\mu_i, \sigma^2)$.
+The parameter $\mu_i$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, and proportion of forest land use (logit-transformed).
+Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to statistically control these effects.
+
+Climate and land use differed clearly between the regions: therefore, we used residuals of the simple linear regressions between either the climate or land use variable (response variable) and region (explanatory variable) to avoid correlation between explanatory variables.
+The residuals represent deviations from the regional averages; positive values indicate values greater than the regional average while negative values indicating values smaller than the regional average.
+
+We constructed two models for each of diversity metrics: global and region-specific models.
+The global model assumes that the effects of watershed area and branching probability are consistent across biogeographic regions (i.e., no interactive effects of region with other linear predictors).
+
+$$
+\mu_i = \xi_0 + \xi_1~log_{10}~WA_i + \xi_2~log_{10}~P_{b,i} + \xi_3~region_i + \sum_k \xi_k x_{k,i}
+$$
+where $\xi_k$ is the intercept and regression coefficients for linear predictors.
+Meanwhile, the region-specific model assumes the effects of watershed area and branching probability differ between regions (i.e., interactions between region and watershed area/branching probability).
+
+$$
+\mu_i = \xi_0 + \xi_1~log_{10}~wa_i + \xi_2~log_{10}~p_{b,i} + \xi_3~region_i + \xi_4~log_{10}~WA_i \cdot region_i + \xi_5~log_{10}~P_{b,i} \cdot region_i + \sum_k \xi_k x_{k,i}
+$$
+We compared the performance of these competing models using the Bayes factor[@wagenmakersPracticalSolutionPervasive2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1).
+We used Bayesian Information Criteria (BIC) of the linear models to approximate the Bayes factor[@wagenmakersPracticalSolutionPervasive2007]:
+
+$$
+Bayes~factor = exp(\Delta BIC_{10}/2)
+$$
+where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$.
+
 # References

### 2021-01-09 manuscript.Rmd
Update manuscript.Rmd

@@
 - Akira Terui^[Department of Biology, University of North Carolina at Greensboro]
-- Seoghyn Kim\footnotemark[1]
+- Seoghyun Kim\footnotemark[1]
 - Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of Minnesota]
@@
 - Yusuke Miyazaki^[Shiraume Gakuen University]
-- Jacques C. Finlay\footnotemark[2]
 output:
+  word_document: default
   html_notebook: default
-  word_document: default
-abstract: |
-  |This is the abstract.
+abstract:
+  The species-area relationship (the SAR), a tendency in which species richness increases with increasing area, is one of the most robust empirical generalizations in ecology and has provided the foundation for area-based conservation strategies.
+However, many ecosystems possess complex spatial structure that cannot be repserented by area (the scale-invariant complexity) and its role in scaling biodiversity is largely unknown.
+Here, we hypthesized that ecosystem size and complexity jointly regulate biodiversity in rivers, a prime example of fractal branching networks where the recurrent merging of diverse streams generates a pronounced self-similarity in complex branching patterns.
+Ecosystem size should dictate metacommunity size and habitat diversity that regulate watershed-scale species richness.
+Meanwhile, ecosystem complexity, which we defined as the probability of branching per unit river distance, should increase watershed-scale species richness by increasing habitat heterogeneity.
+We developed theoretical models simulating metacommunity dynamics in branching river networks and yielded results consistent with our hypothesis.
+Ecosystem size and complexity both increased watershed-scale species richness ($\gamma$ diversity), and the importance of spatial turnover in species composition ($\beta$ diversity) was apparent when simulated species travel short distances.
+Our cross-watershed comparisons across two biogeographic regions (Hokkaido, Japan and Midwest, US) provided empirical supports for the theoretical predictions.
+As predicted, watershed-scale species richness increased with ecosystem size (watershed area) and complexity (branching probability) through enhanced spatial turnover in species composition over the branching network.
+There is now a clear need to consider the dimension of ecosystem complexity in biodiversity conservation.
+The dual dimensional approach - size and complexity - should broaden viable options for spatial planning of protected areas or restoration sites, thereby helping reconcile the conflicts between biodiversity conservation and societal demands.
+
 bibliography: reference.bib
@@
 ```
+
+# Maintext
 
@@
 
-Influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios.
-Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) ().
+Influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios (**cite SI Figure**).
+Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**cite SI Figure**).
 This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity[@hubbellUnifiedNeutralTheory2001].
 In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$).
-Under this scenario, having more branches may not contribute to the overall habitat diversity in the ecosystem because local environmental noise masks environmental differences between branches.
+Under this scenario, having more branches may not contribute to the overall habitat diversity in the ecosystem because local environmental noise masks environmental differences between branches (**cite SI Figure**).
 Therefore, this landscape scenario decouples the intimate relationship between branching structure and habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
@@
 Despite the substantial difference in fish fauna between the study regions, the estimated Bayes factor in favor of the global model was `r round(fit$gamma$bayes_factor, 1)` for $\gamma$ diversity; this result strongly supports the consistent effects of ecosystem size and complexity on $\gamma$ diversity across the two biogeographic regions.
-Further, we found patterns consistent with our theoretical predictions.
+We found patterns consistent with our theoretical predictions (**Table 1 and Figure 4**).
 The estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) across watersheds.
-These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, and land use).
+These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, and land use) (**Table 1**).
 Overall, our statistical analysis provides strong empirical evidence that ecosystem size and complexity jointly, but independently, scale riverine biodiversity at the metacommunity level.
@@
 Similarly, we found weak to moderate supports for the global models of $\alpha$ and $\beta$ diversity (Bayes factor: `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
-In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity while $\alpha$ diversity showing a vague response to these ecosystem properties.
+In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity while $\alpha$ diversity showing a vague response to these ecosystem properties (**Table 1 and Figure 4**).
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly match the previous observations of stream fish movement.
@@
 If the intensive land use by humans causes significant homogenization of in-stream habitat conditions among tributaries, theory predicts weakened effects of branching probability on $\gamma$ diversity.
-However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions to support high spatial trunover of species composition.
+However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions to support high spatial turnover of species composition.
 In support of this interpretation, $\beta$ diversity increased with increasing branching probability in both regions (**Figure 4**).
@@
 First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
-Human-induced habitat alterations, including flow regulation[@poffHomogenizationRegionalRiver2007], habitat fragmentation[@fukushimaModellingEffectsDams2007; @moritaEffectsHabitatFragmentation2002], and stream burial, may compromise or restrict access to the diverse habitats that complex branching networks may provide.
+Human-induced habitat alterations, including flow regulation[@poffHomogenizationRegionalRiver2007], habitat fragmentation[@fukushimaModellingEffectsDams2007; @moritaEffectsHabitatFragmentation2002], and stream burial, may compromise or restrict access to the diverse habitats that complex branching networks may support.
 Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human activities.
-Second, the complexity perspective may provide insights into the spatial arrangement of conservation efforts.
-A growing body of evidence suggests the effectiveness of riverine reserves and local restoration, and how to arrange a spatial network of conservation sites in rivers is an area of active research[@koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013; @sundermannRiverRestorationSuccess2011].
-The results of this study clearly indicate that riverine conservation networks should be designed to involve diverse tributaries, as inferred from a successful reserve network of the Salween basin in Thailand[@koningNetworkGrassrootsReserves2020].
+Second, the complexity perspective may provide insights into spatial planning of conservation efforts.
+Riverine reserves and local restoration are increasingly recognized as an effective management tool, and how to design a spatial network of conservation sites in rivers is an area of active research[@koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013; @sundermannRiverRestorationSuccess2011].
+While large reserves or restoration sites are undoubtedly important[@koningNetworkGrassrootsReserves2020], our results indicate the potential of coordinated networks of local conservation sites in protecting biodiversity.
+For example, synergies of multiple small reserves may emerge at the watershed scale when multiple ecologically-distinct tributaties are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin[@koningNetworkGrassrootsReserves2020].
+Our findings, therefore, offer the ecological foundation for the network-based conservation strategies in rivers, broadening viable options towards successful conservation.
 
@@
 The parameter $\rho$ can take values of $0-1$ with larger values indicating greater spatial autocorrelation.
-In this study, we set $\rho = 1$ to mimic strong spatial autocorrelation in rinverine environments.
+In this study, we set $\rho = 1$ to mimic strong spatial autocorrelation in riverine environments.
 At confluences, we took a weighted mean of environmental values given the relative size of upstream contributing area of joining tributaries:
@@
 where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the interaction coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
+$K_x$ was expressed as a function of the number of upstream contributing patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area[@altermattRiverNetworkProperties2013; @teruiThreeEcologicalFactors2016].
 The parameter $\alpha_{ij}$ is expressed as the strength of interspecific competition relative to that of intraspecific competition such that interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ > 1 (intraspecific competition coefficient $\alpha_{ii} = 1$).
+$\alpha_{ij}$ was drawn randomly from a uniform distribution as $\alpha_{ij} \sim Unif(0, \alpha_{max})$.
 The density-independent reproductive rate $r_{ix}(t)$ is affected by abiotic environments (non-consumable) and determined by the following Gaussian function:
@@
 We compiled fish data at two biogeographic regions: Hokkaido island, Japan and Midwest, US.
-For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish, monitoring data at protected watersheds, and primary data collected from literature.
-Collectively, these fish data encompass more than 7000 sites and covers the entire Hokkaido island.
-For the Midwest, we assembled fish community data collected by XXX.
-We detailed procedures for initial data screening in SI.
+For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish, monitoring data at protected watersheds, and primary data collected from literature, covering the entire Hokkaido island.
+For the Midwest, we assembled fish community data collected by Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
+We detailed procedures for initial data selection in SI.
 
-We further selected data based on the following criteria.
+We selected data based on the following criteria.
 First, we selected sampling sites with reliable coordinates.
@@
 $$
-\mu_i = \xi_0 + \xi_1~log_{10}~wa_i + \xi_2~log_{10}~p_{b,i} + \xi_3~region_i + \xi_4~log_{10}~WA_i \cdot region_i + \xi_5~log_{10}~P_{b,i} \cdot region_i + \sum_k \xi_k x_{k,i}
+\mu_i = \xi_0 + \xi_1~log_{10}~WA_i + \xi_2~log_{10}~P_{b,i} + \xi_3~region_i + \xi_4~log_{10}~WA_i \cdot region_i + \xi_5~log_{10}~P_{b,i} \cdot region_i + \sum_k \xi_k x_{k,i}
 $$

### 2021-01-15 manuscript.Rmd
Update manuscript

@@
 output:
+  html_notebook: default
   word_document: default
-  html_notebook: default
 abstract:
@@
 We constructed a general simulation model of metacommunity dynamics [@thompsonProcessbasedMetacommunityFramework2020], in which 50 competing species disperse and spatially interact in a random branching network.
-Simulated species with different niche in abiotic conditions (optimum and width) compete for resources with varied strengths.
+Simulated species with different niches in abiotic conditions (optimum and width) compete for resources with varied strengths.
 Here, we depicted branching ecosystems as a spatial network of connected habitat patches (**Figure 1**) where mean environmental conditions at each habitat patch are determined by two factors: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
@@
 $$
-where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at patch $k$ (akin to upstream watershed area).
+where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to upstream watershed area).
 With this expression, larger tributaties have a greater influence on the downstream environment, as observed in natural river networks[@bendaNetworkDynamicsHypothesis2004].
@@
 
+We allowed interspecific variation in niche optimum and width, which were drawn from uniform distributions as $\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$.
 We used fixed values for the following parameters: maximum reproductive number ($r_{0,i} =$ 4), niche cost ($\nu =$ `r unique(dat_sim$niche_cost)`), the degree of temporal fluctuation in abiotic environments ($\sigma_z =$ `r unique(dat_sim$sd_env)`), and the degree of spatial autocorrelation in temporal environmental dynamics ($\phi =$ `r unique(dat_sim$phi)`).
@@
 
-We selected data based on the following criteria.
-First, we selected sampling sites with reliable coordinates.
-Sampling sites were treated as the same site if coordinates are identical at 3 decimal degrees.
-Second, for sites with multiple site visits (i.e., temporal replicates), we used the latest data at each sampling site to minimize variation in sampling efforts among sites.
-Lastly, we selected metacommunities (i.e., watersheds) that contain more than 10 sampling sites to reduce statistical uncertainties in estimating $\gamma$ diversity.
-We considered watersheds as separated from others if the river network flows into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in watershed area).
+We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in watershed area).
+Metacommunities with $\ge$ 10 sampling sites were used in our analysis because small sample size inflates statistical uncertainties in estimating diversity metrics.
 
@@
 We collected data for watershed characteristics (watershed area and branching probability), climatic variables (annual mean air temperature and cumulative precipitation), and land use (% forest).
-We delineated watershed polygons and riverlines using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] with ArcMap 10.7 and SAGA 6.3.0 combined with an R package 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018].
+We delineated watershed polygons and river lines (defined as $\ge$ 1 km^2^) using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] with ArcMap 10.7 and SAGA 6.3.0 combined with an R package 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018].
 Watershed area was estimated based on the delineated watershed polygons using functions in an R package 'sf'[@pebesmaSimpleFeaturesStandardized2018].
@@
 
+# Acknowledgements
+
+# Author contributions
+
 # References

### 2021-01-15 supplementary_information.Rmd
Create supplementary_information.Rmd

---
title: |
  | Ecosystem size and complexity dictate riverine biodiversity
  | Supplementary Information for:
author:
- Akira Terui^[Department of Biology, University of North Carolina at Greensboro]
- Seoghyun Kim\footnotemark[1]
- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of
  Minnesota]
- Taku Kadoya^[National Institute for Environmental Studies]
- Yusuke Miyazaki^[Shiraume Gakuen University]
output:
  pdf_document:
    toc: yes
    toc_depth: 2
bibliography: reference.bib
csl: nature.csl
---

```{r setup, include=FALSE}

pacman::p_load(tidyverse, knitr, kableExtra)
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

# Hokkaido data
dat_hkd <- read_csv(here::here('/empirical/data_org_hkd/data_fmt_hkd_latest.csv')) %>% 
  filter(Year >= 1990)

# Midwest data
fishdata <- list.files(path = here::here("/empirical/data_org_mw"), full.names = TRUE) %>% lapply(read_csv)
dat_mw <- do.call(what = bind_rows, args = fishdata)

```

# Fish community data

## Hokkaido, Japan
We used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected from literature[@teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island. Data were collected from summer to fall. We screened data through the following procedure:

1. We listed recorded fish species and re-organized species names to be consistent across the data sets.
1. We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve unidentified species that are rarely observed in the data set (< 100 sites occurrence).
1. For sites with multiple visits (i.e., temporal replicates), we used the latest-year observation at each sampling site to minimize variation in sampling efforts among sites. Surveys that occurred in the same year were aggregated into a single observation.
1. We confined sites to those with the latest observation year of $\ge$ 1990. Although the data set contained observations from 1953, we added this restriction to align the observation period with the data set in the Midwest, US.
1. Four genera (Lethenteron, Pungitius, Rhinogobius, and Tribolodon) were treated as species groups (i.e., spp.) as taxonomic resolutions varied greatly among data sources.

## Midwest, US
We assembled fish community data collected by the Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources. These data sets cover most of Upper Mississippi (HUC 2, region 07) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05). Data were collected from summer to fall with electrofishing (backpack, barge-type, or boat-mounted) and supplemental netting at some locations. We screened data through the following procedure:

1. We used data of the Upper Mississippi (HUC 2, region 07) and Great Lakes basins (HUC 2, region 04) as most sites are included in these regions.
1. We removed records of unidentified species, hybrid species, and commercial species that are apparently absent in the wild (e.g., goldfish).
1. We used the latest observation at each sampling site to minimize variation in sampling efforts among sites.

\newpage

# Tables

## Table S1 Species list in Hokkaido, Japan

Species list in Hokkaido, Japan. Species are ordered alphabetically.

```{r chunk_table1}

dat_hkd %>% 
  filter(Year >= 1990) %>% 
  mutate(Species = str_replace_all(str_to_title(OTU), "_", " ")) %>% 
  mutate(Species = str_replace_all(Species, "(spp$)|(spp\\s)", "spp\\.")) %>% 
  mutate(Species = str_replace_all(Species, "(sp$)", "sp\\.")) %>% 
  mutate(Species = str_replace_all(Species, "(subsp)", "subsp\\. ")) %>% 
  mutate(Species = str_replace_all(Species, "(sp\\sme$)", "sp\\. ME")) %>% 
  group_by(Species) %>% 
  summarise('Number of sites present' = n_distinct(SiteID)) %>% 
  kable(format = 'markdown')

```

\newpage

# Figures

```{r chunk_fig1}

source(here::here("/theory/figure_n_patch_si.R"))

figure_cap <- conditional_text <- NULL

for(i in seq_len(nrow(param))){
  if(param$sigma_h[i] > param$sigma_l[i]){
    conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) exceeds local environmental noise ($\\sigma_{l}$)."
  }else{
    if(param$sigma_h[i] == param$sigma_l[i]){
      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is equal to local environmental noise ($\\sigma_{l}$)."
    }else{
      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is less than local environmental noise ($\\sigma_{l}$)."
    }
  }

  figure_cap[i] <- paste0("Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$). Other parameters are as follows: dispersal probability $p_{d} = `r param$p_d[",i,"]`$; environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$.")
}

figure_size <- NULL
for(i in seq_len(nrow(param))){
  knit_chunk <- paste0("## Figure S", i, " Influence of ecosystem size ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
                       "\n```{r fig", i,", fig.width = 8, fig.height = 6}\n\n f[[",i,"]] \n\n```\n",
                       "\n **Figure S", i, "** ", figure_cap[i], "\n\\pagebreak\n")
  figure_size <- c(figure_size, knit_chunk)
}

```

`r paste(knit(text = figure_size), collapse = '\n')`

```{r chunk_fig2}

source(here::here("/theory/figure_p_branch_si.R"))

figure_cap <- conditional_text <- NULL

for(i in seq_len(nrow(param))){
  if(param$sigma_h[i] > param$sigma_l[i]){
    conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) exceeds local environmental noise ($\\sigma_{l}$)."
  }else{
    if(param$sigma_h[i] == param$sigma_l[i]){
      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is equal to local environmental noise ($\\sigma_{l}$)."
    }else{
      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is less than local environmental noise ($\\sigma_{l}$)."
    }
  }

  figure_cap[i] <- paste0("Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$). Other parameters are as follows: dispersal probability $p_{d} = `r param$p_d[",i,"]`$; environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$.")
}

figure_complex <- NULL
for(i in seq_len(nrow(param))){
  j <- i + 7
  knit_chunk <- paste0("## Figure S", j, " Influence of ecosystem complexity ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
                       "\n```{r fig", j,", fig.width = 8, fig.height = 6}\n\n g[[",i,"]] \n\n```\n",
                       "\n **Figure S", j, "** ", figure_cap[i], "\n\\pagebreak\n")
  figure_complex <- c(figure_complex, knit_chunk)
}

```

`r paste(knit(text = figure_complex), collapse = '\n')`

# References

### 2021-01-15 figures.Rmd
Update misc

--- 2020-11-14 manuscript/figures.Rmd
@@
 
-source(normalizePath("../empirical/figure_map.R"))
+source(here::here("/empirical/figure_map.R"))
 
@@
 Rows represent different competition strength.
-Competitive coefficients ($\\alpha_{c}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
+Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
 Columns represent different dispersal scenarios.
@@
 
-source(normalizePath("../theory/figure_n_patch.R"))
+source(here::here("/theory/figure_n_patch.R"))
 ```
@@
 
-source(normalizePath("../theory/figure_p_branch.R"))
+source(here::here("/theory/figure_p_branch.R"))
 ```
@@
 
-source(normalizePath("../empirical/figure_diversity.R"))
+source(here::here("/empirical/figure_diversity.R"))
 ```

### 2021-01-15 table.Rmd
Update misc

---
title: "Tables"
output:
  pdf_document: default
---

```{r setup, include=FALSE}

  knitr::opts_knit$set(root.dir = here::here("empirical"))

```

```{r, echo = FALSE, message=FALSE, results='asis'}

source(here::here("/empirical/analysis_lm_bf.R"))

stargazer::stargazer(fit$alpha$model, fit$beta$model, fit$gamma$model,
                     header = FALSE,
                     title = "Estimated parameters of linear regression models explaining fish species richness in Hokkaido (Japan) and Midwest (US) regions. Dependent variables were log-10 transformed. Environmental variables (air temperature, precipitation, logit \\% forest) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.",
                     type = "latex",
                     ci = TRUE,
                     covariate.labels = c("$log_{10}$ Watershed area",
                                          "$log_{10}$ Branching probability",
                                          "Region (Midwest vs. Hokkaido)",
                                          "Air temperature",
                                          "Precipitation",
                                          "Logit \\% forest",
                                          "Intercept"),
                     single.row = FALSE,
                     digits = 2,
                     dep.var.labels.include = FALSE,
                     column.labels = c("$\\alpha$ diversity", "$\\beta$ diversity", "$\\gamma$ diversity"),
                     keep.stat = c("rsq"),
                     model.numbers = FALSE)

```

### 2021-01-15 theory/figure_n_patch_si.R

@@ -1,17 +1,23 @@
 
 # setup -------------------------------------------------------------------
 
-  rm(list = ls(all.names = TRUE))
   pacman::p_load(tidyverse)
+  
+  param <- expand.grid(sigma_l = c(0.01, 1), sigma_h = c(1, 0.01), p_d = c(0.1, 0.01)) %>% 
+    filter(!(p_d == 0.01 & sigma_h > sigma_l))
+  
+  f <- list(NULL)
 
+for(i in seq_len(nrow(param))){
+  
 # read data ---------------------------------------------------------------
 
   dat <- read_csv(here::here("theory/result/result_sim2020-11-10.csv")) %>% 
     select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
-           p_dispersal == 0.01,
-           sd_env_source == 0.01,
-           sd_env_lon == 0.01) %>% 
+           p_dispersal == param$p_d[i],
+           sd_env_source == param$sigma_h[i],
+           sd_env_lon == param$sigma_l[i]) %>%
     mutate(beta_div = gamma_div/alpha_div) %>% 
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
@@ -55,7 +61,7 @@
 
 # ecosystem size effect ---------------------------------------------------
 
-  g <- dat %>% 
+  f[[i]] <- dat %>% 
     ggplot(aes(x = n_patch, y = value, color = metric, fill = metric)) +
     geom_smooth(method = "loess", size = 0.5) +
     scale_y_continuous(trans = "log10") +
@@ -66,6 +72,5 @@
          y = "Species richness") +
     guides(color = guide_legend(override.aes = list(fill = NA)),
            fill = FALSE)
-  
-  print(g)
-  
+
+}

### 2021-01-15 theory/figure_p_branch_si.R

@@ -1,17 +1,23 @@
 
 # setup -------------------------------------------------------------------
   
-  rm(list = ls(all.names = TRUE))
   pacman::p_load(tidyverse)
-
+  
+  param <- expand.grid(sigma_l = c(0.01, 1), sigma_h = c(1, 0.01), p_d = c(0.1, 0.01)) %>% 
+    filter(!(p_d == 0.01 & sigma_h > sigma_l))
+  
+  g <- list(NULL)
+  
+for(i in seq_len(nrow(param))){
+  
 # read data ---------------------------------------------------------------
   
   dat <- read_csv(here::here("theory/result/result_sim2020-11-10.csv")) %>% 
     select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
-           p_dispersal == 0.01,
-           sd_env_source == 1,
-           sd_env_lon == 1) %>% 
+           p_dispersal == param$p_d[i],
+           sd_env_source == param$sigma_h[i],
+           sd_env_lon == param$sigma_l[i]) %>% 
     mutate(beta_div = gamma_div/alpha_div) %>% 
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
@@ -55,7 +61,7 @@
 
 # complexity effect -------------------------------------------------------
 
-  g <- dat %>% 
+  g[[i]] <- dat %>% 
     ggplot(aes(x = p_branch, y = value, color = metric, fill = metric)) +
     geom_smooth(method = "loess", size = 0.5) +
     scale_y_continuous(trans = "log10") +
@@ -67,4 +73,4 @@
     guides(color = guide_legend(override.aes = list(fill = NA)),
            fill = FALSE)
   
-  print(g)
+}

### 2021-01-15 supplementary_information.Rmd
Edits: add tables to SI

@@
 title: |
+  | Supplementary Information for:
   | Ecosystem size and complexity dictate riverine biodiversity
-  | Supplementary Information for:
 author:
@@
 # Hokkaido data
-dat_hkd <- read_csv(here::here('/empirical/data_org_hkd/data_fmt_hkd_latest.csv')) %>% 
-  filter(Year >= 1990)
+dat_hkd <- read_csv(here::here('/empirical/data_out/dat_hkd_site.csv'))
 
 # Midwest data
-fishdata <- list.files(path = here::here("/empirical/data_org_mw"), full.names = TRUE) %>% lapply(read_csv)
-dat_mw <- do.call(what = bind_rows, args = fishdata)
+dat_mw <- read_csv(here::here('/empirical/data_out/dat_mw_site.csv'))
 
@@
 
-## Table S1 Species list in Hokkaido, Japan
+## Table S1 List of fish species in Hokkaido, Japan
 
-Species list in Hokkaido, Japan. Species are ordered alphabetically.
+List of fish species in Hokkaido, Japan that are included in our statistical analysis.
+`r n_distinct(dat_hkd$Species)` species are ordered alphabetically with the number of sites present and % occupancy out of `r n_distinct(dat_hkd$SiteID)` sites.
 
@@
 dat_hkd %>% 
-  filter(Year >= 1990) %>% 
-  mutate(Species = str_replace_all(str_to_title(OTU), "_", " ")) %>% 
+  mutate(n_site = n_distinct(SiteID)) %>% 
+  mutate(Species = str_replace_all(str_to_title(Species), "_", " ")) %>% 
   mutate(Species = str_replace_all(Species, "(spp$)|(spp\\s)", "spp\\.")) %>% 
@@
   group_by(Species) %>% 
-  summarise('Number of sites present' = n_distinct(SiteID)) %>% 
+  summarise('Number of sites present' = n_distinct(SiteID),
+            'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
+  kable(format = 'markdown')
+
+```
+
+\newpage
+
+## Table S2 List of fish species in Midwest, US
+
+List of fish species in Midwest, US that are included in our statistical analysis.
+`r n_distinct(dat_mw$Species)` species are ordered alphabetically with the number of sites present and % occupancy out of `r n_distinct(dat_mw$SiteID)` sites.
+
+```{r chunk_table2}
+
+sp_mw_latin <- read_csv(here::here('/empirical/data_out/data_mw_splist_latin.csv'))
+
+dat_mw %>% 
+  mutate(n_site = n_distinct(SiteID)) %>% 
+  rename(Common_name = Species) %>% 
+  group_by(Common_name) %>% 
+  summarise('Number of sites present' = n_distinct(SiteID),
+            'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
+  left_join(sp_mw_latin, by = "Common_name") %>% 
+  select(Species = Latin_name,
+         'Number of sites present',
+         'Occupancy (%)') %>% 
+  arrange(Species) %>% 
   kable(format = 'markdown')

### 2021-01-16 manuscript.Rmd
Update manuscript.Rmd

@@
 output:
+  word_document: default
   html_notebook: default
-  word_document: default
 abstract:
-  The species-area relationship (the SAR), a tendency in which species richness increases with increasing area, is one of the most robust empirical generalizations in ecology and has provided the foundation for area-based conservation strategies.
-However, many ecosystems possess complex spatial structure that cannot be repserented by area (the scale-invariant complexity) and its role in scaling biodiversity is largely unknown.
-Here, we hypthesized that ecosystem size and complexity jointly regulate biodiversity in rivers, a prime example of fractal branching networks where the recurrent merging of diverse streams generates a pronounced self-similarity in complex branching patterns.
-Ecosystem size should dictate metacommunity size and habitat diversity that regulate watershed-scale species richness.
-Meanwhile, ecosystem complexity, which we defined as the probability of branching per unit river distance, should increase watershed-scale species richness by increasing habitat heterogeneity.
+  The species-area relationship (the SAR), a tendency in which species richness increases with increasing area, is one of the most robust empirical generalizations in ecology and formed the basis of area-based conservation strategies.
+However, many ecosystems possess a complex spatial structure that cannot be represented by area (the scale-invariant complexity), and its role in scaling biodiversity is largely unknown.
+Here, we hypothesized that ecosystem size and complexity jointly regulate biodiversity in rivers.
+Rivers are a prime example of fractal branching networks where the recurrent merging of diverse streams generates a pronounced self-similarity in complex branching patterns.
+Ecosystem complexity, which we defined as the probability of branching per unit river distance, should increase watershed-scale species richness by increasing habitat heterogeneity (habitat diversity per unit area).
+Meanwhile, ecosystem size should dictate metacommunity size and total habitat diversity (area x habitat heterogeneity), two primary factors that regulate watershed-scale species richness.
 We developed theoretical models simulating metacommunity dynamics in branching river networks and yielded results consistent with our hypothesis.
-Ecosystem size and complexity both increased watershed-scale species richness ($\gamma$ diversity), and the importance of spatial turnover in species composition ($\beta$ diversity) was apparent when simulated species travel short distances.
-Our cross-watershed comparisons across two biogeographic regions (Hokkaido, Japan and Midwest, US) provided empirical supports for the theoretical predictions.
-As predicted, watershed-scale species richness increased with ecosystem size (watershed area) and complexity (branching probability) through enhanced spatial turnover in species composition over the branching network.
+Ecosystem size and complexity increased watershed-scale species richness ($\gamma$ diversity), and the importance of spatial turnover in species composition ($\beta$ diversity) was apparent when simulated species dispersal is limited.
+Cross-watershed comparisons across two biogeographic regions (Hokkaido, Japan and Midwest, US) provided empirical support for the theoretical predictions.
+In both regions, watershed-scale species richness increased with ecosystem size (watershed area) and complexity (branching probability) through enhanced spatial turnover in species composition over the branching network.
 There is now a clear need to consider the dimension of ecosystem complexity in biodiversity conservation.
@@
 One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR)[@lomolinoEcologyMostGeneral2000a].
-In 1921, Arrhenius[@arrheniusSpeciesArea1921] formulated the SAR as a power-law $S = cA^z$ ($S$ is the number of species observed in a given geographic area $A$), an equation currently known as the Arrhenius species-area relationship.
-Since then, the spatial scaling of species richness has been observed in many taxonomic groups[@triantisIslandSpeciesArea2012], although the underlying mechanisms are still hotly debated[@ben-hurDisentanglingMechanismsUnderlying2020].
+In 1921, Arrhenius[@arrheniusSpeciesArea1921] formulated the SAR as a power-law $S = cA^z$ ($S$ is the number of species observed in a given geographic area $A$, $c$ a constant, and $z$ a scaling exponent), an equation currently known as the Arrhenius species-area relationship.
+Since then, the spatial scaling of species richness has been observed in many taxonomic groups[@triantisIslandSpeciesArea2012].
 The SAR is ubiquitous because multiple mechanisms produce an apparently similar pattern.
@@
 Importantly, the SAR provides the foundation for global conservation efforts.
-For example, conservation ecologists have used the SAR estimates to design marine and terrestrial protected areas, which currently encompass more than 30 million km² globally.
+For example, conservation ecologists have used the SAR estimates to design marine and terrestrial protected areas, which currently encompass more than 30 million km^2^ globally[@deguignet2014UnitedNations2014].
 
-Many ecosystems, however, possess complex spatial structure that cannot be represented by area - a dimension referred to as the scale-invariant complexity[@rinaldoEvolutionSelectionRiver2014; @rodriguez-iturbeFractalRiverBasins2001].
+Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity[@rinaldoEvolutionSelectionRiver2014; @rodriguez-iturbeFractalRiverBasins2001].
 Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few[@rodriguez-iturbeFractalRiverBasins2001].
@@
 Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms[@grantLivingBranchesPopulation2007; @rinaldoRiverNetworksEcological2018;@tonkinRoleDispersalRiver2018].
-Limited, but accumulating evidence suggests that classical concepts cannot predict ecological dynamics driven by branching structure[@faganConnectivityFragmentationExtinction2002; @grantUseMultipleDispersal2010; @teruiMetapopulationStabilityBranching2018], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@altermattDiversityRiverineMetacommunities2013; @carraraComplexInteractionDendritic2014; @carraraDendriticConnectivityControls2012; @teruiMetapopulationStabilityBranching2018].
-However, most research either has explored the consequences of branching complexity for local community structure[@altermattRiverNetworkProperties2013; @brownDendriticNetworkStructure2010] or relied solely on theoretical arguments[@holtRoleBranchingMaintenance2018].
-At present, we lack a comprehensive evaluation of how branching complexity, in combination with ecosystem size, scales biodiversity at the metacommunity level.
+Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure[@faganConnectivityFragmentationExtinction2002; @grantUseMultipleDispersal2010; @teruiMetapopulationStabilityBranching2018], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@altermattDiversityRiverineMetacommunities2013; @carraraComplexInteractionDendritic2014; @carraraDendriticConnectivityControls2012; @teruiMetapopulationStabilityBranching2018].
+However, most research has explored the consequences of branching complexity for local community structure[@altermattRiverNetworkProperties2013; @brownDendriticNetworkStructure2010] or has relied solely on theoretical arguments with limited replications of branching architecture[@holtRoleBranchingMaintenance2018].
+At present, we lack a comprehensive evaluation of how branching complexity, combined with ecosystem size, scales biodiversity at the metacommunity level.
 Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006].
@@
 We predict that ecosystem size and branching complexity increase $\gamma$ diversity by enhancing either $\alpha$ and/or $\beta$ diversity under different ecological scenarios.
-The present study combines theory and empirical analysis of extensive community data to provide crucial insights into how ecological communities are structured in complex branching networks.
+The present study combines theory and empirical analysis of extensive community data from two different regions of the globe to provide crucial insights into how ecological communities are structured in complex branching networks.
 
 First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
-We constructed a general simulation model of metacommunity dynamics [@thompsonProcessbasedMetacommunityFramework2020], in which 50 competing species disperse and spatially interact in a random branching network.
-Simulated species with different niches in abiotic conditions (optimum and width) compete for resources with varied strengths.
-Here, we depicted branching ecosystems as a spatial network of connected habitat patches (**Figure 1**) where mean environmental conditions at each habitat patch are determined by two factors: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+We depicted branching ecosystems as a spatial network of connected habitat patches (**Figure 1**) where two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
 Environmental values at headwaters are drawn randomly from a normal distribution and propagate downstream with local environmental noise (i.e., a spatial autoregressive process with white noise).
 These environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see Methods).
-Therefore, our simulation resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
-We used `r n_scenario` sets of parameter combinations with varied ecological (dispersal and competition strength) and landscape scenarios (the environmental variation at headwaters and the degree of local environmental noise).
-Under each scenario, we simulated metacommunity dynamics in `r max(dat_sim$n_rep)` branching networks that have different ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`) to examine their effects on species diversity.
+Therefore, our network-generation procedure resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
+We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity framework[@thompsonProcessbasedMetacommunityFramework2020].
+In this model, 50 species with different abiotic niches (optimum and width) disperse along a network and compete for resources with varied strengths in temporally dynamic environments (see Methods for model details).
+
+We considered `r n_scenario` simulation scenarios, which comprised a combination of four landscape and eight ecological scenarios.
+We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`).
+When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation.
+In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on habitat heterogeneity.
+Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity.
+We also considered eight ecological scenarios that differ in dispersal distance, dispersal probability, and the maximum value of interspecific competition strength (Methods).
+Under each simulation scenario, we simulated 1000 time steps of metacommunity dynamics in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
 
@@
 The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios.
-The strength of competition and dispersal processes (dispersal distance and probability) did not change the form of the relationships between $\gamma$ diversity and ecosystem properties (compare panels in **Figures 2 and 3**).
-Hence, the ecosystem size and complexity are both expected to increase $\gamma$ diversity regardless of ecological scenarios.
+The strength of competition and dispersal processes (dispersal distance and probability) did not change the relationships between $\gamma$ diversity and ecosystem properties (compare panels in **Figures 2 and 3**).
+Hence, the ecosystem size and complexity are expected to increase $\gamma$ diversity regardless of ecological scenarios.
 
-Dispersal processes, however, affected mechanisms that underlie the positive effects of ecosystem size and complexity on $\gamma$ diversity (compare left and right columns in **Figures 2 and 3**).
+However, dispersal processes affected mechanisms that underlie the positive effects of ecosystem size and complexity on $\gamma$ diversity (compare left and right columns in **Figures 2 and 3**).
 We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation exists (i.e., species travel short distances).
@@
 The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects)[@thompsonProcessbasedMetacommunityFramework2020].
-These patterns were consistent across different levels of dispersal probabilities (**cite SI figure**).
-The strength of competition decreased maximum levels of $\alpha$ diversity but did not change the functional forms of the scaling relationships with ecosystem properties (**Figures 2 and 3**).
-In summary, our theory highlights how the apparently similar patterns in $\gamma$ diversity emerges through different ecological pathways.
+These patterns were consistent across different levels of dispersal probabilities (**Figures S1 and S8**).
+The strength of competition decreased the maximum of $\alpha$ diversity but did not change the scaling relationships with ecosystem properties (**Figures 2 and 3**).
+In summary, our theory highlights how the apparently similar patterns in $\gamma$ diversity emerge through different ecological pathways.
 
-Influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios (**cite SI Figure**).
-Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**cite SI Figure**).
+Influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios.
+Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2 and S1-7**).
 This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity[@hubbellUnifiedNeutralTheory2001].
 In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$).
-Under this scenario, having more branches may not contribute to the overall habitat diversity in the ecosystem because local environmental noise masks environmental differences between branches (**cite SI Figure**).
-Therefore, this landscape scenario decouples the intimate relationship between branching structure and habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
+Under this scenario, branching may not contribute to the ecosystem's overall habitat diversity because local environmental noise masks environmental differences between branches (**Figures S9-14**).
+Therefore, this landscape scenario decouples the intimate relationship between branching structure and total habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
 This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes[@altermattDiversityRiverineMetacommunities2013; @bendaNetworkDynamicsHypothesis2004; @mooreEmergentStabilityLarge2015; @nakamuraDisturbanceRegimesStream2000; @petersonModellingDendriticEcological2013; @teruiMetapopulationStabilityBranching2018].
 Instead, it may be more relevant to severely altered landscapes where human disturbance compromises the environmental distinctiveness of branches through, for example, flow regulations by dams[@poffHomogenizationRegionalRiver2007].
-Hence, our theory has important implications for riverine biodiversity conservation by pointing the crucial role of habitat diversity produced by branching structure.
+Hence, our theory has important implications for riverine biodiversity conservation by pointing to the crucial role of habitat diversity produced by branching structure.
 
 The proposed theory provided important insights into how ecological communities are structured in branching networks; however, empirically testing the predictions is extremely difficult because it requires metacommunity-level replications.
-To confront this logistical challenge, we compiled existing community data of fishes from a variety of sources and developed a unique large dataset that spans across two geographic regions: the Hokkaido island in Japan and the Midwest in the United States.
+To confront this logistical challenge, we compiled fish community data that span across two geographic regions: the Hokkaido island in Japan and the Midwest in the United States.
 These regions are located in comparable ranges of latitude but support distinct fish communities.
-Therefore, this dataset provides an excellent opportunity to examine the generality of our theoretical predictions.
-After careful data selection, we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; Methods) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
-Individual watersheds, i.e., metacommunity replicates in our analysis, were considered as separated if they flow into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-We combined this dataset with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, and percent forest) to examine potential influences of macro-scale drivers of species diversity.
-Using this dataset, we developed global and region-specific models for each of diversity measures ($\alpha$, $\beta$, and $\gamma$ diversity) to examine whether observed patterns are consistent across the two geographic regions.
+Therefore, this data set provides an excellent opportunity to examine the generality of our theoretical predictions.
+After careful data selection (see Methods and Supporting Information), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; Methods) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
+We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area), or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
+We combined this data set with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, and % forest) to examine potential influences of macro-scale drivers of species diversity.
+Using this data set, we developed global and region-specific models for each of the diversity measures ($\alpha$, $\beta$, and $\gamma$ diversity) to examine whether observed patterns are consistent across the two geographic regions.
 In the global model, we assumed that effects of ecosystem size (watershed area) and complexity (branching probability) are constant across the two regions (i.e., fixed slopes).
-Meanwhile, the region-specific model assumes region-specific slopes of ecosystem size and complexity by including interaction terms with the dummy binary variable of region (Hokkaido = 0; Midwest = 1).
+Meanwhile, the region-specific model assumes region-specific slopes of ecosystem size and complexity by including interaction terms with the dummy binary variable of the region (Hokkaido = 0; Midwest = 1).
 We compared the performance of these competing models using the Bayes factor, a measure of the strength of evidence in favor of one model over the alternative.
@@
 These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, and land use) (**Table 1**).
-Overall, our statistical analysis provides strong empirical evidence that ecosystem size and complexity jointly, but independently, scale riverine biodiversity at the metacommunity level.
+Overall, our statistical analysis provides strong empirical evidence that ecosystem size and complexity jointly scale riverine biodiversity at the metacommunity level.
 
@@
 In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity while $\alpha$ diversity showing a vague response to these ecosystem properties (**Table 1 and Figure 4**).
-In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly match the previous observations of stream fish movement.
-Direct (mark-recapture) and indirect observations (e.g., genotyping) recurrently revealed restricted movement of stream fish, typically limited to several tens to hundreds of meters in distance[@comteFishDispersalFlowing2018; @radingerPatternsPredictorsFish2014; @rodriguezRestrictedMovementStream2002].
+In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly matches the previous observations of stream fish movement.
+Direct (mark-recapture) and indirect observations (e.g., genotyping) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters in distance[@comteFishDispersalFlowing2018; @radingerPatternsPredictorsFish2014; @rodriguezRestrictedMovementStream2002].
 The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
@@
 In support of this interpretation, $\beta$ diversity increased with increasing branching probability in both regions (**Figure 4**).
-It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, still persist in human-dominated landscapes to maintain diversity of in-stream processes among tributaties[@bendaNetworkDynamicsHypothesis2004].
-Although our analysis is correlative and cannot provide conclusive evidence, the finding is encouraging because branching complexity of river networks may serve as a natural defense system to human-induced environmental changes.
+It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, persist in human-dominated landscapes to maintain the diversity of in-stream processes among tributaties[@bendaNetworkDynamicsHypothesis2004].
+Although our analysis is correlative and cannot provide conclusive evidence, the finding is encouraging because the branching complexity of river networks may serve as a natural defense system to human-induced environmental changes.
 
-There may be confounding factors that are not incorporated in our statistical models.
-However, we are confident on our statistical inference because the observed patterns were fairly consistent with our theoretical predictions that are free from any confounding effects.
+There may be confounding factors that are not incorporated into our statistical models.
+However, we are confident in our statistical inference because the observed patterns were fairly consistent with our theoretical predictions that are free from any confounding effects.
 Further, our fitted models generally showed high R^2^ values ($\alpha$ diversity: `r round(summary(fit$alpha$model)$r.squared, 2)`; $\beta$ diversity, `r round(summary(fit$beta$model)$r.squared, 2)`; $\gamma$ diversity `r round(summary(fit$gamma$model)$r.squared, 2)`) with no signs of spatial autocorrelation in residuals.
-Therefore, it is very unlikely that our results were driven by spurious correlations.
+Therefore, it is very unlikely that spurious correlations are responsible for our results.
 
@@
 Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human activities.
-Second, the complexity perspective may provide insights into spatial planning of conservation efforts.
+Second, the complexity perspective may provide insights into the spatial planning of conservation efforts.
 Riverine reserves and local restoration are increasingly recognized as an effective management tool, and how to design a spatial network of conservation sites in rivers is an area of active research[@koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013; @sundermannRiverRestorationSuccess2011].
 While large reserves or restoration sites are undoubtedly important[@koningNetworkGrassrootsReserves2020], our results indicate the potential of coordinated networks of local conservation sites in protecting biodiversity.
-For example, synergies of multiple small reserves may emerge at the watershed scale when multiple ecologically-distinct tributaties are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin[@koningNetworkGrassrootsReserves2020].
+For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin[@koningNetworkGrassrootsReserves2020].
 Our findings, therefore, offer the ecological foundation for the network-based conservation strategies in rivers, broadening viable options towards successful conservation.
@@
 While the prevailing evidence supports the importance of ecosystem size in scaling species diversity, ecosystem complexity - especially branching structure - has not received the attention it deserves.
-Ecosystems are inherently complex in its spatial structure, providing a physical template that creates a wide spectrum of niche opportunities for living organisms.
+Ecosystems are inherently complex in their spatial structure, providing a physical template that creates a wide spectrum of niche opportunities for living organisms.
 Hence, our findings should be broadly applicable to many taxa and ecosystems.
-Generalization of our findings in spatially complex ecosystems represents a frontier for future research.
+The generalization of our findings in spatially complex ecosystems represents a frontier for future research.
 
@@
 
-### Theoretical branching networks
+### Network generation
 
@@
 Habitat patches can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
-Two parameters determine geometric properties of simulated branching networks: the number of habitat patches $N_p$ (ecosystem size) and branching probability $P_b$ (ecosystem complexity).
-Each habitat patch is assigned to be a branching patch (including upstream terminals) with probability $P_b$ or non-branching patch with probability $1-P_b$.
+Two parameters determine the geometric properties of simulated branching networks: the number of habitat patches $N_p$ (ecosystem size) and branching probability $P_b$ (ecosystem complexity).
+Each habitat patch is assigned to be a branching patch (including upstream terminals) with probability $P_b$ or a non-branching patch with probability $1-P_b$.
 In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in a single branch $n_b$ is a realization of a random variable drawn from a geometric distribution $n_{b} \sim Ge(P_{b})$.
@@
 
-The long-term average of abiotic environment $\mu_z$ at each habitat patch is characterized by two sources of variation: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
+Two sources of variation characterize the long-term average of abiotic environment $\mu_z$ at each habitat patch: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
 We draw random values from a normal distribution with a mean of zero and SD of $\sigma_{h}$ and assigned them to headwater patches (i.e., the most upstream patches).
@@
 $$
-where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to upstream watershed area).
-With this expression, larger tributaties have a greater influence on the downstream environment, as observed in natural river networks[@bendaNetworkDynamicsHypothesis2004].
+where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area).
+With this expression, larger tributaries have a greater influence on the downstream environment, as observed in natural river networks[@bendaNetworkDynamicsHypothesis2004].
 
@@
 We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al.[@thompsonProcessbasedMetacommunityFramework2020].
-In this framework, abiotic environmental conditions (density independent), intra- and interspecific competition (density dependent), and dispersal regulate the realized population growth of a species.
-Below, we describe details of our metacommunity model.
+In this framework, abiotic environmental conditions (density-independent), intra- and interspecific competition (density-dependent), and dispersal regulate a species' realized population growth.
+Below, we describe the details of our metacommunity model.
 
@@
 
-where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the interaction coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
+where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
 $K_x$ was expressed as a function of the number of upstream contributing patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area[@altermattRiverNetworkProperties2013; @teruiThreeEcologicalFactors2016].
-The parameter $\alpha_{ij}$ is expressed as the strength of interspecific competition relative to that of intraspecific competition such that interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ > 1 (intraspecific competition coefficient $\alpha_{ii} = 1$).
+The parameter $\alpha_{ij}$ is expressed as the strength of interspecific competition relative to that of intraspecific competition such that interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ > 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
 $\alpha_{ij}$ was drawn randomly from a uniform distribution as $\alpha_{ij} \sim Unif(0, \alpha_{max})$.
@@
 $$
-where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche}$ the niche width of species $i$.
-Species with wider niche (greater values of $\sigma_{niche}$) should always have greater competitive ability in the absence of the cost of wide niche.
-Therefore, we introduced the cost of wide niche by multiplying $c$[@chaianunpornEvolutionaryResponsesClimate2015]:
+where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$.
+Species with a wider niche (greater values of $\sigma_{niche}$) should always have a greater competitive ability in the absence of the cost of a wide niche.
+Therefore, we introduced the cost of a wide niche by multiplying $c$[@chaianunpornEvolutionaryResponsesClimate2015]:
 
@@
 
-Smaller values of $\nu$ imply greater costs of having wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$ near the niche optimum.
+Smaller values of $\nu$ imply greater costs of having a wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$ near the niche optimum.
 
 The environmental value at patch $x$ and time $t$, $z_x(t)$, is assumed to follow a multivariate normal distribution as $z_{x}(t) \sim MVN(\mu_z, \Omega_z)$.
-$\mu_z$ is the vector of mean environmental conditions of patches and $\Omega_z$ is the variance-covariance matrix.
+$\mu_z$ is the vector of mean environmental conditions of patches, and $\Omega_z$ is the variance-covariance matrix.
 Spatial autocorrelation in temporal environmental dynamics is considered by expressing the off-diagonal elements as:
@@
 
-where $\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$.
-The parameter $\phi$ determines the degree of distance decay of environmental correlates.
+$\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$.
+The parameter $\phi$ determines the degree of the distance decay of environmental correlates.
 
@@
 ### Simulation
-We used `r n_scenario` sets of parameter combinations to produce different landscape (four patterns of habitat heterogeneity) and ecological scenarios (eight patterns of dispersal and competition).
-To create landscape scenarios with different patterns of habitat heterogeneity, we varied environmental variation at headwaters ($\sigma_h$) and the degree of local environmental noise ($\sigma_l$) separately.
-Larger values of $\sigma_h$ and/or $\sigma_l$ produce greater variation in environmental conditions among habitat patches.
-We used two values for each of the SD parameters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)` and $\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), resulting in four sets of parameter combinations.
-When $\sigma_h > \sigma_l$, having more tributaries in a network exhibits important effects on overall habitat diversity as branching is the primary source of environmental variation.
-When $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on overall habitat diversity in a network.
+We set four landscape and eight ecological scenarios, resulting in a total of `r n_scenario` sets of parameter combinations.
+For landscape scenarios, we changed values of environmental variation at headwaters ($\sigma_h$) and the degree of local environmental noise ($\sigma_l$) separately to create contrasting patterns of habitat heterogeneity.
+Specifically, we used two values (0.01 and 1) for each of SD parameters.
+When $\sigma_h > \sigma_l$, branching exhibits important effects on habitat heterogeneity in the ecosystem because headwaters are the primary source of environmental variation.
+When $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on habitat heterogeneity in the ecosystem.
 
@@
 We compiled fish data at two biogeographic regions: Hokkaido island, Japan and Midwest, US.
-For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish, monitoring data at protected watersheds, and primary data collected from literature, covering the entire Hokkaido island.
+For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish, monitoring data at protected watersheds, and primary data collected from literature, which collectively cover the entire Hokkaido island.
 For the Midwest, we assembled fish community data collected by Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
-We detailed procedures for initial data selection in SI.
+We detailed procedures for initial data selection in Supporting Information.
 
-We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in watershed area).
-Metacommunities with $\ge$ 10 sampling sites were used in our analysis because small sample size inflates statistical uncertainties in estimating diversity metrics.
+We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
+Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (Supporting Information).
 
-We estimated $\alpha$, $\beta$ and $\gamma$ diversity at each watershed.
+We estimated $\alpha$, $\beta$, and $\gamma$ diversity at each watershed.
 $\gamma$ diversity is the total species richness at each watershed.
 Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness can be interpreted as the estimated true species richness in a given area when it is estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014a; @chaseEcosystemDecayExacerbates2020].
-We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via an R package iNEXT[@hsiehINEXTPackageRarefaction2016].
+Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014a; @chaseEcosystemDecayExacerbates2020].
+We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package iNEXT[@hsiehINEXTPackageRarefaction2016].
 We assessed the completeness of the observed species richness based on sample coverage, which is the proportion of observed species richness to asymptotic species richness.
@@
 After the data selection procedure, we obtained diversity estimates from `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (Hokkaido: `r nrow(wsd_subset[[1]])`, Midwest: `r nrow(wsd_subset[[2]])`), which encompassed a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites (Hokkaido: `r nrow(point_subset[[1]])`, Midwest: `r nrow(point_subset[[2]])`).
-We used this dataset for statistical analysis.
+We used this data set for statistical analysis.
+Fish species observed in our data were listed in **Tables S1 and S2**.
 
@@
 We collected data for watershed characteristics (watershed area and branching probability), climatic variables (annual mean air temperature and cumulative precipitation), and land use (% forest).
-We delineated watershed polygons and river lines (defined as $\ge$ 1 km^2^) using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] with ArcMap 10.7 and SAGA 6.3.0 combined with an R package 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018].
-Watershed area was estimated based on the delineated watershed polygons using functions in an R package 'sf'[@pebesmaSimpleFeaturesStandardized2018].
+We delineated watershed polygons and river lines (defined as $\ge$ 1 km^2^) using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] with ArcMap 10.7 and SAGA 6.3.0 combined with the R package 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018].
+Watershed area was estimated based on the delineated watershed polygons using functions in the R package 'sf'[@pebesmaSimpleFeaturesStandardized2018].
 Branching probability was estimated by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$.
 A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
-For each watershed, we estimated the spatial averages of air temperature and cumulative precipitation at a 1-km resolution, which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005] via R package 'raster'.
-We calculated % forest for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
+We estimated the spatial averages of air temperature and cumulative precipitation at a 1-km resolution for each watershed, which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005] via the R package 'raster.' We calculated % forest for each watershed using land-use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
 
@@
 Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $i$, $log_{10}~y_i$, are assumed to follow a normal distribution as $log_{10}~y_i \sim Normal(\mu_i, \sigma^2)$.
-The parameter $\mu_i$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, and proportion of forest land use (logit-transformed).
-Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to statistically control these effects.
+The parameter $\mu_i$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, and percent of forest land use (logit-transformed).
+Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land-use variables to control these effects statistically.
 
-Climate and land use differed clearly between the regions: therefore, we used residuals of the simple linear regressions between either the climate or land use variable (response variable) and region (explanatory variable) to avoid correlation between explanatory variables.
+Climate and land use differed clearly between the regions.
+Therefore, we used residuals of the simple linear regressions between the climate or land-use variable (response variable) and region (explanatory variable) to avoid correlation between explanatory variables.
 The residuals represent deviations from the regional averages; positive values indicate values greater than the regional average while negative values indicating values smaller than the regional average.
 
-We constructed two models for each of diversity metrics: global and region-specific models.
+We constructed two models for each of the diversity metrics: global and region-specific models.
 The global model assumes that the effects of watershed area and branching probability are consistent across biogeographic regions (i.e., no interactive effects of region with other linear predictors).

### 2021-01-16 supplementary_information.Rmd
Update supplementary_information.Rmd

@@
 
-1. We listed recorded fish species and re-organized species names to be consistent across the data sets.
+1. We listed recorded fish species and re-organized species names to be consistent across the data sets. Species that are identified at the family-level were removed.
 1.
@@
 Although the data set contained observations from 1953, we added this restriction to align the observation period with the data set in the Midwest, US.
-1. Four genera (Lethenteron, Pungitius, Rhinogobius, and Tribolodon) were treated as species groups (i.e., spp.) as taxonomic resolutions varied greatly among data sources.
+1.
+Four genera (Lethenteron, Pungitius, Rhinogobius, and Tribolodon) were treated as species groups (i.e., spp.) as they are difficult to identify and taxonomic resolutions varied greatly among data sources.
 

### 2021-01-20 figures.Rmd
Update figures.Rmd

@@
 ```{r, fig.height=6, fig.width=8, fig.cap="(A) Framework for generating theoretical branching river networks.
-Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example).
+Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N_p$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N_p = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example).
 Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (a spatially autoregressive process with white noise; Methods).
@@
 Red dots indicate sampling sites for fish surveys.
-(C) Map of study regions (left, Midwest, US; right, Hokkaido, Japan).
+(C) Map of study regions (left, Hokkaido, Japan; right, Midwest, US).
 Watersheds (i.e., metacommunities) are gray-shaded in proportion to the number of sampling sites."}

### 2021-01-20 theory/figure_alpha_diversity.R
Create figure_alpha_diversity.R

@@ -1,0 +1,107 @@
+
+# library -----------------------------------------------------------------
+
+  rm(list = ls(all.names = TRUE))
+  pacman::p_load(here, tidyverse, foreach, mcbrnet, doParallel, doSNOW)
+
+
+# parallel setup ----------------------------------------------------------
+
+  cl <- makeCluster(detectCores())
+  registerDoSNOW(cl)
+
+# parameter setup ---------------------------------------------------------
+
+  para <- expand.grid(n_species = 50,
+                      mean_env_source = 0,
+                      sd_env_source = c(0.01, 1),
+                      rho = 1,
+                      asymmetry_factor = 1,
+                      min_optim = -1,
+                      max_optim = 1,
+                      sd_env_lon = c(0.01, 1),
+                      theta = c(0.1, 1),
+                      K0 = 100,
+                      sd_env = 0.1,
+                      spatial_env_cor = TRUE,
+                      phi = 0.05,
+                      min_niche_width = 0.1,
+                      max_niche_width = 1,
+                      niche_cost = 1,
+                      p_dispersal = c(0.01, 0.1),
+                      min_alpha = 0,
+                      max_alpha = c(0.75, 1.5))
+  
+  n_set <- nrow(para)
+  n_rep <- 10
+  n_patch <- 100
+  p_branch <- 0.5
+
+# run simulation ----------------------------------------------------------
+
+  pb <- txtProgressBar(max = n_set, style = 3)
+  fun_progress <- function(n) setTxtProgressBar(pb, n)
+  opts <- list(progress = fun_progress)
+  
+  result <- foreach(x = iter(para, by = 'row'), .combine = "bind_rows",
+                    .packages = c("mcbrnet", "foreach", "dplyr"),
+                    .options.snow = opts) %dopar% {
+                      
+                      # within-parameter replicate
+                      df_set <- foreach(j = seq_len(n_rep), .combine = "bind_rows") %do% {
+                        
+                        ## network generation
+                        net <- brnet(n_patch = n_patch,
+                                     p_branch = p_branch,
+                                     mean_env_source = x$mean_env_source,
+                                     sd_env_source = x$sd_env_source,
+                                     rho = x$rho,
+                                     sd_env_lon = x$sd_env_lon,
+                                     asymmetry_factor = x$asymmetry_factor,
+                                     plot = FALSE)
+                        
+                        K <- x$K0 * net$df_patch$n_patch_upstream
+                        
+                        ## metacommunity simulation                                                 
[…]

### 2021-01-21 supplementary_information.Rmd
Update supplementary_information.Rmd

@@
 
+# Theoretical predictions for longitudinal gradients of local species richness
+
+Local biodiversity patterns have been extensively studied in rivers, illuminating typical patterns observed in nature.
+The most common pattern is a downstream increase of local species richness[@mcdowallDiadromyAssemblyRestoration1996; @mcdowallFightingFlowDownstreamupstream1998; @rahelFishAssemblagesHabitat1991; @teruiThreeEcologicalFactors2016].
+However, recent empirical and theoretical studies also showed 'reversed patterns', in which local species richness decreases downstream[@bsemerHeadwatersAreCritical2013; @harveyDisturbanceReversesClassic2018].
+We predicted the longitudinal gradient of local species richness to confirm that our simulation scenarios are capable of reproducing previously observed patterns of local species richness.
+We considered 32 simulation scenarios comprising four landscape and eight ecological scenarios as described in the maintext (a set of parameters is described in **Table SXX**).
+Under each simulation scenario, we generated 10 replicates of branching networks with fixed parameters of ecosystem size ($N_p = 100$) and complexity ($P_b = 0.5$).
+We evaluated the relationship between local species richness and the number of upstream habitat patches, a proxy for the longitudinal position of a habitat patch.
+
+The simulation reproduced diverse patterns of longitudinal gradients in local species richness (**Figures S1-4**).
+The downstream increase of local species richness was predicted under a natural landscape scenario, in which environmental variation at headwaters $\sigma_h$ exceeds the degree of local environmental noise $\sigma_l$ (**Figure S1**).
+This pattern was consistent across ecological scenarios except those with long dispersal distance and high dispersal probability.
+Similarly, we observed a downstream increase of local species richness in scenarios with low habitat diversity ($\sigma_h = \sigma_l = 0.01$) and low dispersal probability ($p_d = 0.01$) (**Figure S3**).
+However, there were cases where local species richness decreased downstream or showed no longitudinal patterns.
+For example, when local environmental noise exceeds environmental variation at headwaters ($\sigma_l \ge \sigma_h$), local species richness showed a downstream decrease or a vague longitudinal pattern (**Figure S4**).
+Therefore, the simulation scenarios are capable of reproducing previously observed patterns, suggesting the appropriateness in the choice of parameter combinations.
+
 # Fish community data
@@
 
-1. We listed recorded fish species and re-organized species names to be consistent across the data sets. Species that are identified at the family-level were removed.
+1. We listed recorded fish species and re-organized species names to be consistent across data sources. Species that are identified at the family-level were removed.
 1.
@@
 1.
-Four genera (Lethenteron, Pungitius, Rhinogobius, and Tribolodon) were treated as species groups (i.e., spp.) as they are difficult to identify and taxonomic resolutions varied greatly among data sources.
+Four genera (*Lethenteron*, *Pungitius*, *Rhinogobius*, and *Tribolodon*) were treated as species groups (i.e., spp.) as they are difficult to identify and taxonomic resolutions varied greatly among data sources.
 
@@
 
-## Table S1 List of fish species in Hokkaido, Japan
+## Table SXX List of fish species in Hokkaido, Japan
 
@@
 
-## Table S2 List of fish species in Midwest, US
+## Table SXX List of fish species in Midwest, US
 
@@
 
-```{r chunk_fig1}
+```{r chunk_fig_set1}
+
+source(here::here("/theory/figure_alpha_pattern.R"))
+
+figure_cap <- conditional_text <- NULL
+
+for(i in seq_len(nrow(param))){
+  if(param$sigma_h[i] > param$sigma_l[i]){
+    conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) exceeds local environmental noise ($\\sigma_{l}$)."
+  }else{
+    if(param$sigma_h[i] == param$sigma_l[i]){
+      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is equal to local environmental noise ($\\sigma_{l}$)."
+    }else{
+      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is less than local environmental noise ($\\sigma_{l}$)."
+    }
+  }
+
+  figure_cap[i] <- paste0("Theoretical predictions for longitudinal gradients of local species richness in branching networks.
+The longitudinal position of each habitat patch (x axis) was expressed as the number of upstream contributing patches.
+`r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
+Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
+Rows represent different competition strength.
+Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
+Columns and lines represent different dispersal scenarios (dispersal distance and probability).
+Left and right columns show long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$) scenarios repectively.
+Red and blue lines show low ($p_d = 0.01$) and high dispersal probabilities ($p_d = 0.10$).
+Other parameters are as follows: environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$; ecosystem size $N_{p} = 100$; ecosystem complexity $P_{b} = 0.5$.")
+}
+
+figure_alpha_pattern <- NULL
+for(i in seq_len(nrow(param))){
+  j <- i
+  knit_chunk <- paste0("## Figure S", j, " Longitudinal gradient of local species richness ($\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
+                       "\n```{r fig", j,", fig.width = 8, fig.height = 6}\n\n h[[",i,"]] \n\n```\n",
+                       "\n **Figure S", j, "** ", figure_cap[i], "\n\\pagebreak\n")
+  figure_alpha_pattern <- c(figure_alpha_pattern, knit_chunk)
+}
+
+```
+
+`r paste(knit(text = figure_alpha_pattern), collapse = '\n')`
+
+```{r chunk_fig_set2}
 
@@
   figure_cap[i] <- paste0("Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
-`r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals.
+`r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
 Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
@@
 for(i in seq_len(nrow(param))){
-  knit_chunk <- paste0("## Figure S", i, " Influence of ecosystem size ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
-                       "\n```{r fig", i,", fig.width = 8, fig.height = 6}\n\n f[[",i,"]] \n\n```\n",
-                       "\n **Figure S", i, "** ", figure_cap[i], "\n\\pagebreak\n")
+  j <- i + 4
+  knit_chunk <- paste0("## Figure S", j, " Influence of ecosystem size ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
+                       "\n```{r fig", j,", fig.width = 8, fig.height = 6}\n\n f[[",i,"]] \n\n```\n",
+                       "\n **Figure S", j, "** ", figure_cap[i], "\n\\pagebreak\n")
   figure_size <- c(figure_size, knit_chunk)
@@
 
-```{r chunk_fig2}
+```{r chunk_fig_set3}
 
@@
   figure_cap[i] <- paste0("Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
-`r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals.
+`r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
 Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
@@
 for(i in seq_len(nrow(param))){
-  j <- i + 7
+  j <- i + 11
   knit_chunk <- paste0("## Figure S", j, " Influence of ecosystem complexity ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 

### 2021-01-21 manuscript.Rmd
Update manuscript.Rmd

@@
 Ecosystem size and complexity increased watershed-scale species richness ($\gamma$ diversity), and the importance of spatial turnover in species composition ($\beta$ diversity) was apparent when simulated species dispersal is limited.
-Cross-watershed comparisons across two biogeographic regions (Hokkaido, Japan and Midwest, US) provided empirical support for the theoretical predictions.
+Cross-watershed comparisons across two biogeographic regions (the Hokkaido island in Japan and the midwestern US) provided empirical support for the theoretical predictions.
 In both regions, watershed-scale species richness increased with ecosystem size (watershed area) and complexity (branching probability) through enhanced spatial turnover in species composition over the branching network.
@@
 
+# for bayes factor
 source(here::here('/empirical/analysis_lm_bf.R'))
+
+# Hokkaido data
+dat_hkd_site <- read_csv(here::here('/empirical/data_out/dat_hkd_site.csv'))
+
+# Midwest data
+dat_mw_site <- read_csv(here::here('/empirical/data_out/dat_mw_site.csv')) %>% 
+  mutate(Year = format(as.Date(Date, format = '%m/%d/%Y'), "%Y"))
 
@@
 However, most research has explored the consequences of branching complexity for local community structure[@altermattRiverNetworkProperties2013; @brownDendriticNetworkStructure2010] or has relied solely on theoretical arguments with limited replications of branching architecture[@holtRoleBranchingMaintenance2018].
-At present, we lack a comprehensive evaluation of how branching complexity, combined with ecosystem size, scales biodiversity at the metacommunity level.
+At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
 Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006].
@@
 First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
-We depicted branching ecosystems as a spatial network of connected habitat patches (**Figure 1**) where two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+We depicted branching ecosystems as a spatial network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**) where two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
 Environmental values at headwaters are drawn randomly from a normal distribution and propagate downstream with local environmental noise (i.e., a spatial autoregressive process with white noise).
@@
 In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on habitat heterogeneity.
-Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity.
-We also considered eight ecological scenarios that differ in dispersal distance, dispersal probability, and the maximum value of interspecific competition strength (Methods).
+Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity withing a network.
+We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel), dispersal probability, and the maximum value of interspecific competition strength (see Methods).
+Our simulation scenarios were capable of reproducing common spatial patterns of local species richness, corroborating the appropriateness of our choice in parameter combinations (Supplementary Information).
 Under each simulation scenario, we simulated 1000 time steps of metacommunity dynamics in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
@@
 The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects)[@thompsonProcessbasedMetacommunityFramework2020].
-These patterns were consistent across different levels of dispersal probabilities (**Figures S1 and S8**).
+These patterns were consistent across different levels of dispersal probabilities (**Figures S5 and S12**).
 The strength of competition decreased the maximum of $\alpha$ diversity but did not change the scaling relationships with ecosystem properties (**Figures 2 and 3**).
@@
 Influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios.
-Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2 and S1-7**).
+Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2 and S5-11**).
 This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity[@hubbellUnifiedNeutralTheory2001].
-In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$).
-Under this scenario, branching may not contribute to the ecosystem's overall habitat diversity because local environmental noise masks environmental differences between branches (**Figures S9-14**).
+In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$; **Figures S13-18**).
+Under this scenario, branching may not contribute to the ecosystem's overall habitat diversity because local environmental noise masks environmental differences between branches.
 Therefore, this landscape scenario decouples the intimate relationship between branching structure and total habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
@@
 The proposed theory provided important insights into how ecological communities are structured in branching networks; however, empirically testing the predictions is extremely difficult because it requires metacommunity-level replications.
-To confront this logistical challenge, we compiled fish community data that span across two geographic regions: the Hokkaido island in Japan and the Midwest in the United States.
-These regions are located in comparable ranges of latitude but support distinct fish communities.
+To confront this logistical challenge, we compiled fish community data that span across two geographic regions: the Hokkaido island in Japan and the midwestern US (Midwest).
+These regions are located in comparable ranges of latitude but support distinct fish communities (**Figure 1**).
 Therefore, this data set provides an excellent opportunity to examine the generality of our theoretical predictions.
-After careful data selection (see Methods and Supporting Information), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; Methods) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
-We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area), or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
+After careful data selection (see Methods and Supplementary Information), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; Methods) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in the Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
+We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area), or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
 We combined this data set with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, and % forest) to examine potential influences of macro-scale drivers of species diversity.
@@
 
-The consistent effect of branching probability on $\gamma$ diversity across the study regions is noteworthy because the watersheds in the Midwest are severely altered by agriculture (median % agricultural land use: `r round(median(wsd_subset[[2]]$frac_agri)*100)`% for Midwest and `r round(median(wsd_subset[[1]]$frac_agri)*100)`% for Hokkaido).
+The consistent effect of branching probability on $\gamma$ diversity across the study regions is noteworthy because the watersheds in the Midwest are severely altered by agriculture (median % agricultural land use: `r round(median(wsd_subset[[2]]$frac_agri)*100)`% in the Midwest and `r round(median(wsd_subset[[1]]$frac_agri)*100)`% in Hokkaido).
 If the intensive land use by humans causes significant homogenization of in-stream habitat conditions among tributaries, theory predicts weakened effects of branching probability on $\gamma$ diversity.
@@
 
-We depicted branching ecosystems as a spatial network of connected habitat patches.
+We depicted branching ecosystems as a spatial network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a].
 Habitat patches can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
@@
 $$
-r_{ix}(t) = cr_{0,i}~exp[{-\frac{(\mu_i-z_x(t))^2}{2\sigma^2_{niche,i}}}]
+r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{(\mu_i-z_x(t))^2}{2\sigma^2_{niche,i}}}]
 $$
@@
 Species with a wider niche (greater values of $\sigma_{niche}$) should always have a greater competitive ability in the absence of the cost of a wide niche.
-Therefore, we introduced the cost of a wide niche by multiplying $c$[@chaianunpornEvolutionaryResponsesClimate2015]:
+Therefore, we introduced the cost of a wide niche by multiplying $\delta$[@chaianunpornEvolutionaryResponsesClimate2015]:
 
 $$
-c = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
+\delta = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
 $$
@@
 
+Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 200 time steps for initialization and 200 time steps for burn-in) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
+During the first 200 time steps (an initialization period), we initialized the simulation by seeding each habitat patch with populations of each species drawn from a Poisson distribution with a mean of 0.5.
+We repeated the seeding every 10 time steps during the initialization to allow species to establish their populations if they can grow from low abundances.
+After the initialization period, we ran 200 time steps as a burn-in period with no seeding to minimize influences of initial conditions.
+We saved the last 1000 time steps to estimate the temporal averages of $\alpha$, $\beta$, and $\gamma$ diversity.
+We removed simulation replicates in which no species establish populations over the initial 400 time steps (`r sum(dat_sim$alpha_div == 0)` replicates out of `r nrow(dat_sim)` replicates).
+Ecosystem size and complexity were drawn randomly from uniform distributions as: $N_p \sim Unif(10, 150)$ and $P_b \sim Unif(0.01, 0.99)$ ($N_p$ was rounded to the nearest integer before running simulations).
+
 ## Empirical data analysis
@@
 
-We compiled fish data at two biogeographic regions: Hokkaido island, Japan and Midwest, US.
+We compiled fish data at two biogeographic regions: the Hokkaido island, Japan and the Midwest, US.
 For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish, monitoring data at protected watersheds, and primary data collected from literature, which collectively cover the entire Hokkaido island.
 For the Midwest, we assembled fish community data collected by Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
-We detailed procedures for initial data selection in Supporting Information.
+We detailed procedures for initial data selection in Supplementary Information.
 
-We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (Supporting Information).
+We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
+Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (Supplementary Information).
 
@@
 After the data selection procedure, we obtained diversity estimates from `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (Hokkaido: `r nrow(wsd_subset[[1]])`, Midwest: `r nrow(wsd_subset[[2]])`), which encompassed a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites (Hokkaido: `r nrow(point_subset[[1]])`, Midwest: `r nrow(point_subset[[2]])`).
-We used this data set for statistical analysis.
-Fish species observed in our data were listed in **Tables S1 and S2**.
+Observations ranged from `r min(dat_hkd_site$Year, na.rm = T)` to `r max(dat_hkd_site$Year, na.rm = T)` in Hokkaido and from `r min(dat_mw_site$Year, na.rm = T)` to `r max(dat_mw_site$Year, na.rm = T)` in the Midwest.
+Fish species observed in the final data set were listed in **Tables S2 and S3**.
 

### 2021-01-22 manuscript.Rmd
Update manuscript.Rmd

@@
 Ecosystem complexity, which we defined as the probability of branching per unit river distance, should increase watershed-scale species richness by increasing habitat heterogeneity (habitat diversity per unit area).
-Meanwhile, ecosystem size should dictate metacommunity size and total habitat diversity (area x habitat heterogeneity), two primary factors that regulate watershed-scale species richness.
+Meanwhile, ecosystem size should dictate metacommunity size and total habitat diversity (area x habitat heterogeneity) that regulate watershed-scale species richness.
 We developed theoretical models simulating metacommunity dynamics in branching river networks and yielded results consistent with our hypothesis.
@@
 One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR)[@lomolinoEcologyMostGeneral2000a].
-In 1921, Arrhenius[@arrheniusSpeciesArea1921] formulated the SAR as a power-law $S = cA^z$ ($S$ is the number of species observed in a given geographic area $A$, $c$ a constant, and $z$ a scaling exponent), an equation currently known as the Arrhenius species-area relationship.
+In 1921, Arrhenius[@arrheniusSpeciesArea1921] formulated the SAR as a power-law $S = cA^z$, an equation currently known as the Arrhenius species-area relationship ($S$ is the number of species observed in a given geographic area $A$, $c$ the constant, and $z$ the scaling exponent).
 Since then, the spatial scaling of species richness has been observed in many taxonomic groups[@triantisIslandSpeciesArea2012].
@@
 At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
-Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006].
+Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006a].
 
@@
 The recurrent merging of diverse streams and rivers produces larger, ecologically distinct channels, ultimately forming a fluvial network with fractal branching patterns[@rodriguez-iturbeFractalRiverBasins2001].
-As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a], should control the habitat heterogeneity of the ecosystem (habitat diversity per unit area).
+As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], should control the ecosystem's habitat heterogeneity (habitat diversity per unit area).
 Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity).
-We predict that ecosystem size and branching complexity increase $\gamma$ diversity by enhancing either $\alpha$ and/or $\beta$ diversity under different ecological scenarios.
+We predict that ecosystem size and branching complexity increase watershed-scale species richness ($\gamma$ diversity) by enhancing local species richness ($\alpha$ diversity) and/or spatial turnover of species composition ($\beta$ diversity) under different ecological scenarios.
 The present study combines theory and empirical analysis of extensive community data from two different regions of the globe to provide crucial insights into how ecological communities are structured in complex branching networks.
@@
 First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
-We depicted branching ecosystems as a spatial network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**) where two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+We depicted branching ecosystems as a spatial network of connected habitat patches or local communities[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**) where two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
 Environmental values at headwaters are drawn randomly from a normal distribution and propagate downstream with local environmental noise (i.e., a spatial autoregressive process with white noise).
@@
 We considered `r n_scenario` simulation scenarios, which comprised a combination of four landscape and eight ecological scenarios.
-We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`).
+We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), both of which are defined as standard deviations of normal distributions.
 When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation.
@@
 We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel), dispersal probability, and the maximum value of interspecific competition strength (see Methods).
-Our simulation scenarios were capable of reproducing common spatial patterns of local species richness, corroborating the appropriateness of our choice in parameter combinations (Supplementary Information).
+These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (Supplementary Information).
 Under each simulation scenario, we simulated 1000 time steps of metacommunity dynamics in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
@@
 
-We depicted branching ecosystems as a spatial network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a].
-Habitat patches can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
+We depicted branching ecosystems as a bifurcating spatial network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**).
+Habitat patches, or local communities, can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
 Two parameters determine the geometric properties of simulated branching networks: the number of habitat patches $N_p$ (ecosystem size) and branching probability $P_b$ (ecosystem complexity).
 Each habitat patch is assigned to be a branching patch (including upstream terminals) with probability $P_b$ or a non-branching patch with probability $1-P_b$.
-In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in a single branch $n_b$ is a realization of a random variable drawn from a geometric distribution $n_{b} \sim Ge(P_{b})$.
-This representation has two merits.
-First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution).
+In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in branch $q$, $n_{p,q}$, is a realization of a random variable drawn from a geometric distribution $n_{p,q} \sim Ge(P_{b})$[@teruiMetapopulationStabilityBranching2018] but conditional on $\sum_{q=1}^{N_b}n_{p,q} = N_p$ ($N_b$ is the number of branches in a network).
+The number of branches $N_b$ is identical to the number of branching habitat patches in a network, or the number of 'success' out of $N_p$ trials.
+This leads to an assumption that $N_b$ is a realization of a random variable drawn from a binomial distribution as $N_b \sim Binomial(N_p, P_b)$.
+This framework has two merits.
+First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution)[@rodriguez-iturbeFractalRiverBasins2001].
 Second, it preserves the fractal nature of branching patterns[@peckhamReformulationHortonLaws1999].
 
-Two sources of variation characterize the long-term average of abiotic environment $\mu_z$ at each habitat patch: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
+In our network generation, we first drew $N_b$ from the binomial distribution but selected an odd number to constitute a bifurcating branching network.
+We then determined $n_{p,q}$ as random draws from the geometric distribution with the constraint of $\sum_{q=1}^{N_b}n_{p,q} = N_p$.
+The generated branches were organized randomly into a bifurcating branching network.
+
+Two sources of variation characterize the long-term average of abiotic environment at each habitat patch: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
 We draw random values from a normal distribution with a mean of zero and SD of $\sigma_{h}$ and assigned them to headwater patches (i.e., the most upstream patches).
@@
 
-where $\mu_{z,k}$ is the environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and SD of $\sigma_l$.
+where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and SD of $\sigma_l$.
 The parameter $\rho$ can take values of $0-1$ with larger values indicating greater spatial autocorrelation.
@@
 where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area).
+The parameter $\omega$ takes values of $0-1$ and represents the relative influence of the right tributary given the relative size of joining tributaries.
 With this expression, larger tributaries have a greater influence on the downstream environment, as observed in natural river networks[@bendaNetworkDynamicsHypothesis2004].
@@
 The environmental value at patch $x$ and time $t$, $z_x(t)$, is assumed to follow a multivariate normal distribution as $z_{x}(t) \sim MVN(\mu_z, \Omega_z)$.
-$\mu_z$ is the vector of mean environmental conditions of patches, and $\Omega_z$ is the variance-covariance matrix.
+$\mu_z$ is the vector of mean environmental conditions of habitat patches, and $\Omega_z$ is the variance-covariance matrix.
 Spatial autocorrelation in temporal environmental dynamics is considered by expressing the off-diagonal elements as:
@@
 We allowed interspecific variation in niche optimum and width, which were drawn from uniform distributions as $\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$.
-We used fixed values for the following parameters: maximum reproductive number ($r_{0,i} =$ 4), niche cost ($\nu =$ `r unique(dat_sim$niche_cost)`), the degree of temporal fluctuation in abiotic environments ($\sigma_z =$ `r unique(dat_sim$sd_env)`), and the degree of spatial autocorrelation in temporal environmental dynamics ($\phi =$ `r unique(dat_sim$phi)`).
+We used fixed values for the following parameters: maximum reproductive rate ($r_{0,i} =$ 4), niche cost ($\nu =$ `r unique(dat_sim$niche_cost)`), the degree of temporal fluctuation in abiotic environments ($\sigma_z =$ `r unique(dat_sim$sd_env)`), and the degree of spatial autocorrelation in temporal environmental dynamics ($\phi =$ `r unique(dat_sim$phi)`).
 
@@
 We saved the last 1000 time steps to estimate the temporal averages of $\alpha$, $\beta$, and $\gamma$ diversity.
-We removed simulation replicates in which no species establish populations over the initial 400 time steps (`r sum(dat_sim$alpha_div == 0)` replicates out of `r nrow(dat_sim)` replicates).
+We removed simulation replicates in which no species established populations over the initial 400 time steps (`r sum(dat_sim$alpha_div == 0)` replicates out of `r nrow(dat_sim)` replicates).
 Ecosystem size and complexity were drawn randomly from uniform distributions as: $N_p \sim Unif(10, 150)$ and $P_b \sim Unif(0.01, 0.99)$ ($N_p$ was rounded to the nearest integer before running simulations).
@@
 We compiled fish data at two biogeographic regions: the Hokkaido island, Japan and the Midwest, US.
-For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish, monitoring data at protected watersheds, and primary data collected from literature, which collectively cover the entire Hokkaido island.
+For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaHokkaidoFreshwaterFish2011; @fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors[@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island.
 For the Midwest, we assembled fish community data collected by Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
@@
 Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014a; @chaseEcosystemDecayExacerbates2020].
+Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014; @chaseEcosystemDecayExacerbates2020].
 We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package iNEXT[@hsiehINEXTPackageRarefaction2016].
@@
 A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
-We estimated the spatial averages of air temperature and cumulative precipitation at a 1-km resolution for each watershed, which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005] via the R package 'raster.' We calculated % forest for each watershed using land-use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
+We estimated the spatial averages of air temperature and cumulative precipitation at a 1-km resolution for each watershed, which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005] via the R package 'raster.' We calculated % forest for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
 
@@
 The parameter $\mu_i$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, and percent of forest land use (logit-transformed).
-Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land-use variables to control these effects statistically.
+Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control these effects statistically.
 
 Climate and land use differed clearly between the regions.
-Therefore, we used residuals of the simple linear regressions between the climate or land-use variable (response variable) and region (explanatory variable) to avoid correlation between explanatory variables.
+Therefore, we used residuals of the simple linear regressions between the climate or land use variable (response variable) and region (explanatory variable) to avoid correlation between explanatory variables.
 The residuals represent deviations from the regional averages; positive values indicate values greater than the regional average while negative values indicating values smaller than the regional average.

### 2021-01-22 supplementary_information.Rmd
Update supplementary_information.Rmd

@@
 
+# simulation data
+dat_sim <- read_csv(here::here('/theory/result/result_sim2020-11-10.csv'))
+
 # Hokkaido data
@@
 
-# Theoretical predictions for longitudinal gradients of local species richness
+# Sensitivity analysis
 
-Local biodiversity patterns have been extensively studied in rivers, illuminating typical patterns observed in nature.
+# Longitudinal gradients of local species richness
+
+Longitudinal gradients of local species richness have been extensively studied in rivers, illuminating typical patterns observed in nature.
 The most common pattern is a downstream increase of local species richness[@mcdowallDiadromyAssemblyRestoration1996; @mcdowallFightingFlowDownstreamupstream1998; @rahelFishAssemblagesHabitat1991; @teruiThreeEcologicalFactors2016].
@@
 # Tables
+
+## Table S1 Simulation parameter
+
+Values and interpretation of parameters used in our simulation model. Refer to the maintext for model details.
+
+```{r}
+
+dat_sim %>% 
+  select(sd_env_source,
+         sd_env_lon,
+         sd_env,
+         rho,
+         phi,
+         niche_cost,
+         max_alpha,
+         theta,
+         p_dispersal
+         ) %>% 
+  summarise(across(everything(), unique)) %>% 
+  mutate(r0 = 4) %>% 
+  pivot_longer(cols = everything(),
+               names_to = "Parameter",
+               values_to = "Value") %>% 
+  group_by(Parameter) %>% 
+  summarize(Value = list(unique(Value))) %>% 
+  mutate(id = case_when(Parameter == 'sd_env_source' ~ 'a',
+                        Parameter == 'sd_env_lon' ~ 'b',
+                        Parameter == 'sd_env' ~ 'c',
+                        Parameter == 'rho' ~ 'd',
+                        Parameter == 'phi' ~ 'e',
+                        Parameter == 'niche_cost' ~ 'f',
+                        Parameter == 'max_alpha' ~ 'g',
+                        Parameter == 'theta' ~ 'h',
+                        Parameter == 'p_dispersal' ~ 'i',
+                        Parameter == 'r0' ~ 'j',
+                        TRUE ~ as.character(Parameter)),
+         Interpretation = case_when(Parameter == 'sd_env_source' ~ 'Environmental variation at headwaters',
+                                    Parameter == 'sd_env_lon' ~ 'Degree of local environmental noise',
+                                    Parameter == 'sd_env' ~ 'Temporal environmental variability',
+                                    Parameter == 'rho' ~ 'Strength of spatial autocorrelation in mean environmental condition',
+                                    Parameter == 'phi' ~ 'Extent of spatial autocorrelation in temporal environmental variation',
+                                    Parameter == 'niche_cost' ~ 'Cost of a wider niche',
+                                    Parameter == 'max_alpha' ~ 'Maximum value of interspecific competition coefficient',
+                                    Parameter == 'theta' ~ 'Rate parameter of an exponential dispersal kernel',
+                                    Parameter == 'p_dispersal' ~ 'Dispersal probability',
+                                    Parameter == 'r0' ~ 'Maxiumum reproductive rate',
+                                    TRUE ~ as.character(Parameter)),
+         Parameter = case_when(Parameter == 'sd_env_source' ~ '$\\sigma_{h}$',
+                               Parameter == 'sd_env_lon' ~ '$\\sigma_{l}$',
+                               Parameter == 'sd_env' ~ '$\\sigma_{z}$',
+                               Parameter == 'rho' ~ '$\\rho$',
+                               Parameter == 'phi' ~ '$\\phi$',
+                               Parameter == 'niche_cost' ~ '$\\nu$',
+                               Parameter == 'max_alpha' ~ '$\\alpha_{max}$',
+                               Parameter == 'theta' ~ '$\\theta$',
+                               Parameter == 'p_dispersal' ~ '$p_{d}$',
+                               Parameter == 'r0' ~ '$r_{0,i}$',
+                               TRUE ~ as.character(Parameter))
+         ) %>% 
+  arrange(id) %>% 
+  select(-id) %>% 
+  kable(format = 'markdown')
+
+```
+
+\newpage
 

### 2021-01-22 theory/run_simulation.R
Update run_simulation.R

@@ -15,11 +15,11 @@
   para <- expand.grid(n_species = 50,
                       mean_env_source = 0,
                       sd_env_source = c(0.01, 1),
+                      sd_env_lon = c(0.01, 1),
                       rho = 1,
                       asymmetry_factor = 1,
                       min_optim = -1,
                       max_optim = 1,
-                      sd_env_lon = c(0.01, 1),
                       theta = c(0.1, 1),
                       K0 = 100,
                       sd_env = 0.1,

### 2021-01-25 supplementary_information.Rmd
Update supplementary_information.Rmd

@@
 
-# simulation data
+  # simulation data main
   dat_sim <- read_csv(here::here('/theory/result/result_sim2020-11-10.csv'))
+
+  # sensitivity analysis  
+  source(here::here("/theory/analysis_sensitivity.R"))
 
@@
 
+  # sensitivity tables
+
+  ## ecosystem size
+  m_area <- fit_sense %>% 
+    mutate(area = str_detect(response, "area")) %>% 
+    filter(area == TRUE)
+
+  star_area <- stargazer::stargazer(m_area$fit[1],
+                                    m_area$fit[2],
+                                    m_area$fit[3],
+                                    header = FALSE,
+                                    type = "latex",
+                                    covariate.labels = c("$\\sigma_{h}$",
+                                                         "$\\sigma_{l}$",
+                                                         "$\\sigma_{z}$",
+                                                         "$\\phi$",
+                                                         "$\\nu$",
+                                                         "$\\alpha_{max}$",
+                                                         "$\\theta$",
+                                                         "$p_{d}$",
+                                                         "Intercept"),
+                                    single.row = FALSE,
+                                    digits = 3,
+                                    dep.var.labels.include = FALSE,
+                                    column.labels = c("Effect of $N_{p}$ on $\\alpha$ diversity",
+                                                      "Effect of $N_{p}$ on $\\beta$ diversity",
+                                                      "Effect of $N_{p}$ on $\\gamma$ diversity"),
+                                    keep.stat = c("rsq"),
+                                    model.numbers = FALSE)
+
+  star_area <- sub('^.+\\caption.+$','', star_area)
+
+  ## Ecosystem complexity
+  m_bp <- fit_sense %>% 
+    mutate(area = str_detect(response, "area")) %>% 
+    filter(area == FALSE)
+
+  star_bp <- stargazer::stargazer(m_bp$fit[1],
+                                  m_bp$fit[2],
+                                  m_bp$fit[3],
+                                  header = FALSE,
+                                  type = "latex",
+                                  covariate.labels = c("$\\sigma_{h}$",
+                                                       "$\\sigma_{l}$",
+                                                       "$\\sigma_{z}$",
+                                                       "$\\phi$",
+                                                       "$\\nu$",
+                                                       "$\\alpha_{max}$",
+                                                       "$\\theta$",
+                                                       "$p_{d}$",
+                                                       "Intercept"),
+                                  single.row = FALSE,
+                                  digits = 3,
+                                  dep.var.labels.include = FALSE,
+                                  column.labels = c("Effect of $P_{b}$ on $\\alpha$ diversity",
+                                                    "Effect of $P_{b}$ on $\\beta$ diversity",
+                                                    "Effect of $P_{b}$ on $\\gamma$ diversity"),
+                                  keep.stat = c("rsq"),
+                                  model.numbers = FALSE)
+
+    star_bp <- sub('^.+\\caption.+$','', star_bp)
+
 ```
 
-# Sensitivity analysis
+# Theory
 
-# Longitudinal gradients of local species richness
+## Sensitivity analysis
+
+We performed a sensitivity analysis of the metacommunity simulation to identify key simulation parameters that strongly affect the relationships between diversity metrics ($\alpha$, $\beta$, and $\gamma$) and ecosystem properties (the number of habitat patches $N_{p}$ and branching probability $P_{b}$).
+We generated 500 sets of parameter combinations by randomly drawing values of 8 simulation parameters from uniform distributions (**Table S1**).
+For each parameter combination, we generated 100 branching networks with the gradients of ecosystem size ($N_p \sim Unif(10, 150)$) and complexity ($P_b \sim Unif(0.01, 0.99)$).
+This results in a total of 50000 simulation replicates.
+In each simulation replicate, we allowed interspecific variation in niche optimum $\mu_i$ and width $\sigma_{niche,i}$ ($\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$, respectively; subscript $i$ represents species) and ran 1400 time steps of metacommunity dynamics.
+We obtained temporal means of $\alpha$, $\beta$, and $\gamma$ diversity for the last 1000 time steps.
+The first 400 time steps were discarded as initialization and burn-in periods.
+
+For each parameter combination, we regressed log-transformed $\alpha$, $\beta$, and $\gamma$ diversity ($log_{10}~y_j$ for network replicate $j$) on the number of habitat patches $N_{p}$ and branching probability $P_{b}$ as:
+
+$$
+\begin{aligned}
+log_{10}~y_j &\sim Normal(\mu_j, \sigma^2)\\
+       \mu_j &= \psi_0 + \psi_1~log_{10}~N_{p,j} + \psi_2~log_{10}~P_{b,j}
+\end{aligned}
+$$
+
+where $\psi_q$ ($q = 0-2$) are the intercept ($\psi_0$) and regression coefficients ($\psi_1$ and $\psi_2$).
+We extracted 500 estimates of $\psi_1$ and $\psi_2$, which represent the effects of $N_{p}$ and $P_{b}$ on diversity metrics under a given parameter combination.
+To examine influences of simulation parameters (**Table S1**) on $\psi_1$ and $\psi_2$, we developed the following regression model taking $\psi_1$ or $\psi_2$ as a dependent variable $u_k$ (parameter combination $k$):
+
+$$
+\begin{aligned}
+u_{k} &\sim Normal(\mu_k, \sigma^2)\\
+\mu_k &= \zeta_0 + \zeta_1 \sigma_{h,k} + \zeta_2 \sigma_{l,k} + \zeta_3 \sigma_{z,k} + \zeta_4 \phi_k + \zeta_5 \nu_k + \zeta_6 \alpha_{max, k} + \zeta_7 \theta_k + \zeta_8 p_{d,k} 
+\end{aligned}
+$$
+where $\zeta_q$ ($q = 0-8$) are the intercept and regression coefficients.
+Explanatory variables were standardized to a mean of zero and a standard deviation of one, so that regression coefficients are comparable.
+
+The sensitivity analysis revealed key simulation parameters.
+For the effects of $N_p$, the following simulation parameters were influential: the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\gamma$ diversity), the maximum value of interspecific competition coefficient ($\alpha_{max}$; influenced the effects on $\alpha$, $\beta$, and $\gamma$ diversity), dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal probability ($p_d$; influenced the effect on $\alpha$ diversity) (**Table S3**).
+For the effects of $P_b$, the following simulation parameters were influential: environmental variation at headwaters ($\sigma_h$; influenced the effect on $\gamma$ diversity), the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity) (**Table S4**).
+
+Based on the results, we identified $\sigma_h$, $\sigma_l$, $\alpha_{max}$, $\theta$, and $p_d$ as key parameters.
+We changed the values of these parameters in the main analysis and examined the relationships between diversity metrics and ecosystem properties.
+
+## Longitudinal gradients of local species richness
 
@@
 The most common pattern is a downstream increase of local species richness[@mcdowallDiadromyAssemblyRestoration1996; @mcdowallFightingFlowDownstreamupstream1998; @rahelFishAssemblagesHabitat1991; @teruiThreeEcologicalFactors2016].
-However, recent empirical and theoretical studies also showed 'reversed patterns', in which local species richness decreases downstream[@bsemerHeadwatersAreCritical2013; @harveyDisturbanceReversesClassic2018].
-We predicted the longitudinal gradient of local species richness to confirm that our simulation scenarios are capable of reproducing previously observed patterns of local species richness.
-We considered 32 simulation scenarios comprising four landscape and eight ecological scenarios as described in the maintext (a set of parameters is described in **Table SXX**).
-Under each simulation scenario, we generated 10 replicates of branching networks with fixed parameters of ecosystem size ($N_p = 100$) and complexity ($P_b = 0.5$).
+However, recent empirical and theoretical studies also showed 'reversed patterns,' in which local species richness decreases downstream[@bsemerHeadwatersAreCritical2013; @harveyDisturbanceReversesClassic2018].
+We predicted the longitudinal gradient of local species richness to confirm that our simulation scenarios are capable of reproducing the previously observed patterns of local species richness.
+We considered 32 simulation scenarios comprising four landscape and eight ecological scenarios, as described in the main text (a set of parameters is described in **Table S2**).
+Under each simulation scenario, we generated 10 branching networks with fixed parameters of ecosystem size ($N_p = 100$) and complexity ($P_b = 0.5$).
+This results in a total of 320 simulation replicates.
+In each simulation replicate, we allowed interspecific variation in niche optimum $\mu_i$ and width $\sigma_{niche,i}$ ($\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$, respectively; subscript $i$ represents species) and ran 1400 time steps of metacommunity dynamics.
+We obtained temporal means of local species richness at each habitat patch for the last 1000 time steps.
+The first 400 time steps were discarded as initialization and burn-in periods.
 We evaluated the relationship between local species richness and the number of upstream habitat patches, a proxy for the longitudinal position of a habitat patch.
@@
 The downstream increase of local species richness was predicted under a natural landscape scenario, in which environmental variation at headwaters $\sigma_h$ exceeds the degree of local environmental noise $\sigma_l$ (**Figure S1**).
-This pattern was consistent across ecological scenarios except those with long dispersal distance and high dispersal probability.
+This pattern was consistent across ecological scenarios except those with long dispersal distance and high dispersal probability (**Figure S1**).
 Similarly, we observed a downstream increase of local species richness in scenarios with low habitat diversity ($\sigma_h = \sigma_l = 0.01$) and low dispersal probability ($p_d = 0.01$) (**Figure S3**).
@@
 For example, when local environmental noise exceeds environmental variation at headwaters ($\sigma_l \ge \sigma_h$), local species richness showed a downstream decrease or a vague longitudinal pattern (**Figure S4**).
-Therefore, the simulation scenarios are capable of reproducing previously observed patterns, suggesting the appropriateness in the choice of parameter combinations.
+Therefore, the simulation scenarios were capable of reproducing previously observed patterns, suggesting the appropriateness in the choice of parameter combinations.
 
-# Fish community data
+# Empirical data
 
-## Hokkaido, Japan
-We used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected from literature[@teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island.
-Data were collected from summer to fall.
+## Fish community data
+
+**Hokkaido, Japan.** We used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaHokkaidoFreshwaterFish2011; @fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors[@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island.
+Fish data were collected from summer to fall.
 We screened data through the following procedure:
 
-1. We listed recorded fish species and re-organized species names to be consistent across data sources. Species that are identified at the family-level were removed.
 1.
-We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve unidentified species that are rarely observed in the data set (< 100 sites occurrence).
+We listed recorded fish species and re-organized species names to be consistent across data sources.
+We removed the following species at this stage: (1) identified at the family-level; (2) marine fish species (including species that occasionally use brackish/freshwater habitats).
+1.
+We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve species identified at the genus level that are rarely observed in the data set (< 100 sites occurrence).
 1.
@@
 1.
-Four genera (*Lethenteron*, *Pungitius*, *Rhinogobius*, and *Tribolodon*) were treated as species groups (i.e., spp.) as they are difficult to identify and taxonomic resolutions varied greatly among data sources.
+Four genera (*Lethenteron*, *Pungitius*, *Rhinogobius*, and *Tribolodon*) were treated as species groups (i.e., spp.) as their taxonomic resolutions varied greatly among data sources due to difficulties in identifying species.
 
-## Midwest, US
-We assembled fish community data collected by the Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
-These data sets cover most of Upper Mississippi (HUC 2, region 07) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05).
-Data were collected from summer to fall with electrofishing (backpack, barge-type, or boat-mounted) and supplemental netting at some locations.
+**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
+These data sets cover most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined
+by U.S.
+Geological Survey and U.S.
+Department of Agriculture Natural Resources Conservation Service[@u.s.geologicalsurveyandu.s.departmentofagriculturenaturalresourcesconservationserviceFederalStandardsProcedures2013]) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05).
+Fish data were collected from summer to fall with electrofishing (backpack, barge-type, or boat-mounted) and supplemental netting at some locations.
 We screened data through the following procedure:
@@
 1. We used data of the Upper Mississippi (HUC 2, region 07) and Great Lakes basins (HUC 2, region 04) as most sites are included in these regions.
-1. We removed records of unidentified species, hybrid species, and commercial species that are apparently absent in the wild (e.g., goldfish).
+1. We removed records of unidentified species, hybrid species, and commercial species apparently absent in the wild (e.g., goldfish).
 1. We used the latest observation at each sampling site to minimize variation in sampling efforts among sites.
@@
 
-## Table S1 Simulation parameter
+## Table S1 Simulation parameter (sensitivity analysis)
 
-Values and interpretation of parameters used in our simulation model. Refer to the maintext for model details.
+**Table S1** Parameter values used in the sensitivity analysis of the metacommunity simulation. See the main text for model details.
 
-```{r}
+```{r chunk_table1}
+
+  tibble(Parameter = c('$\\sigma_{h}$',
+                       '$\\sigma_{l}$',
+                       '$\\sigma_{z}$',
+                       '$\\rho$',
+                       '$\\phi$',
+                       '$\\nu$',
+                       '$\\alpha_{max}$',
+                       '$\\theta$',
+                       '$p_{d}$',
+                       '$r_{0,i}$'),
+         Value = c('Unif(0.01, 1)',
+                   'Unif(0.01, 1)',
+                   'Unif(0.01, 0.5)',
+                   '1',
+                   'Unif(0.01, 1)',
+                   'Unif(1, 5)',
+                   'Unif(0.5, 1.5)',
+                   'Unif(0.1, 1)',
+                   'Unif(0.01, 0.1)',
+                   '4'),
+         Interpretation = c('Environmental variation at headwaters',
+                            'Degree of local environmental noise',
+                            'Temporal environmental variability',
+                            'Strength of spatial autocorrelation in mean environmental condition',
+                            'Extent of spatial autocorrelation in temporal environmental variation',
+                            'Cost of a wider niche',
+                            'Maximum value of interspecific competition coefficient',
+                            'Rate parameter of an exponential dispersal kernel',
+                            'Dispersal probability',
+                            'Maximum reproductive rate')) %>% 
+    kable(format = 'markdown')
+
+```
+
+\newpage
+
+## Table S2 Simulation parameter (main analysis)
+
+**Table S2** Values and interpretation of simulation parameters used in the main simulation. See the main text for model details.
+
+```{r chunk_table2}
 
@@
 
-## Table SXX List of fish species in Hokkaido, Japan
+## Table S3 Sensitivity analysis for the effect of ecosystem size
 
-List of fish species in Hokkaido, Japan that are included in our statistical analysis.
-`r n_distinct(dat_hkd$Species)` species are ordered alphabetically with the number of sites present and % occupancy out of `r n_distinct(dat_hkd$SiteID)` sites.
+**Table S3** Sensitivity analysis of the metacommunity simulation.
+Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
+Dependent variables are the effects of the number of habitat patches ($N_{p}$) on $\alpha$, $\beta$, and $\gamma$ diversity.
+Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.
+See Tables S1 and S2 for interpretation of the simulation parameters.
 
-```{r chunk_table1}
+```{r chunk_table3, results='asis'}
+
+  cat(star_area, sep='\n')
+
+```
+
+\newpage
+
+## Table S4 Sensitivity analysis for the effect of ecosystem complexity
+
+**Table S4** Sensitivity analysis of the metacommunity simulation.
+Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
+Dependent variables are the effects of branching probability ($P_{b}$) on $\alpha$, $\beta$, and $\gamma$ diversity.
+Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.
+See Tables S1 and S2 for interpretation of the simulation parameters.
+
+```{r chunk_table4, results='asis'}
+
+  cat(star_bp, sep='\n')
+
+```
+
+\newpage
+
+## Table S5 List of fish species in Hokkaido, Japan
+
+**Table S5** List of fish species in Hokkaido, Japan, included in our statistical analysis.
+`r n_distinct(dat_hkd$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy out of `r n_distinct(dat_hkd$SiteID)` sites.
+
+```{r chunk_table5}
 
@@
 
-## Table SXX List of fish species in Midwest, US
+## Table S6 List of fish species in Midwest, US
 
-List of fish species in Midwest, US that are included in our statistical analysis.
-`r n_distinct(dat_mw$Species)` species are ordered alphabetically with the number of sites present and % occupancy out of `r n_distinct(dat_mw$SiteID)` sites.
+**Table S6** List of fish species in the Midwest, US, included in our statistical analysis.
+`r n_distinct(dat_mw$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy out of `r n_distinct(dat_mw$SiteID)` sites.
 
-```{r chunk_table2}
+```{r chunk_table6}
 
@@
 
+## Figure S19 Correlation structure of explanatory variables
+
+```{r fig_s19, fig.height = 10, fig.width = 10}
+
+source(here::here('empirical/figure_correlation.R'))
+
+```
+
+**Figure S19 ** Correlation structure of potential explanatory variables for riverine diversity metrics.
+Positive and negative correlations were colored in blue and red, respectively, and darker colors indicate stronger correlations.
+Environmental variables (temperature, precipitation, elevation, logit fraction of forest, logit fraction of urban, logit fraction of agriculture, and dam density) were expressed as deviations from regional averages to remove any regional effects.
+
+\newpage
+
 # References

### 2021-01-25 empirical/figure_diversity.R
Update figure_diversity.R

@@ -43,17 +43,20 @@
   dat <- bind_rows(dat_hkd, dat_mw) %>% 
     rename(gamma = Estimator, alpha = mu_alpha) %>% 
     mutate(beta = gamma/alpha,
-           logit_forest = log(frac_forest) - log(1 - frac_forest)) %>% 
+           logit_forest = log(frac_forest) - log(1 - frac_forest),
+           dam_density = n_dam/area) %>% 
     mutate(resid_forest = resid(lm(logit_forest ~ region, data = .)),
            resid_temp = resid(lm(mean_temp ~ region, data = .)),
-           resid_ppt = resid(lm(mean_ppt ~ region, data = .))) %>% 
+           resid_ppt = resid(lm(mean_ppt ~ region, data = .)),
+           resid_dam = resid(lm(dam_density ~ region, data = .))) %>% 
     pivot_longer(cols = c(alpha, beta, gamma),
                  names_to = "metric")
   
   dat_base <- data.frame(region = factor(rep(c("hokkaido", "midwest"), each = 100)),
                          resid_temp = mean(dat$resid_temp),
                          resid_ppt = mean(dat$resid_ppt),
-                         resid_forest = mean(dat$resid_forest))
+                         resid_forest = mean(dat$resid_forest),
+                         resid_dam = mean(dat$resid_dam))
 
 # data frame for prediction -----------------------------------------------
   
@@ -101,7 +104,8 @@
   g2 <- ggplot(dat, aes(x = p_branch, y = value, color = region)) +
     facet_wrap(facets = ~metric, labeller = label_parsed) +
     geom_point(alpha = 0.25) +
-    geom_line(data = dat_bp, aes(x = p_branch, y = value)) +
+    geom_line(data = dat_bp, aes(x = p_branch, y = value, linetype = metric)) +
+    scale_linetype_manual(values = c('blank', 'solid', 'solid'), guide = "none") +
     scale_color_hue(name = "Region", labels = c("Hokkaido", "Midwest")) +
     xlab("Branching probability") +
     scale_y_continuous(trans='log10') +

### 2021-01-25 empirical/analysis_lm_bf.R
Update analysis_lm_bf.R

@@ -12,10 +12,12 @@
     rename(gamma = Estimator,
            alpha = mu_alpha) %>% 
     mutate(beta = gamma/alpha,
-           logit_forest = log(frac_forest) - log(1 - frac_forest)) %>% 
+           logit_forest = log(frac_forest) - log(1 - frac_forest),
+           dam_density = n_dam/area) %>% 
     mutate(resid_forest = resid(lm(logit_forest ~ region, data = .)),
            resid_temp = resid(lm(mean_temp ~ region, data = .)),
-           resid_ppt = resid(lm(mean_ppt ~ region, data = .)))
+           resid_ppt = resid(lm(mean_ppt ~ region, data = .)),
+           resid_dam = resid(lm(dam_density ~ region, data = .)))
   
 
 # model selection ---------------------------------------------------------
@@ -23,11 +25,11 @@
   m_compare <- function(response, data) {
     
     mod1 <<- lm(log(response, 10) ~ log(area, 10)*region + log(p_branch, 10)*region + region +
-                                    scale(resid_temp) + scale(resid_ppt) + scale(resid_forest),
+                                    scale(resid_temp) + scale(resid_ppt) + scale(resid_forest) + scale(resid_dam),
                 data = data)
     
     mod0 <<- lm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
-                                    scale(resid_temp) + scale(resid_ppt) + scale(resid_forest),
+                                    scale(resid_temp) + scale(resid_ppt) + scale(resid_forest) + scale(resid_dam),
                     data = data)
     
     # bf01: bayes factor in favor of mod0 over mod1

### 2021-01-25 table.Rmd
Update table.Rmd

@@
 ---
-title: "Tables"
+title: "Table"
 output:
@@
                      header = FALSE,
-                     title = "Estimated parameters of linear regression models explaining fish species richness in Hokkaido (Japan) and Midwest (US) regions.
-Dependent variables were log-10 transformed.
-Environmental variables (air temperature, precipitation, logit \\% forest) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.",
                      type = "latex",
                      ci = TRUE,
+                     title = "Estimated parameters of linear regression models explaining fish species richness in Hokkaido (Japan) and Midwest (US) regions.
+The 95\\% confidence intervals are shown in parenthesis.
+Dependent variables were log-10 transformed.
+Environmental variables (air temperature, precipitation, logit \\% forest, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.",
                      covariate.labels = c("$log_{10}$ Watershed area",
@@
                                           "Logit \\% forest",
+                                          "Dam density",
                                           "Intercept"),

### 2021-01-25 theory/analysis_sensitivity.R
Create analysis_sensitivity.R

@@ -1,0 +1,46 @@
+
+# setup -------------------------------------------------------------------
+
+  pacman::p_load(tidyverse, broom)
+
+
+# data --------------------------------------------------------------------
+
+dat_slope <- read_csv(here::here('theory/result/result_sensitivity.csv')) %>% 
+    filter(gamma_div > 0 & alpha_div > 0) %>% 
+    mutate(beta_div = gamma_div/alpha_div) %>% 
+    mutate(group_id = group_indices(., sd_env_source)) %>% 
+    group_by(group_id) %>% 
+    do(slope_alpha_area = c(coef(lm(log(alpha_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[2]),
+       slope_beta_area = c(coef(lm(log(beta_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[2]),
+       slope_gamma_area = c(coef(lm(log(gamma_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[2]),
+       slope_alpha_bp = c(coef(lm(log(alpha_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[3]),
+       slope_beta_bp = c(coef(lm(log(beta_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[3]),
+       slope_gamma_bp = c(coef(lm(log(gamma_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[3])) %>% 
+    summarize(across(everything(), as.numeric))
+  
+dat_para <- read_csv(here::here('theory/result/result_sensitivity.csv')) %>% 
+  mutate(group_id = group_indices(., sd_env_source)) %>% 
+  group_by(group_id) %>% 
+  summarize(sigma_h = unique(sd_env_source),
+            sigma_l = unique(sd_env_lon),
+            sigma_z = unique(sd_env),
+            phi = unique(phi),
+            nu = unique(niche_cost),
+            max_alpha = unique(max_alpha),
+            theta = unique(theta),
+            p_d = unique(p_dispersal))
+    
+dat_sense <- dat_para %>%
+  left_join(dat_slope, by = 'group_id') %>% 
+  pivot_longer(cols = starts_with('slope'),
+               names_to = 'response',
+               values_to = 'slope')
+
+fit_sense <- dat_sense %>% 
+  summarize(group_id = group_id,
[…]

### 2021-01-25 manuscript.Rmd
minor updates

@@
 At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
-Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006a].
+Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006].
 
@@
 The recurrent merging of diverse streams and rivers produces larger, ecologically distinct channels, ultimately forming a fluvial network with fractal branching patterns[@rodriguez-iturbeFractalRiverBasins2001].
-As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], should control the ecosystem's habitat heterogeneity (habitat diversity per unit area).
+As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a], should control the ecosystem's habitat heterogeneity (habitat diversity per unit area).
 Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity).
@@
 First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
-We depicted branching ecosystems as a spatial network of connected habitat patches or local communities[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**) where two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+We depicted branching ecosystems as a spatial network of connected habitat patches or local communities[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**) where two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
 Environmental values at headwaters are drawn randomly from a normal distribution and propagate downstream with local environmental noise (i.e., a spatial autoregressive process with white noise).
@@
 
-We considered `r n_scenario` simulation scenarios, which comprised a combination of four landscape and eight ecological scenarios.
+Given the results of extensive sensitivity analysis (**Supplementaly Information**), we considered `r n_scenario` simulation scenarios, which comprised a combination of four landscape and eight ecological scenarios.
 We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), both of which are defined as standard deviations of normal distributions.
 When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation.
+This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries [@chezikRiverNetworksDampen2017; @mooreEmergentStabilityLarge2015; @petersonModellingDendriticEcological2013].
 In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on habitat heterogeneity.
-Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity withing a network.
+This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities[@mooreSynchronizationPortfolioPerformance2010; @poffHomogenizationRegionalRiver2007; @teruiMetapopulationStabilityBranching2018].
+Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity within a network.
 We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel), dispersal probability, and the maximum value of interspecific competition strength (see Methods).
@@
 However, we are confident in our statistical inference because the observed patterns were fairly consistent with our theoretical predictions that are free from any confounding effects.
-Further, our fitted models generally showed high R^2^ values ($\alpha$ diversity: `r round(summary(fit$alpha$model)$r.squared, 2)`; $\beta$ diversity, `r round(summary(fit$beta$model)$r.squared, 2)`; $\gamma$ diversity `r round(summary(fit$gamma$model)$r.squared, 2)`) with no signs of spatial autocorrelation in residuals.
+Further, our fitted models generally showed high R^2^ values ($\alpha$ diversity: `r round(summary(fit$alpha$model)$r.squared, 2)`; $\beta$ diversity, `r round(summary(fit$beta$model)$r.squared, 2)`; $\gamma$ diversity `r round(summary(fit$gamma$model)$r.squared, 2)`).
 Therefore, it is very unlikely that spurious correlations are responsible for our results.
@@
 
-We depicted branching ecosystems as a bifurcating spatial network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**).
+We depicted branching ecosystems as a bifurcating spatial network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**).
 Habitat patches, or local communities, can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.

### 2021-01-25 empirical/data_merge_hkd.R

@@ -3,7 +3,7 @@
   
   rm(list = ls(all.names = TRUE))
   setwd(here::here("empirical"))
-  pacman::p_load(tidyverse, tidyverse, sf, iNEXT, foreach, magrittr)  
+  pacman::p_load(tidyverse, sf, iNEXT, foreach, magrittr)  
   
 # read gis data -----------------------------------------------------------
 

### 2021-01-25 empirical/table_sim_parameter_main.R

@@ -1,0 +1,63 @@
+
+# setup -------------------------------------------------------------------
+
+  pacman::p_load(tidyverse, knitr, kableExtra)
+  dat_sim <- read_csv(here::here('/theory/result/result_sim2020-11-10.csv'))
+
+# table -------------------------------------------------------------------
+
+  dat_sim %>% 
+    select(sd_env_source,
+           sd_env_lon,
+           sd_env,
+           rho,
+           phi,
+           niche_cost,
+           max_alpha,
+           theta,
+           p_dispersal
+    ) %>% 
+    summarise(across(everything(), unique)) %>% 
+    mutate(r0 = 4) %>% 
+    pivot_longer(cols = everything(),
+                 names_to = "Parameter",
+                 values_to = "Value") %>% 
+    group_by(Parameter) %>% 
+    summarize(Value = list(unique(Value))) %>% 
+    mutate(id = case_when(Parameter == 'sd_env_source' ~ 'a',
+                          Parameter == 'sd_env_lon' ~ 'b',
+                          Parameter == 'sd_env' ~ 'c',
+                          Parameter == 'rho' ~ 'd',
+                          Parameter == 'phi' ~ 'e',
+                          Parameter == 'niche_cost' ~ 'f',
+                          Parameter == 'max_alpha' ~ 'g',
+                          Parameter == 'theta' ~ 'h',
+                          Parameter == 'p_dispersal' ~ 'i',
+                          Parameter == 'r0' ~ 'j',
+                          TRUE ~ as.character(Parameter)),
+           Interpretation = case_when(Parameter == 'sd_env_source' ~ 'Environmental variation at headwaters',
+                                      Parameter == 'sd_env_lon' ~ 'Degree of local environmental noise',
+                                      Parameter == 'sd_env' ~ 'Temporal environmental variability',
+                                      Parameter == 'rho' ~ 'Strength of spatial autocorrelation in mean environmental condition',
+                                      Parameter == 'phi' ~ 'Extent of spatial autocorrelation in temporal environmental variation',
+                                      Parameter == 'niche_cost' ~ 'Cost of a wider niche',
+                                      Parameter == 'max_alpha' ~ 'Maximum value of interspecific competition coefficient',
+                                      Parameter == 'theta' ~ 'Rate parameter of an exponential dispersal kernel',
+                                      Parameter == 'p_dispersal' ~ 'Dispersal probability',
[…]

### 2021-01-25 empirical/table_splist_hkd.R

@@ -1,0 +1,21 @@
+
+# setup -------------------------------------------------------------------
+
+  pacman::p_load(tidyverse, knitr, kableExtra)
+  dat_hkd <- read_csv(here::here('/empirical/data_out/dat_hkd_site.csv'))
+
+# table -------------------------------------------------------------------
+
+  dat_hkd %>% 
+    mutate(n_site = n_distinct(SiteID)) %>% 
+    mutate(Species = str_replace_all(str_to_title(Species), "_", " ")) %>% 
+    mutate(Species = str_replace_all(Species, "(spp$)|(spp\\s)", "spp\\.")) %>% 
+    mutate(Species = str_replace_all(Species, "(sp$)", "sp\\.")) %>% 
+    mutate(Species = str_replace_all(Species, "(subsp)", "subsp\\. ")) %>% 
+    mutate(Species = str_replace_all(Species, "(sp\\sme$)", "sp\\. ME")) %>% 
+    group_by(Species) %>% 
+    summarise('Number of sites present' = n_distinct(SiteID),
+              'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
+    kable(format = 'markdown')
+
+  print(g)

### 2021-01-25 empirical/table_splist_mw.R

@@ -1,0 +1,24 @@
+
+# setup -------------------------------------------------------------------
+
+  pacman::p_load(tidyverse, knitr, kableExtra)
+  dat_mw <- read_csv(here::here('/empirical/data_out/dat_mw_site.csv'))
+
+# table -------------------------------------------------------------------
+
+  sp_mw_latin <- read_csv(here::here('/empirical/data_out/data_mw_splist_latin.csv'))
+  
+  dat_mw %>% 
+    mutate(n_site = n_distinct(SiteID)) %>% 
+    rename(Common_name = Species) %>% 
+    group_by(Common_name) %>% 
+    summarise('Number of sites present' = n_distinct(SiteID),
+              'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
+    left_join(sp_mw_latin, by = "Common_name") %>% 
+    select(Species = Latin_name,
+           'Number of sites present',
+           'Occupancy (%)') %>% 
+    arrange(Species) %>% 
+    kable(format = 'markdown')
+  
+  print(g)

### 2021-01-25 supplementary_information.Rmd
Update supplementary_information.Rmd

@@
 
-## Table S3 Sensitivity analysis for the effect of ecosystem size
+## Table S3 Sensitivity analysis for ecosystem size effects
 
@@
 
-## Table S4 Sensitivity analysis for the effect of ecosystem complexity
+## Table S4 Sensitivity analysis for ecosystem complexity effects
 
@@
 Positive and negative correlations were colored in blue and red, respectively, and darker colors indicate stronger correlations.
-Environmental variables (temperature, precipitation, elevation, logit fraction of forest, logit fraction of urban, logit fraction of agriculture, and dam density) were expressed as deviations from regional averages to remove any regional effects.
+Environmental variables (temperature, precipitation, elevation, logit fraction of forest, logit fraction of urban, logit fraction of agriculture, and dam density) were expressed as deviations from the regional averages to remove any regional effects.
 

### 2021-01-25 manuscript.Rmd
Update manuscript.Rmd

@@
 Environmental values at headwaters are drawn randomly from a normal distribution and propagate downstream with local environmental noise (i.e., a spatial autoregressive process with white noise).
-These environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see Methods).
+These environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see **Methods**).
 Therefore, our network-generation procedure resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
 We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity framework[@thompsonProcessbasedMetacommunityFramework2020].
-In this model, 50 species with different abiotic niches (optimum and width) disperse along a network and compete for resources with varied strengths in temporally dynamic environments (see Methods for model details).
+In this model, 50 species with different abiotic niches (optimum and width) disperse along a network and compete for resources with varied strengths in temporally dynamic environments (see **Methods** for model details).
 
@@
 Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity within a network.
-We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel), dispersal probability, and the maximum value of interspecific competition strength (see Methods).
-These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (Supplementary Information).
+We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel), dispersal probability, and the maximum value of interspecific competition strength (see **Methods**).
+These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supplementary Information**).
 Under each simulation scenario, we simulated 1000 time steps of metacommunity dynamics in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
@@
 Therefore, this data set provides an excellent opportunity to examine the generality of our theoretical predictions.
-After careful data selection (see Methods and Supplementary Information), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; Methods) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in the Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
+After careful data selection (see **Methods** and **Supplementary Information**), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; **Methods**) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in the Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area), or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-We combined this data set with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, and % forest) to examine potential influences of macro-scale drivers of species diversity.
+We combined this data set with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, and fraction of forest) to examine potential influences of macro-scale drivers of species diversity.
 Using this data set, we developed global and region-specific models for each of the diversity measures ($\alpha$, $\beta$, and $\gamma$ diversity) to examine whether observed patterns are consistent across the two geographic regions.
@@
 Meanwhile, the region-specific model assumes region-specific slopes of ecosystem size and complexity by including interaction terms with the dummy binary variable of the region (Hokkaido = 0; Midwest = 1).
-We compared the performance of these competing models using the Bayes factor, a measure of the strength of evidence in favor of one model over the alternative.
+We compared the support of these competing models using the Bayes factor, a measure of the strength of evidence in favor of one model over the alternative.
+In our definition (see **Methods**), the Bayes factor of $> 1$ indicates the support for the global model over the region-specific model.
 
-Despite the substantial difference in fish fauna between the study regions, the estimated Bayes factor in favor of the global model was `r round(fit$gamma$bayes_factor, 1)` for $\gamma$ diversity; this result strongly supports the consistent effects of ecosystem size and complexity on $\gamma$ diversity across the two biogeographic regions.
-We found patterns consistent with our theoretical predictions (**Table 1 and Figure 4**).
+Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`): this result suggests the consistent effects of ecosystem size and complexity on $\gamma$ diversity across the two biogeographic regions.
+Furthermore, the observed patterns were in close agreement with our theoretical predictions (**Table 1 and Figure 4**).
 The estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) across watersheds.
@@
 
-Similarly, we found weak to moderate supports for the global models of $\alpha$ and $\beta$ diversity (Bayes factor: `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
-In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity while $\alpha$ diversity showing a vague response to these ecosystem properties (**Table 1 and Figure 4**).
+Similarly, we found weak to moderate supports for the global models of $\alpha$ and $\beta$ diversity (Bayes factor = `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
+In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity while $\alpha$ diversity showing a weaker or a vague response to these ecosystem properties (**Table 1 and Figure 4**).
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly matches the previous observations of stream fish movement.
@@
 where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
-$K_x$ was expressed as a function of the number of upstream contributing patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area[@altermattRiverNetworkProperties2013; @teruiThreeEcologicalFactors2016].
+$K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area[@altermattRiverNetworkProperties2013; @teruiThreeEcologicalFactors2016].
 The parameter $\alpha_{ij}$ is expressed as the strength of interspecific competition relative to that of intraspecific competition such that interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ > 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
@@
 For the Midwest, we assembled fish community data collected by Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
-We detailed procedures for initial data selection in Supplementary Information.
+We detailed procedures for initial data selection in **Supplementary Information**.
 
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (Supplementary Information).
+These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@giamEnvironmentPredationGovern2016], while posing challenges for stream fishes to traverse across watersheds (the ocean or lentic habitats).
+Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (**Supplementary Information**).
 
@@
 Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014; @chaseEcosystemDecayExacerbates2020].
+Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014a; @chaseEcosystemDecayExacerbates2020].
 We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package iNEXT[@hsiehINEXTPackageRarefaction2016].
@@
 
-We collected data for watershed characteristics (watershed area and branching probability), climatic variables (annual mean air temperature and cumulative precipitation), and land use (% forest).
-We delineated watershed polygons and river lines (defined as $\ge$ 1 km^2^) using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] with ArcMap 10.7 and SAGA 6.3.0 combined with the R package 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018].
+We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (annual mean air temperature [degree celsius] and cumulative precipitation [mm]), and land use (fraction of forest, fraction of urban, fraction of agriculture, and dam density per watershed area [km^-2^]).
+We delineated watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area) using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] with ArcMap 10.7 and SAGA 6.3.0 combined with the R package 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018].
 Watershed area was estimated based on the delineated watershed polygons using functions in the R package 'sf'[@pebesmaSimpleFeaturesStandardized2018].
-Branching probability was estimated by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$.
+We estimated branching probability by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$.
 A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
-We estimated the spatial averages of air temperature and cumulative precipitation at a 1-km resolution for each watershed, which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005] via the R package 'raster.' We calculated % forest for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
+We obtained mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019].
+We estimated the spatial averages of air temperature and cumulative precipitation at a 1-km resolution for each watershed, which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005] via the R package 'raster.' We calculated fraction of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
+We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1)[@lehnerGlobalReservoirDam2011; @lehnerHighResolutionMappingWorld2011].
 
@@
 Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $i$, $log_{10}~y_i$, are assumed to follow a normal distribution as $log_{10}~y_i \sim Normal(\mu_i, \sigma^2)$.
-The parameter $\mu_i$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, and percent of forest land use (logit-transformed).
+The parameter $\mu_i$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, and fraction of forest land use (logit-transformed).
 Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control these effects statistically.
+Fractions of urban and agriculture land use were not included in the statistical models because these variables are strongly correlated with the fraction of forest land use (**Figure S19**).
+Also, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**).
+Correlations for other combinations of explanatory variables were weak to moderate.
 
-Climate and land use differed clearly between the regions.
-Therefore, we used residuals of the simple linear regressions between the climate or land use variable (response variable) and region (explanatory variable) to avoid correlation between explanatory variables.
+Climate (air temperature and precipitation) and land use (fraction of forest and dam density) differed clearly between the regions.
+Therefore, we used residuals of the simple linear regressions between the climate or land use variable (response variable) and region (explanatory variable).
 The residuals represent deviations from the regional averages; positive values indicate values greater than the regional average while negative values indicating values smaller than the regional average.
+Therefore,
 
@@
 $$
-where $\xi_k$ is the intercept and regression coefficients for linear predictors.
+where $\xi_k$ are the intercept and regression coefficients for linear predictors.
 Meanwhile, the region-specific model assumes the effects of watershed area and branching probability differ between regions (i.e., interactions between region and watershed area/branching probability).
@@
 # Acknowledgements
+We acknowledge numerous scientists who have been involved in the collection of fish community data. We thank Michio Fukushima for providing information on the Hokkaido Freshwater Fish Database HFish.
 
@@
 
+# Data and code availability
+Data are provided by third parties and references are provided in the main text where appropriate.
+R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet.' (available at https://github.com/aterui/mcbrnet).
+Codes for simulations, statistical analysis, figures, and tables are available at https://github.com/aterui/public-proj_stream-diversity.
+
 # References

### 2021-01-25 table.Rmd
random

@@
                      ci = TRUE,
-                     title = "Estimated parameters of linear regression models explaining fish species richness in Hokkaido (Japan) and Midwest (US) regions.
+                     title = "Estimated parameters of linear regression models explaining fish species richness in the Hokkaido (Japan) and the Midwest (US) regions.
 The 95\\% confidence intervals are shown in parenthesis.
 Dependent variables were log-10 transformed.
-Environmental variables (air temperature, precipitation, logit \\% forest, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.",
+Climate and land use variables (air temperature, precipitation, logit fraction of forest, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.",
                      covariate.labels = c("$log_{10}$ Watershed area",
@@
                                           "Precipitation",
-                                          "Logit \\% forest",
+                                          "Logit fraction of forest",
                                           "Dam density",

### 2021-01-26 manuscript.Rmd
Update manuscript.Rmd

@@
 output:
+  word_document: default
   html_notebook: default
-  word_document: default
 abstract:
@@
 
-Given the results of extensive sensitivity analysis (**Supplementaly Information**), we considered `r n_scenario` simulation scenarios, which comprised a combination of four landscape and eight ecological scenarios.
+Given the results of extensive sensitivity analysis (**Supplementary Information**), we considered `r n_scenario` simulation scenarios, which comprised a combination of four landscape and eight ecological scenarios.
 We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), both of which are defined as standard deviations of normal distributions.
@@
 The proposed theory provided important insights into how ecological communities are structured in branching networks; however, empirically testing the predictions is extremely difficult because it requires metacommunity-level replications.
-To confront this logistical challenge, we compiled fish community data that span across two geographic regions: the Hokkaido island in Japan and the midwestern US (Midwest).
-These regions are located in comparable ranges of latitude but support distinct fish communities (**Figure 1**).
+To confront this logistical challenge, we compiled fish community data across two geographic regions: the Hokkaido island in Japan and the midwestern US (Midwest).
+These regions are located in comparable latitude ranges but support distinct fish communities (**Figure 1**).
 Therefore, this data set provides an excellent opportunity to examine the generality of our theoretical predictions.
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area), or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-We combined this data set with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, and fraction of forest) to examine potential influences of macro-scale drivers of species diversity.
+We combined this data set with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, and the fraction of forest) to examine potential influences of macro-scale drivers of species diversity.
 Using this data set, we developed global and region-specific models for each of the diversity measures ($\alpha$, $\beta$, and $\gamma$ diversity) to examine whether observed patterns are consistent across the two geographic regions.
@@
 Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`): this result suggests the consistent effects of ecosystem size and complexity on $\gamma$ diversity across the two biogeographic regions.
-Furthermore, the observed patterns were in close agreement with our theoretical predictions (**Table 1 and Figure 4**).
+Furthermore, the observed patterns were closely aligned with our theoretical predictions (**Table 1 and Figure 4**).
 The estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) across watersheds.
-These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, and land use) (**Table 1**).
+These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, the fraction of forest, and dam density) (**Table 1**).
 Overall, our statistical analysis provides strong empirical evidence that ecosystem size and complexity jointly scale riverine biodiversity at the metacommunity level.
@@
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly matches the previous observations of stream fish movement.
-Direct (mark-recapture) and indirect observations (e.g., genotyping) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters in distance[@comteFishDispersalFlowing2018; @radingerPatternsPredictorsFish2014; @rodriguezRestrictedMovementStream2002].
+Direct (mark-recapture) and indirect observations (e.g., genotyping) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters[@comteFishDispersalFlowing2018; @radingerPatternsPredictorsFish2014; @rodriguezRestrictedMovementStream2002].
 The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
@@
 The consistent effect of branching probability on $\gamma$ diversity across the study regions is noteworthy because the watersheds in the Midwest are severely altered by agriculture (median % agricultural land use: `r round(median(wsd_subset[[2]]$frac_agri)*100)`% in the Midwest and `r round(median(wsd_subset[[1]]$frac_agri)*100)`% in Hokkaido).
-If the intensive land use by humans causes significant homogenization of in-stream habitat conditions among tributaries, theory predicts weakened effects of branching probability on $\gamma$ diversity.
+If the intensive land use by humans causes significant homogenization of in-stream habitat conditions among tributaries, theory predicts a weakened effect of branching probability on $\gamma$ diversity.
 However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions to support high spatial turnover of species composition.
@@
 First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
-Human-induced habitat alterations, including flow regulation[@poffHomogenizationRegionalRiver2007], habitat fragmentation[@fukushimaModellingEffectsDams2007; @moritaEffectsHabitatFragmentation2002], and stream burial, may compromise or restrict access to the diverse habitats that complex branching networks may support.
+Human-induced habitat alterations, including flow regulation[@poffHomogenizationRegionalRiver2007], landscape modification[@finlayStreamSizeHuman2011; @moritaEffectsHabitatFragmentation2002], and stream burial[@elmoreDisappearingHeadwatersPatterns2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
 Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human activities.
 Second, the complexity perspective may provide insights into the spatial planning of conservation efforts.
-Riverine reserves and local restoration are increasingly recognized as an effective management tool, and how to design a spatial network of conservation sites in rivers is an area of active research[@koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013; @sundermannRiverRestorationSuccess2011].
+Riverine reserves and local restoration are increasingly recognized as an effective management tool, and designing a spatial network of conservation sites in rivers is an area of active research[@koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013; @sundermannRiverRestorationSuccess2011].
 While large reserves or restoration sites are undoubtedly important[@koningNetworkGrassrootsReserves2020], our results indicate the potential of coordinated networks of local conservation sites in protecting biodiversity.
 For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin[@koningNetworkGrassrootsReserves2020].
-Our findings, therefore, offer the ecological foundation for the network-based conservation strategies in rivers, broadening viable options towards successful conservation.
 
-While the prevailing evidence supports the importance of ecosystem size in scaling species diversity, ecosystem complexity - especially branching structure - has not received the attention it deserves.
-Ecosystems are inherently complex in their spatial structure, providing a physical template that creates a wide spectrum of niche opportunities for living organisms.
-Hence, our findings should be broadly applicable to many taxa and ecosystems.
+While the prevailing evidence supports the importance of ecosystem size in scaling species diversity, ecosystem complexity has not received the attention it deserves.
+However, the ubiquity of scale-invariant complexity across terrestrial[@turnerLandscapeEcologyTheory2015] and aquatic ecosystems[@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of ecosystem structure.
+Our general framework of the dual dimensional approach, ecosystem size and complexity, should apply beyond branching ecosystems and broaden viable options towards successful conservation.
 The generalization of our findings in spatially complex ecosystems represents a frontier for future research.
@@
 
-Two sources of variation characterize the long-term average of abiotic environment at each habitat patch: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
+Two sources of variation characterize the long-term average of the abiotic environment at each habitat patch: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
 We draw random values from a normal distribution with a mean of zero and SD of $\sigma_{h}$ and assigned them to headwater patches (i.e., the most upstream patches).
@@
 For landscape scenarios, we changed values of environmental variation at headwaters ($\sigma_h$) and the degree of local environmental noise ($\sigma_l$) separately to create contrasting patterns of habitat heterogeneity.
-Specifically, we used two values (0.01 and 1) for each of SD parameters.
+Specifically, we used two values (0.01 and 1) for each of the SD parameters.
 When $\sigma_h > \sigma_l$, branching exhibits important effects on habitat heterogeneity in the ecosystem because headwaters are the primary source of environmental variation.
@@
 
-We compiled fish data at two biogeographic regions: the Hokkaido island, Japan and the Midwest, US.
+We compiled fish data at two biogeographic regions: the Hokkaido island, Japan, and the Midwest, US.
 For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaHokkaidoFreshwaterFish2011; @fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors[@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island.
-For the Midwest, we assembled fish community data collected by Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
+For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
 We detailed procedures for initial data selection in **Supplementary Information**.
@@
 
-We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (annual mean air temperature [degree celsius] and cumulative precipitation [mm]), and land use (fraction of forest, fraction of urban, fraction of agriculture, and dam density per watershed area [km^-2^]).
+We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]).
 We delineated watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area) using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] with ArcMap 10.7 and SAGA 6.3.0 combined with the R package 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018].
@@
 We obtained mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019].
-We estimated the spatial averages of air temperature and cumulative precipitation at a 1-km resolution for each watershed, which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005] via the R package 'raster.' We calculated fraction of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
+We estimated the spatial averages of air temperature and cumulative precipitation at a 1-km resolution for each watershed, which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005] via the R package 'raster.' We calculated the fraction of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
 We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1)[@lehnerGlobalReservoirDam2011; @lehnerHighResolutionMappingWorld2011].
@@
 
-We developed linear models to examine the effects of macro-scale drivers on diversity metrics.
+We developed linear regression models to examine the effects of macro-scale drivers on diversity metrics.
 Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $i$, $log_{10}~y_i$, are assumed to follow a normal distribution as $log_{10}~y_i \sim Normal(\mu_i, \sigma^2)$.
-The parameter $\mu_i$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, and fraction of forest land use (logit-transformed).
+The parameter $\mu_i$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, and the fraction of forest land use (logit-transformed).
 Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control these effects statistically.
-Fractions of urban and agriculture land use were not included in the statistical models because these variables are strongly correlated with the fraction of forest land use (**Figure S19**).
-Also, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**).
+We did not include the fractions of urban and agricultural land use in the statistical models because these variables are strongly correlated with the fraction of forest land use (**Figure S19**).
+Similarly, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**).
 Correlations for other combinations of explanatory variables were weak to moderate.
@@
 We constructed two models for each of the diversity metrics: global and region-specific models.
-The global model assumes that the effects of watershed area and branching probability are consistent across biogeographic regions (i.e., no interactive effects of region with other linear predictors).
+The global model assumes that the effects of watershed area and branching probability are consistent across biogeographic regions (i.e., no interactive effects of the region with other linear predictors).
 
@@
 # Acknowledgements
-We acknowledge numerous scientists who have been involved in the collection of fish community data. We thank Michio Fukushima for providing information on the Hokkaido Freshwater Fish Database HFish.
+We acknowledge numerous people who have been involved in the collection of fish community data. We thank Michio Fukushima for providing information on the Hokkaido Freshwater Fish Database HFish.
 
@@
 # Data and code availability
-Data are provided by third parties and references are provided in the main text where appropriate.
+Third parties provided data for empirical data analysis; references are provided in the main text and Supplementary Information where appropriate.
 R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet.' (available at https://github.com/aterui/mcbrnet).

### 2021-01-26 manuscript.Rmd
Update manuscript.Rmd

@@
 Ecosystem complexity, which we defined as the probability of branching per unit river distance, should increase watershed-scale species richness by increasing habitat heterogeneity (habitat diversity per unit area).
-Meanwhile, ecosystem size should dictate metacommunity size and total habitat diversity (area x habitat heterogeneity) that regulate watershed-scale species richness.
+Meanwhile, ecosystem size should dictate metacommunity size and total habitat diversity (area x habitat heterogeneity), two factors that regulate watershed-scale species richness.
 We developed theoretical models simulating metacommunity dynamics in branching river networks and yielded results consistent with our hypothesis.
@@
 First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
-We depicted branching ecosystems as a spatial network of connected habitat patches or local communities[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**) where two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+We depicted branching ecosystems as a spatial network of connected habitat patches where local communities inhabit[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**).
+Two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
 Environmental values at headwaters are drawn randomly from a normal distribution and propagate downstream with local environmental noise (i.e., a spatial autoregressive process with white noise).
@@
 In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$; **Figures S13-18**).
-Under this scenario, branching may not contribute to the ecosystem's overall habitat diversity because local environmental noise masks environmental differences between branches.
-Therefore, this landscape scenario decouples the intimate relationship between branching structure and total habitat diversity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
+Under this scenario, branching may not contribute to the ecosystem's habitat heterogeneity because local environmental noise masks environmental differences between tributaries.
+Therefore, this landscape scenario decouples the intimate relationship between branching structure and habitat heterogeneity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
 This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes[@altermattDiversityRiverineMetacommunities2013; @bendaNetworkDynamicsHypothesis2004; @mooreEmergentStabilityLarge2015; @nakamuraDisturbanceRegimesStream2000; @petersonModellingDendriticEcological2013; @teruiMetapopulationStabilityBranching2018].
@@
 For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin[@koningNetworkGrassrootsReserves2020].
+Hence, our findings offer the ecological foundation for the complexity-based conservation strategies in rivers.
 
@@
 ### Simulation
-We set four landscape and eight ecological scenarios, resulting in a total of `r n_scenario` sets of parameter combinations.
+Based on the results of extensive sensitivity analysis (**Supplementary Information**), we set four landscape and eight ecological scenarios, resulting in a total of `r n_scenario` sets of parameter combinations.
 For landscape scenarios, we changed values of environmental variation at headwaters ($\sigma_h$) and the degree of local environmental noise ($\sigma_l$) separately to create contrasting patterns of habitat heterogeneity.
@@
 The residuals represent deviations from the regional averages; positive values indicate values greater than the regional average while negative values indicating values smaller than the regional average.
-Therefore,
 

### 2021-01-29 manuscript.Rmd
Update manuscript.Rmd

@@
 output:
+  html_notebook: default
   word_document: default
-  html_notebook: default
 abstract:
-  The species-area relationship (the SAR), a tendency in which species richness increases with increasing area, is one of the most robust empirical generalizations in ecology and formed the basis of area-based conservation strategies.
+  The species-area relationship (the SAR), a tendency in which species richness increases with increasing area, is one of the most robust empirical generalizations in ecology and has formed the basis of area-based conservation strategies.
 However, many ecosystems possess a complex spatial structure that cannot be represented by area (the scale-invariant complexity), and its role in scaling biodiversity is largely unknown.
@@
 There is now a clear need to consider the dimension of ecosystem complexity in biodiversity conservation.
-The dual dimensional approach - size and complexity - should broaden viable options for spatial planning of protected areas or restoration sites, thereby helping reconcile the conflicts between biodiversity conservation and societal demands.
+The dual dimensional approach - size and complexity - should broaden viable options for spatial planning of protected areas or restoration sites, thereby helping reconcile the pervasive conflict between biodiversity conservation and societal demands.
 
@@
 At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
-Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where the accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006].
+Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006].
 
@@
 First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
-We depicted branching ecosystems as a spatial network of connected habitat patches where local communities inhabit[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**).
+We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**).
 Two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
@@
 
-Given the results of extensive sensitivity analysis (**Supplementary Information**), we considered `r n_scenario` simulation scenarios, which comprised a combination of four landscape and eight ecological scenarios.
+Given the results of extensive sensitivity analysis (**Supplementary Information**), we considered `r n_scenario` simulation scenarios comprising a combination of four landscape and eight ecological scenarios.
 We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), both of which are defined as standard deviations of normal distributions.
@@
 These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supplementary Information**).
-Under each simulation scenario, we simulated 1000 time steps of metacommunity dynamics in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
+Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 400 time steps of initialization and burn-in periods) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
 
 Our theoretical analysis yielded results consistent with our prediction.
-Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters ($\sigma_h$) is greater than the degree of local environmental noise ($\sigma_l$) [@petersonModellingDendriticEcological2013; @teruiMetapopulationStabilityBranching2018].
+Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters ($\sigma_h$) is greater than the degree of local environmental noise ($\sigma_l$).
 The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios.
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area), or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-We combined this data set with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, and the fraction of forest) to examine potential influences of macro-scale drivers of species diversity.
+We combined this data set with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, the fraction of forest, and dam density) to examine potential influences of macro-scale drivers of species diversity.
 Using this data set, we developed global and region-specific models for each of the diversity measures ($\alpha$, $\beta$, and $\gamma$ diversity) to examine whether observed patterns are consistent across the two geographic regions.
@@
 For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin[@koningNetworkGrassrootsReserves2020].
-Hence, our findings offer the ecological foundation for the complexity-based conservation strategies in rivers.
 
 While the prevailing evidence supports the importance of ecosystem size in scaling species diversity, ecosystem complexity has not received the attention it deserves.
-However, the ubiquity of scale-invariant complexity across terrestrial[@turnerLandscapeEcologyTheory2015] and aquatic ecosystems[@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of ecosystem structure.
-Our general framework of the dual dimensional approach, ecosystem size and complexity, should apply beyond branching ecosystems and broaden viable options towards successful conservation.
+However, the ubiquity of scale-invariant complexity across terrestrial[@turnerLandscapeEcologyTheory2015] and aquatic ecosystems[@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
+Our fundamental findings should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
+The dual dimensional approach - size and complexity - broadens viable options for spatial planning of protected areas or restoration sites, thereby helping reconcile the pervasive conflict between biodiversity conservation and societal demands.
 The generalization of our findings in spatially complex ecosystems represents a frontier for future research.
@@
 
-We depicted branching ecosystems as a bifurcating spatial network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**).
+We depicted branching ecosystems as a bifurcating network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**).
 Habitat patches, or local communities, can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
@@
 
-$\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$.
+$\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (the shortest network path [measured as the number of habitat patches] to reach a target patch).
 The parameter $\phi$ determines the degree of the distance decay of environmental correlates.
@@
 $$
-where $d_{xy}$ is the separation distance between patch $x$ and $y$.
+where $d_{xy}$ is the separation distance between patch $x$ and $y$ (the shortest network path [measured as the number of habitat patches] to reach a target patch).
 The parameter $\theta$ regulates the dispersal distance of a species that follows an exponential distribution ($\theta^{-1}$ corresponds to the expected dispersal distance).
@@
 ### Simulation
-Based on the results of extensive sensitivity analysis (**Supplementary Information**), we set four landscape and eight ecological scenarios, resulting in a total of `r n_scenario` sets of parameter combinations.
-For landscape scenarios, we changed values of environmental variation at headwaters ($\sigma_h$) and the degree of local environmental noise ($\sigma_l$) separately to create contrasting patterns of habitat heterogeneity.
-Specifically, we used two values (0.01 and 1) for each of the SD parameters.
-When $\sigma_h > \sigma_l$, branching exhibits important effects on habitat heterogeneity in the ecosystem because headwaters are the primary source of environmental variation.
-When $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on habitat heterogeneity in the ecosystem.
-
+We used `r n_scenario` sets of parameter combinations (i.e., simulation scenarios) based on the results of extensive sensitivity analysis (**Supplementary Information**).
+The parameter combinations comprises four landscape and eight ecological scenarios.
+Landscape scenarios distinguish spatial patterns of ecosystem's habitat heterogeneity, while ecological scenarios change ecological traits of simulated species.
+For landscape scenarios, we used four combinations of environmental variation at headwaters ($\sigma_h = 0.01, 1$) and the degree of local environmental noise ($\sigma_l = 0.01, 1$).
+The inequality of $\sigma_h$ and $\sigma_l$ controls the coupling of branching complexity and ecosystem's habitat heterogeneity.
 For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`).
@@
 We allowed interspecific variation in niche optimum and width, which were drawn from uniform distributions as $\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$.
-We used fixed values for the following parameters: maximum reproductive rate ($r_{0,i} =$ 4), niche cost ($\nu =$ `r unique(dat_sim$niche_cost)`), the degree of temporal fluctuation in abiotic environments ($\sigma_z =$ `r unique(dat_sim$sd_env)`), and the degree of spatial autocorrelation in temporal environmental dynamics ($\phi =$ `r unique(dat_sim$phi)`).
+We used fixed values for the following parameters: maximum reproductive rate ($r_{0,i} =$ 4), niche cost ($\nu =$ `r unique(dat_sim$niche_cost)`), the degree of temporal environmental variation ($\sigma_z =$ `r unique(dat_sim$sd_env)`), and the extent of spatial autocorrelation in temporal environmental dynamics ($\phi =$ `r unique(dat_sim$phi)`).
 
@@
 Ecosystem size and complexity were drawn randomly from uniform distributions as: $N_p \sim Unif(10, 150)$ and $P_b \sim Unif(0.01, 0.99)$ ($N_p$ was rounded to the nearest integer before running simulations).
+Values of simulation parameters were summarized in **Table S2**.
+We performed simulations using R version 4.0.2[@rcoreteamLanguageEnvironmentStatistical2020].
 
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@giamEnvironmentPredationGovern2016], while posing challenges for stream fishes to traverse across watersheds (the ocean or lentic habitats).
+These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@giamEnvironmentPredationGovern2016], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
 Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (**Supplementary Information**).
@@
 Observations ranged from `r min(dat_hkd_site$Year, na.rm = T)` to `r max(dat_hkd_site$Year, na.rm = T)` in Hokkaido and from `r min(dat_mw_site$Year, na.rm = T)` to `r max(dat_mw_site$Year, na.rm = T)` in the Midwest.
-Fish species observed in the final data set were listed in **Tables S2 and S3**.
+Fish species observed in the final data set were listed in **Tables S5 and S6**.
 
@@
 Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control these effects statistically.
-We did not include the fractions of urban and agricultural land use in the statistical models because these variables are strongly correlated with the fraction of forest land use (**Figure S19**).
+We did not include the fractions of urban and agricultural land use in the statistical models because these variables were strongly correlated with the fraction of forest land use (**Figure S19**).
 Similarly, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**).
@@
 
-Climate (air temperature and precipitation) and land use (fraction of forest and dam density) differed clearly between the regions.
+Climate (air temperature and precipitation) and land use (the fraction of forest and dam density) differed clearly between the regions.
 Therefore, we used residuals of the simple linear regressions between the climate or land use variable (response variable) and region (explanatory variable).
@@
 $$
+
 where $\xi_k$ are the intercept and regression coefficients for linear predictors.
@@
 $$
-where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$.
+
+where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$. We performed statistical analysis using R version 4.0.2[@rcoreteamLanguageEnvironmentStatistical2020].
 

### 2021-01-29 supplementary_information.Rmd
Update supplementary_information.Rmd

@@
                                     digits = 3,
+                                    dep.var.caption  = "Response variable",
                                     dep.var.labels.include = FALSE,
@@
                                   digits = 3,
+                                  dep.var.caption  = "Response variable",
                                   dep.var.labels.include = FALSE,
@@
 We extracted 500 estimates of $\psi_1$ and $\psi_2$, which represent the effects of $N_{p}$ and $P_{b}$ on diversity metrics under a given parameter combination.
-To examine influences of simulation parameters (**Table S1**) on $\psi_1$ and $\psi_2$, we developed the following regression model taking $\psi_1$ or $\psi_2$ as a dependent variable $u_k$ (parameter combination $k$):
+To examine influences of simulation parameters (**Table S1**) on $\psi_1$ and $\psi_2$, we developed the following regression model taking $\psi_1$ or $\psi_2$ as a response variable $u_k$ (parameter combination $k$):
 
@@
 1. We used the latest observation at each sampling site to minimize variation in sampling efforts among sites.
+
+## Asymptotic species richness
+
+We evaluated sensitivity of asymptotic species richness (Chao 2 estimator) to sample size (i.e., the number of sampling sites in a watershed).
+We simulated presence-absence data of species with a known value of true species richness $S_{true}$ and the number of sampling sites $N_{site}$.
+In this simulation, presence of species $i$ at site $x$, $I_{ix}$, was drawn from a Bernoulli distribution as $I_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$.
+Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}I_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT'[@hsiehINEXTPackageRarefaction2016].
+We calculated % bias of estimated asymptotic species richness $S_{est}$:
+
+$$
+\%~bias = \frac{100(S_{est} - S_{true})}{S_{true}}
+$$
+
+Positive values of % bias indicate an overestimation of species richness, while negative values indicate an underestimation.
+
+We used the following values for parameters: $S_{true} = 10, 40, 70, 100$ and $N_{site} = 5, 10, 15, 20, 100$.
+We produced 100 replicates of simulated data sets for each parameter combination, resulting in a total of 2000 simulation replicates.
+In each simulation replicate, the probabilities of detection and true presence were drawn randomly from uniform distributions as $p_i \sim Unif(0.3, 0.8)$ and $\kappa_{ix} \sim Unif(0, 1)$.
+
+The number of sampling sites influenced the estimation accuracy of asymptotic species richness.
+The % bias decreased sharply as the number of sampling sites increased (**Figure S20**).
+In particular, the estimation bias with a small sample size ($N_{site} = 5$) was substantial when the true species richness $S_{true}$ was low; some estimates showed > 150 % bias (**Figure S20**).
+Given the simulation results, estimates of asymptotic species richness at watersheds with < 10 sampling sites may involve substantial statistical uncertainty.
 
@@
 Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
-Dependent variables are the effects of the number of habitat patches ($N_{p}$) on $\alpha$, $\beta$, and $\gamma$ diversity.
+Response variables are the effects of the number of habitat patches ($N_{p}$) on $\alpha$, $\beta$, and $\gamma$ diversity.
 Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.
@@
 Parameter estimates of linear regression models (standard errors in parenthesis) are shown.
-Dependent variables are the effects of branching probability ($P_{b}$) on $\alpha$, $\beta$, and $\gamma$ diversity.
+Response variables are the effects of branching probability ($P_{b}$) on $\alpha$, $\beta$, and $\gamma$ diversity.
 Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.
@@
 **Figure S19 ** Correlation structure of potential explanatory variables for riverine diversity metrics.
+Numeric values in each cell are the Pearson's correlation coefficients.
 Positive and negative correlations were colored in blue and red, respectively, and darker colors indicate stronger correlations.
@@
 
+## Figure S20 Sensitivity analysis of asymptotic species richness
+
+```{r fig_s20, fig.height = 6, fig.width = 8}
+
+source(here::here('empirical/figure_iNEXT_sim.R'))
+
+```
+
+**Figure S20 ** Sensitivity analysis of asymptotic species richness in relation to true species richness $S_{true}$ and the number of sampling sites $N_{site}$.
+Positive values of % bias indicate overestimation of species richness, while negative values indicate underestimation.
+Different panels show results with different true species richness.
+The box boundaries represent 25 and 75 percentiles and the whiskers represent 5 and 95 percentiles.
+Dots represent individual simulation replicates.
+
+\newpage
+
 # References

### 2021-01-29 supplementary_information.Rmd
Update supplementary_information.Rmd

@@
 
-## Longitudinal gradients of local species richness
+## Longitudinal gradient of local species richness
 
@@
 
-```{r fig_s20, fig.height = 6, fig.width = 8}
+```{r fig_s20, fig.height = 6, fig.width = 6}
 
@@
 
-**Figure S20 ** Sensitivity analysis of asymptotic species richness in relation to true species richness $S_{true}$ and the number of sampling sites $N_{site}$.
-Positive values of % bias indicate overestimation of species richness, while negative values indicate underestimation.
+**Figure S20 ** Sensitivity analysis of asymptotic species richness in relation to true species richness $S_{true}$ (panels) and the number of sampling sites $N_{site}$ (x-axis).
+Positive values of % bias indicate an overestimation of species richness, while negative values indicate an underestimation.
 Different panels show results with different true species richness.

### 2021-02-03 table.Rmd
edits: change caption for response variable

@@
 The 95\\% confidence intervals are shown in parenthesis.
-Dependent variables were log-10 transformed.
+Response variables were log-10 transformed.
 Climate and land use variables (air temperature, precipitation, logit fraction of forest, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.",
@@
                      digits = 2,
+                     dep.var.caption  = "Response variable",
                      dep.var.labels.include = FALSE,

### 2021-02-03 supplementary_information.Rmd
edits: si info, minor edits

@@
                                                       "Effect of $N_{p}$ on $\\gamma$ diversity"),
-                                    keep.stat = c("rsq"),
+                                    report = "vcs",
+                                    omit.table.layout = "ns",
                                     model.numbers = FALSE)
@@
                                                     "Effect of $P_{b}$ on $\\gamma$ diversity"),
-                                  keep.stat = c("rsq"),
+                                  report = "vcs",
+                                  omit.table.layout = "ns",
                                   model.numbers = FALSE)
@@
 The first 400 time steps were discarded as initialization and burn-in periods.
+We removed simulation replicates in which no species established populations over the initial 400 time steps.
 
@@
 
-where $\psi_q$ ($q = 0-2$) are the intercept ($\psi_0$) and regression coefficients ($\psi_1$ and $\psi_2$).
+where $\psi_k$ ($k = 0-2$) are the intercept ($\psi_0$) and regression coefficients ($\psi_1$ and $\psi_2$).
 We extracted 500 estimates of $\psi_1$ and $\psi_2$, which represent the effects of $N_{p}$ and $P_{b}$ on diversity metrics under a given parameter combination.
-To examine influences of simulation parameters (**Table S1**) on $\psi_1$ and $\psi_2$, we developed the following regression model taking $\psi_1$ or $\psi_2$ as a response variable $u_k$ (parameter combination $k$):
+To examine influences of simulation parameters (**Table S1**) on $\psi_1$ and $\psi_2$, we developed the following regression model taking $\psi_1$ or $\psi_2$ as a response variable $u_n$ (parameter combination $n$):
 
@@
 \begin{aligned}
-u_{k} &\sim Normal(\mu_k, \sigma^2)\\
-\mu_k &= \zeta_0 + \zeta_1 \sigma_{h,k} + \zeta_2 \sigma_{l,k} + \zeta_3 \sigma_{z,k} + \zeta_4 \phi_k + \zeta_5 \nu_k + \zeta_6 \alpha_{max, k} + \zeta_7 \theta_k + \zeta_8 p_{d,k} 
+u_{n} &\sim Normal(\mu_n, \sigma^2)\\
+\mu_n &= \zeta_0 + \zeta_1 \sigma_{h,n} + \zeta_2 \sigma_{l,n} + \zeta_3 \sigma_{z,n} + \zeta_4 \phi_n + \zeta_5 \nu_n + \zeta_6 \alpha_{max, n} + \zeta_7 \theta_n + \zeta_8 p_{d,n} 
 \end{aligned}
 $$
-where $\zeta_q$ ($q = 0-8$) are the intercept and regression coefficients.
+where $\zeta_k$ ($k = 0-8$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-8}$).
 Explanatory variables were standardized to a mean of zero and a standard deviation of one, so that regression coefficients are comparable.
@@
 The first 400 time steps were discarded as initialization and burn-in periods.
+We removed simulation replicates in which no species established populations over the initial 400 time steps.
 We evaluated the relationship between local species richness and the number of upstream habitat patches, a proxy for the longitudinal position of a habitat patch.
@@
 Therefore, the simulation scenarios were capable of reproducing previously observed patterns, suggesting the appropriateness in the choice of parameter combinations.
+
+\newpage
 
@@
 
-**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
+**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources[@wiltonBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@ilepaIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency[@mpcaDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources[@wdnrGuidelinesAssessingFish2018].
 These data sets cover most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined
@@
 We evaluated sensitivity of asymptotic species richness (Chao 2 estimator) to sample size (i.e., the number of sampling sites in a watershed).
-We simulated presence-absence data of species with a known value of true species richness $S_{true}$ and the number of sampling sites $N_{site}$.
-In this simulation, presence of species $i$ at site $x$, $I_{ix}$, was drawn from a Bernoulli distribution as $I_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$.
-Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}I_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT'[@hsiehINEXTPackageRarefaction2016].
+We simulated presence-absence data of species with known values of true species richness $S_{true}$ and the number of sampling sites $N_{site}$.
+In this simulation, presence of species $i$ at site $x$, $J_{ix}$, was drawn from a Bernoulli distribution as $J_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$.
+Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT'[@hsiehINEXTPackageRarefaction2016].
 We calculated % bias of estimated asymptotic species richness $S_{est}$:
@@
 The % bias decreased sharply as the number of sampling sites increased (**Figure S20**).
-In particular, the estimation bias with a small sample size ($N_{site} = 5$) was substantial when the true species richness $S_{true}$ was low; some estimates showed > 150 % bias (**Figure S20**).
+In particular, the estimation bias with a small sample size ($N_{site} = 5$) was substantial when the true species richness $S_{true}$ was low; some estimates showed > 150% bias (**Figure S20**).
 Given the simulation results, estimates of asymptotic species richness at watersheds with < 10 sampling sites may involve substantial statistical uncertainty.
@@
   figure_cap[i] <- paste0("Theoretical predictions for longitudinal gradients of local species richness in branching networks.
-The longitudinal position of each habitat patch (x axis) was expressed as the number of upstream contributing patches.
+The longitudinal position of each habitat patch (x-axis) was expressed as the number of upstream habitat patches.
 `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
@@
 Different panels show results with different true species richness.
-The box boundaries represent 25 and 75 percentiles and the whiskers represent 5 and 95 percentiles.
+The center lines are median values, the box boundaries 25 and 75 percentiles, and the whiskers 5 and 95 percentiles.
 Dots represent individual simulation replicates.

### 2021-02-03 manuscript.Rmd
edits: minor updates on mansucript

@@
 - Seoghyun Kim\footnotemark[1]
-- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of Minnesota]
+- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of
+  Minnesota]
 - Taku Kadoya^[National Institute for Environmental Studies]
@@
 output:
+  word_document: default
   html_notebook: default
-  word_document: default
-abstract:
-  The species-area relationship (the SAR), a tendency in which species richness increases with increasing area, is one of the most robust empirical generalizations in ecology and has formed the basis of area-based conservation strategies.
+abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is one of the most robust empirical generalizations in ecology and has formed the basis of area-based conservation strategies.
 However, many ecosystems possess a complex spatial structure that cannot be represented by area (the scale-invariant complexity), and its role in scaling biodiversity is largely unknown.
-Here, we hypothesized that ecosystem size and complexity jointly regulate biodiversity in rivers.
+Here, we hypothesize that ecosystem size and complexity jointly regulate biodiversity in rivers.
 Rivers are a prime example of fractal branching networks where the recurrent merging of diverse streams generates a pronounced self-similarity in complex branching patterns.
@@
 Ecosystem size and complexity increased watershed-scale species richness ($\gamma$ diversity), and the importance of spatial turnover in species composition ($\beta$ diversity) was apparent when simulated species dispersal is limited.
-Cross-watershed comparisons across two biogeographic regions (the Hokkaido island in Japan and the midwestern US) provided empirical support for the theoretical predictions.
+Cross-watershed comparisons across two geographic regions (the Hokkaido island in Japan and the midwestern US) provided empirical support for the theoretical predictions.
 In both regions, watershed-scale species richness increased with ecosystem size (watershed area) and complexity (branching probability) through enhanced spatial turnover in species composition over the branching network.
 There is now a clear need to consider the dimension of ecosystem complexity in biodiversity conservation.
-The dual dimensional approach - size and complexity - should broaden viable options for spatial planning of protected areas or restoration sites, thereby helping reconcile the pervasive conflict between biodiversity conservation and societal demands.
-
+The dual dimensional approach - size and complexity - should broaden viable options for spatial planning of protected areas or restoration, thereby helping conserve biodiversity from societal demands that threaten it.
 bibliography: reference.bib
@@
 Ecologists have long sought to understand the general drivers of biodiversity.
-One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR)[@lomolinoEcologyMostGeneral2000a].
+One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR)[@lomolinoEcologyMostGeneral2000].
 In 1921, Arrhenius[@arrheniusSpeciesArea1921] formulated the SAR as a power-law $S = cA^z$, an equation currently known as the Arrhenius species-area relationship ($S$ is the number of species observed in a given geographic area $A$, $c$ the constant, and $z$ the scaling exponent).
-Since then, the spatial scaling of species richness has been observed in many taxonomic groups[@triantisIslandSpeciesArea2012].
+Since then, the spatial scaling of species richness has been observed in many taxonomic groups[@triantisIslandSpeciesareaRelationship2012].
 The SAR is ubiquitous because multiple mechanisms produce an apparently similar pattern.
-Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity[@kallimanisHowDoesHabitat2008a], larger metacommunity size[@ben-hurDisentanglingMechanismsUnderlying2020;@hubbellUnifiedNeutralTheory2001], and/or enhanced colonization dynamics[@lososTheoryIslandBiogeography2009].
-Importantly, the SAR provides the foundation for global conservation efforts.
-For example, conservation ecologists have used the SAR estimates to design marine and terrestrial protected areas, which currently encompass more than 30 million km^2^ globally[@deguignet2014UnitedNations2014].
+Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity[@kallimanisHowDoesHabitat2008], larger metacommunity size[@hubbellUnifiedNeutralTheory2001], and/or enhanced colonization dynamics[@lososTheoryIslandBiogeography2009].
+Importantly, the SAR provides the foundation for global conservation efforts[@myersBiodiversityHotspotsConservation2000; @desmetUsingSpeciesareaRelationship2004;@neigelSpeciesareaRelationshipsMarine2003].
+For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas[@desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003], which currently encompass more than 30 million km^2^ globally[@deguignet2014UnitedNations2014].
 
-Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity[@rinaldoEvolutionSelectionRiver2014; @rodriguez-iturbeFractalRiverBasins2001].
+Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity[@turnerLandscapeEcologyTheory2015;@rodriguez-iturbeFractalRiverBasins2001].
 Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few[@rodriguez-iturbeFractalRiverBasins2001].
 Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike[@rodriguez-iturbeFractalRiverBasins2001].
-Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms[@grantLivingBranchesPopulation2007; @rinaldoRiverNetworksEcological2018;@tonkinRoleDispersalRiver2018].
-Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure[@faganConnectivityFragmentationExtinction2002; @grantUseMultipleDispersal2010; @teruiMetapopulationStabilityBranching2018], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@altermattDiversityRiverineMetacommunities2013; @carraraComplexInteractionDendritic2014; @carraraDendriticConnectivityControls2012; @teruiMetapopulationStabilityBranching2018].
-However, most research has explored the consequences of branching complexity for local community structure[@altermattRiverNetworkProperties2013; @brownDendriticNetworkStructure2010] or has relied solely on theoretical arguments with limited replications of branching architecture[@holtRoleBranchingMaintenance2018].
+Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms[@grantLivingBranchesPopulation2007].
+Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure[@carraraDendriticConnectivityControls2012; @faganConnectivityFragmentationExtinction2002; @teruiMetapopulationStabilityBranching2018;@brownDendriticNetworkStructure2010], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@rinaldoRiverNetworksEcological2018;@petersonModellingDendriticEcological2013].
+For example, this research has highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches[@carraraDendriticConnectivityControls2012].
+However, most research has explored the consequences of branching complexity for local community structure[@brownDendriticNetworkStructure2010; @carraraDendriticConnectivityControls2012] or has relied solely on theoretical arguments with limited replications of branching architecture[@holtRoleBranchingMaintenance2018].
 At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
@@
 The recurrent merging of diverse streams and rivers produces larger, ecologically distinct channels, ultimately forming a fluvial network with fractal branching patterns[@rodriguez-iturbeFractalRiverBasins2001].
-As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a], should control the ecosystem's habitat heterogeneity (habitat diversity per unit area).
+As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], should control the ecosystem's habitat heterogeneity (habitat diversity per unit area).
 Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity).
@@
 First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
-We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**).
+We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**).
 Two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
@@
 When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation.
-This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries [@chezikRiverNetworksDampen2017; @mooreEmergentStabilityLarge2015; @petersonModellingDendriticEcological2013].
+This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries[@mooreEmergentStabilityLarge2015; @petersonModellingDendriticEcological2013].
 In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on habitat heterogeneity.
-This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities[@mooreSynchronizationPortfolioPerformance2010; @poffHomogenizationRegionalRiver2007; @teruiMetapopulationStabilityBranching2018].
+This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities[@poffHomogenizationRegionalRiver2007; @teruiMetapopulationStabilityBranching2018].
 Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity within a network.
@@
 The strength of competition decreased the maximum of $\alpha$ diversity but did not change the scaling relationships with ecosystem properties (**Figures 2 and 3**).
-In summary, our theory highlights how the apparently similar patterns in $\gamma$ diversity emerge through different ecological pathways.
+In summary, our theory highlights how apparently similar patterns in $\gamma$ diversity emerge through different ecological pathways.
 
@@
 Therefore, this landscape scenario decouples the intimate relationship between branching structure and habitat heterogeneity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
-This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, substrate, and flow/sediment regimes[@altermattDiversityRiverineMetacommunities2013; @bendaNetworkDynamicsHypothesis2004; @mooreEmergentStabilityLarge2015; @nakamuraDisturbanceRegimesStream2000; @petersonModellingDendriticEcological2013; @teruiMetapopulationStabilityBranching2018].
+This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, and flow/sediment regimes[@petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015].
 Instead, it may be more relevant to severely altered landscapes where human disturbance compromises the environmental distinctiveness of branches through, for example, flow regulations by dams[@poffHomogenizationRegionalRiver2007].
@@
 
-Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`): this result suggests the consistent effects of ecosystem size and complexity on $\gamma$ diversity across the two biogeographic regions.
+Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`): this result suggests the consistent effects of ecosystem size and complexity on $\gamma$ diversity across the two geographic regions.
 Furthermore, the observed patterns were closely aligned with our theoretical predictions (**Table 1 and Figure 4**).
@@
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly matches the previous observations of stream fish movement.
-Direct (mark-recapture) and indirect observations (e.g., genotyping) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters[@comteFishDispersalFlowing2018; @radingerPatternsPredictorsFish2014; @rodriguezRestrictedMovementStream2002].
+Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters[@radingerPatternsPredictorsFish2014].
 The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
@@
 In support of this interpretation, $\beta$ diversity increased with increasing branching probability in both regions (**Figure 4**).
-It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, persist in human-dominated landscapes to maintain the diversity of in-stream processes among tributaties[@bendaNetworkDynamicsHypothesis2004].
-Although our analysis is correlative and cannot provide conclusive evidence, the finding is encouraging because the branching complexity of river networks may serve as a natural defense system to human-induced environmental changes.
+It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, persist in human-dominated landscapes to maintain the diversity of in-stream processes among tributaties.
+Although our analysis is correlative, the finding is encouraging because the branching complexity of river networks may serve as a natural defense system to human-induced environmental changes.
 
@@
 First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
-Human-induced habitat alterations, including flow regulation[@poffHomogenizationRegionalRiver2007], landscape modification[@finlayStreamSizeHuman2011; @moritaEffectsHabitatFragmentation2002], and stream burial[@elmoreDisappearingHeadwatersPatterns2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
+Human-induced habitat alterations, including flow regulation[@poffHomogenizationRegionalRiver2007], landscape modification[@finlayStreamSizeHuman2011; @grillMappingWorldFreeflowing2019], and stream burial[@elmoreDisappearingHeadwatersPatterns2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
 Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human activities.
 Second, the complexity perspective may provide insights into the spatial planning of conservation efforts.
-Riverine reserves and local restoration are increasingly recognized as an effective management tool, and designing a spatial network of conservation sites in rivers is an area of active research[@koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013; @sundermannRiverRestorationSuccess2011].
-While large reserves or restoration sites are undoubtedly important[@koningNetworkGrassrootsReserves2020], our results indicate the potential of coordinated networks of local conservation sites in protecting biodiversity.
+Riverine reserves and local restoration are increasingly recognized as an effective management tool, and designing a spatial network of conservation sites in rivers is an area of active research[@koningNetworkGrassrootsReserves2020].
+While large reserves or restoration sites are undoubtedly important, our results indicate the potential of coordinated networks of local conservation sites in protecting biodiversity.
 For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin[@koningNetworkGrassrootsReserves2020].
@@
 However, the ubiquity of scale-invariant complexity across terrestrial[@turnerLandscapeEcologyTheory2015] and aquatic ecosystems[@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
-Our fundamental findings should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
-The dual dimensional approach - size and complexity - broadens viable options for spatial planning of protected areas or restoration sites, thereby helping reconcile the pervasive conflict between biodiversity conservation and societal demands.
+Our fundamental findings of the dual control of biodiversity should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
+The dual dimensional approach - size and complexity - broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
 The generalization of our findings in spatially complex ecosystems represents a frontier for future research.
@@
 
-We depicted branching ecosystems as a bifurcating network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014a] (**Figure 1**).
+We depicted branching ecosystems as a bifurcating network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**).
 Habitat patches, or local communities, can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
@@
 
-The environmental value at patch $x$ and time $t$, $z_x(t)$, is assumed to follow a multivariate normal distribution as $z_{x}(t) \sim MVN(\mu_z, \Omega_z)$.
-$\mu_z$ is the vector of mean environmental conditions of habitat patches, and $\Omega_z$ is the variance-covariance matrix.
-Spatial autocorrelation in temporal environmental dynamics is considered by expressing the off-diagonal elements as:
+The environmental value at patch $x$ and time $t$, $z_x(t)$, is assumed to follow a multivariate normal distribution as $z_{x}(t) \sim MVN(\boldsymbol{\mu_z}, \boldsymbol{\Omega_z})$, where $\boldsymbol{\mu_z}$ is the vector of mean environmental conditions of habitat patches and $\boldsymbol{\Omega_z}$ is the variance-covariance matrix.
+The diagonal elements of the variance-covariance matrix $\sigma^2_z$ represent the degree of temporal environmental variation.
+The off-diagonal elements $\Omega_{xy}$ represent spatial autocorrelation in temporal environmental variation as:
 
@@
 
-$\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (the shortest network path [measured as the number of habitat patches] to reach a target patch).
+$\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (the shortest network path measured as the number of habitat patches).
 The parameter $\phi$ determines the degree of the distance decay of environmental correlates.
@@
 $$
-where $d_{xy}$ is the separation distance between patch $x$ and $y$ (the shortest network path [measured as the number of habitat patches] to reach a target patch).
 The parameter $\theta$ regulates the dispersal distance of a species that follows an exponential distribution ($\theta^{-1}$ corresponds to the expected dispersal distance).
@@
 
-We compiled fish data at two biogeographic regions: the Hokkaido island, Japan, and the Midwest, US.
+We compiled fish data at two geographic regions: the Hokkaido island, Japan, and the Midwest, US.
 For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaHokkaidoFreshwaterFish2011; @fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors[@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island.
-For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources, Illinois Environmental Protection Agency and Illinois Department of Natural Resources, Minnesota Pollution Control Agency, and Wisconsin Department of Natural Resources.
+For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources[@wiltonBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@ilepaIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency[@mpcaDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources[@wdnrGuidelinesAssessingFish2018].
 We detailed procedures for initial data selection in **Supplementary Information**.
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@giamEnvironmentPredationGovern2016], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
+These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@comteFishDispersalFlowing2018; @giamEnvironmentPredationGovern2016], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
 Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (**Supplementary Information**).
@@
 Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014a; @chaseEcosystemDecayExacerbates2020].
-We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package iNEXT[@hsiehINEXTPackageRarefaction2016].
+We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT'[@hsiehINEXTPackageRarefaction2016].
 We assessed the completeness of the observed species richness based on sample coverage, which is the proportion of observed species richness to asymptotic species richness.
@@
 
-We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]).
-We delineated watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area) using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] with ArcMap 10.7 and SAGA 6.3.0 combined with the R package 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018].
-Watershed area was estimated based on the delineated watershed polygons using functions in the R package 'sf'[@pebesmaSimpleFeaturesStandardized2018].
+We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]).
+We delineated watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area) using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019], which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^), or a large river ($\ge$ 5000 km^2^ in the watershed area).
+The ocean and large lakes/reservoirs were extracted based on Global 1-second Water Body Map ver 1.0[@yamazakiDevelopmentGlobal90m2015].
+Watershed area was estimated based on the delineated watershed polygons.
 We estimated branching probability by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$.
 A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
-We obtained mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019].
-We estimated the spatial averages of air temperature and cumulative precipitation at a 1-km resolution for each watershed, which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005] via the R package 'raster.' We calculated the fraction of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
-We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1)[@lehnerGlobalReservoirDam2011; @lehnerHighResolutionMappingWorld2011].
+We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019].
+We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (~1 km resolution), which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005].
+We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
+We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1)[@lehnerGlobalReservoirDam2011; @lehnerHighresolutionMappingWorld2011].
+We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018], 'sf'[@pebesmaSimpleFeaturesStandardized2018], 'raster'[@hijmansRasterGeographicData2020], 'rgdal'[@rogerbivandRgdalBindingsGeospatial2020], 'stars'[@edzerpebesmaStarsSpatiotemporalArrays2020], and 'exactextractr'[@danielbastonExactextractrFastExtraction2020].
 
@@
 We developed linear regression models to examine the effects of macro-scale drivers on diversity metrics.
-Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $i$, $log_{10}~y_i$, are assumed to follow a normal distribution as $log_{10}~y_i \sim Normal(\mu_i, \sigma^2)$.
-The parameter $\mu_i$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, and the fraction of forest land use (logit-transformed).
-Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control these effects statistically.
+Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$.
+The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of forest land use (logit-transformed), and dam density.
+Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically.
 We did not include the fractions of urban and agricultural land use in the statistical models because these variables were strongly correlated with the fraction of forest land use (**Figure S19**).
@@
 We constructed two models for each of the diversity metrics: global and region-specific models.
-The global model assumes that the effects of watershed area and branching probability are consistent across biogeographic regions (i.e., no interactive effects of the region with other linear predictors).
+The global model assumes that the effects of watershed area and branching probability are consistent across geographic regions (i.e., no interactive effects of the region with other linear predictors).
 
 $$
-\mu_i = \xi_0 + \xi_1~log_{10}~WA_i + \xi_2~log_{10}~P_{b,i} + \xi_3~region_i + \sum_k \xi_k x_{k,i}
+\mu_w = \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
 $$
@@
 $$
-\mu_i = \xi_0 + \xi_1~log_{10}~WA_i + \xi_2~log_{10}~P_{b,i} + \xi_3~region_i + \xi_4~log_{10}~WA_i \cdot region_i + \xi_5~log_{10}~P_{b,i} \cdot region_i + \sum_k \xi_k x_{k,i}
+\begin{align}
+\mu_w =& \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w +\\
+&\xi_4~log_{10}~WA_w \cdot region_w + \xi_5~log_{10}~P_{b,w} \cdot region_w + \sum_k \xi_k x_{k,w}
+\end{align}
 $$
@@
 # Acknowledgements
-We acknowledge numerous people who have been involved in the collection of fish community data. We thank Michio Fukushima for providing information on the Hokkaido Freshwater Fish Database HFish.
+We are grateful to numerous people who have been involved in the collection of fish community data.
+We thank Michio Fukushima and Hirokazu Urabe for providing information on the Hokkaido Freshwater Fish Database HFish and the fish monitoring data at protected watersheds in Hokkaido.
+This research was funded by National Science Foundation through a Water Sustainability and Climate Program (WSC) Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through a Division of Environmental Biology (DEB 2015634) and by Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1).
 
 # Author contributions
+AT conceived of the project.
+AT performed theoretical and statistical analysis with inputs from TK.
+AT, SK, CLD, and YM collected and managed the fish community data set.
+AT wrote the first draft while SK, CLD, TK, and YM contributed significantly to the final version.
 

### 2021-02-09 manuscript.Rmd
edits: abstract in manuscript

@@
 output:
+  html_notebook: default
   word_document: default
-  html_notebook: default
-abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is one of the most robust empirical generalizations in ecology and has formed the basis of area-based conservation strategies.
-However, many ecosystems possess a complex spatial structure that cannot be represented by area (the scale-invariant complexity), and its role in scaling biodiversity is largely unknown.
-Here, we hypothesize that ecosystem size and complexity jointly regulate biodiversity in rivers.
-Rivers are a prime example of fractal branching networks where the recurrent merging of diverse streams generates a pronounced self-similarity in complex branching patterns.
-Ecosystem complexity, which we defined as the probability of branching per unit river distance, should increase watershed-scale species richness by increasing habitat heterogeneity (habitat diversity per unit area).
-Meanwhile, ecosystem size should dictate metacommunity size and total habitat diversity (area x habitat heterogeneity), two factors that regulate watershed-scale species richness.
-We developed theoretical models simulating metacommunity dynamics in branching river networks and yielded results consistent with our hypothesis.
-Ecosystem size and complexity increased watershed-scale species richness ($\gamma$ diversity), and the importance of spatial turnover in species composition ($\beta$ diversity) was apparent when simulated species dispersal is limited.
+abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous ecological pattern[@lomolinoEcologyMostGeneral2000] and has formed the basis of area-based conservation strategies[@desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003].
+However, many ecosystems possess a complex spatial structure that cannot be represented by area (the scale-invariant complexity)[@rodriguez-iturbeFractalRiverBasins2001; @turnerLandscapeEcologyTheory2015], and its role in scaling biodiversity is largely unknown.
+Here, we use theory and empirical analysis of extensive fish community data to show that ecosystem size and complexity jointly regulate biodiversity in rivers.
+Rivers are a prime example of fractal branching networks where the recurrent merging of diverse streams generates a pronounced self-similarity in complex branching patterns[@rodriguez-iturbeFractalRiverBasins2001].
+Ecosystem complexity, which we define as the probability of branching per unit river distance[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], should increase watershed-scale species richness by increasing habitat heterogeneity.
+Meanwhile, ecosystem size should dictate metacommunity size and total habitat diversity, two factors that regulate watershed-scale species richness[@hubbellUnifiedNeutralTheory2001; @kallimanisHowDoesHabitat2008].
+Metacommunity simulations in branching networks predicted biodiversity patterns consistent with our hypothesis.
+Larger and more branched ecosystems supported greater species richness at the watershed scale, and the importance of spatial difference in species composition was apparent when simulated species dispersal is limited.
 Cross-watershed comparisons across two geographic regions (the Hokkaido island in Japan and the midwestern US) provided empirical support for the theoretical predictions.
-In both regions, watershed-scale species richness increased with ecosystem size (watershed area) and complexity (branching probability) through enhanced spatial turnover in species composition over the branching network.
-There is now a clear need to consider the dimension of ecosystem complexity in biodiversity conservation.
-The dual dimensional approach - size and complexity - should broaden viable options for spatial planning of protected areas or restoration, thereby helping conserve biodiversity from societal demands that threaten it.
+In both regions, watershed-scale species richness increased with ecosystem size (watershed area) and complexity (branching probability) through enhanced spatial difference in species composition.
+Recognizing the dual control of biodiversity should broaden viable options for spatial planning of protected areas or restoration, thereby helping conserve biodiversity from societal demands that threaten it.
 bibliography: reference.bib
@@
 At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
-Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006].
+Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006a].
 
@@
 The recurrent merging of diverse streams and rivers produces larger, ecologically distinct channels, ultimately forming a fluvial network with fractal branching patterns[@rodriguez-iturbeFractalRiverBasins2001].
-As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], should control the ecosystem's habitat heterogeneity (habitat diversity per unit area).
+As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], should control the ecosystem's habitat heterogeneity (habitat diversity per unit area).
 Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity).
-We predict that ecosystem size and branching complexity increase watershed-scale species richness ($\gamma$ diversity) by enhancing local species richness ($\alpha$ diversity) and/or spatial turnover of species composition ($\beta$ diversity) under different ecological scenarios.
+We predict that ecosystem size and branching complexity increase watershed-scale species richness ($\gamma$ diversity) by enhancing local species richness ($\alpha$ diversity) and/or spatial difference of species composition ($\beta$ diversity) under different ecological scenarios.
 The present study combines theory and empirical analysis of extensive community data from two different regions of the globe to provide crucial insights into how ecological communities are structured in complex branching networks.
@@
 We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation exists (i.e., species travel short distances).
-This pattern reflects significant spatial turnover of species composition over the branching network.
+This pattern reflects significant spatial difference of species composition over the branching network.
 In contrast, when the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
@@
 We combined this data set with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, the fraction of forest, and dam density) to examine potential influences of macro-scale drivers of species diversity.
-Using this data set, we developed global and region-specific models for each of the diversity measures ($\alpha$, $\beta$, and $\gamma$ diversity) to examine whether observed patterns are consistent across the two geographic regions.
+Using this data set, we assessed whether observed patterns are consistent across the two geographic regions by developing global and region-specific models.
 In the global model, we assumed that effects of ecosystem size (watershed area) and complexity (branching probability) are constant across the two regions (i.e., fixed slopes).
-Meanwhile, the region-specific model assumes region-specific slopes of ecosystem size and complexity by including interaction terms with the dummy binary variable of the region (Hokkaido = 0; Midwest = 1).
+Meanwhile, the region-specific model assumes region-specific slopes of ecosystem size and complexity (**Methods**).
 We compared the support of these competing models using the Bayes factor, a measure of the strength of evidence in favor of one model over the alternative.
-In our definition (see **Methods**), the Bayes factor of $> 1$ indicates the support for the global model over the region-specific model.
+In our definition (**Methods**), the Bayes factor of $> 1$ indicates the support for the global model over the region-specific model.
 
@@
 If the intensive land use by humans causes significant homogenization of in-stream habitat conditions among tributaries, theory predicts a weakened effect of branching probability on $\gamma$ diversity.
-However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions to support high spatial turnover of species composition.
+However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions to support high spatial difference of species composition.
 In support of this interpretation, $\beta$ diversity increased with increasing branching probability in both regions (**Figure 4**).
@@
 Second, it preserves the fractal nature of branching patterns[@peckhamReformulationHortonLaws1999].
+An alternative option is the use of optimal channel networks[@carraroGenerationApplicationRiver2020].
+However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to link theoretical predictions with empirical observations.
 
@@
 Two sources of variation characterize the long-term average of the abiotic environment at each habitat patch: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
-We draw random values from a normal distribution with a mean of zero and SD of $\sigma_{h}$ and assigned them to headwater patches (i.e., the most upstream patches).
+We drew random values from a normal distribution with a mean of zero and a standard deviation of $\sigma_{h}$ and assigned them to headwater patches (i.e., the most upstream patches).
 These environmental values at headwaters propagate downstream through a spatial autoregressive process defined as:
@@
 
-where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and SD of $\sigma_l$.
+where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and a standard deviation of $\sigma_l$.
 The parameter $\rho$ can take values of $0-1$ with larger values indicating greater spatial autocorrelation.
@@
 The realized discrete number of individuals is drawn from a Poisson distribution to account for stochasticity in demographic and dispersal processes[@fronhoferClassicalMetapopulationDynamics2017; @thompsonProcessbasedMetacommunityFramework2020].
-Local community dynamics are simulated based on the Beverton-Holt equation:
+Local community dynamics are simulated based on the Beverton-Holt equation[@bevertonDynamicsExploitedFish1957]:
 
@@
 $$
-r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{(\mu_i-z_x(t))^2}{2\sigma^2_{niche,i}}}]
+r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{\{\mu_i-z_x(t)\}^2}{2\sigma^2_{niche,i}}}]
 $$
 where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$.
-Species with a wider niche (greater values of $\sigma_{niche}$) should always have a greater competitive ability in the absence of the cost of a wide niche.
-Therefore, we introduced the cost of a wide niche by multiplying $\delta$[@chaianunpornEvolutionaryResponsesClimate2015]:
+We introduced the cost of a wide niche by multiplying $\delta$[@chaianunpornEvolutionaryResponsesClimate2015]:
 
@@
 The parameter combinations comprises four landscape and eight ecological scenarios.
-Landscape scenarios distinguish spatial patterns of ecosystem's habitat heterogeneity, while ecological scenarios change ecological traits of simulated species.
+Landscape scenarios distinguish spatial patterns of habitat heterogeneity, while ecological scenarios change ecological traits of simulated species.
 For landscape scenarios, we used four combinations of environmental variation at headwaters ($\sigma_h = 0.01, 1$) and the degree of local environmental noise ($\sigma_l = 0.01, 1$).
-The inequality of $\sigma_h$ and $\sigma_l$ controls the coupling of branching complexity and ecosystem's habitat heterogeneity.
+The inequality of $\sigma_h$ and $\sigma_l$ controls the coupling of branching complexity and habitat heterogeneity.
 For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`).
@@
 For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaHokkaidoFreshwaterFish2011; @fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors[@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island.
-For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources[@wiltonBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@ilepaIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency[@mpcaDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources[@wdnrGuidelinesAssessingFish2018].
+For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources[@iowadepartmentofnaturalresourcesBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@illinoisenvironmentalprotectionagencyIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency[@minnesotapollutioncontrolagencyDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources[@wisconsindepartmentofnaturalresourcesGuidelinesAssessingFish2018].
 We detailed procedures for initial data selection in **Supplementary Information**.
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@comteFishDispersalFlowing2018; @giamEnvironmentPredationGovern2016], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
+These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@comteFishDispersalFlowing2018; @giamEnvironmentPredationGovern2016a], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
 Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (**Supplementary Information**).
@@
 Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014a; @chaseEcosystemDecayExacerbates2020].
+Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014; @chaseEcosystemDecayExacerbates2020].
 We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT'[@hsiehINEXTPackageRarefaction2016].
@@
 $\alpha$ diversity was estimated by taking an average of local species richness at each site.
-$\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity.
+$\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity[@whittakerVegetationSiskiyouMountains1960].
 
@@
 We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]).
-We delineated watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area) using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019], which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^), or a large river ($\ge$ 5000 km^2^ in the watershed area).
-The ocean and large lakes/reservoirs were extracted based on Global 1-second Water Body Map ver 1.0[@yamazakiDevelopmentGlobal90m2015].
+We used Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area).
+The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0[@yamazakiDevelopmentGlobal90m2015].
 Watershed area was estimated based on the delineated watershed polygons.
@@
 AT performed theoretical and statistical analysis with inputs from TK.
-AT, SK, CLD, and YM collected and managed the fish community data set.
+AT, SK, CLD, and YM compiled and managed the fish community data set.
 AT wrote the first draft while SK, CLD, TK, and YM contributed significantly to the final version.

### 2021-02-09 supplementary_information.Rmd
Update supplementary_information.Rmd

@@
 **Hokkaido, Japan.** We used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaHokkaidoFreshwaterFish2011; @fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors[@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island.
-Fish data were collected from summer to fall.
+Most data were collected from summer to fall.
 We screened data through the following procedure:
@@
 1.
-We listed recorded fish species and re-organized species names to be consistent across data sources.
+We listed recorded fish species and re-organized species names to make them consistent across data sources.
 We removed the following species at this stage: (1) identified at the family-level; (2) marine fish species (including species that occasionally use brackish/freshwater habitats).
 1.
-We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve species identified at the genus level that are rarely observed in the data set (< 100 sites occurrence).
+We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve unidentified species (genus level) that are rarely observed in the data set (< 100 sites occurrence).
 1.
@@
 
-**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources[@wiltonBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@ilepaIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency[@mpcaDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources[@wdnrGuidelinesAssessingFish2018].
+**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources[@iowadepartmentofnaturalresourcesBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@illinoisenvironmentalprotectionagencyIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency[@minnesotapollutioncontrolagencyDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources[@wisconsindepartmentofnaturalresourcesGuidelinesAssessingFish2018].
 These data sets cover most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined

### 2021-02-13 figure.Rmd
Create figure.Rmd
edits: Rmd output directory

--- 2021-01-20 figures.Rmd
@@
   pdf_document: default
+knit: (function(inputFile, encoding) {
+        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
+      })
 ---
@@
 Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values).
+In this example, we used values of environmental variation at headwaters $\\sigma_{h} = 1$ and the degree of local environmental noise $\\sigma_{l} = 0.01$.
 (B) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in C).

### 2021-02-13 manuscript.Rmd
edits: Rmd output directory

@@
 output:
+  word_document: default
   html_notebook: default
-  word_document: default
-abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous ecological pattern[@lomolinoEcologyMostGeneral2000] and has formed the basis of area-based conservation strategies[@desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003].
+abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern[@lomolinoEcologyMostGeneral2000] and has formed the basis of area-based conservation strategies[@desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003].
 However, many ecosystems possess a complex spatial structure that cannot be represented by area (the scale-invariant complexity)[@rodriguez-iturbeFractalRiverBasins2001; @turnerLandscapeEcologyTheory2015], and its role in scaling biodiversity is largely unknown.
@@
 csl: nature.csl
+knit: (function(inputFile, encoding) {
+        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
+      })
 ---
@@
 Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure[@carraraDendriticConnectivityControls2012; @faganConnectivityFragmentationExtinction2002; @teruiMetapopulationStabilityBranching2018;@brownDendriticNetworkStructure2010], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@rinaldoRiverNetworksEcological2018;@petersonModellingDendriticEcological2013].
-For example, this research has highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches[@carraraDendriticConnectivityControls2012].
+For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches[@carraraDendriticConnectivityControls2012].
 However, most research has explored the consequences of branching complexity for local community structure[@brownDendriticNetworkStructure2010; @carraraDendriticConnectivityControls2012] or has relied solely on theoretical arguments with limited replications of branching architecture[@holtRoleBranchingMaintenance2018].
 At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
-Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006a].
+Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006].
 
-Here, we hypothesize that ecosystem size and complexity dictate biodiversity patterns in rivers, a prime example of complex branching ecosystems.
+Here, we hypothesize that ecosystem size and complexity dictate biodiversity patterns in rivers - a prime example of complex branching ecosystems.
 The recurrent merging of diverse streams and rivers produces larger, ecologically distinct channels, ultimately forming a fluvial network with fractal branching patterns[@rodriguez-iturbeFractalRiverBasins2001].
@@
 Second, it preserves the fractal nature of branching patterns[@peckhamReformulationHortonLaws1999].
-An alternative option is the use of optimal channel networks[@carraroGenerationApplicationRiver2020].
-However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to link theoretical predictions with empirical observations.
+An alternative approach is the use of optimal channel networks[@carraroGenerationApplicationRiver2020].
+However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to compare theoretical predictions with empirical observations.
 
@@
 $K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area[@altermattRiverNetworkProperties2013; @teruiThreeEcologicalFactors2016].
-The parameter $\alpha_{ij}$ is expressed as the strength of interspecific competition relative to that of intraspecific competition such that interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ > 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
+The parameter $\alpha_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ > 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
 $\alpha_{ij}$ was drawn randomly from a uniform distribution as $\alpha_{ij} \sim Unif(0, \alpha_{max})$.
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@comteFishDispersalFlowing2018; @giamEnvironmentPredationGovern2016a], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
+These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@comteFishDispersalFlowing2018; @giamEnvironmentPredationGovern2016], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
 Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (**Supplementary Information**).
@@
 Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014; @chaseEcosystemDecayExacerbates2020].
+Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014a; @chaseEcosystemDecayExacerbates2020].
 We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT'[@hsiehINEXTPackageRarefaction2016].

### 2021-02-13 empirical/figure_diversity.R
edits: figure source file

@@ -34,7 +34,7 @@
 # read data ---------------------------------------------------------------
   
   ## model estimate
-  source(normalizePath("../empirical/analysis_lm_bf.R"))
+  source("analysis_lm_bf.R")
   
   ## redefine data.frame
   dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")

### 2021-02-14 empirical/table_sim_parameter_main.R
Delete table_sim_parameter_main.R

@@ -1,63 +1,0 @@
-
-# setup -------------------------------------------------------------------
-
-  pacman::p_load(tidyverse, knitr, kableExtra)
-  dat_sim <- read_csv(here::here('/theory/result/result_sim2020-11-10.csv'))
-
-# table -------------------------------------------------------------------
-
-  dat_sim %>% 
-    select(sd_env_source,
-           sd_env_lon,
-           sd_env,
-           rho,
-           phi,
-           niche_cost,
-           max_alpha,
-           theta,
-           p_dispersal
-    ) %>% 
-    summarise(across(everything(), unique)) %>% 
-    mutate(r0 = 4) %>% 
-    pivot_longer(cols = everything(),
-                 names_to = "Parameter",
-                 values_to = "Value") %>% 
-    group_by(Parameter) %>% 
-    summarize(Value = list(unique(Value))) %>% 
-    mutate(id = case_when(Parameter == 'sd_env_source' ~ 'a',
-                          Parameter == 'sd_env_lon' ~ 'b',
-                          Parameter == 'sd_env' ~ 'c',
-                          Parameter == 'rho' ~ 'd',
-                          Parameter == 'phi' ~ 'e',
-                          Parameter == 'niche_cost' ~ 'f',
-                          Parameter == 'max_alpha' ~ 'g',
-                          Parameter == 'theta' ~ 'h',
-                          Parameter == 'p_dispersal' ~ 'i',
-                          Parameter == 'r0' ~ 'j',
-                          TRUE ~ as.character(Parameter)),
-           Interpretation = case_when(Parameter == 'sd_env_source' ~ 'Environmental variation at headwaters',
-                                      Parameter == 'sd_env_lon' ~ 'Degree of local environmental noise',
-                                      Parameter == 'sd_env' ~ 'Temporal environmental variability',
-                                      Parameter == 'rho' ~ 'Strength of spatial autocorrelation in mean environmental condition',
-                                      Parameter == 'phi' ~ 'Extent of spatial autocorrelation in temporal environmental variation',
-                                      Parameter == 'niche_cost' ~ 'Cost of a wider niche',
-                                      Parameter == 'max_alpha' ~ 'Maximum value of interspecific competition coefficient',
-                                      Parameter == 'theta' ~ 'Rate parameter of an exponential dispersal kernel',
-                                      Parameter == 'p_dispersal' ~ 'Dispersal probability',
[…]

### 2021-02-14 empirical/table_splist_hkd.R
edits: tables

@@ -6,7 +6,7 @@
 
 # table -------------------------------------------------------------------
 
-  dat_hkd %>% 
+  table_output <- dat_hkd %>% 
     mutate(n_site = n_distinct(SiteID)) %>% 
     mutate(Species = str_replace_all(str_to_title(Species), "_", " ")) %>% 
     mutate(Species = str_replace_all(Species, "(spp$)|(spp\\s)", "spp\\.")) %>% 
@@ -17,5 +17,3 @@
     summarise('Number of sites present' = n_distinct(SiteID),
               'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
     kable(format = 'markdown')
-
-  print(g)

### 2021-02-14 empirical/table_splist_mw.R

@@ -8,7 +8,7 @@
 
   sp_mw_latin <- read_csv(here::here('/empirical/data_out/data_mw_splist_latin.csv'))
   
-  dat_mw %>% 
+  table_output <- dat_mw %>% 
     mutate(n_site = n_distinct(SiteID)) %>% 
     rename(Common_name = Species) %>% 
     group_by(Common_name) %>% 
@@ -20,5 +20,3 @@
            'Occupancy (%)') %>% 
     arrange(Species) %>% 
     kable(format = 'markdown')
-  
-  print(g)

### 2021-02-14 theory/table_sensitivity_analysis.R

@@ -1,0 +1,72 @@
+
+# setup -------------------------------------------------------------------
+
+  pacman::p_load(tidyverse, knitr, kableExtra)
+  source(here::here("/theory/analysis_sensitivity.R"))
+
+
+# sensitivity tables ------------------------------------------------------
+
+  ## ecosystem size
+  m_area <- fit_sense %>% 
+    mutate(area = str_detect(response, "area")) %>% 
+    filter(area == TRUE)
+  
+  star_area <- stargazer::stargazer(m_area$fit[1],
+                                    m_area$fit[2],
+                                    m_area$fit[3],
+                                    header = FALSE,
+                                    type = "latex",
+                                    covariate.labels = c("$\\sigma_{h}$",
+                                                         "$\\sigma_{l}$",
+                                                         "$\\sigma_{z}$",
+                                                         "$\\phi$",
+                                                         "$\\nu$",
+                                                         "$\\alpha_{max}$",
+                                                         "$\\theta$",
+                                                         "$p_{d}$",
+                                                         "Intercept"),
+                                    single.row = FALSE,
+                                    digits = 3,
+                                    dep.var.caption  = "Response variable",
+                                    dep.var.labels.include = FALSE,
+                                    column.labels = c("Effect of $N_{p}$ on $\\alpha$ diversity",
+                                                      "Effect of $N_{p}$ on $\\beta$ diversity",
+                                                      "Effect of $N_{p}$ on $\\gamma$ diversity"),
+                                    report = "vcs",
+                                    omit.table.layout = "ns",
+                                    model.numbers = FALSE)
+  
+  star_area <- sub('^.+\\caption.+$','', star_area)
+  
+  ## Ecosystem complexity
+  m_bp <- fit_sense %>% 
+    mutate(area = str_detect(response, "area")) %>% 
+    filter(area == FALSE)
+  
+  star_bp <- stargazer::stargazer(m_bp$fit[1],
+                                  m_bp$fit[2],
+                                  m_bp$fit[3],
+                                  header = FALSE,
+                                  type = "latex",
+                                  covariate.labels = c("$\\sigma_{h}$",
+                                                       "$\\sigma_{l}$",
+                                                       "$\\sigma_{z}$",
+                                                       "$\\phi$",
+                                                       "$\\nu$",
+                                                       "$\\alpha_{max}$",
+                                                       "$\\theta$",
+                                                       "$p_{d}$",
[…]

### 2021-02-14 theory/table_sim_parameter_main.R

@@ -1,0 +1,64 @@
+
+# setup -------------------------------------------------------------------
+
+  pacman::p_load(tidyverse, knitr, kableExtra)
+  dat_sim <- read_csv(here::here('/theory/result/result_sim2020-11-10.csv'))
+
+# table -------------------------------------------------------------------
+
+  table_output <- dat_sim %>% 
+    select(sd_env_source,
+           sd_env_lon,
+           sd_env,
+           rho,
+           phi,
+           niche_cost,
+           max_alpha,
+           theta,
+           p_dispersal
+    ) %>% 
+    summarise(across(everything(), unique)) %>% 
+    mutate(r0 = 4) %>% 
+    pivot_longer(cols = everything(),
+                 names_to = "Parameter",
+                 values_to = "Value") %>% 
+    group_by(Parameter) %>% 
+    summarize(Value = list(unique(Value))) %>% 
+    mutate(id = case_when(Parameter == 'sd_env_source' ~ 'a',
+                          Parameter == 'sd_env_lon' ~ 'b',
+                          Parameter == 'sd_env' ~ 'c',
+                          Parameter == 'rho' ~ 'd',
+                          Parameter == 'phi' ~ 'e',
+                          Parameter == 'niche_cost' ~ 'f',
+                          Parameter == 'max_alpha' ~ 'g',
+                          Parameter == 'theta' ~ 'h',
+                          Parameter == 'p_dispersal' ~ 'i',
+                          Parameter == 'r0' ~ 'j',
+                          TRUE ~ as.character(Parameter)),
+           Interpretation = case_when(Parameter == 'sd_env_source' ~ 'Environmental variation at headwaters',
+                                      Parameter == 'sd_env_lon' ~ 'Degree of local environmental noise',
+                                      Parameter == 'sd_env' ~ 'Temporal environmental variability',
+                                      Parameter == 'rho' ~ 'Strength of spatial autocorrelation in mean environmental condition',
+                                      Parameter == 'phi' ~ 'Extent of spatial autocorrelation in temporal environmental variation',
+                                      Parameter == 'niche_cost' ~ 'Cost of a wider niche',
+                                      Parameter == 'max_alpha' ~ 'Maximum value of interspecific competition coefficient',
+                                      Parameter == 'theta' ~ 'Rate parameter of an exponential dispersal kernel',
[…]

### 2021-02-14 supplementary_information.Rmd
edits: sourced tables

--- 2021-02-09 supplementary_information.Rmd
@@
 author:
-- Akira Terui^[Department of Biology, University of North Carolina at Greensboro]
+- Akira Terui^[Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA]
 - Seoghyun Kim\footnotemark[1]
 - Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of
-  Minnesota]
-- Taku Kadoya^[National Institute for Environmental Studies]
-- Yusuke Miyazaki^[Shiraume Gakuen University]
+  Minnesota, St. Paul, MN 55108, USA]
+- Taku Kadoya^[National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan]
+- Yusuke Miyazaki^[Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan]
 output:
@@
 
-  # simulation data main
-  dat_sim <- read_csv(here::here('/theory/result/result_sim2020-11-10.csv'))
-
-  # sensitivity analysis  
-  source(here::here("/theory/analysis_sensitivity.R"))
-
   # Hokkaido data
@@
   # sensitivity tables
-
-  ## ecosystem size
-  m_area <- fit_sense %>% 
-    mutate(area = str_detect(response, "area")) %>% 
-    filter(area == TRUE)
-
-  star_area <- stargazer::stargazer(m_area$fit[1],
-                                    m_area$fit[2],
-                                    m_area$fit[3],
-                                    header = FALSE,
-                                    type = "latex",
-                                    covariate.labels = c("$\\sigma_{h}$",
-                                                         "$\\sigma_{l}$",
-                                                         "$\\sigma_{z}$",
-                                                         "$\\phi$",
-                                                         "$\\nu$",
-                                                         "$\\alpha_{max}$",
-                                                         "$\\theta$",
-                                                         "$p_{d}$",
-                                                         "Intercept"),
-                                    single.row = FALSE,
-                                    digits = 3,
-                                    dep.var.caption  = "Response variable",
-                                    dep.var.labels.include = FALSE,
-                                    column.labels = c("Effect of $N_{p}$ on $\\alpha$ diversity",
-                                                      "Effect of $N_{p}$ on $\\beta$ diversity",
-                                                      "Effect of $N_{p}$ on $\\gamma$ diversity"),
-                                    report = "vcs",
-                                    omit.table.layout = "ns",
-                                    model.numbers = FALSE)
-
-  star_area <- sub('^.+\\caption.+$','', star_area)
-
-  ## Ecosystem complexity
-  m_bp <- fit_sense %>% 
-    mutate(area = str_detect(response, "area")) %>% 
-    filter(area == FALSE)
-
-  star_bp <- stargazer::stargazer(m_bp$fit[1],
-                                  m_bp$fit[2],
-                                  m_bp$fit[3],
-                                  header = FALSE,
-                                  type = "latex",
-                                  covariate.labels = c("$\\sigma_{h}$",
-                                                       "$\\sigma_{l}$",
-                                                       "$\\sigma_{z}$",
-                                                       "$\\phi$",
-                                                       "$\\nu$",
-                                                       "$\\alpha_{max}$",
-                                                       "$\\theta$",
-                                                       "$p_{d}$",
-                                                       "Intercept"),
-                                  single.row = FALSE,
-                                  digits = 3,
-                                  dep.var.caption  = "Response variable",
-                                  dep.var.labels.include = FALSE,
-                                  column.labels = c("Effect of $P_{b}$ on $\\alpha$ diversity",
-                                                    "Effect of $P_{b}$ on $\\beta$ diversity",
-                                                    "Effect of $P_{b}$ on $\\gamma$ diversity"),
-                                  report = "vcs",
-                                  omit.table.layout = "ns",
-                                  model.numbers = FALSE)
-
-    star_bp <- sub('^.+\\caption.+$','', star_bp)
+  source(here::here('theory/table_sensitivity_analysis.R'))
 
@@
 
-  tibble(Parameter = c('$\\sigma_{h}$',
-                       '$\\sigma_{l}$',
-                       '$\\sigma_{z}$',
-                       '$\\rho$',
-                       '$\\phi$',
-                       '$\\nu$',
-                       '$\\alpha_{max}$',
-                       '$\\theta$',
-                       '$p_{d}$',
-                       '$r_{0,i}$'),
-         Value = c('Unif(0.01, 1)',
-                   'Unif(0.01, 1)',
-                   'Unif(0.01, 0.5)',
-                   '1',
-                   'Unif(0.01, 1)',
-                   'Unif(1, 5)',
-                   'Unif(0.5, 1.5)',
-                   'Unif(0.1, 1)',
-                   'Unif(0.01, 0.1)',
-                   '4'),
-         Interpretation = c('Environmental variation at headwaters',
-                            'Degree of local environmental noise',
-                            'Temporal environmental variability',
-                            'Strength of spatial autocorrelation in mean environmental condition',
-                            'Extent of spatial autocorrelation in temporal environmental variation',
-                            'Cost of a wider niche',
-                            'Maximum value of interspecific competition coefficient',
-                            'Rate parameter of an exponential dispersal kernel',
-                            'Dispersal probability',
-                            'Maximum reproductive rate')) %>% 
-    kable(format = 'markdown')
+  source(here::here('empirical/table_sim_parameter_sensitivity.R'))
+  table_output
 
@@
 
-  dat_sim %>% 
-    select(sd_env_source,
-           sd_env_lon,
-           sd_env,
-           rho,
-           phi,
-           niche_cost,
-           max_alpha,
-           theta,
-           p_dispersal
-    ) %>% 
-    summarise(across(everything(), unique)) %>% 
-    mutate(r0 = 4) %>% 
-    pivot_longer(cols = everything(),
-                 names_to = "Parameter",
-                 values_to = "Value") %>% 
-    group_by(Parameter) %>% 
-    summarize(Value = list(unique(Value))) %>% 
-    mutate(id = case_when(Parameter == 'sd_env_source' ~ 'a',
-                          Parameter == 'sd_env_lon' ~ 'b',
-                          Parameter == 'sd_env' ~ 'c',
-                          Parameter == 'rho' ~ 'd',
-                          Parameter == 'phi' ~ 'e',
-                          Parameter == 'niche_cost' ~ 'f',
-                          Parameter == 'max_alpha' ~ 'g',
-                          Parameter == 'theta' ~ 'h',
-                          Parameter == 'p_dispersal' ~ 'i',
-                          Parameter == 'r0' ~ 'j',
-                          TRUE ~ as.character(Parameter)),
-           Interpretation = case_when(Parameter == 'sd_env_source' ~ 'Environmental variation at headwaters',
-                                      Parameter == 'sd_env_lon' ~ 'Degree of local environmental noise',
-                                      Parameter == 'sd_env' ~ 'Temporal environmental variability',
-                                      Parameter == 'rho' ~ 'Strength of spatial autocorrelation in mean environmental condition',
-                                      Parameter == 'phi' ~ 'Extent of spatial autocorrelation in temporal environmental variation',
-                                      Parameter == 'niche_cost' ~ 'Cost of a wider niche',
-                                      Parameter == 'max_alpha' ~ 'Maximum value of interspecific competition coefficient',
-                                      Parameter == 'theta' ~ 'Rate parameter of an exponential dispersal kernel',
-                                      Parameter == 'p_dispersal' ~ 'Dispersal probability',
-                                      Parameter == 'r0' ~ 'Maxiumum reproductive rate',
-                                      TRUE ~ as.character(Parameter)),
-           Parameter = case_when(Parameter == 'sd_env_source' ~ '$\\sigma_{h}$',
-                                 Parameter == 'sd_env_lon' ~ '$\\sigma_{l}$',
-                                 Parameter == 'sd_env' ~ '$\\sigma_{z}$',
-                                 Parameter == 'rho' ~ '$\\rho$',
-                                 Parameter == 'phi' ~ '$\\phi$',
-                                 Parameter == 'niche_cost' ~ '$\\nu$',
-                                 Parameter == 'max_alpha' ~ '$\\alpha_{max}$',
-                                 Parameter == 'theta' ~ '$\\theta$',
-                                 Parameter == 'p_dispersal' ~ '$p_{d}$',
-                                 Parameter == 'r0' ~ '$r_{0,i}$',
-                                 TRUE ~ as.character(Parameter))
-    ) %>% 
-    arrange(id) %>% 
-    select(-id) %>% 
-    kable(format = 'markdown')
+  source(here::here('empirical/table_sim_parameter_main.R'))
+  table_output
 
@@
 
-dat_hkd %>% 
-    mutate(n_site = n_distinct(SiteID)) %>% 
-    mutate(Species = str_replace_all(str_to_title(Species), "_", " ")) %>% 
-    mutate(Species = str_replace_all(Species, "(spp$)|(spp\\s)", "spp\\.")) %>% 
-    mutate(Species = str_replace_all(Species, "(sp$)", "sp\\.")) %>% 
-    mutate(Species = str_replace_all(Species, "(subsp)", "subsp\\. ")) %>% 
-    mutate(Species = str_replace_all(Species, "(sp\\sme$)", "sp\\. ME")) %>% 
-    group_by(Species) %>% 
-    summarise('Number of sites present' = n_distinct(SiteID),
-              'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
-    kable(format = 'markdown')
+  source(here::here('empirical/table_splist_hkd.R'))
+  table_output
 
@@
 
-sp_mw_latin <- read_csv(here::here('/empirical/data_out/data_mw_splist_latin.csv'))
-
-  dat_mw %>% 
-    mutate(n_site = n_distinct(SiteID)) %>% 
-    rename(Common_name = Species) %>% 
-    group_by(Common_name) %>% 
-    summarise('Number of sites present' = n_distinct(SiteID),
-              'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
-    left_join(sp_mw_latin, by = "Common_name") %>% 
-    select(Species = Latin_name,
-           'Number of sites present',
-           'Occupancy (%)') %>% 
-    arrange(Species) %>% 
-    kable(format = 'markdown')
+  source(here::here('empirical/table_splist_mw.R'))
+  table_output
 

### 2021-02-14 manuscript.Rmd
Update manuscript.Rmd

@@
   html_notebook: default
-abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern[@lomolinoEcologyMostGeneral2000] and has formed the basis of area-based conservation strategies[@desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003].
+abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern in ecology[@lomolinoEcologyMostGeneral2000] and has formed the basis of area-based conservation strategies[@desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003].
 However, many ecosystems possess a complex spatial structure that cannot be represented by area (the scale-invariant complexity)[@rodriguez-iturbeFractalRiverBasins2001; @turnerLandscapeEcologyTheory2015], and its role in scaling biodiversity is largely unknown.
@@
 Third parties provided data for empirical data analysis; references are provided in the main text and Supplementary Information where appropriate.
-R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet.' (available at https://github.com/aterui/mcbrnet).
-Codes for simulations, statistical analysis, figures, and tables are available at https://github.com/aterui/public-proj_stream-diversity.
+R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at https://github.com/aterui/mcbrnet).
+Codes for simulations, statistical analysis, figures, and tables are available at XXX.
 

### 2021-02-18 manuscript.Rmd
edits: automated edits by visual editor

@@
 output:
-  word_document: default
   html_notebook: default
@@
 ## read gis files
-filename <- list.files(path = here::here('/empirical/data_gis'), full.names = T)
+filename <- list.files(path = here::here('empirical/data_gis'), full.names = T)
 wsd_subset <- lapply(filename[str_detect(filename, "wsd_subset")], st_read)
@@
 ## read theory file
-dat_sim <- read_csv(here::here('/theory/result/result_sim2020-11-10.csv'))
+dat_sim <- read_csv(here::here('theory/result/result_sim2020-11-10.csv'))
 
@@
 # for bayes factor
-source(here::here('/empirical/analysis_lm_bf.R'))
+source(here::here('empirical/analysis_lm_bf.R'))
 
 # Hokkaido data
-dat_hkd_site <- read_csv(here::here('/empirical/data_out/dat_hkd_site.csv'))
+dat_hkd_site <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))
 
 # Midwest data
-dat_mw_site <- read_csv(here::here('/empirical/data_out/dat_mw_site.csv')) %>% 
+dat_mw_site <- read_csv(here::here('empirical/data_out/data_mw_site.csv')) %>% 
   mutate(Year = format(as.Date(Date, format = '%m/%d/%Y'), "%Y"))
@@
 Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity[@kallimanisHowDoesHabitat2008], larger metacommunity size[@hubbellUnifiedNeutralTheory2001], and/or enhanced colonization dynamics[@lososTheoryIslandBiogeography2009].
-Importantly, the SAR provides the foundation for global conservation efforts[@myersBiodiversityHotspotsConservation2000; @desmetUsingSpeciesareaRelationship2004;@neigelSpeciesareaRelationshipsMarine2003].
+Importantly, the SAR provides the foundation for global conservation efforts[@myersBiodiversityHotspotsConservation2000; @desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003].
 For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas[@desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003], which currently encompass more than 30 million km^2^ globally[@deguignet2014UnitedNations2014].
 
-Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity[@turnerLandscapeEcologyTheory2015;@rodriguez-iturbeFractalRiverBasins2001].
+Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity[@turnerLandscapeEcologyTheory2015; @rodriguez-iturbeFractalRiverBasins2001].
 Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few[@rodriguez-iturbeFractalRiverBasins2001].
@@
 Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms[@grantLivingBranchesPopulation2007].
-Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure[@carraraDendriticConnectivityControls2012; @faganConnectivityFragmentationExtinction2002; @teruiMetapopulationStabilityBranching2018;@brownDendriticNetworkStructure2010], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@rinaldoRiverNetworksEcological2018;@petersonModellingDendriticEcological2013].
+Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure[@carraraDendriticConnectivityControls2012; @faganConnectivityFragmentationExtinction2002; @teruiMetapopulationStabilityBranching2018; @brownDendriticNetworkStructure2010], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@rinaldoRiverNetworksEcological2018; @petersonModellingDendriticEcological2013].
 For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches[@carraraDendriticConnectivityControls2012].
@@
 $$
+
 where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area).
@@
 ### Metacommunity model
+
 We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al.[@thompsonProcessbasedMetacommunityFramework2020].
@@
 $$
+
 where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$.
@@
 $K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area[@altermattRiverNetworkProperties2013; @teruiThreeEcologicalFactors2016].
-The parameter $\alpha_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ > 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
+The parameter $\alpha_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ \> 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
 $\alpha_{ij}$ was drawn randomly from a uniform distribution as $\alpha_{ij} \sim Unif(0, \alpha_{max})$.
@@
 $$
+
 where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$.
@@
 The diagonal elements of the variance-covariance matrix $\sigma^2_z$ represent the degree of temporal environmental variation.
-The off-diagonal elements $\Omega_{xy}$ represent spatial autocorrelation in temporal environmental variation as:
+The off-diagonal elements $\Omega_{xy}$ represent the spatial autocorrelation in temporal environmental variation as:
 
@@
 $$
+
 The parameter $\theta$ regulates the dispersal distance of a species that follows an exponential distribution ($\theta^{-1}$ corresponds to the expected dispersal distance).
@@
 ### Simulation
+
 We used `r n_scenario` sets of parameter combinations (i.e., simulation scenarios) based on the results of extensive sensitivity analysis (**Supplementary Information**).
@@
 We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019].
-We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (~1 km resolution), which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005].
+We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005].
 We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
@@
 $$
+
 We compared the performance of these competing models using the Bayes factor[@wagenmakersPracticalSolutionPervasive2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1).
@@
 # Acknowledgements
+
 We are grateful to numerous people who have been involved in the collection of fish community data.
@@
 # Author contributions
+
 AT conceived of the project.
@@
 # Data and code availability
+
 Third parties provided data for empirical data analysis; references are provided in the main text and Supplementary Information where appropriate.
-R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at https://github.com/aterui/mcbrnet).
+R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at <https://github.com/aterui/mcbrnet>).
 Codes for simulations, statistical analysis, figures, and tables are available at XXX.

### 2021-02-21 manuscript.Rmd
Update manuscript.Rmd

@@
   html_notebook: default
-abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern in ecology[@lomolinoEcologyMostGeneral2000] and has formed the basis of area-based conservation strategies[@desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003].
-However, many ecosystems possess a complex spatial structure that cannot be represented by area (the scale-invariant complexity)[@rodriguez-iturbeFractalRiverBasins2001; @turnerLandscapeEcologyTheory2015], and its role in scaling biodiversity is largely unknown.
+abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern in ecology[@lomolino2000] and has formed the basis of area-based conservation strategies[@desmet2004; @neigel2003].
+However, many ecosystems possess a complex spatial structure that cannot be represented by area (the scale-invariant complexity)[@rodríguez-iturbe2001; @turner2015], and its role in scaling biodiversity is largely unknown.
 Here, we use theory and empirical analysis of extensive fish community data to show that ecosystem size and complexity jointly regulate biodiversity in rivers.
-Rivers are a prime example of fractal branching networks where the recurrent merging of diverse streams generates a pronounced self-similarity in complex branching patterns[@rodriguez-iturbeFractalRiverBasins2001].
-Ecosystem complexity, which we define as the probability of branching per unit river distance[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], should increase watershed-scale species richness by increasing habitat heterogeneity.
-Meanwhile, ecosystem size should dictate metacommunity size and total habitat diversity, two factors that regulate watershed-scale species richness[@hubbellUnifiedNeutralTheory2001; @kallimanisHowDoesHabitat2008].
+Rivers are a prime example of fractal branching networks where the recurrent merging of diverse streams generates a pronounced self-similarity in complex branching patterns[@rodríguez-iturbe2001].
+Ecosystem complexity, which we define as the probability of branching per unit river distance[@terui2018; @yeakel2014], should increase watershed-scale species richness by increasing habitat heterogeneity.
+Meanwhile, ecosystem size should dictate metacommunity size and total habitat diversity, two factors that regulate watershed-scale species richness[@hubbell2001; @kallimanis2008].
 Metacommunity simulations in branching networks predicted biodiversity patterns consistent with our hypothesis.
@@
 Recognizing the dual control of biodiversity should broaden viable options for spatial planning of protected areas or restoration, thereby helping conserve biodiversity from societal demands that threaten it.
-bibliography: reference.bib
+
 csl: nature.csl
@@
       })
+bibliography: references.bib
 ---
@@
 Ecologists have long sought to understand the general drivers of biodiversity.
-One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR)[@lomolinoEcologyMostGeneral2000].
-In 1921, Arrhenius[@arrheniusSpeciesArea1921] formulated the SAR as a power-law $S = cA^z$, an equation currently known as the Arrhenius species-area relationship ($S$ is the number of species observed in a given geographic area $A$, $c$ the constant, and $z$ the scaling exponent).
-Since then, the spatial scaling of species richness has been observed in many taxonomic groups[@triantisIslandSpeciesareaRelationship2012].
+One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR)[@lomolino2000].
+In 1921, Arrhenius[@arrhenius1921] formulated the SAR as a power-law $S = cA^z$, an equation currently known as the Arrhenius species-area relationship ($S$ is the number of species observed in a given geographic area $A$, $c$ the constant, and $z$ the scaling exponent).
+Since then, the spatial scaling of species richness has been observed in many taxonomic groups[@triantis2012].
 The SAR is ubiquitous because multiple mechanisms produce an apparently similar pattern.
-Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity[@kallimanisHowDoesHabitat2008], larger metacommunity size[@hubbellUnifiedNeutralTheory2001], and/or enhanced colonization dynamics[@lososTheoryIslandBiogeography2009].
-Importantly, the SAR provides the foundation for global conservation efforts[@myersBiodiversityHotspotsConservation2000; @desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003].
-For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas[@desmetUsingSpeciesareaRelationship2004; @neigelSpeciesareaRelationshipsMarine2003], which currently encompass more than 30 million km^2^ globally[@deguignet2014UnitedNations2014].
+Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity[@kallimanis2008], larger metacommunity size[@hubbell2001], and/or enhanced colonization dynamics[@losos2009].
+Importantly, the SAR provides the foundation for global conservation efforts[@myers2000; @desmet2004; @neigel2003].
+For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas[@desmet2004; @neigel2003], which currently encompass more than 30 million km^2^ globally[@deguignet2014].
 
-Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity[@turnerLandscapeEcologyTheory2015; @rodriguez-iturbeFractalRiverBasins2001].
-Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few[@rodriguez-iturbeFractalRiverBasins2001].
-Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike[@rodriguez-iturbeFractalRiverBasins2001].
-Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms[@grantLivingBranchesPopulation2007].
-Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure[@carraraDendriticConnectivityControls2012; @faganConnectivityFragmentationExtinction2002; @teruiMetapopulationStabilityBranching2018; @brownDendriticNetworkStructure2010], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@rinaldoRiverNetworksEcological2018; @petersonModellingDendriticEcological2013].
-For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches[@carraraDendriticConnectivityControls2012].
-However, most research has explored the consequences of branching complexity for local community structure[@brownDendriticNetworkStructure2010; @carraraDendriticConnectivityControls2012] or has relied solely on theoretical arguments with limited replications of branching architecture[@holtRoleBranchingMaintenance2018].
+Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity[@turner2015; @rodríguez-iturbe2001].
+Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few[@rodríguez-iturbe2001].
+Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike[@rodríguez-iturbe2001].
+Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms[@grant2007].
+Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure[@carrara2012; @ers2019], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@rinaldo2018; @mccluney2014].
+For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches[@carrara2012].
+However, most research has explored the consequences of branching complexity for local community structure[@ers2019; @carrara2012] or has relied solely on theoretical arguments with limited replications of branching architecture[@holt2018].
 At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
-Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services[@dudgeonFreshwaterBiodiversityImportance2006].
+Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services[@dudgeon2006].
 
 Here, we hypothesize that ecosystem size and complexity dictate biodiversity patterns in rivers - a prime example of complex branching ecosystems.
-The recurrent merging of diverse streams and rivers produces larger, ecologically distinct channels, ultimately forming a fluvial network with fractal branching patterns[@rodriguez-iturbeFractalRiverBasins2001].
-As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], should control the ecosystem's habitat heterogeneity (habitat diversity per unit area).
-Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity).
+Individual streams and rivers flow through different landscapes with distinct land use and geological backgrounds, serving as a spatial unit of unique in-stream environments[@moore2015; @terui2018].
+The recurrent merging of the diverse streams and rivers ultimately forms a fluvial network with fractal branching patterns[@rodríguez-iturbe2001].
+As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance[@terui2018; @yeakel2014], may represent a macro-scale control of the ecosystem's habitat heterogeneity (habitat diversity per unit area)[@terui2018; @moore2015].
+Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity), two factors that regulate biodiversity at the metacommunity level[@hubbell2001; @iwasaki2012].
 We predict that ecosystem size and branching complexity increase watershed-scale species richness ($\gamma$ diversity) by enhancing local species richness ($\alpha$ diversity) and/or spatial difference of species composition ($\beta$ diversity) under different ecological scenarios.
@@
 First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
-We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**).
+We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit[@terui2018; @yeakel2014] (**Figure 1**).
 Two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
@@
 Therefore, our network-generation procedure resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
-We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity framework[@thompsonProcessbasedMetacommunityFramework2020].
+We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity framework[@thompson2020].
 In this model, 50 species with different abiotic niches (optimum and width) disperse along a network and compete for resources with varied strengths in temporally dynamic environments (see **Methods** for model details).
@@
 When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation.
-This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries[@mooreEmergentStabilityLarge2015; @petersonModellingDendriticEcological2013].
+This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries[@moore2015; @peterson2013].
 In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on habitat heterogeneity.
-This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities[@poffHomogenizationRegionalRiver2007; @teruiMetapopulationStabilityBranching2018].
+This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities[@poff2007; @terui2018].
 Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity within a network.
@@
 In contrast, when the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
-The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects)[@thompsonProcessbasedMetacommunityFramework2020].
+The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects)[@thompson2020].
 These patterns were consistent across different levels of dispersal probabilities (**Figures S5 and S12**).
@@
 Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2 and S5-11**).
-This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity[@hubbellUnifiedNeutralTheory2001].
+This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity[@hubbell2001].
 In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$; **Figures S13-18**).
@@
 Therefore, this landscape scenario decouples the intimate relationship between branching structure and habitat heterogeneity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
-This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, and flow/sediment regimes[@petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015].
-Instead, it may be more relevant to severely altered landscapes where human disturbance compromises the environmental distinctiveness of branches through, for example, flow regulations by dams[@poffHomogenizationRegionalRiver2007].
+This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, and flow/sediment regimes[@peterson2013; @moore2015].
+Instead, it may be more relevant to severely altered landscapes where human disturbance compromises the environmental distinctiveness of branches through, for example, flow regulations by dams[@poff2007].
 Hence, our theory has important implications for riverine biodiversity conservation by pointing to the crucial role of habitat diversity produced by branching structure.
@@
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly matches the previous observations of stream fish movement.
-Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters[@radingerPatternsPredictorsFish2014].
+Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters[@radinger2014].
 The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
@@
 First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
-Human-induced habitat alterations, including flow regulation[@poffHomogenizationRegionalRiver2007], landscape modification[@finlayStreamSizeHuman2011; @grillMappingWorldFreeflowing2019], and stream burial[@elmoreDisappearingHeadwatersPatterns2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
+Human-induced habitat alterations, including flow regulation[@poff2007], habitat fragmentation[@grill2019], and stream burial[@elmore2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
 Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human activities.
 Second, the complexity perspective may provide insights into the spatial planning of conservation efforts.
-Riverine reserves and local restoration are increasingly recognized as an effective management tool, and designing a spatial network of conservation sites in rivers is an area of active research[@koningNetworkGrassrootsReserves2020].
+Riverine reserves and local restoration are increasingly recognized as an effective management tool, and designing a spatial network of conservation sites in rivers is an area of active research[@koning2020].
 While large reserves or restoration sites are undoubtedly important, our results indicate the potential of coordinated networks of local conservation sites in protecting biodiversity.
-For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin[@koningNetworkGrassrootsReserves2020].
+For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin[@koning2020].
 
 While the prevailing evidence supports the importance of ecosystem size in scaling species diversity, ecosystem complexity has not received the attention it deserves.
-However, the ubiquity of scale-invariant complexity across terrestrial[@turnerLandscapeEcologyTheory2015] and aquatic ecosystems[@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
+However, the ubiquity of scale-invariant complexity across terrestrial[@turner2015] and aquatic ecosystems[@rodríguez-iturbe2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
 Our fundamental findings of the dual control of biodiversity should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
@@
 
-We depicted branching ecosystems as a bifurcating network of connected habitat patches[@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**).
+We depicted branching ecosystems as a bifurcating network of connected habitat patches[@terui2018; @yeakel2014] (**Figure 1**).
 Habitat patches, or local communities, can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
@@
 Each habitat patch is assigned to be a branching patch (including upstream terminals) with probability $P_b$ or a non-branching patch with probability $1-P_b$.
-In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in branch $q$, $n_{p,q}$, is a realization of a random variable drawn from a geometric distribution $n_{p,q} \sim Ge(P_{b})$[@teruiMetapopulationStabilityBranching2018] but conditional on $\sum_{q=1}^{N_b}n_{p,q} = N_p$ ($N_b$ is the number of branches in a network).
+In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in branch $q$, $n_{p,q}$, is a realization of a random variable drawn from a geometric distribution $n_{p,q} \sim Ge(P_{b})$[@terui2018] but conditional on $\sum_{q=1}^{N_b}n_{p,q} = N_p$ ($N_b$ is the number of branches in a network).
 The number of branches $N_b$ is identical to the number of branching habitat patches in a network, or the number of 'success' out of $N_p$ trials.
@@
 This framework has two merits.
-First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution)[@rodriguez-iturbeFractalRiverBasins2001].
-Second, it preserves the fractal nature of branching patterns[@peckhamReformulationHortonLaws1999].
-An alternative approach is the use of optimal channel networks[@carraroGenerationApplicationRiver2020].
+First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution)[@rodríguez-iturbe2001].
+Second, it preserves the fractal nature of branching patterns[@peckham1999].
+An alternative approach is the use of optimal channel networks[@carraro2020].
 However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to compare theoretical predictions with empirical observations.
@@
 The parameter $\omega$ takes values of $0-1$ and represents the relative influence of the right tributary given the relative size of joining tributaries.
-With this expression, larger tributaries have a greater influence on the downstream environment, as observed in natural river networks[@bendaNetworkDynamicsHypothesis2004].
+With this expression, larger tributaries have a greater influence on the downstream environment, as observed in natural river networks[@benda2004].
 
@@
 
-We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al.[@thompsonProcessbasedMetacommunityFramework2020].
+We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al[@thompson2020].
 In this framework, abiotic environmental conditions (density-independent), intra- and interspecific competition (density-dependent), and dispersal regulate a species' realized population growth.
@@
 where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$.
-The realized discrete number of individuals is drawn from a Poisson distribution to account for stochasticity in demographic and dispersal processes[@fronhoferClassicalMetapopulationDynamics2017; @thompsonProcessbasedMetacommunityFramework2020].
-Local community dynamics are simulated based on the Beverton-Holt equation[@bevertonDynamicsExploitedFish1957]:
+The realized discrete number of individuals is drawn from a Poisson distribution to account for stochasticity in demographic and dispersal processes[@fronhofer2017; @thompson2020].
+Local community dynamics are simulated based on the Beverton-Holt equation[@beverton1957]:
 
@@
 where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
-$K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area[@altermattRiverNetworkProperties2013; @teruiThreeEcologicalFactors2016].
+$K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area[@terui2016; @rahel1991].
 The parameter $\alpha_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ \> 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
@@
 where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$.
-We introduced the cost of a wide niche by multiplying $\delta$[@chaianunpornEvolutionaryResponsesClimate2015]:
+We introduced the cost of a wide niche by multiplying $\delta$[@chaianunporn2015]:
 
@@
 Values of simulation parameters were summarized in **Table S2**.
-We performed simulations using R version 4.0.2[@rcoreteamLanguageEnvironmentStatistical2020].
+We performed simulations using R version 4.0.2[@rcoreteam2020].
 
@@
 We compiled fish data at two geographic regions: the Hokkaido island, Japan, and the Midwest, US.
-For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaHokkaidoFreshwaterFish2011; @fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors[@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island.
-For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources[@iowadepartmentofnaturalresourcesBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@illinoisenvironmentalprotectionagencyIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency[@minnesotapollutioncontrolagencyDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources[@wisconsindepartmentofnaturalresourcesGuidelinesAssessingFish2018].
+For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish[@fukushima2007; @fukushima2011], monitoring data at protected watersheds[@comte2021; @terui2018], and primary data collected by the authors[@miyazaki2016; @terui2016], which collectively cover the entire Hokkaido island.
+For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources[@iowadepartmentofnaturalresources2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@illinoisenvironmentalprotectionagency2014], Minnesota Pollution Control Agency[@minnesotapollutioncontrolagency2014], and Wisconsin Department of Natural Resources[@wisconsindepartmentofnaturalresources2018].
 We detailed procedures for initial data selection in **Supplementary Information**.
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@comteFishDispersalFlowing2018; @giamEnvironmentPredationGovern2016], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
+These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@comte2018; @giam2016], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
 Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (**Supplementary Information**).
@@
 Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014a; @chaseEcosystemDecayExacerbates2020].
-We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT'[@hsiehINEXTPackageRarefaction2016].
+Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chao2014; @chase2020].
+We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT'[@hsieh2016].
 We assessed the completeness of the observed species richness based on sample coverage, which is the proportion of observed species richness to asymptotic species richness.
@@
 $\alpha$ diversity was estimated by taking an average of local species richness at each site.
-$\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity[@whittakerVegetationSiskiyouMountains1960].
+$\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity[@whittaker1960].
 
@@
 We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]).
-We used Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area).
-The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0[@yamazakiDevelopmentGlobal90m2015].
+We used Hydrologically Adjusted Elevations of MERIT Hydro[@yamazaki2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area).
+The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0[@yamazaki2015].
 Watershed area was estimated based on the delineated watershed polygons.
@@
 A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
-We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazakiMERITHydroHighResolution2019].
-We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4[@hijmansVeryHighResolution2005].
-We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhornCopernicusGlobalLand2020].
-We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1)[@lehnerGlobalReservoirDam2011; @lehnerHighresolutionMappingWorld2011].
-We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA'[@brenningRSAGASAGAGeoprocessing2018], 'sf'[@pebesmaSimpleFeaturesStandardized2018], 'raster'[@hijmansRasterGeographicData2020], 'rgdal'[@rogerbivandRgdalBindingsGeospatial2020], 'stars'[@edzerpebesmaStarsSpatiotemporalArrays2020], and 'exactextractr'[@danielbastonExactextractrFastExtraction2020].
+We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazaki2019].
+We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4[@hijmans2005].
+We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhorn2020].
+We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1)[@lehner2011].
+We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA'[@brenning2018], 'sf'[@pebesma2018], 'raster'[@hijmans2020], 'rgdal'[@rogerbivand2020], 'stars'[@edzerpebesma2020], and 'exactextractr'[@danielbaston2020].
 
@@
 
-We compared the performance of these competing models using the Bayes factor[@wagenmakersPracticalSolutionPervasive2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1).
-We used Bayesian Information Criteria (BIC) of the linear models to approximate the Bayes factor[@wagenmakersPracticalSolutionPervasive2007]:
+We compared the performance of these competing models using the Bayes factor[@wagenmakers2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1).
+We used Bayesian Information Criteria (BIC) of the linear models to approximate the Bayes factor[@wagenmakers2007]:
 
@@
 
-where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$. We performed statistical analysis using R version 4.0.2[@rcoreteamLanguageEnvironmentStatistical2020].
+where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$. We performed statistical analysis using R version 4.0.2[@rcoreteam2020].
 
@@
 We thank Michio Fukushima and Hirokazu Urabe for providing information on the Hokkaido Freshwater Fish Database HFish and the fish monitoring data at protected watersheds in Hokkaido.
-This research was funded by National Science Foundation through a Water Sustainability and Climate Program (WSC) Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through a Division of Environmental Biology (DEB 2015634) and by Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1).
+This research was funded by National Science Foundation through a Water Sustainability and Climate Program (WSC) Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1), and the University of North Carolina at Greensboro through a start-up fund.
 

### 2021-02-22 supplementary_information.Rmd
Update supplementary_information.Rmd

@@
     toc_depth: 2
-bibliography: reference.bib
+bibliography: references.bib
 csl: nature.csl
@@
 $$
+
 where $\zeta_k$ ($k = 0-8$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-8}$).
@@
 Longitudinal gradients of local species richness have been extensively studied in rivers, illuminating typical patterns observed in nature.
-The most common pattern is a downstream increase of local species richness[@mcdowallDiadromyAssemblyRestoration1996; @mcdowallFightingFlowDownstreamupstream1998; @rahelFishAssemblagesHabitat1991; @teruiThreeEcologicalFactors2016].
-However, recent empirical and theoretical studies also showed 'reversed patterns,' in which local species richness decreases downstream[@bsemerHeadwatersAreCritical2013; @harveyDisturbanceReversesClassic2018].
+The most common pattern is a downstream increase of local species richness[@mcdowall1996; @mcdowall1998; @rahel1991; @terui2016].
+However, recent empirical and theoretical studies also showed 'reversed patterns,' in which local species richness decreases downstream[@bsemer2013; @harvey2018].
 We predicted the longitudinal gradient of local species richness to confirm that our simulation scenarios are capable of reproducing the previously observed patterns of local species richness.
@@
 
-**Hokkaido, Japan.** We used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaHokkaidoFreshwaterFish2011; @fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors[@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island.
+**Hokkaido, Japan.** We used data from the Hokkaido Freshwater Fish Database HFish[@fukushima2011; @fukushima2007], monitoring data at protected watersheds[@comte2021; @terui2018], and primary data collected by the authors[@miyazaki2016; @terui2016], which collectively cover the entire Hokkaido island.
 Most data were collected from summer to fall.
@@
 We removed the following species at this stage: (1) identified at the family-level; (2) marine fish species (including species that occasionally use brackish/freshwater habitats).
-1.
-We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve unidentified species (genus level) that are rarely observed in the data set (< 100 sites occurrence).
-1.
+2.
+We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve unidentified species (genus level) that are rarely observed in the data set (\< 100 sites occurrence).
+3.
 For sites with multiple visits (i.e., temporal replicates), we used the latest-year observation at each sampling site to minimize variation in sampling efforts among sites.
 Surveys that occurred in the same year were aggregated into a single observation.
-1.
+4.
 We confined sites to those with the latest observation year of $\ge$ 1990.
 Although the data set contained observations from 1953, we added this restriction to align the observation period with the data set in the Midwest, US.
-1.
+5.
 Four genera (*Lethenteron*, *Pungitius*, *Rhinogobius*, and *Tribolodon*) were treated as species groups (i.e., spp.) as their taxonomic resolutions varied greatly among data sources due to difficulties in identifying species.
 
-**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources[@iowadepartmentofnaturalresourcesBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@illinoisenvironmentalprotectionagencyIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency[@minnesotapollutioncontrolagencyDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources[@wisconsindepartmentofnaturalresourcesGuidelinesAssessingFish2018].
-These data sets cover most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined
-by U.S.
+**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources[@iowadepartmentofnaturalresources2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@illinoisenvironmentalprotectionagency2014], Minnesota Pollution Control Agency[@minnesotapollutioncontrolagency2014], and Wisconsin Department of Natural Resources[@wisconsindepartmentofnaturalresources2018].
+These data sets cover most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined by U.S.
 Geological Survey and U.S.
-Department of Agriculture Natural Resources Conservation Service[@u.s.geologicalsurveyandu.s.departmentofagriculturenaturalresourcesconservationserviceFederalStandardsProcedures2013]) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05).
+Department of Agriculture Natural Resources Conservation Service[@u.s.geologicalsurveyandu.s.departmentofagriculturenaturalresourcesconservationservice2013]) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05).
 Fish data were collected from summer to fall with electrofishing (backpack, barge-type, or boat-mounted) and supplemental netting at some locations.
@@
 1.  We used data of the Upper Mississippi (HUC 2, region 07) and Great Lakes basins (HUC 2, region 04) as most sites are included in these regions.
-1. We removed records of unidentified species, hybrid species, and commercial species apparently absent in the wild (e.g., goldfish).
-1. We used the latest observation at each sampling site to minimize variation in sampling efforts among sites.
+2.  We removed records of unidentified species, hybrid species, and commercial species apparently absent in the wild (e.g., goldfish).
+3.  We used the latest observation at each sampling site to minimize variation in sampling efforts among sites.
 
@@
 In this simulation, presence of species $i$ at site $x$, $J_{ix}$, was drawn from a Bernoulli distribution as $J_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$.
-Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT'[@hsiehINEXTPackageRarefaction2016].
+Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT'[@hsieh2016].
 We calculated % bias of estimated asymptotic species richness $S_{est}$:
@@
 The % bias decreased sharply as the number of sampling sites increased (**Figure S20**).
-In particular, the estimation bias with a small sample size ($N_{site} = 5$) was substantial when the true species richness $S_{true}$ was low; some estimates showed > 150% bias (**Figure S20**).
-Given the simulation results, estimates of asymptotic species richness at watersheds with < 10 sampling sites may involve substantial statistical uncertainty.
+In particular, the estimation bias with a small sample size ($N_{site} = 5$) was substantial when the true species richness $S_{true}$ was low; some estimates showed \> 150% bias (**Figure S20**).
+Given the simulation results, estimates of asymptotic species richness at watersheds with \< 10 sampling sites may involve substantial statistical uncertainty.
 
@@
 
-**Figure S19 ** Correlation structure of potential explanatory variables for riverine diversity metrics.
+**Figure S19** Correlation structure of potential explanatory variables for riverine diversity metrics.
 Numeric values in each cell are the Pearson's correlation coefficients.
@@
 
-**Figure S20 ** Sensitivity analysis of asymptotic species richness in relation to true species richness $S_{true}$ (panels) and the number of sampling sites $N_{site}$ (x-axis).
+**Figure S20** Sensitivity analysis of asymptotic species richness in relation to true species richness $S_{true}$ (panels) and the number of sampling sites $N_{site}$ (x-axis).
 Positive values of % bias indicate an overestimation of species richness, while negative values indicate an underestimation.

### 2021-02-22 manuscript.Rmd
Update manuscript.Rmd

@@
 - Yusuke Miyazaki^[Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan]
-output:
-  html_notebook: default
-abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern in ecology[@lomolino2000] and has formed the basis of area-based conservation strategies[@desmet2004; @neigel2003].
-However, many ecosystems possess a complex spatial structure that cannot be represented by area (the scale-invariant complexity)[@rodríguez-iturbe2001; @turner2015], and its role in scaling biodiversity is largely unknown.
+output: html_notebook
+abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern in ecology[@lomolino2000] and is the foundation of many conservation strategies[@desmet2004; @neigel2003].
+However, many ecosystems possess a complex spatial structure that cannot be represented simply by area[@rodríguez-iturbe2001; @turner2015], and the role of  such scale-invariant complexity in scaling biodiversity relationships is largely unknown.
 Here, we use theory and empirical analysis of extensive fish community data to show that ecosystem size and complexity jointly regulate biodiversity in rivers.
@@
 Metacommunity simulations in branching networks predicted biodiversity patterns consistent with our hypothesis.
-Larger and more branched ecosystems supported greater species richness at the watershed scale, and the importance of spatial difference in species composition was apparent when simulated species dispersal is limited.
-Cross-watershed comparisons across two geographic regions (the Hokkaido island in Japan and the midwestern US) provided empirical support for the theoretical predictions.
+Larger and more branched ecosystems supported greater species richness at the watershed scale, and the importance of spatial difference in species composition was increasingly apparent when simulated species dispersal was limited.
+Cross-watershed comparisons across two geographic regions (Hokkaido Island in Japan and the Midwestern US) provided empirical support for the theoretical predictions.
 In both regions, watershed-scale species richness increased with ecosystem size (watershed area) and complexity (branching probability) through enhanced spatial difference in species composition.
@@
 Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms[@grant2007].
-Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure[@carrara2012; @ers2019], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@rinaldo2018; @mccluney2014].
+Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure, and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@rinaldo2018].
 For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches[@carrara2012].
@@
 Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity within a network.
-We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel), dispersal probability, and the maximum value of interspecific competition strength (see **Methods**).
+We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel $\theta$), dispersal probability, and the maximum value of interspecific competition strength (see **Methods**).
 These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supplementary Information**).
@@
 We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation exists (i.e., species travel short distances).
-This pattern reflects significant spatial difference of species composition over the branching network.
+This pattern reflects significant spatial variation in species composition over the branching network and is likely driven by the local association of species' niche and abiotic environments (i.e., species sorting)[@thompson2020].
 In contrast, when the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
@@
 In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$; **Figures S13-18**).
-Under this scenario, branching may not contribute to the ecosystem's habitat heterogeneity because local environmental noise masks environmental differences between tributaries.
-Therefore, this landscape scenario decouples the intimate relationship between branching structure and habitat heterogeneity, thereby eliminating the positive effect of branching complexity on $\gamma$ diversity.
+Under this scenario, branching does not contribute to the ecosystem's habitat heterogeneity because local environmental noise masks environmental differences between tributaries.
+Therefore, this landscape scenario eliminates the positive effect of branching complexity on $\gamma$ diversity.
 This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, and flow/sediment regimes[@peterson2013; @moore2015].
@@
 The proposed theory provided important insights into how ecological communities are structured in branching networks; however, empirically testing the predictions is extremely difficult because it requires metacommunity-level replications.
-To confront this logistical challenge, we compiled fish community data across two geographic regions: the Hokkaido island in Japan and the midwestern US (Midwest).
+To confront this logistical challenge, we compiled fish community data across two geographic regions: Hokkaido Island in Japan and the Midwestern US (Midwest).
 These regions are located in comparable latitude ranges but support distinct fish communities (**Figure 1**).
@@
 
-The consistent effect of branching probability on $\gamma$ diversity across the study regions is noteworthy because the watersheds in the Midwest are severely altered by agriculture (median % agricultural land use: `r round(median(wsd_subset[[2]]$frac_agri)*100)`% in the Midwest and `r round(median(wsd_subset[[1]]$frac_agri)*100)`% in Hokkaido).
+The consistent effect of branching probability on $\gamma$ diversity across the study regions is noteworthy because the watersheds in the Midwest are severely altered by agriculture (mean % agricultural land use: `r round(mean(wsd_subset[[2]]$frac_agri)*100)`% in the Midwest and `r round(mean(wsd_subset[[1]]$frac_agri)*100)`% in Hokkaido).
 If the intensive land use by humans causes significant homogenization of in-stream habitat conditions among tributaries, theory predicts a weakened effect of branching probability on $\gamma$ diversity.
@@
 However, we are confident in our statistical inference because the observed patterns were fairly consistent with our theoretical predictions that are free from any confounding effects.
-Further, our fitted models generally showed high R^2^ values ($\alpha$ diversity: `r round(summary(fit$alpha$model)$r.squared, 2)`; $\beta$ diversity, `r round(summary(fit$beta$model)$r.squared, 2)`; $\gamma$ diversity `r round(summary(fit$gamma$model)$r.squared, 2)`).
+Further, our fitted models showed moderate to high R^2^ values ($\alpha$ diversity: `r round(summary(fit$alpha$model)$r.squared, 2)`; $\beta$ diversity, `r round(summary(fit$beta$model)$r.squared, 2)`; $\gamma$ diversity `r round(summary(fit$gamma$model)$r.squared, 2)`).
 Therefore, it is very unlikely that spurious correlations are responsible for our results.
@@
 
-While the prevailing evidence supports the importance of ecosystem size in scaling species diversity, ecosystem complexity has not received the attention it deserves.
+While the prevailing evidence supports the importance of ecosystem size in scaling species diversity[@iwasaki2012; @triantis2012], ecosystem complexity has not received the attention it deserves.
 However, the ubiquity of scale-invariant complexity across terrestrial[@turner2015] and aquatic ecosystems[@rodríguez-iturbe2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
@@
 
-where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area).
+where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area; $A_k = 1$ at the most upstream patch).
 The parameter $\omega$ takes values of $0-1$ and represents the relative influence of the right tributary given the relative size of joining tributaries.

### 2021-02-22 empirical/table_splist_hkd.R
edits: sp list tables, minor correction

@@ -2,7 +2,7 @@
 # setup -------------------------------------------------------------------
 
   pacman::p_load(tidyverse, knitr, kableExtra)
-  dat_hkd <- read_csv(here::here('/empirical/data_out/dat_hkd_site.csv'))
+  dat_hkd <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))
 
 # table -------------------------------------------------------------------
 

### 2021-02-22 empirical/table_splist_mw.R

@@ -2,11 +2,11 @@
 # setup -------------------------------------------------------------------
 
   pacman::p_load(tidyverse, knitr, kableExtra)
-  dat_mw <- read_csv(here::here('/empirical/data_out/dat_mw_site.csv'))
+  dat_mw <- read_csv(here::here('empirical/data_out/data_mw_site.csv'))
 
 # table -------------------------------------------------------------------
 
-  sp_mw_latin <- read_csv(here::here('/empirical/data_out/data_mw_splist_latin.csv'))
+  sp_mw_latin <- read_csv(here::here('empirical/data_out/data_mw_splist_latin.csv'))
   
   table_output <- dat_mw %>% 
     mutate(n_site = n_distinct(SiteID)) %>% 

### 2021-02-22 theory/table_sensitivity_analysis.R
edits: theory tables, minor correction

@@ -2,7 +2,7 @@
 # setup -------------------------------------------------------------------
 
   pacman::p_load(tidyverse, knitr, kableExtra)
-  source(here::here("/theory/analysis_sensitivity.R"))
+  source(here::here("theory/analysis_sensitivity.R"))
 
 
 # sensitivity tables ------------------------------------------------------

### 2021-02-22 theory/table_sim_parameter_main.R

@@ -2,7 +2,7 @@
 # setup -------------------------------------------------------------------
 
   pacman::p_load(tidyverse, knitr, kableExtra)
-  dat_sim <- read_csv(here::here('/theory/result/result_sim2020-11-10.csv'))
+  dat_sim <- read_csv(here::here('theory/result/result_sim2020-11-10.csv'))
 
 # table -------------------------------------------------------------------
 

### 2021-02-22 supplementary_information.Rmd
edits: SI, source file corrections

@@
   # Hokkaido data
-  dat_hkd <- read_csv(here::here('/empirical/data_out/dat_hkd_site.csv'))
+  dat_hkd <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))
 
   # Midwest data
-  dat_mw <- read_csv(here::here('/empirical/data_out/dat_mw_site.csv'))
+  dat_mw <- read_csv(here::here('empirical/data_out/data_mw_site.csv'))
 
@@
 
-  source(here::here('empirical/table_sim_parameter_sensitivity.R'))
+  source(here::here('theory/table_sim_parameter_sensitivity.R'))
   table_output
@@
 
-  source(here::here('empirical/table_sim_parameter_main.R'))
+  source(here::here('theory/table_sim_parameter_main.R'))
   table_output
@@
 
-source(here::here("/theory/figure_alpha_pattern.R"))
+source(here::here("theory/figure_alpha_pattern.R"))
 
@@
 
-source(here::here("/theory/figure_n_patch_si.R"))
+source(here::here("theory/figure_n_patch_si.R"))
 
@@
 
-source(here::here("/theory/figure_p_branch_si.R"))
+source(here::here("theory/figure_p_branch_si.R"))
 

### 2021-02-22 theory/analysis_sensitivity.R
edits: corrected some awkward errors

@@ -6,41 +6,44 @@
 
 # data --------------------------------------------------------------------
 
-dat_slope <- read_csv(here::here('theory/result/result_sensitivity.csv')) %>% 
-    filter(gamma_div > 0 & alpha_div > 0) %>% 
-    mutate(beta_div = gamma_div/alpha_div) %>% 
+  dat_slope <- read_csv(here::here('theory/result/result_sensitivity.csv')) %>% 
+      filter(gamma_div > 0 & alpha_div > 0) %>% 
+      mutate(beta_div = gamma_div/alpha_div) %>% 
+      mutate(group_id = group_indices(., sd_env_source)) %>% 
+      group_by(group_id) %>% 
+      do(slope_alpha_area = c(coef(lm(log(alpha_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[2]),
+         slope_beta_area = c(coef(lm(log(beta_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[2]),
+         slope_gamma_area = c(coef(lm(log(gamma_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[2]),
+         slope_alpha_bp = c(coef(lm(log(alpha_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[3]),
+         slope_beta_bp = c(coef(lm(log(beta_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[3]),
+         slope_gamma_bp = c(coef(lm(log(gamma_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[3])) %>% 
+      summarize(across(everything(), as.numeric))
+    
+  dat_para <- read_csv(here::here('theory/result/result_sensitivity.csv')) %>% 
     mutate(group_id = group_indices(., sd_env_source)) %>% 
     group_by(group_id) %>% 
-    do(slope_alpha_area = c(coef(lm(log(alpha_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[2]),
-       slope_beta_area = c(coef(lm(log(beta_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[2]),
-       slope_gamma_area = c(coef(lm(log(gamma_div, 10) ~ log(n_patch, 10) + log(p_branch, 10), data = .))[2]),
[…]

### 2021-02-22 table.Rmd
edits: Rmd output directory
edits: delete backslash

@@
 
-source(here::here("/empirical/analysis_lm_bf.R"))
+source(here::here("empirical/analysis_lm_bf.R"))
 

### 2021-02-22 empirical/figure_map.R
edits: add network figures

@@ -5,10 +5,10 @@
   rm(list = ls(all.names = TRUE))
   pacman::p_load(tidyverse, sf, patchwork, mcbrnet, igraph, ggraph, foreach)
   setwd(here::here("empirical"))
-
-
-# fig: network ------------------------------------------------------------
   
+
+# set theme ---------------------------------------------------------------
+
   ## set theme
   plt_theme <- theme_bw() + theme(
     plot.background = element_blank(),
@@ -33,13 +33,30 @@
   
   theme_set(plt_theme)
   
+
+# fig: network ------------------------------------------------------------
+
   ## network generation
-  n_patch <- 50
-  p_branch <- seq(0.2, 0.8, by = 0.3)
+  n_patch <- 30
+  p_branch <- c(0.2, 0.8)
+  sd_env_lon <- c(0.01, 1)
+  sd_env_source <- c(0.01, 1)
+  para <- expand.grid(n_patch = n_patch,
+                      p_branch = p_branch,
+                      sd_env_source = sd_env_source,
+                      sd_env_lon = sd_env_lon) %>% 
+    filter(!(sd_env_lon == sd_env_source))
   
-  set.seed(111)
-  net <- lapply(p_branch, FUN = function(x) brnet(n_patch = n_patch, p_branch = x, plot= FALSE,
-                                                  sd_env_lon = 0.01, sd_env_source = 1))
+  
+  net <- foreach(i = seq_len(nrow(para))) %do% {
+    set.seed(123)
+    brnet(n_patch = para$n_patch[i],
+          p_branch = para$p_branch[i],
+          sd_env_source = para$sd_env_source[i],
+          sd_env_lon = para$sd_env_lon[i],
+          plot = FALSE)
+  }
+  
   v_env <- unlist(lapply(seq_len(length(net)), FUN = function(x) net[[x]]$df_patch$environment))
   
   colvalue <- data.frame(color = viridis::viridis(length(v_env)),
@@ -56,8 +73,8 @@
       geom_node_point(shape = 21,
                       fill = colvalue$color[match(V(adj)$env, colvalue$value)],
                       color = grey(0.5),
-                      size = 2) +
-      labs(subtitle = paste("Branching prob. =", p_branch[i]))
+                      size = 3) +
+      labs(subtitle = paste("Branching prob. =", para$p_branch[i]))
   }
   
   
@@ -136,7 +153,8 @@
   
[…]

### 2021-02-22 figure.Rmd
edits: add network panels

@@
 
-```{r, fig.height=6, fig.width=8, fig.cap="(A) Framework for generating theoretical branching river networks.
-Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N_p$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N_p = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example).
-Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (a spatially autoregressive process with white noise; Methods).
+```{r, fig.height=6, fig.width=10, fig.cap="(A and B) Theoretical branching networks generated under contrasting landscape scenarios.
+Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N_p$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N_p = 30$ and $P_{b} = \\{0.2, 0.8\\}$ in this example).
+Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (Methods).
 Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values).
-In this example, we used values of environmental variation at headwaters $\\sigma_{h} = 1$ and the degree of local environmental noise $\\sigma_{l} = 0.01$.
-(B) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in C).
+Panel A and B show distinct landscape scenarios.
+Environmental variation at headwaters $\\sigma_{h}$ exceeds the degree of local environmental noise $\\sigma_{l}$ in A ($\\sigma_{h} = 1, \\sigma_{l} = 0.01$), while the opposite is true in B ($\\sigma_{h} = 0.01, \\sigma_{l} = 1$).
+(C) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in D).
 Red dots indicate sampling sites for fish surveys.
-(C) Map of study regions (left, Hokkaido, Japan; right, Midwest, US).
+(D) Map of study regions (left, Hokkaido, Japan; right, Midwest, US).
 Watersheds (i.e., metacommunities) are gray-shaded in proportion to the number of sampling sites."}
 
-source(here::here("/empirical/figure_map.R"))
+source(here::here("empirical/figure_map.R"))
 
@@
 
-source(here::here("/theory/figure_n_patch.R"))
+source(here::here("theory/figure_n_patch.R"))
 ```
@@
 
-source(here::here("/theory/figure_p_branch.R"))
+source(here::here("theory/figure_p_branch.R"))
 ```
@@
 
-source(here::here("/empirical/figure_diversity.R"))
+source(here::here("empirical/figure_diversity.R"))
 ```

### 2021-02-22 manuscript.Rmd
edits: minor updates

@@
 abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern in ecology[@lomolino2000] and is the foundation of many conservation strategies[@desmet2004; @neigel2003].
-However, many ecosystems possess a complex spatial structure that cannot be represented simply by area[@rodríguez-iturbe2001; @turner2015], and the role of  such scale-invariant complexity in scaling biodiversity relationships is largely unknown.
+However, many ecosystems possess a complex spatial structure that cannot be represented simply by area[@rodríguez-iturbe2001; @turner2015], and the role of  such scale-invariant complexity in scaling biodiversity is largely unknown.
 Here, we use theory and empirical analysis of extensive fish community data to show that ecosystem size and complexity jointly regulate biodiversity in rivers.
@@
 However, dispersal processes affected mechanisms that underlie the positive effects of ecosystem size and complexity on $\gamma$ diversity (compare left and right columns in **Figures 2 and 3**).
-We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation exists (i.e., species travel short distances).
+We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation existed (i.e., species travel short distances).
 This pattern reflects significant spatial variation in species composition over the branching network and is likely driven by the local association of species' niche and abiotic environments (i.e., species sorting)[@thompson2020].

### 2021-02-22 empirical/analysis_lm_bf.R
edits: change land use variable

@@ -12,9 +12,9 @@
     rename(gamma = Estimator,
            alpha = mu_alpha) %>% 
     mutate(beta = gamma/alpha,
-           logit_forest = log(frac_forest) - log(1 - frac_forest),
+           logit_agri = log(frac_agri) - log(1 - frac_agri),
            dam_density = n_dam/area) %>% 
-    mutate(resid_forest = resid(lm(logit_forest ~ region, data = .)),
+    mutate(resid_agri = resid(lm(logit_agri ~ region, data = .)),
            resid_temp = resid(lm(mean_temp ~ region, data = .)),
            resid_ppt = resid(lm(mean_ppt ~ region, data = .)),
            resid_dam = resid(lm(dam_density ~ region, data = .)))
@@ -25,11 +25,11 @@
   m_compare <- function(response, data) {
     
     mod1 <<- lm(log(response, 10) ~ log(area, 10)*region + log(p_branch, 10)*region + region +
-                                    scale(resid_temp) + scale(resid_ppt) + scale(resid_forest) + scale(resid_dam),
+                                    scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
                 data = data)
     
     mod0 <<- lm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
-                                    scale(resid_temp) + scale(resid_ppt) + scale(resid_forest) + scale(resid_dam),
+                                    scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
                     data = data)
     
     # bf01: bayes factor in favor of mod0 over mod1

### 2021-02-22 empirical/figure_diversity.R

@@ -43,9 +43,9 @@
   dat <- bind_rows(dat_hkd, dat_mw) %>% 
     rename(gamma = Estimator, alpha = mu_alpha) %>% 
     mutate(beta = gamma/alpha,
-           logit_forest = log(frac_forest) - log(1 - frac_forest),
+           logit_agri = log(frac_agri) - log(1 - frac_agri),
            dam_density = n_dam/area) %>% 
-    mutate(resid_forest = resid(lm(logit_forest ~ region, data = .)),
+    mutate(resid_agri = resid(lm(logit_agri ~ region, data = .)),
            resid_temp = resid(lm(mean_temp ~ region, data = .)),
            resid_ppt = resid(lm(mean_ppt ~ region, data = .)),
            resid_dam = resid(lm(dam_density ~ region, data = .))) %>% 
@@ -55,7 +55,7 @@
   dat_base <- data.frame(region = factor(rep(c("hokkaido", "midwest"), each = 100)),
                          resid_temp = mean(dat$resid_temp),
                          resid_ppt = mean(dat$resid_ppt),
-                         resid_forest = mean(dat$resid_forest),
+                         resid_agri = mean(dat$resid_agri),
                          resid_dam = mean(dat$resid_dam))
 
 # data frame for prediction -----------------------------------------------

### 2021-02-22 manuscript.Rmd
Update manuscript.Rmd

--- 2021-02-22 manuscript.Rmd
@@
 - Yusuke Miyazaki^[Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan]
-output: html_notebook
-abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern in ecology[@lomolino2000] and is the foundation of many conservation strategies[@desmet2004; @neigel2003].
+output: word_document
+abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern in ecology[@lomolino2000] and is the foundation of many conservation strategies[@myers2000; @desmet2004; @neigel2003].
 However, many ecosystems possess a complex spatial structure that cannot be represented simply by area[@rodríguez-iturbe2001; @turner2015], and the role of such scale-invariant complexity in scaling biodiversity relationships is largely unknown.
@@
 Here, we hypothesize that ecosystem size and complexity dictate biodiversity patterns in rivers - a prime example of complex branching ecosystems.
-Individual streams and rivers flow through different landscapes with distinct land use and geological backgrounds, serving as a spatial unit of unique in-stream environments[@moore2015; @terui2018].
-The recurrent merging of the diverse streams and rivers ultimately forms a fluvial network with fractal branching patterns[@rodríguez-iturbe2001].
-As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance[@terui2018; @yeakel2014], may represent a macro-scale control of the ecosystem's habitat heterogeneity (habitat diversity per unit area)[@terui2018; @moore2015].
+Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments[@peterson2013; @moore2015; @terui2018].
+The recurrent merging of the diverse tributaries ultimately forms a fluvial network with fractal branching patterns[@rodríguez-iturbe2001].
+As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance[@terui2018; @yeakel2014], may represent a macro-scale control of the ecosystem's habitat heterogeneity (habitat diversity per unit area)[@grant2007; @moore2015; @terui2018].
 Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity), two factors that regulate biodiversity at the metacommunity level[@hubbell2001; @iwasaki2012].
@@
 First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
-We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit[@terui2018; @yeakel2014] (**Figure 1**).
+We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit[@terui2018; @yeakel2014] (**Figure 1A and B**).
 Two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
@@
 We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), both of which are defined as standard deviations of normal distributions.
-When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation.
-This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries[@moore2015; @peterson2013].
-In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on habitat heterogeneity.
+When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation (**Figure 1A**).
+This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary[@moore2015; @peterson2013].
+In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to limited influences of branching on habitat heterogeneity (**Figure 1B**).
 This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities[@poff2007; @terui2018].
 Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity within a network.
-We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel $\theta$), dispersal probability, and the maximum value of interspecific competition strength (see **Methods**).
+We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel $\theta$), dispersal probability, and the maximum value of interspecific competition strength $\alpha_{max}$ (see Methods).
 These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supplementary Information**).
@@
 Our theoretical analysis yielded results consistent with our prediction.
-Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters ($\sigma_h$) is greater than the degree of local environmental noise ($\sigma_l$).
+Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**).
 The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios.
@@
 However, dispersal processes affected mechanisms that underlie the positive effects of ecosystem size and complexity on $\gamma$ diversity (compare left and right columns in **Figures 2 and 3**).
-We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation exists (i.e., species travel short distances).
-This pattern reflects significant spatial variation in species composition over the branching network and is likely driven by the local association of species' niche and abiotic environments (i.e., species sorting)[@thompson2020].
+We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation existed (i.e., species travel short distances).
+This pattern reflected significant spatial variation in species composition over the branching network and was likely driven by the local association of species' niche and abiotic environments (i.e., species sorting)[@thompson2020].
 In contrast, when the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
@@
 In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$; **Figures S13-18**).
-Under this scenario, branching does not contribute to the ecosystem's habitat heterogeneity because local environmental noise masks environmental differences between tributaries.
+Under this scenario, branching has a minor influence on the ecosystem's habitat heterogeneity because patch-level environmental variation is equivalent to or greater than environmental differences between tributaries (**Figure 1B**).
 Therefore, this landscape scenario eliminates the positive effect of branching complexity on $\gamma$ diversity.
-This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams with diverse geological and/or climatic backgrounds show distinct environmental conditions, including water temperature, water chemistry, and flow/sediment regimes[@peterson2013; @moore2015].
-Instead, it may be more relevant to severely altered landscapes where human disturbance compromises the environmental distinctiveness of branches through, for example, flow regulations by dams[@poff2007].
+This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams show distinct and spatially-correlated environmental conditions, including water temperature, water chemistry, and flow/sediment regimes[@peterson2013; @moore2015].
+Instead, it may be most relevant to severely altered landscapes where localized human disturbance disrupts the environmental distinctiveness of branches through, for example, flow regulations by dams[@poff2007].
 Hence, our theory has important implications for riverine biodiversity conservation by pointing to the crucial role of habitat diversity produced by branching structure.
@@
 To confront this logistical challenge, we compiled fish community data across two geographic regions: Hokkaido Island in Japan and the Midwestern US (Midwest).
-These regions are located in comparable latitude ranges but support distinct fish communities (**Figure 1**).
+These regions are located in comparable latitude ranges (**Figure 1D**) but support distinct fish communities (**Tables S5 and S6**).
 Therefore, this data set provides an excellent opportunity to examine the generality of our theoretical predictions.
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area), or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-We combined this data set with geospatial information (watershed area, branching probability, annual mean temperature, annual cumulative precipitation, the fraction of forest, and dam density) to examine potential influences of macro-scale drivers of species diversity.
-Using this data set, we assessed whether observed patterns are consistent across the two geographic regions by developing global and region-specific models.
+These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at a multi-generation time scale[@comte2018], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
+We combined this data set with geospatial information, including watershed characteristics (watershed area and branching probability), climates (annual mean temperature and annual cumulative precipitation), and land use patterns (the fraction of agricultural land use and dam density).
+Using this data set, we assessed whether observed effects of the macro-scale factors are consistent across the two geographic regions by developing global and region-specific models.
 In the global model, we assumed that effects of ecosystem size (watershed area) and complexity (branching probability) are constant across the two regions (i.e., fixed slopes).
@@
 The estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) across watersheds.
-These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, the fraction of forest, and dam density) (**Table 1**).
+These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, agricultural land use, and dam density) (**Table 1**).
 Overall, our statistical analysis provides strong empirical evidence that ecosystem size and complexity jointly scale riverine biodiversity at the metacommunity level.
@@
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly matches the previous observations of stream fish movement.
-Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters[@radinger2014].
+Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters at an annual scale[@radinger2014].
 The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
 
-The consistent effect of branching probability on $\gamma$ diversity across the study regions is noteworthy because the watersheds in the Midwest are severely altered by agriculture (mean % agricultural land use: `r round(mean(wsd_subset[[2]]$frac_agri)*100)`% in the Midwest and `r round(mean(wsd_subset[[1]]$frac_agri)*100)`% in Hokkaido).
-If the intensive land use by humans causes significant homogenization of in-stream habitat conditions among tributaries, theory predicts a weakened effect of branching probability on $\gamma$ diversity.
-However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions to support high spatial difference of species composition.
-In support of this interpretation, $\beta$ diversity increased with increasing branching probability in both regions (**Figure 4**).
-It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, persist in human-dominated landscapes to maintain the diversity of in-stream processes among tributaties.
+The consistent effect of branching probability on $\gamma$ diversity across the study regions is noteworthy because many watersheds in the Midwest have been altered by agricultural land use (mean % agricultural land use: `r round(mean(wsd_subset[[2]]$frac_agri)*100)`% in the Midwest and `r round(mean(wsd_subset[[1]]$frac_agri)*100)`% in Hokkaido).
+If the intensive land use by humans impairs biological or physical distinctiveness among tributaries, theory predicts a weakened effect of branching probability on $\gamma$ diversity.
+However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions to support high spatial variation in species composition.
+Indeed, $\beta$ diversity increased with increasing branching probability in both regions (**Figure 4**).
+It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, persist in human-dominated landscapes to maintain the diversity of in-stream processes among tributaries.
+The lack of land use effects (the fraction of agricultural land use) corroborates our interpretation (**Table 1**).
 Although our analysis is correlative, the finding is encouraging because the branching complexity of river networks may serve as a natural defense system to human-induced environmental changes.
@@
 However, we are confident in our statistical inference because the observed patterns were fairly consistent with our theoretical predictions that are free from any confounding effects.
-Further, our fitted models showed moderate to high R^2^ values ($\alpha$ diversity: `r round(summary(fit$alpha$model)$r.squared, 2)`; $\beta$ diversity, `r round(summary(fit$beta$model)$r.squared, 2)`; $\gamma$ diversity `r round(summary(fit$gamma$model)$r.squared, 2)`).
+Further, our fitted models accounted for possible covariates (climates and land use patterns; **Table 1**) and showed moderate to high R^2^ values ($\alpha$ diversity: `r round(summary(fit$alpha$model)$r.squared, 2)`; $\beta$ diversity, `r round(summary(fit$beta$model)$r.squared, 2)`; $\gamma$ diversity `r round(summary(fit$gamma$model)$r.squared, 2)`).
 Therefore, it is very unlikely that spurious correlations are responsible for our results.
@@
 
-While the prevailing evidence supports the importance of ecosystem size in scaling species diversity[@iwasaki2012; @triantis2012], ecosystem complexity has not received the attention it deserves.
+While the prevailing evidence supports the importance of ecosystem size in scaling species diversity[@hubbell2001; @triantis2012; @iwasaki2012], ecosystem complexity has not received the attention it deserves.
 However, the ubiquity of scale-invariant complexity across terrestrial[@turner2015] and aquatic ecosystems[@rodríguez-iturbe2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at an ecological time scale[@comte2018; @giam2016], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
 Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (**Supplementary Information**).
@@
 Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$.
-The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of forest land use (logit-transformed), and dam density.
+The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use (logit-transformed), and dam density.
 Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically.
-We did not include the fractions of urban and agricultural land use in the statistical models because these variables were strongly correlated with the fraction of forest land use (**Figure S19**).
+We did not include the fractions of urban and forest land use in the statistical models because these variables were strongly correlated with the fraction of agricultural land use (**Figure S19**).
 Similarly, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**).
@@
 
-Climate (air temperature and precipitation) and land use (the fraction of forest and dam density) differed clearly between the regions.
+Climate (air temperature and precipitation) and land use (the fraction of agricultural land use and dam density) differed clearly between the regions.
 Therefore, we used residuals of the simple linear regressions between the climate or land use variable (response variable) and region (explanatory variable).
@@
 
+All explanatory variables except watershed area, branching probability, and region were standardized to a mean of zero and a standard deviation of one before the analysis.
+
 We compared the performance of these competing models using the Bayes factor[@wagenmakers2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1).
@@
 We thank Michio Fukushima and Hirokazu Urabe for providing information on the Hokkaido Freshwater Fish Database HFish and the fish monitoring data at protected watersheds in Hokkaido.
+We thank Jacques Finlay for his constructive comments on the earlier version of the manuscript.
 This research was funded by National Science Foundation through a Water Sustainability and Climate Program (WSC) Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1), and the University of North Carolina at Greensboro through a start-up fund.

### 2021-02-22 table.Rmd
edits: change land use variable

@@
 Response variables were log-10 transformed.
-Climate and land use variables (air temperature, precipitation, logit fraction of forest, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.",
+Climate and land use variables (air temperature, precipitation, logit fraction of agriculture, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.",
                      covariate.labels = c("$log_{10}$ Watershed area",
@@
                                           "Precipitation",
-                                          "Logit fraction of forest",
+                                          "Logit fraction of agriculture",
                                           "Dam density",

### 2021-02-22 manuscript.Rmd
Update manuscript.Rmd

@@
 Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments[@peterson2013; @moore2015; @terui2018].
-The recurrent merging of the diverse tributaries ultimately forms a fluvial network with fractal branching patterns[@rodríguez-iturbe2001].
+The recurrent merging of diverse tributaries ultimately forms a fluvial network with fractal branching patterns[@rodríguez-iturbe2001].
 As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance[@terui2018; @yeakel2014], may represent a macro-scale control of the ecosystem's habitat heterogeneity (habitat diversity per unit area)[@grant2007; @moore2015; @terui2018].
@@
 R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at <https://github.com/aterui/mcbrnet>).
-Codes for simulations, statistical analysis, figures, and tables are available at XXX.
+Codes for simulations, statistical analysis, figures, and tables are available at <https://github.com/aterui/public-proj_stream-diversity>.
 

### 2021-02-22 manuscript.Rmd
Update manuscript.Rmd

@@
 For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches[@carrara2012].
-However, most research has explored the consequences of branching complexity for local community structure[@ers2019; @carrara2012] or has relied solely on theoretical arguments with limited replications of branching architecture[@holt2018].
+However, most empirical research has explored the consequences of branching complexity for local community structure[@ers2019; @carrara2012] or has relied solely on theoretical arguments with limited replications of branching architecture[@holt2018].
 At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
@@
 These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, agricultural land use, and dam density) (**Table 1**).
-Overall, our statistical analysis provides strong empirical evidence that ecosystem size and complexity jointly scale riverine biodiversity at the metacommunity level.
+Our statistical analysis provides the first empirical evidence that ecosystem complexity regulates riverine biodiversity at the metacommunity level while conferring additional support for the ecosystem size effect on fish communities[@iwasaki2012].
 

### 2021-02-23 manuscript.Rmd
Update manuscript.Rmd

@@
 Metacommunity simulations in branching networks predicted biodiversity patterns consistent with our hypothesis.
-Larger and more branched ecosystems supported greater species richness at the watershed scale, and the importance of spatial difference in species composition was increasingly apparent when simulated species dispersal was limited.
+Larger and more branched ecosystems supported greater species richness at the watershed scale, and the importance of local environmental filtering of species was increasingly apparent when simulated species dispersal was limited.
 Cross-watershed comparisons across two geographic regions (Hokkaido Island in Japan and the Midwestern US) provided empirical support for the theoretical predictions.

### 2021-03-01 manuscript_science.Rmd
edits: re-format to Science

--- 2021-02-22 manuscript.Rmd
@@
 title: "Ecosystem size and complexity dictate riverine biodiversity"
-author:
-- Akira Terui^[Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA]
-- Seoghyun Kim\footnotemark[1]
-- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of
-  Minnesota, St. Paul, MN 55108, USA]
-- Taku Kadoya^[National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan]
-- Yusuke Miyazaki^[Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan]
-output: word_document
-abstract: The species-area relationship, a tendency in which species richness increases with increasing area, is a ubiquitous pattern in ecology[@lomolino2000] and is the foundation of many conservation strategies[@myers2000; @desmet2004; @neigel2003].
-However, many ecosystems possess a complex spatial structure that cannot be represented simply by area[@rodríguez-iturbe2001; @turner2015], and the role of such scale-invariant complexity in scaling biodiversity relationships is largely unknown.
-Here, we use theory and empirical analysis of extensive fish community data to show that ecosystem size and complexity jointly regulate biodiversity in rivers.
-Rivers are a prime example of fractal branching networks where the recurrent merging of diverse streams generates a pronounced self-similarity in complex branching patterns[@rodríguez-iturbe2001].
-Ecosystem complexity, which we define as the probability of branching per unit river distance[@terui2018; @yeakel2014], should increase watershed-scale species richness by increasing habitat heterogeneity.
-Meanwhile, ecosystem size should dictate metacommunity size and total habitat diversity, two factors that regulate watershed-scale species richness[@hubbell2001; @kallimanis2008].
-Metacommunity simulations in branching networks predicted biodiversity patterns consistent with our hypothesis.
-Larger and more branched ecosystems supported greater species richness at the watershed scale, and the importance of spatial difference in species composition was increasingly apparent when simulated species dispersal was limited.
-Cross-watershed comparisons across two geographic regions (Hokkaido Island in Japan and the Midwestern US) provided empirical support for the theoretical predictions.
-In both regions, watershed-scale species richness increased with ecosystem size (watershed area) and complexity (branching probability) through enhanced spatial difference in species composition.
-Recognizing the dual control of biodiversity should broaden viable options for spatial planning of protected areas or restoration, thereby helping conserve biodiversity from societal demands that threaten it.
-
-csl: nature.csl
+output:
+  pdf_document:
+    latex_engine: xelatex
+csl: science.csl
 knit: (function(inputFile, encoding) {
@@
 
+**One sentence summary:** Using theory and empirical analysis of extensive community data, this research provides the first robust evidence that ecosystem size and complexity jointly regulate biodiversity in rivers at large spatial scales.
+
+**Authors:** Akira Terui^1^, Seoghyun Kim^1^, Christine L. Dolph^2^, Taku Kadoya^3^, Yusuke Miyazaki^4^
+
+**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ Department of Ecology, Evolution and Behavior, University of Minnesota, St.
+Paul, MN 55108, USA ^3^ National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan ^4^ Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan
+
+**Abstract:** Larger ecosystems generally support more species; this ubiquitous ecological pattern is the foundation of many conservation strategies.
+However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such ecosystem complexity in scaling biodiversity is largely unknown.
+Here, we use theory and empirical analysis of extensive fish community data from two geographic regions (Japan and US) to show that ecosystem size and complexity dictate riverine biodiversity.
+We found that larger and more branched 'complex' river networks harbored greater species richness due to increased space and environmental heterogeneity.
+The complexity effect was comparative to the size effect, and this pattern emerged regardless of ecological contexts.
+Recognizing the dual control of biodiversity should broaden viable options for successful conservation.
+
 # Maintext
@@
 Ecologists have long sought to understand the general drivers of biodiversity.
-One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR)[@lomolino2000].
-In 1921, Arrhenius[@arrhenius1921] formulated the SAR as a power-law $S = cA^z$, an equation currently known as the Arrhenius species-area relationship ($S$ is the number of species observed in a given geographic area $A$, $c$ the constant, and $z$ the scaling exponent).
-Since then, the spatial scaling of species richness has been observed in many taxonomic groups[@triantis2012].
+One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR) [@lomolino2000].
+In 1921, Arrhenius [@arrhenius1921] formulated the SAR as a power-law $S = cA^z$, an equation currently known as the Arrhenius species-area relationship ($S$ is the number of species observed in a given geographic area $A$, $c$ the constant, and $z$ the scaling exponent).
+Since then, the spatial scaling of species richness has been observed in many taxonomic groups [@triantis2012].
 The SAR is ubiquitous because multiple mechanisms produce an apparently similar pattern.
-Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity[@kallimanis2008], larger metacommunity size[@hubbell2001], and/or enhanced colonization dynamics[@losos2009].
-Importantly, the SAR provides the foundation for global conservation efforts[@myers2000; @desmet2004; @neigel2003].
-For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas[@desmet2004; @neigel2003], which currently encompass more than 30 million km^2^ globally[@deguignet2014].
+Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity [@kallimanis2008], larger metacommunity size [@hubbell2001], and/or enhanced colonization dynamics [@losos2009].
+Importantly, the SAR provides the foundation for global conservation efforts [@myers2000; @desmet2004; @neigel2003].
+For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas [@desmet2004; @neigel2003], which currently encompass more than 30 million km^2^ globally [@deguignet2014].
 
-Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity[@turner2015; @rodríguez-iturbe2001].
-Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few[@rodríguez-iturbe2001].
-Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike[@rodríguez-iturbe2001].
-Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms[@grant2007].
-Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure, and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems[@rinaldo2018].
-For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches[@carrara2012].
-However, most research has explored the consequences of branching complexity for local community structure[@ers2019; @carrara2012] or has relied solely on theoretical arguments with limited replications of branching architecture[@holt2018].
+Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity [@turner2015; @rodríguez-iturbe2001].
+Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few [@rodríguez-iturbe2001].
+Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike [@rodríguez-iturbe2001].
+Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms [@grant2007].
+Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure, and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems [@rinaldo2018].
+For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches [@carrara2012].
+However, most empirical research has explored the consequences of branching complexity for local community structure [@ers2019; @carrara2012] or has relied solely on theoretical arguments with limited replications of branching architecture [@holt2018].
 At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
-Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services[@dudgeon2006].
+Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services [@dudgeon2006].
 
 Here, we hypothesize that ecosystem size and complexity dictate biodiversity patterns in rivers - a prime example of complex branching ecosystems.
-Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments[@peterson2013; @moore2015; @terui2018].
-The recurrent merging of diverse tributaries ultimately forms a fluvial network with fractal branching patterns[@rodríguez-iturbe2001].
-As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance[@terui2018; @yeakel2014], may represent a macro-scale control of the ecosystem's habitat heterogeneity (habitat diversity per unit area)[@grant2007; @moore2015; @terui2018].
-Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity), two factors that regulate biodiversity at the metacommunity level[@hubbell2001; @iwasaki2012].
+Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@peterson2013; @moore2015; @terui2018].
+The recurrent merging of diverse tributaries ultimately forms a fluvial network with fractal branching patterns [@rodríguez-iturbe2001].
+As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@terui2018; @yeakel2014], may represent a macro-scale control of the ecosystem's habitat heterogeneity (habitat diversity per unit area) [@grant2007; @moore2015; @terui2018].
+Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity), two factors that regulate biodiversity at the metacommunity level [@hubbell2001; @iwasaki2012].
 We predict that ecosystem size and branching complexity increase watershed-scale species richness ($\gamma$ diversity) by enhancing local species richness ($\alpha$ diversity) and/or spatial difference of species composition ($\beta$ diversity) under different ecological scenarios.
@@
 
+# Synthesizing ecosystem size and complexity influences
+
 First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
-We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit[@terui2018; @yeakel2014] (**Figure 1A and B**).
+We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit [@terui2018; @yeakel2014] (**Figure 1A and B**).
 Two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
 Environmental values at headwaters are drawn randomly from a normal distribution and propagate downstream with local environmental noise (i.e., a spatial autoregressive process with white noise).
-These environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see **Methods**).
+These environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see **Materials and Methods**).
 Therefore, our network-generation procedure resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
-We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity framework[@thompson2020].
-In this model, 50 species with different abiotic niches (optimum and width) disperse along a network and compete for resources with varied strengths in temporally dynamic environments (see **Methods** for model details).
+We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity framework [@thompson2020].
+In this model, 50 species with different abiotic niches (optimum and width) disperse along a network and compete for resources with varied strengths in temporally dynamic environments (see **Materials and Methods** for model details).
 
-Given the results of extensive sensitivity analysis (**Supplementary Information**), we considered `r n_scenario` simulation scenarios comprising a combination of four landscape and eight ecological scenarios.
+Given the results of extensive sensitivity analysis (**Supplementary Text**), we considered `r n_scenario` simulation scenarios comprising a combination of four landscape and eight ecological scenarios.
 We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), both of which are defined as standard deviations of normal distributions.
 When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation (**Figure 1A**).
-This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary[@moore2015; @peterson2013].
+This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary [@moore2015; @peterson2013].
 In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to limited influences of branching on habitat heterogeneity (**Figure 1B**).
-This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities[@poff2007; @terui2018].
+This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities [@poff2007; @terui2018].
 Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity within a network.
-We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel $\theta$), dispersal probability, and the maximum value of interspecific competition strength $\alpha_{max}$ (see Methods).
-These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supplementary Information**).
+We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel $\theta$), dispersal probability, and the maximum value of interspecific competition strength $\alpha_{max}$ (see **Materials and Methods**).
+These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supplementary Text**).
 Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 400 time steps of initialization and burn-in periods) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
@@
 We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation existed (i.e., species travel short distances).
-This pattern reflected significant spatial variation in species composition over the branching network and was likely driven by the local association of species' niche and abiotic environments (i.e., species sorting)[@thompson2020].
+This pattern reflected significant spatial variation in species composition over the branching network and was likely driven by the local association of species' niche and abiotic environments (i.e., species sorting) [@thompson2020].
 In contrast, when the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
-The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects)[@thompson2020].
+The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects) [@thompson2020].
 These patterns were consistent across different levels of dispersal probabilities (**Figures S5 and S12**).
@@
 Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2 and S5-11**).
-This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity[@hubbell2001].
+This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity [@hubbell2001].
 In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$; **Figures S13-18**).
@@
 Therefore, this landscape scenario eliminates the positive effect of branching complexity on $\gamma$ diversity.
-This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams show distinct and spatially-correlated environmental conditions, including water temperature, water chemistry, and flow/sediment regimes[@peterson2013; @moore2015].
-Instead, it may be most relevant to severely altered landscapes where localized human disturbance disrupts the environmental distinctiveness of branches through, for example, flow regulations by dams[@poff2007].
+This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams show distinct and spatially-correlated environmental conditions, including water temperature, water chemistry, and flow/sediment regimes [@peterson2013; @moore2015].
+Instead, it may be most relevant to severely altered landscapes where localized human disturbance disrupts the environmental distinctiveness of branches through, for example, flow regulations by dams [@poff2007].
 Hence, our theory has important implications for riverine biodiversity conservation by pointing to the crucial role of habitat diversity produced by branching structure.
+
+# Empirical evidence from distinct geographic regions
 
@@
 Therefore, this data set provides an excellent opportunity to examine the generality of our theoretical predictions.
-After careful data selection (see **Methods** and **Supplementary Information**), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; **Methods**) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in the Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
-We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area), or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at a multi-generation time scale[@comte2018], while posing challenges to traverse across watersheds (the ocean or lentic habitats).
+After careful data selection (see **Materials and Methods** and **Supplementary Text**), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; **Materials and Methods**) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in the Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
+These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at a multi-generation time scale [@comte2018], while posing challenges to traverse across watersheds (the ocean or lentic habitats; see **Materials and Methods** for watershed definition).
 We combined this data set with geospatial information, including watershed characteristics (watershed area and branching probability), climates (annual mean temperature and annual cumulative precipitation), and land use patterns (the fraction of agricultural land use and dam density).
@@
 In the global model, we assumed that effects of ecosystem size (watershed area) and complexity (branching probability) are constant across the two regions (i.e., fixed slopes).
-Meanwhile, the region-specific model assumes region-specific slopes of ecosystem size and complexity (**Methods**).
+Meanwhile, the region-specific model assumes region-specific slopes of ecosystem size and complexity (**Materials and Methods**).
 We compared the support of these competing models using the Bayes factor, a measure of the strength of evidence in favor of one model over the alternative.
-In our definition (**Methods**), the Bayes factor of $> 1$ indicates the support for the global model over the region-specific model.
+In our definition (**Materials and Methods**), the Bayes factor of $> 1$ indicates the support for the global model over the region-specific model.
 
@@
 These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, agricultural land use, and dam density) (**Table 1**).
-Overall, our statistical analysis provides strong empirical evidence that ecosystem size and complexity jointly scale riverine biodiversity at the metacommunity level.
+Our statistical analysis provides the first empirical evidence that ecosystem complexity regulates riverine biodiversity at the metacommunity level while conferring additional support for the ecosystem size effect on fish communities [@iwasaki2012].
 
@@
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly matches the previous observations of stream fish movement.
-Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters at an annual scale[@radinger2014].
+Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters at an annual scale [@radinger2014].
 The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
@@
 
+# Implications for biodiversity conservation
+
 The emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
 First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
-Human-induced habitat alterations, including flow regulation[@poff2007], habitat fragmentation[@grill2019], and stream burial[@elmore2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
+Human-induced habitat alterations, including flow regulation [@poff2007], habitat fragmentation [@grill2019], and stream burial [@elmore2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
 Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human activities.
 Second, the complexity perspective may provide insights into the spatial planning of conservation efforts.
-Riverine reserves and local restoration are increasingly recognized as an effective management tool, and designing a spatial network of conservation sites in rivers is an area of active research[@koning2020].
+Riverine reserves and local restoration are increasingly recognized as an effective management tool, and designing a spatial network of conservation sites in rivers is an area of active research [@koning2020].
 While large reserves or restoration sites are undoubtedly important, our results indicate the potential of coordinated networks of local conservation sites in protecting biodiversity.
-For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin[@koning2020].
+For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin [@koning2020].
 
-While the prevailing evidence supports the importance of ecosystem size in scaling species diversity[@hubbell2001; @triantis2012; @iwasaki2012], ecosystem complexity has not received the attention it deserves.
-However, the ubiquity of scale-invariant complexity across terrestrial[@turner2015] and aquatic ecosystems[@rodríguez-iturbe2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
+While the prevailing evidence supports the importance of ecosystem size in scaling species diversity [@hubbell2001; @triantis2012; @iwasaki2012], ecosystem complexity has not received the attention it deserves.
+However, the ubiquity of scale-invariant complexity across terrestrial [@turner2015] and aquatic ecosystems [@rodríguez-iturbe2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
 Our fundamental findings of the dual control of biodiversity should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
@@
 The generalization of our findings in spatially complex ecosystems represents a frontier for future research.
-
-# Methods
-
-## Theory
-
-### Network generation
-
-We depicted branching ecosystems as a bifurcating network of connected habitat patches[@terui2018; @yeakel2014] (**Figure 1**).
-Habitat patches, or local communities, can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
-Two parameters determine the geometric properties of simulated branching networks: the number of habitat patches $N_p$ (ecosystem size) and branching probability $P_b$ (ecosystem complexity).
-Each habitat patch is assigned to be a branching patch (including upstream terminals) with probability $P_b$ or a non-branching patch with probability $1-P_b$.
-In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in branch $q$, $n_{p,q}$, is a realization of a random variable drawn from a geometric distribution $n_{p,q} \sim Ge(P_{b})$[@terui2018] but conditional on $\sum_{q=1}^{N_b}n_{p,q} = N_p$ ($N_b$ is the number of branches in a network).
-The number of branches $N_b$ is identical to the number of branching habitat patches in a network, or the number of 'success' out of $N_p$ trials.
-This leads to an assumption that $N_b$ is a realization of a random variable drawn from a binomial distribution as $N_b \sim Binomial(N_p, P_b)$.
-This framework has two merits.
-First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution)[@rodríguez-iturbe2001].
-Second, it preserves the fractal nature of branching patterns[@peckham1999].
-An alternative approach is the use of optimal channel networks[@carraro2020].
-However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to compare theoretical predictions with empirical observations.
-
-In our network generation, we first drew $N_b$ from the binomial distribution but selected an odd number to constitute a bifurcating branching network.
-We then determined $n_{p,q}$ as random draws from the geometric distribution with the constraint of $\sum_{q=1}^{N_b}n_{p,q} = N_p$.
-The generated branches were organized randomly into a bifurcating branching network.
-
-Two sources of variation characterize the long-term average of the abiotic environment at each habitat patch: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
-We drew random values from a normal distribution with a mean of zero and a standard deviation of $\sigma_{h}$ and assigned them to headwater patches (i.e., the most upstream patches).
-These environmental values at headwaters propagate downstream through a spatial autoregressive process defined as:
-
-$$
-\mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k}
-$$
-
-where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and a standard deviation of $\sigma_l$.
-The parameter $\rho$ can take values of $0-1$ with larger values indicating greater spatial autocorrelation.
-In this study, we set $\rho = 1$ to mimic strong spatial autocorrelation in riverine environments.
-At confluences, we took a weighted mean of environmental values given the relative size of upstream contributing area of joining tributaries:
-
-$$
-\begin{align}
-\mu_{z,k} &= \omega(\rho \mu_{z,k+1}^R + \epsilon_{k}^R) + (1-\omega)(\rho \mu_{z,k+1}^L + \epsilon_{k}^L) \\
-\omega &= \frac{A_{k+1}^R}{A_{k+1}^R + A_{k+1}^L}
-\end{align}
-$$
-
-where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area; $A_k = 1$ at the most upstream patch).
-The parameter $\omega$ takes values of $0-1$ and represents the relative influence of the right tributary given the relative size of joining tributaries.
-With this expression, larger tributaries have a greater influence on the downstream environment, as observed in natural river networks[@benda2004].
-
-### Metacommunity model
-
-We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al[@thompson2020].
-In this framework, abiotic environmental conditions (density-independent), intra- and interspecific competition (density-dependent), and dispersal regulate a species' realized population growth.
-Below, we describe the details of our metacommunity model.
-
-The realized number of individuals $N_{ix}(t + 1)$ (species $i$ at patch $x$ and time $t+1$) is given as:
-
-$$
-N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
-$$
-
-where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$.
-The realized discrete number of individuals is drawn from a Poisson distribution to account for stochasticity in demographic and dispersal processes[@fronhofer2017; @thompson2020].
-Local community dynamics are simulated based on the Beverton-Holt equation[@beverton1957]:
-
-$$
-n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}}
-$$
-
-where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
-$K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area[@terui2016; @rahel1991].
-The parameter $\alpha_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ \> 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
-$\alpha_{ij}$ was drawn randomly from a uniform distribution as $\alpha_{ij} \sim Unif(0, \alpha_{max})$.
-The density-independent reproductive rate $r_{ix}(t)$ is affected by abiotic environments (non-consumable) and determined by the following Gaussian function:
-
-$$
-r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{\{\mu_i-z_x(t)\}^2}{2\sigma^2_{niche,i}}}]
-$$
-
-where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$.
-We introduced the cost of a wide niche by multiplying $\delta$[@chaianunporn2015]:
-
-$$
-\delta = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
-$$
-
-Smaller values of $\nu$ imply greater costs of having a wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$ near the niche optimum.
-
-The environmental value at patch $x$ and time $t$, $z_x(t)$, is assumed to follow a multivariate normal distribution as $z_{x}(t) \sim MVN(\boldsymbol{\mu_z}, \boldsymbol{\Omega_z})$, where $\boldsymbol{\mu_z}$ is the vector of mean environmental conditions of habitat patches and $\boldsymbol{\Omega_z}$ is the variance-covariance matrix.
-The diagonal elements of the variance-covariance matrix $\sigma^2_z$ represent the degree of temporal environmental variation.
-The off-diagonal elements $\Omega_{xy}$ represent the spatial autocorrelation in temporal environmental variation as:
-
-$$
-\Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy})
-$$
-
-$\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (the shortest network path measured as the number of habitat patches).
-The parameter $\phi$ determines the degree of the distance decay of environmental correlates.
-
-The expected number of emigrants at time $t$ is the product of dispersal probability $p_d$ and $n_{ix}(t)$: $E_{ix}(t) = p_{d}n_{ix}(t)$.
-The immigration probability at patch $x$ for species $i$, $\xi_{ix}(t)$, is calculated using the following equation that accounts for separation distance among habitat patches and dispersal capability of a species:
-
-$$
-\xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}
-$$
-
-The parameter $\theta$ regulates the dispersal distance of a species that follows an exponential distribution ($\theta^{-1}$ corresponds to the expected dispersal distance).
-The expected number of immigrants is calculated as $I_{ix}(t) = \xi_{ix}(t)\sum_x^{N_p} E_{ix}$.
-
-### Simulation
-
-We used `r n_scenario` sets of parameter combinations (i.e., simulation scenarios) based on the results of extensive sensitivity analysis (**Supplementary Information**).
-The parameter combinations comprises four landscape and eight ecological scenarios.
-Landscape scenarios distinguish spatial patterns of habitat heterogeneity, while ecological scenarios change ecological traits of simulated species.
-For landscape scenarios, we used four combinations of environmental variation at headwaters ($\sigma_h = 0.01, 1$) and the degree of local environmental noise ($\sigma_l = 0.01, 1$).
-The inequality of $\sigma_h$ and $\sigma_l$ controls the coupling of branching complexity and habitat heterogeneity.
-For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`).
-This setup results in eight ecological scenarios with different levels of dispersal and competition.
-
-We allowed interspecific variation in niche optimum and width, which were drawn from uniform distributions as $\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$.
-We used fixed values for the following parameters: maximum reproductive rate ($r_{0,i} =$ 4), niche cost ($\nu =$ `r unique(dat_sim$niche_cost)`), the degree of temporal environmental variation ($\sigma_z =$ `r unique(dat_sim$sd_env)`), and the extent of spatial autocorrelation in temporal environmental dynamics ($\phi =$ `r unique(dat_sim$phi)`).
-
-Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 200 time steps for initialization and 200 time steps for burn-in) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
-During the first 200 time steps (an initialization period), we initialized the simulation by seeding each habitat patch with populations of each species drawn from a Poisson distribution with a mean of 0.5.
-We repeated the seeding every 10 time steps during the initialization to allow species to establish their populations if they can grow from low abundances.
-After the initialization period, we ran 200 time steps as a burn-in period with no seeding to minimize influences of initial conditions.
-We saved the last 1000 time steps to estimate the temporal averages of $\alpha$, $\beta$, and $\gamma$ diversity.
-We removed simulation replicates in which no species established populations over the initial 400 time steps (`r sum(dat_sim$alpha_div == 0)` replicates out of `r nrow(dat_sim)` replicates).
-Ecosystem size and complexity were drawn randomly from uniform distributions as: $N_p \sim Unif(10, 150)$ and $P_b \sim Unif(0.01, 0.99)$ ($N_p$ was rounded to the nearest integer before running simulations).
-Values of simulation parameters were summarized in **Table S2**.
-We performed simulations using R version 4.0.2[@rcoreteam2020].
-
-## Empirical data analysis
-
-### Fish community data
-
-We compiled fish data at two geographic regions: the Hokkaido island, Japan, and the Midwest, US.
-For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish[@fukushima2007; @fukushima2011], monitoring data at protected watersheds[@comte2021; @terui2018], and primary data collected by the authors[@miyazaki2016; @terui2016], which collectively cover the entire Hokkaido island.
-For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources[@iowadepartmentofnaturalresources2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@illinoisenvironmentalprotectionagency2014], Minnesota Pollution Control Agency[@minnesotapollutioncontrolagency2014], and Wisconsin Department of Natural Resources[@wisconsindepartmentofnaturalresources2018].
-We detailed procedures for initial data selection in **Supplementary Information**.
-
-We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (**Supplementary Information**).
-
-We estimated $\alpha$, $\beta$, and $\gamma$ diversity at each watershed.
-$\gamma$ diversity is the total species richness at each watershed.
-Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity[@chao2014; @chase2020].
-We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT'[@hsieh2016].
-We assessed the completeness of the observed species richness based on sample coverage, which is the proportion of observed species richness to asymptotic species richness.
-We excluded watersheds whose sample coverage was below 0.9 because the estimates of asymptotic species richness may contain non-negligible statistical uncertainty.
-$\alpha$ diversity was estimated by taking an average of local species richness at each site.
-$\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity[@whittaker1960].
-
-After the data selection procedure, we obtained diversity estimates from `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (Hokkaido: `r nrow(wsd_subset[[1]])`, Midwest: `r nrow(wsd_subset[[2]])`), which encompassed a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites (Hokkaido: `r nrow(point_subset[[1]])`, Midwest: `r nrow(point_subset[[2]])`).
-Observations ranged from `r min(dat_hkd_site$Year, na.rm = T)` to `r max(dat_hkd_site$Year, na.rm = T)` in Hokkaido and from `r min(dat_mw_site$Year, na.rm = T)` to `r max(dat_mw_site$Year, na.rm = T)` in the Midwest.
-Fish species observed in the final data set were listed in **Tables S5 and S6**.
-
-### Environmental data
-
-We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]).
-We used Hydrologically Adjusted Elevations of MERIT Hydro[@yamazaki2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area).
-The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0[@yamazaki2015].
-Watershed area was estimated based on the delineated watershed polygons.
-We estimated branching probability by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$.
-A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
-We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro[@yamazaki2019].
-We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4[@hijmans2005].
-We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution)[@marcelbuchhorn2020].
-We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1)[@lehner2011].
-We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA'[@brenning2018], 'sf'[@pebesma2018], 'raster'[@hijmans2020], 'rgdal'[@rogerbivand2020], 'stars'[@edzerpebesma2020], and 'exactextractr'[@danielbaston2020].
-
-### Statistical analysis
-
-We developed linear regression models to examine the effects of macro-scale drivers on diversity metrics.
-Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$.
-The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use (logit-transformed), and dam density.
-Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically.
-We did not include the fractions of urban and forest land use in the statistical models because these variables were strongly correlated with the fraction of agricultural land use (**Figure S19**).
-Similarly, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**).
-Correlations for other combinations of explanatory variables were weak to moderate.
-
-Climate (air temperature and precipitation) and land use (the fraction of agricultural land use and dam density) differed clearly between the regions.
-Therefore, we used residuals of the simple linear regressions between the climate or land use variable (response variable) and region (explanatory variable).
-The residuals represent deviations from the regional averages; positive values indicate values greater than the regional average while negative values indicating values smaller than the regional average.
-
-We constructed two models for each of the diversity metrics: global and region-specific models.
-The global model assumes that the effects of watershed area and branching probability are consistent across geographic regions (i.e., no interactive effects of the region with other linear predictors).
-
-$$
-\mu_w = \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
-$$
-
-where $\xi_k$ are the intercept and regression coefficients for linear predictors.
-Meanwhile, the region-specific model assumes the effects of watershed area and branching probability differ between regions (i.e., interactions between region and watershed area/branching probability).
-
-$$
-\begin{align}
-\mu_w =& \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w +\\
-&\xi_4~log_{10}~WA_w \cdot region_w + \xi_5~log_{10}~P_{b,w} \cdot region_w + \sum_k \xi_k x_{k,w}
-\end{align}
-$$
-
-All explanatory variables except watershed area, branching probability, and region were standardized to a mean of zero and a standard deviation of one before the analysis.
-
-We compared the performance of these competing models using the Bayes factor[@wagenmakers2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1).
-We used Bayesian Information Criteria (BIC) of the linear models to approximate the Bayes factor[@wagenmakers2007]:
-
-$$
-Bayes~factor = exp(\Delta BIC_{10}/2)
-$$
-
-where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$. We performed statistical analysis using R version 4.0.2[@rcoreteam2020].
 
@@
 
-Third parties provided data for empirical data analysis; references are provided in the main text and Supplementary Information where appropriate.
+Third parties provided data for empirical data analysis; references are provided in the main text and Supplementary Text where appropriate.
 R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at <https://github.com/aterui/mcbrnet>).

### 2021-03-01 supplementary_information_science.Rmd
edits: re-format to Science

---
title: |
  | Supplementary Information for:
  | Ecosystem size and complexity dictate riverine biodiversity
author:
- Akira Terui^[Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA]
- Seoghyun Kim\footnotemark[1]
- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of Minnesota, St. Paul, MN 55108, USA]
- Taku Kadoya^[National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan]
- Yusuke Miyazaki^[Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan]
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
bibliography: references.bib
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

```{r setup, include=FALSE}

  pacman::p_load(tidyverse, knitr, kableExtra)
  knitr::opts_chunk$set(echo = FALSE,
                        message = FALSE,
                        warning = FALSE)

  pacman::p_load(tidyverse, sf)

  ## read gis files
  filename <- list.files(path = here::here('empirical/data_gis'), full.names = T)
  wsd_subset <- lapply(filename[str_detect(filename, "wsd_subset")], st_read)
  point_subset <- lapply(filename[str_detect(filename, "point_subset")], st_read)
  shape <- lapply(filename[str_detect(filename, "shape")], st_read)
  shape[[1]] <- st_set_crs(shape[[1]], st_crs(wsd_subset[[1]]))

  ## read theory file
  dat_sim <- read_csv(here::here('theory/result/result_sim2020-11-10.csv'))

  n_scenario <- dat_sim %>% distinct(n_species,
                       mean_env_source,
                       sd_env_source,
                       rho,
                       asymmetry_factor,
                       min_optim,
                       max_optim,
                       sd_env_lon,
                       theta,
                       K0,
                       sd_env,
                       spatial_env_cor,
                       phi,
                       min_niche_width,
                       max_niche_width,
                       niche_cost,
                       p_dispersal,
                       min_alpha,
                       max_alpha) %>% 
    nrow()

  # for bayes factor
  source(here::here('empirical/analysis_lm_bf.R'))

  # Hokkaido data
  dat_hkd_site <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))

  # Midwest data
  dat_mw_site <- read_csv(here::here('empirical/data_out/data_mw_site.csv')) %>% 
    mutate(Year = format(as.Date(Date, format = '%m/%d/%Y'), "%Y"))

  # sensitivity tables
  source(here::here('theory/table_sensitivity_analysis.R'))

```

# Materials and Methods

## Theory

### Network generation

We depicted branching ecosystems as a bifurcating network of connected habitat patches [@terui2018; @yeakel2014] (**Figure 1**). Habitat patches, or local communities, can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions. Two parameters determine the geometric properties of simulated branching networks: the number of habitat patches $N_p$ (ecosystem size) and branching probability $P_b$ (ecosystem complexity). Each habitat patch is assigned to be a branching patch (including upstream terminals) with probability $P_b$ or a non-branching patch with probability $1-P_b$. In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in branch $q$, $n_{p,q}$, is a realization of a random variable drawn from a geometric distribution $n_{p,q} \sim Ge(P_{b})$ [@terui2018] but conditional on $\sum_{q=1}^{N_b}n_{p,q} = N_p$ ($N_b$ is the number of branches in a network). The number of branches $N_b$ is identical to the number of branching habitat patches in a network, or the number of 'success' out of $N_p$ trials. This leads to an assumption that $N_b$ is a realization of a random variable drawn from a binomial distribution as $N_b \sim Binomial(N_p, P_b)$. This framework has two merits. First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution) [@rodríguez-iturbe2001]. Second, it preserves the fractal nature of branching patterns [@peckham1999]. An alternative approach is the use of optimal channel networks [@carraro2020]. However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to compare theoretical predictions with empirical observations.

In our network generation, we first drew $N_b$ from the binomial distribution but selected an odd number to constitute a bifurcating branching network. We then determined $n_{p,q}$ as random draws from the geometric distribution with the constraint of $\sum_{q=1}^{N_b}n_{p,q} = N_p$. The generated branches were organized randomly into a bifurcating branching network.

Two sources of variation characterize the long-term average of the abiotic environment at each habitat patch: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$). We drew random values from a normal distribution with a mean of zero and a standard deviation of $\sigma_{h}$ and assigned them to headwater patches (i.e., the most upstream patches). These environmental values at headwaters propagate downstream through a spatial autoregressive process defined as:

$$
\mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k}
$$

where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and a standard deviation of $\sigma_l$. The parameter $\rho$ can take values of 0-1 with larger values indicating greater spatial autocorrelation. In this study, we set $\rho = 1$ to mimic strong spatial autocorrelation in riverine environments. At confluences, we took a weighted mean of environmental values given the relative size of upstream contributing area of joining tributaries:

$$
\begin{aligned}
\mu_{z,k} &= \omega(\rho \mu_{z,k+1}^R + \epsilon_{k}^R) + (1-\omega)(\rho \mu_{z,k+1}^L + \epsilon_{k}^L) \\
\omega &= \frac{A_{k+1}^R}{A_{k+1}^R + A_{k+1}^L}
\end{aligned}
$$

where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area; $A_k = 1$ at the most upstream patch). The parameter $\omega$ takes values of 0-1 and represents the relative influence of the right tributary given the relative size of joining tributaries. With this expression, larger tributaries have a greater influence on the downstream environment, as observed in natural river networks [@benda2004].

### Metacommunity model

We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al [@thompson2020]. In this framework, abiotic environmental conditions (density-independent), intra- and interspecific competition (density-dependent), and dispersal regulate a species' realized population growth. Below, we describe the details of our metacommunity model.

The realized number of individuals $N_{ix}(t + 1)$ (species $i$ at patch $x$ and time $t+1$) is given as:

$$
N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
$$

where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$. The realized discrete number of individuals is drawn from a Poisson distribution to account for stochasticity in demographic and dispersal processes [@fronhofer2017; @thompson2020]. Local community dynamics are simulated based on the Beverton-Holt equation [@beverton1957]:

$$
n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}}
$$

where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity. $K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area [@terui2016; @rahel1991]. The parameter $\alpha_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ \> 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$). $\alpha_{ij}$ was drawn randomly from a uniform distribution as $\alpha_{ij} \sim Unif(0, \alpha_{max})$. The density-independent reproductive rate $r_{ix}(t)$ is affected by abiotic environments (non-consumable) and determined by the following Gaussian function:

$$
r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{\{\mu_i-z_x(t)\}^2}{2\sigma^2_{niche,i}}}]
$$

where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$. We introduced the cost of a wide niche by multiplying $\delta$ [@chaianunporn2015]:

$$
\delta = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
$$

Smaller values of $\nu$ imply greater costs of having a wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$ near the niche optimum.

The environmental value at patch $x$ and time $t$, $z_x(t)$, is assumed to follow a multivariate normal distribution as $z_{x}(t) \sim MVN(\boldsymbol{\mu_z}, \boldsymbol{\Omega_z})$, where $\boldsymbol{\mu_z}$ is the vector of mean environmental conditions of habitat patches and $\boldsymbol{\Omega_z}$ is the variance-covariance matrix. The diagonal elements of the variance-covariance matrix $\sigma^2_z$ represent the degree of temporal environmental variation. The off-diagonal elements $\Omega_{xy}$ represent the spatial autocorrelation in temporal environmental variation as:

$$
\Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy})
$$

$\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (the shortest network path measured as the number of habitat patches). The parameter $\phi$ determines the degree of the distance decay of environmental correlates.

The expected number of emigrants at time $t$ is the product of dispersal probability $p_d$ and $n_{ix}(t)$: $E_{ix}(t) = p_{d}n_{ix}(t)$. The immigration probability at patch $x$ for species $i$, $\xi_{ix}(t)$, is calculated using the following equation that accounts for separation distance among habitat patches and dispersal capability of a species:

$$
\xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}
$$

The parameter $\theta$ regulates the dispersal distance of a species that follows an exponential distribution ($\theta^{-1}$ corresponds to the expected dispersal distance). The expected number of immigrants is calculated as $I_{ix}(t) = \xi_{ix}(t)\sum_x^{N_p} E_{ix}$.

### Simulation

We used `r n_scenario` sets of parameter combinations (i.e., simulation scenarios) based on the results of extensive sensitivity analysis (**Supplementary Text**). The parameter combinations comprises four landscape and eight ecological scenarios. Landscape scenarios distinguish spatial patterns of habitat heterogeneity, while ecological scenarios change ecological traits of simulated species. For landscape scenarios, we used four combinations of environmental variation at headwaters ($\sigma_h = 0.01, 1$) and the degree of local environmental noise ($\sigma_l = 0.01, 1$). The inequality of $\sigma_h$ and $\sigma_l$ controls the relationship between branching complexity and habitat heterogeneity. For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`). This setup results in eight ecological scenarios with different levels of dispersal and competition.

We allowed interspecific variation in niche optimum and width, which were drawn from uniform distributions as $\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$. We used fixed values for the following parameters: maximum reproductive rate ($r_{0,i} =$ 4), niche cost ($\nu =$ `r unique(dat_sim$niche_cost)`), the degree of temporal environmental variation ($\sigma_z =$ `r unique(dat_sim$sd_env)`), and the extent of spatial autocorrelation in temporal environmental dynamics ($\phi =$ `r unique(dat_sim$phi)`).

Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 200 time steps for initialization and 200 time steps for burn-in) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`). During the first 200 time steps (an initialization period), we initialized the simulation by seeding each habitat patch with populations of each species drawn from a Poisson distribution with a mean of 0.5. We repeated the seeding every 10 time steps during the initialization to allow species to establish their populations if they can grow from low abundances. After the initialization period, we ran 200 time steps as a burn-in period with no seeding to minimize influences of initial conditions. We saved the last 1000 time steps to estimate the temporal averages of $\alpha$, $\beta$, and $\gamma$ diversity. We removed simulation replicates in which no species established populations over the initial 400 time steps (`r sum(dat_sim$alpha_div == 0)` replicates out of `r nrow(dat_sim)` replicates). Ecosystem size and complexity were drawn randomly from uniform distributions as: $N_p \sim Unif(10, 150)$ and $P_b \sim Unif(0.01, 0.99)$ ($N_p$ was rounded to the nearest integer before running simulations). Values of simulation parameters were summarized in **Table S2**. We performed simulations using R version 4.0.2 [@rcoreteam2020].

## Empirical data analysis

### Fish community data

We compiled fish data at two geographic regions: the Hokkaido island, Japan, and the Midwest, US. For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish [@fukushima2007; @fukushima2011], monitoring data at protected watersheds [@comte2021; @terui2018], and primary data collected by the authors [@miyazaki2016; @terui2016], which collectively cover the entire Hokkaido island. For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources [@iowadepartmentofnaturalresources2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources [@illinoisenvironmentalprotectionagency2014], Minnesota Pollution Control Agency [@minnesotapollutioncontrolagency2014], and Wisconsin Department of Natural Resources [@wisconsindepartmentofnaturalresources2018]. We detailed procedures for initial data selection in **Supplementary Text**.

We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area). Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (**Supplementary Text**).

We estimated $\alpha$, $\beta$, and $\gamma$ diversity at each watershed. $\gamma$ diversity is the total species richness at each watershed. Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity. Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity [@chao2014]. We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT' [@hsieh2016]. We assessed the completeness of the observed species richness based on sample coverage, which is the proportion abundances of observed species to the whole community [@chao2014]. We excluded watersheds whose sample coverage was below 0.9 because the estimates of asymptotic species richness may contain non-negligible statistical uncertainty. $\alpha$ diversity was estimated by taking an average of local species richness at each site. $\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity [@whittaker1960].

After the data selection procedure, we obtained diversity estimates from `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (Hokkaido: `r nrow(wsd_subset[[1]])`, Midwest: `r nrow(wsd_subset[[2]])`), which encompassed a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites (Hokkaido: `r nrow(point_subset[[1]])`, Midwest: `r nrow(point_subset[[2]])`). Observations ranged from `r min(dat_hkd_site$Year, na.rm = T)` to `r max(dat_hkd_site$Year, na.rm = T)` in Hokkaido and from `r min(dat_mw_site$Year, na.rm = T)` to `r max(dat_mw_site$Year, na.rm = T)` in the Midwest. Fish species observed in the final data set were listed in **Tables S5 and S6**.

### Environmental data

We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]). We used Hydrologically Adjusted Elevations of MERIT Hydro [@yamazaki2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area). The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0 [@yamazaki2015]. Watershed area was estimated based on the delineated watershed polygons. We estimated branching probability by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$. A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$. We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro [@yamazaki2019]. We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4 [@hijmans2005]. We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhorn2020]. We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehner2011]. We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenning2018], 'sf' [@pebesma2018], 'raster' [@hijmans2020], 'rgdal' [@rogerbivand2020], 'stars' [@edzerpebesma2020], and 'exactextractr' [@danielbaston2020].

### Statistical analysis

We developed linear regression models to examine the effects of macro-scale drivers on diversity metrics. Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$. The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use (logit-transformed), and dam density. Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically. We did not include the fractions of urban and forest land use in the statistical models because these variables were strongly correlated with the fraction of agricultural land use (**Figure S19**). Similarly, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**). Correlations for other combinations of explanatory variables were weak to moderate.

Climate (air temperature and precipitation) and land use (the fraction of agricultural land use and dam density) differed clearly between the regions. Therefore, we used residuals of the simple linear regressions between the climate or land use variable (response variable) and region (explanatory variable). The residuals represent deviations from the regional averages; positive values indicate values greater than the regional average while negative values indicating values smaller than the regional average.

We constructed two models for each of the diversity metrics: global and region-specific models. The global model assumes that the effects of watershed area and branching probability are consistent across geographic regions (i.e., no interactive effects of the region with other linear predictors).

$$
\mu_w = \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
$$

where $\xi_k$ are the intercept and regression coefficients for linear predictors. Meanwhile, the region-specific model assumes the effects of watershed area and branching probability differ between regions (i.e., interactions between region and watershed area/branching probability).

$$
\begin{aligned}
\mu_w =& \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w +\\
&\xi_4~log_{10}~WA_w \cdot region_w + \xi_5~log_{10}~P_{b,w} \cdot region_w + \sum_k \xi_k x_{k,w}
\end{aligned}
$$

All explanatory variables except watershed area, branching probability, and region were standardized to a mean of zero and a standard deviation of one before the analysis.

We compared the performance of these competing models using the Bayes factor [@wagenmakers2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1). We used Bayesian Information Criteria (BIC) of the linear models to approximate the Bayes factor [@wagenmakers2007]:

$$
Bayes~factor = exp(\Delta BIC_{10}/2)
$$

where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$. We performed statistical analysis using R version 4.0.2 [@rcoreteam2020].

\newpage

# Supplementary Text

## Theory

### Sensitivity analysis

We performed a sensitivity analysis of the metacommunity simulation to identify key simulation parameters that strongly affect the relationships between diversity metrics ($\alpha$, $\beta$, and $\gamma$) and ecosystem properties (the number of habitat patches $N_{p}$ and branching probability $P_{b}$). We generated 500 sets of parameter combinations by randomly drawing values of 8 simulation parameters from uniform distributions (**Table S1**). For each parameter combination, we generated 100 branching networks with the gradients of ecosystem size ($N_p \sim Unif(10, 150)$) and complexity ($P_b \sim Unif(0.01, 0.99)$). This results in a total of 50000 simulation replicates. In each simulation replicate, we allowed interspecific variation in niche optimum $\mu_i$ and width $\sigma_{niche,i}$ ($\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$, respectively; subscript $i$ represents species) and ran 1400 time steps of metacommunity dynamics. We obtained temporal means of $\alpha$, $\beta$, and $\gamma$ diversity for the last 1000 time steps. The first 400 time steps were discarded as initialization and burn-in periods. We removed simulation replicates in which no species established populations over the initial 400 time steps.

For each parameter combination, we regressed log-transformed $\alpha$, $\beta$, and $\gamma$ diversity ($log_{10}~y_j$ for network replicate $j$) on the number of habitat patches $N_{p}$ and branching probability $P_{b}$ as:

$$
\begin{aligned}
log_{10}~y_j &\sim Normal(\mu_j, \sigma^2)\\
       \mu_j &= \psi_0 + \psi_1~log_{10}~N_{p,j} + \psi_2~log_{10}~P_{b,j}
\end{aligned}
$$

where $\psi_k$ ($k = 0-2$) are the intercept ($\psi_0$) and regression coefficients ($\psi_1$ and $\psi_2$). We extracted 500 estimates of $\psi_1$ and $\psi_2$, which represent the effects of $N_{p}$ and $P_{b}$ on diversity metrics under a given parameter combination. To examine influences of simulation parameters (**Table S1**) on $\psi_1$ and $\psi_2$, we developed the following regression model taking $\psi_1$ or $\psi_2$ as a response variable $u_n$ (parameter combination $n$):

$$
\begin{aligned}
u_{n} &\sim Normal(\mu_n, \sigma^2)\\
\mu_n &= \zeta_0 + \zeta_1 \sigma_{h,n} + \zeta_2 \sigma_{l,n} + \zeta_3 \sigma_{z,n} + \zeta_4 \phi_n + \zeta_5 \nu_n + \zeta_6 \alpha_{max, n} + \zeta_7 \theta_n + \zeta_8 p_{d,n} 
\end{aligned}
$$

where $\zeta_k$ ($k = 0-8$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-8}$). Explanatory variables were standardized to a mean of zero and a standard deviation of one, so that regression coefficients are comparable.

The sensitivity analysis revealed key simulation parameters. For the effects of $N_p$, the following simulation parameters were influential: the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\gamma$ diversity), the maximum value of interspecific competition coefficient ($\alpha_{max}$; influenced the effects on $\alpha$, $\beta$, and $\gamma$ diversity), dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal probability ($p_d$; influenced the effect on $\alpha$ diversity) (**Table S3**). For the effects of $P_b$, the following simulation parameters were influential: environmental variation at headwaters ($\sigma_h$; influenced the effect on $\gamma$ diversity), the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity) (**Table S4**).

Based on the results, we identified $\sigma_h$, $\sigma_l$, $\alpha_{max}$, $\theta$, and $p_d$ as key parameters. We changed the values of these parameters in the main analysis and examined the relationships between diversity metrics and ecosystem properties.

### Longitudinal gradient of local species richness

Longitudinal gradients of local species richness have been extensively studied in rivers, illuminating typical patterns observed in nature. The most common pattern is a downstream increase of local species richness [@mcdowall1996; @mcdowall1998; @rahel1991; @terui2016]. However, recent empirical and theoretical studies also showed 'reversed patterns,' in which local species richness decreases downstream [@bsemer2013; @harvey2018]. We predicted the longitudinal gradient of local species richness to confirm that our simulation scenarios are capable of reproducing the previously observed patterns of local species richness. We considered 32 simulation scenarios comprising four landscape and eight ecological scenarios, as described in the main text (a set of parameters is described in **Table S2**). Under each simulation scenario, we generated 10 branching networks with fixed parameters of ecosystem size ($N_p = 100$) and complexity ($P_b = 0.5$). This results in a total of 320 simulation replicates. In each simulation replicate, we allowed interspecific variation in niche optimum $\mu_i$ and width $\sigma_{niche,i}$ ($\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$, respectively; subscript $i$ represents species) and ran 1400 time steps of metacommunity dynamics. We obtained temporal means of local species richness at each habitat patch for the last 1000 time steps. The first 400 time steps were discarded as initialization and burn-in periods. We removed simulation replicates in which no species established populations over the initial 400 time steps. We evaluated the relationship between local species richness and the number of upstream habitat patches, a proxy for the longitudinal position of a habitat patch.

The simulation reproduced diverse patterns of longitudinal gradients in local species richness (**Figures S1-4**). The downstream increase of local species richness was predicted under a natural landscape scenario, in which environmental variation at headwaters $\sigma_h$ exceeds the degree of local environmental noise $\sigma_l$ (**Figure S1**). This pattern was consistent across ecological scenarios except those with long dispersal distance and high dispersal probability (**Figure S1**). Similarly, we observed a downstream increase of local species richness in scenarios with low habitat diversity ($\sigma_h = \sigma_l = 0.01$) and low dispersal probability ($p_d = 0.01$) (**Figure S3**). However, there were cases where local species richness decreased downstream or showed no longitudinal patterns. For example, when local environmental noise exceeds environmental variation at headwaters ($\sigma_l \ge \sigma_h$), local species richness showed a downstream decrease or a vague longitudinal pattern (**Figure S4**). Therefore, the simulation scenarios were capable of reproducing previously observed patterns, suggesting the appropriateness in the choice of parameter combinations.

\newpage

## Empirical data

### Fish community data

**Hokkaido, Japan.** We used data from the Hokkaido Freshwater Fish Database HFish [@fukushima2011; @fukushima2007], monitoring data at protected watersheds [@comte2021; @terui2018], and primary data collected by the authors [@miyazaki2016; @terui2016], which collectively cover the entire Hokkaido island. Most data were collected from summer to fall. We screened data through the following procedure:

1.  We listed recorded fish species and re-organized species names to make them consistent across data sources. We removed the following species at this stage: (1) identified at the family-level; (2) marine fish species (including species that occasionally use brackish/freshwater habitats).
2.  We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve unidentified species (genus level) that are rarely observed in the data set (\< 100 sites occurrence).
3.  For sites with multiple visits (i.e., temporal replicates), we used the latest-year observation at each sampling site to minimize variation in sampling efforts among sites. Surveys that occurred in the same year were aggregated into a single observation.
4.  We confined sites to those with the latest observation year of $\ge$ 1990. Although the data set contained observations from 1953, we added this restriction to align the observation period with the data set in the Midwest, US.
5.  Four genera (*Lethenteron*, *Pungitius*, *Rhinogobius*, and *Tribolodon*) were treated as species groups (i.e., spp.) as their taxonomic resolutions varied greatly among data sources due to difficulties in identifying species.

**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources [@iowadepartmentofnaturalresources2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources [@illinoisenvironmentalprotectionagency2014], Minnesota Pollution Control Agency [@minnesotapollutioncontrolagency2014], and Wisconsin Department of Natural Resources [@wisconsindepartmentofnaturalresources2018]. These data sets cover most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined by U.S. Geological Survey and U.S. Department of Agriculture Natural Resources Conservation Service [@u.s.geologicalsurveyandu.s.departmentofagriculturenaturalresourcesconservationservice2013]) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05). Fish data were collected from summer to fall with electrofishing (backpack, barge-type, or boat-mounted) and supplemental netting at some locations. We screened data through the following procedure:

1.  We used data of the Upper Mississippi (HUC 2, region 07) and Great Lakes basins (HUC 2, region 04) as most sites are included in these regions.
2.  We removed records of unidentified species, hybrid species, and commercial species apparently absent in the wild (e.g., goldfish).
3.  We used the latest observation at each sampling site to minimize variation in sampling efforts among sites.

### Asymptotic species richness

We evaluated sensitivity of asymptotic species richness (Chao 2 estimator) to sample size (i.e., the number of sampling sites in a watershed). We simulated presence-absence data of species with known values of true species richness $S_{true}$ and the number of sampling sites $N_{site}$. In this simulation, presence of species $i$ at site $x$, $J_{ix}$, was drawn from a Bernoulli distribution as $J_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$. Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT' [@hsieh2016]. We calculated % bias of estimated asymptotic species richness $S_{est}$:

$$
\%~bias = \frac{100(S_{est} - S_{true})}{S_{true}}
$$

Positive values of % bias indicate an overestimation of species richness, while negative values indicate an underestimation.

We used the following values for parameters: $S_{true} = 10, 40, 70, 100$ and $N_{site} = 5, 10, 15, 20, 100$. We produced 100 replicates of simulated data sets for each parameter combination, resulting in a total of 2000 simulation replicates. In each simulation replicate, the probabilities of detection and true presence were drawn randomly from uniform distributions as $p_i \sim Unif(0.3, 0.8)$ and $\kappa_{ix} \sim Unif(0, 1)$.

The number of sampling sites influenced the estimation accuracy of asymptotic species richness. The % bias decreased sharply as the number of sampling sites increased (**Figure S20**). In particular, the estimation bias with a small sample size ($N_{site} = 5$) was substantial when the true species richness $S_{true}$ was low; some estimates showed \> 150% bias (**Figure S20**). Given the simulation results, estimates of asymptotic species richness at watersheds with \< 10 sampling sites may involve substantial statistical uncertainty.

\newpage

## Tables

### Table S1 Simulation parameter (sensitivity analysis)

**Table S1** Parameter values used in the sensitivity analysis of the metacommunity simulation. See the main text for model details.

```{r chunk_table1}

  source(here::here('theory/table_sim_parameter_sensitivity.R'))
  table_output

```

\newpage

### Table S2 Simulation parameter (main analysis)

**Table S2** Values and interpretation of simulation parameters used in the main simulation. See the main text for model details.

```{r chunk_table2}

  source(here::here('theory/table_sim_parameter_main.R'))
  table_output

```

\newpage

### Table S3 Sensitivity analysis for ecosystem size effects

**Table S3** Sensitivity analysis of the metacommunity simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are the effects of the number of habitat patches ($N_{p}$) on $\alpha$, $\beta$, and $\gamma$ diversity. Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis. See Tables S1 and S2 for interpretation of the simulation parameters.

```{r chunk_table3, results='asis'}

  cat(star_area, sep='\n')

```

\newpage

### Table S4 Sensitivity analysis for ecosystem complexity effects

**Table S4** Sensitivity analysis of the metacommunity simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are the effects of branching probability ($P_{b}$) on $\alpha$, $\beta$, and $\gamma$ diversity. Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis. See Tables S1 and S2 for interpretation of the simulation parameters.

```{r chunk_table4, results='asis'}

  cat(star_bp, sep='\n')

```

\newpage

### Table S5 List of fish species in Hokkaido, Japan

**Table S5** List of fish species in Hokkaido, Japan, included in our statistical analysis. `r n_distinct(dat_hkd$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy out of `r n_distinct(dat_hkd$SiteID)` sites.

```{r chunk_table5}

  source(here::here('empirical/table_splist_hkd.R'))
  table_output

```

\newpage

### Table S6 List of fish species in Midwest, US

**Table S6** List of fish species in the Midwest, US, included in our statistical analysis. `r n_distinct(dat_mw$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy out of `r n_distinct(dat_mw$SiteID)` sites.

```{r chunk_table6}

  source(here::here('empirical/table_splist_mw.R'))
  table_output

```

\newpage

## Figures

```{r chunk_fig_set1}

source(here::here("theory/figure_alpha_pattern.R"))

figure_cap <- conditional_text <- NULL

for(i in seq_len(nrow(param))){
  if(param$sigma_h[i] > param$sigma_l[i]){
    conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) exceeds local environmental noise ($\\sigma_{l}$)."
  }else{
    if(param$sigma_h[i] == param$sigma_l[i]){
      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is equal to local environmental noise ($\\sigma_{l}$)."
    }else{
      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is less than local environmental noise ($\\sigma_{l}$)."
    }
  }

  figure_cap[i] <- paste0("Theoretical predictions for longitudinal gradients of local species richness in branching networks. The longitudinal position of each habitat patch (x-axis) was expressed as the number of upstream habitat patches. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns and lines represent different dispersal scenarios (dispersal distance and probability). Left and right columns show long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$) scenarios repectively. Red and blue lines show low ($p_d = 0.01$) and high dispersal probabilities ($p_d = 0.10$). Other parameters are as follows: environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$; ecosystem size $N_{p} = 100$; ecosystem complexity $P_{b} = 0.5$.")
}

figure_alpha_pattern <- NULL
for(i in seq_len(nrow(param))){
  j <- i
  knit_chunk <- paste0("### Figure S", j, " Longitudinal gradient of local species richness ($\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
                       "\n```{r fig", j,", fig.width = 8, fig.height = 6}\n\n h[[",i,"]] \n\n```\n",
                       "\n **Figure S", j, "** ", figure_cap[i], "\n\\pagebreak\n")
  figure_alpha_pattern <- c(figure_alpha_pattern, knit_chunk)
}

```

`r paste(knit(text = figure_alpha_pattern), collapse = '\n')`

```{r chunk_fig_set2}

source(here::here("theory/figure_n_patch_si.R"))

figure_cap <- conditional_text <- NULL

for(i in seq_len(nrow(param))){
  if(param$sigma_h[i] > param$sigma_l[i]){
    conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) exceeds local environmental noise ($\\sigma_{l}$)."
  }else{
    if(param$sigma_h[i] == param$sigma_l[i]){
      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is equal to local environmental noise ($\\sigma_{l}$)."
    }else{
      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is less than local environmental noise ($\\sigma_{l}$)."
    }
  }

  figure_cap[i] <- paste0("Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$). Other parameters are as follows: dispersal probability $p_{d} = `r param$p_d[",i,"]`$; environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$.")
}

figure_size <- NULL
for(i in seq_len(nrow(param))){
  j <- i + 4
  knit_chunk <- paste0("### Figure S", j, " Influence of ecosystem size ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
                       "\n```{r fig", j,", fig.width = 8, fig.height = 6}\n\n f[[",i,"]] \n\n```\n",
                       "\n **Figure S", j, "** ", figure_cap[i], "\n\\pagebreak\n")
  figure_size <- c(figure_size, knit_chunk)
}

```

`r paste(knit(text = figure_size), collapse = '\n')`

```{r chunk_fig_set3}

source(here::here("theory/figure_p_branch_si.R"))

figure_cap <- conditional_text <- NULL

for(i in seq_len(nrow(param))){
  if(param$sigma_h[i] > param$sigma_l[i]){
    conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) exceeds local environmental noise ($\\sigma_{l}$)."
  }else{
    if(param$sigma_h[i] == param$sigma_l[i]){
      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is equal to local environmental noise ($\\sigma_{l}$)."
    }else{
      conditional_text[i] <- "In this simulation, environmental variation at headwaters ($\\sigma_{h}$) is less than local environmental noise ($\\sigma_{l}$)."
    }
  }

  figure_cap[i] <- paste0("Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$). Other parameters are as follows: dispersal probability $p_{d} = `r param$p_d[",i,"]`$; environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$.")
}

figure_complex <- NULL
for(i in seq_len(nrow(param))){
  j <- i + 11
  knit_chunk <- paste0("### Figure S", j, " Influence of ecosystem complexity ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
                       "\n```{r fig", j,", fig.width = 8, fig.height = 6}\n\n g[[",i,"]] \n\n```\n",
                       "\n **Figure S", j, "** ", figure_cap[i], "\n\\pagebreak\n")
  figure_complex <- c(figure_complex, knit_chunk)
}

```

`r paste(knit(text = figure_complex), collapse = '\n')`

### Figure S19 Correlation structure of explanatory variables

```{r fig_s19, fig.height = 10, fig.width = 10}

source(here::here('empirical/figure_correlation.R'))

```

**Figure S19** Correlation structure of potential explanatory variables for riverine diversity metrics. Numeric values in each cell are the Pearson's correlation coefficients. Positive and negative correlations were colored in blue and red, respectively, and darker colors indicate stronger correlations. Environmental variables (temperature, precipitation, elevation, logit fraction of forest, logit fraction of urban, logit fraction of agriculture, and dam density) were expressed as deviations from the regional averages to remove any regional effects.

\newpage

### Figure S20 Sensitivity analysis of asymptotic species richness

```{r fig_s20, fig.height = 6, fig.width = 6}

source(here::here('empirical/figure_iNEXT_sim.R'))

```

**Figure S20** Sensitivity analysis of asymptotic species richness in relation to true species richness $S_{true}$ (panels) and the number of sampling sites $N_{site}$ (x-axis). Positive values of % bias indicate an overestimation of species richness, while negative values indicate an underestimation. Different panels show results with different true species richness. The center lines are median values, the box boundaries 25 and 75 percentiles, and the whiskers 5 and 95 percentiles. Dots represent individual simulation replicates.

\newpage

# References

### 2021-03-02 manuscript_science.Rmd
edits: manuscript for science

@@
 
-## read gis files
+  # define digits function
+  op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x)
+
+  # read gis files
   filename <- list.files(path = here::here('empirical/data_gis'), full.names = T)
@@
 
-## read theory file
+  # read theory file
   dat_sim <- read_csv(here::here('theory/result/result_sim2020-11-10.csv'))
@@
 
-# for bayes factor
-source(here::here('empirical/analysis_lm_bf.R'))
+  # for Bayes factor
+  source(here::here('empirical/analysis_rlm_bf.R'))
 
@@
 
-**One sentence summary:** Using theory and empirical analysis of extensive community data, this research provides the first robust evidence that ecosystem size and complexity jointly regulate biodiversity in rivers at large spatial scales.
+**One sentence summary:** Using theory and empirical analysis of extensive community data, this research provides the first robust evidence that ecosystem size and complexity jointly regulate biodiversity in river networks.
 
@@
 
-**Abstract:** Larger ecosystems generally support more species; this ubiquitous ecological pattern is the foundation of many conservation strategies.
-However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such ecosystem complexity in scaling biodiversity is largely unknown.
-Here, we use theory and empirical analysis of extensive fish community data from two geographic regions (Japan and US) to show that ecosystem size and complexity dictate riverine biodiversity.
+**Abstract:** Larger ecosystems support more species; this ubiquitous ecological pattern is the foundation of current conservation schemes.
+However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such complexity in scaling biodiversity is largely unknown.
+Here, we use theory and extensive fish community data from two distinct geographic regions (Japan and United States) to show that ecosystem size and complexity dictate riverine biodiversity.
 We found that larger and more branched 'complex' river networks harbored greater species richness due to increased space and environmental heterogeneity.
-The complexity effect was comparative to the size effect, and this pattern emerged regardless of ecological contexts.
-Recognizing the dual control of biodiversity should broaden viable options for successful conservation.
+The complexity effect was comparable to the size effect, and this pattern emerged regardless of ecological contexts.
+The dual control of biodiversity may be a pervasive feature that has far-reaching implications for biodiversity conservation.
 
@@
 Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms [@grant2007].
-Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure, and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems [@rinaldo2018].
+Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure [@fagan2002; @grant2010; @brown2010; @henriquessilvarenato], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems [@rinaldo2018].
 For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches [@carrara2012].
 However, most empirical research has explored the consequences of branching complexity for local community structure [@ers2019; @carrara2012] or has relied solely on theoretical arguments with limited replications of branching architecture [@holt2018].
-At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity at the metacommunity level.
+At present, we lack a synthetic framework integrating the influences of ecosystem size and complexity on biodiversity at the metacommunity level.
 Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services [@dudgeon2006].
@@
 Here, we hypothesize that ecosystem size and complexity dictate biodiversity patterns in rivers - a prime example of complex branching ecosystems.
-Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@peterson2013; @moore2015; @terui2018].
+Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brown2010; @peterson2013; @moore2015; @terui2018].
 The recurrent merging of diverse tributaries ultimately forms a fluvial network with fractal branching patterns [@rodríguez-iturbe2001].
@@
 
-# Synthesizing ecosystem size and complexity influences
+## Synthesizing ecosystem size and complexity influences
 
-First, we theoretically analyzed the influences of ecosystem size and branching complexity on $\gamma$ diversity.
+First, we developed a theoretical framework synthesizing the influences of ecosystem size and complexity on biodiversity patterns in branching ecosystems.
 We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit [@terui2018; @yeakel2014] (**Figure 1A and B**).
@@
 When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation (**Figure 1A**).
-This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary [@moore2015; @peterson2013].
+This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary [@brown2010; @peterson2013; @moore2015].
 In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to limited influences of branching on habitat heterogeneity (**Figure 1B**).
@@
 We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation existed (i.e., species travel short distances).
-This pattern reflected significant spatial variation in species composition over the branching network and was likely driven by the local association of species' niche and abiotic environments (i.e., species sorting) [@thompson2020].
+This pattern reflected significant spatial variation in species composition over the branching network and was likely driven by the local association of species' niche and abiotic environments (i.e., species sorting) [@leibold2004; @thompson2020].
 In contrast, when the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
-The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects) [@thompson2020].
+The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects) [@leibold2004; @economo2008; @thompson2020].
 These patterns were consistent across different levels of dispersal probabilities (**Figures S5 and S12**).
@@
 
-# Empirical evidence from distinct geographic regions
+## Empirical evidence from distinct geographic regions
 
@@
 We combined this data set with geospatial information, including watershed characteristics (watershed area and branching probability), climates (annual mean temperature and annual cumulative precipitation), and land use patterns (the fraction of agricultural land use and dam density).
-Using this data set, we assessed whether observed effects of the macro-scale factors are consistent across the two geographic regions by developing global and region-specific models.
+Using this data set, we assessed whether observed effects of the macro-scale factors are consistent across the two geographic regions by developing global and region-specific robust regression models.
 In the global model, we assumed that effects of ecosystem size (watershed area) and complexity (branching probability) are constant across the two regions (i.e., fixed slopes).
@@
 
-Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`): this result suggests the consistent effects of ecosystem size and complexity on $\gamma$ diversity across the two geographic regions.
-Furthermore, the observed patterns were closely aligned with our theoretical predictions (**Table 1 and Figure 4**).
-The estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) across watersheds.
-These effects remained significant even after controlling for the potential influences of other environmental factors (precipitation, temperature, agricultural land use, and dam density) (**Table 1**).
-Our statistical analysis provides the first empirical evidence that ecosystem complexity regulates riverine biodiversity at the metacommunity level while conferring additional support for the ecosystem size effect on fish communities [@iwasaki2012].
+Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`).
+In line with theory, the estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions.
+In particular, the effect of ecosystem complexity was striking in its magnitude.
+XXX.
+These effects remained significant even after controlling for the potential influences of other environmental factors (**Table 1**).
 
@@
 Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters at an annual scale [@radinger2014].
-The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
+The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation, which results in the dominance of species sorting process [@thompson2020], plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
 
@@
 It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, persist in human-dominated landscapes to maintain the diversity of in-stream processes among tributaries.
-The lack of land use effects (the fraction of agricultural land use) corroborates our interpretation (**Table 1**).
+The lack of land use effects (the fraction of agricultural land use) further corroborates our interpretation (**Table 1**).
 Although our analysis is correlative, the finding is encouraging because the branching complexity of river networks may serve as a natural defense system to human-induced environmental changes.
 
-There may be confounding factors that are not incorporated into our statistical models.
-However, we are confident in our statistical inference because the observed patterns were fairly consistent with our theoretical predictions that are free from any confounding effects.
-Further, our fitted models accounted for possible covariates (climates and land use patterns; **Table 1**) and showed moderate to high R^2^ values ($\alpha$ diversity: `r round(summary(fit$alpha$model)$r.squared, 2)`; $\beta$ diversity, `r round(summary(fit$beta$model)$r.squared, 2)`; $\gamma$ diversity `r round(summary(fit$gamma$model)$r.squared, 2)`).
-Therefore, it is very unlikely that spurious correlations are responsible for our results.
+Overall, our results provide the first empirical evidence that ecosystem size and complexity play comparable roles in controlling biodiversity in rivers.
+Further, these patterns were fairly consistent with our theoretical predictions that are free from any confounding factors, suggesting that spurious correlations are very unlikely.
 
-# Implications for biodiversity conservation
+## Implications for biodiversity conservation
 
@@
 Our fundamental findings of the dual control of biodiversity should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
-The dual dimensional approach - size and complexity - broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
+Further, the proposed framework may be extended to other aspects of biodiversity; for example, a logical next step is to explore how these ecosystem properties regulate functional diversity [@petchey2002; @su2021] and community assembly processes [@chase2010].
+Recognizing the dual control of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
 The generalization of our findings in spatially complex ecosystems represents a frontier for future research.
 
-# Acknowledgements
+# Acknowledgments
 
@@
 
-Third parties provided data for empirical data analysis; references are provided in the main text and Supplementary Text where appropriate.
+Third parties provided data for empirical data analysis; references are provided where appropriate.
 R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at <https://github.com/aterui/mcbrnet>).

### 2021-03-02 empirical/function_avpc.R
Create function_avpc.R

@@ -1,0 +1,73 @@
+
+# setup -------------------------------------------------------------------
+
+  pacman::p_load(tidyverse, foreach)
+  source(here::here('empirical/analysis_lm_bf.R'))
+
+
+# simulation --------------------------------------------------------------
+  
+  m <- fit$gamma$model
+  u <- 'log(p_branch, 10)'
+  v <- c('log(area, 10)', 'scale(resid_temp)', 'scale(resid_ppt)', 'region')
+  
+
+# extract model data frame ------------------------------------------------
+  
+  if(class(m) %in% c('lm', 'rlm')) {
+    m <- m$model
+  }
+  
+  if(class(m) %in% 'lmerMod') {
+   m <- m@frame  
+  }
+  
+  # extract character variables and convert them to numeric values
+  m_chr <- m %>% 
+    summarise(across(.cols = is.character,
+                     .fns = ~ as.numeric(as.factor(.x)) - 1)) %>% 
+    mutate(id = as.numeric(rownames(m)))
+  
+  # extract numeric variables
+  m_dbl <- m %>% 
+    summarise(across(.cols = is.numeric)) %>% 
+    mutate(id = as.numeric(rownames(m)))
+  
+  # combine
+  mod <- m_chr %>% 
+    left_join(m_dbl, by = 'id')
+
+
+# get pairs for u and v ---------------------------------------------------
+  
+  if(!is.null(v)) {
+    X1 <- X2 <- mod %>% select(v)
+  } else {
+    X1 <- X2 <- mod %>% select(-id, -v)
+  }
+  
+  X <- X1 %>% mutate(id = as.numeric(rownames(.)))
+  
+  # mahalanobis distance for a set of v variables
+  m_cov <- cov(X1)
+  m_dist <- apply(X1, 1, function(row_i) mahalanobis(X2, row_i, m_cov))
+  df_v <-  tibble(sq_distance = c(m_dist),
+                  row_id = rep(seq_len(nrow(m_dist)), times = ncol(m_dist)),
+                  col_id = rep(seq_len(ncol(m_dist)), each = nrow(m_dist))) %>% 
+    mutate(weight = 1/(1 + sq_distance))
+  
+  # combine with input u
+  m_u <- mod %>%
+    select(u) %>% 
+    rename(u_input = u) %>% 
+    mutate(id = as.numeric(rownames(.)))
+  
[…]

### 2021-03-02 empirical/figure_diversity.R
edits: figure diversity, change mean values for covariates

@@ -34,7 +34,7 @@
 # read data ---------------------------------------------------------------
   
   ## model estimate
-  source("analysis_lm_bf.R")
+  source("analysis_rlm_bf.R")
   
   ## redefine data.frame
   dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
@@ -42,21 +42,15 @@
   
   dat <- bind_rows(dat_hkd, dat_mw) %>% 
     rename(gamma = Estimator, alpha = mu_alpha) %>% 
-    mutate(beta = gamma/alpha,
-           logit_agri = log(frac_agri) - log(1 - frac_agri),
-           dam_density = n_dam/area) %>% 
-    mutate(resid_agri = resid(lm(logit_agri ~ region, data = .)),
-           resid_temp = resid(lm(mean_temp ~ region, data = .)),
-           resid_ppt = resid(lm(mean_ppt ~ region, data = .)),
-           resid_dam = resid(lm(dam_density ~ region, data = .))) %>% 
+    mutate(beta = gamma/alpha) %>% 
     pivot_longer(cols = c(alpha, beta, gamma),
                  names_to = "metric")
   
   dat_base <- data.frame(region = factor(rep(c("hokkaido", "midwest"), each = 100)),
-                         resid_temp = mean(dat$resid_temp),
-                         resid_ppt = mean(dat$resid_ppt),
-                         resid_agri = mean(dat$resid_agri),
-                         resid_dam = mean(dat$resid_dam))
+                         resid_temp = 0,
+                         resid_ppt = 0,
+                         resid_agri = 0,
+                         resid_dam = 0)
 
 # data frame for prediction -----------------------------------------------
   

### 2021-03-02 empirical/analysis_rlm_bf.R
Create analysis_rlm_bf.R

@@ -1,0 +1,54 @@
+
+# setup -------------------------------------------------------------------
+
+  pacman::p_load(tidyverse, MASS)
+
+# read data ---------------------------------------------------------------
+  
+  dat_hkd <- read_csv(here::here("empirical/data_out/data_hkd.csv")) %>% mutate(region = "hokkaido")
+  dat_mw <- read_csv(here::here("empirical/data_out/data_mw.csv")) %>% mutate(region = "midwest")
+  
+  dat <- bind_rows(dat_hkd, dat_mw) %>% 
+    rename(gamma = Estimator,
+           alpha = mu_alpha) %>% 
+    mutate(beta = gamma/alpha,
+           logit_agri = log(frac_agri) - log(1 - frac_agri),
+           dam_density = n_dam/area) %>% 
+    mutate(resid_agri = resid(lm(logit_agri ~ region, data = .)),
+           resid_temp = resid(lm(mean_temp ~ region, data = .)),
+           resid_ppt = resid(lm(mean_ppt ~ region, data = .)),
+           resid_dam = resid(lm(dam_density ~ region, data = .)))
+  
+
+# model selection ---------------------------------------------------------
+
+  m_compare <- function(response, data) {
+    
+    mod1 <<- rlm(log(response, 10) ~ log(area, 10)*region + log(p_branch, 10)*region + region +
+                                     scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
+                 psi = psi.huber,
+                 method = 'M',
+                 data = data)
+    
+    mod0 <<- rlm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
+                                     scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
+                 method = 'M',
+                 psi = psi.huber,
+                 data = data)
+    
+    # bf01: bayes factor in favor of mod0 over mod1
+    bf01 <- exp(0.5*(BIC(mod1) - BIC(mod0)))
+    
+    if(bf01 >= 1) m <- mod0 else m <- mod1
+    
+    return(list(model = m, bayes_factor = bf01))
+    
+  }
+  
+  fit <- lapply(dat[,c("alpha", "beta", "gamma")], FUN = m_compare, data = dat)
+  
+
+# detach MASS (to avoid conflicts with tidyverse) -------------------------
+
+  detach('package:MASS', unload = TRUE)
+  

### 2021-03-02 table.Rmd
edits: table 1, delete 'the'

@@
 
-source(here::here("empirical/analysis_lm_bf.R"))
+source(here::here("empirical/analysis_rlm_bf.R"))
 
@@
                      ci = TRUE,
-                     title = "Estimated parameters of linear regression models explaining fish species richness in the Hokkaido (Japan) and the Midwest (US) regions.
+                     title = "Estimated parameters of linear regression models explaining fish species richness in Hokkaido (Japan) and the Midwest (US) regions.
 The 95\\% confidence intervals are shown in parenthesis.

### 2021-03-07 manuscript_science.Rmd
edits: manuscript, introduction

@@
 
-**Abstract:** Larger ecosystems support more species; this ubiquitous ecological pattern is the foundation of current conservation schemes.
+**Abstract:** Larger ecosystems support more species; this ubiquitous phenomenon is the foundation of current conservation schemes.
 However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such complexity in scaling biodiversity is largely unknown.
@@
 We found that larger and more branched 'complex' river networks harbored greater species richness due to increased space and environmental heterogeneity.
-The complexity effect was comparable to the size effect, and this pattern emerged regardless of ecological contexts.
+The complexity effect was comparable to the size effect, and this pattern has emerged regardless of ecological contexts.
 The dual control of biodiversity may be a pervasive feature that has far-reaching implications for biodiversity conservation.
@@
 However, most empirical research has explored the consequences of branching complexity for local community structure [@ers2019; @carrara2012] or has relied solely on theoretical arguments with limited replications of branching architecture [@holt2018].
-At present, we lack a synthetic framework integrating the influences of ecosystem size and complexity on biodiversity at the metacommunity level.
+The lack of a metacommunity-level framework integrating the influences of ecosystem size and complexity hinders an objective assessment of their roles in controlling biodiversity patterns.
 Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services [@dudgeon2006].
 
-Here, we hypothesize that ecosystem size and complexity dictate biodiversity patterns in rivers - a prime example of complex branching ecosystems.
+Here, we show that ecosystem size and complexity play comparable roles in controlling biodiversity patterns in rivers - a prime example of complex branching ecosystems.
 Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brown2010; @peterson2013; @moore2015; @terui2018].

### 2021-03-07 supplementary_information_science.Rmd
edits: manuscript, introduction

@@
 
-  # for bayes factor
-  source(here::here('empirical/analysis_lm_bf.R'))
-
   # Hokkaido data
+  dat_hkd <- read_csv(here::here("empirical/data_out/data_hkd.csv")) %>% mutate(region = "hokkaido")
   dat_hkd_site <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))
@@
   # Midwest data
+  dat_mw <- read_csv(here::here("empirical/data_out/data_mw.csv")) %>% mutate(region = "midwest")
   dat_mw_site <- read_csv(here::here('empirical/data_out/data_mw_site.csv')) %>% 
@@
 
-  # sensitivity tables
+  # tables
+
+  ## sensitivity
   source(here::here('theory/table_sensitivity_analysis.R'))
@@
 
-## Empirical data analysis
+## Empirical data
 
@@
 We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT' [@hsieh2016].
-We assessed the completeness of the observed species richness based on sample coverage, which is the proportion abundances of observed species to the whole community [@chao2014].
+We assessed the completeness of the observed species richness based on sample coverage, which is the total proportional abundances of observed species to the whole metacommunity [@chao2014].
 We excluded watersheds whose sample coverage was below 0.9 because the estimates of asymptotic species richness may contain non-negligible statistical uncertainty.
@@
 
-We developed linear regression models to examine the effects of macro-scale drivers on diversity metrics.
+We developed robust regression models with an M-estimation method to examine the effects of macro-scale drivers on diversity metrics.
+We employed robust regression models given the uncertainty of diversity estimates (see **Fish community data**).
 Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$.
@@
 
-### Fish community data
+### Data selection criteria
 

### 2021-03-07 empirical/analysis_rlm_bf.R

@@ -24,14 +24,14 @@
 
   m_compare <- function(response, data) {
     
-    mod1 <<- MASS::rlm(log(response, 10) ~ log(area, 10)*region + log(p_branch, 10)*region + region +
-                                     scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
+    mod1 <- MASS::rlm(log(response, 10) ~ log(area, 10)*region + log(p_branch, 10)*region + region +
+                                          scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
                        psi = MASS::psi.huber,
                        method = 'M',
                        data = data)
     
-    mod0 <<- MASS::rlm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
-                                     scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
+    mod0 <- MASS::rlm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
+                                          scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
                        method = 'M',
                        psi = MASS::psi.huber,
                        data = data)

### 2021-03-07 manuscript_science.Rmd
edits: manuscript, average predictive comparison

@@
 
+  # for average predictive comparisons
+  source(here::here('empirical/analysis_apcomp.R'))
+
   # Hokkaido data
@@
 
-**Abstract:** Larger ecosystems support more species; this ubiquitous phenomenon is the foundation of current conservation schemes.
+**Abstract:** Larger ecosystems support more species; this ubiquitous pattern is the foundation of current conservation schemes.
 However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such complexity in scaling biodiversity is largely unknown.
@@
 Therefore, our network-generation procedure resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
-We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity framework [@thompson2020].
+We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity model [@thompson2020].
 In this model, 50 species with different abiotic niches (optimum and width) disperse along a network and compete for resources with varied strengths in temporally dynamic environments (see **Materials and Methods** for model details).
@@
 Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity within a network.
-We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel $\theta$), dispersal probability, and the maximum value of interspecific competition strength $\alpha_{max}$ (see **Materials and Methods**).
+We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel $\theta$), dispersal probability $p_{d}$, and the maximum value of interspecific competition strength $\alpha_{max}$ (see **Materials and Methods**).
 These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supplementary Text**).
@@
 Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`).
-In line with theory, the estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions.
+In line with our theoretical predictions, the estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions.
 In particular, the effect of ecosystem complexity was striking in its magnitude.
-XXX.
-These effects remained significant even after controlling for the potential influences of other environmental factors (**Table 1**).
+An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelman2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r op(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in watershed area (see **Table S7** for estimated average predictive comparisons).
+These effects remained significant even after controlling for the potential influences of climates and land use patterns (**Table 1**).
 

### 2021-03-08 manuscript_science.Rmd
Update manuscript_science.Rmd

@@
 In particular, the effect of ecosystem complexity was striking in its magnitude.
-An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelman2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r op(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in watershed area (see **Table S7** for estimated average predictive comparisons).
+An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelman2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for estimated average predictive comparisons).
 These effects remained significant even after controlling for the potential influences of climates and land use patterns (**Table 1**).

### 2021-03-08 supplementary_information_science.Rmd
edits: SI, average predictive comparisons

@@
 
-where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$. We performed statistical analysis using R version 4.0.2 [@rcoreteam2020].
+where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$.
+
+For the supported model of $\gamma$ diversity, we estimated average predictive comparisons of watershed area and branching probability to compare their effect sizes.
+The average predictive comparison is an expected change of the response variable per a unit difference of the explanatory variable of interest [@gelman2007].
+Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method is applicable to models with variable transformations and allows direct comparisons of the effect sizes of watershed area and branching probability (see **Supplementary Text** for further details).
+We performed statistical analysis using R version 4.0.2 [@rcoreteam2020].
 
@@
 
+### Average predictive comparison
+
+For regression models, standardized regression coefficients (or its variant) are perhaps the most common summary when comparing effect sizes of explanatory variables.
+These values are useful if they are directly interpretable.
+For example, in linear regression models without variable transformations, regression coefficients have direct interpretations as they represent additive effects.
+However, there are many cases where regression coefficients are difficult to interpret.
+In our case, we regressed the log-transformed species richness on explanatory variables, so regression coefficients do not have direct interpretations at the original scale of the response variable $y$ (i.e., species richness).
+
+The average predictive comparison provides an intuitive yet rigorous way to quantify effect sizes for each of explanatory variables in regression models with interactions and/or variable transformations [@gelman2007].
+The basic predictive comparison $\delta_u$ is an expected change in $y$ on the original scale per a unit difference of the explanatory variable of interest:
+
+$$
+\delta_u(u^{(1)} \to u^{(2)}, v, \Theta) = \frac{E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta)}{u^{(2)} - u^{(1)}}
+$$
+
+where $E(\cdot)$ is a known function (e.g., exponential), $u$ the input of interest (a value for the explanatory variable of interest), $v$ all the other inputs (a vector in general), $\Theta$ a set of parameters in a regression model.
+In general, $\delta_u$ depends on $u^{(1)}$ and $u^{(2)}$ (the beginning and end points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$.
+Therefore, Gelman and Pardoe [@gelman2007] defined the *average predictive comparison* $\Delta_u$, the mean value of $\delta_u$ over specified distributions of the inputs and model parameters:
+
+$$
+\Delta_u = \frac{\int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta (E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta))~p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta)}{ \int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta~(u^{(2)} - u^{(1)})~ p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta) }
+$$
+
+However, directly using the above equation is impractical because estimating $p(u^{(1)}|v)$ and $p(u^{(2)}|v)$ from finite data points is challenging (especially when $v$ is continuous).
+Instead, we estimated $\Delta_u$ using the following equation proposed by Gelman and Pardoe [@gelman2007]:
+
+$$
+\hat\Delta_u = \frac{\sum_{i=1}^n \sum_{j=1}^n \sum_{s=1}^S w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}{\sum_{i=1}^n \sum_{j=1}^n \sum_{s=1}^S w_{ij}(u_j - u_i)sign(u_j - u_i)}
+$$
+
+The summations over $n$ data ($i$ and $j$ are a given data point) and $S$ parameter replicates ($s$ is a given simulation replicate) are a realization of averaging over the distributions of $(u^{(1)},v)$ , $u^{(2)}$, and $\Theta$.
+The factor $w_{ij}$ is a weight that serves to approximate $p(u^{(1)}|v)$ and $p(u^{(2)}|v)$.
+In theory, $v$ must be held constant while the input of interest changes from $u^{(1)}$ to $u^{(2)}$.
+However, there are, if any, few transitions from $u^{(1)}$ to $u^{(2)}$ with a common $v$.
+We approximate such exact transitions by assigning each pair of data points with a weight:
+
+$$
+w_{ij} = w(v_i, v_j)
+$$
+
+which should represent how likely it is for $u$ to transition from $u_i$ to $u_j$ with $v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$).
+We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelman2007]:
+
+$$
+w(v_i, v_j) = \frac{1}{1 + (v_i - v_j)^T\sum_v^{-1}(v_i-v_j)}
+$$
+
+where $\sum_v$ is the variance-covariance matrix of $v$.
+
+We estimated $\hat \Delta_u$ for watershed area and branching probability using the estimated coefficients $\hat \xi_k$ of the regression model explaining $\gamma$ diversity.
+A thousand of vectors of simulated parameters $\Theta_s$ were drawn from normal distributions with means of $\hat \xi_k$ and standard deviations of $\sigma_{\xi, k}$ (the estimated standard errors of parameter $\xi_k$).
+The estimated average predictive comparisons are $\hat \Delta_{u} = \frac{1}{S} \sum_{s=1}^S \hat \Delta_{u,s}$ where
+
+$$
+\hat \Delta_{u,s} = \frac{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(u_j - u_i)sign(u_j - u_i)}
+$$
+
+Then
+
+$$
+S.E.(\hat \Delta_{u,s}) = \sqrt{\frac{1}{S-1} \sum_{s-1}^S (\hat \Delta_{u,s} - \hat \Delta_{u})^2}
+$$
+
+The estimated average predictive comparisons were summarized in **Table S7**.
+
 \newpage
@@
   source(here::here('empirical/table_splist_mw.R'))
+  table_output
+
+```
+
+\newpage
+
+### Table S7 Average predictive comparisons
+
+Estimated average predictive comparisons.
+Regression coefficients were derived from the regression model explaining $\gamma$ diversity (see **Table 1** in the maintext for the estimated regression parameters).
+The average predictive comparisons (an expected increase in $\gamma$ diversity per a unit difference of the explanatory variable of interest) were estimated based on units of 1000 km^2^ for watershed area and 0.1 for branching probability.
+
+```{r chunk_table7}
+
+  source(here::here('empirical/table_apcomp.R'))
   table_output

### 2021-03-08 supplementary_information_science.Rmd
Update supplementary_information_science.Rmd

@@
 We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehner2011].
-We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenning2018], 'sf' [@pebesma2018], 'raster' [@hijmans2020], 'rgdal' [@rogerbivand2020], 'stars' [@edzerpebesma2020], and 'exactextractr' [@danielbaston2020].
+We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenning2018], 'sf' [@pebesma2018] 'raster' [@hijmans2020] 'stars' [@pebesma2020], and 'exactextractr' [@baston2020].
 

### 2021-03-08 manuscript_science.Rmd
edits: manuscript intro

@@
 Ecologists have long sought to understand the general drivers of biodiversity.
-One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR) [@lomolino2000].
-In 1921, Arrhenius [@arrhenius1921] formulated the SAR as a power-law $S = cA^z$, an equation currently known as the Arrhenius species-area relationship ($S$ is the number of species observed in a given geographic area $A$, $c$ the constant, and $z$ the scaling exponent).
-Since then, the spatial scaling of species richness has been observed in many taxonomic groups [@triantis2012].
+One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR) [@lomolinoEcologyMostGeneral2000].
+In 1921, Arrhenius @arrheniusSpeciesArea1921 formulated the SAR as a power-law $S = cA^z$, an equation currently known as the Arrhenius species-area relationship ($S$ is the number of species observed in a given geographic area $A$, $c$ the constant, and $z$ the scaling exponent).
+Since then, the spatial scaling of species richness has been observed in many taxonomic groups [@triantisIslandSpeciesareaRelationship2012].
 The SAR is ubiquitous because multiple mechanisms produce an apparently similar pattern.
-Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity [@kallimanis2008], larger metacommunity size [@hubbell2001], and/or enhanced colonization dynamics [@losos2009].
-Importantly, the SAR provides the foundation for global conservation efforts [@myers2000; @desmet2004; @neigel2003].
-For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas [@desmet2004; @neigel2003], which currently encompass more than 30 million km^2^ globally [@deguignet2014].
+Larger ecosystems typically support more diverse metacommunities due to increased habitat diversity [@kallimanisHowDoesHabitat2008], larger metacommunity size [@hubbellUnifiedNeutralTheory2001], and/or enhanced colonization dynamics [@lososTheoryIslandBiogeography2009].
+Importantly, the SAR provides the foundation for global conservation efforts [@neigelSpeciesareaRelationshipsMarine2003; @desmetUsingSpeciesareaRelationship2004; @myersBiodiversityHotspotsConservation2000].
+For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas [@neigelSpeciesareaRelationshipsMarine2003; @desmetUsingSpeciesareaRelationship2004], which currently encompass more than 30 million km^2^ globally [@deguignet2014UnitedNations2014].
 
-Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity [@turner2015; @rodríguez-iturbe2001].
-Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few [@rodríguez-iturbe2001].
-Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike [@rodríguez-iturbe2001].
-Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms [@grant2007].
-Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure [@fagan2002; @grant2010; @brown2010; @henriquessilvarenato], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems [@rinaldo2018].
-For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches [@carrara2012].
-However, most empirical research has explored the consequences of branching complexity for local community structure [@ers2019; @carrara2012] or has relied solely on theoretical arguments with limited replications of branching architecture [@holt2018].
-The lack of a metacommunity-level framework integrating the influences of ecosystem size and complexity hinders an objective assessment of their roles in controlling biodiversity patterns.
-Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services [@dudgeon2006].
+Many ecosystems, however, possess a complex spatial structure that cannot be represented by area - a dimension referred to as scale-invariant complexity [@turnerLandscapeEcologyTheory2015; @rodriguez-iturbeFractalRiverBasins2001].
+Such complexity is evident in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few [@rodriguez-iturbeFractalRiverBasins2001].
+Geomorphic or biological processes generate a pronounced self-similarity in complex branching patterns such that the part and the whole look alike [@rodriguez-iturbeFractalRiverBasins2001].
+Even though the branching structure is independent of spatial scale, it forms a physical template that dictates habitat diversity and dispersal corridors for living organisms [@grantLivingBranchesPopulation2007].
+Limited, but accumulating evidence suggests that classical metapopulation and metacommunity theories cannot predict ecological dynamics driven by branching structure [@faganConnectivityFragmentationExtinction2002; @grantUseMultipleDispersal2010; @brownDendriticNetworkStructure2010], and this recognition has led to recent developments of spatial theories devoted to complex branching ecosystems [@rinaldoRiverNetworksEcological2018].
+For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches [@carraraDendriticConnectivityControls2012].
+However, most empirical research has explored the consequences of branching complexity for local community structure [@erosLandscapeEcologyRivers2019] or has relied solely on theoretical arguments with limited replications of branching architecture [@holtRoleBranchingMaintenance2018].
+At present, we lack a comprehensive evaluation of how ecosystem complexity controls biodiversity patterns at the metacommunity level.
+Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services [@reidEmergingThreatsPersistent2019].
 
 Here, we show that ecosystem size and complexity play comparable roles in controlling biodiversity patterns in rivers - a prime example of complex branching ecosystems.
-Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brown2010; @peterson2013; @moore2015; @terui2018].
-The recurrent merging of diverse tributaries ultimately forms a fluvial network with fractal branching patterns [@rodríguez-iturbe2001].
-As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@terui2018; @yeakel2014], may represent a macro-scale control of the ecosystem's habitat heterogeneity (habitat diversity per unit area) [@grant2007; @moore2015; @terui2018].
-Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity), two factors that regulate biodiversity at the metacommunity level [@hubbell2001; @iwasaki2012].
+Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018].
+The recurrent merging of diverse tributaries ultimately forms a fluvial network with fractal branching patterns [@rodriguez-iturbeFractalRiverBasins2001].
+As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], may represent a macro-scale control of the ecosystem's habitat heterogeneity (habitat diversity per unit area) [@grantLivingBranchesPopulation2007; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018].
+Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity), two factors that regulate biodiversity at the metacommunity level [@hubbellUnifiedNeutralTheory2001; @kallimanisHowDoesHabitat2008].
 We predict that ecosystem size and branching complexity increase watershed-scale species richness ($\gamma$ diversity) by enhancing local species richness ($\alpha$ diversity) and/or spatial difference of species composition ($\beta$ diversity) under different ecological scenarios.

### 2021-03-08 manuscript_science.Rmd
edits: manuscript results

@@
 First, we developed a theoretical framework synthesizing the influences of ecosystem size and complexity on biodiversity patterns in branching ecosystems.
-We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit [@terui2018; @yeakel2014] (**Figure 1A and B**).
+We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit [@yeakelSynchronisationStabilityRiver2014; @teruiMetapopulationStabilityBranching2018] (**Figure 1A and B**).
 Two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
@@
 Therefore, our network-generation procedure resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
-We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity model [@thompson2020].
+We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity model [@thompsonProcessbasedMetacommunityFramework2020].
 In this model, 50 species with different abiotic niches (optimum and width) disperse along a network and compete for resources with varied strengths in temporally dynamic environments (see **Materials and Methods** for model details).
@@
 When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation (**Figure 1A**).
-This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary [@brown2010; @peterson2013; @moore2015].
+This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015].
 In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to limited influences of branching on habitat heterogeneity (**Figure 1B**).
-This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities [@poff2007; @terui2018].
+This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities [@poffHomogenizationRegionalRiver2007; @teruiMetapopulationStabilityBranching2018].
 Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity within a network.
@@
 We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation existed (i.e., species travel short distances).
-This pattern reflected significant spatial variation in species composition over the branching network and was likely driven by the local association of species' niche and abiotic environments (i.e., species sorting) [@leibold2004; @thompson2020].
+This pattern reflected significant spatial variation in species composition over the branching network and was likely driven by the local association of species' niche and abiotic environments (i.e., species sorting) [@leiboldMetacommunityConceptFramework2004; @thompsonProcessbasedMetacommunityFramework2020].
 In contrast, when the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
-The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects) [@leibold2004; @economo2008; @thompson2020].
+The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects) [@leiboldMetacommunityConceptFramework2004; @economoSpeciesDiversityNeutral2008; @thompsonProcessbasedMetacommunityFramework2020].
 These patterns were consistent across different levels of dispersal probabilities (**Figures S5 and S12**).
@@
 Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2 and S5-11**).
-This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity [@hubbell2001].
+This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity [@hubbellUnifiedNeutralTheory2001].
 In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$; **Figures S13-18**).
@@
 Therefore, this landscape scenario eliminates the positive effect of branching complexity on $\gamma$ diversity.
-This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams show distinct and spatially-correlated environmental conditions, including water temperature, water chemistry, and flow/sediment regimes [@peterson2013; @moore2015].
-Instead, it may be most relevant to severely altered landscapes where localized human disturbance disrupts the environmental distinctiveness of branches through, for example, flow regulations by dams [@poff2007].
+This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams show distinct and spatially-correlated environmental conditions, including water temperature, water chemistry, and flow/sediment regimes [@petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015].
+Instead, it may be most relevant to severely altered landscapes where localized human disturbance disrupts the environmental distinctiveness of branches through, for example, flow regulations by dams [@poffHomogenizationRegionalRiver2007].
 Hence, our theory has important implications for riverine biodiversity conservation by pointing to the crucial role of habitat diversity produced by branching structure.
@@
 After careful data selection (see **Materials and Methods** and **Supplementary Text**), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; **Materials and Methods**) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in the Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
-These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at a multi-generation time scale [@comte2018], while posing challenges to traverse across watersheds (the ocean or lentic habitats; see **Materials and Methods** for watershed definition).
+These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at a multi-generation time scale [@comteFishDispersalFlowing2018], while posing challenges to traverse across watersheds (the ocean or lentic habitats; see **Materials and Methods** for watershed definition).
 We combined this data set with geospatial information, including watershed characteristics (watershed area and branching probability), climates (annual mean temperature and annual cumulative precipitation), and land use patterns (the fraction of agricultural land use and dam density).
@@
 In particular, the effect of ecosystem complexity was striking in its magnitude.
-An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelman2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for estimated average predictive comparisons).
+An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelmanAveragePredictiveComparisons2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for estimated average predictive comparisons).
 These effects remained significant even after controlling for the potential influences of climates and land use patterns (**Table 1**).
@@
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly matches the previous observations of stream fish movement.
-Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters at an annual scale [@radinger2014].
-The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation, which results in the dominance of species sorting process [@thompson2020], plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
+Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters at an annual scale [@radingerPatternsPredictorsFish2014].
+The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation, which results in the dominance of species sorting process [@thompsonProcessbasedMetacommunityFramework2020], plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
 

### 2021-03-08 manuscript_science.Rmd
edits: manuscript, implications

@@
 First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
-Human-induced habitat alterations, including flow regulation [@poff2007], habitat fragmentation [@grill2019], and stream burial [@elmore2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
+Human-induced habitat alterations, including flow regulation [@poffHomogenizationRegionalRiver2007], habitat fragmentation [@grillMappingWorldFreeflowing2019], and stream burial [@elmoreDisappearingHeadwatersPatterns2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
 Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human activities.
 Second, the complexity perspective may provide insights into the spatial planning of conservation efforts.
-Riverine reserves and local restoration are increasingly recognized as an effective management tool, and designing a spatial network of conservation sites in rivers is an area of active research [@koning2020].
+Riverine reserves and local restoration are increasingly recognized as an effective management tool, and designing a spatial network of conservation sites in rivers is an area of active research [@koningNetworkGrassrootsReserves2020].
 While large reserves or restoration sites are undoubtedly important, our results indicate the potential of coordinated networks of local conservation sites in protecting biodiversity.
-For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin [@koning2020].
+For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin [@koningNetworkGrassrootsReserves2020].
 
-While the prevailing evidence supports the importance of ecosystem size in scaling species diversity [@hubbell2001; @triantis2012; @iwasaki2012], ecosystem complexity has not received the attention it deserves.
-However, the ubiquity of scale-invariant complexity across terrestrial [@turner2015] and aquatic ecosystems [@rodríguez-iturbe2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
+While the prevailing evidence supports the importance of ecosystem size in scaling species diversity [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012], ecosystem complexity has not received the attention it deserves.
+However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
 Our fundamental findings of the dual control of biodiversity should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
-Further, the proposed framework may be extended to other aspects of biodiversity; for example, a logical next step is to explore how these ecosystem properties regulate functional diversity [@petchey2002; @su2021] and community assembly processes [@chase2010].
+Further, the proposed framework may be extended to other aspects of biodiversity; for example, a logical next step is to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002; @suHumanImpactsGlobal2021] and shifts in community assembly processes [@chaseStochasticCommunityAssembly2010].
 Recognizing the dual control of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.

### 2021-03-08 manuscript_science.Rmd
edits: manuscript, minor chage

@@
 In particular, the effect of ecosystem complexity was striking in its magnitude.
-An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelmanAveragePredictiveComparisons2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for estimated average predictive comparisons).
+An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelmanAveragePredictiveComparisons2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
 These effects remained significant even after controlling for the potential influences of climates and land use patterns (**Table 1**).

### 2021-03-08 supplementary_information_science.Rmd
edits: si, methods & materials

@@
 
-We depicted branching ecosystems as a bifurcating network of connected habitat patches [@terui2018; @yeakel2014] (**Figure 1**).
+We depicted branching ecosystems as a bifurcating network of connected habitat patches [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**).
 Habitat patches, or local communities, can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
@@
 Each habitat patch is assigned to be a branching patch (including upstream terminals) with probability $P_b$ or a non-branching patch with probability $1-P_b$.
-In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in branch $q$, $n_{p,q}$, is a realization of a random variable drawn from a geometric distribution $n_{p,q} \sim Ge(P_{b})$ [@terui2018] but conditional on $\sum_{q=1}^{N_b}n_{p,q} = N_p$ ($N_b$ is the number of branches in a network).
+In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in branch $q$, $n_{p,q}$, is a realization of a random variable drawn from a geometric distribution $n_{p,q} \sim Ge(P_{b})$ [@teruiMetapopulationStabilityBranching2018] but conditional on $\sum_{q=1}^{N_b}n_{p,q} = N_p$ ($N_b$ is the number of branches in a network).
 The number of branches $N_b$ is identical to the number of branching habitat patches in a network, or the number of 'success' out of $N_p$ trials.
@@
 This framework has two merits.
-First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution) [@rodríguez-iturbe2001].
-Second, it preserves the fractal nature of branching patterns [@peckham1999].
-An alternative approach is the use of optimal channel networks [@carraro2020].
+First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution) [@rodriguez-iturbeFractalRiverBasins2001].
+Second, it preserves the fractal nature of branching patterns [@peckhamReformulationHortonLaws1999].
+An alternative approach is the use of optimal channel networks [@carraroGenerationApplicationRiver2020].
 However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to compare theoretical predictions with empirical observations.
@@
 The parameter $\omega$ takes values of 0-1 and represents the relative influence of the right tributary given the relative size of joining tributaries.
-With this expression, larger tributaries have a greater influence on the downstream environment, as observed in natural river networks [@benda2004].
+With this expression, larger tributaries have a greater influence on the downstream environment, as observed in natural river networks [@bendaNetworkDynamicsHypothesis2004].
 
@@
 
-We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al [@thompson2020].
+We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al [@thompsonProcessbasedMetacommunityFramework2020].
 In this framework, abiotic environmental conditions (density-independent), intra- and interspecific competition (density-dependent), and dispersal regulate a species' realized population growth.
@@
 where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$.
-The realized discrete number of individuals is drawn from a Poisson distribution to account for stochasticity in demographic and dispersal processes [@fronhofer2017; @thompson2020].
-Local community dynamics are simulated based on the Beverton-Holt equation [@beverton1957]:
+The realized discrete number of individuals is drawn from a Poisson distribution to account for stochasticity in demographic and dispersal processes [@fronhoferClassicalMetapopulationDynamics2017; @thompsonProcessbasedMetacommunityFramework2020].
+Local community dynamics are simulated based on the Beverton-Holt equation [@bevertonDynamicsExploitedFish1957]:
 
@@
 where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
-$K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area [@terui2016; @rahel1991].
+$K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area [@teruiThreeEcologicalFactors2016; @rahelFishAssemblagesHabitat1991].
 The parameter $\alpha_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ \> 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
@@
 where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$.
-We introduced the cost of a wide niche by multiplying $\delta$ [@chaianunporn2015]:
+We introduced the cost of a wide niche by multiplying $\delta$ [@chaianunpornEvolutionaryResponsesClimate2015]:
 
@@
 Values of simulation parameters were summarized in **Table S2**.
-We performed simulations using R version 4.0.2 [@rcoreteam2020].
+We performed simulations using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].
 
@@
 We compiled fish data at two geographic regions: the Hokkaido island, Japan, and the Midwest, US.
-For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish [@fukushima2007; @fukushima2011], monitoring data at protected watersheds [@comte2021; @terui2018], and primary data collected by the authors [@miyazaki2016; @terui2016], which collectively cover the entire Hokkaido island.
-For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources [@iowadepartmentofnaturalresources2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources [@illinoisenvironmentalprotectionagency2014], Minnesota Pollution Control Agency [@minnesotapollutioncontrolagency2014], and Wisconsin Department of Natural Resources [@wisconsindepartmentofnaturalresources2018].
+For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish [@fukushimaModellingEffectsDams2007; @fukushimaHokkaidoFreshwaterFish2011], monitoring data at protected watersheds [@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors [@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire island.
+For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources [@iowadepartmentofnaturalresourcesBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources [@illinoisenvironmentalprotectionagencyIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency [@minnesotapollutioncontrolagencyDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources [@wisconsindepartmentofnaturalresourcesGuidelinesAssessingFish2018].
 We detailed procedures for initial data selection in **Supplementary Text**.
@@
 Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity [@chao2014].
-We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT' [@hsieh2016].
-We assessed the completeness of the observed species richness based on sample coverage, which is the total proportional abundances of observed species to the whole metacommunity [@chao2014].
+Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity [@chaoRarefactionExtrapolationHill2014a].
+We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016].
+We assessed the completeness of the observed species richness based on sample coverage, which is the total proportional abundances of observed species to the whole metacommunity [@chaoRarefactionExtrapolationHill2014a].
 We excluded watersheds whose sample coverage was below 0.9 because the estimates of asymptotic species richness may contain non-negligible statistical uncertainty.
 $\alpha$ diversity was estimated by taking an average of local species richness at each site.
-$\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity [@whittaker1960].
+$\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity [@whittakerVegetationSiskiyouMountains1960].
 
@@
 We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]).
-We used Hydrologically Adjusted Elevations of MERIT Hydro [@yamazaki2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area).
-The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0 [@yamazaki2015].
+We used Hydrologically Adjusted Elevations of MERIT Hydro [@yamazakiMERITHydroHighResolution2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area).
+The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0 [@yamazakiDevelopmentGlobal90m2015].
 Watershed area was estimated based on the delineated watershed polygons.
@@
 A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
-We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro [@yamazaki2019].
-We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4 [@hijmans2005].
-We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhorn2020].
-We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehner2011].
-We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenning2018], 'sf' [@pebesma2018] 'raster' [@hijmans2020] 'stars' [@pebesma2020], and 'exactextractr' [@baston2020].
+We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro [@yamazakiMERITHydroHighResolution2019].
+We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4 [@hijmansVeryHighResolution2005].
+We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehnerGlobalReservoirDam2011].
+We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenningRSAGASAGAGeoprocessing2018], 'sf' [@pebesmaSimpleFeaturesStandardized2018] 'raster' [@hijmansRasterGeographicData2020] 'stars' [@pebesmaStarsSpatiotemporalArrays2020], and 'exactextractr' [@bastonExactextractrFastExtraction2020].
 
@@
 We developed robust regression models with an M-estimation method to examine the effects of macro-scale drivers on diversity metrics.
-We employed robust regression models given the uncertainty of diversity estimates (see **Fish community data**).
+The robust regression analysis is insensitive to outliers of a response variable; therefore, this methods allows us to account for uncertainties of our diversity estimates (see **Fish community data**).
 Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$.
@@
 
-We compared the performance of these competing models using the Bayes factor [@wagenmakers2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1).
-We used Bayesian Information Criteria (BIC) of the linear models to approximate the Bayes factor [@wagenmakers2007]:
+We compared the performance of these competing models using the Bayes factor [@wagenmakersPracticalSolutionPervasive2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1).
+We used Bayesian Information Criteria (BIC) of the linear models to approximate the Bayes factor [@wagenmakersPracticalSolutionPervasive2007]:
 
@@
 For the supported model of $\gamma$ diversity, we estimated average predictive comparisons of watershed area and branching probability to compare their effect sizes.
-The average predictive comparison is an expected change of the response variable per a unit difference of the explanatory variable of interest [@gelman2007].
+The average predictive comparison is an expected change of the response variable per a unit difference of the explanatory variable of interest [@gelmanAveragePredictiveComparisons2007].
 Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method is applicable to models with variable transformations and allows direct comparisons of the effect sizes of watershed area and branching probability (see **Supplementary Text** for further details).
-We performed statistical analysis using R version 4.0.2 [@rcoreteam2020].
+We performed statistical analysis using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].
 

### 2021-03-08 manuscript_science.Rmd
edits: final edits for manuscripts etc

--- 2021-03-08 manuscript_science.Rmd
@@
 ---
-title: "Ecosystem size and complexity dictate riverine biodiversity"
+title: "Title: Ecosystem size and complexity dictate riverine biodiversity"
 output:
@@
 bibliography: references.bib
+header-includes:
+  - \usepackage[left]{lineno}
+  - \linenumbers
 ---
@@
 
-**One sentence summary:** Using theory and empirical analysis of extensive community data, this research provides the first robust evidence that ecosystem size and complexity jointly regulate biodiversity in river networks.
+**One sentence summary:** This study provides the first evidence that ecosystem size and complexity play comparable roles in regulating biodiversity.
 
@@
 The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios.
+Importantly, the impact of ecosystem complexity was comparable to that of ecosystem size (**Figures 2 and 3**); therefore, they play equally-important roles in regulating biodiversity.
 The strength of competition and dispersal processes (dispersal distance and probability) did not change the relationships between $\gamma$ diversity and ecosystem properties (compare panels in **Figures 2 and 3**).
@@
 Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`).
-In line with our theoretical predictions, the estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions.
+In line with our theoretical predictions, the estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions (**Table 1 and Figure 4**).
 In particular, the effect of ecosystem complexity was striking in its magnitude.
-An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelmanAveragePredictiveComparisons2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for estimated average predictive comparisons).
+Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supplementary Text**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
 These effects remained significant even after controlling for the potential influences of climates and land use patterns (**Table 1**).
@@
 
-While the prevailing evidence supports the importance of ecosystem size in scaling species diversity [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012], ecosystem complexity has not received the attention it deserves.
+While the prevailing evidence supports the importance of ecosystem size in scaling biodiversity patterns [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
 However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.

### 2021-03-08 supplementary_information_science.Rmd
edits: final edits for manuscripts etc

@@
 title: |
-  | Supplementary Information for:
+  | Supplementary Materials for:
   | Ecosystem size and complexity dictate riverine biodiversity
@@
 We developed robust regression models with an M-estimation method to examine the effects of macro-scale drivers on diversity metrics.
-The robust regression analysis is insensitive to outliers of a response variable; therefore, this methods allows us to account for uncertainties of our diversity estimates (see **Fish community data**).
+The robust regression analysis is insensitive to outliers of a response variable; therefore, this method allows us to account for uncertainties of our diversity estimates (see **Fish community data**).
 Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$.
@@
 Longitudinal gradients of local species richness have been extensively studied in rivers, illuminating typical patterns observed in nature.
-The most common pattern is a downstream increase of local species richness [@mcdowall1996; @mcdowall1998; @rahel1991; @terui2016].
-However, recent empirical and theoretical studies also showed 'reversed patterns,' in which local species richness decreases downstream [@bsemer2013; @harvey2018].
+The most common pattern is a downstream increase of local species richness [@mcdowallFightingFlowDownstreamupstream1998; @rahelFishAssemblagesHabitat1991; @teruiThreeEcologicalFactors2016].
+However, recent empirical and theoretical studies also showed 'reversed patterns,' in which local species richness decreases downstream [@bsemerHeadwatersAreCritical2013; @harveyDisturbanceReversesClassic2018].
 We predicted the longitudinal gradient of local species richness to confirm that our simulation scenarios are capable of reproducing the previously observed patterns of local species richness.
@@
 
-**Hokkaido, Japan.** We used data from the Hokkaido Freshwater Fish Database HFish [@fukushima2011; @fukushima2007], monitoring data at protected watersheds [@comte2021; @terui2018], and primary data collected by the authors [@miyazaki2016; @terui2016], which collectively cover the entire Hokkaido island.
-Most data were collected from summer to fall.
-We screened data through the following procedure:
+**Hokkaido, Japan.** In Hokkaido, most data were collected from summer to fall. We screened data through the following procedure:
 
@@
 
-**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources [@iowadepartmentofnaturalresources2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources [@illinoisenvironmentalprotectionagency2014], Minnesota Pollution Control Agency [@minnesotapollutioncontrolagency2014], and Wisconsin Department of Natural Resources [@wisconsindepartmentofnaturalresources2018].
-These data sets cover most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined by U.S.
+**Midwest, US.** In the Midwest, the data set covered most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined by U.S.
 Geological Survey and U.S.
-Department of Agriculture Natural Resources Conservation Service [@u.s.geologicalsurveyandu.s.departmentofagriculturenaturalresourcesconservationservice2013]) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05).
+Department of Agriculture Natural Resources Conservation Service [@u.s.geologicalsurveyandu.s.departmentofagriculturenaturalresourcesconservationserviceFederalStandardsProcedures2013]) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05).
 Fish data were collected from summer to fall with electrofishing (backpack, barge-type, or boat-mounted) and supplemental netting at some locations.
@@
 In this simulation, presence of species $i$ at site $x$, $J_{ix}$, was drawn from a Bernoulli distribution as $J_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$.
-Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT' [@hsieh2016].
+Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016].
 We calculated % bias of estimated asymptotic species richness $S_{est}$:
@@
 
-The average predictive comparison provides an intuitive yet rigorous way to quantify effect sizes for each of explanatory variables in regression models with interactions and/or variable transformations [@gelman2007].
+The average predictive comparison provides an intuitive yet rigorous way to quantify effect sizes for each of explanatory variables in regression models with interactions and/or variable transformations [@gelmanAveragePredictiveComparisons2007].
 The basic predictive comparison $\delta_u$ is an expected change in $y$ on the original scale per a unit difference of the explanatory variable of interest:
@@
 In general, $\delta_u$ depends on $u^{(1)}$ and $u^{(2)}$ (the beginning and end points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$.
-Therefore, Gelman and Pardoe [@gelman2007] defined the *average predictive comparison* $\Delta_u$, the mean value of $\delta_u$ over specified distributions of the inputs and model parameters:
+Therefore, Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007] defined the *average predictive comparison* $\Delta_u$, the mean value of $\delta_u$ over specified distributions of the inputs and model parameters:
 
@@
 However, directly using the above equation is impractical because estimating $p(u^{(1)}|v)$ and $p(u^{(2)}|v)$ from finite data points is challenging (especially when $v$ is continuous).
-Instead, we estimated $\Delta_u$ using the following equation proposed by Gelman and Pardoe [@gelman2007]:
+Instead, we estimated $\Delta_u$ using the following equation proposed by Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:
 
@@
 which should represent how likely it is for $u$ to transition from $u_i$ to $u_j$ with $v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$).
-We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelman2007]:
+We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:
 
@@
 We estimated $\hat \Delta_u$ for watershed area and branching probability using the estimated coefficients $\hat \xi_k$ of the regression model explaining $\gamma$ diversity.
-A thousand of vectors of simulated parameters $\Theta_s$ were drawn from normal distributions with means of $\hat \xi_k$ and standard deviations of $\sigma_{\xi, k}$ (the estimated standard errors of parameter $\xi_k$).
+A thousand of vectors of simulated parameters $\Theta_s$ were drawn from normal distributions with means of $\hat \xi_k$ and standard deviations of $\sigma_{\xi, k}$ (the estimated standard errors of parameters $\xi_k$).
 The estimated average predictive comparisons are $\hat \Delta_{u} = \frac{1}{S} \sum_{s=1}^S \hat \Delta_{u,s}$ where

### 2021-03-08 table.Rmd
edits: final edits for manuscripts etc

@@
                      type = "latex",
-                     ci = TRUE,
-                     title = "Estimated parameters of linear regression models explaining fish species richness in Hokkaido (Japan) and the Midwest (US) regions.
-The 95\\% confidence intervals are shown in parenthesis.
+                     title = "Estimated parameters of robust regression models explaining fish species richness in Hokkaido (Japan) and the Midwest (US).
+The standard errors are shown in parenthesis.
 Response variables were log-10 transformed.

### 2021-03-08 manuscript_science.Rmd
Update manuscript_science.Rmd

@@
 Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**).
-The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios.
-Importantly, the impact of ecosystem complexity was comparable to that of ecosystem size (**Figures 2 and 3**); therefore, they play equally-important roles in regulating biodiversity.
-The strength of competition and dispersal processes (dispersal distance and probability) did not change the relationships between $\gamma$ diversity and ecosystem properties (compare panels in **Figures 2 and 3**).
-Hence, the ecosystem size and complexity are expected to increase $\gamma$ diversity regardless of ecological scenarios.
+The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios (compare panels in **Figures 2 and 3**).
+Importantly, the impact of ecosystem complexity was comparable to that of ecosystem size.
+Hence, the ecosystem size and complexity play equally important roles in regulating $\gamma$ diversity regardless of ecological scenarios.
 

### 2021-03-08 supplementary_information_science.Rmd
edits: equations

@@
 
-$$
+\begin{equation}
   \mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k}
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
 \begin{aligned}
@@
 \end{aligned}
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}}
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{\{\mu_i-z_x(t)\}^2}{2\sigma^2_{niche,i}}}]
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   \delta = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   \Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy})
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   \xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   \mu_w = \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   Bayes~factor = exp(\Delta BIC_{10}/2)
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   \%~bias = \frac{100(S_{est} - S_{true})}{S_{true}}
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   \delta_u(u^{(1)} \to u^{(2)}, v, \Theta) = \frac{E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta)}{u^{(2)} - u^{(1)}}
-$$
+\end{equation}
 
@@
 
-$$
-\Delta_u = \frac{\int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta (E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta))~p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta)}{ \int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta~(u^{(2)} - u^{(1)})~ p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta) }
-$$
+\begin{equation}
+  \Delta_u = \frac{\int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta (E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta))~p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta)}
+                  { \int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta~(u^{(2)} - u^{(1)})~ p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta) }
+\end{equation}
 
@@
 
-$$
-\hat\Delta_u = \frac{\sum_{i=1}^n \sum_{j=1}^n \sum_{s=1}^S w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}{\sum_{i=1}^n \sum_{j=1}^n \sum_{s=1}^S w_{ij}(u_j - u_i)sign(u_j - u_i)}
-$$
+\begin{equation}
+  \hat\Delta_u = \frac{\sum_{i=1}^n \sum_{j=1}^n \sum_{s=1}^S w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}
+                      {\sum_{i=1}^n \sum_{j=1}^n \sum_{s=1}^S w_{ij}(u_j - u_i)sign(u_j - u_i)}
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   w_{ij} = w(v_i, v_j)
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
 w(v_i, v_j) = \frac{1}{1 + (v_i - v_j)^T\sum_v^{-1}(v_i-v_j)}
-$$
+\end{equation}
 
@@
 
-$$
-\hat \Delta_{u,s} = \frac{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(u_j - u_i)sign(u_j - u_i)}
-$$
+\begin{equation}
+  \hat \Delta_{u,s} = \frac{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}
+                           {\sum_{i=1}^n \sum_{j=1}^n w_{ij}(u_j - u_i)sign(u_j - u_i)}
+\end{equation}
 
@@
 
-$$
+\begin{equation}
   S.E.(\hat \Delta_{u,s}) = \sqrt{\frac{1}{S-1} \sum_{s-1}^S (\hat \Delta_{u,s} - \hat \Delta_{u})^2}
-$$
+\end{equation}
 

### 2021-03-10 supplementary_information_science.Rmd
edits: si, minor correction
Update supplementary_information_science.Rmd

@@
 where $E(\cdot)$ is a known function (e.g., exponential), $u$ the input of interest (a value for the explanatory variable of interest), $v$ all the other inputs (a vector in general), $\Theta$ a set of parameters in a regression model.
-In general, $\delta_u$ depends on $u^{(1)}$ and $u^{(2)}$ (the beginning and end points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$.
+In general, $\delta_u$ depends on $u^{(1)}$ and $u^{(2)}$ (the lower and higher points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$.
 Therefore, Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007] defined the *average predictive comparison* $\Delta_u$, the mean value of $\delta_u$ over specified distributions of the inputs and model parameters:
@@
 
-which should represent how likely it is for $u$ to transition from $u_i$ to $u_j$ with $v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$).
+which should represent the likelihood of $u$ changing from $u_i$ to $u_j$ with $v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$).
 We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:
@@
 \begin{equation}
-  S.E.(\hat \Delta_{u,s}) = \sqrt{\frac{1}{S-1} \sum_{s-1}^S (\hat \Delta_{u,s} - \hat \Delta_{u})^2}
+  S.E.(\hat \Delta_{u,s}) = \sqrt{\frac{1}{S-1} \sum_{s=1}^S (\hat \Delta_{u,s} - \hat \Delta_{u})^2}
 \end{equation}

### 2021-03-10 supplementary_information_science.Rmd
Update supplementary_information_science.Rmd

@@
 Second, it preserves the fractal nature of branching patterns [@peckhamReformulationHortonLaws1999].
-An alternative approach is the use of optimal channel networks [@carraroGenerationApplicationRiver2020].
+An alternative approach is the use of optimal channel networks [@carraroGenerationApplicationRiver2020a].
 However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to compare theoretical predictions with empirical observations.
@@
 
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
+```
 where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and a standard deviation of $\sigma_l$.
@@
 \end{equation}
-
+```
 where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area; $A_k = 1$ at the most upstream patch).
@@
 \end{equation}
-
+```
 where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$.
@@
 \end{equation}
-
+```
 where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
@@
 \end{equation}
-
+```
 where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$.
@@
 \end{equation}
-
+```
 Smaller values of $\nu$ imply greater costs of having a wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$ near the niche optimum.
@@
 \end{equation}
-
+```
 $\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (the shortest network path measured as the number of habitat patches).
@@
 \end{equation}
-
+```
 The parameter $\theta$ regulates the dispersal distance of a species that follows an exponential distribution ($\theta^{-1}$ corresponds to the expected dispersal distance).
@@
 \end{equation}
-
+```
 where $\xi_k$ are the intercept and regression coefficients for linear predictors.
@@
 \end{equation}
-
+```
 All explanatory variables except watershed area, branching probability, and region were standardized to a mean of zero and a standard deviation of one before the analysis.
@@
 \end{equation}
-
+```
 where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$.
@@
 \end{equation}
-
+```
 where $\psi_k$ ($k = 0-2$) are the intercept ($\psi_0$) and regression coefficients ($\psi_1$ and $\psi_2$).
@@
 \end{equation}
-
+```
 where $\zeta_k$ ($k = 0-8$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-8}$).
@@
 \end{equation}
-
+```
 Positive values of % bias indicate an overestimation of species richness, while negative values indicate an underestimation.
@@
 These values are useful if they are directly interpretable.
-For example, in linear regression models without variable transformations, regression coefficients have direct interpretations as they represent additive effects.
+For example, in linear regression models without interactions and/or variable transformations, regression coefficients have direct interpretations as they represent additive effects.
 However, there are many cases where regression coefficients are difficult to interpret.
@@
 \end{equation}
-
+```
 where $E(\cdot)$ is a known function (e.g., exponential), $u$ the input of interest (a value for the explanatory variable of interest), $v$ all the other inputs (a vector in general), $\Theta$ a set of parameters in a regression model.
-In general, $\delta_u$ depends on $u^{(1)}$ and $u^{(2)}$ (the lower and higher points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$.
+In general, $\delta_u$ rests on $u^{(1)}$ and $u^{(2)}$ (the lower and higher points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$.
 Therefore, Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007] defined the *average predictive comparison* $\Delta_u$, the mean value of $\delta_u$ over specified distributions of the inputs and model parameters:
 
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
+```
 However, directly using the above equation is impractical because estimating $p(u^{(1)}|v)$ and $p(u^{(2)}|v)$ from finite data points is challenging (especially when $v$ is continuous).
@@
 \end{equation}
-
+```
 The summations over $n$ data ($i$ and $j$ are a given data point) and $S$ parameter replicates ($s$ is a given simulation replicate) are a realization of averaging over the distributions of $(u^{(1)},v)$ , $u^{(2)}$, and $\Theta$.
@@
 \end{equation}
-
-which should represent the likelihood of $u$ changing from $u_i$ to $u_j$ with $v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$).
+```
+The weight factor should represent the likelihood of $u$ changing from $u_i$ to $u_j$ with a common $v = v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$).
 We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:
 
+```{=tex}
 \begin{equation}
-w(v_i, v_j) = \frac{1}{1 + (v_i - v_j)^T\sum_v^{-1}(v_i-v_j)}
+w(v_i, v_j) = \frac{1}{1 + (v_i - v_j)^T\Omega_v^{-1}(v_i-v_j)}
 \end{equation}
-
-where $\sum_v$ is the variance-covariance matrix of $v$.
+```
+where $\Omega_v^{-1}$ is the inverse of the variance-covariance matrix of $v$.
 
@@
 
+```{=tex}
 \begin{equation}
   \hat \Delta_{u,s} = \frac{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}
-                           {\sum_{i=1}^n \sum_{j=1}^n w_{ij}(u_j - u_i)sign(u_j - u_i)}
+                           {\sum_{i=1}^n \sum_{j=1}^n w_{ij}(10^{u_j} - 10^{u_i})sign(u_j - u_i)}
 \end{equation}
+```
+We exponentiated $u_i$ and $u_j$ because we log-transformed watershed area and branching probability in the statistical model. Then
 
-Then
-
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
+```
 The estimated average predictive comparisons were summarized in **Table S7**.

### 2021-03-10 supplementary_information_science.Rmd
Update supplementary_information_science.Rmd

@@
 These values are useful if they are directly interpretable.
-For example, in linear regression models without interactions and/or variable transformations, regression coefficients have direct interpretations as they represent additive effects.
+For example, in linear regression models without interactions and variable transformations, regression coefficients have direct interpretations as they represent additive effects.
 However, there are many cases where regression coefficients are difficult to interpret.
@@
 \begin{equation}
-  \Delta_u = \frac{\int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta (E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta))~p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta)}
-                  { \int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta~(u^{(2)} - u^{(1)})~ p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta) }
+  \Delta_u = \frac{\int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta (E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta))~p(u^{(1)}|v)~p(u^{(2)}|v)~p(v)~p(\Theta)}
+                  { \int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta~(u^{(2)} - u^{(1)})~ p(u^{(1)}|v)~p(u^{(2)}|v)~p(v)~p(\Theta) }
 \end{equation}
@@
 where $\Omega_v^{-1}$ is the inverse of the variance-covariance matrix of $v$.
+The function gives the maximum weight for a pair of $u_i$ and $u_j$ if $v_i = v_j$ (note that $v=v_i$ when $u = u_i$) while giving a less weight as the Mahalanobis distance between $v_i$ and $v_j$ increases.
+This property makes sense because our goal is to approximate the probability of transition from $u_i$ to $u_j$ with a common $v$ (i.e., $v_i = v_j$).
 
@@
 ```
-We exponentiated $u_i$ and $u_j$ because we log-transformed watershed area and branching probability in the statistical model. Then
+We exponentiated $u_i$ and $u_j$ in the denominator because we log-transformed watershed area and branching probability in the statistical model. Then
 

### 2021-03-11 empirical/table_splist_hkd.R
edits: minor change in table source files

@@ -2,11 +2,11 @@
 # setup -------------------------------------------------------------------
 
   pacman::p_load(tidyverse, knitr, kableExtra)
-  dat_hkd <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))
+  dat_hkd_site <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))
 
 # table -------------------------------------------------------------------
 
-  table_output <- dat_hkd %>% 
+  table_output <- dat_hkd_site %>% 
     mutate(n_site = n_distinct(SiteID)) %>% 
     mutate(Species = str_replace_all(str_to_title(Species), "_", " ")) %>% 
     mutate(Species = str_replace_all(Species, "(spp$)|(spp\\s)", "spp\\.")) %>% 

### 2021-03-11 empirical/table_splist_mw.R

@@ -2,13 +2,13 @@
 # setup -------------------------------------------------------------------
 
   pacman::p_load(tidyverse, knitr, kableExtra)
-  dat_mw <- read_csv(here::here('empirical/data_out/data_mw_site.csv'))
+  dat_mw_site <- read_csv(here::here('empirical/data_out/data_mw_site.csv'))
 
 # table -------------------------------------------------------------------
 
   sp_mw_latin <- read_csv(here::here('empirical/data_out/data_mw_splist_latin.csv'))
   
-  table_output <- dat_mw %>% 
+  table_output <- dat_mw_site %>% 
     mutate(n_site = n_distinct(SiteID)) %>% 
     rename(Common_name = Species) %>% 
     group_by(Common_name) %>% 

### 2021-03-11 supplementary_information_science.Rmd
edits: si, table caption

@@
 Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.
-See Tables S1 and S2 for interpretation of the simulation parameters.
+See **Tables S1 and S2** for interpretation of the simulation parameters.
 
@@
 **Table S5** List of fish species in Hokkaido, Japan, included in our statistical analysis.
-`r n_distinct(dat_hkd$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy out of `r n_distinct(dat_hkd$SiteID)` sites.
+`r n_distinct(dat_hkd_site$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy of `r n_distinct(dat_hkd_site$SiteID)` sites.
 
@@
 **Table S6** List of fish species in the Midwest, US, included in our statistical analysis.
-`r n_distinct(dat_mw$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy out of `r n_distinct(dat_mw$SiteID)` sites.
+`r n_distinct(dat_mw_site$Species)` species are ordered alphabetically, along with the number of sites present and % occupancy of `r n_distinct(dat_mw_site$SiteID)` sites.
 

### 2021-03-12 manuscript_sciad.Rmd
edits: resubmit to sciad

--- 2021-03-08 manuscript_science.Rmd
@@
 ---
-title: "Title: Ecosystem size and complexity dictate riverine biodiversity"
+title: "Ecosystem size and complexity dictate riverine biodiversity"
 output:
@@
 
-**One sentence summary:** This study provides the first evidence that ecosystem size and complexity play comparable roles in regulating biodiversity.
-
 **Authors:** Akira Terui^1^, Seoghyun Kim^1^, Christine L. Dolph^2^, Taku Kadoya^3^, Yusuke Miyazaki^4^
@@
 **Abstract:** Larger ecosystems support more species; this ubiquitous pattern is the foundation of current conservation schemes.
-However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such complexity in scaling biodiversity is largely unknown.
+However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such complexity in controlling biodiversity is largely unknown.
 Here, we use theory and extensive fish community data from two distinct geographic regions (Japan and United States) to show that ecosystem size and complexity dictate riverine biodiversity.
@@
 
-# Maintext
+## Introduction
 
@@
 However, most empirical research has explored the consequences of branching complexity for local community structure [@erosLandscapeEcologyRivers2019] or has relied solely on theoretical arguments with limited replications of branching architecture [@holtRoleBranchingMaintenance2018].
-At present, we lack a comprehensive evaluation of how ecosystem complexity controls biodiversity patterns at the metacommunity level.
+At present, we lack a comprehensive evaluation of how branching complexity controls biodiversity patterns at the metacommunity level.
 Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services [@reidEmergingThreatsPersistent2019].
@@
 
-## Synthesizing ecosystem size and complexity influences
+## Results and Discussion
+
+### Theoretical synthesis of ecosystem size and complexity influences
 
@@
 Importantly, the impact of ecosystem complexity was comparable to that of ecosystem size.
-Hence, the ecosystem size and complexity play equally important roles in regulating $\gamma$ diversity regardless of ecological scenarios.
+Hence, regardless of ecological scenarios, ecosystem size and complexity are likely to be equally important in regulating $\gamma$ diversity.
 
@@
 
-## Empirical evidence from distinct geographic regions
+### Empirical evidence from distinct geographic regions
 
@@
 
-## Implications for biodiversity conservation
+### Implications
 
@@
 However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
-Our fundamental findings of the dual control of biodiversity should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
+Our fundamental findings should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
 Further, the proposed framework may be extended to other aspects of biodiversity; for example, a logical next step is to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002; @suHumanImpactsGlobal2021] and shifts in community assembly processes [@chaseStochasticCommunityAssembly2010].

### 2021-03-13 manuscript_sciad.Rmd
edits: maintext

@@
 Here, we show that ecosystem size and complexity play comparable roles in controlling biodiversity patterns in rivers - a prime example of complex branching ecosystems.
-Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018].
+Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016].
 The recurrent merging of diverse tributaries ultimately forms a fluvial network with fractal branching patterns [@rodriguez-iturbeFractalRiverBasins2001].
@@
 The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects) [@leiboldMetacommunityConceptFramework2004; @economoSpeciesDiversityNeutral2008; @thompsonProcessbasedMetacommunityFramework2020].
+Therefore, ecosystem size and complexity can increase $\gamma$ diversity via enhanced species sorting or mass effects, and which takes primacy is dependent on the degree of dispersal limitation.
 These patterns were consistent across different levels of dispersal probabilities (**Figures S5 and S12**).
@@
 Influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios.
-Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2 and S5-11**).
+Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2 and S5-S11**).
 This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity [@hubbellUnifiedNeutralTheory2001].
-In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$; **Figures S13-18**).
+In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$; **Figures S13-S18**).
 Under this scenario, branching has a minor influence on the ecosystem's habitat heterogeneity because patch-level environmental variation is equivalent to or greater than environmental differences between tributaries (**Figure 1B**).
@@
 
-Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`).
-In line with our theoretical predictions, the estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions (**Table 1 and Figure 4**).
+We found decisive support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`) despite the substantial difference in fish fauna between the study regions.
+The estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions (**Table 1 and Figure 4**).
 In particular, the effect of ecosystem complexity was striking in its magnitude.
 Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supplementary Text**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
-These effects remained significant even after controlling for the potential influences of climates and land use patterns (**Table 1**).
+This result is reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016] - the sole theoretical assumption required for the dual control of $\gamma$ diversity to emerge.
+Further, the consistent patterns across geographic regions with distinct fish fauna suggest that ecological traits of species in metacommunities may have a minor effect on the scaling relationships as predicted by our theory.
 
-Similarly, we found weak to moderate supports for the global models of $\alpha$ and $\beta$ diversity (Bayes factor = `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
+Similarly, there were weak to moderate supports for the global models of $\alpha$ and $\beta$ diversity (Bayes factor = `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
 In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity while $\alpha$ diversity showing a weaker or a vague response to these ecosystem properties (**Table 1 and Figure 4**).
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly matches the previous observations of stream fish movement.
-Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several tens to hundreds of meters at an annual scale [@radingerPatternsPredictorsFish2014].
-The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation, which results in the dominance of species sorting process [@thompsonProcessbasedMetacommunityFramework2020], plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
+Field studies (e.g., mark-recapture) recurrently revealed the restricted movement of stream fish, typically limited to several hundreds of meters at an annual time scale [@radingerPatternsPredictorsFish2014].
+The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation, which results in the increasing importance of species sorting process (**Figures 2 and 3**), plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.
 
@@
 
-Overall, our results provide the first empirical evidence that ecosystem size and complexity play comparable roles in controlling biodiversity in rivers.
-Further, these patterns were fairly consistent with our theoretical predictions that are free from any confounding factors, suggesting that spurious correlations are very unlikely.
+A potential criticism is that our results are driven by spurious correlations; however, this is very unlikely.
+We have statistically controlled the potential influences of climates and land use patterns (**Table 1**).
+Moreover, our empirical results were fairly consistent with theoretical predictions, which are free from any confounding factors.
+Thus, we are confident in our statistical inference.
 
@@
 
-The emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
+Using theory and extensive community data, our study provides the strong evidence that ecosystem size and complexity play equally important roles in regulating riverine biodiversity.
+In particular, the emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
 First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.

### 2021-03-13 manuscript_sciad.Rmd
edits: maintext minor

@@
 This result is reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016] - the sole theoretical assumption required for the dual control of $\gamma$ diversity to emerge.
-Further, the consistent patterns across geographic regions with distinct fish fauna suggest that ecological traits of species in metacommunities may have a minor effect on the scaling relationships as predicted by our theory.
+Further, the consistent patterns across geographic regions with distinct fish fauna suggest that ecological traits of species in metacommunities may have a minor effect on the scaling relationships, as predicted by our theory.
 
@@
 It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, persist in human-dominated landscapes to maintain the diversity of in-stream processes among tributaries.
-The lack of land use effects (the fraction of agricultural land use) further corroborates our interpretation (**Table 1**).
+The lack of land use effects (the fraction of agricultural land use and dam density) further corroborates our interpretation (**Table 1**).
 Although our analysis is correlative, the finding is encouraging because the branching complexity of river networks may serve as a natural defense system to human-induced environmental changes.

### 2021-03-13 manuscript_sciad.Rmd
edits: maintext

@@
 We thank Jacques Finlay for his constructive comments on the earlier version of the manuscript.
-This research was funded by National Science Foundation through a Water Sustainability and Climate Program (WSC) Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1), and the University of North Carolina at Greensboro through a start-up fund.
+This research was funded by National Science Foundation through a Water Sustainability and Climate Program Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1), and the University of North Carolina at Greensboro through a start-up fund.
 

### 2021-03-13 supplementary_information_sciad.Rmd
Update supplementary_information_sciad.Rmd

--- 2021-03-11 supplementary_information_science.Rmd
@@
 The average predictive comparison is an expected change of the response variable per a unit difference of the explanatory variable of interest [@gelmanAveragePredictiveComparisons2007].
-Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method is applicable to models with variable transformations and allows direct comparisons of the effect sizes of watershed area and branching probability (see **Supplementary Text** for further details).
+Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method provides intuitive yet rigorous estimates of effect size in models with non-linear variable transformations (see **Supplementary Text** for further details).
 We performed statistical analysis using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].
@@
 However, there are many cases where regression coefficients are difficult to interpret.
-In our case, we regressed the log-transformed species richness on explanatory variables, so regression coefficients do not have direct interpretations at the original scale of the response variable $y$ (i.e., species richness).
+In our case, we regressed the log-transformed species richness on explanatory variables, so regression coefficients do not have direct interpretations on the original scale of the response variable $y$ (i.e., species richness).
 

### 2021-03-13 supplementary_information_sciad.Rmd
Update supplementary_information_sciad.Rmd

@@
 For landscape scenarios, we used four combinations of environmental variation at headwaters ($\sigma_h = 0.01, 1$) and the degree of local environmental noise ($\sigma_l = 0.01, 1$).
-The inequality of $\sigma_h$ and $\sigma_l$ controls the relationship between branching complexity and habitat heterogeneity.
+The inequality of $\sigma_h$ and $\sigma_l$ controls the relationship between branching complexity and habitat heterogeneity (**Figures 1A and 1B**).
 For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`).
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating diversity metrics (**Supplementary Text**).
+Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating asymptotic species richness (**Supplementary Text**).
 
@@
 where $\Omega_v^{-1}$ is the inverse of the variance-covariance matrix of $v$.
-The function gives the maximum weight for a pair of $u_i$ and $u_j$ if $v_i = v_j$ (note that $v=v_i$ when $u = u_i$) while giving a less weight as the Mahalanobis distance between $v_i$ and $v_j$ increases.
+The function gives the maximum weight for a pair of $u_i$ and $u_j$ if $v_i = v_j$ ($v=v_i$ when $u = u_i$) while giving a less weight as the Mahalanobis distance between $v_i$ and $v_j$ increases.
 This property makes sense because our goal is to approximate the probability of transition from $u_i$ to $u_j$ with a common $v$ (i.e., $v_i = v_j$).
 
-We estimated $\hat \Delta_u$ for watershed area and branching probability using the estimated coefficients $\hat \xi_k$ of the regression model explaining $\gamma$ diversity.
+We estimated $\hat \Delta_u$ for watershed area and branching probability using the estimated coefficients $\hat \xi_k$ of the regression model explaining $\gamma$ diversity (see **Table 1**).
 A thousand of vectors of simulated parameters $\Theta_s$ were drawn from normal distributions with means of $\hat \xi_k$ and standard deviations of $\sigma_{\xi, k}$ (the estimated standard errors of parameters $\xi_k$).

### 2021-03-14 coverletter.Rmd
Create coverletter.Rmd

---
output: pdf_document
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

Dear *Editor*

We are excited to submit our manuscript entitled 'Ecosystem size and complexity dictate riverine biodiversity' to PNAS. Given the unprecedented rate of global biodiversity loss, a crucial task for ecologists is to guide conservation efforts by identifying key environmental factors that regulate biodiversity. A prevailing wisdom suggests that species diversity is primarily demined by area; larger ecosystems support more species (i.e., the Species Area Relationship; SAR). This ecological pattern has been found in many taxa and geographic regions, forming the foundation of current conservation schemes. For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas, which encompass more than 30 million km2 globally. However, what is largely overlooked in current biodiversity research is the role of a 'scale-invariant' complexity of ecosystem's geometric structure (hereafter, 'ecosystem complexity'). Since ecosystem complexity is independent of spatial scale or ecosystem size, existing theories are inappropriate to predict biodiversity patterns in spatially complex ecosystems.

Here, we offer a synthetic framework integrating ecosystem size and complexity influences on biodiversity patterns in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few. In this widespread yet largely overlooked fractal ecosystem's geometry, branching patterns remain constant across a wide range of spatial scales. Even so, the complexity of branching patterns forms a physical template providing a wide spectrum of environmental niches for living organisms. In this research, using theory and extensive fish community data from two distinct geographic regions, **we found that ecosystem size and complexity play comparable roles in regulating riverine biodiversity; ecosystem size alone was insufficient to predict biodiversity patterns.** Larger and more branched 'complex' river networks supported greater species richness due to increased space and habitat heterogeneity. In particular, the effect of ecosystem complexity was striking in its magnitude. A unit increase of ecosystem complexity (the prevalence of branching) resulted in an increase of species diversity that would require 1911 km2 in the areal area. Further, these patterns have consistently emerged regardless of ecological traits of species and geographic regions, suggesting that the dual control of riverine biodiversity may be pervasive across taxonomic groups and geographic regions.

Our research will attract a broad audience of PNAS for the following reasons. First, our proposed framework may apply beyond branching ecosystems as both ecosystem size and complexity represent a physical template of the ecosystem's environmental heterogeneity. Second, the results of the present study provide the ecological foundation for complexity-based ecosystem management - an important perspective overlooked in the current schemes of biodiversity conservation. Hence, we have confidence that our research not only provides fundamental insights into regulating factors of biodiversity but also has far-reaching implications for biodiversity conservation.

This work is original and is not under consideration in any other journal. All authors agree with the content and with the submission for publication, and all appropriate ethical and other necessary approvals were obtained for this research. We look forward to your reply and hope that you find our article suitable for publication in your journal.

Sincerely,

Akira Terui, Ph.D. (corresponding author)

### 2021-03-14 manuscript_sciad.Rmd
edits: remove methods

@@
 Here, we show that ecosystem size and complexity play comparable roles in controlling biodiversity patterns in rivers - a prime example of complex branching ecosystems.
-Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016].
+Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018].
 The recurrent merging of diverse tributaries ultimately forms a fluvial network with fractal branching patterns [@rodriguez-iturbeFractalRiverBasins2001].
@@
 These environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see **Materials and Methods**).
-Therefore, our network-generation procedure resembles natural processes of how branching river networks create diverse habitats in a metacommunity.
+Therefore, our network-generation procedure resembles natural processes of how branching river networks create diverse habitats in a metacommunity [@mcguireNetworkAnalysisReveals2014].
 We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity model [@thompsonProcessbasedMetacommunityFramework2020].
@@
 When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation (**Figure 1A**).
-This landscape scenario should reproduce natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015].
+This landscape scenario reproduces natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary[@petersonModellingDendriticEcological2013; @mcguireNetworkAnalysisReveals2014].
 In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to limited influences of branching on habitat heterogeneity (**Figure 1B**).
@@
 Therefore, this landscape scenario eliminates the positive effect of branching complexity on $\gamma$ diversity.
-This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams show distinct and spatially-correlated environmental conditions, including water temperature, water chemistry, and flow/sediment regimes [@petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015].
+This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams show distinct and spatially-correlated environmental conditions, including water temperature, water chemistry, and flow/sediment regimes [@petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @mcguireNetworkAnalysisReveals2014].
 Instead, it may be most relevant to severely altered landscapes where localized human disturbance disrupts the environmental distinctiveness of branches through, for example, flow regulations by dams [@poffHomogenizationRegionalRiver2007].
@@
 Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supplementary Text**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
-This result is reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016] - the sole theoretical assumption required for the dual control of $\gamma$ diversity to emerge.
+This result is reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018] - the sole theoretical assumption required for the dual control of $\gamma$ diversity to emerge.
 Further, the consistent patterns across geographic regions with distinct fish fauna suggest that ecological traits of species in metacommunities may have a minor effect on the scaling relationships, as predicted by our theory.
@@
 
+# Materials and Methods
+
+## Theory
+
+### Network generation
+
+We depicted branching ecosystems as a bifurcating network of connected habitat patches [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**).
+Habitat patches, or local communities, can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
+Two parameters determine the geometric properties of simulated branching networks: the number of habitat patches $N_p$ (ecosystem size) and branching probability $P_b$ (ecosystem complexity).
+Each habitat patch is assigned to be a branching patch (including upstream terminals) with probability $P_b$ or a non-branching patch with probability $1-P_b$.
+In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in branch $q$, $n_{p,q}$, is a realization of a random variable drawn from a geometric distribution $n_{p,q} \sim Ge(P_{b})$ [@teruiMetapopulationStabilityBranching2018] but conditional on $\sum_{q=1}^{N_b}n_{p,q} = N_p$ ($N_b$ is the number of branches in a network).
+The number of branches $N_b$ is identical to the number of branching habitat patches in a network, or the number of 'success' out of $N_p$ trials.
+This leads to an assumption that $N_b$ is a realization of a random variable drawn from a binomial distribution as $N_b \sim Binomial(N_p, P_b)$.
+This framework has two merits.
+First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution) [@rodriguez-iturbeFractalRiverBasins2001].
+Second, it preserves the fractal nature of branching patterns [@peckhamReformulationHortonLaws1999].
+An alternative approach is the use of optimal channel networks [@carraroGenerationApplicationRiver2020a].
+However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to compare theoretical predictions with empirical observations.
+
+In our network generation, we first drew $N_b$ from the binomial distribution but selected an odd number to constitute a bifurcating branching network.
+We then determined $n_{p,q}$ as random draws from the geometric distribution with the constraint of $\sum_{q=1}^{N_b}n_{p,q} = N_p$.
+The generated branches were organized randomly into a bifurcating branching network.
+
+Two sources of variation characterize the long-term average of the abiotic environment at each habitat patch: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
+We drew random values from a normal distribution with a mean of zero and a standard deviation of $\sigma_{h}$ and assigned them to headwater patches (i.e., the most upstream patches).
+These environmental values at headwaters propagate downstream through a spatial autoregressive process defined as:
+
+```{=tex}
+\begin{equation}
+  \mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k}
+\end{equation}
+```
+where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and a standard deviation of $\sigma_l$.
+The parameter $\rho$ can take values of 0-1 with larger values indicating greater spatial autocorrelation.
+In this study, we set $\rho = 1$ to mimic strong spatial autocorrelation in riverine environments.
+At confluences, we took a weighted mean of environmental values given the relative size of upstream contributing area of joining tributaries:
+
+```{=tex}
+\begin{equation}
+\begin{aligned}
+  \mu_{z,k} &= \omega(\rho \mu_{z,k+1}^R + \epsilon_{k}^R) + (1-\omega)(\rho \mu_{z,k+1}^L + \epsilon_{k}^L) \\
+  \omega &= \frac{A_{k+1}^R}{A_{k+1}^R + A_{k+1}^L}
+\end{aligned}
+\end{equation}
+```
+where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area; $A_k = 1$ at the most upstream patch).
+The parameter $\omega$ takes values of 0-1 and represents the relative influence of the right tributary given the relative size of joining tributaries.
+With this expression, larger tributaries have a greater influence on the downstream environment, as observed in natural river networks [@bendaNetworkDynamicsHypothesis2004].
+
+### Metacommunity model
+
+We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al [@thompsonProcessbasedMetacommunityFramework2020].
+In this framework, abiotic environmental conditions (density-independent), intra- and interspecific competition (density-dependent), and dispersal regulate a species' realized population growth.
+Below, we describe the details of our metacommunity model.
+
+The realized number of individuals $N_{ix}(t + 1)$ (species $i$ at patch $x$ and time $t+1$) is given as:
+
+```{=tex}
+\begin{equation}
+  N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
+\end{equation}
+```
+where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$.
+The realized discrete number of individuals is drawn from a Poisson distribution to account for stochasticity in demographic and dispersal processes [@fronhoferClassicalMetapopulationDynamics2017; @thompsonProcessbasedMetacommunityFramework2020].
+Local community dynamics are simulated based on the Beverton-Holt equation [@bevertonDynamicsExploitedFish1957]:
+
+```{=tex}
+\begin{equation}
+  n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}}
+\end{equation}
+```
+where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
+$K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area [@teruiThreeEcologicalFactors2016; @rahelFishAssemblagesHabitat1991].
+The parameter $\alpha_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ \> 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
+$\alpha_{ij}$ was drawn randomly from a uniform distribution as $\alpha_{ij} \sim Unif(0, \alpha_{max})$.
+The density-independent reproductive rate $r_{ix}(t)$ is affected by abiotic environments (non-consumable) and determined by the following Gaussian function:
+
+```{=tex}
+\begin{equation}
+  r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{\{\mu_i-z_x(t)\}^2}{2\sigma^2_{niche,i}}}]
+\end{equation}
+```
+where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$.
+We introduced the cost of a wide niche by multiplying $\delta$ [@chaianunpornEvolutionaryResponsesClimate2015]:
+
+```{=tex}
+\begin{equation}
+  \delta = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
+\end{equation}
+```
+Smaller values of $\nu$ imply greater costs of having a wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$ near the niche optimum.
+
+The environmental value at patch $x$ and time $t$, $z_x(t)$, is assumed to follow a multivariate normal distribution as $z_{x}(t) \sim MVN(\boldsymbol{\mu_z}, \boldsymbol{\Omega_z})$, where $\boldsymbol{\mu_z}$ is the vector of mean environmental conditions of habitat patches and $\boldsymbol{\Omega_z}$ is the variance-covariance matrix.
+The diagonal elements of the variance-covariance matrix $\sigma^2_z$ represent the degree of temporal environmental variation.
+The off-diagonal elements $\Omega_{xy}$ represent the spatial autocorrelation in temporal environmental variation as:
+
+```{=tex}
+\begin{equation}
+  \Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy})
+\end{equation}
+```
+$\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (the shortest network path measured as the number of habitat patches).
+The parameter $\phi$ determines the degree of the distance decay of environmental correlates.
+
+The expected number of emigrants at time $t$ is the product of dispersal probability $p_d$ and $n_{ix}(t)$: $E_{ix}(t) = p_{d}n_{ix}(t)$.
+The immigration probability at patch $x$ for species $i$, $\xi_{ix}(t)$, is calculated using the following equation that accounts for separation distance among habitat patches and dispersal capability of a species:
+
+```{=tex}
+\begin{equation}
+  \xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}
+\end{equation}
+```
+The parameter $\theta$ regulates the dispersal distance of a species that follows an exponential distribution ($\theta^{-1}$ corresponds to the expected dispersal distance).
+The expected number of immigrants is calculated as $I_{ix}(t) = \xi_{ix}(t)\sum_x^{N_p} E_{ix}$.
+
+### Simulation
+
+We used `r n_scenario` sets of parameter combinations (i.e., simulation scenarios) based on the results of extensive sensitivity analysis (**Supplementary Text**).
+The parameter combinations comprises four landscape and eight ecological scenarios.
+Landscape scenarios distinguish spatial patterns of habitat heterogeneity, while ecological scenarios change ecological traits of simulated species.
+For landscape scenarios, we used four combinations of environmental variation at headwaters ($\sigma_h = 0.01, 1$) and the degree of local environmental noise ($\sigma_l = 0.01, 1$).
+The inequality of $\sigma_h$ and $\sigma_l$ controls the relationship between branching complexity and habitat heterogeneity (**Figures 1A and 1B**).
+For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`).
+This setup results in eight ecological scenarios with different levels of dispersal and competition.
+
+We allowed interspecific variation in niche optimum and width, which were drawn from uniform distributions as $\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$.
+We used fixed values for the following parameters: maximum reproductive rate ($r_{0,i} =$ 4), niche cost ($\nu =$ `r unique(dat_sim$niche_cost)`), the degree of temporal environmental variation ($\sigma_z =$ `r unique(dat_sim$sd_env)`), and the extent of spatial autocorrelation in temporal environmental dynamics ($\phi =$ `r unique(dat_sim$phi)`).
+
+Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 200 time steps for initialization and 200 time steps for burn-in) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
+During the first 200 time steps (an initialization period), we initialized the simulation by seeding each habitat patch with populations of each species drawn from a Poisson distribution with a mean of 0.5.
+We repeated the seeding every 10 time steps during the initialization to allow species to establish their populations if they can grow from low abundances.
+After the initialization period, we ran 200 time steps as a burn-in period with no seeding to minimize influences of initial conditions.
+We saved the last 1000 time steps to estimate the temporal averages of $\alpha$, $\beta$, and $\gamma$ diversity.
+We removed simulation replicates in which no species established populations over the initial 400 time steps (`r sum(dat_sim$alpha_div == 0)` replicates out of `r nrow(dat_sim)` replicates).
+Ecosystem size and complexity were drawn randomly from uniform distributions as: $N_p \sim Unif(10, 150)$ and $P_b \sim Unif(0.01, 0.99)$ ($N_p$ was rounded to the nearest integer before running simulations).
+Values of simulation parameters were summarized in **Table S2**.
+We performed simulations using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].
+
+## Empirical data
+
+### Fish community data
+
+We compiled fish data at two geographic regions: the Hokkaido island, Japan, and the Midwest, US.
+For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish [@fukushimaModellingEffectsDams2007; @fukushimaHokkaidoFreshwaterFish2011], monitoring data at protected watersheds [@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors [@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire island.
+For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources [@iowadepartmentofnaturalresourcesBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources [@illinoisenvironmentalprotectionagencyIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency [@minnesotapollutioncontrolagencyDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources [@wisconsindepartmentofnaturalresourcesGuidelinesAssessingFish2018].
+We detailed procedures for initial data selection in **Supplementary Text**.
+
+We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
+Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating asymptotic species richness (**Supplementary Text**).
+
+We estimated $\alpha$, $\beta$, and $\gamma$ diversity at each watershed.
+$\gamma$ diversity is the total species richness at each watershed.
+Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
+Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity [@chaoRarefactionExtrapolationHill2014a].
+We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016].
+We assessed the completeness of the observed species richness based on sample coverage, which is the total proportional abundances of observed species to the whole metacommunity [@chaoRarefactionExtrapolationHill2014a].
+We excluded watersheds whose sample coverage was below 0.9 because the estimates of asymptotic species richness may contain non-negligible statistical uncertainty.
+$\alpha$ diversity was estimated by taking an average of local species richness at each site.
+$\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity [@whittakerVegetationSiskiyouMountains1960].
+
+After the data selection procedure, we obtained diversity estimates from `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (Hokkaido: `r nrow(wsd_subset[[1]])`, Midwest: `r nrow(wsd_subset[[2]])`), which encompassed a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites (Hokkaido: `r nrow(point_subset[[1]])`, Midwest: `r nrow(point_subset[[2]])`).
+Observations ranged from `r min(dat_hkd_site$Year, na.rm = T)` to `r max(dat_hkd_site$Year, na.rm = T)` in Hokkaido and from `r min(dat_mw_site$Year, na.rm = T)` to `r max(dat_mw_site$Year, na.rm = T)` in the Midwest.
+Fish species observed in the final data set were listed in **Tables S5 and S6**.
+
+### Environmental data
+
+We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]).
+We used Hydrologically Adjusted Elevations of MERIT Hydro [@yamazakiMERITHydroHighResolution2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area).
+The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0 [@yamazakiDevelopmentGlobal90m2015].
+Watershed area was estimated based on the delineated watershed polygons.
+We estimated branching probability by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$.
+A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
+We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro [@yamazakiMERITHydroHighResolution2019].
+We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4 [@hijmansVeryHighResolution2005].
+We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehnerGlobalReservoirDam2011].
+We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenningRSAGASAGAGeoprocessing2018], 'sf' [@pebesmaSimpleFeaturesStandardized2018] 'raster' [@hijmansRasterGeographicData2020] 'stars' [@pebesmaStarsSpatiotemporalArrays2020], and 'exactextractr' [@bastonExactextractrFastExtraction2020].
+
+### Statistical analysis
+
+We developed robust regression models with an M-estimation method to examine the effects of macro-scale drivers on diversity metrics.
+The robust regression analysis is insensitive to outliers of a response variable; therefore, this method allows us to account for uncertainties of our diversity estimates (see **Fish community data**).
+Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$.
+The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use (logit-transformed), and dam density.
+Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically.
+We did not include the fractions of urban and forest land use in the statistical models because these variables were strongly correlated with the fraction of agricultural land use (**Figure S19**).
+Similarly, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**).
+Correlations for other combinations of explanatory variables were weak to moderate.
+
+Climate (air temperature and precipitation) and land use (the fraction of agricultural land use and dam density) differed clearly between the regions.
+Therefore, we used residuals of the simple linear regressions between the climate or land use variable (response variable) and region (explanatory variable).
+The residuals represent deviations from the regional averages; positive values indicate values greater than the regional average while negative values indicating values smaller than the regional average.
+
+We constructed two models for each of the diversity metrics: global and region-specific models.
+The global model assumes that the effects of watershed area and branching probability are consistent across geographic regions (i.e., no interactive effects of the region with other linear predictors).
+
+```{=tex}
+\begin{equation}
+  \mu_w = \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
+\end{equation}
+```
+where $\xi_k$ are the intercept and regression coefficients for linear predictors.
+Meanwhile, the region-specific model assumes the effects of watershed area and branching probability differ between regions (i.e., interactions between region and watershed area/branching probability).
+
+```{=tex}
+\begin{equation}
+\begin{aligned}
+  \mu_w =& \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w +\\
+  &\xi_4~log_{10}~WA_w \cdot region_w + \xi_5~log_{10}~P_{b,w} \cdot region_w + \sum_k \xi_k x_{k,w}
+\end{aligned}
+\end{equation}
+```
+All explanatory variables except watershed area, branching probability, and region were standardized to a mean of zero and a standard deviation of one before the analysis.
+
+We compared the performance of these competing models using the Bayes factor [@wagenmakersPracticalSolutionPervasive2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1).
+We used Bayesian Information Criteria (BIC) of the linear models to approximate the Bayes factor [@wagenmakersPracticalSolutionPervasive2007]:
+
+```{=tex}
+\begin{equation}
+  Bayes~factor = exp(\Delta BIC_{10}/2)
+\end{equation}
+```
+where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$.
+
+For the supported model of $\gamma$ diversity, we estimated average predictive comparisons of watershed area and branching probability to compare their effect sizes.
+The average predictive comparison is an expected change of the response variable per a unit difference of the explanatory variable of interest [@gelmanAveragePredictiveComparisons2007].
+Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method provides intuitive yet rigorous estimates of effect size in models with non-linear variable transformations (see **Supplementary Text** for further details).
+We performed statistical analysis using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].
+
 # Acknowledgments
@@
 We thank Jacques Finlay for his constructive comments on the earlier version of the manuscript.
-This research was funded by National Science Foundation through a Water Sustainability and Climate Program Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1), and the University of North Carolina at Greensboro through a start-up fund.
+This research was supported by National Science Foundation through a Water Sustainability and Climate Program Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1), and the University of North Carolina at Greensboro through a start-up fund.
 

### 2021-03-14 supplementary_information_sciad.Rmd
Update supplementary_information_sciad.Rmd
edits: remove methods

@@
 
-# Materials and Methods
+# Theory
 
-## Theory
-
-### Network generation
-
-We depicted branching ecosystems as a bifurcating network of connected habitat patches [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014] (**Figure 1**).
-Habitat patches, or local communities, can be either non-branching or branching river sections with a unit length $l$, which defines the scale of local species interactions.
-Two parameters determine the geometric properties of simulated branching networks: the number of habitat patches $N_p$ (ecosystem size) and branching probability $P_b$ (ecosystem complexity).
-Each habitat patch is assigned to be a branching patch (including upstream terminals) with probability $P_b$ or a non-branching patch with probability $1-P_b$.
-In this framework, an individual branch is a consecutive series of non-branching patches terminated at a branching patch; therefore, the number of habitat patches in branch $q$, $n_{p,q}$, is a realization of a random variable drawn from a geometric distribution $n_{p,q} \sim Ge(P_{b})$ [@teruiMetapopulationStabilityBranching2018] but conditional on $\sum_{q=1}^{N_b}n_{p,q} = N_p$ ($N_b$ is the number of branches in a network).
-The number of branches $N_b$ is identical to the number of branching habitat patches in a network, or the number of 'success' out of $N_p$ trials.
-This leads to an assumption that $N_b$ is a realization of a random variable drawn from a binomial distribution as $N_b \sim Binomial(N_p, P_b)$.
-This framework has two merits.
-First, it reflects observed patterns of branch length distribution, which is known to follow an exponential distribution (a continuous version of a geometric distribution) [@rodriguez-iturbeFractalRiverBasins2001].
-Second, it preserves the fractal nature of branching patterns [@peckhamReformulationHortonLaws1999].
-An alternative approach is the use of optimal channel networks [@carraroGenerationApplicationRiver2020a].
-However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to compare theoretical predictions with empirical observations.
-
-In our network generation, we first drew $N_b$ from the binomial distribution but selected an odd number to constitute a bifurcating branching network.
-We then determined $n_{p,q}$ as random draws from the geometric distribution with the constraint of $\sum_{q=1}^{N_b}n_{p,q} = N_p$.
-The generated branches were organized randomly into a bifurcating branching network.
-
-Two sources of variation characterize the long-term average of the abiotic environment at each habitat patch: environmental variation at headwaters ($\sigma_h$) and local environmental noise ($\sigma_l$).
-We drew random values from a normal distribution with a mean of zero and a standard deviation of $\sigma_{h}$ and assigned them to headwater patches (i.e., the most upstream patches).
-These environmental values at headwaters propagate downstream through a spatial autoregressive process defined as:
-
-```{=tex}
-\begin{equation}
-  \mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k}
-\end{equation}
-```
-where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and a standard deviation of $\sigma_l$.
-The parameter $\rho$ can take values of 0-1 with larger values indicating greater spatial autocorrelation.
-In this study, we set $\rho = 1$ to mimic strong spatial autocorrelation in riverine environments.
-At confluences, we took a weighted mean of environmental values given the relative size of upstream contributing area of joining tributaries:
-
-```{=tex}
-\begin{equation}
-\begin{aligned}
-  \mu_{z,k} &= \omega(\rho \mu_{z,k+1}^R + \epsilon_{k}^R) + (1-\omega)(\rho \mu_{z,k+1}^L + \epsilon_{k}^L) \\
-  \omega &= \frac{A_{k+1}^R}{A_{k+1}^R + A_{k+1}^L}
-\end{aligned}
-\end{equation}
-```
-where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area; $A_k = 1$ at the most upstream patch).
-The parameter $\omega$ takes values of 0-1 and represents the relative influence of the right tributary given the relative size of joining tributaries.
-With this expression, larger tributaries have a greater influence on the downstream environment, as observed in natural river networks [@bendaNetworkDynamicsHypothesis2004].
-
-### Metacommunity model
-
-We simulated metacommunity dynamics in branching river networks following the metacommunity framework proposed by Thompson et al [@thompsonProcessbasedMetacommunityFramework2020].
-In this framework, abiotic environmental conditions (density-independent), intra- and interspecific competition (density-dependent), and dispersal regulate a species' realized population growth.
-Below, we describe the details of our metacommunity model.
-
-The realized number of individuals $N_{ix}(t + 1)$ (species $i$ at patch $x$ and time $t+1$) is given as:
-
-```{=tex}
-\begin{equation}
-  N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
-\end{equation}
-```
-where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$.
-The realized discrete number of individuals is drawn from a Poisson distribution to account for stochasticity in demographic and dispersal processes [@fronhoferClassicalMetapopulationDynamics2017; @thompsonProcessbasedMetacommunityFramework2020].
-Local community dynamics are simulated based on the Beverton-Holt equation [@bevertonDynamicsExploitedFish1957]:
-
-```{=tex}
-\begin{equation}
-  n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}}
-\end{equation}
-```
-where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
-$K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area [@teruiThreeEcologicalFactors2016; @rahelFishAssemblagesHabitat1991].
-The parameter $\alpha_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ \> 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
-$\alpha_{ij}$ was drawn randomly from a uniform distribution as $\alpha_{ij} \sim Unif(0, \alpha_{max})$.
-The density-independent reproductive rate $r_{ix}(t)$ is affected by abiotic environments (non-consumable) and determined by the following Gaussian function:
-
-```{=tex}
-\begin{equation}
-  r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{\{\mu_i-z_x(t)\}^2}{2\sigma^2_{niche,i}}}]
-\end{equation}
-```
-where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$.
-We introduced the cost of a wide niche by multiplying $\delta$ [@chaianunpornEvolutionaryResponsesClimate2015]:
-
-```{=tex}
-\begin{equation}
-  \delta = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
-\end{equation}
-```
-Smaller values of $\nu$ imply greater costs of having a wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$ near the niche optimum.
-
-The environmental value at patch $x$ and time $t$, $z_x(t)$, is assumed to follow a multivariate normal distribution as $z_{x}(t) \sim MVN(\boldsymbol{\mu_z}, \boldsymbol{\Omega_z})$, where $\boldsymbol{\mu_z}$ is the vector of mean environmental conditions of habitat patches and $\boldsymbol{\Omega_z}$ is the variance-covariance matrix.
-The diagonal elements of the variance-covariance matrix $\sigma^2_z$ represent the degree of temporal environmental variation.
-The off-diagonal elements $\Omega_{xy}$ represent the spatial autocorrelation in temporal environmental variation as:
-
-```{=tex}
-\begin{equation}
-  \Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy})
-\end{equation}
-```
-$\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (the shortest network path measured as the number of habitat patches).
-The parameter $\phi$ determines the degree of the distance decay of environmental correlates.
-
-The expected number of emigrants at time $t$ is the product of dispersal probability $p_d$ and $n_{ix}(t)$: $E_{ix}(t) = p_{d}n_{ix}(t)$.
-The immigration probability at patch $x$ for species $i$, $\xi_{ix}(t)$, is calculated using the following equation that accounts for separation distance among habitat patches and dispersal capability of a species:
-
-```{=tex}
-\begin{equation}
-  \xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}
-\end{equation}
-```
-The parameter $\theta$ regulates the dispersal distance of a species that follows an exponential distribution ($\theta^{-1}$ corresponds to the expected dispersal distance).
-The expected number of immigrants is calculated as $I_{ix}(t) = \xi_{ix}(t)\sum_x^{N_p} E_{ix}$.
-
-### Simulation
-
-We used `r n_scenario` sets of parameter combinations (i.e., simulation scenarios) based on the results of extensive sensitivity analysis (**Supplementary Text**).
-The parameter combinations comprises four landscape and eight ecological scenarios.
-Landscape scenarios distinguish spatial patterns of habitat heterogeneity, while ecological scenarios change ecological traits of simulated species.
-For landscape scenarios, we used four combinations of environmental variation at headwaters ($\sigma_h = 0.01, 1$) and the degree of local environmental noise ($\sigma_l = 0.01, 1$).
-The inequality of $\sigma_h$ and $\sigma_l$ controls the relationship between branching complexity and habitat heterogeneity (**Figures 1A and 1B**).
-For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`).
-This setup results in eight ecological scenarios with different levels of dispersal and competition.
-
-We allowed interspecific variation in niche optimum and width, which were drawn from uniform distributions as $\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$.
-We used fixed values for the following parameters: maximum reproductive rate ($r_{0,i} =$ 4), niche cost ($\nu =$ `r unique(dat_sim$niche_cost)`), the degree of temporal environmental variation ($\sigma_z =$ `r unique(dat_sim$sd_env)`), and the extent of spatial autocorrelation in temporal environmental dynamics ($\phi =$ `r unique(dat_sim$phi)`).
-
-Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 200 time steps for initialization and 200 time steps for burn-in) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
-During the first 200 time steps (an initialization period), we initialized the simulation by seeding each habitat patch with populations of each species drawn from a Poisson distribution with a mean of 0.5.
-We repeated the seeding every 10 time steps during the initialization to allow species to establish their populations if they can grow from low abundances.
-After the initialization period, we ran 200 time steps as a burn-in period with no seeding to minimize influences of initial conditions.
-We saved the last 1000 time steps to estimate the temporal averages of $\alpha$, $\beta$, and $\gamma$ diversity.
-We removed simulation replicates in which no species established populations over the initial 400 time steps (`r sum(dat_sim$alpha_div == 0)` replicates out of `r nrow(dat_sim)` replicates).
-Ecosystem size and complexity were drawn randomly from uniform distributions as: $N_p \sim Unif(10, 150)$ and $P_b \sim Unif(0.01, 0.99)$ ($N_p$ was rounded to the nearest integer before running simulations).
-Values of simulation parameters were summarized in **Table S2**.
-We performed simulations using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].
-
-## Empirical data
-
-### Fish community data
-
-We compiled fish data at two geographic regions: the Hokkaido island, Japan, and the Midwest, US.
-For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish [@fukushimaModellingEffectsDams2007; @fukushimaHokkaidoFreshwaterFish2011], monitoring data at protected watersheds [@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors [@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire island.
-For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources [@iowadepartmentofnaturalresourcesBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources [@illinoisenvironmentalprotectionagencyIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency [@minnesotapollutioncontrolagencyDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources [@wisconsindepartmentofnaturalresourcesGuidelinesAssessingFish2018].
-We detailed procedures for initial data selection in **Supplementary Text**.
-
-We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating asymptotic species richness (**Supplementary Text**).
-
-We estimated $\alpha$, $\beta$, and $\gamma$ diversity at each watershed.
-$\gamma$ diversity is the total species richness at each watershed.
-Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity [@chaoRarefactionExtrapolationHill2014a].
-We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016].
-We assessed the completeness of the observed species richness based on sample coverage, which is the total proportional abundances of observed species to the whole metacommunity [@chaoRarefactionExtrapolationHill2014a].
-We excluded watersheds whose sample coverage was below 0.9 because the estimates of asymptotic species richness may contain non-negligible statistical uncertainty.
-$\alpha$ diversity was estimated by taking an average of local species richness at each site.
-$\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity [@whittakerVegetationSiskiyouMountains1960].
-
-After the data selection procedure, we obtained diversity estimates from `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (Hokkaido: `r nrow(wsd_subset[[1]])`, Midwest: `r nrow(wsd_subset[[2]])`), which encompassed a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites (Hokkaido: `r nrow(point_subset[[1]])`, Midwest: `r nrow(point_subset[[2]])`).
-Observations ranged from `r min(dat_hkd_site$Year, na.rm = T)` to `r max(dat_hkd_site$Year, na.rm = T)` in Hokkaido and from `r min(dat_mw_site$Year, na.rm = T)` to `r max(dat_mw_site$Year, na.rm = T)` in the Midwest.
-Fish species observed in the final data set were listed in **Tables S5 and S6**.
-
-### Environmental data
-
-We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]).
-We used Hydrologically Adjusted Elevations of MERIT Hydro [@yamazakiMERITHydroHighResolution2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area).
-The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0 [@yamazakiDevelopmentGlobal90m2015].
-Watershed area was estimated based on the delineated watershed polygons.
-We estimated branching probability by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$.
-A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
-We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro [@yamazakiMERITHydroHighResolution2019].
-We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4 [@hijmansVeryHighResolution2005].
-We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
-We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehnerGlobalReservoirDam2011].
-We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenningRSAGASAGAGeoprocessing2018], 'sf' [@pebesmaSimpleFeaturesStandardized2018] 'raster' [@hijmansRasterGeographicData2020] 'stars' [@pebesmaStarsSpatiotemporalArrays2020], and 'exactextractr' [@bastonExactextractrFastExtraction2020].
-
-### Statistical analysis
-
-We developed robust regression models with an M-estimation method to examine the effects of macro-scale drivers on diversity metrics.
-The robust regression analysis is insensitive to outliers of a response variable; therefore, this method allows us to account for uncertainties of our diversity estimates (see **Fish community data**).
-Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$.
-The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use (logit-transformed), and dam density.
-Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically.
-We did not include the fractions of urban and forest land use in the statistical models because these variables were strongly correlated with the fraction of agricultural land use (**Figure S19**).
-Similarly, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**).
-Correlations for other combinations of explanatory variables were weak to moderate.
-
-Climate (air temperature and precipitation) and land use (the fraction of agricultural land use and dam density) differed clearly between the regions.
-Therefore, we used residuals of the simple linear regressions between the climate or land use variable (response variable) and region (explanatory variable).
-The residuals represent deviations from the regional averages; positive values indicate values greater than the regional average while negative values indicating values smaller than the regional average.
-
-We constructed two models for each of the diversity metrics: global and region-specific models.
-The global model assumes that the effects of watershed area and branching probability are consistent across geographic regions (i.e., no interactive effects of the region with other linear predictors).
-
-```{=tex}
-\begin{equation}
-  \mu_w = \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
-\end{equation}
-```
-where $\xi_k$ are the intercept and regression coefficients for linear predictors.
-Meanwhile, the region-specific model assumes the effects of watershed area and branching probability differ between regions (i.e., interactions between region and watershed area/branching probability).
-
-```{=tex}
-\begin{equation}
-\begin{aligned}
-  \mu_w =& \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w +\\
-  &\xi_4~log_{10}~WA_w \cdot region_w + \xi_5~log_{10}~P_{b,w} \cdot region_w + \sum_k \xi_k x_{k,w}
-\end{aligned}
-\end{equation}
-```
-All explanatory variables except watershed area, branching probability, and region were standardized to a mean of zero and a standard deviation of one before the analysis.
-
-We compared the performance of these competing models using the Bayes factor [@wagenmakersPracticalSolutionPervasive2007], which gives the relative strength of evidence in favor of the global model (M0) over the region-specific model (M1).
-We used Bayesian Information Criteria (BIC) of the linear models to approximate the Bayes factor [@wagenmakersPracticalSolutionPervasive2007]:
-
-```{=tex}
-\begin{equation}
-  Bayes~factor = exp(\Delta BIC_{10}/2)
-\end{equation}
-```
-where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$.
-
-For the supported model of $\gamma$ diversity, we estimated average predictive comparisons of watershed area and branching probability to compare their effect sizes.
-The average predictive comparison is an expected change of the response variable per a unit difference of the explanatory variable of interest [@gelmanAveragePredictiveComparisons2007].
-Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method provides intuitive yet rigorous estimates of effect size in models with non-linear variable transformations (see **Supplementary Text** for further details).
-We performed statistical analysis using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].
-
-\newpage
-
-# Supplementary Text
-
-## Theory
-
-### Sensitivity analysis
+## Sensitivity analysis
 
@@
 
-### Longitudinal gradient of local species richness
+## Longitudinal gradient of local species richness
 
@@
 
-\newpage
+# Empirical data
 
-## Empirical data
-
-### Data selection criteria
+## Data selection criteria
 
@@
 
-### Asymptotic species richness
+## Asymptotic species richness
 
@@
 
-### Average predictive comparison
+## Average predictive comparison
 
@@
 
-## Tables
+# Tables
 
-### Table S1 Simulation parameter (sensitivity analysis)
+## Table S1 Simulation parameter (sensitivity analysis)
 
@@
 
-### Table S2 Simulation parameter (main analysis)
+## Table S2 Simulation parameter (main analysis)
 
@@
 
-### Table S3 Sensitivity analysis for ecosystem size effects
+## Table S3 Sensitivity analysis for ecosystem size effects
 
@@
 
-### Table S4 Sensitivity analysis for ecosystem complexity effects
+## Table S4 Sensitivity analysis for ecosystem complexity effects
 
@@
 
-### Table S5 List of fish species in Hokkaido, Japan
+## Table S5 List of fish species in Hokkaido, Japan
 
@@
 
-### Table S6 List of fish species in Midwest, US
+## Table S6 List of fish species in Midwest, US
 
@@
 
-### Table S7 Average predictive comparisons
+## Table S7 Average predictive comparisons
 
@@
 
-## Figures
+# Figures
 
@@
   j <- i
-  knit_chunk <- paste0("### Figure S", j, " Longitudinal gradient of local species richness ($\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
+  knit_chunk <- paste0("## Figure S", j, " Longitudinal gradient of local species richness ($\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
                        "\n```{r fig", j,", fig.width = 8, fig.height = 6}\n\n h[[",i,"]] \n\n```\n",
@@
   j <- i + 4
-  knit_chunk <- paste0("### Figure S", j, " Influence of ecosystem size ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
+  knit_chunk <- paste0("## Figure S", j, " Influence of ecosystem size ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
                        "\n```{r fig", j,", fig.width = 8, fig.height = 6}\n\n f[[",i,"]] \n\n```\n",
@@
   j <- i + 11
-  knit_chunk <- paste0("### Figure S", j, " Influence of ecosystem complexity ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
+  knit_chunk <- paste0("## Figure S", j, " Influence of ecosystem complexity ($p_{d} = `r param$p_d[",i,"]`$, $\\sigma_{h} = `r param$sigma_h[",i,"]`$, $\\sigma_{l} = `r param$sigma_l[",i,"]`$)", 
                        "\n```{r fig", j,", fig.width = 8, fig.height = 6}\n\n g[[",i,"]] \n\n```\n",
@@
 
-### Figure S19 Correlation structure of explanatory variables
+## Figure S19 Correlation structure of explanatory variables
 
@@
 
-### Figure S20 Sensitivity analysis of asymptotic species richness
+## Figure S20 Sensitivity analysis of asymptotic species richness
 

### 2021-03-14 manuscript_sciad.Rmd
edits: 'Supp Text' to "Supp Mat"

--- 2021-03-14 manuscript_sciad.Rmd
@@
 
-Given the results of extensive sensitivity analysis (**Supplementary Text**), we considered `r n_scenario` simulation scenarios comprising a combination of four landscape and eight ecological scenarios.
+Given the results of extensive sensitivity analysis (**Supplementary Materials**), we considered `r n_scenario` simulation scenarios comprising a combination of four landscape and eight ecological scenarios.
 We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), both of which are defined as standard deviations of normal distributions.
@@
 We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel $\theta$), dispersal probability $p_{d}$, and the maximum value of interspecific competition strength $\alpha_{max}$ (see **Materials and Methods**).
-These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supplementary Text**).
+These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supplementary Materials**).
 Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 400 time steps of initialization and burn-in periods) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
@@
 Therefore, this data set provides an excellent opportunity to examine the generality of our theoretical predictions.
-After careful data selection (see **Materials and Methods** and **Supplementary Text**), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; **Materials and Methods**) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in the Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
+After careful data selection (see **Materials and Methods** and **Supplementary Materials**), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; **Materials and Methods**) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in the Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
 These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at a multi-generation time scale [@comteFishDispersalFlowing2018], while posing challenges to traverse across watersheds (the ocean or lentic habitats; see **Materials and Methods** for watershed definition).
@@
 In particular, the effect of ecosystem complexity was striking in its magnitude.
-Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supplementary Text**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
+Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supplementary Materials**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
 This result is reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018] - the sole theoretical assumption required for the dual control of $\gamma$ diversity to emerge.
@@
 
-We used `r n_scenario` sets of parameter combinations (i.e., simulation scenarios) based on the results of extensive sensitivity analysis (**Supplementary Text**).
+We used `r n_scenario` sets of parameter combinations (i.e., simulation scenarios) based on the results of extensive sensitivity analysis (**Supplementary Materials**).
 The parameter combinations comprises four landscape and eight ecological scenarios.
@@
 For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources [@iowadepartmentofnaturalresourcesBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources [@illinoisenvironmentalprotectionagencyIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency [@minnesotapollutioncontrolagencyDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources [@wisconsindepartmentofnaturalresourcesGuidelinesAssessingFish2018].
-We detailed procedures for initial data selection in **Supplementary Text**.
+We detailed procedures for initial data selection in **Supplementary Materials**.
 
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating asymptotic species richness (**Supplementary Text**).
+Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating asymptotic species richness (**Supplementary Materials**).
 
@@
 The average predictive comparison is an expected change of the response variable per a unit difference of the explanatory variable of interest [@gelmanAveragePredictiveComparisons2007].
-Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method provides intuitive yet rigorous estimates of effect size in models with non-linear variable transformations (see **Supplementary Text** for further details).
+Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method provides intuitive yet rigorous estimates of effect size in models with non-linear variable transformations (see **Supplementary Materials** for further details).
 We performed statistical analysis using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].

### 2021-03-14 supplementary_information_sciad.Rmd
edits: supp materials, minor edits

@@
 ```
-The weight factor should represent the likelihood of $u$ changing from $u_i$ to $u_j$ with a common $v = v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$).
+The weight factor should represent the likelihood of $u$ changing from $u_i$ to $u_j$ with a common $v = v_i$ ($v_i$ is in general a vector of explanatory variables for data point $i$).
 We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:
@@
 where $\Omega_v^{-1}$ is the inverse of the variance-covariance matrix of $v$.
-The function gives the maximum weight for a pair of $u_i$ and $u_j$ if $v_i = v_j$ ($v=v_i$ when $u = u_i$) while giving a less weight as the Mahalanobis distance between $v_i$ and $v_j$ increases.
+Note that $v=v_i$ when $u = u_i$, and $v=v_j$ when $u = u_j$.
+The function gives the maximum weight for a pair of $u_i$ and $u_j$ if $v_i = v_j$ while giving a less weight as the Mahalanobis distance between $v_i$ and $v_j$ increases.
 This property makes sense because our goal is to approximate the probability of transition from $u_i$ to $u_j$ with a common $v$ (i.e., $v_i = v_j$).

### 2021-03-15 manuscript_sciad.Rmd
edits: methods, minor reorganization
edits: maintext, minor edits
edits: maintext, minor edit

@@
 We found decisive support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`) despite the substantial difference in fish fauna between the study regions.
-The estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions (**Table 1 and Figure 4**).
+The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) at a log-log scale (i.e., power-law), and these patterns were consistent across the study regions (**Table 1 and Figure 4**).
+Thus, watershed-scale riverine biodiversity obeys the general scaling law along the two orthogonal dimensions of ecosystem structure: size and complexity.
 In particular, the effect of ecosystem complexity was striking in its magnitude.
 Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supplementary Materials**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
-This result is reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018] - the sole theoretical assumption required for the dual control of $\gamma$ diversity to emerge.
+This result is reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018] - the sole theoretical assumption required for the dual scaling of $\gamma$ diversity to emerge.
 Further, the consistent patterns across geographic regions with distinct fish fauna suggest that ecological traits of species in metacommunities may have a minor effect on the scaling relationships, as predicted by our theory.
@@
 The generalization of our findings in spatially complex ecosystems represents a frontier for future research.
+
+\newpage
 
@@
 For landscape scenarios, we used four combinations of environmental variation at headwaters ($\sigma_h = 0.01, 1$) and the degree of local environmental noise ($\sigma_l = 0.01, 1$).
-The inequality of $\sigma_h$ and $\sigma_l$ controls the relationship between branching complexity and habitat heterogeneity (**Figures 1A and 1B**).
+The inequality of $\sigma_h$ and $\sigma_l$ controls the relationship between branching complexity and habitat heterogeneity (**Figure 1A and B**).
 For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`).
@@
 We considered watersheds as independent replicates of metacommunities if the river network flows into one of the following: the ocean, a large lake/reservoir ($\ge$ 10 km² in the areal area) or a large river that may represent lentic habitats ($\ge$ 5000 km² in the watershed area).
-Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating asymptotic species richness (**Supplementary Materials**).
-
 We estimated $\alpha$, $\beta$, and $\gamma$ diversity at each watershed.
@@
 We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016].
+Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating asymptotic species richness (**Supplementary Materials**).
 We assessed the completeness of the observed species richness based on sample coverage, which is the total proportional abundances of observed species to the whole metacommunity [@chaoRarefactionExtrapolationHill2014a].

### 2021-03-16 manuscript_sciad.Rmd
edits: maintext, minor

@@
 
-Here, we show that ecosystem size and complexity play comparable roles in controlling biodiversity patterns in rivers - a prime example of complex branching ecosystems.
+Here, we show that ecosystem size and complexity play comparable roles in scaling biodiversity patterns in rivers - a prime example of complex branching ecosystems.
 Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018].
@@
 In the global model, we assumed that effects of ecosystem size (watershed area) and complexity (branching probability) are constant across the two regions (i.e., fixed slopes).
-Meanwhile, the region-specific model assumes region-specific slopes of ecosystem size and complexity (**Materials and Methods**).
+Meanwhile, the region-specific model assumes different slopes of ecosystem size and complexity between the regions (**Materials and Methods**).
 We compared the support of these competing models using the Bayes factor, a measure of the strength of evidence in favor of one model over the alternative.
@@
 
-We found decisive support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`) despite the substantial difference in fish fauna between the study regions.
-The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) at a log-log scale (i.e., power-law), and these patterns were consistent across the study regions (**Table 1 and Figure 4**).
-Thus, watershed-scale riverine biodiversity obeys the general scaling law along the two orthogonal dimensions of ecosystem structure: size and complexity.
+We found decisive support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`) despite the substantial difference in fish fauna between the study regions (**Tables S5 and S6**).
+The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) on a log-log scale (i.e., power-law), and these patterns were consistent across the study regions (**Table 1 and Figure 4**).
+Thus, watershed-scale riverine biodiversity likely obeys the general scaling law along the two orthogonal dimensions of ecosystem structure, i,e, size and complexity.
 In particular, the effect of ecosystem complexity was striking in its magnitude.
@@
 This result is reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018] - the sole theoretical assumption required for the dual scaling of $\gamma$ diversity to emerge.
-Further, the consistent patterns across geographic regions with distinct fish fauna suggest that ecological traits of species in metacommunities may have a minor effect on the scaling relationships, as predicted by our theory.
+Further, the consistent patterns across the geographic regions with distinct evolutionary histories imply that ecological traits of species in metacommunities may have a minor effect on the scaling relationships, as predicted by our theory.
 
@@
 
-Using theory and extensive community data, our study provides the strong evidence that ecosystem size and complexity play equally important roles in regulating riverine biodiversity.
+Using theory and extensive community data, our study provides the strong evidence that ecosystem size and complexity play equally important roles in shaping riverine biodiversity.
 In particular, the emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
@@
 
-While the prevailing evidence supports the importance of ecosystem size in scaling biodiversity patterns [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
+While the prevailing evidence supports the importance of ecosystem size in biodiversity relationships [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
 However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
@@
 We thank Jacques Finlay for his constructive comments on the earlier version of the manuscript.
-This research was supported by National Science Foundation through a Water Sustainability and Climate Program Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1), and the University of North Carolina at Greensboro through a start-up fund.
+This material is based upon work supported by the National Science Foundation through a Water Sustainability and Climate Program Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1), and the University of North Carolina at Greensboro through a start-up fund.
 

### 2021-03-16 figure.Rmd
edits: final edits for manuscripts etc
Update figure.Rmd
edits: figure caption, minor

@@
 Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values).
-Panel A and B show distinct landscape scenarios.
+Panels A and B show distinct landscape scenarios.
 Environmental variation at headwaters $\\sigma_{h}$ exceeds the degree of local environmental noise $\\sigma_{l}$ in A ($\\sigma_{h} = 1, \\sigma_{l} = 0.01$), while the opposite is true in B ($\\sigma_{h} = 0.01, \\sigma_{l} = 1$).
@@
 ```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
-Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals.
+Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
 Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
@@
 ```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
-Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals.
+Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
 Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
@@
 ```{r, fig.height=6, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (left), $\\beta$ (middle), and $\\gamma$ diversity (right) in Hokkaido and Midwest regions.
-Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the linear regression models."}
+Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models."}
 

### 2021-03-16 coverletter.Rmd
Update coverletter.Rmd

@@
 
-We are excited to submit our manuscript entitled 'Ecosystem size and complexity dictate riverine biodiversity' to PNAS.
+We are excited to submit our manuscript entitled 'Ecosystem size and complexity dictate riverine biodiversity' to *Science Advances*.
 Given the unprecedented rate of global biodiversity loss, a crucial task for ecologists is to guide conservation efforts by identifying key environmental factors that regulate biodiversity.
-A prevailing wisdom suggests that species diversity is primarily demined by area; larger ecosystems support more species (i.e., the Species Area Relationship; SAR).
+A prevailing thought suggests that species diversity is primarily determined by area; larger ecosystems support more species (i.e., the Species Area Relationship; the SAR).
 This ecological pattern has been found in many taxa and geographic regions, forming the foundation of current conservation schemes.
 For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas, which encompass more than 30 million km2 globally.
-However, what is largely overlooked in current biodiversity research is the role of a 'scale-invariant' complexity of ecosystem's geometric structure (hereafter, 'ecosystem complexity').
-Since ecosystem complexity is independent of spatial scale or ecosystem size, existing theories are inappropriate to predict biodiversity patterns in spatially complex ecosystems.
+However, what is largely overlooked in current biodiversity research is the role of 'scale-invariant' complexity of ecosystem's geometric structure (hereafter, 'ecosystem complexity').
+Since ecosystem complexity is independent of spatial scale or ecosystem size, existing theories may be inappropriate to predict biodiversity patterns in spatially complex ecosystems.
 
-Here, we offer a synthetic framework integrating ecosystem size and complexity influences on biodiversity patterns in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few.
-In this widespread yet largely overlooked fractal ecosystem's geometry, branching patterns remain constant across a wide range of spatial scales.
+Here, we offer a synthetic framework integrating ecosystem size and complexity influences on biodiversity patterns in branching ecosystems, such as rivers, trees, and mountain ranges, to name just a few.
+In this widespread yet largely overlooked landscape geometry, branching patterns remain constant across a wide range of spatial scales.
 Even so, the complexity of branching patterns forms a physical template providing a wide spectrum of environmental niches for living organisms.
-In this research, using theory and extensive fish community data from two distinct geographic regions, **we found that ecosystem size and complexity play comparable roles in regulating riverine biodiversity; ecosystem size alone was insufficient to predict biodiversity patterns.** Larger and more branched 'complex' river networks supported greater species richness due to increased space and habitat heterogeneity.
+In this research, using theory and extensive fish community data from two geographic regions, **we found that ecosystem size and complexity play comparable roles in scaling riverine biodiversity - ecosystem size alone was insufficient to predict biodiversity patterns.** Larger and more branched 'complex' river networks supported greater species richness due to increased space and habitat heterogeneity.
 In particular, the effect of ecosystem complexity was striking in its magnitude.
 A unit increase of ecosystem complexity (the prevalence of branching) resulted in an increase of species diversity that would require 1911 km2 in the areal area.
-Further, these patterns have consistently emerged regardless of ecological traits of species and geographic regions, suggesting that the dual control of riverine biodiversity may be pervasive across taxonomic groups and geographic regions.
+Further, these relationships followed a general power-law scaling across the study regions despite hosting different species with distinct evolutionary histories (Japan and US); therefore, the dual control of riverine biodiversity may be pervasive.
 
-Our research will attract a broad audience of PNAS for the following reasons.
+Our research will attract a broad audience of your journal for the following reasons.
 First, our proposed framework may apply beyond branching ecosystems as both ecosystem size and complexity represent a physical template of the ecosystem's environmental heterogeneity.
-Second, the results of the present study provide the ecological foundation for complexity-based ecosystem management - an important perspective overlooked in the current schemes of biodiversity conservation.
+Second, the results of the present study provide the ecological foundation for complexity-based ecosystem management - an important perspective overlooked in current schemes of biodiversity conservation.
 Hence, we have confidence that our research not only provides fundamental insights into regulating factors of biodiversity but also has far-reaching implications for biodiversity conservation.

### 2021-03-17 manuscript_sciad.Rmd
edits: maintext, minor

@@
 Therefore, ecosystem size and complexity can increase $\gamma$ diversity via enhanced species sorting or mass effects, and which takes primacy is dependent on the degree of dispersal limitation.
-These patterns were consistent across different levels of dispersal probabilities (**Figures S5 and S12**).
+These patterns were qualitatively similar across different levels of dispersal probabilities (**Figures S5 and S12**).
 The strength of competition decreased the maximum of $\alpha$ diversity but did not change the scaling relationships with ecosystem properties (**Figures 2 and 3**).
@@
 The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) on a log-log scale (i.e., power-law), and these patterns were consistent across the study regions (**Table 1 and Figure 4**).
-Thus, watershed-scale riverine biodiversity likely obeys the general scaling law along the two orthogonal dimensions of ecosystem structure, i,e, size and complexity.
+Thus, watershed-scale riverine biodiversity likely obeys a general scaling law along the two orthogonal dimensions of ecosystem structure, i,e, size and complexity.
 In particular, the effect of ecosystem complexity was striking in its magnitude.

### 2021-03-17 supplementary_information_sciad.Rmd
edits: si, minor

@@
 In general, $\delta_u$ rests on $u^{(1)}$ and $u^{(2)}$ (the lower and higher points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$.
-Therefore, Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007] defined the *average predictive comparison* $\Delta_u$, the mean value of $\delta_u$ over specified distributions of the inputs and model parameters:
+Therefore, Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007] defined the *average predictive comparison* $\Delta_u$ as "the mean value of $\delta_u$ over some specified distribution of the inputs and parameters":
 

### 2021-03-23 manuscript_pnas.Rmd
Create manuscript_pnas.Rmd

--- 2021-03-17 manuscript_sciad.Rmd
@@
 ---
-title: "Ecosystem size and complexity dictate riverine biodiversity"
+title: "Emergent dual scaling of riverine biodiversity"
 output:
@@
     latex_engine: xelatex
-csl: science.csl
+csl: pnas.csl
 knit: (function(inputFile, encoding) {
@@
 
-**Abstract:** Larger ecosystems support more species; this ubiquitous pattern is the foundation of current conservation schemes.
+**Abstract:** A prevailing thought suggests that species richness increases with area in a decelerating way; this ubiquitous power-law scaling, the species-area relationship, has formed the foundation of many conservation strategies.
+In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because the scale-invariant complexity of fractal ecosystem structure may drive ecological dynamics in space.
+Here, we use theory and analysis of extensive fish community data from two distinct geographic regions (Hokkaido Island in Japan and the midwestern United States) to show that ecosystem size and complexity play equally-important roles in scaling biodiversity in rivers.
+The recurrent merging of various streams and rivers forms fractal branching systems, where the prevalence of branching (ecosystem complexity) represents a macro-scale control of the ecosystem's habitat heterogeneity.
+In the meantime, ecosystem size dictates metacommunity size and total habitat diversity, two factors regulating biodiversity in nature.
+Our theory predicted that, regardless of simulated species' traits, larger and more branched 'complex' networks supported greater species richness due to increased space and environmental heterogeneity.
+Both relationships were linear on a log-log scale, suggesting the general power-law scaling along the two orthogonal dimensions of ecosystem structure.
+In support of this theoretical prediction, the robust dual power-law scaling of riverine fish diversity has consistently emerged across the study regions despite hosting different fauna with distinct evolutionary histories.
+The dual scaling of biodiversity may be a pervasive emergent property of branching networks with important implications for biodiversity conservation.
+
+**Significance** Larger ecosystems support more species; this ubiquitous pattern is the foundation of current conservation schemes.
 However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such complexity in controlling biodiversity is largely unknown.
-Here, we use theory and extensive fish community data from two distinct geographic regions (Japan and United States) to show that ecosystem size and complexity dictate riverine biodiversity.
+Here, we use theory and extensive fish community data to show that ecosystem size and complexity dictate riverine biodiversity.
 We found that larger and more branched 'complex' river networks harbored greater species richness due to increased space and environmental heterogeneity.
 The complexity effect was comparable to the size effect, and this pattern has emerged regardless of ecological contexts.
-The dual control of biodiversity may be a pervasive feature that has far-reaching implications for biodiversity conservation.
+The dual scaling of biodiversity may be a pervasive feature that has far-reaching implications for biodiversity conservation.
+
+**Key words:** metacommunity, species diversity, scaling law, network theory, freshwater
 
@@
 
-Using theory and extensive community data, our study provides the strong evidence that ecosystem size and complexity play equally important roles in shaping riverine biodiversity.
+Using theory and extensive community data, our study provides strong evidence that ecosystem size and complexity play equally important roles in shaping riverine biodiversity.
 In particular, the emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.

### 2021-03-23 coverletter.Rmd
Update coverletter.Rmd

--- 2021-03-14 coverletter.Rmd
@@
 
-We are excited to submit our manuscript entitled 'Ecosystem size and complexity dictate riverine biodiversity' to PNAS.
-Given the unprecedented rate of global biodiversity loss, a crucial task for ecologists is to guide conservation efforts by identifying key environmental factors that regulate biodiversity.
-A prevailing wisdom suggests that species diversity is primarily demined by area; larger ecosystems support more species (i.e., the Species Area Relationship; SAR).
-This ecological pattern has been found in many taxa and geographic regions, forming the foundation of current conservation schemes.
-For example, conservation ecologists have used SAR estimates to design marine and terrestrial protected areas, which encompass more than 30 million km2 globally.
-However, what is largely overlooked in current biodiversity research is the role of a 'scale-invariant' complexity of ecosystem's geometric structure (hereafter, 'ecosystem complexity').
-Since ecosystem complexity is independent of spatial scale or ecosystem size, existing theories are inappropriate to predict biodiversity patterns in spatially complex ecosystems.
+We are excited to submit our manuscript entitled 'Emergent dual scaling of riverine biodiversity' to *Proceedings of the National Academy Sciences*.
 
-Here, we offer a synthetic framework integrating ecosystem size and complexity influences on biodiversity patterns in branching ecosystems, including rivers, trees, and mountain ranges, to name just a few.
-In this widespread yet largely overlooked fractal ecosystem's geometry, branching patterns remain constant across a wide range of spatial scales.
-Even so, the complexity of branching patterns forms a physical template providing a wide spectrum of environmental niches for living organisms.
-In this research, using theory and extensive fish community data from two distinct geographic regions, **we found that ecosystem size and complexity play comparable roles in regulating riverine biodiversity; ecosystem size alone was insufficient to predict biodiversity patterns.** Larger and more branched 'complex' river networks supported greater species richness due to increased space and habitat heterogeneity.
+In the Anthropocene, it is more imperative than ever to identify ecological factors that underpin diverse ecological communities in nature.
+Much attention has been paid to the ubiquitous power-law scaling of species richness and area, in which species richness increases with area in a decelerating way.
+Ecologists have used this ecological *law* to inform many conservation strategies, including marine and terrestrial protected areas that currently encompass > 30 million km^2^ globally.
+In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because 'scale-invariant' complexity of ecosystem structure may drive ecological dynamics in space.
+Branching river networks are an outstanding example of such complex ecosystems, where geometric ecosystem structure (e.g., branching patterns) remains constant across a wide range of spatial scales.
+
+Here, we used theory and analysis of large fish community data to show that **ecosystem complexity of branching networks (measured as the prevalence of branching) plays a crucial role in scaling metacommunity-level biodiversity in rivers (**$\gamma$ **diversity); ecosystem size and other macro-scale drivers (e.g., climates and land use patterns) alone were insufficient to describe biodiversity patterns in complex river networks.** Our theory predicted that, regardless of simulated species' traits, more branched 'complex' river networks supported greater species richness due to increased habitat heterogeneity.
+This relationship had a characteristic of power-law, revealing the overlooked scaling relationship in complex branching networks.
+Importantly, the complexity effect was comparable to the size effect - hence, riverine biodiversity should follow a dual scaling law along the two orthogonal dimensions of ecosystem structure, i.e., size and scale-invariant complexity.
+
+We confirmed the theoretical predictions using extensive fish community data, which included 180 replicates of metacommunities (i.e., watersheds) across two geographic regions (Japan and the US).
+The dual scaling of riverine fish diversity has consistently emerged across the study regions despite hosting different fish fauna with distinct evolutionary histories.
+This result agrees elegantly with theoretical predictions, in which species' traits played a minor role in shaping the dual power-law scaling.
 In particular, the effect of ecosystem complexity was striking in its magnitude.
-A unit increase of ecosystem complexity (the prevalence of branching) resulted in an increase of species diversity that would require 1911 km2 in the areal area.
-Further, these patterns have consistently emerged regardless of ecological traits of species and geographic regions, suggesting that the dual control of riverine biodiversity may be pervasive across taxonomic groups and geographic regions.
+A unit increase of ecosystem complexity (the prevalence of branching) resulted in an increase of species diversity that would require 1911 km^2^ in the areal area.
 
-Our research will attract a broad audience of PNAS for the following reasons.
-First, our proposed framework may apply beyond branching ecosystems as both ecosystem size and complexity represent a physical template of the ecosystem's environmental heterogeneity.
-Second, the results of the present study provide the ecological foundation for complexity-based ecosystem management - an important perspective overlooked in the current schemes of biodiversity conservation.
-Hence, we have confidence that our research not only provides fundamental insights into regulating factors of biodiversity but also has far-reaching implications for biodiversity conservation.
+Our study distinguishes itself from other studies in three ways.
+First, we offer a synthetic framework integrating ecosystem size and complexity influences on biodiversity, which should apply beyond branching ecosystems.
+Second, unlike most previous studies focused on local biodiversity patterns ($\alpha$ diversity), our empirical analysis used metacommunities as replicates of statistical analysis.
+Therefore, this study provides crucial insights into how ecological communities are structured *at the metacommunity level*.
+Lastly, the present study provides the foundation for complexity-based ecosystem management - an important perspective overlooked in current conservation schemes.
+Hence, we have confidence that our research provides fundamental insights into regulating factors of biodiversity and has far-reaching implications for biodiversity conservation.
 

### 2021-03-23 coverletter.Rmd
Update coverletter.Rmd

@@
 ---
-output: pdf_document
+output: word_document
 knit: (function(inputFile, encoding) {
@@
 ---
+
+![](images/uncgreensboro_DoB_h_pms-c.png){width="200"}
 
@@
 Much attention has been paid to the ubiquitous power-law scaling of species richness and area, in which species richness increases with area in a decelerating way.
-Ecologists have used this ecological *law* to inform many conservation strategies, including marine and terrestrial protected areas that currently encompass > 30 million km^2^ globally.
-In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because 'scale-invariant' complexity of ecosystem structure may drive ecological dynamics in space.
+Ecologists have used this ecological *law* to inform many conservation strategies, including marine and terrestrial protected areas that currently encompass \> 30 million km^2^ globally.
+In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because 'scale-invariant' complexity of fractal ecosystem structure may drive ecological dynamics in space.
 Branching river networks are an outstanding example of such complex ecosystems, where geometric ecosystem structure (e.g., branching patterns) remains constant across a wide range of spatial scales.
 
-Here, we used theory and analysis of large fish community data to show that **ecosystem complexity of branching networks (measured as the prevalence of branching) plays a crucial role in scaling metacommunity-level biodiversity in rivers (**$\gamma$ **diversity); ecosystem size and other macro-scale drivers (e.g., climates and land use patterns) alone were insufficient to describe biodiversity patterns in complex river networks.** Our theory predicted that, regardless of simulated species' traits, more branched 'complex' river networks supported greater species richness due to increased habitat heterogeneity.
+Here, we used theory and analysis of large fish community data to show that **ecosystem complexity of branching networks (measured as the prevalence of branching) plays a crucial role in scaling metacommunity-level biodiversity in rivers (**$\gamma$ **diversity); ecosystem size and other macro-scale drivers (e.g., climates and land use patterns) were insufficient to describe riverine biodiversity patterns.** Our theory predicted that, regardless of simulated species' traits, more branched 'complex' river networks supported greater species richness due to increased habitat heterogeneity.
 This relationship had a characteristic of power-law, revealing the overlooked scaling relationship in complex branching networks.
@@
 The dual scaling of riverine fish diversity has consistently emerged across the study regions despite hosting different fish fauna with distinct evolutionary histories.
-This result agrees elegantly with theoretical predictions, in which species' traits played a minor role in shaping the dual power-law scaling.
-In particular, the effect of ecosystem complexity was striking in its magnitude.
+This result agrees elegantly with our theoretical predictions, in which species' traits played a minor role in shaping the dual power-law scaling.
+Further, the effect of ecosystem complexity was striking in its magnitude.
 A unit increase of ecosystem complexity (the prevalence of branching) resulted in an increase of species diversity that would require 1911 km^2^ in the areal area.

### 2021-03-23 manuscript_pnas.Rmd
edits: maintext minor

@@
 
-**Abstract:** A prevailing thought suggests that species richness increases with area in a decelerating way; this ubiquitous power-law scaling, the species-area relationship, has formed the foundation of many conservation strategies.
+**Abstract:** A prevailing paradigm suggests that species richness increases with area in a decelerating way; this ubiquitous power-law scaling, the species-area relationship, has formed the foundation of many conservation strategies.
 In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because the scale-invariant complexity of fractal ecosystem structure may drive ecological dynamics in space.
@@
 Our theory predicted that, regardless of simulated species' traits, larger and more branched 'complex' networks supported greater species richness due to increased space and environmental heterogeneity.
-Both relationships were linear on a log-log scale, suggesting the general power-law scaling along the two orthogonal dimensions of ecosystem structure.
+Both relationships were linear on a log-log scale, suggesting the general power-law scaling along the two orthogonal dimensions of ecosystem structure, i.e., size and complexity.
 In support of this theoretical prediction, the robust dual power-law scaling of riverine fish diversity has consistently emerged across the study regions despite hosting different fauna with distinct evolutionary histories.
@@
 
-Given the results of extensive sensitivity analysis (**Supplementary Materials**), we considered `r n_scenario` simulation scenarios comprising a combination of four landscape and eight ecological scenarios.
+Given the results of extensive sensitivity analysis (**Supporting Information**), we considered `r n_scenario` simulation scenarios comprising a combination of four landscape and eight ecological scenarios.
 We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), both of which are defined as standard deviations of normal distributions.
@@
 We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel $\theta$), dispersal probability $p_{d}$, and the maximum value of interspecific competition strength $\alpha_{max}$ (see **Materials and Methods**).
-These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supplementary Materials**).
+These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supporting Information**).
 Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 400 time steps of initialization and burn-in periods) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
@@
 Therefore, this data set provides an excellent opportunity to examine the generality of our theoretical predictions.
-After careful data selection (see **Materials and Methods** and **Supplementary Materials**), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; **Materials and Methods**) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in the Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
+After careful data selection (see **Materials and Methods** and **Supporting Information**), we estimated $\alpha$, $\beta$, and $\gamma$ diversity (asymptotic species richness; **Materials and Methods**) at `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (`r nrow(wsd_subset[[1]])` in Hokkaido and `r nrow(wsd_subset[[2]])` in the Midwest), each of which comprised $\ge$ 10 sites of presence-absence fish community data (a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites).
 These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at a multi-generation time scale [@comteFishDispersalFlowing2018], while posing challenges to traverse across watersheds (the ocean or lentic habitats; see **Materials and Methods** for watershed definition).
@@
 In particular, the effect of ecosystem complexity was striking in its magnitude.
-Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supplementary Materials**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
+Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supporting Information**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
 This result is reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018] - the sole theoretical assumption required for the dual scaling of $\gamma$ diversity to emerge.
@@
 
-We used `r n_scenario` sets of parameter combinations (i.e., simulation scenarios) based on the results of extensive sensitivity analysis (**Supplementary Materials**).
+We used `r n_scenario` sets of parameter combinations (i.e., simulation scenarios) based on the results of extensive sensitivity analysis (**Supporting Information**).
 The parameter combinations comprises four landscape and eight ecological scenarios.
@@
 For the Midwest, we assembled fish community data collected by the Iowa Department of Natural Resources [@iowadepartmentofnaturalresourcesBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources [@illinoisenvironmentalprotectionagencyIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency [@minnesotapollutioncontrolagencyDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources [@wisconsindepartmentofnaturalresourcesGuidelinesAssessingFish2018].
-We detailed procedures for initial data selection in **Supplementary Materials**.
+We detailed procedures for initial data selection in **Supporting Information**.
 
@@
 We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016].
-Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating asymptotic species richness (**Supplementary Materials**).
+Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating asymptotic species richness (**Supporting Information**).
 We assessed the completeness of the observed species richness based on sample coverage, which is the total proportional abundances of observed species to the whole metacommunity [@chaoRarefactionExtrapolationHill2014a].
@@
 The average predictive comparison is an expected change of the response variable per a unit difference of the explanatory variable of interest [@gelmanAveragePredictiveComparisons2007].
-Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method provides intuitive yet rigorous estimates of effect size in models with non-linear variable transformations (see **Supplementary Materials** for further details).
+Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method provides intuitive yet rigorous estimates of effect size in models with non-linear variable transformations (see **Supporting Information** for further details).
 We performed statistical analysis using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].

### 2021-03-23 supplementary_information_pnas.Rmd
Create supplementary_information_pnas.Rmd

--- 2021-03-17 supplementary_information_sciad.Rmd
@@
 title: |
-  | Supplementary Materials for:
-  | Ecosystem size and complexity dictate riverine biodiversity
+  | Supporting Information for:
+  | Emergent dual scaling of riverine biodiversity
 author:
@@
 bibliography: references.bib
-csl: science.csl
+csl: pnas.csl
 knit: (function(inputFile, encoding) {

### 2021-03-23 manuscript_pnas.Rmd
edits: maintext, minor

@@
 Our theory predicted that, regardless of simulated species' traits, larger and more branched 'complex' networks supported greater species richness due to increased space and environmental heterogeneity.
-Both relationships were linear on a log-log scale, suggesting the general power-law scaling along the two orthogonal dimensions of ecosystem structure, i.e., size and complexity.
+Both relationships were linear on a log-log scale, indicating a general power-law scaling along the two orthogonal dimensions of ecosystem structure, i.e., size and complexity.
 In support of this theoretical prediction, the robust dual power-law scaling of riverine fish diversity has consistently emerged across the study regions despite hosting different fauna with distinct evolutionary histories.
@@
 **Significance** Larger ecosystems support more species; this ubiquitous pattern is the foundation of current conservation schemes.
-However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such complexity in controlling biodiversity is largely unknown.
+However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such complexity in scaling biodiversity patterns is largely unknown.
 Here, we use theory and extensive fish community data to show that ecosystem size and complexity dictate riverine biodiversity.
@@
 However, most empirical research has explored the consequences of branching complexity for local community structure [@erosLandscapeEcologyRivers2019] or has relied solely on theoretical arguments with limited replications of branching architecture [@holtRoleBranchingMaintenance2018].
-At present, we lack a comprehensive evaluation of how branching complexity controls biodiversity patterns at the metacommunity level.
+At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity patterns at the metacommunity level.
 Filling this knowledge gap may provide common ground for achieving successful conservation in spatially complex ecosystems, where accelerated species loss threatens the delivery of ecosystem services [@reidEmergingThreatsPersistent2019].
@@
 Further, the proposed framework may be extended to other aspects of biodiversity; for example, a logical next step is to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002; @suHumanImpactsGlobal2021] and shifts in community assembly processes [@chaseStochasticCommunityAssembly2010].
-Recognizing the dual control of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
+Recognizing the dual scaling of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
 The generalization of our findings in spatially complex ecosystems represents a frontier for future research.

### 2021-03-23 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 Both relationships were linear on a log-log scale, indicating a general power-law scaling along the two orthogonal dimensions of ecosystem structure, i.e., size and complexity.
-In support of this theoretical prediction, the robust dual power-law scaling of riverine fish diversity has consistently emerged across the study regions despite hosting different fauna with distinct evolutionary histories.
+In support of this theoretical prediction, the dual power-law scaling of riverine fish diversity has consistently emerged across the study regions despite hosting different fauna with distinct evolutionary histories.
 The dual scaling of biodiversity may be a pervasive emergent property of branching networks with important implications for biodiversity conservation.

### 2021-03-24 manuscript_pnas.Rmd
edits: maintext, emphasize scaling law

@@
 In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because the scale-invariant complexity of fractal ecosystem structure may drive ecological dynamics in space.
-Here, we use theory and analysis of extensive fish community data from two distinct geographic regions (Hokkaido Island in Japan and the midwestern United States) to show that ecosystem size and complexity play equally-important roles in scaling biodiversity in rivers.
+Here, we use theory and analysis of extensive fish community data from two distinct geographic regions (Hokkaido Island in Japan and the midwestern United States) to show the emergence of robust scaling law along the two orthogonal dimensions of ecosystem size and complexity in rivers.
 The recurrent merging of various streams and rivers forms fractal branching systems, where the prevalence of branching (ecosystem complexity) represents a macro-scale control of the ecosystem's habitat heterogeneity.
@@
 Our theory predicted that, regardless of simulated species' traits, larger and more branched 'complex' networks supported greater species richness due to increased space and environmental heterogeneity.
-Both relationships were linear on a log-log scale, indicating a general power-law scaling along the two orthogonal dimensions of ecosystem structure, i.e., size and complexity.
+Both relationships were linear on a log-log scale, indicating a robust scaling law along the dimensions of size and complexity.
 In support of this theoretical prediction, the dual power-law scaling of riverine fish diversity has consistently emerged across the study regions despite hosting different fauna with distinct evolutionary histories.
@@
 
-Here, we show that ecosystem size and complexity play comparable roles in scaling biodiversity patterns in rivers - a prime example of complex branching ecosystems.
+Here, we show the emergence of robust scaling law along the two orthogonal dimensions of ecosystem size and complexity in rivers - a prime example of complex branching ecosystems.
 Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018].
@@
 Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**).
-The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios (compare panels in **Figures 2 and 3**).
+The power-law relationships (i.e., linear in a log-log scale) have emerged along the both axes of ecosystem size and complexity irrespective of ecological scenarios (compare panels in **Figures 2 and 3**).
 Importantly, the impact of ecosystem complexity was comparable to that of ecosystem size.
-Hence, regardless of ecological scenarios, ecosystem size and complexity are likely to be equally important in regulating $\gamma$ diversity.
+Hence, regardless of ecological scenarios, ecosystem size and complexity are likely to be equally important in scaling $\gamma$ diversity.
 
@@
 The strength of competition decreased the maximum of $\alpha$ diversity but did not change the scaling relationships with ecosystem properties (**Figures 2 and 3**).
-In summary, our theory highlights how apparently similar patterns in $\gamma$ diversity emerge through different ecological pathways.
+In summary, our theory highlights how apparently similar scaling in $\gamma$ diversity emerge through different ecological pathways.
 
@@
 We found decisive support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`) despite the substantial difference in fish fauna between the study regions (**Tables S5 and S6**).
-The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) on a log-log scale (i.e., power-law), and these patterns were consistent across the study regions (**Table 1 and Figure 4**).
-Thus, watershed-scale riverine biodiversity likely obeys a general scaling law along the two orthogonal dimensions of ecosystem structure, i,e, size and complexity.
-In particular, the effect of ecosystem complexity was striking in its magnitude.
+The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) on a log-log scale (i.e., power-law), and the estimated scaling exponents were consistent across the study regions (`r op(coef(fit$gamma$model)[2])` for watershed area and `r op(coef(fit$gamma$model)[3])` for branching probability; **Table 1 and Figure 4**).
+Thus, watershed-scale riverine biodiversity likely obeys a general scaling law along the two orthogonal dimensions of ecosystem size and complexity.
+The effect of ecosystem complexity was striking in its magnitude.
 Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supporting Information**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
@@
 Using theory and extensive community data, our study provides strong evidence that ecosystem size and complexity play equally important roles in shaping riverine biodiversity.
-In particular, the emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
+In particular, the emergent power-law scaling between ecosystem complexity and biodiversity points to several important avenues for riverine biodiversity conservation.
 First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.

### 2021-03-24 coverletter.Rmd
Update coverletter.Rmd

@@
 ---
-output: word_document
+output: pdf_document
 knit: (function(inputFile, encoding) {
@@
 
-We are excited to submit our manuscript entitled 'Emergent dual scaling of riverine biodiversity' to *Proceedings of the National Academy Sciences*.
+We are excited to submit our manuscript entitled '*Emergent dual scaling of riverine biodiversity*' to *Proceedings of the National Academy Sciences*.
 
 In the Anthropocene, it is more imperative than ever to identify ecological factors that underpin diverse ecological communities in nature.
-Much attention has been paid to the ubiquitous power-law scaling of species richness and area, in which species richness increases with area in a decelerating way.
-Ecologists have used this ecological *law* to inform many conservation strategies, including marine and terrestrial protected areas that currently encompass \> 30 million km^2^ globally.
+Much attention has been paid to the ubiquitous power-law scaling between species richness and area, in which species richness increases with area in a decelerating way.
 In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because 'scale-invariant' complexity of fractal ecosystem structure may drive ecological dynamics in space.
@@
 
-Here, we used theory and analysis of large fish community data to show that **ecosystem complexity of branching networks (measured as the prevalence of branching) plays a crucial role in scaling metacommunity-level biodiversity in rivers (**$\gamma$ **diversity); ecosystem size and other macro-scale drivers (e.g., climates and land use patterns) were insufficient to describe riverine biodiversity patterns.** Our theory predicted that, regardless of simulated species' traits, more branched 'complex' river networks supported greater species richness due to increased habitat heterogeneity.
-This relationship had a characteristic of power-law, revealing the overlooked scaling relationship in complex branching networks.
-Importantly, the complexity effect was comparable to the size effect - hence, riverine biodiversity should follow a dual scaling law along the two orthogonal dimensions of ecosystem structure, i.e., size and scale-invariant complexity.
+In this research, we used theory and analysis of extensive fish data to show that the scale-invariant complexity of branching networks is an alternative dimension of ecosystem structure to dictate riverine biodiversity patterns.
+Theory and empirical analysis agreed that, **regardless of ecological traits of constituent species, riverine biodiversity exhibited a dual scaling law along the two orthogonal dimensions of ecosystem size and scale-invariant complexity.** An elegant consistency of theoretical and empirical results provided strong evidence that the dual scaling of biodiversity is a pervasive yet overlooked feature of complex ecosystems with important implications for biodiversity conservation.
 
-We confirmed the theoretical predictions using extensive fish community data, which included 180 replicates of metacommunities (i.e., watersheds) across two geographic regions (Japan and the US).
-The dual scaling of riverine fish diversity has consistently emerged across the study regions despite hosting different fish fauna with distinct evolutionary histories.
-This result agrees elegantly with our theoretical predictions, in which species' traits played a minor role in shaping the dual power-law scaling.
-Further, the effect of ecosystem complexity was striking in its magnitude.
-A unit increase of ecosystem complexity (the prevalence of branching) resulted in an increase of species diversity that would require 1911 km^2^ in the areal area.
+Our study distinguishes itself from previous studies in three important ways.
+(1) Our study is the first to show the *dual* scaling law of biodiversity.
+Notably, this pattern has emerged irrespective of ecological contexts or geographic regions, emphasizing the generality of our finding.
+(2) Our empirical analysis used *watershed ecosystems* as individual replicates of statistical analysis; our data set included 180 watersheds with 6605 sites across Japan and the US and this extensive data enabled us to perform the ecosystem-level analysis across different geographic regions.
+Therefore, unlike most previous studies focused on local biodiversity patterns *within a single watershed*, this study provides crucial insights into how ecological communities are structured *across watersheds*.
+(3) The present study provides the foundation for complexity-based ecosystem management.
+While there have been substantial debates as to whether area-based ecosystem management is sufficient to conserve biodiversity at broad spatial scales (e.g., Akasaka et al, Conservation Letters, 10: 539-546), there is, to our knowledge, no conservation scheme that explicitly accounts for ecosystem complexity in the design.
+Hence, our research provides a novel perspective to spatial planning of protected areas or ecological restoration.
 
-Our study distinguishes itself from other studies in three ways.
-First, we offer a synthetic framework integrating ecosystem size and complexity influences on biodiversity, which should apply beyond branching ecosystems.
-Second, unlike most previous studies focused on local biodiversity patterns ($\alpha$ diversity), our empirical analysis used metacommunities as replicates of statistical analysis.
-Therefore, this study provides crucial insights into how ecological communities are structured *at the metacommunity level*.
-Lastly, the present study provides the foundation for complexity-based ecosystem management - an important perspective overlooked in current conservation schemes.
-Hence, we have confidence that our research provides fundamental insights into regulating factors of biodiversity and has far-reaching implications for biodiversity conservation.
+In addition to the significance described above, the connection between network complexity and biodiversity has a broad implication for a truly interdisciplinary audience, including scientists working on fluvial geomorphology, network theory, and biodiversity conservation.
+Our study is also timely given the unprecedented rate of global biodiversity loss in freshwater ecosystems.
+Therefore, *Proceedings of the National Academy Sciences* is an ideal outlet for this manuscript.
+
+We suggest the following leading scientists in the field as potential reviewers:
+
+-   Dr. Florian Altermatt (EAWAG; florian.altermatt\@eawag.ch): Lead a number of projects on biodiversity in river networks
+
+-   Dr. Emanuel Fronhofer (Université de Montpellier; emanuel.fronhofer\@umontpellier.fr): Works on theoretical spatial ecology with a focus on complex networks
+
+-   Dr. Jonathan Moore (Simon Fraser University; jwmoore\@sfu.ca): Works on emergent ecological properties of river networks
+
+-   Dr. Justin Yeakel (University of California Merced; jdyeakel\@gmail.com): Develops theoretical models for ecological communities, including species interactions in a spatial context
+
+-   Dr. Jean Gibert (Duke University; jean.gibert\@duke.edu): Develops general theoretical models for ecological communities
+
+-   Dr. Winsor Lowe (University of Montana; winsor.lowe\@umontana.edu): Lead a number of projects on animal movements in stream networks
 
@@
 Akira Terui, Ph.D. (corresponding author)
+
+University of North Carolina at Greensboro

### 2021-03-24 coverletter.Rmd
Update coverletter.Rmd

@@
 
-In the Anthropocene, it is more imperative than ever to identify ecological factors that underpin diverse ecological communities in nature.
+Despite the inherent complexity of nature, some ecological patterns follow simple mathematical rules with far-reaching implications for biodiversity conservation.
 Much attention has been paid to the ubiquitous power-law scaling between species richness and area, in which species richness increases with area in a decelerating way.
-In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because 'scale-invariant' complexity of fractal ecosystem structure may drive ecological dynamics in space.
+In spatially complex ecosystems, however, there may be an overlooked scaling law of biodiversity because 'scale-invariant' complexity of fractal ecosystem structure drives ecological dynamics in space.
 Branching river networks are an outstanding example of such complex ecosystems, where geometric ecosystem structure (e.g., branching patterns) remains constant across a wide range of spatial scales.
@@
 In this research, we used theory and analysis of extensive fish data to show that the scale-invariant complexity of branching networks is an alternative dimension of ecosystem structure to dictate riverine biodiversity patterns.
-Theory and empirical analysis agreed that, **regardless of ecological traits of constituent species, riverine biodiversity exhibited a dual scaling law along the two orthogonal dimensions of ecosystem size and scale-invariant complexity.** An elegant consistency of theoretical and empirical results provided strong evidence that the dual scaling of biodiversity is a pervasive yet overlooked feature of complex ecosystems with important implications for biodiversity conservation.
+Theory and empirical analysis agreed that, **regardless of ecological traits of constituent species, riverine biodiversity exhibited a dual scaling law along the two orthogonal dimensions of ecosystem size and scale-invariant complexity.** An elegant consistency of theoretical and empirical results provided strong evidence that the dual scaling of biodiversity is a pervasive yet overlooked feature of complex ecosystems.
 
@@
 Notably, this pattern has emerged irrespective of ecological contexts or geographic regions, emphasizing the generality of our finding.
-(2) Our empirical analysis used *watershed ecosystems* as individual replicates of statistical analysis; our data set included 180 watersheds with 6605 sites across Japan and the US and this extensive data enabled us to perform the ecosystem-level analysis across different geographic regions.
+(2) Our empirical analysis used *watershed ecosystems* as individual replicates of statistical analysis; our data set included 180 watersheds with 6605 sites across Japan and the US and this extensive data enabled us to perform the ecosystem-level analysis.
 Therefore, unlike most previous studies focused on local biodiversity patterns *within a single watershed*, this study provides crucial insights into how ecological communities are structured *across watersheds*.

### 2021-03-24 coverletter.Rmd
Update coverletter.Rmd

@@
 In this research, we used theory and analysis of extensive fish data to show that the scale-invariant complexity of branching networks is an alternative dimension of ecosystem structure to dictate riverine biodiversity patterns.
-Theory and empirical analysis agreed that, **regardless of ecological traits of constituent species, riverine biodiversity exhibited a dual scaling law along the two orthogonal dimensions of ecosystem size and scale-invariant complexity.** An elegant consistency of theoretical and empirical results provided strong evidence that the dual scaling of biodiversity is a pervasive yet overlooked feature of complex ecosystems.
+Theory and empirical analysis agreed that, **regardless of ecological traits of constituent species, riverine biodiversity exhibited a dual scaling law along the two orthogonal dimensions of ecosystem size and scale-invariant complexity.** The elegant consistency of theoretical and empirical results provided strong evidence that the dual scaling of biodiversity is a pervasive yet overlooked feature of complex ecosystems.
 
@@
 (1) Our study is the first to show the *dual* scaling law of biodiversity.
-Notably, this pattern has emerged irrespective of ecological contexts or geographic regions, emphasizing the generality of our finding.
+Notably, this pattern has emerged irrespective of ecological contexts or geographic regions, emphasizing the generality of our findings.
 (2) Our empirical analysis used *watershed ecosystems* as individual replicates of statistical analysis; our data set included 180 watersheds with 6605 sites across Japan and the US and this extensive data enabled us to perform the ecosystem-level analysis.
@@
 (3) The present study provides the foundation for complexity-based ecosystem management.
-While there have been substantial debates as to whether area-based ecosystem management is sufficient to conserve biodiversity at broad spatial scales (e.g., Akasaka et al, Conservation Letters, 10: 539-546), there is, to our knowledge, no conservation scheme that explicitly accounts for ecosystem complexity in the design.
+While area-based ecosystem management spearheads global conservation efforts (e.g., protected areas), we are unaware of any conservation scheme that explicitly accounts for ecosystem complexity in the design.
 Hence, our research provides a novel perspective to spatial planning of protected areas or ecological restoration.
 
-In addition to the significance described above, the connection between network complexity and biodiversity has a broad implication for a truly interdisciplinary audience, including scientists working on fluvial geomorphology, network theory, and biodiversity conservation.
+In addition to the significance described above, the connection between network complexity and biodiversity has a broad implication for a truly interdisciplinary audience, including scientists working on fluvial geomorphology, network theory, and biodiversity.
 Our study is also timely given the unprecedented rate of global biodiversity loss in freshwater ecosystems.

### 2021-03-24 manuscript_pnas.Rmd
edits: maintext, abst

@@
 In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because the scale-invariant complexity of fractal ecosystem structure may drive ecological dynamics in space.
-Here, we use theory and analysis of extensive fish community data from two distinct geographic regions (Hokkaido Island in Japan and the midwestern United States) to show the emergence of robust scaling law along the two orthogonal dimensions of ecosystem size and complexity in rivers.
-The recurrent merging of various streams and rivers forms fractal branching systems, where the prevalence of branching (ecosystem complexity) represents a macro-scale control of the ecosystem's habitat heterogeneity.
+Here, we use theory and analysis of extensive fish community data from two distinct geographic regions to show a robust scaling law of riverine biodiversity along the two orthogonal dimensions of ecosystem size and complexity.
+In river networks, the recurrent merging of various tributaries forms fractal branching systems, where the prevalence of branching (ecosystem complexity) represents a macro-scale control of the ecosystem's habitat heterogeneity.
 In the meantime, ecosystem size dictates metacommunity size and total habitat diversity, two factors regulating biodiversity in nature.
 Our theory predicted that, regardless of simulated species' traits, larger and more branched 'complex' networks supported greater species richness due to increased space and environmental heterogeneity.
-Both relationships were linear on a log-log scale, indicating a robust scaling law along the dimensions of size and complexity.
-In support of this theoretical prediction, the dual power-law scaling of riverine fish diversity has consistently emerged across the study regions despite hosting different fauna with distinct evolutionary histories.
-The dual scaling of biodiversity may be a pervasive emergent property of branching networks with important implications for biodiversity conservation.
+The relationships were linear on logarithmic axes, indicating a power-law scaling by ecosystem size and complexity.
+In support of this theoretical prediction, the dual power-law scaling of riverine fish diversity has consistently emerged across the study regions (Hokkaido Island in Japan and the midwestern United States) despite hosting different fauna with distinct evolutionary histories.
+The emergence of dual scaling law may be a pervasive property of branching networks with important implications for biodiversity conservation.
 

### 2021-03-25 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 Thus, watershed-scale riverine biodiversity likely obeys a general scaling law along the two orthogonal dimensions of ecosystem size and complexity.
-The effect of ecosystem complexity was striking in its magnitude.
+The regional consistency implies that ecological traits of constituent species have a minor effect on the scaling relationships, as theory predicts (**Figures 2 and 3**).
+It is important to note that the effect of ecosystem complexity was striking in its magnitude.
 Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supporting Information**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
-This result is reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018] - the sole theoretical assumption required for the dual scaling of $\gamma$ diversity to emerge.
-Further, the consistent patterns across the geographic regions with distinct evolutionary histories imply that ecological traits of species in metacommunities may have a minor effect on the scaling relationships, as predicted by our theory.
+Overall, the observed patterns were reasonable because numerous studies have shown that tributaries are the primary source of environmental heterogeneity in river networks [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018] - the sole theoretical assumption required for the dual scaling of $\gamma$ diversity to emerge.
 

### 2021-03-25 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 
-Using theory and extensive community data, our study provides strong evidence that ecosystem size and complexity play equally important roles in shaping riverine biodiversity.
-In particular, the emergent power-law scaling between ecosystem complexity and biodiversity points to several important avenues for riverine biodiversity conservation.
+The excellent match between theoretical and empirical results provides strong evidence that ecosystem size and complexity play equally important roles in scaling riverine biodiversity.
+In particular, the emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
 First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.

### 2021-03-25 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 
-Here, we show the emergence of robust scaling law along the two orthogonal dimensions of ecosystem size and complexity in rivers - a prime example of complex branching ecosystems.
+Here, we show a dual scaling law of biodiversity along the two orthogonal dimensions of ecosystem size and complexity in rivers - a prime example of complex branching ecosystems.
 Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018].

### 2021-03-25 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because the scale-invariant complexity of fractal ecosystem structure may drive ecological dynamics in space.
-Here, we use theory and analysis of extensive fish community data from two distinct geographic regions to show a robust scaling law of riverine biodiversity along the two orthogonal dimensions of ecosystem size and complexity.
+Here, we use theory and analysis of extensive fish community data from two distinct geographic regions to show that riverine biodiversity follows a robust scaling law along the two orthogonal dimensions of ecosystem size and complexity.
 In river networks, the recurrent merging of various tributaries forms fractal branching systems, where the prevalence of branching (ecosystem complexity) represents a macro-scale control of the ecosystem's habitat heterogeneity.
@@
 The strength of competition decreased the maximum of $\alpha$ diversity but did not change the scaling relationships with ecosystem properties (**Figures 2 and 3**).
-In summary, our theory highlights how apparently similar scaling in $\gamma$ diversity emerge through different ecological pathways.
+In summary, our theory highlights how apparently similar scaling in $\gamma$ diversity emerges through different ecological pathways.
 

### 2021-03-25 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 The relationships were linear on logarithmic axes, indicating a power-law scaling by ecosystem size and complexity.
-In support of this theoretical prediction, the dual power-law scaling of riverine fish diversity has consistently emerged across the study regions (Hokkaido Island in Japan and the midwestern United States) despite hosting different fauna with distinct evolutionary histories.
+In support of this theoretical prediction, the power laws have consistently emerged in riverine fish communities across the study regions (Hokkaido Island in Japan and the midwestern United States) despite hosting different fauna with distinct evolutionary histories.
 The emergence of dual scaling law may be a pervasive property of branching networks with important implications for biodiversity conservation.

### 2021-03-25 coverletter.Rmd
Update coverletter.Rmd

@@
 
-Despite the inherent complexity of nature, some ecological patterns follow simple mathematical rules with far-reaching implications for biodiversity conservation.
+Despite the inherent complexity of nature, some ecological patterns follow surprisingly simple rules with far-reaching implications for biodiversity conservation.
 Much attention has been paid to the ubiquitous power-law scaling between species richness and area, in which species richness increases with area in a decelerating way.

### 2021-03-25 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 
-Here, we show a dual scaling law of biodiversity along the two orthogonal dimensions of ecosystem size and complexity in rivers - a prime example of complex branching ecosystems.
+Here, we propose a unified framework of ecosystem size and complexity in scaling biodiversity patterns in rivers - a prime example of complex branching ecosystems.
 Individual streams and rivers flow through different landscapes with distinct geological and climatic backgrounds, serving as a spatial unit of unique in-stream environments [@brownDendriticNetworkStructure2010; @petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018; @isaakSlowClimateVelocities2016; @mcguireNetworkAnalysisReveals2014; @abbottUnexpectedSpatialStability2018].
@@
 Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity), two factors that regulate biodiversity at the metacommunity level [@hubbellUnifiedNeutralTheory2001; @kallimanisHowDoesHabitat2008].
-We predict that ecosystem size and branching complexity increase watershed-scale species richness ($\gamma$ diversity) by enhancing local species richness ($\alpha$ diversity) and/or spatial difference of species composition ($\beta$ diversity) under different ecological scenarios.
-The present study combines theory and empirical analysis of extensive community data from two different regions of the globe to provide crucial insights into how ecological communities are structured in complex branching networks.
+The present study combines theory and analysis of extensive community data from two different regions of the globe to show that multiple ecological pathways converge to the emergence of dual diversity scaling along the two orthogonal dimensions of branching networks.
+Specifically, watershed-scale species richness ($\gamma$ diversity) increased linearly with ecosystem size and branching complexity on logarithmic axes regardless of ecological contexts; however, contributing factors of increased $\gamma$ diversity - i.e., either enhanced local species richness ($\alpha$ diversity) and/or spatial variation of species composition ($\beta$ diversity) - depended on constituent species' characteristics.
+Our findings suggest that the dual scaling law is a pervasive yet overlooked feature of complex ecosystems with important implications for biodiversity conservation.
 
@@
 
-Our theoretical analysis yielded results consistent with our prediction.
-Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**).
+Theory predicted that ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**).
 The power-law relationships (i.e., linear in a log-log scale) have emerged along the both axes of ecosystem size and complexity irrespective of ecological scenarios (compare panels in **Figures 2 and 3**).

### 2021-03-25 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 In the meantime, ecosystem size dictates metacommunity size and total habitat diversity, two factors regulating biodiversity in nature.
-Our theory predicted that, regardless of simulated species' traits, larger and more branched 'complex' networks supported greater species richness due to increased space and environmental heterogeneity.
+Our theory predicted that, regardless of simulated species' traits, larger and more branched 'complex' networks support greater species richness due to increased space and environmental heterogeneity.
 The relationships were linear on logarithmic axes, indicating a power-law scaling by ecosystem size and complexity.
@@
 The present study combines theory and analysis of extensive community data from two different regions of the globe to show that multiple ecological pathways converge to the emergence of dual diversity scaling along the two orthogonal dimensions of branching networks.
-Specifically, watershed-scale species richness ($\gamma$ diversity) increased linearly with ecosystem size and branching complexity on logarithmic axes regardless of ecological contexts; however, contributing factors of increased $\gamma$ diversity - i.e., either enhanced local species richness ($\alpha$ diversity) and/or spatial variation of species composition ($\beta$ diversity) - depended on constituent species' characteristics.
+Specifically, watershed-scale species richness ($\gamma$ diversity) increased linearly with ecosystem size and branching complexity on logarithmic axes (i.e., power laws) regardless of ecological contexts; however, contributing factors of increased $\gamma$ diversity - i.e., either enhanced local species richness ($\alpha$ diversity) and/or spatial variation of species composition ($\beta$ diversity) - depended on constituent species' characteristics.
 Our findings suggest that the dual scaling law is a pervasive yet overlooked feature of complex ecosystems with important implications for biodiversity conservation.
@@
 
-Theory predicted that ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**).
-The power-law relationships (i.e., linear in a log-log scale) have emerged along the both axes of ecosystem size and complexity irrespective of ecological scenarios (compare panels in **Figures 2 and 3**).
+Theory predicted that ecosystem size and complexity both increase $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**).
+These relationships followed power laws (i.e., linear in a log-log scale) and were consistent across ecological scenarios (compare panels in **Figures 2 and 3**).
 Importantly, the impact of ecosystem complexity was comparable to that of ecosystem size.
@@
 
-Influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios.
+Yet, influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios.
 Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2 and S5-S11**).
@@
 These watersheds are small enough (`r round(min(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` to `r round(max(c(wsd_subset[[1]]$area, wsd_subset[[2]]$area)))` km^2^) to assume that fishes can disperse therein at a multi-generation time scale [@comteFishDispersalFlowing2018], while posing challenges to traverse across watersheds (the ocean or lentic habitats; see **Materials and Methods** for watershed definition).
-We combined this data set with geospatial information, including watershed characteristics (watershed area and branching probability), climates (annual mean temperature and annual cumulative precipitation), and land use patterns (the fraction of agricultural land use and dam density).
-Using this data set, we assessed whether observed effects of the macro-scale factors are consistent across the two geographic regions by developing global and region-specific robust regression models.
-In the global model, we assumed that effects of ecosystem size (watershed area) and complexity (branching probability) are constant across the two regions (i.e., fixed slopes).
-Meanwhile, the region-specific model assumes different slopes of ecosystem size and complexity between the regions (**Materials and Methods**).
+We combined this data set with geospatial information, including watershed characteristics (watershed area and branching probability), climates (annual mean temperature and annual cumulative precipitation), and land use patterns (the fraction of agricultural land use and dam density) to evaluate potential influences of macro-scale factors.
+
+Using this data set, we were able to ask the following questions that have never been addressed in tandem: Is there a dual scaling law in riverine biodiversity?
+If so, is the dual scaling consistent across the study regions despite hosting drastically different fauna with distinct evolutionary histories?
+To test these questions, we developed global and region-specific models of robust linear regression in log-log space (see **Materials and Methods**).
+In the global model, we assumed that slopes of ecosystem size (watershed area) and complexity (branching probability) are constant across the two regions (i.e., fixed scaling exponents).
+Meanwhile, the region-specific model assumes different slopes of ecosystem size and complexity between the regions (i.e., varied scaling exponents).
 We compared the support of these competing models using the Bayes factor, a measure of the strength of evidence in favor of one model over the alternative.
@@
 
-We found decisive support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`) despite the substantial difference in fish fauna between the study regions (**Tables S5 and S6**).
+Surprisingly, we found decisive support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`).
 The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) on a log-log scale (i.e., power-law), and the estimated scaling exponents were consistent across the study regions (`r op(coef(fit$gamma$model)[2])` for watershed area and `r op(coef(fit$gamma$model)[3])` for branching probability; **Table 1 and Figure 4**).
-Thus, watershed-scale riverine biodiversity likely obeys a general scaling law along the two orthogonal dimensions of ecosystem size and complexity.
+Thus, watershed-scale riverine biodiversity likely obeys a general scaling law along the two independent axes of ecosystem size and complexity.
 The regional consistency implies that ecological traits of constituent species have a minor effect on the scaling relationships, as theory predicts (**Figures 2 and 3**).
-It is important to note that the effect of ecosystem complexity was striking in its magnitude.
+It is also important to note that the effect of ecosystem complexity was striking in its magnitude.
 Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supporting Information**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons).
@@
 Watershed area was estimated based on the delineated watershed polygons.
-We estimated branching probability by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$.
+We estimated branching probability by fitting exponential distributions to histograms of branch length as $branch~length \sim Exp(\lambda)$ (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal).
 A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$.
-We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro [@yamazakiMERITHydroHighResolution2019].
-We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4 [@hijmansVeryHighResolution2005].
-We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
-We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehnerGlobalReservoirDam2011].
+
+We estimated the spatial averages of elevation, mean annual air temperature and cumulative precipitation for each watershed polygon, which were extracted from Hydrologically Adjusted Elevations of MERIT Hydro [@yamazakiMERITHydroHighResolution2019] and WorldClim 1.4 [@hijmansVeryHighResolution2005].
+The fractions of forest, urban, and agriculture were calculated based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020].
+The Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehnerGlobalReservoirDam2011] was used to estimate dam density per unit watershed area (km^-2^).
 We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenningRSAGASAGAGeoprocessing2018], 'sf' [@pebesmaSimpleFeaturesStandardized2018] 'raster' [@hijmansRasterGeographicData2020] 'stars' [@pebesmaStarsSpatiotemporalArrays2020], and 'exactextractr' [@bastonExactextractrFastExtraction2020].

### 2021-03-26 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
   # define digits function
-  op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x)
+  op = function(x, d = 2) sprintf(paste0("%1.",d,"f"), x)
 
@@
 Our theory predicted that, regardless of simulated species' traits, larger and more branched 'complex' networks support greater species richness due to increased space and environmental heterogeneity.
-The relationships were linear on logarithmic axes, indicating a power-law scaling by ecosystem size and complexity.
+The relationships were linear on logarithmic axes, indicating power-law scaling by ecosystem size and complexity.
 In support of this theoretical prediction, the power laws have consistently emerged in riverine fish communities across the study regions (Hokkaido Island in Japan and the midwestern United States) despite hosting different fauna with distinct evolutionary histories.
@@
 One of the most robust empirical generalizations in ecology is the positive relationship between species richness and area, i.e., the species-area relationship (the SAR) [@lomolinoEcologyMostGeneral2000].
-In 1921, Arrhenius @arrheniusSpeciesArea1921 formulated the SAR as a power-law $S = cA^z$, an equation currently known as the Arrhenius species-area relationship ($S$ is the number of species observed in a given geographic area $A$, $c$ the constant, and $z$ the scaling exponent).
+In 1921, Arrhenius @arrheniusSpeciesArea1921 formulated the SAR as a power law $S = cA^z$, an equation currently known as the Arrhenius species-area relationship ($S$ is the number of species observed in a given geographic area $A$, $c$ the constant, and $z$ the scaling exponent).
 Since then, the spatial scaling of species richness has been observed in many taxonomic groups [@triantisIslandSpeciesareaRelationship2012].
@@
 Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity), two factors that regulate biodiversity at the metacommunity level [@hubbellUnifiedNeutralTheory2001; @kallimanisHowDoesHabitat2008].
-The present study combines theory and analysis of extensive community data from two different regions of the globe to show that multiple ecological pathways converge to the emergence of dual diversity scaling along the two orthogonal dimensions of branching networks.
-Specifically, watershed-scale species richness ($\gamma$ diversity) increased linearly with ecosystem size and branching complexity on logarithmic axes (i.e., power laws) regardless of ecological contexts; however, contributing factors of increased $\gamma$ diversity - i.e., either enhanced local species richness ($\alpha$ diversity) and/or spatial variation of species composition ($\beta$ diversity) - depended on constituent species' characteristics.
+Hence, we hypothesize that riverine biodiversity obeys power laws along the two orthogonal dimensions of branching networks.
+
+The present study combines theory and analysis of extensive community data from two different regions of the globe to show that multiple ecological pathways converge to the emergence of dual diversity scaling.
+Specifically, watershed-scale species richness ($\gamma$ diversity) increased linearly with ecosystem size $A$ and branching probability $P_b$ on logarithmic axes as $log_{10}~\gamma = log_{10}~c + \xi_1 log_{10}~A + \xi_2log_{10}~P_b$ ($\xi_1$ and $\xi_2$ are the scaling exponents) regardless of ecological contexts; however, contributing factors of increased $\gamma$ diversity - either enhanced local species richness ($\alpha$ diversity) and/or spatial variation of species composition ($\beta$ diversity) - depended on constituent species' characteristics.
 Our findings suggest that the dual scaling law is a pervasive yet overlooked feature of complex ecosystems with important implications for biodiversity conservation.
@@
 Using this data set, we were able to ask the following questions that have never been addressed in tandem: Is there a dual scaling law in riverine biodiversity?
-If so, is the dual scaling consistent across the study regions despite hosting drastically different fauna with distinct evolutionary histories?
+If so, is the dual scaling consistent across different geographic regions despite hosting drastically different fauna with distinct evolutionary histories?
 To test these questions, we developed global and region-specific models of robust linear regression in log-log space (see **Materials and Methods**).
@@
 Surprisingly, we found decisive support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`).
-The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) on a log-log scale (i.e., power-law), and the estimated scaling exponents were consistent across the study regions (`r op(coef(fit$gamma$model)[2])` for watershed area and `r op(coef(fit$gamma$model)[3])` for branching probability; **Table 1 and Figure 4**).
+The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) on a log-log scale, and the estimated scaling exponents were consistent across the study regions (`r op(coef(fit$gamma$model)[2])` for watershed area and `r op(coef(fit$gamma$model)[3])` for branching probability; **Table 1 and Figure 4**).
 Thus, watershed-scale riverine biodiversity likely obeys a general scaling law along the two independent axes of ecosystem size and complexity.
@@
 
-The excellent match between theoretical and empirical results provides strong evidence that ecosystem size and complexity play equally important roles in scaling riverine biodiversity.
+The excellent match between theoretical and empirical results provides strong evidence for the dual diversity scaling.
 In particular, the emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
@@
 
-Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 200 time steps for initialization and 200 time steps for burn-in) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
+Under each simulation scenario, we introduced 50 species ($S = 50$) and simulated 1400 time steps of metacommunity dynamics (including 200 time steps for initialization and 200 time steps for burn-in) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
 During the first 200 time steps (an initialization period), we initialized the simulation by seeding each habitat patch with populations of each species drawn from a Poisson distribution with a mean of 0.5.
@@
 
-We developed robust regression models with an M-estimation method to examine the effects of macro-scale drivers on diversity metrics.
+We developed robust regression models with an M-estimation method to examine power laws of riverine biodiversity.
 The robust regression analysis is insensitive to outliers of a response variable; therefore, this method allows us to account for uncertainties of our diversity estimates (see **Fish community data**).
 Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$.
-The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use (logit-transformed), and dam density.
+The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~A$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use (logit-transformed), and dam density.
 Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically.
@@
 \begin{equation}
-  \mu_w = \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
+  \mu_w = \xi_0 + \xi_1~log_{10}~A_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
 \end{equation}
@@
 where $\xi_k$ are the intercept and regression coefficients for linear predictors.
+In an ordinary scale, the global model represents a dual scaling law as $E(y) = cA^{\xi_1}P_b^{\xi_2}$, where $c = 10^{\xi_0 + \xi_3~region + \sum_k \xi_k x_{k}}$.
 Meanwhile, the region-specific model assumes the effects of watershed area and branching probability differ between regions (i.e., interactions between region and watershed area/branching probability).
@@
 \begin{aligned}
-  \mu_w =& \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w +\\
-  &\xi_4~log_{10}~WA_w \cdot region_w + \xi_5~log_{10}~P_{b,w} \cdot region_w + \sum_k \xi_k x_{k,w}
+  \mu_w =& \xi_0 + \xi_1~log_{10}~A_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w +\\
+  &\xi_4~log_{10}~A_w \cdot region_w + \xi_5~log_{10}~P_{b,w} \cdot region_w + \sum_k \xi_k x_{k,w}
 \end{aligned}
@@
 ```
+This is equivalent to:
+
+```{=tex}
+\begin{equation}
+\begin{aligned}
+  \mu_w =& \xi_0 + (\xi_1 + \xi_4~region_w)~log_{10}~A_w + (\xi_2 + \xi_5~region_w)~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
+\end{aligned}
+\end{equation}
+```
+Therefore, in an ordinary scale, the model assumes different scaling exponents between regions as $E(y) = cA^{\xi_1 + \xi_4region}P_b^{\xi_2 + \xi_5region}$.
 All explanatory variables except watershed area, branching probability, and region were standardized to a mean of zero and a standard deviation of one before the analysis.

### 2021-03-26 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 where $\xi_k$ are the intercept and regression coefficients for linear predictors.
-In an ordinary scale, the global model represents a dual scaling law as $E(y) = cA^{\xi_1}P_b^{\xi_2}$, where $c = 10^{\xi_0 + \xi_3~region + \sum_k \xi_k x_{k}}$.
+In an ordinary scale, the global model represents a dual scaling law as $E(y) = cA^{\xi_1}P_b^{\xi_2}$, where $c = 10^{\xi_0 + \xi_3region + \sum_k \xi_k x_{k}}$.
 Meanwhile, the region-specific model assumes the effects of watershed area and branching probability differ between regions (i.e., interactions between region and watershed area/branching probability).

### 2021-03-26 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity), two factors that regulate biodiversity at the metacommunity level [@hubbellUnifiedNeutralTheory2001; @kallimanisHowDoesHabitat2008].
-Hence, we hypothesize that riverine biodiversity obeys power laws along the two orthogonal dimensions of branching networks.
+Hence, riverine biodiversity may manifest scaling laws along the two orthogonal dimensions of branching networks.
 
 The present study combines theory and analysis of extensive community data from two different regions of the globe to show that multiple ecological pathways converge to the emergence of dual diversity scaling.
-Specifically, watershed-scale species richness ($\gamma$ diversity) increased linearly with ecosystem size $A$ and branching probability $P_b$ on logarithmic axes as $log_{10}~\gamma = log_{10}~c + \xi_1 log_{10}~A + \xi_2log_{10}~P_b$ ($\xi_1$ and $\xi_2$ are the scaling exponents) regardless of ecological contexts; however, contributing factors of increased $\gamma$ diversity - either enhanced local species richness ($\alpha$ diversity) and/or spatial variation of species composition ($\beta$ diversity) - depended on constituent species' characteristics.
+Specifically, watershed-scale species richness ($\gamma$ diversity) increased linearly with ecosystem size $A$ and branching probability $P_b$ on logarithmic axes as $log_{10}~\gamma = log_{10}~c + \xi_1 log_{10}~A + \xi_2log_{10}~P_b$ ($\xi_1$ and $\xi_2$ are the scaling exponents) regardless of ecological contexts.
+However, contributing factors of increased $\gamma$ diversity - either enhanced local species richness ($\alpha$ diversity) and/or spatial variation of species composition ($\beta$ diversity) - depended on constituent species' characteristics.
 Our findings suggest that the dual scaling law is a pervasive yet overlooked feature of complex ecosystems with important implications for biodiversity conservation.

### 2021-03-26 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 The present study combines theory and analysis of extensive community data from two different regions of the globe to show that multiple ecological pathways converge to the emergence of dual diversity scaling.
-Specifically, watershed-scale species richness ($\gamma$ diversity) increased linearly with ecosystem size $A$ and branching probability $P_b$ on logarithmic axes as $log_{10}~\gamma = log_{10}~c + \xi_1 log_{10}~A + \xi_2log_{10}~P_b$ ($\xi_1$ and $\xi_2$ are the scaling exponents) regardless of ecological contexts.
+Specifically, watershed-scale species richness ($\gamma$ diversity) followed power laws with ecosystem size $A$ and branching probability $P_b$ as $\gamma = cA^{\xi_1}P_b^{\xi_2}$ ($\xi_1$ and $\xi_2$ are the scaling exponents) regardless of ecological contexts.
 However, contributing factors of increased $\gamma$ diversity - either enhanced local species richness ($\alpha$ diversity) and/or spatial variation of species composition ($\beta$ diversity) - depended on constituent species' characteristics.

### 2021-06-01 manuscript_pnas.Rmd
edits: correct paths

@@
 title: "Emergent dual scaling of riverine biodiversity"
-output:
-  pdf_document:
-    latex_engine: xelatex
+output: word_document
 csl: pnas.csl
@@
   # read gis files
-  filename <- list.files(path = here::here('empirical/data_gis'), full.names = T)
+  filename <- list.files(path = here::here('code_empirical/data_gis'), full.names = T)
   wsd_subset <- lapply(filename[str_detect(filename, "wsd_subset")], st_read)
@@
   # read theory file
-  dat_sim <- read_csv(here::here('theory/result/result_sim2020-11-10.csv'))
+  dat_sim <- read_csv(here::here('code_theory/result/result_sim2020-11-10.csv'))
 
@@
   # for Bayes factor
-  source(here::here('empirical/analysis_rlm_bf.R'))
+  source(here::here('code_empirical/analysis_rlm_bf.R'))
 
   # for average predictive comparisons
-  source(here::here('empirical/analysis_apcomp.R'))
+  source(here::here('code_empirical/analysis_apcomp.R'))
 
   # Hokkaido data
-  dat_hkd_site <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))
+  dat_hkd_site <- read_csv(here::here('code_empirical/data_out/data_hkd_site.csv'))
 
   # Midwest data
-  dat_mw_site <- read_csv(here::here('empirical/data_out/data_mw_site.csv')) %>% 
+  dat_mw_site <- read_csv(here::here('code_empirical/data_out/data_mw_site.csv')) %>% 
     mutate(Year = format(as.Date(Date, format = '%m/%d/%Y'), "%Y"))
@@
 Second, it preserves the fractal nature of branching patterns [@peckhamReformulationHortonLaws1999].
-An alternative approach is the use of optimal channel networks [@carraroGenerationApplicationRiver2020a].
+An alternative approach is the use of optimal channel networks [@carraroGenerationApplicationRiver2020].
 However, we employed our framework because branching probability $P_b$ is quantifiable in natural river networks, enabling us to compare theoretical predictions with empirical observations.

### 2021-06-01 code_empirical/figure_map.R

@@ -187,6 +187,8 @@
 
   network1 <- (ng[[1]] + labs(title = "A")) + ng[[2]]
   network2 <- (ng[[3]] + labs(title = "B")) + ng[[4]]
-  print((network1 | network2) / ((eg + labs(title = "C")) + (hkd + theme(legend.position = "none") + labs(title = "D")) + mw))
+  print((network1 | network2) / ((eg + labs(title = "C")) + 
+        (hkd + theme(legend.position = "none") + 
+        labs(title = "D")) + mw))
   
   

### 2021-06-01 code_empirical/figure_diversity.R
edits: empirical figures

@@ -48,7 +48,8 @@
     pivot_longer(cols = c(alpha, beta, gamma),
                  names_to = "metric")
   
-  dat_base <- data.frame(region = factor(rep(c("hokkaido", "midwest"), each = 100)),
+  dat_base <- data.frame(region = factor(rep(c("hokkaido", "midwest"),
+                                             each = 100)),
                          resid_temp = 0,
                          resid_ppt = 0,
                          resid_agri = 0,
@@ -88,24 +89,47 @@
   
 # fig ---------------------------------------------------------------------
   
-  g1 <- ggplot(dat, aes(x = area, y = value, color = region)) +
-    facet_wrap(facets = ~metric, labeller = label_parsed) +
+  region_label <- c("Hokkaido", "Midwest")
+  names(region_label) <- c("hokkaido", "midwest")
+  
+  g1 <- ggplot(dat, aes(x = area,
+                        y = value,
+                        color = metric)) +
+    facet_wrap(facets = ~ region,
+               ncol = 2,
+               labeller = labeller(region = region_label)) +
     geom_point(alpha = 0.25) +
-    geom_line(data = dat_area, aes(x = area, y = value)) +
-    scale_color_hue(name = "Region", labels = c("Hokkaido", "Midwest")) +
+    geom_line(data = dat_area,
+              aes(x = area,
+                  y = value)) +
     xlab(expression("Watershed area ("~km^2~")")) +
     scale_y_continuous(trans='log10') +
-    scale_x_continuous(trans='log10')
+    scale_x_continuous(trans='log10') +
+    scale_color_hue(name = NULL,
+                    labels = c(expression(alpha~"diversity"),
+                               expression(beta~"diversity"),
+                               expression(gamma~"diversity")))
     
-  g2 <- ggplot(dat, aes(x = p_branch, y = value, color = region)) +
-    facet_wrap(facets = ~metric, labeller = label_parsed) +
+  g2 <- ggplot(dat, aes(x = p_branch,
+                        y = value,
+                        color = metric)) +
+    facet_wrap(facets = ~ region,
+               ncol = 2, 
+               labeller = labeller(region = region_label)) +
     geom_point(alpha = 0.25) +
-    geom_line(data = dat_bp, aes(x = p_branch, y = value, linetype = metric)) +
-    scale_linetype_manual(values = c('blank', 'solid', 'solid'), guide = "none") +
-    scale_color_hue(name = "Region", labels = c("Hokkaido", "Midwest")) +
+    geom_line(data = dat_bp,
[…]

### 2021-06-01 code_theory/figure_p_branch.R

@@ -52,7 +52,12 @@
 
 
 # complexity effect -------------------------------------------------------
-
+  
+  x1 <- 0.2
+  x2 <- 0.3 
+  y1 <- 100 * x1^0.91  
+  y2 <- 100 * x2^0.91  
+  
   g <- dat %>% 
     ggplot(aes(x = p_branch,
                y = value,
@@ -69,6 +74,10 @@
     labs(x = "Branching probability",
          y = "Species richness") +
     guides(color = guide_legend(override.aes = list(fill = NA)),
-           fill = FALSE)
+           fill = FALSE) +
+    geom_segment(aes(x = x1,
+                     xend = x2,
+                     y = y1,
+                     yend = y2))
   
   print(g)

### 2021-06-01 code_theory/figure_n_patch.R
revert: back to original figure script file

@@ -6,11 +6,13 @@
 
 # read data ---------------------------------------------------------------
 
-  dat <- read_csv(here::here("code_theory/result/result_sim2021-05-28.csv")) %>% 
+  dat <- read_csv(here::here("code_theory/result/result_sim2020-11-10.csv")) %>% 
+    select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
            p_dispersal == 0.01,
            sd_env_source == 1,
            sd_env_lon == 0.01) %>% 
+    mutate(beta_div = gamma_div / alpha_div) %>% 
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
     mutate(competition = recode(max_alpha,

### 2021-06-01 code_theory/figure_p_branch.R

@@ -6,11 +6,13 @@
 
 # read data ---------------------------------------------------------------
   
-  dat <- read_csv(here::here("code_theory/result/result_sim2021-05-28.csv")) %>% 
+  dat <- read_csv(here::here("code_theory/result/result_sim2020-11-10.csv")) %>% 
+    select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
            p_dispersal == 0.01,
            sd_env_source == 1,
            sd_env_lon == 0.01) %>% 
+    mutate(beta_div = gamma_div / alpha_div) %>% 
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
     mutate(competition = recode(max_alpha,

### 2021-06-01 figure.Rmd
edits: correct paths

@@
 
-source(here::here("empirical/figure_map.R"))
+source(here::here("code_empirical/figure_map.R"))
 
@@
 
-source(here::here("theory/figure_n_patch.R"))
+source(here::here("code_theory/figure_n_patch.R"))
 ```
@@
 
-source(here::here("theory/figure_p_branch.R"))
+source(here::here("code_theory/figure_p_branch.R"))
 ```
@@
 
-source(here::here("empirical/figure_diversity.R"))
+source(here::here("code_empirical/figure_diversity.R"))
 ```

### 2021-06-01 supplementary_information_pnas.Rmd
edits: correct paths

@@
   ## read gis files
-  filename <- list.files(path = here::here('empirical/data_gis'), full.names = T)
+  filename <- list.files(path = here::here('code_empirical/data_gis'), full.names = T)
   wsd_subset <- lapply(filename[str_detect(filename, "wsd_subset")], st_read)
@@
   ## read theory file
-  dat_sim <- read_csv(here::here('theory/result/result_sim2020-11-10.csv'))
+  dat_sim <- read_csv(here::here('code_theory/result/result_sim2020-11-10.csv'))
 
@@
   # Hokkaido data
-  dat_hkd <- read_csv(here::here("empirical/data_out/data_hkd.csv")) %>% mutate(region = "hokkaido")
-  dat_hkd_site <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))
+  dat_hkd <- read_csv(here::here("code_empirical/data_out/data_hkd.csv")) %>% mutate(region = "hokkaido")
+  dat_hkd_site <- read_csv(here::here('code_empirical/data_out/data_hkd_site.csv'))
 
   # Midwest data
-  dat_mw <- read_csv(here::here("empirical/data_out/data_mw.csv")) %>% mutate(region = "midwest")
-  dat_mw_site <- read_csv(here::here('empirical/data_out/data_mw_site.csv')) %>% 
+  dat_mw <- read_csv(here::here("code_empirical/data_out/data_mw.csv")) %>% mutate(region = "midwest")
+  dat_mw_site <- read_csv(here::here('code_empirical/data_out/data_mw_site.csv')) %>% 
     mutate(Year = format(as.Date(Date, format = '%m/%d/%Y'), "%Y"))
@@
   ## sensitivity
-  source(here::here('theory/table_sensitivity_analysis.R'))
+  source(here::here('code_theory/table_sensitivity_analysis.R'))
 
@@
 
-  source(here::here('theory/table_sim_parameter_sensitivity.R'))
+  source(here::here('code_theory/table_sim_parameter_sensitivity.R'))
   table_output
@@
 
-  source(here::here('theory/table_sim_parameter_main.R'))
+  source(here::here('code_theory/table_sim_parameter_main.R'))
   table_output
@@
 
-  source(here::here('empirical/table_splist_hkd.R'))
+  source(here::here('code_empirical/table_splist_hkd.R'))
   table_output
@@
 
-  source(here::here('empirical/table_splist_mw.R'))
+  source(here::here('code_empirical/table_splist_mw.R'))
   table_output
@@
 
-  source(here::here('empirical/table_apcomp.R'))
+  source(here::here('code_empirical/table_apcomp.R'))
   table_output
@@
 
-source(here::here("theory/figure_alpha_pattern.R"))
+source(here::here("code_theory/figure_alpha_pattern.R"))
 
@@
 
-source(here::here("theory/figure_n_patch_si.R"))
+source(here::here("code_theory/figure_n_patch_si.R"))
 
@@
 
-source(here::here("theory/figure_p_branch_si.R"))
+source(here::here("code_theory/figure_p_branch_si.R"))
 
@@
 
-source(here::here('empirical/figure_correlation.R'))
+source(here::here('code_empirical/figure_correlation.R'))
 
@@
 
-source(here::here('empirical/figure_iNEXT_sim.R'))
+source(here::here('code_empirical/figure_iNEXT_sim.R'))
 

### 2021-06-01 code_theory/figure_alpha_pattern.R
revert: figure codes

@@ -12,7 +12,7 @@ for(i in seq_len(nrow(param))){
 
 # data --------------------------------------------------------------------
 
-  dat <- read_csv(here::here("code_theory/result/result_sim_alpha_pattern2021-05-28.csv")) %>% 
+  dat <- read_csv(here::here("code_theory/result/result_sim_alpha_pattern2021-01-20.csv")) %>% 
     filter(sd_env_source == param$sigma_h[i],
            sd_env_lon == param$sigma_l[i]) %>%
     mutate(competition = recode(max_alpha,

### 2021-06-01 code_theory/figure_n_patch_si.R

@@ -12,11 +12,13 @@ for(i in seq_len(nrow(param))){
   
 # read data ---------------------------------------------------------------
 
-  dat <- read_csv(here::here("code_theory/result/result_sim2021-05-28.csv")) %>% 
+  dat <- read_csv(here::here("code_theory/result/result_sim2020-11-10.csv")) %>% 
+    select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
            p_dispersal == param$p_d[i],
            sd_env_source == param$sigma_h[i],
            sd_env_lon == param$sigma_l[i]) %>%
+    mutate(beta_div = gamma_div / alpha_div) %>% 
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
     mutate(competition = recode(max_alpha,

### 2021-06-01 code_theory/figure_p_branch_si.R

@@ -12,11 +12,13 @@ for(i in seq_len(nrow(param))){
   
 # read data ---------------------------------------------------------------
   
-  dat <- read_csv(here::here("code_theory/result/result_sim2021-05-28.csv")) %>% 
+  dat <- read_csv(here::here("code_theory/result/result_sim2020-11-10.csv")) %>% 
+    select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
            p_dispersal == param$p_d[i],
            sd_env_source == param$sigma_h[i],
            sd_env_lon == param$sigma_l[i]) %>% 
+    mutate(beta_div = gamma_div / alpha_div) %>% 
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
     mutate(competition = recode(max_alpha,

### 2021-06-02 manuscript_pnas.Rmd
edits: manuscript Rmd
modified to work in word format

@@
 bibliography: references.bib
-header-includes:
-  - \usepackage[left]{lineno}
-  - \linenumbers
 ---
@@
 
-```{=tex}
-\begin{equation}
-  \mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k}
-\end{equation}
-```
+$$
+\begin{aligned}
+\mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k} &\text{(1)}
+\end{aligned}
+$$
+
 where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and a standard deviation of $\sigma_l$.
@@
 
-```{=tex}
-\begin{equation}
+$$
 \begin{aligned}
-  \mu_{z,k} &= \omega(\rho \mu_{z,k+1}^R + \epsilon_{k}^R) + (1-\omega)(\rho \mu_{z,k+1}^L + \epsilon_{k}^L) \\
-  \omega &= \frac{A_{k+1}^R}{A_{k+1}^R + A_{k+1}^L}
+\mu_{z,k} &= \omega(\rho \mu_{z,k+1}^R + \epsilon_{k}^R) + (1-\omega)(\rho \mu_{z,k+1}^L + \epsilon_{k}^L) &&\\
+\omega &= \frac{A_{k+1}^R}{A_{k+1}^R + A_{k+1}^L} &&\text{(2)}
 \end{aligned}
-\end{equation}
-```
+$$
+
 where $R$ and $L$ denote "right" and "left" branches, respectively, and $A_k$ is the number of upstream habitat patches at longitudinal position $k$ (akin to the upstream watershed area; $A_k = 1$ at the most upstream patch).
@@
 
-```{=tex}
-\begin{equation}
-  N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
-\end{equation}
-```
+$$
+\begin{aligned}
+N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t)) &\text{(3)}
+\end{aligned}
+$$
+
 where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$.
@@
 
-```{=tex}
-\begin{equation}
-  n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}}
-\end{equation}
-```
+$$
+\begin{aligned}
+n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}} &\text{(4)}
+\end{aligned}
+$$
+
 where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
@@
 
-```{=tex}
-\begin{equation}
-  r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{\{\mu_i-z_x(t)\}^2}{2\sigma^2_{niche,i}}}]
-\end{equation}
-```
+$$
+\begin{aligned}
+r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{\{\mu_i-z_x(t)\}^2}{2\sigma^2_{niche,i}}}] &\text{(5)}
+\end{aligned}
+$$
+
 where $\mu_i$ is the optimal environmental value for species $i$, $z_x(t)$ the environmental value at patch $x$ and time $t$, and $\sigma_{niche,i}$ the niche width of species $i$.
@@
 
-```{=tex}
-\begin{equation}
-  \delta = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
-\end{equation}
-```
+$$
+\begin{aligned}
+\delta = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2}) &\text{(6)}
+\end{aligned}
+$$
+
 Smaller values of $\nu$ imply greater costs of having a wider niche (i.e., decreased maximum reproductive rate) and reduce the realized reproductive rate $r_{ix}(t)$ near the niche optimum.
@@
 
-```{=tex}
-\begin{equation}
-  \Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy})
-\end{equation}
-```
+$$
+\begin{aligned}
+\Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy}) &\text{(7)}
+\end{aligned}
+$$
+
 $\Omega_{xy}$ denotes the temporal covariance of environmental conditions between patch $x$ and $y$, which is assumed to decay exponentially with increasing distance between the patches $d_{xy}$ (the shortest network path measured as the number of habitat patches).
@@
 
-```{=tex}
-\begin{equation}
-  \xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}
-\end{equation}
-```
+$$
+\begin{aligned}
+\xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})} &\text{(8)}
+\end{aligned}
+$$
+
 The parameter $\theta$ regulates the dispersal distance of a species that follows an exponential distribution ($\theta^{-1}$ corresponds to the expected dispersal distance).
@@
 
-```{=tex}
-\begin{equation}
-  \mu_w = \xi_0 + \xi_1~log_{10}~A_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
-\end{equation}
-```
+$$
+\begin{aligned}
+\mu_w = \xi_0 + \xi_1~log_{10}~A_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w} &\text{(9)}
+\end{aligned}
+$$
+
 where $\xi_k$ are the intercept and regression coefficients for linear predictors.
@@
 
-```{=tex}
-\begin{equation}
+$$
 \begin{aligned}
-  \mu_w =& \xi_0 + \xi_1~log_{10}~A_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w +\\
+  \mu_w =& \xi_0 + \xi_1~log_{10}~A_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + &&\\
   &\xi_4~log_{10}~A_w \cdot region_w + \xi_5~log_{10}~P_{b,w} \cdot region_w + \sum_k \xi_k x_{k,w}
+&&\text{(10)}
 \end{aligned}
-\end{equation}
-```
+$$
+
 This is equivalent to:
 
-```{=tex}
-\begin{equation}
+$$
 \begin{aligned}
-  \mu_w =& \xi_0 + (\xi_1 + \xi_4~region_w)~log_{10}~A_w + (\xi_2 + \xi_5~region_w)~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
+  \mu_w =& \xi_0 + (\xi_1 + \xi_4~region_w)~log_{10}~A_w + (\xi_2 + \xi_5~region_w)~log_{10}~P_{b,w} + &&\\
+  &\xi_3~region_w + \sum_k \xi_k x_{k,w}
+&&\text{(11)}
 \end{aligned}
-\end{equation}
-```
+$$
+
 Therefore, in an ordinary scale, the model assumes different scaling exponents between regions as $E(y) = cA^{\xi_1 + \xi_4region}P_b^{\xi_2 + \xi_5region}$.
@@
 
-```{=tex}
-\begin{equation}
-  Bayes~factor = exp(\Delta BIC_{10}/2)
-\end{equation}
-```
+$$
+\begin{aligned}
+Bayes~factor = exp(\Delta BIC_{10}/2) &\text{(12)}
+\end{aligned}
+$$
+
 where $\Delta BIC_{10} = BIC(M1) - BIC(M0)$.

### 2021-06-02 figure.Rmd
edits: figure diversity

@@
 
-```{r, fig.height=6, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (left), $\\beta$ (middle), and $\\gamma$ diversity (right) in Hokkaido and Midwest regions.
+```{r, fig.height=7, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (red), $\\beta$ (green), and $\\gamma$ diversity (blue) in Hokkaido and Midwest regions.
 Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models."}

### 2021-06-02 code_empirical/figure_diversity.R

@@ -88,21 +88,42 @@
   
 # fig ---------------------------------------------------------------------
   
-  g1 <- ggplot(dat, aes(x = area, y = value, color = region)) +
-    facet_wrap(facets = ~metric, labeller = label_parsed) +
+  region_label <- c("Hokkaido", "Midwest")
+  names(region_label) <- c("hokkaido", "midwest")
+  
+  g1 <- ggplot(dat, aes(x = area,
+                        y = value,
+                        color = metric)) +
+    facet_wrap(facets = ~ region,
+               labeller = labeller(region = region_label)) +
     geom_point(alpha = 0.25) +
-    geom_line(data = dat_area, aes(x = area, y = value)) +
-    scale_color_hue(name = "Region", labels = c("Hokkaido", "Midwest")) +
+    geom_line(data = dat_area,
+              aes(x = area,
+                  y = value)) +
+    scale_color_hue(name = NULL,
+                    labels = c(expression(alpha~"diversity"),
+                               expression(beta~"diversity"),
+                               expression(gamma~"diversity"))) +
     xlab(expression("Watershed area ("~km^2~")")) +
     scale_y_continuous(trans='log10') +
     scale_x_continuous(trans='log10')
     
-  g2 <- ggplot(dat, aes(x = p_branch, y = value, color = region)) +
-    facet_wrap(facets = ~metric, labeller = label_parsed) +
+  g2 <- ggplot(dat, aes(x = p_branch,
+                        y = value,
+                        color = metric)) +
+    facet_wrap(facets = ~ region,
+               labeller = labeller(region = region_label)) +
     geom_point(alpha = 0.25) +
-    geom_line(data = dat_bp, aes(x = p_branch, y = value, linetype = metric)) +
-    scale_linetype_manual(values = c('blank', 'solid', 'solid'), guide = "none") +
-    scale_color_hue(name = "Region", labels = c("Hokkaido", "Midwest")) +
+    geom_line(data = dat_bp,
+              aes(x = p_branch,
+                  y = value,
+                  linetype = metric)) +
+    scale_color_hue(name = NULL,
+                    labels = c(expression(alpha~"diversity"),
+                               expression(beta~"diversity"),
+                               expression(gamma~"diversity"))) +
+    scale_linetype_manual(values = c("dashed", "solid", "solid"),
+                          guide = "none") +
     xlab("Branching probability") +
     scale_y_continuous(trans='log10') +
     scale_x_continuous(trans='log10')

### 2021-06-04 figure.Rmd
edits: figure re-organization

@@
 
-```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
+```{r, fig.height=6, fig.width=10, fig.cap="Qualitative match between theoretical predictions and empirical patterns in power law scaling of biodiversity.
+(A) Theory predicts that ecosystem size (the number of habitat patches) scales $\\gamma$ diversity through increased $\\alpha$ or $\\beta$ diversity across ecological scenarios.
 Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
@@
 Rows represent different competition strength.
-Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
+Competitive coefficients ($\\eta_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
 Columns represent different dispersal scenarios.
@@
 In this simulation, environmental variability among headwaters (i.e., the most upstream patches), which is expressed as the standard deviation of a normal distribution ($\\sigma_{h} = 1.0$), was greater than that of local environmental noise occurring at each habitat patch ($\\sigma_{l} = 0.01$).
-Dispersal probability $p_{d}$ was 0.01 for all the scenarios."}
+Dispersal probability $p_{d}$ was 0.01 for all the scenarios.
+(B) Empirical biodiversity patterns match theoretical predictions of power law scaling along the axis of ecosystem size.
+Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models.
+Observed patterns were consistent across geographically distant regions with distinct fish fauna (top: Hokkaido, Japan; bottom: Midwest, US)."}
 
@@
 
-```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks.
+```{r, fig.height=6, fig.width=10, fig.cap="Qualitative match between theoretical predictions and empirical patterns in power law scaling of biodiversity.
+(A) Theory predicts that ecosystem complexity (branching probability) scales $\\gamma$ diversity through increased $\\alpha$ or $\\beta$ diversity across ecological scenarios.
 Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
 Each panel represents different ecological scenarios under which metacommunity dynamics were simulated.
-See Figure 2 for details."}
+See Figure 2 for details.
+(B) Empirical biodiversity patterns match theoretical predictions of power law scaling along the axis of ecosystem complexity.
+Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models (solid: siginificant relationships; dashed: insignificant).
+Observed patterns were consistent across geographically distant regions with distinct fish fauna (top: Hokkaido, Japan; bottom: Midwest, US)."}
 
@@
 ```
-
-\newpage
-
-```{r, fig.height=7, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (red), $\\beta$ (green), and $\\gamma$ diversity (blue) in Hokkaido and Midwest regions.
-Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models."}
-
-source(here::here("code_empirical/figure_diversity.R"))
-```

### 2021-06-04 code_empirical/figure_diversity.R

@@ -95,7 +95,8 @@
                         y = value,
                         color = metric)) +
     facet_wrap(facets = ~ region,
-               labeller = labeller(region = region_label)) +
+               labeller = labeller(region = region_label),
+               ncol = 1) +
     geom_point(alpha = 0.25) +
     geom_line(data = dat_area,
               aes(x = area,
@@ -106,13 +107,16 @@
                                expression(gamma~"diversity"))) +
     xlab(expression("Watershed area ("~km^2~")")) +
     scale_y_continuous(trans='log10') +
-    scale_x_continuous(trans='log10')
-    
+    scale_x_continuous(trans='log10') +
+    ylab("Species richness") +
+    theme(legend.position = "none")
+  
   g2 <- ggplot(dat, aes(x = p_branch,
                         y = value,
                         color = metric)) +
     facet_wrap(facets = ~ region,
-               labeller = labeller(region = region_label)) +
+               labeller = labeller(region = region_label),
+               ncol = 1) +
     geom_point(alpha = 0.25) +
     geom_line(data = dat_bp,
               aes(x = p_branch,
@@ -126,10 +130,12 @@
                           guide = "none") +
     xlab("Branching probability") +
     scale_y_continuous(trans='log10') +
-    scale_x_continuous(trans='log10')
-  
-  print(  
-    (g1 + theme(legend.position = "none") + ylab("Species richness"))/
-    (g2 + ylab("Species richness")) + plot_layout(guides = "collect") +
-    plot_annotation(tag_levels = 'A')
-  )  
+    scale_x_continuous(trans='log10') +
+    ylab("Species richness") +
+    theme(legend.position = "none")
+    
+  #print(  
+  #  (g1 + theme(legend.position = "none") + ylab("Species richness"))/
+  #  (g2 + ylab("Species richness")) + plot_layout(guides = "collect") +
+  #  plot_annotation(tag_levels = 'A')
+  #)  

### 2021-06-04 code_theory/figure_n_patch.R

@@ -3,8 +3,14 @@
 
   rm(list = ls(all.names = TRUE))
   pacman::p_load(tidyverse)
+  pacman::p_load(tidyverse, patchwork)
+  
+# empirical data ----------------------------------------------------------
+  
+  source(here::here("code_empirical/figure_diversity.R"))
 
-# read data ---------------------------------------------------------------
+
+# theoretical data --------------------------------------------------------
 
   dat <- read_csv(here::here("code_theory/result/result_sim2021-05-28.csv")) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
@@ -14,8 +20,8 @@
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
     mutate(competition = recode(max_alpha,
-                                `0.75` = sprintf('"Weak competition"~(alpha[max]=="%.2f")', max_alpha),
-                                `1.5` = sprintf('"Strong competition"~(alpha[max]=="%.2f")', max_alpha)),
+                                `0.75` = sprintf('"Weak competition"~(eta[max]=="%.2f")', max_alpha),
+                                `1.5` = sprintf('"Strong competition"~(eta[max]=="%.2f")', max_alpha)),
            dispersal = recode(theta,
                               `0.1` = sprintf('"Long-distance dispersal"~(theta=="%.2f")', theta),
                               `1.0` = sprintf('"Short-distance dispersal"~(theta=="%.2f")', theta)))
@@ -65,4 +71,7 @@
     guides(color = guide_legend(override.aes = list(fill = NA)),
            fill = FALSE)
   
-  print(g)
+  print(g + ggtitle("Theory") +
+        g1 + ggtitle("Empirical") +
+        plot_annotation(tag_levels = 'A') + 
+        plot_layout(guides = "collect", width = c(2,1)))

### 2021-06-04 code_theory/figure_n_patch_si.R

@@ -20,8 +20,8 @@ for(i in seq_len(nrow(param))){
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
     mutate(competition = recode(max_alpha,
-                                `0.75` = sprintf('"Weak competition"~(alpha[max]=="%.2f")', max_alpha),
-                                `1.5` = sprintf('"Strong competition"~(alpha[max]=="%.2f")', max_alpha)),
+                                `0.75` = sprintf('"Weak competition"~(eta[max]=="%.2f")', max_alpha),
+                                `1.5` = sprintf('"Strong competition"~(eta[max]=="%.2f")', max_alpha)),
            dispersal = recode(theta,
                               `0.1` = sprintf('"Long-distance dispersal"~(theta=="%.2f")', theta),
                               `1.0` = sprintf('"Short-distance dispersal"~(theta=="%.2f")', theta)))

### 2021-06-04 code_theory/figure_p_branch.R

@@ -2,22 +2,26 @@
 # setup -------------------------------------------------------------------
   
   rm(list = ls(all.names = TRUE))
-  pacman::p_load(tidyverse)
+  pacman::p_load(tidyverse, patchwork)
 
-# read data ---------------------------------------------------------------
+  
+# empirical data ----------------------------------------------------------
+  
+  source(here::here("code_empirical/figure_diversity.R"))
+
+    
+# theoretical data --------------------------------------------------------
   
   dat <- read_csv(here::here("code_theory/result/result_sim2021-05-28.csv")) %>% 
-    select(-beta_div) %>% 
     filter(alpha_div > 0 & gamma_div > 0,
            p_dispersal == 0.01,
            sd_env_source == 1,
            sd_env_lon == 0.01) %>% 
-    mutate(beta_div = gamma_div / alpha_div) %>% 
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
     mutate(competition = recode(max_alpha,
-                                `0.75` = sprintf('"Weak competition"~(alpha[max]=="%.2f")', max_alpha),
-                                `1.5` = sprintf('"Strong competition"~(alpha[max]=="%.2f")', max_alpha)),
+                                `0.75` = sprintf('"Weak competition"~(eta[max]=="%.2f")', max_alpha),
+                                `1.5` = sprintf('"Strong competition"~(eta[max]=="%.2f")', max_alpha)),
            dispersal = recode(theta,
                               `0.1` = sprintf('"Long-distance dispersal"~(theta=="%.2f")', theta),
                               `1.0` = sprintf('"Short-distance dispersal"~(theta=="%.2f")', theta)))
@@ -25,8 +29,7 @@
   labels <- c(expression(alpha~"diversity"),
               expression(beta~"diversity"),
               expression(gamma~"diversity"))
-
-
+  
 # set plot theme ----------------------------------------------------------
 
   plt_theme <- theme_bw() + theme(
@@ -63,7 +66,7 @@
     geom_smooth(method = "loess", size = 0.5) +
     scale_y_continuous(trans = "log10") +
     scale_x_continuous(trans = "log10",
-                       breaks = c(0.01, 0.1, 0.5, 1.0)) +
+                       breaks = c(0.02, 0.1, 0.5, 1.0)) +
     scale_color_hue(name = NULL, labels = labels) +
[…]

### 2021-06-11 code_theory/figure_n_patch.R
edits: figure codes

@@ -20,8 +20,8 @@
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
     mutate(competition = recode(max_alpha,
-                                `0.75` = sprintf('"Weak competition"~(eta[max]=="%.2f")', max_alpha),
-                                `1.5` = sprintf('"Strong competition"~(eta[max]=="%.2f")', max_alpha)),
+                                `0.75` = sprintf('"Weak competition"~(b[max]=="%.2f")', max_alpha),
+                                `1.5` = sprintf('"Strong competition"~(b[max]=="%.2f")', max_alpha)),
            dispersal = recode(theta,
                               `0.1` = sprintf('"Long-distance dispersal"~(theta=="%.2f")', theta),
                               `1.0` = sprintf('"Short-distance dispersal"~(theta=="%.2f")', theta)))
@@ -71,7 +71,7 @@
     guides(color = guide_legend(override.aes = list(fill = NA)),
            fill = FALSE)
   
-  print(g + ggtitle("Theory") +
-        g1 + ggtitle("Empirical") +
+  print(g + ggtitle("Theoretical prediction") +
+        g1 + ggtitle("Empirical observation") +
         plot_annotation(tag_levels = 'A') + 
         plot_layout(guides = "collect", width = c(2,1)))

### 2021-06-11 code_theory/figure_n_patch_si.R

@@ -20,8 +20,8 @@ for(i in seq_len(nrow(param))){
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
     mutate(competition = recode(max_alpha,
-                                `0.75` = sprintf('"Weak competition"~(eta[max]=="%.2f")', max_alpha),
-                                `1.5` = sprintf('"Strong competition"~(eta[max]=="%.2f")', max_alpha)),
+                                `0.75` = sprintf('"Weak competition"~(b[max]=="%.2f")', max_alpha),
+                                `1.5` = sprintf('"Strong competition"~(b[max]=="%.2f")', max_alpha)),
            dispersal = recode(theta,
                               `0.1` = sprintf('"Long-distance dispersal"~(theta=="%.2f")', theta),
                               `1.0` = sprintf('"Short-distance dispersal"~(theta=="%.2f")', theta)))

### 2021-06-11 code_theory/figure_p_branch.R

@@ -20,8 +20,8 @@
     pivot_longer(cols = c("alpha_div", "beta_div", "gamma_div"),
                  names_to = "metric") %>% 
     mutate(competition = recode(max_alpha,
-                                `0.75` = sprintf('"Weak competition"~(eta[max]=="%.2f")', max_alpha),
-                                `1.5` = sprintf('"Strong competition"~(eta[max]=="%.2f")', max_alpha)),
+                                `0.75` = sprintf('"Weak competition"~(b[max]=="%.2f")', max_alpha),
+                                `1.5` = sprintf('"Strong competition"~(b[max]=="%.2f")', max_alpha)),
            dispersal = recode(theta,
                               `0.1` = sprintf('"Long-distance dispersal"~(theta=="%.2f")', theta),
                               `1.0` = sprintf('"Short-distance dispersal"~(theta=="%.2f")', theta)))
@@ -76,7 +76,7 @@
     guides(color = guide_legend(override.aes = list(fill = NA)),
            fill = FALSE)
   
-  print(g + ggtitle("Theory") +
-        g2 + ggtitle("Empirical") +
+  print(g + ggtitle("Theoretical prediction") +
+        g2 + ggtitle("Empirical observation") +
         plot_annotation(tag_levels = 'A') + 
         plot_layout(guides = "collect", width = c(2,1)))

### 2021-06-11 figure.Rmd
edits: figure Rmd

@@
 output:
-  pdf_document: default
+  pdf_document:
+    latex_engine: xelatex
 knit: (function(inputFile, encoding) {
-        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
+        rmarkdown::render(inputFile,
+                          encoding = encoding,
+                          output_dir = "document_output")
       })
@@
 ```{r, fig.height=6, fig.width=10, fig.cap="Qualitative match between theoretical predictions and empirical patterns in power law scaling of biodiversity.
-(A) Theory predicts that ecosystem size (the number of habitat patches) scales $\\gamma$ diversity through increased $\\alpha$ or $\\beta$ diversity across ecological scenarios.
+(A) Theoretical predictions.
+Ecosystem size (the number of habitat patches) scales $\\gamma$ diversity through increased $\\alpha$ or $\\beta$ diversity across ecological scenarios.
 Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
@@
 Rows represent different competition strength.
-Competitive coefficients ($\\eta_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
+Competition coefficients ($b_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
 Columns represent different dispersal scenarios.
@@
 Dispersal probability $p_{d}$ was 0.01 for all the scenarios.
-(B) Empirical biodiversity patterns match theoretical predictions of power law scaling along the axis of ecosystem size.
+(B) Empirical observations.
+Observed biodiversity patterns match theoretical predictions of power law scaling along the axis of ecosystem size.
 Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models.
-Observed patterns were consistent across geographically distant regions with distinct fish fauna (top: Hokkaido, Japan; bottom: Midwest, US)."}
+The estimated slopes (i.e., the scaling exponents) were consistent across geographically distant regions with distinct fish fauna (top: Hokkaido, Japan; bottom: Midwest, US)."}
 
@@
 ```{r, fig.height=6, fig.width=10, fig.cap="Qualitative match between theoretical predictions and empirical patterns in power law scaling of biodiversity.
-(A) Theory predicts that ecosystem complexity (branching probability) scales $\\gamma$ diversity through increased $\\alpha$ or $\\beta$ diversity across ecological scenarios.
+(A) Theoretical predictions.
+Ecosystem complexity (branching probability) scales $\\gamma$ diversity through increased $\\alpha$ or $\\beta$ diversity across ecological scenarios.
 Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals.
@@
 See Figure 2 for details.
-(B) Empirical biodiversity patterns match theoretical predictions of power law scaling along the axis of ecosystem complexity.
+(B) Empirical observations.
+Observed biodiversity patterns match theoretical predictions of power law scaling along the axis of ecosystem complexity.
 Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models (solid: siginificant relationships; dashed: insignificant).
-Observed patterns were consistent across geographically distant regions with distinct fish fauna (top: Hokkaido, Japan; bottom: Midwest, US)."}
+The estimated slopes (i.e., the scaling exponents) were consistent across geographically distant regions with distinct fish fauna (top: Hokkaido, Japan; bottom: Midwest, US)."}
 

### 2021-06-15 manuscript_pnas.Rmd
edits: main text

@@
 
-  n_scenario <- dat_sim %>% distinct(n_species,
+  n_scenario <- dat_sim %>%
+    distinct(n_species,
              mean_env_source,
@@
 In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because the scale-invariant complexity of fractal ecosystem structure may drive ecological dynamics in space.
-Here, we use theory and analysis of extensive fish community data from two distinct geographic regions to show that riverine biodiversity follows a robust scaling law along the two orthogonal dimensions of ecosystem size and complexity.
+Here, we use theory and analysis of extensive fish community data from two distinct geographic regions to show that riverine biodiversity follows a robust scaling law along the two orthogonal dimensions of ecosystem size and complexity (i.e., the dual scaling law).
 In river networks, the recurrent merging of various tributaries forms fractal branching systems, where the prevalence of branching (ecosystem complexity) represents a macro-scale control of the ecosystem's habitat heterogeneity.
@@
 Our theory predicted that, regardless of simulated species' traits, larger and more branched 'complex' networks support greater species richness due to increased space and environmental heterogeneity.
-The relationships were linear on logarithmic axes, indicating power-law scaling by ecosystem size and complexity.
-In support of this theoretical prediction, the power laws have consistently emerged in riverine fish communities across the study regions (Hokkaido Island in Japan and the midwestern United States) despite hosting different fauna with distinct evolutionary histories.
+The relationships were linear on logarithmic axes, indicating power law scaling by ecosystem size and complexity.
+In support of this theoretical prediction, the power laws have consistently emerged in riverine fish communities across the study regions (Hokkaido Island in Japan and the Midwestern United States) despite hosting different fauna with distinct evolutionary histories.
 The emergence of dual scaling law may be a pervasive property of branching networks with important implications for biodiversity conservation.
@@
 As such, the complexity of branching structure, which we define here as the probability of branching per unit river distance [@teruiMetapopulationStabilityBranching2018; @yeakelSynchronisationStabilityRiver2014], may represent a macro-scale control of the ecosystem's habitat heterogeneity (habitat diversity per unit area) [@grantLivingBranchesPopulation2007; @mooreEmergentStabilityLarge2015; @teruiMetapopulationStabilityBranching2018].
-Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area x heterogeneity), two factors that regulate biodiversity at the metacommunity level [@hubbellUnifiedNeutralTheory2001; @kallimanisHowDoesHabitat2008].
+Meanwhile, ecosystem size (watershed area) should determine the metacommunity size and total habitat diversity (area times heterogeneity), two factors that regulate biodiversity at the metacommunity level [@hubbellUnifiedNeutralTheory2001; @kallimanisHowDoesHabitat2008].
 Hence, riverine biodiversity may manifest scaling laws along the two orthogonal dimensions of branching networks.
+We call this the dual scaling hypothesis of biodiversity.
 
@@
 
-First, we developed a theoretical framework synthesizing the influences of ecosystem size and complexity on biodiversity patterns in branching ecosystems.
+We developed a theoretical framework synthesizing the influences of ecosystem size and complexity on biodiversity patterns in branching ecosystems.
 We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit [@yeakelSynchronisationStabilityRiver2014; @teruiMetapopulationStabilityBranching2018] (**Figure 1A and B**).
-Two factors determine mean environmental conditions at each habitat patch: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
-Environmental values at headwaters are drawn randomly from a normal distribution and propagate downstream with local environmental noise (i.e., a spatial autoregressive process with white noise).
-These environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see **Materials and Methods**).
+Two factors determine the mean environmental condition at each habitat patch $\mu_z$: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+Environmental values at headwaters are drawn randomly from a normal distribution with a mean of zero and a standard deviation of $\sigma_h$ and propagate downstream.
+We modeled the downstream propagation as a spatial autoregressive process, in which local noise is added to the adjacent upstream environment as $\mu_{z,k} \sim Normal(\mu_{z,k+1}, \sigma_{l}^2)$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet) .
+The environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see **Materials and Methods**).
 Therefore, our network-generation procedure resembles natural processes of how branching river networks create diverse habitats in a metacommunity [@mcguireNetworkAnalysisReveals2014].
-We then simulated metacommunity dynamics in the theoretical branching networks using a general metacommunity model [@thompsonProcessbasedMetacommunityFramework2020].
-In this model, 50 species with different abiotic niches (optimum and width) disperse along a network and compete for resources with varied strengths in temporally dynamic environments (see **Materials and Methods** for model details).
 
-Given the results of extensive sensitivity analysis (**Supporting Information**), we considered `r n_scenario` simulation scenarios comprising a combination of four landscape and eight ecological scenarios.
-We distinguished landscape scenarios by setting four combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), both of which are defined as standard deviations of normal distributions.
+Metacommunity dynamics were then simulated in the theoretical branching networks using a general metacommunity model [@thompsonProcessbasedMetacommunityFramework2020].
+In this model, the realized species' population growth is regulated by local abiotic environments, competition, and dispersal.
+Specifically, the number of individuals $N_{ix}(t + 1)$ for species $i$ at patch $x$ and time $t+1$ was given as:
+
+$$
+N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
+$$
+
+where $n_{ix}(t)$ is the expected number of individuals given the local community dynamics at time $t$, $I_{ix}(t)$ the expected number of immigrants to patch $x$, and $E_{ix}(t)$ the expected number of emigrants from patch $x$.
+We assumed the Beverton-Holt equation to simulate local community dynamics [@bevertonDynamicsExploitedFish1957]:
+
+$$
+\begin{aligned}
+n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{b_{ij}N_{jx}(t)}}
+\end{aligned}
+$$
+
+$r_{ix}(t)$ is the site- and time-specific reproductive rate of species $i$, $r_{0,i}$ the maximum reproductive rate, $K_{x}$ the site-specific carrying capacity, $b_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity ($S = 50$).
+Interspecific competition coefficients are random draws from a uniform distribution as $b_{ij, i \neq j} \sim Unif(0,b_{max})$ while keeping intraspecific competition coefficients constant ($b_{ii} = 1$).
+Here, the reproductive rate $r_{ix}(t)$ was related to local abiotic environments through a Gaussian function with species' niche optimum $\mu_i$ and width $\sigma_{niche,i}$.
+That is, $r_{ix}(t)$ decreases as temporally-variable abiotic environments (drawn randomly from the mean environment $\mu_{z,x}$) deviate from $\mu_i$ (see **Materials and Methods**).
+Species' reproductive performance has therefore an explicit linkage with local abiotic environments, which can be driven largely by branching structure.
+After local community dynamics, species emigrate from the local habitat patch with probability $p_d$ and disperse through the branching network following an exponential dispersal kernel with the rate parameter $\theta$ (the reciprocal $1/\theta$ represents an expected dispersal distance).
+These dispersal parameters affect the number of immigrants $I_{ix}(t)$ and emigrants $E_{ix}(t)$.
+
+Prior to the main simulation analysis, we performed a systematic sensitivity analysis to identify simulation parameters that strongly influence the relationships between biodiversity metrics ($\alpha$, $\beta$, and $\gamma$ diversity) and ecosystem properties (size and complexity).
+Our analysis revealed that the following parameters were particularly influential: environmental variation at headwaters $\sigma_h$, local environmental noise $\sigma_l$, maximum value of interspecific competition coefficient $b_{max}$ , dispersal probability $p_d$, and dispersal rate parameter $\theta$ (**Supporting Information**).
+Therefore, we considered `r n_scenario` combinations of these parameters as primary simulation scenarios, which include a combination of four landscape and eight ecological scenarios.
+
+The four landscape scenarios represent distinct patterns of spatial environmental heterogeneity, which were produced by different combinations of environmental variation at headwaters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)`) and the degree of local environmental noise ($\sigma_l =$ `r unique(dat_sim$sd_env_lon)`).
 When $\sigma_h > \sigma_l$, branching produces greater habitat heterogeneity because headwaters are the primary source of environmental variation (**Figure 1A**).
-This landscape scenario reproduces natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary[@petersonModellingDendriticEcological2013; @mcguireNetworkAnalysisReveals2014].
+This landscape scenario reproduces natural patterns of habitat heterogeneity, in which environmental conditions differ greatly among tributaries but are highly correlated within a tributary [@petersonModellingDendriticEcological2013; @mcguireNetworkAnalysisReveals2014].
 In the meantime, when $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to limited influences of branching on habitat heterogeneity (**Figure 1B**).
-This scenario may reflect human-modified landscapes where the physical or biological distinctiveness of tributaries has been compromised due to human activities [@poffHomogenizationRegionalRiver2007; @teruiMetapopulationStabilityBranching2018].
-Thus, the inequality between $\sigma_h$ and $\sigma_l$ creates contrasting patterns of habitat heterogeneity within a network.
-We also considered eight ecological scenarios that differ in dispersal distance (controlled by the rate parameter of an exponential dispersal kernel $\theta$), dispersal probability $p_{d}$, and the maximum value of interspecific competition strength $\alpha_{max}$ (see **Materials and Methods**).
-These simulation scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supporting Information**).
+This scenario may reflect human-modified landscapes, in which human activities may reduce the headwater diversity $\sigma_h$ by homogenizing in-stream processes (e.g., dams) [@poffHomogenizationRegionalRiver2007] and/or may increase the local environmental noise $\sigma_l$ through localized habitat degradation (e.g., removal of riparian forests) [@dala-corteThresholdsFreshwaterBiodiversity2020].
+Thus, the inequality between $\sigma_h$ and $\sigma_l$ defines the contrasting scenarios of natural and human-dominated landscapes.
+The eight ecological scenarios distinguish ecological characteristics of constituent species in a metacommunity.
+Among the ecological scenarios, we changed dispersal distance ($\theta = 0.1, 1.0$), dispersal probability ($p_{d} = 0.01, 0.1$), and the maximum value of interspecific competition strength ($b_{max} = 0.75, 1.50$).
+This setup enables us to examine how ecological traits of constituent species mediate biodiversity relationships.
+The combinations of landscape and ecological scenarios were capable of reproducing common spatial patterns of local species richness in rivers, corroborating the appropriateness of our choice in parameter combinations (**Supporting Information**).
 Under each simulation scenario, we simulated 1400 time steps of metacommunity dynamics (including 400 time steps of initialization and burn-in periods) in `r max(dat_sim$n_rep)` branching networks with the gradients of ecosystem size (the number of habitat patches: `r min(dat_sim$n_patch)` to `r max(dat_sim$n_patch)`) and complexity (branching probability: `r round(min(dat_sim$p_branch), 2)` to `r round(max(dat_sim$p_branch), 2)`).
 
-Theory predicted that ecosystem size and complexity both increase $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**).
-These relationships followed power laws (i.e., linear in a log-log scale) and were consistent across ecological scenarios (compare panels in **Figures 2 and 3**).
+Our simulation predicted the emergence of dual scaling law under a realistic landscape scenario, where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**).
+Ecosystem size and complexity both increased $\gamma$ diversity (**Figures 2A and 3A**) with a signature of power law (i.e., linear in a log-log scale), and these relationships were consistent across ecological scenarios (compare panels in **Figures 2A and 3A**).
 Importantly, the impact of ecosystem complexity was comparable to that of ecosystem size.
 Hence, regardless of ecological scenarios, ecosystem size and complexity are likely to be equally important in scaling $\gamma$ diversity.
+Our results contrast with predictions from neutral models, in which the enhanced connectivity of highly branched networks reduced $\gamma$ diversity by facilitating the further expansion of an already widespread species [@muneepeerakulEvolvingBiodiversityPatterns2019].
+Non-neutral components of our model should therefore have played a central role in generating the predicted patterns.
+Indeed, the robustness of the scaling law stemmed from the convergence of niche and dispersal assembly as described below.
 
-However, dispersal processes affected mechanisms that underlie the positive effects of ecosystem size and complexity on $\gamma$ diversity (compare left and right columns in **Figures 2 and 3**).
+Dispersal regulated community assembly processes that converged to the robust scaling relationships of $\gamma$ diversity (compare left and right columns in **Figures 2A and 3A**).
 We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation existed (i.e., species travel short distances).
-This pattern reflected significant spatial variation in species composition over the branching network and was likely driven by the local association of species' niche and abiotic environments (i.e., species sorting) [@leiboldMetacommunityConceptFramework2004; @thompsonProcessbasedMetacommunityFramework2020].
+This result reflected significant spatial variation in species composition over the branching network and was likely driven by the local association of species' niche and abiotic environments (i.e., species sorting) [@leiboldMetacommunityConceptFramework2004; @thompsonProcessbasedMetacommunityFramework2020].
 In contrast, when the dispersal limitation was relaxed (species travel long distances), a clear increase in $\alpha$ diversity underpinned the positive relationships between $\gamma$ diversity and ecosystem properties.
@@
 These patterns were qualitatively similar across different levels of dispersal probabilities (**Figures S5 and S12**).
-The strength of competition decreased the maximum of $\alpha$ diversity but did not change the scaling relationships with ecosystem properties (**Figures 2 and 3**).
-In summary, our theory highlights how apparently similar scaling in $\gamma$ diversity emerges through different ecological pathways.
 
-Yet, influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios.
-Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2 and S5-S11**).
+Interspecific competition had minimal influences on the underlying mechanisms (compare top and bottom rows in **Figures 2A and 3A**).
+Strong competition reduced $\alpha$ diversity as observed in former studies [@thompsonProcessbasedMetacommunityFramework2020].
+Yet, it did not change the qualitative relationships between biodiversity and ecosystem properties (**Figures 2A and 3A**).
+Accordingly, macroecological patterns are expected to be robust to variation in species interaction networks.
+This result deserves attention given the long-lasting debate on how species interactions change the dynamics of ecological communities [@kadoyaPotentialOscillatorsKeystone2018; @ushioFluctuatingInteractionNetwork2018].
+Collectively, our theoretical analysis highlights how apparently similar scaling in $\gamma$ diversity emerges through different ecological pathways by explicitly modeling niche and dispersal assembly processes.
+
+It should be borne in mind that influences of ecosystem size and complexity differed significantly in their dependence on landscape scenarios.
+Ecosystem size had positive effects on $\gamma$ diversity regardless of landscape scenarios, although the slopes were steeper with greater environmental variation (higher $\sigma_h$ and/or $\sigma_l$) (**Figures 2A and S5-S11**).
 This result is attributable to the fact that larger ecosystems can hold more individuals in a metacommunity [@hubbellUnifiedNeutralTheory2001].
-In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_l \ge \sigma_h$; **Figures S13-S18**).
+In contrast, we observed limited or no influences of branching complexity when local environmental noise was equal to or exceeded environmental variation at headwaters ($\sigma_h \le \sigma_l$; **Figures S13-S18**).
 Under this scenario, branching has a minor influence on the ecosystem's habitat heterogeneity because patch-level environmental variation is equivalent to or greater than environmental differences between tributaries (**Figure 1B**).
@@
 This theoretical prediction may not apply to pristine or semi-natural river networks where individual streams show distinct and spatially-correlated environmental conditions, including water temperature, water chemistry, and flow/sediment regimes [@petersonModellingDendriticEcological2013; @mooreEmergentStabilityLarge2015; @mcguireNetworkAnalysisReveals2014].
-Instead, it may be most relevant to severely altered landscapes where localized human disturbance disrupts the environmental distinctiveness of branches through, for example, flow regulations by dams [@poffHomogenizationRegionalRiver2007].
+Instead, it may be most relevant to severely altered landscapes where human disturbance disrupts the environmental distinctiveness of branches through, for example, flow regulations by dams [@poffHomogenizationRegionalRiver2007].
 Hence, our theory has important implications for riverine biodiversity conservation by pointing to the crucial role of habitat diversity produced by branching structure.
@@
 Surprisingly, we found decisive support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`).
-The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) on a log-log scale, and the estimated scaling exponents were consistent across the study regions (`r op(coef(fit$gamma$model)[2])` for watershed area and `r op(coef(fit$gamma$model)[3])` for branching probability; **Table 1 and Figure 4**).
+The estimated $\gamma$ diversity linearly increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity) on a log-log scale, and the estimated scaling exponents were consistent across the study regions (`r op(coef(fit$gamma$model)[2])` for watershed area and `r op(coef(fit$gamma$model)[3])` for branching probability; **Table 1 and Figures 2B and 3B**).
 Thus, watershed-scale riverine biodiversity likely obeys a general scaling law along the two independent axes of ecosystem size and complexity.
-The regional consistency implies that ecological traits of constituent species have a minor effect on the scaling relationships, as theory predicts (**Figures 2 and 3**).
+The regional consistency implies that ecological traits of constituent species have a minor effect on the scaling relationships, as our theory predicts (**Figures 2A and 3A**).
 It is also important to note that the effect of ecosystem complexity was striking in its magnitude.
@@
 Similarly, there were weak to moderate supports for the global models of $\alpha$ and $\beta$ diversity (Bayes factor = `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively).
-In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity while $\alpha$ diversity showing a weaker or a vague response to these ecosystem properties (**Table 1 and Figure 4**).
+In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity while $\alpha$ diversity showing a weaker or a vague response to these ecosystem properties (**Table 1 and Figures 2B and 3B**).
 In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly matches the previous observations of stream fish movement.
@@
 The consistent effect of branching probability on $\gamma$ diversity across the study regions is noteworthy because many watersheds in the Midwest have been altered by agricultural land use (mean % agricultural land use: `r round(mean(wsd_subset[[2]]$frac_agri)*100)`% in the Midwest and `r round(mean(wsd_subset[[1]]$frac_agri)*100)`% in Hokkaido).
-If the intensive land use by humans impairs biological or physical distinctiveness among tributaries, theory predicts a weakened effect of branching probability on $\gamma$ diversity.
+If the intensive land use by humans impairs biological or physical distinctiveness among tributaries, theory predicts a weakened effect of branching probability on $\gamma$ diversity (**Figures S13-S18**).
 However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions to support high spatial variation in species composition.
 Indeed, $\beta$ diversity increased with increasing branching probability in both regions (**Figure 4**).
-It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, persist in human-dominated landscapes to maintain the diversity of in-stream processes among tributaries.
+It is conceivable that local geological and geomorphological differences, such as slope, aspect, and soil porosity, persist in human-dominated landscapes to maintain the diversity of in-stream processes.
 The lack of land use effects (the fraction of agricultural land use and dam density) further corroborates our interpretation (**Table 1**).
@@
 We have statistically controlled the potential influences of climates and land use patterns (**Table 1**).
-Moreover, our empirical results were fairly consistent with theoretical predictions, which are free from any confounding factors.
+Moreover, our empirical results were qualitatively consistent with theoretical predictions, which are free from any confounding factors.
 Thus, we are confident in our statistical inference.
@@
 
-The excellent match between theoretical and empirical results provides strong evidence for the dual diversity scaling.
+Recent advancement of spatial theories has sparked discussion of how the complex spatial structure of ecosystems drives macroecological patterns of diverse organisms.
+Several studies have explicitly considered the physical architecture of branching networks [@rinaldoRiverNetworksEcological2018] and have succeeded in reproducing some of the core biodiversity patterns (e.g., spatial distribution of local species richness) at coarse spatial resolutions (\~5000 km^2^) [@muneepeerakulNeutralMetacommunityModels2008a].
+Yet, we have overlooked one of the fundamental rules in complex ecosystems, i.e., the dual scaling law.
+Here, the unified framework of ecosystem size and complexity provided strong evidence for the dual scaling law.
+Notably, this pattern has emerged irrespective of ecological contexts or geographic regions, emphasizing the generality of our findings.
+The dual scaling law of biodiversity may be an overlooked yet pervasive property of branching ecosystems.
+
 In particular, the emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
@@
 \begin{aligned}
-\mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k} &\text{(1)}
+\mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_k &\text{(1)}
 \end{aligned}
@@
 
-where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ is the strength of spatial autocorrelation and $\epsilon_k$ is the local environmental noise that follows a normal distribution with a mean of zero and a standard deviation of $\sigma_l$.
+where $\mu_{z,k}$ is the mean environmental value at longitudinal position $k$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet), $\rho$ the strength of spatial autocorrelation, and $\epsilon_k$ the local environmental noise that follows a normal distribution with a mean of zero and a standard deviation of $\sigma_l$.
 The parameter $\rho$ can take values of 0-1 with larger values indicating greater spatial autocorrelation.
@@
 \begin{aligned}
-n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}} &\text{(4)}
+n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{b_{ij}N_{jx}(t)}} &\text{(4)}
 \end{aligned}
@@
 
-where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
+where $r_{ix}(t)$ is the reproductive rate of species $i$ given the environmental condition at patch $x$ and time $t$, $r_{0,i}$ the maximum reproductive rate of species $i$, $K_{x}$ the carrying capacity at patch $x$, $b_{ij}$ the competition coefficient between species $i$ and $j$, and $S$ the number of species in a metacommunity.
 $K_x$ was expressed as a function of the number of upstream habitat patches $A_x$ ($K_x = 100A_x$) to represent increasing habitat size with increasing upstream watershed area [@teruiThreeEcologicalFactors2016; @rahelFishAssemblagesHabitat1991].
-The parameter $\alpha_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $\alpha_{ij}$ \> 1 (intraspecific competition coefficient was set constant as $\alpha_{ii} = 1$).
-$\alpha_{ij}$ was drawn randomly from a uniform distribution as $\alpha_{ij} \sim Unif(0, \alpha_{max})$.
+The parameter $b_{ij}$ represents the strength of interspecific competition relative to that of intraspecific competition: interspecific competition is greater than intraspecific competition if $b_{ij}$ \> 1 (intraspecific competition coefficient was set constant as $b_{ii} = 1$).
+$b_{ij}$ was drawn randomly from a uniform distribution as $b_{ij} \sim Unif(0, b_{max})$.
 The density-independent reproductive rate $r_{ix}(t)$ is affected by abiotic environments (non-consumable) and determined by the following Gaussian function:
@@
 The inequality of $\sigma_h$ and $\sigma_l$ controls the relationship between branching complexity and habitat heterogeneity (**Figure 1A and B**).
-For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`).
+For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($b_{max} =$ `r unique(dat_sim$max_alpha)`).
 This setup results in eight ecological scenarios with different levels of dispersal and competition.
@@
 We saved the last 1000 time steps to estimate the temporal averages of $\alpha$, $\beta$, and $\gamma$ diversity.
+$\beta$ diversity was defined as $\gamma/\alpha$.
 We removed simulation replicates in which no species established populations over the initial 400 time steps (`r sum(dat_sim$alpha_div == 0)` replicates out of `r nrow(dat_sim)` replicates).
@@
 Values of simulation parameters were summarized in **Table S2**.
-We performed simulations using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].
+We performed simulations using R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2020].
 
@@
 
-We compiled fish data at two geographic regions: the Hokkaido island, Japan, and the Midwest, US.
+We compiled fish data at two geographic regions: Hokkaido Island in Japan and the Midwestern US (Midwest).
 For Hokkaido, we used data from the Hokkaido Freshwater Fish Database HFish [@fukushimaModellingEffectsDams2007; @fukushimaHokkaidoFreshwaterFish2011], monitoring data at protected watersheds [@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors [@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire island.
@@
 Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method provides intuitive yet rigorous estimates of effect size in models with non-linear variable transformations (see **Supporting Information** for further details).
-We performed statistical analysis using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].
+We performed statistical analysis using R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2020].
 

### 2021-06-21 manuscript_pnas.Rmd
edits: manscript and SI

@@
   # read theory file
-  dat_sim <- read_csv(here::here('code_theory/result/result_sim2020-11-10.csv'))
+  dat_sim <- read_csv(here::here('code_theory/result/result_sim2021-05-28.csv'))
 
@@
 For example, these studies have highlighted key roles of branching structure in driving local biodiversity patterns, such as increased species richness at merging points of branches [@carraraDendriticConnectivityControls2012].
-However, most empirical research has explored the consequences of branching complexity for local community structure [@erosLandscapeEcologyRivers2019] or has relied solely on theoretical arguments with limited replications of branching architecture [@holtRoleBranchingMaintenance2018].
+However, most research has explored the consequences of branching complexity for local community structure [@erosLandscapeEcologyRivers2019] or has relied solely on theoretical arguments with limited replications of branching architecture [@holtRoleBranchingMaintenance2018].
 At present, we lack a comprehensive evaluation of how branching complexity scales biodiversity patterns at the metacommunity level.
@@
 We depicted branching ecosystems as a spatial network of connected habitat patches which local communities inhabit [@yeakelSynchronisationStabilityRiver2014; @teruiMetapopulationStabilityBranching2018] (**Figure 1A and B**).
-Two factors determine the mean environmental condition at each habitat patch $\mu_z$: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+In this network, the number of habitat patches $N_p$ (a theoretical proxy for ecosystem size $A$) and branching probability $P_b$ (ecosystem complexity) shape the spatial structure (**Materials and Methods**).
+We introduced two factors determining the temporal mean of environmental condition at each habitat patch $\mu_z$: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
 Environmental values at headwaters are drawn randomly from a normal distribution with a mean of zero and a standard deviation of $\sigma_h$ and propagate downstream.
@@
 Non-neutral components of our model should therefore have played a central role in generating the predicted patterns.
-Indeed, the robustness of the scaling law stemmed from the convergence of niche and dispersal assembly as described below.
+Indeed, the robustness of the scaling law stemmed from the convergence of niche and dispersal assembly processes as described below.
 
-Dispersal regulated community assembly processes that converged to the robust scaling relationships of $\gamma$ diversity (compare left and right columns in **Figures 2A and 3A**).
+Dispersal strength regulated the relative importance of ecological mechanisms that underlie the scaling relationships of $\gamma$ diversity (compare left and right columns in **Figures 2A and 3A**).
 We observed a greater contribution of $\beta$ diversity (defined as $\frac{\gamma}{\alpha}$) to increased $\gamma$ diversity when dispersal limitation existed (i.e., species travel short distances).
@@
 The results agree with previous predictions that increased dispersal homogenizes community composition while enhancing local diversity through increased immigrants from suitable habitat patches (i.e., mass effects) [@leiboldMetacommunityConceptFramework2004; @economoSpeciesDiversityNeutral2008; @thompsonProcessbasedMetacommunityFramework2020].
-Therefore, ecosystem size and complexity can increase $\gamma$ diversity via enhanced species sorting or mass effects, and which takes primacy is dependent on the degree of dispersal limitation.
+Therefore, ecosystem size and complexity can increase $\gamma$ diversity via enhanced species sorting (niche assembly) or mass effects (dispersal assembly), and which takes primacy is dependent on the degree of dispersal limitation.
 These patterns were qualitatively similar across different levels of dispersal probabilities (**Figures S5 and S12**).
@@
 
+While our empirical results showed an excellent match with the predictions of our niche-based model (**Figures 2 and 3**), we must note that a neutral model developed by Muneepeerakul et al.
+[@muneepeerakulNeutralMetacommunityModels2008a] was also capable of reproducing fish diversity patterns in the Mississippi-Missouri River Basin.
+This apparent contradiction is perhaps not a surprise when considering the difference in the spatial resolution of interest.
+Their neutral model used sub-basins (ca.
+5000 km^2^ in the watershed area) as a unit of local communities (metacommunities in our study) and modeled variation in habitat capacity and dispersal among those units.
+At this coarse resolution, stochastic immigration processes coupled with random speciation, a core of the Unified Neutral Theory of Biodiversity [@hubbellUnifiedNeutralTheory2001], are critical to forming biogeographic patterns [@carvajal-quinteroDrainageNetworkPosition2019].
+Meanwhile, we defined local communities at much finer resolutions (several tens to hundred meters) at which species' niche should interact with environments to determine community structure [@jacksonWhatControlsWho2001].
+It is therefore necessary for our theoretical model to assume niche-based processes.
+This interpretation is supported by the fact that a neutral model could not reproduce the positive complexity-diversity relationship observed in our empirical data [@muneepeerakulEvolvingBiodiversityPatterns2019].
+As such, our research is uniquely significant in showing the qualitative agreement of theoretical and empirical results at this level of biological organization.
+
 A potential criticism is that our results are driven by spurious correlations; however, this is very unlikely.
@@
 
-Recent advancement of spatial theories has sparked discussion of how the complex spatial structure of ecosystems drives macroecological patterns of diverse organisms.
-Several studies have explicitly considered the physical architecture of branching networks [@rinaldoRiverNetworksEcological2018] and have succeeded in reproducing some of the core biodiversity patterns (e.g., spatial distribution of local species richness) at coarse spatial resolutions (\~5000 km^2^) [@muneepeerakulNeutralMetacommunityModels2008a].
-Yet, we have overlooked one of the fundamental rules in complex ecosystems, i.e., the dual scaling law.
-Here, the unified framework of ecosystem size and complexity provided strong evidence for the dual scaling law.
-Notably, this pattern has emerged irrespective of ecological contexts or geographic regions, emphasizing the generality of our findings.
-The dual scaling law of biodiversity may be an overlooked yet pervasive property of branching ecosystems.
+The past two decades have witnessed efforts to illuminate the role of spatial ecosystem structure in shaping biodiversity patterns [@rinaldoRiverNetworksEcological2018; @grantLivingBranchesPopulation2007].
+Yet, current schemes have overlooked one of the fundamental rules in branching ecosystems, i.e., the dual scaling law.
+Here, our unified framework unveiled the surprising consistency of dual scaling across ecological contexts or geographic regions, suggesting the universality of our findings.
+This discovery brings a paradigm shift in macroecological science.
 
@@
 
-While the prevailing evidence supports the importance of ecosystem size in biodiversity relationships [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
+While prevailing evidence supports the importance of ecosystem size in biodiversity relationships [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
 However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
@@
 We thank Jacques Finlay for his constructive comments on the earlier version of the manuscript.
-This material is based upon work supported by the National Science Foundation through a Water Sustainability and Climate Program Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through a Water Quality Benefits grant (EPA-G2015-STAR-A1), and the University of North Carolina at Greensboro through a start-up fund.
+This material is based upon work supported by the National Science Foundation through the Water Sustainability and Climate Program Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through the Water Quality Benefits grant (EPA-G2015-STAR-A1), the University of North Carolina at Greensboro through a start-up fund, and the Japan Society for the Promotion of Science through the KAKENHI grant (20H03010).
 

### 2021-06-21 coverletter.Rmd
Update coverletter.Rmd

@@
 
-We are excited to submit our manuscript entitled '*Emergent dual scaling of riverine biodiversity*' to *Proceedings of the National Academy Sciences*.
+We are excited to submit our manuscript entitled '*Emergent dual scaling of riverine biodiversity*' to *Proceedings of the National Academy of Sciences*.
 
@@
 Our study is also timely given the unprecedented rate of global biodiversity loss in freshwater ecosystems.
-Therefore, *Proceedings of the National Academy Sciences* is an ideal outlet for this manuscript.
+Therefore, *Proceedings of the National Academy of Sciences* is an ideal outlet for this manuscript.
 

### 2021-06-22 manuscript_pnas.Rmd
edits: main manuscript

@@
 title: "Emergent dual scaling of riverine biodiversity"
-output: word_document
+output:
+  word_document:
+    reference_docx: word_format.docx
 csl: pnas.csl
@@
 Yet, current schemes have overlooked one of the fundamental rules in branching ecosystems, i.e., the dual scaling law.
-Here, our unified framework unveiled the surprising consistency of dual scaling across ecological contexts or geographic regions, suggesting the universality of our findings.
-This discovery brings a paradigm shift in macroecological science.
+Our unified framework unveiled the surprising consistency of dual scaling across ecological contexts or geographic regions, suggesting the universality of our findings.
+This discovery, therefore, should bring a paradigm shift in macroecological science.
 
@@
 Values of simulation parameters were summarized in **Table S2**.
-We performed simulations using R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2020].
+We performed simulations using R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
 
@@
 Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method provides intuitive yet rigorous estimates of effect size in models with non-linear variable transformations (see **Supporting Information** for further details).
-We performed statistical analysis using R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2020].
+We performed statistical analysis using R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].
 

### 2021-06-22 manuscript_pnas.Rmd
edits: main text

@@
 Environmental values at headwaters are drawn randomly from a normal distribution with a mean of zero and a standard deviation of $\sigma_h$ and propagate downstream.
-We modeled the downstream propagation as a spatial autoregressive process, in which local noise is added to the adjacent upstream environment as $\mu_{z,k} \sim Normal(\mu_{z,k+1}, \sigma_{l}^2)$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet) .
+We modeled the downstream propagation as a spatial autoregressive process, in which local noise is added to the adjacent upstream environment as $\mu_{z,k} \sim Normal(\mu_{z,k+1}, \sigma_{l}^2)$ ($k$ is the network distance from the outlet patch; $k = 1$ at the outlet).
 The environmental values recurrently 'mix' at confluences considering the relative size of joining tributaries (see **Materials and Methods**).

### 2021-06-29 supplementary_information_pnas.Rmd
edits: manscript and SI
Update supplementary_information_pnas.Rmd

@@
     toc_depth: 3
-bibliography: references.bib
+bibliography: reference.bib
 csl: pnas.csl
@@
   ## read theory file
-  dat_sim <- read_csv(here::here('code_theory/result/result_sim2020-11-10.csv'))
+  dat_sim <- read_csv(here::here('code_theory/result/result_sim2021-05-28.csv'))
 

### 2021-06-29 code_empirical/figure_map.R
edits: figure scripts

@@ -191,4 +191,6 @@
         (hkd + theme(legend.position = "none") + 
         labs(title = "D")) + mw))
   
-  
+  ggsave(normalizePath("../document_output/figure_01.pdf"),
+         width = 10,
+         height = 6)

### 2021-06-29 code_theory/figure_n_patch.R

@@ -75,3 +75,7 @@
         g1 + ggtitle("Empirical observation") +
         plot_annotation(tag_levels = 'A') + 
         plot_layout(guides = "collect", width = c(2,1)))
+  
+  ggsave(normalizePath("../document_output/figure_02.pdf"),
+         width = 10,
+         height = 6)

### 2021-06-29 code_theory/figure_p_branch.R

@@ -80,3 +80,7 @@
         g2 + ggtitle("Empirical observation") +
         plot_annotation(tag_levels = 'A') + 
         plot_layout(guides = "collect", width = c(2,1)))
+  
+  ggsave(normalizePath("../document_output/figure_03.pdf"),
+         width = 10,
+         height = 6)

### 2021-06-29 supplementary_information_pnas.Rmd
Update supplementary_information_pnas.Rmd

@@
 We simulated presence-absence data of species with known values of true species richness $S_{true}$ and the number of sampling sites $N_{site}$.
-In this simulation, presence of species $i$ at site $x$, $J_{ix}$, was drawn from a Bernoulli distribution as $J_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$.
+In this simulation, the presence of species $i$ at site $x$, $J_{ix}$, was drawn from a Bernoulli distribution as $J_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$.
 Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016].

### 2021-06-29 title.tex
Create title.tex

%\begin{titlepage}
\begin{flushleft}
\LARGE{\textbf{Supplementary Information for: \newline Emergent dual scaling of riverine biodiversity}}\\
\vspace*{\baselineskip}
\large{Akira Terui$^{*,1}$, Seoghyun Kim$^1$, Christine L. Dolph$^2$, Taku Kadoya$^3$, Yusuke Miyazaki$^4$}\\
\vspace*{1\baselineskip}
\normalsize{*Corresponding author \newline Email: hanabi0111@gmail.com}\\
\vspace*{1\baselineskip}
\normalsize{
$^1$ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA \newline
$^2$ Department of Ecology, Evolution and Behavior, University of Minnesota, St. Paul, MN 55108, USA \newline
$^3$ National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan \newline
$^4$ Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan}\\
\vspace*{2\baselineskip}
\textbf{This PDF file includes:}
\begin{itemize}
\item Supplementary text
\item Tables S1 - S7
\item Figures S1 - S20
\item SI References
\end{itemize}
\end{flushleft}
% \end{titlepage}

\newpage

### 2021-06-29 supplementary_information_pnas.Rmd
Update supplementary_information_pnas.Rmd

@@
 title: |
-  | Supporting Information for:
-  | Emergent dual scaling of riverine biodiversity
-author:
-- Akira Terui^[Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA]
-- Seoghyun Kim\footnotemark[1]
-- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of Minnesota, St. Paul, MN 55108, USA]
-- Taku Kadoya^[National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan]
-- Yusuke Miyazaki^[Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan]
+  ![](image/logo.png){width=4in}  
 output:
@@
     latex_engine: xelatex
-    toc: yes
-    toc_depth: 3
+    toc: true
+    includes:
+        before_body: title.tex
 bibliography: reference.bib
@@
 ```
+
+\newpage
 

### 2021-06-30 manuscript_pnas.Rmd
edits: main text
Update manuscript_pnas.Rmd

@@
       })
-bibliography: references.bib
+bibliography: reference.bib
 ---
@@
 
-**Authors:** Akira Terui^1^, Seoghyun Kim^1^, Christine L. Dolph^2^, Taku Kadoya^3^, Yusuke Miyazaki^4^
+**Authors:** Akira Terui^1,\*^, Seoghyun Kim^1^, Christine L. Dolph^2^, Taku Kadoya^3^, Yusuke Miyazaki^4^
+
+\*Corresponding author: hanabi0111\@gmail.com
 
@@
 **Key words:** metacommunity, species diversity, scaling law, network theory, freshwater
+
+\newpage
 
@@
 Here, the reproductive rate $r_{ix}(t)$ was related to local abiotic environments through a Gaussian function with species' niche optimum $\mu_i$ and width $\sigma_{niche,i}$.
-That is, $r_{ix}(t)$ decreases as temporally-variable abiotic environments (drawn randomly from the mean environment $\mu_{z,x}$) deviate from $\mu_i$ (see **Materials and Methods**).
+That is, $r_{ix}(t)$ decreases as the temporally-variable abiotic environment $z_x(t)$ deviates from $\mu_i$ ($z_x(t)$ is drawn randomly from a multivariate normal distribution with the mean environment of the patch $\mu_{z,x}$; see **Materials and Methods**).
 Species' reproductive performance has therefore an explicit linkage with local abiotic environments, which can be driven largely by branching structure.
@@
 The consistent effect of branching probability on $\gamma$ diversity across the study regions is noteworthy because many watersheds in the Midwest have been altered by agricultural land use (mean % agricultural land use: `r round(mean(wsd_subset[[2]]$frac_agri)*100)`% in the Midwest and `r round(mean(wsd_subset[[1]]$frac_agri)*100)`% in Hokkaido).
-If the intensive land use by humans impairs biological or physical distinctiveness among tributaries, theory predicts a weakened effect of branching probability on $\gamma$ diversity (**Figures S13-S18**).
+If the intensive land use by humans impairs biological or physical distinctiveness among tributaries, our theory predicts a weakened effect of branching probability on $\gamma$ diversity (**Figures S13-S18**).
 However, $\gamma$ diversity increased significantly with increasing branching probability in this highly modified landscape, suggesting that tributaries still sustain unique environmental conditions to support high spatial variation in species composition.
@@
 While our empirical results showed an excellent match with the predictions of our niche-based model (**Figures 2 and 3**), we must note that a neutral model developed by Muneepeerakul et al.
-[@muneepeerakulNeutralMetacommunityModels2008a] was also capable of reproducing fish diversity patterns in the Mississippi-Missouri River Basin.
+[@muneepeerakulNeutralMetacommunityModels2008] was also capable of reproducing fish diversity patterns in the Mississippi-Missouri River Basin.
 This apparent contradiction is perhaps not a surprise when considering the difference in the spatial resolution of interest.
@@
 Our fundamental findings should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
-Further, the proposed framework may be extended to other aspects of biodiversity; for example, a logical next step is to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002; @suHumanImpactsGlobal2021] and shifts in community assembly processes [@chaseStochasticCommunityAssembly2010].
+Further, the proposed framework may be extended to other aspects of biodiversity; for example, a logical next step is to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002; @suHumanImpactsGlobal2021] and shifts in stochastic/deterministic community assembly [@chaseStochasticCommunityAssembly2010].
 Recognizing the dual scaling of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
@@
 Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity.
-Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity [@chaoRarefactionExtrapolationHill2014a].
+Asymptotic species richness can be interpreted as the estimated true species richness in a given area when estimated using spatial replicates of local community data within a metacommunity [@chaoRarefactionExtrapolationHill2014].
 We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016].
 Metacommunities with $\ge$ 10 sampling sites were used in our analysis because a small sample size inflates statistical uncertainties in estimating asymptotic species richness (**Supporting Information**).
-We assessed the completeness of the observed species richness based on sample coverage, which is the total proportional abundances of observed species to the whole metacommunity [@chaoRarefactionExtrapolationHill2014a].
+We assessed the completeness of the observed species richness based on sample coverage, which is the total proportional abundances of observed species to the whole metacommunity [@chaoRarefactionExtrapolationHill2014].
 We excluded watersheds whose sample coverage was below 0.9 because the estimates of asymptotic species richness may contain non-negligible statistical uncertainty.
@@
 We thank Jacques Finlay for his constructive comments on the earlier version of the manuscript.
-This material is based upon work supported by the National Science Foundation through the Water Sustainability and Climate Program Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through the Water Quality Benefits grant (EPA-G2015-STAR-A1), the University of North Carolina at Greensboro through a start-up fund, and the Japan Society for the Promotion of Science through the KAKENHI grant (20H03010).
+This material is based upon work supported by the National Science Foundation through the Water Sustainability and Climate Program Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through the Water Quality Benefits grant (EPA-G2015-STAR-A1), the University of North Carolina at Greensboro through start-up funds, and the Japan Society for the Promotion of Science through the KAKENHI grant (20H03010).
 

### 2021-06-30 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 
-Third parties provided data for empirical data analysis; references are provided where appropriate.
+Part of our fish data set is available from the RiverFishTIME database [@comteRivFishTIMEGlobalDatabase2021].
+The fish data provided by third parties are not available due to licensing issues.
+Environmental data are available at MERIT Hydro (http://hydro.iis.u-tokyo.ac.jp/\~yamadai/MERIT_Hydro/) [@yamazakiMERITHydroHighResolution2019], Global 3-second/1-second Water Body Map (http://hydro.iis.u-tokyo.ac.jp/\~yamadai/G3WBM/index.html) [@yamazakiDevelopmentGlobal90m2015],WorldClim (https://www.worldclim.org/data/v1.4/worldclim14.html) [@hijmansVeryHighResolution2005], Copernicus Global Land Service (https:/doi.org/10.5281/zenodo.3939038) [@marcelbuchhornCopernicusGlobalLand2020], and Global Reservoir and Dam database (https://doi.org/10.7927/H4N877QK) [@lehnerGlobalReservoirDam2011].
 R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at <https://github.com/aterui/mcbrnet>).

### 2021-06-30 code_empirical/figure_map.R
edits: figure titles

@@ -189,7 +189,8 @@
   network2 <- (ng[[3]] + labs(title = "B")) + ng[[4]]
   print((network1 | network2) / ((eg + labs(title = "C")) + 
         (hkd + theme(legend.position = "none") + 
-        labs(title = "D")) + mw))
+        labs(title = "D")) + mw) +
+        plot_annotation(title = "Figure 1"))
   
   ggsave(normalizePath("../document_output/figure_01.pdf"),
          width = 10,

### 2021-06-30 code_theory/figure_n_patch.R

@@ -73,7 +73,7 @@
   
   print(g + ggtitle("Theoretical prediction") +
         g1 + ggtitle("Empirical observation") +
-        plot_annotation(tag_levels = 'A') + 
+        plot_annotation(tag_levels = 'A', title = "Figure 2") + 
         plot_layout(guides = "collect", width = c(2,1)))
   
   ggsave(normalizePath("../document_output/figure_02.pdf"),

### 2021-06-30 code_theory/figure_p_branch.R

@@ -78,7 +78,7 @@
   
   print(g + ggtitle("Theoretical prediction") +
         g2 + ggtitle("Empirical observation") +
-        plot_annotation(tag_levels = 'A') + 
+        plot_annotation(tag_levels = 'A', title = "Figure 3") + 
         plot_layout(guides = "collect", width = c(2,1)))
   
   ggsave(normalizePath("../document_output/figure_03.pdf"),

### 2021-06-30 manuscript_pnas.Rmd
edits: manuscript

--- 2021-06-30 manuscript_pnas.Rmd
@@
 The past two decades have witnessed efforts to illuminate the role of spatial ecosystem structure in shaping biodiversity patterns [@rinaldoRiverNetworksEcological2018; @grantLivingBranchesPopulation2007].
-Yet, current schemes have overlooked one of the fundamental rules in branching ecosystems, i.e., the dual scaling law.
+Yet, current schemes have overlooked one of the fundamental phenomena in spatially complex ecosystems - the dual scaling law.
 Our unified framework unveiled the surprising consistency of dual scaling across ecological contexts or geographic regions, suggesting the universality of our findings.
-This discovery, therefore, should bring a paradigm shift in macroecological science.
+This discovery, therefore, should bring a crucial perspective to macroecological science.
 
@@
 
-Third parties provided data for empirical data analysis; references are provided where appropriate.
+Part of our fish data set is available from the RiverFishTIME database [@comteRivFishTIMEGlobalDatabase2021].
+The fish data provided by third parties are not available due to licensing issues.
+Environmental data are available at MERIT Hydro ([http://hydro.iis.u-tokyo.ac.jp/\\\~yamadai/MERIT_Hydro/](http://hydro.iis.u-tokyo.ac.jp/~yamadai/MERIT_Hydro/){.uri}) [@yamazakiMERITHydroHighResolution2019], Global 3-second/1-second Water Body Map ([http://hydro.iis.u-tokyo.ac.jp/\\\~yamadai/G3WBM/index.html](http://hydro.iis.u-tokyo.ac.jp/~yamadai/G3WBM/index.html){.uri}) [@yamazakiDevelopmentGlobal90m2015],WorldClim (<https://www.worldclim.org/data/v1.4/worldclim14.html>) [@hijmansVeryHighResolution2005], Copernicus Global Land Service (<https:/doi.org/10.5281/zenodo.3939038>) [@marcelbuchhornCopernicusGlobalLand2020], and Global Reservoir and Dam database (<https://doi.org/10.7927/H4N877QK>) [@lehnerGlobalReservoirDam2011].
 R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at <https://github.com/aterui/mcbrnet>).

### 2021-07-02 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 
-The past two decades have witnessed efforts to illuminate the role of spatial ecosystem structure in shaping biodiversity patterns [@rinaldoRiverNetworksEcological2018; @grantLivingBranchesPopulation2007].
-Yet, current schemes have overlooked one of the fundamental phenomena in spatially complex ecosystems - the dual scaling law.
 Our unified framework unveiled the surprising consistency of dual scaling across ecological contexts or geographic regions, suggesting the universality of our findings.
-This discovery, therefore, should bring a crucial perspective to macroecological science.
-
 In particular, the emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
@@
 For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin [@koningNetworkGrassrootsReserves2020].
+Recognizing the dual scaling of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
 
-While prevailing evidence supports the importance of ecosystem size in biodiversity relationships [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
-However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
-Our fundamental findings should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
-Further, the proposed framework may be extended to other aspects of biodiversity; for example, a logical next step is to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002; @suHumanImpactsGlobal2021] and shifts in stochastic/deterministic community assembly [@chaseStochasticCommunityAssembly2010].
-Recognizing the dual scaling of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
-The generalization of our findings in spatially complex ecosystems represents a frontier for future research.
+Ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
+However, while the foundational concepts in ecology emphasize the importance of ecosystem size in biodiversity relationships [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
+The ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
+In this context, our study serves as a conceptual pillar for future research.
+For example, the proposed framework may be extended to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002] and shifts in stochastic/deterministic community assembly [@chaseStochasticCommunityAssembly2010].The discovery of the present study should therefore bring a paradigm shift in macroecological science.
 
@@
 We are grateful to numerous people who have been involved in the collection of fish community data.
-We thank Michio Fukushima and Hirokazu Urabe for providing information on the Hokkaido Freshwater Fish Database HFish and the fish monitoring data at protected watersheds in Hokkaido.
+We thank Illinois Environmental Protection Agency, Minnesota Pollution Control Agency, Iowa Department of Natural Resources, Wisconsin Department of Natural Resources, Michio Fukushima and Hirokazu Urabe for providing data for our empirical analysis.
 We thank Jacques Finlay for his constructive comments on the earlier version of the manuscript.

### 2021-07-02 supplementary_information_pnas.Rmd
Update supplementary_information_pnas.Rmd

@@
       })
+header-includes:
+  \pagenumbering{gobble}
 ---
@@
 \newpage
+\pagenumbering{arabic}
 

### 2021-07-02 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin [@koningNetworkGrassrootsReserves2020].
-Recognizing the dual scaling of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
 
-Ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms.
-However, while the foundational concepts in ecology emphasize the importance of ecosystem size in biodiversity relationships [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
-The ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
-In this context, our study serves as a conceptual pillar for future research.
-For example, the proposed framework may be extended to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002] and shifts in stochastic/deterministic community assembly [@chaseStochasticCommunityAssembly2010].The discovery of the present study should therefore bring a paradigm shift in macroecological science.
+While the foundational concepts in ecology emphasize the importance of ecosystem size in biodiversity relationships [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
+However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
+In this context, this study substantially advanced our understanding of how biodiversity is organized in spatially complex ecosystems, serving as a conceptual pillar for future research.
+For example, the proposed framework may be extended to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002] and shifts in stochastic/deterministic community assembly [@chaseStochasticCommunityAssembly2010].
+Recognizing the dual control of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
+The generalization of our discovery should therefore bring a paradigm shift in macroecological science with far-reaching implications for biodiversity conservation.
 

### 2021-07-02 figure_legends.Rmd

---
title: "Figure legends"
output:
  word_document:
    reference_docx: word_format.docx
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Figure 1** (A and B) Theoretical branching networks generated under contrasting landscape scenarios. Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N_p$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N_p = 30$ and $P_{b} = 0.2, 0.8$ in this example). Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (Materials and Methods). Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values). Panels A and B show distinct landscape scenarios. Environmental variation at headwaters $\sigma_{h}$ exceeds the degree of local environmental noise $\sigma_{l}$ in A ($\sigma_{h} = 1, \sigma_{l} = 0.01$), while the opposite is true in B ($\sigma_{h} = 0.01, \sigma_{l} = 1$). (C) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in D). Red dots indicate sampling sites for fish surveys. (D) Map of study regions (left, Hokkaido, Japan; right, Midwest, US). Watersheds (i.e., metacommunities) are gray-shaded in proportion to the number of sampling sites.

**Figure 2** Qualitative match between theoretical predictions and empirical patterns in power law scaling of biodiversity. (A) Theoretical predictions. Ecosystem size (the number of habitat patches) scales $\gamma$ diversity through increased $\alpha$ or $\beta$ diversity across ecological scenarios. Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competition coefficients ($b_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\theta = 0.10$) and short-distance dispersal ($\theta = 1.0$). In this simulation, environmental variability among headwaters (i.e., the most upstream patches), which is expressed as the standard deviation of a normal distribution ($\sigma_{h} = 1.0$), was greater than that of local environmental noise occurring at each habitat patch ($\sigma_{l} = 0.01$). Dispersal probability $p_{d}$ was 0.01 for all the scenarios. (B) Empirical observations. Observed biodiversity patterns match theoretical predictions of power law scaling along the axis of ecosystem size. Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models. The estimated slopes (i.e., the scaling exponents) were consistent across geographically distant regions with distinct fish fauna (top: Hokkaido, Japan; bottom: Midwest, US)

**Figure 3** Qualitative match between theoretical predictions and empirical patterns in power law scaling of biodiversity. (A) Theoretical predictions. Ecosystem complexity (branching probability) scales $\gamma$ diversity through increased $\alpha$ or $\beta$ diversity across ecological scenarios. Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. See Figure 2 for details. (B) Empirical observations. Observed biodiversity patterns match theoretical predictions of power law scaling along the axis of ecosystem complexity. Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models (solid: siginificant relationships; dashed: insignificant). The estimated slopes (i.e., the scaling exponents) were consistent across geographically distant regions with distinct fish fauna (top: Hokkaido, Japan; bottom: Midwest, US).

### 2021-07-02 manuscript_pnas.Rmd

@@
 However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
-In this context, this study substantially advanced our understanding of how biodiversity is organized in spatially complex ecosystems, serving as a conceptual pillar for future research.
+In this context, the present study substantially advanced our understanding of how biodiversity is organized in spatially complex ecosystems, offering a conceptual pillar for future research.
 For example, the proposed framework may be extended to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002] and shifts in stochastic/deterministic community assembly [@chaseStochasticCommunityAssembly2010].

### 2021-07-02 table_kable.Rmd

---
title: "Table"
output:
  word_document:
    reference_docx: word_format.docx
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

source(here::here("code_empirical/analysis_rlm_bf.R"))
op = function(x, d = 2) sprintf(paste0("%1.", d, "f"), x)

x  <-  lapply(fit, function(x) {

  conf <- confint.default(x$model)
  ci_test <- conf[,1] * conf[,2]

  paste0(op(coef(summary(x$model))[,1]),
         " (",
         op(coef(summary(x$model))[,2]),
         ")",
         ifelse(ci_test < 0, "", "*"))
})

Parameter <- c("$\\xi_0$",
              "$\\xi_1$", 
              "$\\xi_2$",    
              "$\\xi_3$",                             
              "$\\xi_4$",                                         
              "$\\xi_5$",
              "$\\xi_6$",
              "$\\xi_7$")

Effect <- c("Intercept",
            "$log_{10}$ Watershed area", 
            "$log_{10}$ Branching probability",    
            "Region (Midwest vs. Hokkaido)",                             
            "Air temperature",                                         
            "Precipitation",
            "Logit fraction of agriculture",
            "Dam density")

output <- tibble::as_tibble(do.call(cbind, x)) %>% 
  rename("$\\alpha$ diversity" = alpha,
         "$\\beta$ diversity" = beta,
         "$\\gamma$ diversity" = gamma) %>% 
  mutate(Effect,
         Parameter) %>% 
  relocate(Parameter,
           Effect)

```

**Table 1** Estimated parameters of robust regression models explaining fish species richness in Hokkaido (Japan) and the Midwest (US). The standard errors (SE) are shown in parenthesis. Response variables were log-10 transformed. Climate and land use variables (air temperature, precipitation, logit fraction of agriculture, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.

```{r table1}

knitr::kable(output)

```

Note: * parameter estimates whose 95% confidence intervals (approximately $\xi_k \pm 2SE$) do not include zero

### 2021-07-03 code_empirical/analysis_rlm_bf.R
edits: gis files

@@ -34,8 +34,8 @@
     
     mod0 <- MASS::rlm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
                                           scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
-                      method = 'M',
                       psi = MASS::psi.huber,
+                      method = 'M',
                       data = data)
     
     # bf01: bayes factor in favor of mod0 over mod1

### 2021-07-03 code_empirical/data_merge_hkd.R
Update data_merge_hkd.R

@@ -48,7 +48,7 @@
   ## convert data to frequency
   dat_freq <- dat_fish %>% 
     group_by(watershed_id, Species) %>% 
-    summarise(freq = n()) %>% 
+    summarise(freq = n_distinct(SiteID)) %>% 
     pivot_wider(id_cols = watershed_id,
                 names_from = Species,
                 values_from = freq,
@@ -114,8 +114,8 @@
   ## export point data
   albers_point <- d0 %>% 
     filter(watershed_id %in% wsd_subset) %>% 
-    group_by(SiteID) %>% 
-    distinct(SiteID)
+    select(SiteID, geometry) %>% 
+    distinct()
   
   st_write(albers_point,
            "data_gis/albers_point_subset_hkd.gpkg",

### 2021-07-03 code_empirical/data_merge_mw.R
Update data_merge_mw.R

@@ -65,7 +65,7 @@
   ## convert data to frequency
   dat_freq <- dat_fish %>% 
     group_by(watershed_id, Species) %>% 
-    summarise(freq = n()) %>% 
+    summarise(freq = n_distinct(SiteID)) %>% 
     pivot_wider(id_cols = watershed_id,
                 names_from = Species,
                 values_from = freq,
@@ -131,8 +131,8 @@
   ## export point data
   albers_point <- d0 %>% 
     filter(watershed_id %in% wsd_subset) %>% 
-    group_by(SiteID) %>% 
-    distinct(SiteID)
+    select(SiteID, geometry) %>% 
+    distinct()
   
   st_write(albers_point,
            "data_gis/albers_point_subset_mw.gpkg",

### 2021-08-17 supplementary_information_pnas.Rmd
Update supplementary_information_pnas.Rmd
edits: parameter name correction

@@
 
+```{=tex}
 \newpage
 \pagenumbering{arabic}
-
+```
 # Theory
@@
   u_{n} &\sim Normal(\mu_n, \sigma^2)\\
-  \mu_n &= \zeta_0 + \zeta_1 \sigma_{h,n} + \zeta_2 \sigma_{l,n} + \zeta_3 \sigma_{z,n} + \zeta_4 \phi_n + \zeta_5 \nu_n + \zeta_6 \alpha_{max, n} + \zeta_7 \theta_n + \zeta_8 p_{d,n} 
+  \mu_n &= \zeta_0 + \zeta_1 \sigma_{h,n} + \zeta_2 \sigma_{l,n} + \zeta_3 \sigma_{z,n} + \zeta_4 \phi_n + \zeta_5 \nu_n + \zeta_6 b_{max, n} + \zeta_7 \theta_n + \zeta_8 p_{d,n} 
 \end{aligned}
@@
 The sensitivity analysis revealed key simulation parameters.
-For the effects of $N_p$, the following simulation parameters were influential: the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\gamma$ diversity), the maximum value of interspecific competition coefficient ($\alpha_{max}$; influenced the effects on $\alpha$, $\beta$, and $\gamma$ diversity), dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal probability ($p_d$; influenced the effect on $\alpha$ diversity) (**Table S3**).
+For the effects of $N_p$, the following simulation parameters were influential: the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\gamma$ diversity), the maximum value of interspecific competition coefficient ($b_{max}$; influenced the effects on $\alpha$, $\beta$, and $\gamma$ diversity), dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal probability ($p_d$; influenced the effect on $\alpha$ diversity) (**Table S3**).
 For the effects of $P_b$, the following simulation parameters were influential: environmental variation at headwaters ($\sigma_h$; influenced the effect on $\gamma$ diversity), the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity) (**Table S4**).
 
-Based on the results, we identified $\sigma_h$, $\sigma_l$, $\alpha_{max}$, $\theta$, and $p_d$ as key parameters.
+Based on the results, we identified $\sigma_h$, $\sigma_l$, $b_{max}$, $\theta$, and $p_d$ as key parameters.
 We changed the values of these parameters in the main analysis and examined the relationships between diversity metrics and ecosystem properties.
@@
 Rows represent different competition strength.
-Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
+Competition coefficients ($b_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
 Columns and lines represent different dispersal scenarios (dispersal distance and probability).
@@
 Rows represent different competition strength.
-Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
+Competition coefficients ($b_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition).
 Columns represent different dispersal scenarios.

### 2021-08-17 code_theory/figure_alpha_pattern.R

@@ -16,9 +16,9 @@ for(i in seq_len(nrow(param))){
     filter(sd_env_source == param$sigma_h[i],
            sd_env_lon == param$sigma_l[i]) %>%
     mutate(competition = recode(max_alpha,
-                                `0.75` = sprintf('"Weak competition"~(alpha[max]=="%.2f")',
+                                `0.75` = sprintf('"Weak competition"~(b[max]=="%.2f")',
                                                  max_alpha),
-                                `1.5` = sprintf('"Strong competition"~(alpha[max]=="%.2f")',
+                                `1.5` = sprintf('"Strong competition"~(b[max]=="%.2f")',
                                                 max_alpha)),
            dispersal = recode(theta,
                               `0.1` = sprintf('"Long-distance dispersal"~(theta=="%.2f")',

### 2021-08-17 code_theory/table_sensitivity_analysis.R

@@ -22,7 +22,7 @@
                                                          "$\\sigma_{z}$",
                                                          "$\\phi$",
                                                          "$\\nu$",
-                                                         "$\\alpha_{max}$",
+                                                         "$b_{max}$",
                                                          "$\\theta$",
                                                          "$p_{d}$",
                                                          "Intercept"),
@@ -54,7 +54,7 @@
                                                        "$\\sigma_{z}$",
                                                        "$\\phi$",
                                                        "$\\nu$",
-                                                       "$\\alpha_{max}$",
+                                                       "$b_{max}$",
                                                        "$\\theta$",
                                                        "$p_{d}$",
                                                        "Intercept"),

### 2021-08-17 code_theory/table_sim_parameter_main.R

@@ -52,7 +52,7 @@
                                  Parameter == 'rho' ~ '$\\rho$',
                                  Parameter == 'phi' ~ '$\\phi$',
                                  Parameter == 'niche_cost' ~ '$\\nu$',
-                                 Parameter == 'max_alpha' ~ '$\\alpha_{max}$',
+                                 Parameter == 'max_alpha' ~ '$b_{max}$',
                                  Parameter == 'theta' ~ '$\\theta$',
                                  Parameter == 'p_dispersal' ~ '$p_{d}$',
                                  Parameter == 'r0' ~ '$r_{0,i}$',

### 2021-08-17 code_theory/table_sim_parameter_sensitivity.R

@@ -5,7 +5,7 @@ table_output <- tibble(Parameter = c('$\\sigma_{h}$',
                                      '$\\rho$',
                                      '$\\phi$',
                                      '$\\nu$',
-                                     '$\\alpha_{max}$',
+                                     '$b_{max}$',
                                      '$\\theta$',
                                      '$p_{d}$',
                                      '$r_{0,i}$'),

### 2021-08-17 code_empirical/analysis_rlm_bf.R
edits: create scaled variables

@@ -13,27 +13,28 @@
   dat <- bind_rows(dat_hkd, dat_mw) %>% 
     rename(gamma = Estimator,
            alpha = mu_alpha) %>% 
-    mutate(beta = gamma/alpha,
+    mutate(beta = gamma / alpha,
            logit_agri = log(frac_agri) - log(1 - frac_agri),
-           dam_density = n_dam/area) %>% 
-    mutate(resid_agri = resid(lm(logit_agri ~ region, data = .)),
-           resid_temp = resid(lm(mean_temp ~ region, data = .)),
-           resid_ppt = resid(lm(mean_ppt ~ region, data = .)),
-           resid_dam = resid(lm(dam_density ~ region, data = .)))
+           dam_density = n_dam / area) %>% 
+    mutate(scl_resid_agri = c(scale(resid(lm(logit_agri ~ region, data = .)))),
+           scl_resid_temp = c(scale(resid(lm(mean_temp ~ region, data = .)))),
+           scl_resid_ppt = c(scale(resid(lm(mean_ppt ~ region, data = .)))),
+           scl_resid_dam = c(scale(resid(lm(dam_density ~ region, data = .))))
+           )
   
 
 # model selection ---------------------------------------------------------
 
   m_compare <- function(response, data) {
     
-    mod1 <- MASS::rlm(log(response, 10) ~ log(area, 10)*region + log(p_branch, 10)*region + region +
-                                          scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
+    mod1 <- MASS::rlm(log(response, 10) ~ log(area, 10) * region + log(p_branch, 10) * region + region +
+                                          scl_resid_temp + scl_resid_ppt + scl_resid_agri + scl_resid_dam,
                       psi = MASS::psi.huber,
                       method = 'M',
                       data = data)
     
     mod0 <- MASS::rlm(log(response, 10) ~ log(area, 10) + log(p_branch, 10) + region +
-                                          scale(resid_temp) + scale(resid_ppt) + scale(resid_agri) + scale(resid_dam),
+                                          scl_resid_temp + scl_resid_ppt + scl_resid_agri + scl_resid_dam,
                       psi = MASS::psi.huber,
                       method = 'M',
                       data = data)

### 2021-08-17 code_empirical/figure_diversity.R

@@ -49,10 +49,10 @@
                  names_to = "metric")
   
   dat_base <- data.frame(region = factor(rep(c("hokkaido", "midwest"), each = 100)),
-                         resid_temp = 0,
-                         resid_ppt = 0,
-                         resid_agri = 0,
-                         resid_dam = 0)
+                         scl_resid_temp = 0,
+                         scl_resid_ppt = 0,
+                         scl_resid_agri = 0,
+                         scl_resid_dam = 0)
 
 # data frame for prediction -----------------------------------------------
   

### 2021-08-17 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 **Significance** Larger ecosystems support more species; this ubiquitous pattern is the foundation of current conservation schemes.
-However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such complexity in scaling biodiversity patterns is largely unknown.
+However, many ecosystems possess a complex spatial structure that cannot be represented by area, and the role of such complexity in regulating biodiversity patterns is largely unknown.
 Here, we use theory and extensive fish community data to show that ecosystem size and complexity dictate riverine biodiversity.
@@
 The complexity effect was comparable to the size effect, and this pattern has emerged regardless of ecological contexts.
-The dual scaling of biodiversity may be a pervasive feature that has far-reaching implications for biodiversity conservation.
+Our discovery illuminated a fundamental yet overlooked law in complex ecosystems, laying the groundwork for future research exploring macroecological patterns.
 
@@
 In particular, the emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
-First and foremost, there is now a clear need to explicitly consider the dimension of ecosystem complexity to achieve successful conservation.
-Human-induced habitat alterations, including flow regulation [@poffHomogenizationRegionalRiver2007], habitat fragmentation [@grillMappingWorldFreeflowing2019], and stream burial [@elmoreDisappearingHeadwatersPatterns2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
-Hence, it is imperative to recognize the role of branching complexity and minimize the homogenizing effects of human activities.
+First and foremost, the simplification of complex river networks may result in regional biodiversity loss via reduced environmental diversity.
+For example, flow regulation [@poffHomogenizationRegionalRiver2007], habitat fragmentation [@grillMappingWorldFreeflowing2019], and stream burial [@elmoreDisappearingHeadwatersPatterns2008] may compromise or restrict access to the diverse habitats that complex branching networks may support.
+Hence, our results illuminate the importance of preserving the structural complexity of ecosystems, providing empirical support for....
 Second, the complexity perspective may provide insights into the spatial planning of conservation efforts.
@@
 
-While the foundational concepts in ecology emphasize the importance of ecosystem size in biodiversity relationships [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
+Although the foundational concepts in ecology emphasize the importance of ecosystem size in biodiversity relationships [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves.
 However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure.
@@
 Recognizing the dual control of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it.
-The generalization of our discovery should therefore bring a paradigm shift in macroecological science with far-reaching implications for biodiversity conservation.
+The generalization of our discovery should therefore bring paradigm shifts in macroecological science with far-reaching implications for biodiversity conservation.
 

### 2021-08-17 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 The complexity effect was comparable to the size effect, and this pattern has emerged regardless of ecological contexts.
-Our discovery illuminated a fundamental yet overlooked law in complex ecosystems, laying the groundwork for future research exploring macroecological patterns.
+Our discovery illustrates a fundamental ecological law in complex ecosystems, laying the groundwork for future research exploring macroecological patterns.
 
@@
 In particular, the emerging complexity-diversity relationship points to several important avenues for riverine biodiversity conservation.
-First and foremost, the simplification of complex river networks may result in regional biodiversity loss via reduced environmental diversity.
-For example, flow regulation [@poffHomogenizationRegionalRiver2007], habitat fragmentation [@grillMappingWorldFreeflowing2019], and stream burial [@elmoreDisappearingHeadwatersPatterns2008] may compromise or restrict access to the diverse habitats that complex branching networks may support.
-Hence, our results illuminate the importance of preserving the structural complexity of ecosystems, providing empirical support for....
+First and foremost, any simplification of complex river networks may result in regional biodiversity loss via reduced environmental heterogeneity.
+Human-induced habitat alterations, including flow regulation [@poffHomogenizationRegionalRiver2007], habitat fragmentation [@grillMappingWorldFreeflowing2019], and stream burial [@elmoreDisappearingHeadwatersPatterns2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
+Hence, our results confirm the importance of preserving the structural complexity of ecosystems and support the modern conservation initiative that seeks to protect a diverse habitat portfolio [@schindlerPortfolioConceptEcology2015].
 Second, the complexity perspective may provide insights into the spatial planning of conservation efforts.
-Riverine reserves and local restoration are increasingly recognized as an effective management tool, and designing a spatial network of conservation sites in rivers is an area of active research [@koningNetworkGrassrootsReserves2020].
-While large reserves or restoration sites are undoubtedly important, our results indicate the potential of coordinated networks of local conservation sites in protecting biodiversity.
+Riverine reserves and local restoration are increasingly recognized as an effective management tool, and the spatial prioritization of conservation sites in rivers is an area of active research [@koningNetworkGrassrootsReserves2020].
+While the old "single large or several small" debate has led to a principle prioritizing a single large habitat [@diamondIslandDilemmaLessons1975], emerging perspectives posit the potential of coordinated networks of small habitats in protecting biodiversity [@fahrigWhySeveralSmall2020].
+Understanding the role of branching complexity helps design such networks.
 For example, synergies of multiple small reserves may emerge at the watershed scale when ecologically-distinct tributaries are involved in the design, as evidenced by the recent successful conservation of tropical fishes in Thailand's Salween basin [@koningNetworkGrassrootsReserves2020].

### 2021-08-17 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 
-**Abstract:** A prevailing paradigm suggests that species richness increases with area in a decelerating way; this ubiquitous power-law scaling, the species-area relationship, has formed the foundation of many conservation strategies.
+**Abstract:** A prevailing paradigm suggests that species richness increases with area in a decelerating way.
+This ubiquitous power-law scaling, the species-area relationship, has formed the foundation of many conservation strategies.
 In spatially complex ecosystems, however, the area may not be the sole dimension to scale biodiversity patterns because the scale-invariant complexity of fractal ecosystem structure may drive ecological dynamics in space.
@@
 Human-induced habitat alterations, including flow regulation [@poffHomogenizationRegionalRiver2007], habitat fragmentation [@grillMappingWorldFreeflowing2019], and stream burial [@elmoreDisappearingHeadwatersPatterns2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
-Hence, our results confirm the importance of preserving the structural complexity of ecosystems and support the modern conservation initiative that seeks to protect a diverse habitat portfolio [@schindlerPortfolioConceptEcology2015].
+Our findings underscore the importance of preserving the structural complexity of ecosystems and support the modern conservation initiative that seeks to protect a diverse habitat portfolio [@schindlerPortfolioConceptEcology2015].
 Second, the complexity perspective may provide insights into the spatial planning of conservation efforts.
@@
 We thank Illinois Environmental Protection Agency, Minnesota Pollution Control Agency, Iowa Department of Natural Resources, Wisconsin Department of Natural Resources, Michio Fukushima and Hirokazu Urabe for providing data for our empirical analysis.
-We thank Jacques Finlay for his constructive comments on the earlier version of the manuscript.
+We thank Jacques Finlay for his constructive comments on the earlier version of the manuscript and Tatsuya Amano, Nobuo Ishiyama, and Masashi Soga for their technical support.
 This material is based upon work supported by the National Science Foundation through the Water Sustainability and Climate Program Observatory grant (EAR‐1209402): REACH (Resilience under Accelerated Change) and through the Division of Environmental Biology (DEB 2015634), Environmental Protection Agency through the Water Quality Benefits grant (EPA-G2015-STAR-A1), the University of North Carolina at Greensboro through start-up funds, and the Japan Society for the Promotion of Science through the KAKENHI grant (20H03010).

### 2021-09-01 manuscript_pnas.Rmd
edits: update results

@@
 Human-induced habitat alterations, including flow regulation [@poffHomogenizationRegionalRiver2007], habitat fragmentation [@grillMappingWorldFreeflowing2019], and stream burial [@elmoreDisappearingHeadwatersPatterns2008], may compromise or restrict access to the diverse habitats that complex branching networks may support.
-Our findings underscore the importance of preserving the structural complexity of ecosystems and support the modern conservation initiative that seeks to protect a diverse habitat portfolio [@schindlerPortfolioConceptEcology2015].
+Our findings underscore the importance of preserving the structural complexity of ecosystems and support the modern conservation initiative that seeks to protect a diverse habitat portfolio [@schindlerPortfolioConceptEcology2015a].
 Second, the complexity perspective may provide insights into the spatial planning of conservation efforts.
@@
 We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]).
-We used Hydrologically Adjusted Elevations of MERIT Hydro [@yamazakiMERITHydroHighResolution2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area).
+We used MERIT Hydro [@yamazakiMERITHydroHighResolution2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area).
 The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0 [@yamazakiDevelopmentGlobal90m2015].
@@
 The Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehnerGlobalReservoirDam2011] was used to estimate dam density per unit watershed area (km^-2^).
-We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenningRSAGASAGAGeoprocessing2018], 'sf' [@pebesmaSimpleFeaturesStandardized2018] 'raster' [@hijmansRasterGeographicData2020] 'stars' [@pebesmaStarsSpatiotemporalArrays2020], and 'exactextractr' [@bastonExactextractrFastExtraction2020].
+We used ArcMap 10.7 and the following R packages to perform geospatial analysis: 'sf' [@pebesmaSimpleFeaturesStandardized2018] 'raster' [@hijmansRasterGeographicData2020] 'stars' [@pebesmaStarsSpatiotemporalArrays2020], and 'exactextractr' [@bastonExactextractrFastExtraction2020].
 
@@
 Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$.
-The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~A$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use (logit-transformed), and dam density.
+The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~A$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use, and dam density.
 Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically.

### 2021-09-01 supplementary_information_pnas.Rmd
edits: update results

@@
 Positive and negative correlations were colored in blue and red, respectively, and darker colors indicate stronger correlations.
-Environmental variables (temperature, precipitation, elevation, logit fraction of forest, logit fraction of urban, logit fraction of agriculture, and dam density) were expressed as deviations from the regional averages to remove any regional effects.
+Environmental variables (temperature, precipitation, elevation, fraction of forest, fraction of urban, fraction of agriculture, and dam density) were expressed as deviations from the regional averages to remove any regional effects.
 

### 2021-09-01 table_kable.Rmd
edits: minor correction for table 1
edits: update results

@@
             "Precipitation",
-            "Logit fraction of agriculture",
+            "Fraction of agriculture",
             "Dam density")
@@
 Response variables were log-10 transformed.
-Climate and land use variables (air temperature, precipitation, logit fraction of agriculture, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.
+Climate and land use variables (air temperature, precipitation, fraction of agriculture, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.
 

### 2021-09-10 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

@@
 Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically.
-We did not include the fractions of urban and forest land use in the statistical models because these variables were strongly correlated with the fraction of agricultural land use (**Figure S19**).
+We did not include the fractions of urban and forest land use in the statistical models because these variables were strongly correlated with the fraction of agricultural land use (**Figure S19**) or had a very limited range of values.
 Similarly, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**).

### 2021-09-14 manuscript_pnas.Rmd
edits: minor text edit

@@
 In this network, the number of habitat patches $N_p$ (a theoretical proxy for ecosystem size $A$) and branching probability $P_b$ (ecosystem complexity) shape the spatial structure (**Materials and Methods**).
-We introduced two factors determining the temporal mean of environmental condition at each habitat patch $\mu_z$: (1) headwater environments (the most upstream habitat patch) and (2) local environmental noise.
+We introduced two factors determining the temporal mean of environmental condition at each habitat patch $\mu_z$: headwater environments (the most upstream habitat patch) and local environmental noise.
 Environmental values at headwaters are drawn randomly from a normal distribution with a mean of zero and a standard deviation of $\sigma_h$ and propagate downstream.
